### 2020-09-25 main.tex
First commit

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
\usepackage{virginialake}

\parindent=0pt

\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]

\theoremstyle{definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{notation}[thm]{Notation}
\newtheorem{proposition}[thm]{Proposition}
\newtheorem{theorem_}[thm]{Theorem}
\newtheorem{example}[thm]{Example}
\newtheorem{remark}[thm]{Remark}

\title{On first-order combinatorial proofs}
\author{Jui-Hsuan Wu, Lutz Strassburger}

\begin{document}

\maketitle

\section{From skew bifibration to contraction/weakening}

\begin{theorem_}
Let $A$ and $B$ be two formulas and $f: G(A) \rightarrow G(B)$ a skew bifibration. Then there exists a derivation $\od{\odd{\odh {A}}{\Delta}{B}{\{\wD, \cD\}}}$.
\end{theorem_}

\begin{proof}
$f$ can be seen as a skew fibration from $G(A^P)$ to $G(B^P)$, which gives the existence of the propositions $A'$ and $B'$, and of the following derivation:
  \[\od{\odd{\odd{\odd{\odh{A^P} }
  {\Delta }{A'}{\me} }
  {\Delta’ }{B'}{\acD} }
  {\Delta’’}{B^P}{\wD}} \]

Now we prove that there exists $B''$ such that $B''^P$ = $B'$.

We consider now the dervation $\Delta''$. If some $U_x$ (or $E_x$) is introduced
via weakening, then all the atoms it binds in $B^P$ should also be introduced 
via weakening. In fact, an atom of $B^P$ is introduced via weakening is 
equivalent to the fact that its corresponding vertex is not in the image of $f$. 
Since there is an edge from $U_x$ (resp. $E_x$) to all the literals it binds in the 
binding graph $\overrightarrow{G(B)}$, if one of the atoms is in the image, 
$U_x$ (resp. $E_x$) should also be in the image since $f$ is a fibration on binding graphs.

This means that a such $B''$ can be obtained from $B$ by erasing all the $U_x$ and $E_x$ introduced via weakening and all the atoms they bind.

\end{proof}
\end{document}

### 2020-11-24 main.tex
Add some key elements

@@
 
-\usepackage{amsthm}
-\theoremstyle{plain}
+\usepackage{amsthm}\theoremstyle{plain}
 \newtheorem{thm}{Theorem}[section]
@@
 
-\begin{proof}
 $f$ can be seen as a skew fibration from $G(A^P)$ to $G(B^P)$, which gives the existence of the propositions $A'$ and $B'$, and of the following derivation:
@@
   {\Delta }{A'}{\me} }
-  {\Delta’ }{B'}{\acD} }
-  {\Delta’’}{B^P}{\wD}} \]
+  {\Delta' }{B'}{\acD} }
+  {\Delta''}{B^P}{\wD}} \]
 
-Now we prove that there exists $B''$ such that $B''^P$ = $B'$.
+\begin{lemma} there exists $B''$ such that $B''^P$ = $B'$.
 
-We consider now the dervation $\Delta''$. If some $U_x$ (or $E_x$) is introduced
+\begin{proof}
+Consider the dervation $\Delta''$. If some $U_x$ (or $E_x$) is introduced
 via weakening, then all the atoms it binds in $B^P$ should also be introduced 
@@
 This means that a such $B''$ can be obtained from $B$ by erasing all the $U_x$ and $E_x$ introduced via weakening and all the atoms they bind.
+\end{proof}
+\end{lemma}
+
+We introduce new (atomic) symbols $E_x^*$ and $U_x^*$ which are used to
+represent disjunctions of $E_x$ and $U_x$ respectiveley.
+
+We define a translation $(\cdot)^*$ inductively by:
+\begin{itemize}
+  \item $(E_x \vee \cdots \vee E_x)* = E_x^*$
+  \item $(U_x \vee \cdots \vee U_x)* = U_x^*$
+  \item structural recursion in all the other cases.
+\end{itemize}
+
+Then the derivation:
+ \[\od{\odd{\odd{\odh{A^P} }
+  {\Delta }{A'}{\me} }
+  {\Delta' }{B'}{\acD}} \]
+can be translated to the derivation:
+\[\od{\odd{\odh{(A^P)^*} }
+{\Delta^* }{(B')^*}{}} \]
+
+where $\Delta^*$ is the derivation obtained by replacing all the formulas $F$
+with $F^*$.
+
+Note that we should also introduce new rules in the derivation $\Delta^*$.
+Otherwise, the rule applications cannot work in general.
+
+To do that, we define the following rule transformation:
+
+\begin{center}
+\mbox{
+\begin{prooftree}
+  \hypo{Q_x^*}
+  \infer1[$\acD$]{Q_x^*}
+\end{prooftree}
+
+$\leadsto$
+
+\begin{prooftree}
+  \hypo{Q_x^*}
+  \infer1[$=$]{Q_x^*}
+\end{prooftree}
+
+}
+\vspace{0.4cm}
+
+\mbox{
+\begin{prooftree}
+  \hypo{(Q_x^* \wedge C) \vee (Q_x^* \wedge D)}
+  \infer1[$\me$]{Q_x^* \wedge (C \vee D)}
+\end{prooftree}
+
+$\leadsto$
+
+\begin{prooftree}
+  \hypo{(Q_x^* \wedge C) \vee (Q_x^* \wedge D)}
+  \infer1[$\me'$]{Q_x^* \wedge (C \vee D)}
+\end{prooftree}
+
+}
+
+\end{center}
+where $Q_x^*$ stands for $E_x^*$ or $U_x^*$.
+
+$\Delta^*$ can now be transformed into a valid derivation $\Delta_1$ by using the two
+transformation rules above and by applying them in a bottom-up theoremstyle:
+\[\od{\odd{\odh{(A^P)^*} }
+{\Delta_1 }{(B')^*}{\acD, \me, \me'}} \]
+
+\begin{lemma}
+Every line of $\Delta_1$ is a propositional encoding (by
+confounding $Q_x^*$ with $Q_x$).
+
+\begin{proof}
+We proceed by bottom-up induction in the derivation.
+Clearly, $B'*$ is a propositional encoding as there is no disjunction of $Q_x$
+in it.
+
+Now consider the $\me$ rule:
+\begin{prooftree}
+  \hypo{(C \wedge D) \vee (E \wedge F)}
+  \infer1[$\me$]{(C \vee E) \wedge (D \vee F)}
+\end{prooftree}
+
+Suppose that $(C \vee E) \wedge (D \vee F) = G^P$ for some $G$.
+Since $C \vee E$ cannot be $Q_x$ (otherwise, the rule applied would be
+$\me'$), $G$ can be written as $G_1 \wedge G_2$ with $C \vee E = G_1^P$ and $D
+\vee F = G_2^P$.
+
+We have thus $G_i = \forall x_i H_i$ or $J_i \vee K_i (i = 1, 2)$.
+
+If $G_i = \forall x H_i$ for some $i$, then there will a conjunction of $U_x*$
+and some formula which can never be eliminated by the rules $\me$, $\me'$ and
+$\acD$. However, there exists no such conjunction in ${A^P}^*$, which leads to a
+contradiction.
+
+Hence, $G_i$ can be written as $J_i \vee K_i$ for $i = 1, 2$. We now have $(C
+\wedge D) \vee (E \wedge F) = ((J_1 \wedge J_2) \vee (K_1 \wedge K_2))^P$.
 
 \end{proof}	
+\end{lemma}
 \end{document}

### 2020-11-24 main.tex
Finish a proof

@@
 \parindent=0pt
+\parskip=0.6em
 
@@
 
+First consider the $\acD$ rule:
+\begin{prooftree}
+  \hypo{C \vee C}
+  \infer1[$\acD$]{C}
+\end{prooftree}
+
+It is clear that if $C$ is a propositional encoding, then so is $C \vee C$.
+
 Now consider the $\me$ rule:
@@
 
-If $G_i = \forall x H_i$ for some $i$, then there will a conjunction of $U_x*$
+If $G_i = \forall x H_i$ for some $i$, then there will a conjunction of $U_x^*$
 and some formula which can never be eliminated by the rules $\me$, $\me'$ and
@@
 
+Finally, consider the $\me'$ rule:
+
+\begin{prooftree}
+  \hypo{(Q_x^* \wedge C) \vee (Q_x^* \wedge D)}
+  \infer1[$\me'$]{Q_x^* \wedge (C \vee D)}
+\end{prooftree}
+
+Suppose that $Q_X^* \wedge (C \vee D)$ = $F^P$ for some $P$. It is clear
+that $Q_x^* = E_x^*$ and $F = \exists x G$ with $G^P = C \vee D$ for some $G$.
+We distinguish two cases:
+\begin{itemize}
+  \item $G = \forall y H$: in this case, $(Q_x^* \wedge C) \vee (Q_x^* \wedge
+D)$ has a subformula $(E_x^* \wedge U_y^*)$, which cannot be eliminated by the
+rules $\me$, $\me'$, $\acD$. It is clear that ${A^P}^*$ does not
+have a subformula of this form, which leads to a contradiction.
+  \item $G = G_1 \vee G_2$: in this case, $(Q_x^* \wedge C) \vee (Q_x^* \wedge
+	  D) = ((\exists x G_1) \vee (\exists x G_2))^P$.
+\end{itemize}
+
 \end{proof}	
 \end{lemma}
+
 \end{document}

### 2020-11-30 main.tex
Add preliminaries

@@
 \usepackage{virginialake}
+\usepackage{cmll}
+\usepackage{tikz}
 
@@
 
-\section{From skew bifibration to contraction/weakening}
+\section{From first-order logic to combinatorial proofs}
+
+\subsection{{\bf LK}}
+We start with Gentzen's sequent calculus system {\bf LK}.
+
+\begin{center}
+
+\mbox{
+\begin{prooftree}
+  \infer0[$ax$]{\vdash A, \neg A}
+\end{prooftree}
+\hspace{2cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A}
+  \hypo{\vdash \Delta, \neg A}
+  \infer2[$cut$]{\vdash \Gamma, \Delta}
+\end{prooftree}}
+
+\mbox{
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A}
+  \hypo{\vdash \Delta, B}
+  \infer2[$\wedge$]{\vdash \Gamma, \Delta, A \wedge B}
+\end{prooftree}
+\hspace{1.5cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A, B}
+  \infer1[$\vee$]{\vdash \Gamma, A \vee B}
+\end{prooftree}}
+
+\mbox{
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A, A}
+  \infer1[$ctr$]{\vdash \Gamma, A}
+\end{prooftree}
+	\hspace{2cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma}
+  \infer1[$wk$]{\vdash \Gamma, A}
+\end{prooftree}}
+
+\mbox{
+\begin{prooftree}
+\infer0[$\ttt$]{\vdash \ttt}
+\end{prooftree}
+\hspace{2cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma}
+	\infer1[$\fff$]{\vdash \Gamma, \fff}
+\end{prooftree}}
+
+\mbox{
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A}
+  \infer1[$\forall$]{\vdash \Gamma, \forall x A}
+\end{prooftree}
+($x \notin fv(\Gamma)$)
+\hspace{2cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A[t/x]}
+  \infer1[$\exists$]{\vdash \Gamma, \exists x A}
+\end{prooftree}}
+
+\end{center}
+
+We also consider the mix rule here:
+
+\begin{center}
+\begin{prooftree}
+\hypo{\vdash \Gamma}
+\hypo{\vdash \Delta}
+\infer2[$mix$]{\vdash \Gamma, \Delta}
+\end{prooftree}
+\end{center}
+
+Note that the mix rule is derivable via weakening in {\bf LK}.
+
+Consider the following deep rules:
+\begin{center}
+\mbox{
+\begin{prooftree}
+  \hypo{\vdash S\{A \vee A\}}
+  \infer1[$\cD$]{\vdash S\{A\}}
+\end{prooftree}
+\hspace{2cm}
+
+\begin{prooftree}
+  \hypo{\vdash S\{\fff \}}
+  \infer1[$\wD$]{\vdash S\{A\}}
+\end{prooftree}
+}
+\end{center}
+
+Note that the $ctr$ (resp. $wk$) rule in {\bf LK} is derivable in $\{\cD, \vee\}$
+(resp. $\{\wD, \fff\}$) and that $\cD$ and $\wD$ rules
+permute downwards with the non-structural rules of {\bf LK}.
+
+\begin{center}
+\mbox{
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A, A}
+  \infer1[$ctr$]{\vdash \Gamma, A}
+\end{prooftree}
+
+$\ \leadsto \ $
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A, A}
+  \infer1[$\vee$]{\vdash \Gamma, A \vee A}
+  \infer1[$\cD$]{\vdash \Gamma, A}
+\end{prooftree}}
+\vspace{0.2cm}
+
+\mbox{
+\begin{prooftree}
+  \hypo{\vdash \Gamma}
+  \infer1[$wk$]{\vdash \Gamma, A}
+\end{prooftree}
+
+$\ \leadsto \ $
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma}
+  \infer1[$\fff$]{\vdash \Gamma, \fff}
+  \infer1[$\wD$]{\vdash \Gamma, A}
+\end{prooftree}}
+
+\end{center}
+
+We also give an example to show how rule permutation works:
+
+\begin{center}
+
+\mbox{
+\begin{prooftree}
+\hypo{\Gamma,A \vee A}
+\infer1[$\cD$]{\Gamma,A} 
+\hypo{\Delta,B}
+\infer2[$\wedge$]{\Gamma, \Delta, A \wedge B} 
+\end{prooftree}
+
+$\ \leadsto \ $
+
+\begin{prooftree}
+\hypo{\Gamma,A \vee A}
+\hypo{\Delta,B}
+\infer2[$\wedge$]{\Gamma, \Delta, (A \vee A) \wedge B} 
+\infer1[$\cD$]{\Gamma, \Delta, A \wedge B} 
+\end{prooftree}}
+
+\end{center}
+
+We want to establish the following theorem:
+
+\begin{theorem_}
+\label{thm1}
+Let $\Gamma$ be a sequent.
+Then there is a proof of $\Pi$ in {\bf LK} + $mix$ iff there is a proof of some sequent $\Delta$ in {\bf MLL1} + $mix$ and a derivation from $\Delta$ to $\Gamma$ consisting of the $\cD$ and $\wD$ rules only.
+\end{theorem_}
+
+\begin{proof}
+($\Rightarrow$) This direction comes from the above observation: it suffices to permute downwards all the instances of the $\cD$ and $\wD$ rules.
+
+($\Leftarrow$)
+We regard the proof in {\bf MLL1} + $mix$ as a proof in {\bf LK} + $mix$.
+Then we put the derivation consisting of only $\cD$ and $\wD$ under the proof in {\bf LK} + $mix$. Now we try to permute all the instances $\cD$ and $\wD$ upwards with the rules of LK and $mix$. 
+For the $\cD$ part, the only non-trivial case is the permutation with the $\vee$ rule where the formula generated is $A \vee A$.
+
+\begin{center}
+\mbox{
+\begin{prooftree}
+\hypo{\vdash \Gamma, A, A}
+\infer1[$\vee$]{\vdash \Gamma, A \vee A}
+\infer1[$\cD$]{\vdash \Gamma, A}
+\end{prooftree}
+
+$\ \leadsto \ $
+
+\begin{prooftree}
+\hypo{\vdash \Gamma, A, A}
+\infer1[$ctr$]{\vdash \Gamma, A}
+\end{prooftree}
+
+} 
+\end{center}
+
+In this case, the permutation of this instance of $\cD$ stops and we continue with the remaining instances.
+
+For the $\wD$ part, the only non-trivial case is the permutation with the $\fff$ rule (or the instance of $wk$ where $\fff$ is introduced):
+
+\begin{center}
+\mbox{
+\begin{prooftree}
+\hypo{\vdash \Gamma}
+\infer1[$\fff$]{\vdash \Gamma, f}
+\infer1[$\wD$]{\vdash \Gamma, A}
+\end{prooftree}
+
+$\ \leadsto \ $
+
+\begin{prooftree}
+\hypo{\vdash \Gamma}
+\infer1[$wk$]{\vdash \Gamma, A}
+\end{prooftree}
+
+} 
+\end{center}
+
+In this case, the permutation of this instance of $\wD$ stops and we continue with the remaining instances.
+
+\end{proof}
+
+\iffalse
+
+Now consider a proof $\Pi$ of some sequent $\Gamma$ in {\bf LK}:
+The observation above gives the possibility of
+transforming the proof into a proof in {\bf MLL} followed by a derivation consisting
+of the $\cD$ and $\wD$ rules only.
+
+Conversely, consider a proof $\Pi$ of some sequent $\Gamma$ consisting of a
+proof $\Pi'$ in {\bf LK} followed by a derivation $\Pi''$ consisting
+the $\cD$ and $\wD$ rules only. 
+We can assume that the proof $\Pi'$ is cut-free and contains only atomic
+axioms.
+Now consider some instance of $\cD$ in the derivation $\Pi''$:
+\begin{prooftree}
+  \hypo{S\{A \vee A\}} 
+  \infer1[$\cD$]{S\{A\}}
+\end{prooftree}
+
+If the subformula $A \vee A$ is erased at some point by the $\wD$ rule:
+
+\begin{center}
+\begin{prooftree}
+  \hypo{\vdash T\{\fff\}}
+  \infer1[$\wD$]{\vdash T\{B\}}
+  \ellipsis{$\mathcal{D}$}{\vdash S\{A \vee A\}}
+  \infer1[$\cD$]{\vdash S\{A\}}
+\end{prooftree}
+\end{center}
+
+where $A \vee A$ is a subformula of $B$, then we can erase the instance of $\cD$
+rule considered
+and obtain the derivation:
+
+\begin{center}
+\begin{prooftree}
+  \hypo{\vdash T\{\fff\}}
+  \infer1[$\wD$]{\vdash T\{B[A \vee A \leftarrow A]\}}
+  \ellipsis{$\mathcal{D}[A \vee A \leftarrow A]$}{\vdash S\{A\}}
+\end{prooftree}
+\end{center}
+
+where $B[A \vee A \leftarrow A]$ (resp. $\mathcal{D}[A \vee A \leftarrow A]$) is the
+formula (resp. derivation) obtained from $B$ (resp. $\mathcal{D}$) by replacing every
+occurrence of $A \vee A$ with $A$.
+
+Now suppose that the subformula $A \vee A$ is not erased in the derivation
+$\Pi''$.
+
+Since there is the contraction rule $ctr$, the subformula $A \vee A$ might be duplicated in the proof $\Pi'$. We now consider a branch of the proof $\Pi'$
+
+Since $\Pi'$ is cut-free, it enjoys the subformula property and since all axioms
+are atomic, the "subformula" $A \vee A$ should be decomposed at some point in the
+proof and thus the proof $\Pi$ should be of the following form:
+
+\begin{center}
+\begin{prooftree}
+  \hypo{\cdots}
+  \hypo{\vdash \Gamma, A, A}
+  \infer1[$\vee$]{\vdash \Gamma, A \vee A}
+  \ellipsis{$\mathcal{D}$}{}
+  \infer2[]{\vdash T\{A \vee A\}}
+  \ellipsis{$\mathcal{D}_1$}{\vdash S\{A \vee A\}}
+  \infer1[$\cD$]{\vdash S\{A\}}
+  \ellipsis{$\mathcal{D}_2$}{\vdash \Gamma}
+\end{prooftree}
+\end{center}
+
+where $\Pi'$ =
+\begin{prooftree}
+  \hypo{\vdash T\{A \vee A\}}
+  \ellipsis{}{\vdash \Gamma}
+\end{prooftree}
+
+We can thus to apply the $ctr$ rule first and to replace each occurrence of $A
+\vee A$ in the derivation (branch) $\mathcal{D}$:
+
+\begin{center}
+\begin{prooftree}
+  \hypo{\cdots}
+  \hypo{\vdash \Gamma, A, A}
+  \infer1[$ctr$]{\vdash \Gamma, A}
+  \ellipsis{$\mathcal{D}[A \vee A \leftarrow A]$}{}
+  \infer2[]{\vdash T\{A \vee A\}}
+  \ellipsis{$\mathcal{D}_1$}{\vdash S\{A \vee A\}}
+  \infer1[$\cD$]{\vdash S\{A\}}
+  \ellipsis{$\mathcal{D}_2$}{\vdash \Gamma}
+\end{prooftree}
+\end{center}
+
+By applying the same process to all the branches of occurrences of $A \vee A$,
+we obtain a proof of $\Gamma$ without the instance
+\begin{prooftree}
+  \hypo{S\{A \vee A\}}
+  \infer1[$\cD$]{S\{A\}}
+\end{prooftree}
+of the $\cD$ rule. The derivation $\Pi'$ can be replaced by the following:
+\begin{center}
+\begin{prooftree}
+  \hypo{\vdash T\{A\}}
+  \ellipsis{$\mathcal{D}_1[A \vee A \leftarrow A]$}{\vdash S\{A\}}
+  \ellipsis{$\mathcal{D}_2[A \vee A \leftarrow A]$}{\vdash \Gamma}
+\end{prooftree}
+\end{center}
+
+We can thus eliminate all the instances of the $\cD$ rule in the proof. Suppose
+now that the derivation $\Pi''$ consists of the $\wD$ rule only.
+
+[PROOF TO DO]
+
+\fi
+
+D. Hughes proves the soundness and completeness of
+unification nets with respect to {\bf MLL1} + $mix$. In the following, we establish the
+equivalence between unification nets and fonets.
+
+\subsection{Equivalence between unification nets and fonets}
+In the following, we usually confound a vertex with its label.
+
+We also confound $\parr$ with $\vee$ and $\otimes$ with $\wedge$ as unification
+nets and first-order nets (fonets) are defined in different contexts.
+
+\begin{definition} A \textit{switching path} of a unification structure $U(\lambda)$ is a path in a switching graph of $U(\lambda)$.
+\end{definition}
+
+\begin{definition} A \textit{switching path} of a  formula tree $F(\phi)$ is a path in $F(\phi)$ that does not go through both incoming edges of a $\parr$.
+\end{definition}
+
+\begin{proposition}
+\label{prop1}
+In a formula tree, the root is connected to every vertex by a switching path.
+\end{proposition}
+
+Now we give the key proposition relating a fograph to its corresponding formula
+tree.
+
+\begin{proposition}
+\label{prop2}
+Let $u$ and $v$ be two distinct vertices of a fograph $G(\phi)$, then we have the equivalence
+between:
+\begin{itemize}
+  \item $u$ and $v$ are adjacent in $G(\phi)$
+  \item $u$ and $v$ are connected by a switching path of $F(\phi)$, and if one of them is a universal quantifier, then the other is
+	not a descendant of the former.
+  \end{itemize}
+\begin{proof}
+By induction on $\phi$.
+\begin{itemize}
+  \item If $\phi$ is an atom, trivial.
+  \item If $\phi = \phi_1 \wedge \phi_2$, then we distinguish two cases:
+    \begin{itemize}
+      \item $u$ and $v$ are both in $\phi_1$ (resp. $\phi_2$): trivial by
+	      the induction hypothesis.
+      \item one of them is in $\phi_1$ and the other is in $\phi_2$: they are
+	      adjacent in $G(\phi)$ by definition. By Proposition \ref{prop1},
+		    the one in $\phi_1$ (resp. $\phi_2$) is connected to the
+		    vertex representing $\phi_1$ (resp. $\phi_2$) by a switching
+		    path. Together with the two edges incident to $\phi_1 \wedge
+		    \phi_2$, we obtain a switching path connecting $u$ and $v$.
+    \end{itemize}
+  \item If $\phi = \phi_1 \vee \phi_2$, then we distinguish two cases:
+    \begin{itemize}
+      \item $u$ and $v$ are both in $\phi_1$ (resp. $\phi_2$): trivial by
+	      the induction hypothesis.
+      \item one of them is in $\phi_1$ and the other is in $\phi_2$: they are not
+	      adjacent in $G(\phi)$ by definition. It is clear that they
+		    are not connected by a switching path.
+    \end{itemize}
+  \item If $\phi = \exists x \ \phi'$, then we distinguish two cases:
+    \begin{itemize}
+      \item $u$ and $v$ are both in $\phi'$: trivial by the induction
+	      hypothesis.
+      \item one of them is $\exists x$ and the other is in $\phi'$: trivial
+	      by Proposition \ref{prop1}
+
+    \end{itemize}
+  \item If $\phi = \forall x \ \phi'$, then we distinguish two cases:
+    \begin{itemize}
+      \item $u$ and $v$ are both in $\phi'$: trivial by the induction
+	      hypothesis.
+      \item one of them is $\forall x$ and the other is in $\phi'$:
+	they are not adjacent in $G(\phi)$ by definition and it is clear that
+		    the former is a descendant of $\forall x$.
+    \end{itemize}
+\end{itemize}
+\end{proof}
+\end{proposition}
+
+\begin{proposition}
+If there exists an induced bimatching of the linked fograph $G = G(\phi)$, then there exists a switching graph of the corresponding unification net which contains a cycle.
+\begin{proof}
+  Suppose that there exists a set $W$ inducing a bimatching in $G$.
+  Then $(W, E_G)$ and $(W, L_G)$ are matchings.\\
+  Let $E_W$ (resp. $L_W$) be the restriction of $E_G$ (resp. $L_G$) to $W$. \\
+  If $E_W \cap L_W \neq \emptyset$, then there exist $u$ and $v$ such that $uv
+  \in E_G$ and $uv \in L_G$. By Proposition \ref{prop2}, there exists a
+  switching path of the formula tree of $\phi$. Together with the leap
+  $uv$, this path induces a cycle in a switching graph of the
+  corresponding unification structure. \\
+  We can now suppose that $E_W$ and $L_W$ are disjoint. It is not difficult to
+  see the existence of an alternating and elementary cycle  in the bicoloured graph $(W, E_W \uplus L_W)$, i.e.
+a cycle of which the edges are alternately in $E_W$ and $L_W$ and containing no two equal vertices.
+  By Proposition \ref{prop2}, this cycle induces a cycle in the unification
+  structure. Now we want to construct a switching graph that contains this cycle.\\
+  Consider a universal quantifier $\forall x$. If $\forall x \notin W$, then        
+  we keep the incoming edge from its direct subformula and remove all the 
+  dependencies. Otherwise, since $(W, L_G)$ is a matching, there exists a
+  unique existential quantifier adjacent to $\forall x$ and we keep thus the
+  corresponding edge in the unification structure. \\
+  Now consider a $\parr$. We distinguish three cases:
+  \begin{itemize}
+    \item the cycle goes through none of the two branches (incoming edges) of
+	    the $\parr$: we can choose an
+	    arbitrary switching for this $\parr$
+    \item the cycle goes through exactly one branch: we choose the corresponding
+	    switching
+    \item the cycle goes through both branches:
+	    this means that there exist $v_L \in W$ (resp. $v_R$) in the left
+		  (resp. right) branch, $u_L$, $u_R \in W$, such that
+		  $u_Lv_L, u_Rv_R \in E_W$ and that the corresponding switching path from $u_L$ to $v_L$ (resp. from $u_R$ to $v_R$) goes through the left (resp. right) edge of $\parr$.
+
+    \begin{center}	
+    \begin{tikzpicture}
+    \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
+    \draw (0, 0) node (par) {$\parr$};
+    \draw (1, 1.7) node (dots1) {$\vdots$};
+    \draw (-1, 1.7) node (dots2) {$\vdots$};
+    \draw (1, 3.4) node (vr) {$v_R$};
+    \draw (-1, 3.4) node (vl) {$v_L$};
+    \draw (1.5, -1) node (dots3) {$\vdots$};
+    \draw (-1.5, -1) node (dots4) {$\vdots$};
+    \draw (2.9, -1) node (ul) {$u_L$};
+    \draw (-2.9, -1) node (ur) {$u_R$};
+    \draw (par) -- (dots1) [color=blue];
+    \draw (par) -- (dots2) [color=red];
+    \draw (dots1) -- (vr) [color=blue]; 
+    \draw (dots2) -- (vl) [color=red];
+    \draw (dots4) -- (ur) [color=blue]; 
+    \draw (dots3) -- (ul) [color=red];
+    \draw (dots4) -- (par) [color=blue]; 
+    \draw (dots3) -- (par) [color=red];
+    \end{tikzpicture}
+
+    {\bf Figure 7.} A schema showing that the two branches of the same $\parr$ cannot be used in the cycle at the same time. 
+    \end{center}
+
+    The red (resp. blue) path is the switching path corresponding to the edge $u_Lv_L$ (resp. $u_Rv_R$) in $E_W$.
+
+    It is clear that $u_L$ (resp. $u_R$) is not in the branches of the
+	 $\parr$. Otherwise, there will be no switching path from $u_L$ to $v_L$
+
+    By Proposition \ref{prop2}, we know that $u_L$ and $u_R$ are not
+	universal quantifiers which are ancestors the $\parr$
+	and that there exist one switching path from $u_L$ to $v_L$ and one
+	from $u_R$ to $v_R$. In particular, there exist one switching path from
+	$u_L$ to the $\parr$ and one from the $\parr$ to $v_R$, and by
+	concatenating the two, we obtain a switching path from $u_L$ to $v_R$. 
+	By Proposition \ref{prop2}, $u_L$ and $v_R$ are thus adjacent in $(W,
+	E_G)$, which is impossible since $(W, E_W)$ is a matching.
+  \end{itemize}
+  Notice that the switching paths here are in the underlying formula tree. We
+  have to verify that they are compatible with the choices of switching made for
+  universal quantifiers. That is, if $uv \in E_W$, then for all the
+  universal quantifiers $\forall x$ on the switching path (in the formula
+	tree), we have chosen in the first part of the proof to keep the only
+	edge from the child of $\forall x$ to itself. In fact, if there exists
+	a universal quantifier $w \in W$ on the switching path $u \rightarrow
+	v$, then one of $u$ and $v$ is not a descendant of $w$. Moreover, if
+	$u$ (resp. $v$) is a universal quantifier, then $w$ is not in its scope.
+	By Proposition \ref{prop2}, $\{wu, wv\} \cap E_W \neq \emptyset$, which
+	is impossible since $(W, E_W)$ is a matching.
+  We have thus constructed a switching graph containing this cycle.
+\end{proof}
+\end{proposition}
+
+\begin{proposition}
+If one of the switching graphs of the unification structure of $\phi$
+contains a cycle or is not connected, then there exists an induced bimatching of the
+corresponding linked fograph.
+
+\begin{proof}
+
+We use frames introduced by Hughes in Section 4 of \cite{Hughes 2015}.
+
+\begin{definition}
+Let $\theta$ be a unification structure on an {\bf MLL1} sequent $\Gamma$.
+We define the \textit{frame}  of $\theta$ by exhaustively applying the following subformula rewriting steps, to obtain a proof structure $\theta_m$ on an {\bf MLL} sequent $\Gamma_m$:
+
+\begin{enumerate}
+  \item {\bf Encode dependencies as fresh links.} For each dependency $\exists x \rightarrow \forall y$, with corresponding subformulas $\exists x A$ and $\forall y B$, we add a fresh link as follows.
+Let $P$ be a fresh (nullary) predicate symbol.
+Replace $\exists x A$ with $P \otimes \exists x A$ and $\forall y B$ with $\overline{P} \parr \forall y B$, and add an axiom link between $P$ and $\overline{P}$.
+  \item {\bf Erase quantifiers.} After step 1, erase all the quantifiers. (We no longer need their leaps since they are encoded as links in step 1.
+  \item {\bf Simplify atoms.} After step 2, replace every predicate $Pt_1 \cdots t_n$ with a nullary predicate symbol $P$.
+\end{enumerate}
+\end{definition}
+
+\begin{center}
+\mbox{
+\begin{tikzpicture}
+  \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
+  \draw (0, 0) node (par1) {$\parr$};
+  \draw (1.8, 1.2) node (z) {\color{blue} $\forall z$};
+  \draw (-1.8, 1.2) node (par2) {$\parr$};
+    \draw (-2.8, 2.4) node (x) {\color{red} $\exists x$};
+    \draw (-0.8, 2.4) node (y) {$\exists y$};
+    \draw (-2.8, 3.6) node (px) {$\overline{p}x$};
+    \draw (-0.8, 3.6) node (qy) {$\overline{q}y$};
+    \draw (1.8, 2.4) node (tens) {$\otimes$};
+    \draw (0.8, 3.6) node (pz) {$pz$};
+    \draw (2.8, 3.6) node (qfz) {$qfz$};
+    \draw (par1) -- (par2) [<-];
+    \draw (par1) -- (z) [<-];
+    \draw (par2) -- (x) [<-]; 
+    \draw (par2) -- (y) [<-];
+    \draw (x) -- (px) [<-]; 
+    \draw (y) -- (qy) [<-];
+    \draw (z) -- (tens) [<-]; 
+    \draw (tens) -- (pz) [<-];
+    \draw (tens) -- (qfz) [<-];
+    \draw (y) -- (z) [dotted, ->];
+    \draw (x) -- (z) [dotted, ->];
+    \draw[color=blue, dashed] (px) to [bend left] (pz);
+    \draw[color=red, dashed] (qy) to [bend left] (qfz);
+\end{tikzpicture}
+\hspace{0.5cm}
+
+\begin{tikzpicture}
+  \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
+  \draw (0, 0) node (par1) {$\parr$};
+  \draw (1, 0.9) node (par3) {\color{blue} $\parr$};
+  \draw (-1.8, 1.2) node (par2) {$\parr$};
+  \draw (-2.6, 2.4) node (tens1) {\color{red} $\otimes$};
+  \draw (-1, 2.4) node (tens2) {$\otimes$};
+  \draw (-2.2, 3.6) node (S) {\color{red} $S$};
+  \draw (-0.6, 3.6) node (R) {$R$};
+  \draw (-3, 3.6) node (nP) {$\overline{P}$};
+  \draw (-1.4, 3.6) node (nQ) {$\overline{Q}$};
+  \draw (0.4, 3.6) node (nS) {\color{blue} $\overline{S}$};
+  \draw (1.6, 1.8) node (par4) {$\parr$};
+  \draw (2.2, 2.7) node (tens3) {$\otimes$};
+  \draw (2, 3.6) node (P) {$P$};
+  \draw (2.8, 3.6) node (Q) {$Q$};
+  \draw (1.2, 3.6) node (nR) {$\overline{R}$};
+  \draw (par2) -- (par1) [->];
+  \draw (par3) -- (par1) [->];
+  \draw (tens1) -- (par2) [->];
+  \draw (tens2) -- (par2) [->];
+  \draw (nP) -- (tens1) [->];
+  \draw (S) -- (tens1) [->, color=red];
+  \draw (nQ) -- (tens2) [->];
+  \draw (R) -- (tens2) [->];
+  \draw (nS) -- (par3) [->, color=blue];
+  \draw (nR) -- (par4) [->];
+  \draw (tens3) -- (par4) [->];
+  \draw (P) -- (tens3) [->];
+  \draw (Q) -- (tens3) [->];
+  \draw (par4) -- (par3) [->];
+  \draw (nP) to [bend left] (P);
+  \draw (nQ) to [bend left] (Q);
+  \draw (S) to [bend left] (nS);
+  \draw (R) to [bend left] (nR);
+\end{tikzpicture}
+}
+
+{\bf Figure 8.} The unification net in Example \ref{exunif} and its frame. The colored part shows how the dependency ${\color{red} \exists x} \rightarrow {\color{blue} \forall z}$ is transformed.
+\end{center}
+
+We have the following results:
+
+Let $u$ and $v$ be atoms or quantifiers in a unification structure $\theta$.
+Then they are connected by a switching path in the unification structure if, and only if, their corresponding nodes are connected by a switching path in $\theta_m$.
+
+Consider now a switching graph $H$ of a unification structure $\theta$ of $\phi$.
+
+If $H$ contains a cycle, then the corresponding switching graph of $\theta_m$ also contains a cycle.
+Hence, by applying the propositional results (Theorem 7) from \cite{Retore 2003}, we conclude that there exists a chordless, alternating, and elementary cycle in the bicoloured graph ($W, E_W \uplus L_W$), which corresponds to an induced bimatching in the linked fograph.
+(Note that the linked fograph (cograph) corresponding to $\theta_m$ is equivalent to the one corresponding to $\theta$.)
+
+\iffalse
+Consider a switching graph.
+We associate to this switching graph a proof net for {\bf MLL} by replacing quantifiers with fresh atoms and dependencies with new axiom links using the following schema:
+
+\begin{center}	
+\mbox{
+    \begin{tikzpicture}
+    \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
+    \draw (0, -2) node (existsx) {$\exists x$};
+    \draw (0, 0) node (A) {$A$};
+    \draw (existsx) -- (A) ;
+    \end{tikzpicture}
+
+    \vspace{0.5cm}
+    \begin{tikzpicture}
+    \draw (0, 1) node
+    {$\leadsto$};
+    \draw (0, 2) node {};
+    \draw (0, 0) node {};
+    \end{tikzpicture}
+    \vspace{0.5cm}
+
+    \begin{tikzpicture}
+    \tikzstyle{every node}=[draw, circle, minimum size= 12 pt, inner sep=3pt]
+    \draw (0, 0) node (existx) {$E_x$};
+    \draw (1.2, -2) node (tens) {$\otimes$};
+    \draw (2.4, 0) node (A) {$A$};
+    \draw (tens) -- (A);
+    \draw (tens) -- (existx);
+    \end{tikzpicture}
+}
+\vspace{0.3cm}
+
+\mbox{
+    \begin{tikzpicture}
+    \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
+    \draw (0, -2) node (forallx) {$\forall x$};
+    \draw (0, 0) node (A) {$A$};
+    \draw (forallx) -- (A) ;
+    \end{tikzpicture}
+
+    \vspace{0.5cm}
+    \begin{tikzpicture}
+    \draw (0, 1) node
+    {$\leadsto$};
+    \draw (0, 2) node {};
+    \draw (0, 0) node {};
+    \end{tikzpicture}
+    \vspace{0.5cm}
+
+    \begin{tikzpicture}
+    \tikzstyle{every node}=[draw, circle, minimum size= 12 pt, inner sep=3pt]
+     \draw (0, 0) node (Ux) {$U_x$};
+    \draw (1.2, -2) node (parr) {$\parr$};
+    \draw (2.4, 0) node (A) {$A$};
+    \draw (parr) -- (A);
+    \draw (parr) -- (Ux);
+    \end{tikzpicture}
+}
+
+\mbox{
+    \begin{tikzpicture}
+    \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
+    \draw (-2, -2) node (existsx) {$\exists x$};
+    \draw (-2, 0) node (A) {$A$}; 
+    \draw (0, -2) node (forally) {$\forall y$};
+    \draw (0, 0) node (B) {$B$};
+    \draw (forally) -- (B);
+    \draw (existsx) -- (A);
+    \draw[->] (existsx) -- (forally);
+    \end{tikzpicture}
+
+    \vspace{0.5cm}
+    \begin{tikzpicture}
+    \draw (0, 1) node
+    {$\leadsto$};
+    \draw (0, 2) node {};
+    \draw (0, 0) node {};
+    \end{tikzpicture}
+    \vspace{0.5cm}
+
+    \begin{tikzpicture}
+    \tikzstyle{every node}=[draw, circle, minimum size= 12 pt, inner sep=3pt]
+    \draw (4.8, 0) node (Uy) {$U_y$};
+    \draw (6, -2) node (parr) {$\parr$};
+    \draw (7.2, 0) node (B) {$B$};
+    \draw (parr) -- (B);
+    \draw (parr) -- (Uy);
+    \draw (2.4, 0) node (existx) {$E_x$};
+    \draw (1.2, -2) node (tens) {$\otimes$};
+    \draw (0, 0) node (A) {$A$};
+    \draw (tens) -- (A);
+    \draw (tens) -- (existx);
+    \draw (3.6, 2) node (ax) {$ax$};
+    \draw (ax) to [bend right] (existx);
+    \draw (ax) to [bend left] (Uy);
+
+    \end{tikzpicture}
+}
+\end{center}
+\fi
+
+\end{proof}
+
+\iffalse
+
+\begin{proof}
+Let $C$ be a cycle contained in a switching graph. We can suppose that $C$ is
+minimum, i.e., for all $V' \subsetneq V $, there is no cycle going through exactly $V'$ in a switching graph of the unification structure, where $V$ is the set of vertices of $C$.
+
+Now write $C$ as the
+concatenation of $l_1, p_1, l_2, p_2, ..., l_n, p_n$ where the $l_i$ are
+leaps and the $p_i$ are paths consisting of the other edges. We first prove that
+for all $i$, $p_i$ is non-empty.
+
+Suppose that $p_k$ is empty. The only possible case is:
+\begin{center}
+\begin{tikzpicture}
+  \node (x0) at (0, 0) {$\forall y$};
+  \node (x1) at (2, 0) {$\exists x$};
+  \node (x2) at (4, 0) {$\forall z$}; 
+  \draw [->] (x1) -- (x0) node [midway, above=7pt] {$l_k$};
+  \draw [->] (x1) -- (x2) node [midway, above=7pt] {$l_{k+1}$};
+\end{tikzpicture}
+\end{center}
+
+This means that every unifier of the unification structure assigns a term
+containing $y$ and $z$ to the existential binder $x$, which also implies
+the existence of an atom which is a descendant of the $\exists x$. Without loss of
+generality, we can assume that the predual of this atom is in the scope
+of $\forall y$, then it must contain $y$ and $z$, which is contradictory.
+
+Hence, all the $p_i$ are non-empty.
+
+Let $u_i$ and $v_i$ be the two extremes of the path $p_i$. Since $C$ is
+elementary, $u_i$ and $v_i$ are distinct. If one of them, say $u_i$, is a
+universal quantifier $\forall x$, then $v_i$ is not in its scope. In fact, since a
+dependency edge incident to $\forall x$ is in the switching graph, the
+incoming edge from the direct subterm of $\forall x$ to $\forall x$ in the
+unification structure is removed in the switching graph.\\
+Hence, $u_i$ and $v_i$ are adjacent in the corresponding fograph by proposition
+\ref{prop2}.
+
+We now prove that $W = \{u_i | 1 \leq i \leq n \} \cup \{v_i | 1 \leq i \leq n \}$ induces a bimatching in the corresponding linked fograph.
+
+If $u_i$ and $u_j$ (resp. $v_j$ ($i \neq j$) are adjacent in the fograph, then $C$ is not minimum. Hence $u_i$ and $v_i$ are the only neighbours to each other in the fograph.
+
+The reasoning for proving that $p_k$ is non-empty also proves that every existential quantifier has a unique neighbour in the leap graph.
+The uniqueness of neighbours of universal quantifiers in the leap graph is guaranteed by the definition of switching graph.
+
+\end{proof}
+\fi
+\end{proposition}
+
+\subsection{From contraction/weakening to skew bifibrations}
+
+We first introduce the atomic contraction rule, the medial rule, and two rules
+on quantifiers.
+
+\begin{center}
+\mbox{
+\begin{prooftree}
+  \hypo{\vdash S\{a \vee a\}}
+  \infer1[$\acD$]{\vdash S\{a\}}
+\end{prooftree}
+\hspace{0.3cm}
+
+\begin{prooftree}
+  \hypo{\vdash S\{(A \wedge B) \vee (C \wedge D)\}}
+  \infer1[$\me$]{\vdash S\{(A \vee C) \wedge (B \vee D)\}}
+\end{prooftree}
+\hspace{0.3cm}
+
+\begin{prooftree}
+  \hypo{\vdash S\{\exists x A \vee \exists x B\}}
+  \infer1[$\mee$]{\vdash S\{\exists x (A \vee B)\}}
+\end{prooftree}	
+\hspace{0.3cm}
+
+\begin{prooftree}
+  \hypo{\vdash S\{\forall x A \vee \forall x B\}}
+  \infer1[$\meee$]{\vdash S\{\forall x (A \vee B)\}}
+\end{prooftree}	
+}
+\end{center}
+
+Here, we also consider the equivalence generated by the associativity, commutativity of $\vee$ and the equations $\ttt \vee A \equiv \ttt$ and $\fff \vee A \equiv A$.
+
+Now we have the following lemma:
+
+\begin{lemma}
+\label{lemma_ctr}
+The contraction rule $\cD$ is derivable for $\{\acD, \me, \mee, \meee\}$.
+\end{lemma}
+\begin{proof}
+	We prove that there is always $\vlderivation{\vlde{}{\{\acD, \me, \mee,
+	\meee\}}{A}{\vlhy {A \vee A}}}$ by structural induction on $A$.
+\begin{itemize}
+  \item If $A = \ttt$ or $A = \fff$, we have 
+	  \begin{prooftree} 
+	    \hypo{\vdash S\{A \vee A\}}
+	    \infer1[$\equiv$]{\vdash S\{A\}}
+	  \end{prooftree}. (the premiss and the conclusion are equivalent)
+  \item If $A = a$, then we have 
+	  \begin{prooftree}
+	    \hypo{\vdash S\{a \vee a\}}
+	    \infer1[$\acD$]{\vdash S\{a\}}.
+	  \end{prooftree}
+  \item If $A = A_1 \vee A_2$, then by the induction hypothesis, we have 
+	  $\vlderivation{\vlde{}{\{\acD, \me, \mee,
+	\meee\}}{A_i}{\vlhy {A_i \vee A_i}}}$ for $i = 1, 2$.
+
+	Hence, we have
+	\begin{prooftree}
+	  \hypo{\vdash S\{(A_1 \vee A_2) \vee (A_1 \vee A_2)\}}
+	  \infer1[$\equiv$]{\vdash S\{(A_1 \vee A_1) \vee (A_2 \vee A_2)\}}
+	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
+		   {\vdash S\{A_1 \vee (A_2 \vee A_2)\}}
+	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
+		   {\vdash S\{A_1 \vee A_2\}}
+	\end{prooftree}
+  \item If $A = A_1 \wedge A_2$, then by the induction hypothesis, we have 
+$\vlderivation{\vlde{}{\{\acD, \me, \mee, \meee\}}{A_i}
+	      {\vlhy {A_i \vee A_i}}}$ for $i = 1, 2$.
+
+ 	Hence, we have
+	\begin{prooftree}
+	  \hypo{\vdash S\{(A_1 \wedge A_2) \vee (A_1 \wedge A_2)\}}
+	  \infer1[$\me$]{\vdash S\{(A_1 \vee A_1) \wedge (A_2 \vee A_2)\}}
+	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
+		   {\vdash S\{A_1 \wedge (A_2 \vee A_2)\}}
+	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
+		   {\vdash S\{A_1 \wedge A_2\}}
+	\end{prooftree}
+  \item If $A = \exists x A'$, then by the induction hypothesis, we have $\vlderivation{\vlde{}{\{\acD, \me, \mee,
+	\meee\}}{A'}{\vlhy {A' \vee A'}}}$.
+
+	Hence, we have
+	\begin{prooftree}
+	  \hypo{\vdash S\{\exists x A' \vee \exists x A'\}}
+ 	  \infer1[$\mee$]{\vdash S\{\exists x (A' \vee A')\}}
+	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
+		   {\vdash S\{\exists x A'\}}
+	\end{prooftree}
+  \item If $A = \forall x A'$, then by the induction hypothesis, we have $\vlderivation{\vlde{}{\{\acD, \me, \mee,
+	\meee\}}{A'}{\vlhy {A' \vee A'}}}$.
+
+	Hence, we have
+	\begin{prooftree}
+	  \hypo{\vdash S\{\forall x A' \vee \forall x A'\}}
+ 	  \infer1[$\meee$]{\vdash S\{\forall x (A' \vee A')\}}
+	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
+		   {\vdash S\{\forall x A'\}}
+	\end{prooftree}
+
+\end{itemize}
+
+\end{proof}
+
+\begin{lemma}
+The rules $\mee$ and $\meee$ are derivable for $\{\wD, \cD\}$.
+\end{lemma}
+
+\begin{proof}
+We have:
+\begin{center}
+\begin{prooftree}
+\hypo{\exists x A}
+\infer1[$\equiv$]{\exists x (A \vee \fff)}
+\infer1[$\wD$]{\exists x (A \vee B)}
+\end{prooftree}
+\hspace{0.5cm}
+and 
+\hspace{0.5cm}
+\begin{prooftree}
+\hypo{\exists x B}
+\infer1[$\equiv$]{\exists x (\fff \vee B)}
+\infer1[$\wD$]{\exists x (A \vee B)}
+\end{prooftree}
+\end{center}
+Thus, we have:
+
+\begin{center}
+\begin{prooftree}
+\hypo{\exists x A \vee \exists x B}
+\ellipsis{}{\exists x (A \vee B) \vee \exists x (A \vee B)}
+\infer1[$\cD$]{\exists x (A \vee B)}
+\end{prooftree}
+\end{center}
+Similar for $\meee$.
+\end{proof}
+
+Now we define a propositional encoding for first-order formulas.
+
+\begin{definition}
+The propositional encoding $A^P$ of a formula $A$ is defined inductively by:
+
+\begin{centering}
+	$a^P = a$ for every atom $a$
+
+	$(A \vee B)^P = A^P \vee B^P$ \hspace{2cm} $(A \wedge B)^P = A^P \wedge B^P$
+
+	$(\forall x A)^P = U_x \vee A^P$ \hspace{2cm} $(\exists x A)^P = E_x \wedge A^P$
+
+\end{centering}
+where $U_x$ and $E_x$ are fresh nullary atoms.
+
+\end{definition}
+
+Similarly, we can define the propositional encoding $S^P$ of a context $S$ inductively by setting $\Box^P = \Box$. Note that $S^P$ is also an encoding.
+
+We have the following facts:
+
+\begin{proposition}
+For any context $S$ and any formula $A$:
+\begin{itemize}
+  \item $A^P$ is a formula containing no quantifier for any formula $A$.
+  \item $G(A^P) = G(A)$ by confounding the atoms $U_x$, $E_x$ with the variable
+	  $x$. Thus, a map $f : G(A^P) \rightarrow G(B^P)$ can be seen as a map
+		$f : G(A) \rightarrow G(B)$.
+  \item $(S\{A\})^P = S^P\{A^P\}$.
+\end{itemize}
+
+\end{proposition}
+
+\begin{proposition}
+\label{prop311}
+Let $A$ and $B$ be two formulas such that
+$\od{\odd{\odh {A}}{}{B}{\{\wD, \cD\}}}$. Then 
+$\od{\odd{\odh {A^P}}{}{B^P}{\{\wD, \cD\}}}$.
+\end{proposition}
+
+\iffalse
+\begin{proof}
+
+We say that a rule \begin{prooftree} \hypo{C} \infer1[]{D} \end{prooftree}
+is $P$-derivable for $\{\wD, \cD\}$ if
+        $\od{\odd{\odh {C^P}}{}{D^P}{\{\wD, \cD\}}}$.
+
+We now prove that $\wD$ and $\cD$ are
+	$P$-derivable for $\{\wD, \cD\}$.
+
+\begin{itemize}
+\item $\wD$ is $P$-derivable: we have
+  \begin{prooftree}
+    \hypo{S^P\{\fff\}}
+    \infer1[$\wD$]{S^P\{C^P\}}
+  \end{prooftree}
+
+\item $\cD$ is $P$-derivable: we have
+  \begin{prooftree}
+    \hypo{S^P\{C^P \vee C^P\}}
+    \infer1[$\cD$]{S^P\{C^P\}}
+  \end{prooftree}
+
+\end{itemize}
+
+Hence, $\od{\odd{\odh {A^P}}{}{B^P}{\{\wD, \cD\}}}$.
+
+\end{proof}
+\fi
+
+\begin{lemma}
+\label{mlem}
+	Given two formulas $A$ and $B$ and a derivation $\od{\odd{\odh {A}}
+	{\Delta}{B}{\{\wD, \cD\}}}$, then there exists a skew bifibration $G(A)
+	\rightarrow G(B)$.
+\end{lemma}
+
+\begin{proof}
+By Lemma \ref{lemma_ctr}, there exists a derivation $\od{\odd{\odh {A}}
+	{\Delta}{B}{\{\wD, \acD, \me, \mee, \meee \}}}$.
+
+For each rule from $\{\wD, \acD, \me, \mee, \meee \}$, we define a map and show that it is a skew fibration.
+
+\begin{itemize}
+  \item \begin{prooftree}
+  \hypo{\vdash S\{\fff \}}
+  \infer1[$\wD$]{\vdash S\{A\}}
+\end{prooftree}:
+
+  the map $wk$ maps $\fff$ to anything and is identity elsewhere.
+
+  \item
+    \begin{prooftree}
+      \hypo{\vdash S\{a \vee a\}}
+       \infer1[$\acD$]{\vdash S\{a\}} 
+    \end{prooftree}:
+
+    the map $ac$ maps the two $a$-labelled literals in the premise to the $a$-labelled literal in the conclusion.
+
+  \item 
+    \begin{prooftree}
+      \hypo{\vdash S\{(A \wedge B) \vee (C \wedge D)\}}
+      \infer1[$\me$]{\vdash S\{(A \vee C) \wedge (B \vee D)\}}
+    \end{prooftree}:
+
+    the map $m$ is the canonical identity that maps $A$ to $A$, $\cdots$, $D$ to $D$.
+  \item 
+    \begin{prooftree}
+      \hypo{\vdash S\{\exists x A \vee \exists x B\}}
+      \infer1[$\mee$]{\vdash S\{\exists x (A \vee B)\}}
+    \end{prooftree}:
+
+    the map $m_1$ maps the two $x$-labelled binders in the premise to the $x$-labelled binder in the conclusion,  $A$ to $A$ and $B$ to $B$.
+  \item
+    \begin{prooftree}
+      \hypo{\vdash S\{\forall x A \vee \forall x B\}}
+      \infer1[$\meee$]{\vdash S\{\forall x (A \vee B)\}}
+    \end{prooftree}:
+
+    the map $m_2$ maps the two $x$-labelled binders in the premise to the $x$-labelled binder in the conclusion,  $A$ to $A$ and $B$ to $B$.
+
+\end{itemize}
+
+By considering propositional encodings, the maps defined are label-preserving skew fibrations on the underlying fographs according to \cite{Strassburger 2007}.
+
+Now we prove that each map $g \in \{wk, ac, m, m_1, m_2 \}$ is a skew bifibration.
+To do that, it suffices to prove that $g$ is a fibration between the corresponding binding graphs since it is already a skew fibration on the corresponding fographs and it is label-preserving and existential-preserving.
+\begin{center}
+	for each $x$-binder $b$ in $G(B^P)$, for each vertex $v \in V(G(A^P))$
+such that $g(v)$ is bound by $b$, there exists a unique binder $b'$ such
+that $b'$ binds $v$.
+\end{center}
+
+\begin{itemize}
+  \item $wk$ and $m$ are clearly fibrations: the binding relations of the premise and the conclusion are exactly the same.
+  \item $ac$ is a fibration: suppose that $a$ that in the conclusion $a$ is bound by some quantifier $b$ in $S$, then for each of its preimages by $ac$, there exists exactly one binder (in fact, $b$) in $S$ that binds it.
+  \item $m_1$ and $m_2$ are fibrations: in the conclusion, for every atom $a$ in $A \vee B$ bound by the $x$-labelled quantifier, $a$ has exactly one preimage and it is bound by the $x$-llabelled quantifier in the premise.
+\end{itemize}
+
+  Therefore, all of these maps are skew bifibrations and since skew bifibrations on fographs compose (Lemma 10.32, \cite{Hughes 2019}), there exists a skew bifibration from $G(A)$ to $G(B)$.
+
+\iffalse
+
+By Proposition \ref{prop311}, $\od{\odd{\odh {A^P}}{}{B^P}{\{\wD, \cD\}}}$.
+Since both $A^P$ and $B^P$ are propositional (without quantifier), we
+can place ourselves in a propositional setting. We have thus a skew
+fibration $f$ from $G(A^P) = G(A)$ to $G(B^P) = G(B)$ by Theorem 7.8
+of \cite{Strassburger 2007}. To check that it is a skew bifibration, it suffices to check that:
+\begin{center}
+	for each $x$-binder $b$ in $G(B^P)$, for each vertex $v \in V(G(A^P))$
+such that $f(v)$ is bound by $b$, there exists a unique binder $b'$ such
+that $b'$ binds $v$.
+\end{center}
+
+According to \cite{Strassburger 2007}, a such map $f$ can be seen as a
+composition of:
+\begin{itemize}
+  \item an identity map on labels $i: G(A^P) \rightarrow G(C)$ which is a skew fibration,
+  \item a label-preserving atomic contraction map $c: G(C) \rightarrow G(D)$, i.e., a
+	surjective skew fibration such that for all $u, v \in V_{G(C)}$,
+	we have $u \frown_{C} v$ iff $c(u) \frown_{D} c(v)$, and
+  \item a label-preserving weakening map $w: G(D) \rightarrow G(B^P)$, i.e., an
+	injective skew fibration such that for all $u, v \in V_{G(D)}$, we have 
+	$u \frown_{D} v$ iff $w(u) \frown_{B^P} w(v)$.
+
+\end{itemize}
+Here, $u \frown_{C} v$ means that the first common ancestor of $u$ and $v$ in
+the "propositional" formula $C$ is a $\wedge$, i.e., $u$ and $v$ are adjacent in
+$G(C)$.
+
+	Let $b$ be an $x$-binder in $G(B)$ and let $v \in V_{G(A^P)}$. Suppose that $f(v)$ is bound by $b$.
+
+We distinguish two cases:
+\begin{itemize}
+	\item $b$ is existential: $b$ and $f(v)$ are adjacent in $V_{G(B)}$ since
+	$f(v)$ is in the scope of $b$ and its atom contains $x$. Hence, the
+	$E_x$-labelled vertex $u$ corresponding to $b$ is such that
+	$u \frown_{B^P} f(v) = w(c(v))$. \\
+	Now we prove that $u$ is in the image of $w$. Since $w$ is a skew
+	fibration, there exists $\tilde{u} \in V_{G(D)}$ such that
+		$\tilde{u} \frown_{D} c(v)$ and $w(\tilde{u}) \nfrown_{B^P} u$.
+	Suppose that $w(\tilde{u}) \neq u$.
+	We distinguish two cases:
+	\begin{itemize}
+	  \item $w(\tilde{u})$ corresponds to a descendant of $b$ in $B$: we have $w(\tilde{u}) \frown_{B^P} u$ by definition of $B^P$, which is contradictory.
+	  \item $w(\tilde{u})$ does not correspond to a descendant of $b$ in $B$: this implies that in $B^P$, $b$ is a descendant of the first common ancestor of $w(\tilde{u})$ and $f(v)$ .
+We have also $w(\tilde{u}) \frown {B^P} f(v)$.
+Hence, the first common ancestor of $b$ and $w(\tilde{u})$ is equal to the latter.
+We have thus $w(\tilde{u}) \frown_{B^P}$, which is again contradictory.
+  \end{itemize}
+  Hence, $w(\tilde{u}) = u$.
+  And since $w$ is injective, such $\tilde{u}$ is unique.
+  We have thus a unique u such that $w(\tilde{u}) \frown_{B^P} f(v) = w(c(v))$, which is equivalent to $\tilde{u} \frown_{D} c(v)$.
+Since $c$ is a skew fibration, there exists $\tilde{\tilde{u}} \in V_(G(C))$ such that $\tilde{\tilde{u}} \frown{C} v$ and
+  $c(\tilde{\tilde{u}}) \nfrown_{D} \tilde{u}$.
+  The same reasoning as the previous one proves that $c(\tilde{\tilde{u}}) = \tilde{u}$.  
+  \item 
+\end{itemize}
+
+\fi
+
+\end{proof}
+
+\begin{theorem_}
+If a formula $\phi$ is provable in {\bf LK}, then it has a combinatorial proof.
+\end{theorem_}
+
+\begin{proof}
+By Theorem \ref{thm1}, there exists a formula $\phi'$ such that there is a proof $\Pi$ of $\phi'$ in {\bf MLL1} and a derivation $D$ from $\phi'$ to $\phi$ consisting of the $\wD$ and $\cD$ rules only.
+The proof $\Pi$ corresponds to a unique unification net which is equivalent to the fonet corresponding to $\Pi$, i.e., the fograph $G(\phi')$ together with the links of $\Pi$.
+By Lemma \ref{mlem}, there exists a skew bifibration $G(\phi') \rightarrow G(\phi)$.
+We have thus a combinatorial proof of $\phi$.
+
+\end{proof}
+
+\subsection{From skew bifibrations to contraction/weakening}
 
@@
 $\Delta^*$ can now be transformed into a valid derivation $\Delta_1$ by using the two
-transformation rules above and by applying them in a bottom-up theoremstyle:
+transformation rules above and by applying them in a bottom-up style:
 \[\od{\odd{\odh{(A^P)^*} }
@@
 
-If $G_i = \forall x H_i$ for some $i$, then there will a conjunction of $U_x^*$
+If $G_i = \forall x H_i$ for some $i$, then there will be a conjunction of $U_x^*$
 and some formula which can never be eliminated by the rules $\me$, $\me'$ and

### 2020-12-17 bibliography.tex
Add the bibliography

\vspace{-0.3em}
\bibliographystyle{abbrv}
\begin{thebibliography}{99}

\bibitem{AS 2019}
  Matteo Acclavio and Lutz Straßburger. On Combinatorial Proofs for Modal Logic. In \textit{International Conference on Automated Reasoning with Analytic Tableaux and Related Methods}, London, 2019. Springer.

\bibitem{BT 2001}
  Kai Brünnler and Alwen Tiu. A local system for classical logic. In R. Nieuwenhuis and A. Voronkov, editors, \textit{LPAR 2001}, volume 2250 of \textit{Lecture Notes in Artificial Intelligence}, pages 347-361, 2001. Springer.

\bibitem{Gentzen 1935}
  Gerhard Gentzen. Investigations into logical deduction. In M. E. Szabo, editor, \textit{The Collected Papers of Gerhard Gentzen}, pages 68-131. North-Holland, Amsterdam, 1935.

\bibitem{Hughes 2006}
  Dominic J. D. Hughes. Proofs without syntax. \textit{Annals of Mathematics}, 164(3):1065-1076, 2006.

\bibitem{Hughes 2015}
  Dominic J. D. Hughes.  Unification nets: canonical proof net quantifiers. In \textit{Proc. LICS '18}, 2018.

\bibitem{Hughes 2019}
  Dominic J. D. Hughes. First-order proofs without syntax. Available at arXiv.org, 2019.

\bibitem{Strassburger 2007}
	Lutz Straßburger. A characterization of medial as rewriting rule. In
		\textit{International Conference on Rewriting Techniques and
		Applications}, pages 344-358. Springer, 2007.

\end{thebibliography}

### 2020-12-17 main.tex
Add the bibliography

@@
 \usepackage{tikz}
-
-\parindent=0pt
-\parskip=0.6em
+\usepackage{natbib}
+
+\parindent=0pt % indent spacing
+\parskip=0.6em % spacing between two paragraphs
+\setlength{\bibsep}{1.2ex} % bibliography vertical spacing
 
@@
 \subsection{{\bf LK}}
-We start with Gentzen's sequent calculus system {\bf LK}.
+We start with Gentzen's sequent calculus system {\bf LK} \cite{Gentzen 1935}.
 
@@
 
-Consider the following deep rules:
+Consider the following deep rules \cite{BT 2001}:
 \begin{center}
@@
 
-D. Hughes proves the soundness and completeness of
+D. Hughes proves in \cite{Hughes 2019} the soundness and completeness of
 unification nets with respect to {\bf MLL1} + $mix$. In the following, we establish the
@@
 
+\input{bibliography}
 \end{document}

### 2020-12-21 main.tex
Add the style file

@@
-\documentclass{article}
+%% bare_conf.tex
+%% V1.4b
+%% 2015/08/26
+%% by Michael Shell
+%% See:
+%% http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
+%% conference paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/pkg/ieeetran
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall the IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. The IEEE's font choices and paper sizes can   ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+\documentclass[conference]{IEEEtran}
+% Some Computer Society conferences also require the compsoc mode option,
+% but others use the standard conference format.
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[conference]{../sty/IEEEtran}
+
+% *** PACKAGES *** %
+
 \usepackage[utf8]{inputenc}
@@
 \usepackage{natbib}
-
-\parindent=0pt % indent spacing
-\parskip=0.6em % spacing between two paragraphs
-\setlength{\bibsep}{1.2ex} % bibliography vertical spacing
-
 \usepackage{amsthm}\theoremstyle{plain}
@@
 
-\title{On first-order combinatorial proofs}
-\author{Jui-Hsuan Wu, Lutz Strassburger}
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/pkg/ifpdf
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
+%
+%\usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of the IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off
+% such as if a citation ever needs to be enclosed in parenthesis.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% The latest version can be obtained at:
+% http://www.ctan.org/pkg/cite
+% The documentation is contained in the cite.sty file itself.
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  % \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at: 
+% http://www.ctan.org/pkg/graphicx
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/pkg/epslatex
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+%\usepackage{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics.
+%
+% Note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/amsmath
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/pkg/algorithms
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/pkg/algorithmicx
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/array
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+% *** SUBFIGURE PACKAGES ***
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false,font=footnotesize]{subfig}
+%\fi
+% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
+% for subfigure.sty, the latter of which is no longer maintained and is
+% incompatible with some LaTeX packages including fixltx2e. However,
+% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
+% which will override IEEEtran.cls' handling of captions and this will result
+% in non-IEEE style figure/table captions. To prevent this problem, be sure
+% and invoke subfig.sty's "caption=false" package option (available since
+% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
+% handling of captions.
+% Note that the Computer Society format requires a larger sans serif font
+% than the serif footnote size font used in traditional IEEE formatting
+% and thus the need to invoke different subfig.sty package options depending
+% on whether compsoc mode has been enabled.
+%
+% The latest version and documentation of subfig.sty can be obtained at:
+% http://www.ctan.org/pkg/subfig
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure.
+% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
+% corrections already built into the system in which case a warning will
+% be issued if an attempt is made to load fixltx2e.sty as it is no longer
+% needed.
+% The latest version and documentation can be found at:
+% http://www.ctan.org/pkg/fixltx2e
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/stfloats
+% Do not use the stfloats baselinefloat ability as the IEEE does not allow
+% \baselineskip to stretch. Authors submitting work to the IEEE should note
+% that the IEEE rarely uses double column equations and that authors should try
+% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
+% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
+% such ways.
+% Do not attempt to use stfloats with fixltx2e as they are incompatible.
+% Instead, use Morten Hogholm'a dblfloatfix which combines the features
+% of both fixltx2e and stfloats:
+%
+% \usepackage{dblfloatfix}
+% The latest version can be found at:
+% http://www.ctan.org/pkg/dblfloatfix
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+%\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/url
+% Basically, \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% *** MACROS ***
+
+% ** SYSTEMS **
+
+\newcommand*{\LK}{\mathsf{LK}}
+\newcommand*{\LKm}{\mathsf{LK + mix}}
+\newcommand*{\MLL}{\mathsf{MLL}}
+\newcommand*{\FOMLL}{\mathsf{MLL1}} 
+\newcommand*{\FOMLLm}{\mathsf{MLL1 + mix}}
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
 
 \begin{document}
-
+%
+% paper title
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
+% Do not put math or special symbols in the title.
+\title{On First-order Proofs without syntax}
+
+% author names and affiliations
+% use a multiple column layout for up to three different
+% affiliations
+\author{\IEEEauthorblockN{Dominic J. D. Hughes}
+\IEEEauthorblockA{}
+\and
+\IEEEauthorblockN{Lutz Straßburger}
+\IEEEauthorblockA{Inria, Equipe Partout\\
+Ecole Polytechnique\\
+LIX UMR 7161\\
+France}
+\and
+\IEEEauthorblockN{Jui-Hsuan Wu}
+\IEEEauthorblockA{Ecole Normale Supérieure\\
+France}}
+
+% conference papers do not typically use \thanks and this command
+% is locked out in conference mode. If really needed, such as for
+% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
+% after \documentclass
+
+% for over three affiliations, or if they all won't fit within the width
+% of the page, use this alternative format:
+% 
+%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
+%Homer Simpson\IEEEauthorrefmark{2},
+%James Kirk\IEEEauthorrefmark{3}, 
+%Montgomery Scott\IEEEauthorrefmark{3} and
+%Eldon Tyrell\IEEEauthorrefmark{4}}
+%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
+%Georgia Institute of Technology,
+%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
+%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
+%Email: homer@thesimpsons.com}
+%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
+%Telephone: (800) 555--1212, Fax: (888) 555--1212}
+%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
+
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
+% make the title area
 \maketitle
+
+% As a general rule, do not put math, special symbols or citations
+% in the abstract
+\begin{abstract}
+\end{abstract}
+
+% no keywords
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
 
@@
 Let $\Gamma$ be a sequent.
-Then there is a proof of $\Pi$ in {\bf LK} + $mix$ iff there is a proof of some sequent $\Delta$ in {\bf MLL1} + $mix$ and a derivation from $\Delta$ to $\Gamma$ consisting of the $\cD$ and $\wD$ rules only.
+Then there is a proof of $\Pi$ in $\LKm$ iff there is a proof of some sequent $\Delta$ in $\FOMLLm$ and a derivation from $\Delta$ to $\Gamma$ consisting of the $\cD$ and $\wD$ rules only.
 \end{theorem_}
@@
 ($\Leftarrow$)
-We regard the proof in {\bf MLL1} + $mix$ as a proof in {\bf LK} + $mix$.
-Then we put the derivation consisting of only $\cD$ and $\wD$ under the proof in {\bf LK} + $mix$. Now we try to permute all the instances $\cD$ and $\wD$ upwards with the rules of LK and $mix$. 
+We regard the proof in $\FOMLLm$ as a proof in $\LKm$.
+Then we put the derivation consisting of only $\cD$ and $\wD$ under the proof in $\LKm$. Now we try to permute all the instances $\cD$ and $\wD$ upwards with the rules of LK and $mix$. 
 For the $\cD$ part, the only non-trivial case is the permutation with the $\vee$ rule where the formula generated is $A \vee A$.
@@
 
-\iffalse
-
-Now consider a proof $\Pi$ of some sequent $\Gamma$ in {\bf LK}:
-The observation above gives the possibility of
-transforming the proof into a proof in {\bf MLL} followed by a derivation consisting
-of the $\cD$ and $\wD$ rules only.
-
-Conversely, consider a proof $\Pi$ of some sequent $\Gamma$ consisting of a
-proof $\Pi'$ in {\bf LK} followed by a derivation $\Pi''$ consisting
-the $\cD$ and $\wD$ rules only. 
-We can assume that the proof $\Pi'$ is cut-free and contains only atomic
-axioms.
-Now consider some instance of $\cD$ in the derivation $\Pi''$:
-\begin{prooftree}
-  \hypo{S\{A \vee A\}} 
-  \infer1[$\cD$]{S\{A\}}
-\end{prooftree}
-
-If the subformula $A \vee A$ is erased at some point by the $\wD$ rule:
-
-\begin{center}
-\begin{prooftree}
-  \hypo{\vdash T\{\fff\}}
-  \infer1[$\wD$]{\vdash T\{B\}}
-  \ellipsis{$\mathcal{D}$}{\vdash S\{A \vee A\}}
-  \infer1[$\cD$]{\vdash S\{A\}}
-\end{prooftree}
-\end{center}
-
-where $A \vee A$ is a subformula of $B$, then we can erase the instance of $\cD$
-rule considered
-and obtain the derivation:
-
-\begin{center}
-\begin{prooftree}
-  \hypo{\vdash T\{\fff\}}
-  \infer1[$\wD$]{\vdash T\{B[A \vee A \leftarrow A]\}}
-  \ellipsis{$\mathcal{D}[A \vee A \leftarrow A]$}{\vdash S\{A\}}
-\end{prooftree}
-\end{center}
-
-where $B[A \vee A \leftarrow A]$ (resp. $\mathcal{D}[A \vee A \leftarrow A]$) is the
-formula (resp. derivation) obtained from $B$ (resp. $\mathcal{D}$) by replacing every
-occurrence of $A \vee A$ with $A$.
-
-Now suppose that the subformula $A \vee A$ is not erased in the derivation
-$\Pi''$.
-
-Since there is the contraction rule $ctr$, the subformula $A \vee A$ might be duplicated in the proof $\Pi'$. We now consider a branch of the proof $\Pi'$
-
-Since $\Pi'$ is cut-free, it enjoys the subformula property and since all axioms
-are atomic, the "subformula" $A \vee A$ should be decomposed at some point in the
-proof and thus the proof $\Pi$ should be of the following form:
-
-\begin{center}
-\begin{prooftree}
-  \hypo{\cdots}
-  \hypo{\vdash \Gamma, A, A}
-  \infer1[$\vee$]{\vdash \Gamma, A \vee A}
-  \ellipsis{$\mathcal{D}$}{}
-  \infer2[]{\vdash T\{A \vee A\}}
-  \ellipsis{$\mathcal{D}_1$}{\vdash S\{A \vee A\}}
-  \infer1[$\cD$]{\vdash S\{A\}}
-  \ellipsis{$\mathcal{D}_2$}{\vdash \Gamma}
-\end{prooftree}
-\end{center}
-
-where $\Pi'$ =
-\begin{prooftree}
-  \hypo{\vdash T\{A \vee A\}}
-  \ellipsis{}{\vdash \Gamma}
-\end{prooftree}
-
-We can thus to apply the $ctr$ rule first and to replace each occurrence of $A
-\vee A$ in the derivation (branch) $\mathcal{D}$:
-
-\begin{center}
-\begin{prooftree}
-  \hypo{\cdots}
-  \hypo{\vdash \Gamma, A, A}
-  \infer1[$ctr$]{\vdash \Gamma, A}
-  \ellipsis{$\mathcal{D}[A \vee A \leftarrow A]$}{}
-  \infer2[]{\vdash T\{A \vee A\}}
-  \ellipsis{$\mathcal{D}_1$}{\vdash S\{A \vee A\}}
-  \infer1[$\cD$]{\vdash S\{A\}}
-  \ellipsis{$\mathcal{D}_2$}{\vdash \Gamma}
-\end{prooftree}
-\end{center}
-
-By applying the same process to all the branches of occurrences of $A \vee A$,
-we obtain a proof of $\Gamma$ without the instance
-\begin{prooftree}
-  \hypo{S\{A \vee A\}}
-  \infer1[$\cD$]{S\{A\}}
-\end{prooftree}
-of the $\cD$ rule. The derivation $\Pi'$ can be replaced by the following:
-\begin{center}
-\begin{prooftree}
-  \hypo{\vdash T\{A\}}
-  \ellipsis{$\mathcal{D}_1[A \vee A \leftarrow A]$}{\vdash S\{A\}}
-  \ellipsis{$\mathcal{D}_2[A \vee A \leftarrow A]$}{\vdash \Gamma}
-\end{prooftree}
-\end{center}
-
-We can thus eliminate all the instances of the $\cD$ rule in the proof. Suppose
-now that the derivation $\Pi''$ consists of the $\wD$ rule only.
-
-[PROOF TO DO]
-
-\fi
-
 D. Hughes proves in \cite{Hughes 2019} the soundness and completeness of
-unification nets with respect to {\bf MLL1} + $mix$. In the following, we establish the
+unification nets with respect to $\FOMLLm$. In the following, we establish the
 equivalence between unification nets and fonets.
@@
 corresponding linked fograph.
-
 \begin{proof}
-
-We use frames introduced by Hughes in Section 4 of \cite{Hughes 2015}.
+We use frames introduced by D. Hughes in Section 4 of \cite{Hughes 2015}.
 
 \begin{definition}
-Let $\theta$ be a unification structure on an {\bf MLL1} sequent $\Gamma$.
-We define the \textit{frame}  of $\theta$ by exhaustively applying the following subformula rewriting steps, to obtain a proof structure $\theta_m$ on an {\bf MLL} sequent $\Gamma_m$:
+Let $\theta$ be a unification structure on an $\FOMLL$ sequent $\Gamma$.
+We define the \textit{frame}  of $\theta$ by exhaustively applying the following subformula rewriting steps, to obtain a proof structure $\theta_m$ on an $\MLL$ sequent $\Gamma_m$:
 
@@
 \begin{center}
-\mbox{
 \begin{tikzpicture}
@@
 \end{tikzpicture}
-\hspace{0.5cm}
+\vspace{0.5cm}
 
@@
 \end{tikzpicture}
-}
-
-{\bf Figure 8.} The unification net in Example \ref{exunif} and its frame. The colored part shows how the dependency ${\color{red} \exists x} \rightarrow {\color{blue} \forall z}$ is transformed.
+
+{\bf Figure 8.} A unification net and its frame. The colored part shows how the dependency ${\color{red} \exists x} \rightarrow {\color{blue} \forall z}$ is transformed.
 \end{center}
@@
 
-\iffalse
-Consider a switching graph.
-We associate to this switching graph a proof net for {\bf MLL} by replacing quantifiers with fresh atoms and dependencies with new axiom links using the following schema:
-
-\begin{center}	
-\mbox{
-    \begin{tikzpicture}
-    \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
-    \draw (0, -2) node (existsx) {$\exists x$};
-    \draw (0, 0) node (A) {$A$};
-    \draw (existsx) -- (A) ;
-    \end{tikzpicture}
-
-    \vspace{0.5cm}
-    \begin{tikzpicture}
-    \draw (0, 1) node
-    {$\leadsto$};
-    \draw (0, 2) node {};
-    \draw (0, 0) node {};
-    \end{tikzpicture}
-    \vspace{0.5cm}
-
-    \begin{tikzpicture}
-    \tikzstyle{every node}=[draw, circle, minimum size= 12 pt, inner sep=3pt]
-    \draw (0, 0) node (existx) {$E_x$};
-    \draw (1.2, -2) node (tens) {$\otimes$};
-    \draw (2.4, 0) node (A) {$A$};
-    \draw (tens) -- (A);
-    \draw (tens) -- (existx);
-    \end{tikzpicture}
-}
-\vspace{0.3cm}
-
-\mbox{
-    \begin{tikzpicture}
-    \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
-    \draw (0, -2) node (forallx) {$\forall x$};
-    \draw (0, 0) node (A) {$A$};
-    \draw (forallx) -- (A) ;
-    \end{tikzpicture}
-
-    \vspace{0.5cm}
-    \begin{tikzpicture}
-    \draw (0, 1) node
-    {$\leadsto$};
-    \draw (0, 2) node {};
-    \draw (0, 0) node {};
-    \end{tikzpicture}
-    \vspace{0.5cm}
-
-    \begin{tikzpicture}
-    \tikzstyle{every node}=[draw, circle, minimum size= 12 pt, inner sep=3pt]
-     \draw (0, 0) node (Ux) {$U_x$};
-    \draw (1.2, -2) node (parr) {$\parr$};
-    \draw (2.4, 0) node (A) {$A$};
-    \draw (parr) -- (A);
-    \draw (parr) -- (Ux);
-    \end{tikzpicture}
-}
-
-\mbox{
-    \begin{tikzpicture}
-    \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
-    \draw (-2, -2) node (existsx) {$\exists x$};
-    \draw (-2, 0) node (A) {$A$}; 
-    \draw (0, -2) node (forally) {$\forall y$};
-    \draw (0, 0) node (B) {$B$};
-    \draw (forally) -- (B);
-    \draw (existsx) -- (A);
-    \draw[->] (existsx) -- (forally);
-    \end{tikzpicture}
-
-    \vspace{0.5cm}
-    \begin{tikzpicture}
-    \draw (0, 1) node
-    {$\leadsto$};
-    \draw (0, 2) node {};
-    \draw (0, 0) node {};
-    \end{tikzpicture}
-    \vspace{0.5cm}
-
-    \begin{tikzpicture}
-    \tikzstyle{every node}=[draw, circle, minimum size= 12 pt, inner sep=3pt]
-    \draw (4.8, 0) node (Uy) {$U_y$};
-    \draw (6, -2) node (parr) {$\parr$};
-    \draw (7.2, 0) node (B) {$B$};
-    \draw (parr) -- (B);
-    \draw (parr) -- (Uy);
-    \draw (2.4, 0) node (existx) {$E_x$};
-    \draw (1.2, -2) node (tens) {$\otimes$};
-    \draw (0, 0) node (A) {$A$};
-    \draw (tens) -- (A);
-    \draw (tens) -- (existx);
-    \draw (3.6, 2) node (ax) {$ax$};
-    \draw (ax) to [bend right] (existx);
-    \draw (ax) to [bend left] (Uy);
-
-    \end{tikzpicture}
-}
-\end{center}
-\fi
-
 \end{proof}
-
-\iffalse
-
-\begin{proof}
-Let $C$ be a cycle contained in a switching graph. We can suppose that $C$ is
-minimum, i.e., for all $V' \subsetneq V $, there is no cycle going through exactly $V'$ in a switching graph of the unification structure, where $V$ is the set of vertices of $C$.
-
-Now write $C$ as the
-concatenation of $l_1, p_1, l_2, p_2, ..., l_n, p_n$ where the $l_i$ are
-leaps and the $p_i$ are paths consisting of the other edges. We first prove that
-for all $i$, $p_i$ is non-empty.
-
-Suppose that $p_k$ is empty. The only possible case is:
-\begin{center}
-\begin{tikzpicture}
-  \node (x0) at (0, 0) {$\forall y$};
-  \node (x1) at (2, 0) {$\exists x$};
-  \node (x2) at (4, 0) {$\forall z$}; 
-  \draw [->] (x1) -- (x0) node [midway, above=7pt] {$l_k$};
-  \draw [->] (x1) -- (x2) node [midway, above=7pt] {$l_{k+1}$};
-\end{tikzpicture}
-\end{center}
-
-This means that every unifier of the unification structure assigns a term
-containing $y$ and $z$ to the existential binder $x$, which also implies
-the existence of an atom which is a descendant of the $\exists x$. Without loss of
-generality, we can assume that the predual of this atom is in the scope
-of $\forall y$, then it must contain $y$ and $z$, which is contradictory.
-
-Hence, all the $p_i$ are non-empty.
-
-Let $u_i$ and $v_i$ be the two extremes of the path $p_i$. Since $C$ is
-elementary, $u_i$ and $v_i$ are distinct. If one of them, say $u_i$, is a
-universal quantifier $\forall x$, then $v_i$ is not in its scope. In fact, since a
-dependency edge incident to $\forall x$ is in the switching graph, the
-incoming edge from the direct subterm of $\forall x$ to $\forall x$ in the
-unification structure is removed in the switching graph.\\
-Hence, $u_i$ and $v_i$ are adjacent in the corresponding fograph by proposition
-\ref{prop2}.
-
-We now prove that $W = \{u_i | 1 \leq i \leq n \} \cup \{v_i | 1 \leq i \leq n \}$ induces a bimatching in the corresponding linked fograph.
-
-If $u_i$ and $u_j$ (resp. $v_j$ ($i \neq j$) are adjacent in the fograph, then $C$ is not minimum. Hence $u_i$ and $v_i$ are the only neighbours to each other in the fograph.
-
-The reasoning for proving that $p_k$ is non-empty also proves that every existential quantifier has a unique neighbour in the leap graph.
-The uniqueness of neighbours of universal quantifiers in the leap graph is guaranteed by the definition of switching graph.
-
-\end{proof}
-\fi
 \end{proposition}
@@
 
-\iffalse
-
-By Proposition \ref{prop311}, $\od{\odd{\odh {A^P}}{}{B^P}{\{\wD, \cD\}}}$.
-Since both $A^P$ and $B^P$ are propositional (without quantifier), we
-can place ourselves in a propositional setting. We have thus a skew
-fibration $f$ from $G(A^P) = G(A)$ to $G(B^P) = G(B)$ by Theorem 7.8
-of \cite{Strassburger 2007}. To check that it is a skew bifibration, it suffices to check that:
-\begin{center}
-	for each $x$-binder $b$ in $G(B^P)$, for each vertex $v \in V(G(A^P))$
-such that $f(v)$ is bound by $b$, there exists a unique binder $b'$ such
-that $b'$ binds $v$.
-\end{center}
-
-According to \cite{Strassburger 2007}, a such map $f$ can be seen as a
-composition of:
-\begin{itemize}
-  \item an identity map on labels $i: G(A^P) \rightarrow G(C)$ which is a skew fibration,
-  \item a label-preserving atomic contraction map $c: G(C) \rightarrow G(D)$, i.e., a
-	surjective skew fibration such that for all $u, v \in V_{G(C)}$,
-	we have $u \frown_{C} v$ iff $c(u) \frown_{D} c(v)$, and
-  \item a label-preserving weakening map $w: G(D) \rightarrow G(B^P)$, i.e., an
-	injective skew fibration such that for all $u, v \in V_{G(D)}$, we have 
-	$u \frown_{D} v$ iff $w(u) \frown_{B^P} w(v)$.
-
-\end{itemize}
-Here, $u \frown_{C} v$ means that the first common ancestor of $u$ and $v$ in
-the "propositional" formula $C$ is a $\wedge$, i.e., $u$ and $v$ are adjacent in
-$G(C)$.
-
-	Let $b$ be an $x$-binder in $G(B)$ and let $v \in V_{G(A^P)}$. Suppose that $f(v)$ is bound by $b$.
-
-We distinguish two cases:
-\begin{itemize}
-	\item $b$ is existential: $b$ and $f(v)$ are adjacent in $V_{G(B)}$ since
-	$f(v)$ is in the scope of $b$ and its atom contains $x$. Hence, the
-	$E_x$-labelled vertex $u$ corresponding to $b$ is such that
-	$u \frown_{B^P} f(v) = w(c(v))$. \\
-	Now we prove that $u$ is in the image of $w$. Since $w$ is a skew
-	fibration, there exists $\tilde{u} \in V_{G(D)}$ such that
-		$\tilde{u} \frown_{D} c(v)$ and $w(\tilde{u}) \nfrown_{B^P} u$.
-	Suppose that $w(\tilde{u}) \neq u$.
-	We distinguish two cases:
-	\begin{itemize}
-	  \item $w(\tilde{u})$ corresponds to a descendant of $b$ in $B$: we have $w(\tilde{u}) \frown_{B^P} u$ by definition of $B^P$, which is contradictory.
-	  \item $w(\tilde{u})$ does not correspond to a descendant of $b$ in $B$: this implies that in $B^P$, $b$ is a descendant of the first common ancestor of $w(\tilde{u})$ and $f(v)$ .
-We have also $w(\tilde{u}) \frown {B^P} f(v)$.
-Hence, the first common ancestor of $b$ and $w(\tilde{u})$ is equal to the latter.
-We have thus $w(\tilde{u}) \frown_{B^P}$, which is again contradictory.
-  \end{itemize}
-  Hence, $w(\tilde{u}) = u$.
-  And since $w$ is injective, such $\tilde{u}$ is unique.
-  We have thus a unique u such that $w(\tilde{u}) \frown_{B^P} f(v) = w(c(v))$, which is equivalent to $\tilde{u} \frown_{D} c(v)$.
-Since $c$ is a skew fibration, there exists $\tilde{\tilde{u}} \in V_(G(C))$ such that $\tilde{\tilde{u}} \frown{C} v$ and
-  $c(\tilde{\tilde{u}}) \nfrown_{D} \tilde{u}$.
-  The same reasoning as the previous one proves that $c(\tilde{\tilde{u}}) = \tilde{u}$.  
-  \item 
-\end{itemize}
-
-\fi
-
 \end{proof}
@@
 \begin{theorem_}
-If a formula $\phi$ is provable in {\bf LK}, then it has a combinatorial proof.
+If a formula $\phi$ is provable in $\LK$, then it has a combinatorial proof.
 \end{theorem_}
@@
 \begin{proof}
-By Theorem \ref{thm1}, there exists a formula $\phi'$ such that there is a proof $\Pi$ of $\phi'$ in {\bf MLL1} and a derivation $D$ from $\phi'$ to $\phi$ consisting of the $\wD$ and $\cD$ rules only.
+By Theorem \ref{thm1}, there exists a formula $\phi'$ such that there is a proof $\Pi$ of $\phi'$ in $\FOMLL$ and a derivation $D$ from $\phi'$ to $\phi$ consisting of the $\wD$ and $\cD$ rules only.
 The proof $\Pi$ corresponds to a unique unification net which is equivalent to the fonet corresponding to $\Pi$, i.e., the fograph $G(\phi')$ together with the links of $\Pi$.
@@
 
+% An example of a floating figure using the graphicx package.
+% Note that \label must occur AFTER (or within) \caption.
+% For figures, \caption should occur after the \includegraphics.
+% Note that IEEEtran v1.7 and later has special internal code that
+% is designed to preserve the operation of \label within \caption
+% even when the captionsoff option is in effect. However, because
+% of issues like this, it may be the safest practice to put all your
+% \label just after \caption rather than within \caption{}.
+%
+% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
+% option should be used if it is desired that the figures are to be
+% displayed while in draft mode.
+%
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=2.5in]{myfigure}
+% where an .eps filename suffix will be assumed under latex, 
+% and a .pdf suffix will be assumed for pdflatex; or what has been declared
+% via \DeclareGraphicsExtensions.
+%\caption{Simulation results for the network.}
+%\label{fig_sim}
+%\end{figure}
+
+% Note that the IEEE typically puts floats only at the top, even when this
+% results in a large percentage of a column being occupied by floats.
+
+% An example of a double column floating figure using two subfigures.
+% (The subfig.sty package must be loaded for this to work.)
+% The subfigure \label commands are set within each subfloat command,
+% and the \label for the overall figure must come after \caption.
+% \hfil is used as a separator to get equal spacing.
+% Watch out that the combined width of all the subfigures on a 
+% line do not exceed the text width or a line break will occur.
+%
+%\begin{figure*}[!t]
+%\centering
+%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
+%\label{fig_first_case}}
+%\hfil
+%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
+%\label{fig_second_case}}
+%\caption{Simulation results for the network.}
+%\label{fig_sim}
+%\end{figure*}
+%
+% Note that often IEEE papers with subfigures do not employ subfigure
+% captions (using the optional argument to \subfloat[]), but instead will
+% reference/describe all of them (a), (b), etc., within the main caption.
+% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
+% labels, the optional argument to \subfloat must be present. If a
+% subcaption is not desired, just leave its contents blank,
+% e.g., \subfloat[].
+
+% An example of a floating table. Note that, for IEEE style tables, the
+% \caption command should come BEFORE the table and, given that table
+% captions serve much like titles, are usually capitalized except for words
+% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
+% and up, which are usually not capitalized unless they are the first or
+% last word of the caption. Table text will default to \footnotesize as
+% the IEEE normally uses this smaller font for tables.
+% The \label must come after \caption as always.
+%
+%\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+%\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+%\caption{An Example of a Table}
+%\label{table_example}
+%\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+%\begin{tabular}{|c||c|}
+%\hline
+%One & Two\\
+%\hline
+%Three & Four\\
+%\hline
+%\end{tabular}
+%\end{table}
+
+% Note that the IEEE does not put floats in the very first column
+% - or typically anywhere on the first page for that matter. Also,
+% in-text middle ("here") positioning is typically not used, but it
+% is allowed and encouraged for Computer Society conferences (but
+% not Computer Society journals). Most IEEE journals/conferences use
+% top floats exclusively. 
+% Note that, LaTeX2e, unlike IEEE journals/conferences, places
+% footnotes above bottom floats. This can be corrected via the
+% \fnbelowfloat command of the stfloats package.
+
+\section{Conclusion}
+
+% conference papers do not normally have an appendix
+
+% use section* for acknowledgment
+%\section*{Acknowledgment}
+
+%The authors would like to thank...
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+%\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+%\bibliography{IEEEabrv,../bib/paper}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+
 \input{bibliography}
+
+\begin{thebibliography}{1}
+
+\bibitem{IEEEhowto:kopka}
+H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+
+\end{thebibliography}
+
+% that's all folks
 \end{document}

### 2020-12-23 main.tex
Add some basic definitions

@@
 
+% ** FONT STYLE **
+
+\DeclareTextFontCommand{\bfit}{\bfseries\itshape}
+
 % correct bad hyphenation here
@@
 
+\section{Introduction}
+
+\section{First-order Combinatorial Proofs}
+\subsection{First-order Logic and Graphs}
+
+\bfit{Terms} $s, t, u, \ldots$ and \bfit{atoms} (atomic formulas) $\alpha, \beta,
+\gamma, \ldots$ are generated inductively from variables $x, y, z, \ldots$: if
+$f$ (resp. $p$) is an $n$-ary function (resp. predicate) symbol and $t_1, \ldots,
+t_n$ are terms, then $ft_1 \ldots t_n$ (resp. $pt_1 \ldots t_n$) is a term
+(resp. atom). The set of atoms is extended with logical constant $\ttt$ and
+$\fff$. We also assume that each predicate symbol $p$ has a \bfit{dual}
+predicate symbol $\overline{p}$ with $\overline{p} \neq p$ and
+$\overline{\overline{p}} = p$. We extend the duality to atoms with
+$\overline{pt_1 \ldots t_n} = \overline{p}t_1 \ldots t_n$, $\overline{\ttt} =
+\fff$, and $\overline{\fff} = \ttt$. \bfit{Formulas} $f, g, h$ are generated inductively from atoms by binary
+connectives $\vee$ and $\wedge$ and quantifiers $\forall x$ and $\exists x$.
+The \bfit{negation} $\neg$ is defined in the usual way.
+
+A \bfit{directed graph} $G = (V, E)$ consists of a finite set $V$ of
+\bfit{vertices} and a set of $E \subseteq V \times V$ of \bfit{direct edges}. An
+\bfit{undirected graph} $G = (V, E)$ consists of a finite set $V$ of vertices
+and a set of $E$ of \bfit{undirected edges} (two-element subsets of $V$).
+For a given (directed or undirected) graph $G$, we write $V_G$ and $E_G$ for its
+vertex and edge sets respectively. We write $vw$ for an edge $(v, w)$ or $\{v,
+w\}$. Let $G = (V, E)$ and $G' = (V', E')$ be two undirected graphs. Without
+loss of generality, we assume that $V$ and $V'$ are disjoint. The \bfit{union}
+$G + G'$ is the graph $(V \cup V', E \cup E')$ and the \bfit{join} $G \times G'$
+is the graph $(V \cup V', E \cup E' \cup \{vv' | v \ in V, v' \in V'\})$. A
+\bfit{cograph} is a $P_4$-free undireced grpah, i.e., for any distinct vertices $v_1,
+v_2, v_3, v_4 \in V$, the restriction of the edge sets on them is not equal to
+$\{v_1v_2, v_2v_3, v_3v_4\}$. In a graph $G = (V, E)$, the \bfit{neighbourhood}
+$N(v)$ of $v \in V$ is defined as the set $\{w | vw \in E\}$, and a module is a
+set $M \subseteq V$ such that $N(v) \ M = N(w) \ M$ for all $v, w \in M$. A
+\bfit{module} $M$ is strong if for every module $M'$, we have $M' \subseteq M$, $M
+\subseteq$ or $M \cap M' = \emptyset$.
+
+\subsection{First-order graphs}
+A cograph is \bfit{logical} if every vertex is labelled either by an atom or variable,
+and it has at least one atom-labelled vertex. An atom-labelled vertex is called
+a \bfit{literal} and a variable-labelled vertex is called a \bfit{binder}. A
+binder labelled with $x$ is called an \bfit{$x$-binder}. The \bfit{scope} of a binder
+$b$ is the smallest strong module containing at least two vertices, including
+the binder itself.
+In a logical cograph $G$, a binder $b$ is \bfit{existential} (resp. \bfit{universal}) if, for every other
+vertex $v$ in its scope, we have $bv \in E_G$ (resp. $bv \notin E_G$). An
+$x$-binder is \bfit{legal} if its scope contains no other $x$-binder and at least one
+literal.
+
 \section{From first-order logic to combinatorial proofs}
 
-\subsection{{\bf LK}}
-We start with Gentzen's sequent calculus system {\bf LK} \cite{Gentzen 1935}.
+\subsection{$\LK$}
+We start with Gentzen's sequent calculus system $\LK$ \cite{Gentzen 1935}.
 
@@
 
-Note that the mix rule is derivable via weakening in {\bf LK}.
+Note that the mix rule is derivable via weakening in $\LK$.
 
@@
 
-Note that the $ctr$ (resp. $wk$) rule in {\bf LK} is derivable in $\{\cD, \vee\}$
+Note that the $ctr$ (resp. $wk$) rule in $\LK$ is derivable in $\{\cD, \vee\}$
 (resp. $\{\wD, \fff\}$) and that $\cD$ and $\wD$ rules
-permute downwards with the non-structural rules of {\bf LK}.
+permute downwards with the non-structural rules of $\LK$.
 

### 2020-12-23 main.tex
Add some basic definitions

@@
 
+% ** SPECIAL **
+
+\newcommand*{\Gr}{\mathcal{G}}
+\newcommand*{\LG}{\mathcal{L}}
+
 % ** FONT STYLE **
@@
 $\overline{pt_1 \ldots t_n} = \overline{p}t_1 \ldots t_n$, $\overline{\ttt} =
-\fff$, and $\overline{\fff} = \ttt$. \bfit{Formulas} $f, g, h$ are generated inductively from atoms by binary
+\fff$, and $\overline{\fff} = \ttt$. \bfit{Formulas} $A, B, C$ are generated inductively from atoms by binary
 connectives $\vee$ and $\wedge$ and quantifiers $\forall x$ and $\exists x$.
 The \bfit{negation} $\neg$ is defined in the usual way.
+A formula is \bfit{rectified} if all bound variables are distinct from one another and from all free variables.
+Without loss of generality, we assume that all formulas are rectifed throughtout the paper as every formula has a logically equivalent rectified form.
 
@@
 $G + G'$ is the graph $(V \cup V', E \cup E')$ and the \bfit{join} $G \times G'$
-is the graph $(V \cup V', E \cup E' \cup \{vv' | v \ in V, v' \in V'\})$. A
+is the graph $(V \cup V', E \cup E' \cup \{vv' | v \in V, v' \in V'\})$. A
 \bfit{cograph} is a $P_4$-free undireced grpah, i.e., for any distinct vertices $v_1,
@@
 $\{v_1v_2, v_2v_3, v_3v_4\}$. In a graph $G = (V, E)$, the \bfit{neighbourhood}
-$N(v)$ of $v \in V$ is defined as the set $\{w | vw \in E\}$, and a module is a
+$N(v)$ of $v \in V$ is defined as the set $\{w | vw \in E\}$, a set $W \subseteq
+V$ induces a \bfit{matching} if for all $w \in W$, $N(w) \cap E$ is a singleton, and a module is a
 set $M \subseteq V$ such that $N(v) \ M = N(w) \ M$ for all $v, w \in M$. A
 \bfit{module} $M$ is strong if for every module $M'$, we have $M' \subseteq M$, $M
-\subseteq$ or $M \cap M' = \emptyset$.
-
-\subsection{First-order graphs}
+\subseteq$ or $M \cap M' = \emptyset$. A \bfit{graph homomorphism} $h: (V, E)
+\rightarrow (V', E')$ is a function $h : V \rightarrow V'$ such that $h(v)h(w)
+\in E'$ whenever $vw \in E$.
+
+\subsection{First-order Graphs}
 A cograph is \bfit{logical} if every vertex is labelled either by an atom or variable,
-and it has at least one atom-labelled vertex. An atom-labelled vertex is called
+and it has at least one atom-labelled vertex. We denote by $label_G(v)$, or simply
+$label(v)$ the label of a vertex in a logical cograph $G$. An atom-labelled vertex is called
 a \bfit{literal} and a variable-labelled vertex is called a \bfit{binder}. A
@@
 $b$ is the smallest strong module containing at least two vertices, including
-the binder itself.
+the binder itself. An \bfit{$x$-literal} is a literal whose atom contains the variable $x$. An $x$-binder \bfit{binds} every $x$-literal in its scope.
 In a logical cograph $G$, a binder $b$ is \bfit{existential} (resp. \bfit{universal}) if, for every other
@@
 literal.
+
+We now introduce first-order graphs which are used to represent first-order formulas.
+
+\begin{definition}
+A \bfit{first-order graph} or \bfit{fograph} is a logical cograph with legal binders.
+\end{definition}
+
+For a formula $A$, we can define its associated fograph $\Gr(A)$ inductively by: $\Gr(\alpha) = \cdot \alpha$ (a single-vertex graph whose vertex is labelled by $\alpha$); $\Gr(A \vee B) = \Gr(A) + \Gr(B)$ and $\Gr(A \wedge B) = \Gr(A) \times \Gr(B)$.
+The \bfit{binding graph} of a forgraph $G$ is the directed graph $(V_G, \{(b,
+l) | b \text{ binds } l\})$.
+
+\subsection{Fonets}
+In a fograph, two atoms are \bfit{pre-dual} if their predicate symbols are dual
+(e.g. $pxy$ and $\overline{p}yz$) and two literals are \bfit{pre-dual} if their
+labels (atoms) are pre-dual. A \bfit{linked fograph} is a coloured fograph such
+that every colour, called a \bfit{link}, consists of two pre-dual literals, and
+every literal is either $\ttt$-labelled or in a link.
+
+Let $G$ be a linked fograph. The set of links can be seen as a unification problem
+by identifying dual predicate symbols. A \bfit{dualizer} of $G$ is an assignment
+unifying all the links of $G$. Since a first-order unification problem is either
+solvable or has a most general unifier, we can define the notion of \bfit{most
+general dualizer}. A \bfit{dependency} is a pair $(\cdot x, \cdot y)$ of an
+existential binder $\cdot x$ and a universal binder $\cdot y$ such that the most
+general dualizer assigns to $x$ a term containing $y$. A \bfit{leap} is either a
+link or a dependency. The \bfit{leap graph} $\LG_G$ of $G$ is the undirected graph $(V_G,
+L_G)$ where $L_G$ is the set of leaps of $G$. A set $W \subseteq V_G$ induces a
+\bfit{bimatching} in $G$ if $W$ induces a matching in $G$ and in the leap graph
+$\LG_G$ as well.
+
+\begin{definition}
+A \bfit{first-order net} or \bfit{fonet} is a linked fograph which has
+dualizer but no induced bimatching.  
+\end{definition}
+
+\subsection{Skew bifibrations}
+
+A graph homomorphism $h: (V, E) \rightarrow (V', E')$ is a \bfit{fibration} if
+for all $v \in V$ and $wh(v) \in E'$, there exists a unique $\tilde{w}$ such
+that $\tilde{w}v \in E$ and $h(\tilde{w}) = w$, and is a \bfit{skew fibration}
+if for all $v \in V$ and $wh(v) \in E'$ there exists $\tilde{w}$ such that
+$\tilde{w}v \in E$ and $h(\tilde{w})w \notin E'$. A \bfit{fograph homomorphism}
+is a graph homomorphism between the underlying graphs of the fographs
+considered. A fograph homomorphism $h : G \rightarrow G'$ is
+\bfit{label-preserving} if forall $v \in V_G, label(v) = label(h(v))$, and is
+\bfit{existential-preserving} if for all existental binder $b$ in $G$, the
+vertex $h(b)$ is an existential binder in $G'$.
+
+\begin{definition}
+A \bfit{skew bifibration} between fographs is a label-preserving and
+	existential-preserving fograph homomorphism whose restriction to the
+	binding graphs is a fibration.
+\end{definition}
 
@@
 
-\input{bibliography}
-
-\begin{thebibliography}{1}
-
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-\end{thebibliography}
+%\input{bibliography}
+
+%\begin{thebibliography}{1}
+
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+
+%\end{thebibliography}
 

### 2020-12-24 main.tex
Add some more definitions

@@
 
+% ** SYMBOLS **
+
+\newcommand{\ax}{\mathsf{ax}}
+\newcommand{\cut}{\mathsf{cut}}
+\newcommand{\conj}{\mathsf{\wedge}}
+\newcommand{\disj}{\mathsf{\vee}}
+\newcommand{\univ}{\mathsf{\forall}}
+\newcommand{\exist}{\mathsf{\exists}}
+\newcommand{\mix}{\mathsf{mix}}
 % ** SPECIAL **
 
-\newcommand*{\Gr}{\mathcal{G}}
-\newcommand*{\LG}{\mathcal{L}}
+\newcommand{\Gr}{\mathcal{G}}
+\newcommand{\LG}{\mathcal{L}}
+\newcommand{\FT}{\mathcal{F}}
+\newcommand{\US}{\mathcal{U}}
 
@@
 \gamma, \ldots$ are generated inductively from variables $x, y, z, \ldots$: if
-$f$ (resp. $p$) is an $n$-ary function (resp. predicate) symbol and $t_1, \ldots,
-t_n$ are terms, then $ft_1 \ldots t_n$ (resp. $pt_1 \ldots t_n$) is a term
+$\delta$ (resp. $p$) is an $n$-ary function (resp. predicate) symbol and $t_1, \ldots,
+t_n$ are terms, then $\delta t_1 \ldots t_n$ (resp. $pt_1 \ldots t_n$) is a term
 (resp. atom). The set of atoms is extended with logical constant $\ttt$ and
@@
 \bfit{module} $M$ is strong if for every module $M'$, we have $M' \subseteq M$, $M
-\subseteq$ or $M \cap M' = \emptyset$. A \bfit{graph homomorphism} $h: (V, E)
-\rightarrow (V', E')$ is a function $h : V \rightarrow V'$ such that $h(v)h(w)
+\subseteq$ or $M \cap M' = \emptyset$. A \bfit{graph homomorphism} $f: (V, E)
+\rightarrow (V', E')$ is a function $f : V \rightarrow V'$ such that $f(v)f(w)
 \in E'$ whenever $vw \in E$.
 
-\subsection{First-order Graphs}
+\subsection{First-order combinatorial proofs}
 A cograph is \bfit{logical} if every vertex is labelled either by an atom or variable,
@@
 
-\subsection{Fonets}
 In a fograph, two atoms are \bfit{pre-dual} if their predicate symbols are dual
@@
 
-\subsection{Skew bifibrations}
-
-A graph homomorphism $h: (V, E) \rightarrow (V', E')$ is a \bfit{fibration} if
-for all $v \in V$ and $wh(v) \in E'$, there exists a unique $\tilde{w}$ such
-that $\tilde{w}v \in E$ and $h(\tilde{w}) = w$, and is a \bfit{skew fibration}
-if for all $v \in V$ and $wh(v) \in E'$ there exists $\tilde{w}$ such that
-$\tilde{w}v \in E$ and $h(\tilde{w})w \notin E'$. A \bfit{fograph homomorphism}
+A graph homomorphism $f: (V, E) \rightarrow (V', E')$ is a \bfit{fibration} if
+for all $v \in V$ and $wf(v) \in E'$, there exists a unique $\tilde{w}$ such
+that $\tilde{w}v \in E$ and $f(\tilde{w}) = w$, and is a \bfit{skew fibration}
+if for all $v \in V$ and $wf(v) \in E'$ there exists $\tilde{w}$ such that
+$\tilde{w}v \in E$ and $f(\tilde{w})w \notin E'$. A \bfit{fograph homomorphism}
 is a graph homomorphism between the underlying graphs of the fographs
-considered. A fograph homomorphism $h : G \rightarrow G'$ is
-\bfit{label-preserving} if forall $v \in V_G, label(v) = label(h(v))$, and is
+considered. A fograph homomorphism $f : G \rightarrow G'$ is
+\bfit{label-preserving} if forall $v \in V_G, label(v) = label(f(v))$, and is
 \bfit{existential-preserving} if for all existental binder $b$ in $G$, the
-vertex $h(b)$ is an existential binder in $G'$.
+vertex $f(b)$ is an existential binder in $G'$.
 
@@
 \end{definition}
+
+\begin{definition}
+	A \bfit{first-order combinatorial proof} of a fograph $G$ is a skew
+bifibration $f: N \rightarrow G$ where $N$ is a fonet. A \bfit{first-order
+combinatorial proof} of a formula $A$ is a combinatorial proof of its graph
+	$\Gr(A)$.
+\end{definition}
+
+\subsection{$\FOMLL$ and Unification Nets}
+
+In $\FOMLL$, terms, atoms, formulas are defined as in first-order logic. For
+simplicity, we choose to use $\vee$ and $\wedge$ instead of $\parr$ and
+$\otimes$ which are generally used in the presentation of linear logic.
+A formula $A$ is identified with its \bfit{formula tree} $\FT(A)$, a directed
+tree with leaves labelled by atoms, internal nodes labelled by connectives and
+quantifiers, and edges directed from leaves to the root. A \bfit{sequent} $\Gamma$ is simply a disjoint union of formulas. We write
+comma for disjoint union.
+
+Sequents are proved using the inference rules of $\FOMLL$:
+\begin{center}
+
+\mbox{
+\begin{prooftree}
+  \infer0[$\ax$]{\vdash A, \neg A}
+\end{prooftree}
+\hspace{2cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A}
+  \hypo{\vdash \Delta, \neg A}
+  \infer2[$\cut$]{\vdash \Gamma, \Delta}
+\end{prooftree}}
+
+\mbox{
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A}
+  \hypo{\vdash \Delta, B}
+  \infer2[$\conj$]{\vdash \Gamma, \Delta, A \wedge B}
+\end{prooftree}
+\hspace{1.5cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A, B}
+  \infer1[$\disj$]{\vdash \Gamma, A \vee B}
+\end{prooftree}}
+
+\mbox{
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A}
+  \infer1[$\univ$]{\vdash \Gamma, \forall x A}
+\end{prooftree}
+($x \notin fv(\Gamma)$)
+\hspace{2cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A[t/x]}
+  \infer1[$\exist$]{\vdash \Gamma, \exists x A}
+\end{prooftree}}
+\end{center}
+
+We also consider the $\mix$ rule:
+
+\begin{center}
+\begin{prooftree}
+\hypo{\vdash \Gamma}
+\hypo{\vdash \Delta}
+\infer2[$\mix$]{\vdash \Gamma, \Delta}
+\end{prooftree}
+\end{center}
+
+Let $\Gamma$ be a sequent in $\FOMLLm$. A \bfit{link} on $\Gamma$ is a pair of
+leaves whose atoms are pre-dual. A \bfit{linking} on $\Gamma$ is a set of 
+disjoint links such that each leaf of $\Gamma$ is in exacly one link. Similar
+to the set of links in the linked fograph, a linking can be seen as a
+unification problem, and a link is said \bfit{unifiable} if the corresponding
+unification problem is solvable. \bfit{Dependencies} are defined as previously.
+
+Let $\lambda$ is a unifiable linking on $\Gamma = A_1, \ldots, A_n$.
+Let $A = A_1 \vee \ldots \vee A_n$. The \bfit{unification structure}
+$\US(\lambda)$
+associated to $\lambda$ is the formula tree $\FT(A)$ together with an undirected
+edge between leaves $l$ and $l'$ for every link $\{l, l'\}$ in $\lambda$ and a
+directed edge from $\exists x$ to $\forall y$ for every dependency $\exists x
+\rightarrow \forall y$.
+
+A \bfit{switching graph} of a unification structure $\US(\lambda)$ is any
+derivative of $\US(\lambda)$ obtained by keeping only one edge into each $\parr$
+and $\forall$ and undirecting remaining edges. A linking is \bfit{correct} if it
+is unifiable and all of the switching graphs of its associated unification
+structure are acyclic.
+
+\begin{definition}
+  A \bfit{unification net} on a sequent $\Gamma$ is a correct linking on $\Gamma$.
+\end{definition}
+
+\subsection{Deep Inference}
+In this paper we also use some \bfit{deep inference} \cite{BT 2001} rules that are in the
+following form:
+\begin{center}
+\begin{prooftree}
+  \hypo{\vdash S\{A\}}
+  \infer1[]{\vdash S\{B\}}
+\end{prooftree}
+\end{center}
+where $S\{ \ \}$ stands for a \bfit{context}, which corresponds to a sequent
+or a formula with a hole taking the place of an atom, and $S\{A\}$ represents
+the sequent or formula obtained by replacing the hole in $S\{ \ \}$ with the formula $A$. Formally,
+
+  \[C ::= \Box \ | \ A \vee C \ | \ C \wedge A \ | \ \exists x C \ | \ \forall x C \].
+  \[S ::= C \ | \ A, S \ | \ S, A \] where $A$ is a formula.
+The above rule can be thus seen as the rewriting rule $A \rightarrow B$.
+
+We use the notation $\vlderivation{\vlde{}{\mathcal{P}}{B}{\vlhy {A}}}$ for denoting that there is a derivation from premise $\vdash S\{A\}$ to conclusion $\vdash S\{B\}$ in system $P$ for any context $S$.
 
@@
 
-%\input{bibliography}
+\input{bibliography}
 

### 2020-12-28 main.tex
Fix the notation

@@
 where $S\{ \ \}$ stands for a \bfit{context}, which corresponds to a sequent
-or a formula with a hole taking the place of an atom, and $S\{A\}$ represents
+with a hole taking the place of an atom, and $S\{A\}$ represents
 the sequent or formula obtained by replacing the hole in $S\{ \ \}$ with the formula $A$. Formally,
@@
 
-\begin{definition} A \textit{switching path} of a  formula tree $F(\phi)$ is a path in $F(\phi)$ that does not go through both incoming edges of a $\parr$.
+\begin{definition} A \textit{switching path} of a  formula tree $\FT(A)$ is a
+	path in $\FT(A)$ that does not go through both incoming edges of a $\parr$.
 \end{definition}
@@
 \label{prop2}
-Let $u$ and $v$ be two distinct vertices of a fograph $G(\phi)$, then we have the equivalence
+Let $u$ and $v$ be two distinct vertices of a fograph $\Gr(A)$, then we have the equivalence
 between:
 \begin{itemize}
-  \item $u$ and $v$ are adjacent in $G(\phi)$
-  \item $u$ and $v$ are connected by a switching path of $F(\phi)$, and if one of them is a universal quantifier, then the other is
+  \item $u$ and $v$ are adjacent in $\Gr(A)$
+  \item $u$ and $v$ are connected by a switching path of $F(A)$, and if one of them is a universal quantifier, then the other is
 	not a descendant of the former.
@@
 \begin{proof}
-By induction on $\phi$.
+By induction on $A$.
 \begin{itemize}
-  \item If $\phi$ is an atom, trivial.
-  \item If $\phi = \phi_1 \wedge \phi_2$, then we distinguish two cases:
+  \item If $A$ is an atom, trivial.
+  \item If $A = A_1 \wedge A_2$, then we distinguish two cases:
     \begin{itemize}
-      \item $u$ and $v$ are both in $\phi_1$ (resp. $\phi_2$): trivial by
+      \item $u$ and $v$ are both in $A_1$ (resp. $A_2$): trivial by
 	      the induction hypothesis.
-      \item one of them is in $\phi_1$ and the other is in $\phi_2$: they are
-	      adjacent in $G(\phi)$ by definition. By Proposition \ref{prop1},
-		    the one in $\phi_1$ (resp. $\phi_2$) is connected to the
-		    vertex representing $\phi_1$ (resp. $\phi_2$) by a switching
-		    path. Together with the two edges incident to $\phi_1 \wedge
-		    \phi_2$, we obtain a switching path connecting $u$ and $v$.
+      \item one of them is in $A_1$ and the other is in $A_2$: they are
+	      adjacent in $\Gr(A)$ by definition. By Proposition \ref{prop1},
+		    the one in $A_1$ (resp. $A_2$) is connected to the
+		    vertex representing $A_1$ (resp. $A_2$) by a switching
+		    path. Together with the two edges incident to $A_1 \wedge
+		    A_2$, we obtain a switching path connecting $u$ and $v$.
     \end{itemize}
-  \item If $\phi = \phi_1 \vee \phi_2$, then we distinguish two cases:
+  \item If $A = A_1 \vee A_2$, then we distinguish two cases:
     \begin{itemize}
-      \item $u$ and $v$ are both in $\phi_1$ (resp. $\phi_2$): trivial by
+      \item $u$ and $v$ are both in $A_1$ (resp. $A_2$): trivial by
 	      the induction hypothesis.
-      \item one of them is in $\phi_1$ and the other is in $\phi_2$: they are not
-	      adjacent in $G(\phi)$ by definition. It is clear that they
+      \item one of them is in $A_1$ and the other is in $A_2$: they are not
+	      adjacent in $\Gr(A)$ by definition. It is clear that they
 		    are not connected by a switching path.
     \end{itemize}
-  \item If $\phi = \exists x \ \phi'$, then we distinguish two cases:
+  \item If $A = \exists x \ A'$, then we distinguish two cases:
     \begin{itemize}
-      \item $u$ and $v$ are both in $\phi'$: trivial by the induction
+      \item $u$ and $v$ are both in $A'$: trivial by the induction
 	      hypothesis.
-      \item one of them is $\exists x$ and the other is in $\phi'$: trivial
+      \item one of them is $\exists x$ and the other is in $A'$: trivial
 	      by Proposition \ref{prop1}
@@
     \end{itemize}
-  \item If $\phi = \forall x \ \phi'$, then we distinguish two cases:
+  \item If $A = \forall x \ A'$, then we distinguish two cases:
     \begin{itemize}
-      \item $u$ and $v$ are both in $\phi'$: trivial by the induction
+      \item $u$ and $v$ are both in $A'$: trivial by the induction
 	      hypothesis.
-      \item one of them is $\forall x$ and the other is in $\phi'$:
-	they are not adjacent in $G(\phi)$ by definition and it is clear that
+      \item one of them is $\forall x$ and the other is in $A'$:
+	      they are not adjacent in $\Gr(A)$ by definition and it is clear that
 		    the former is a descendant of $\forall x$.
@@
 \begin{proposition}
-If there exists an induced bimatching of the linked fograph $G = G(\phi)$, then there exists a switching graph of the corresponding unification net which contains a cycle.
+If there exists an induced bimatching of the linked fograph $G = \Gr(A)$, then there exists a switching graph of the corresponding unification net which contains a cycle.
 \begin{proof}
@@
   \in E_G$ and $uv \in L_G$. By Proposition \ref{prop2}, there exists a
-  switching path of the formula tree of $\phi$. Together with the leap
+  switching path of the formula tree of $A$. Together with the leap
   $uv$, this path induces a cycle in a switching graph of the
@@
 \begin{proposition}
-If one of the switching graphs of the unification structure of $\phi$
+If one of the switching graphs of the unification structure of $A$
 contains a cycle or is not connected, then there exists an induced bimatching of the
@@
 
-Consider now a switching graph $H$ of a unification structure $\theta$ of $\phi$.
+Consider now a switching graph $H$ of a unification structure $\theta$ of $A$.
 
@@
   \infer1[$\me$]{\vdash S\{(A \vee C) \wedge (B \vee D)\}}
-\end{prooftree}
-\hspace{0.3cm}
-
+\end{prooftree}}
+\vspace{0.2cm}
+
+\mbox{
 \begin{prooftree}
@@
   \item $A^P$ is a formula containing no quantifier for any formula $A$.
-  \item $G(A^P) = G(A)$ by confounding the atoms $U_x$, $E_x$ with the variable
-	  $x$. Thus, a map $f : G(A^P) \rightarrow G(B^P)$ can be seen as a map
-		$f : G(A) \rightarrow G(B)$.
+  \item $\Gr(A^P) = \Gr(A)$ by confounding the atoms $U_x$, $E_x$ with the variable
+	  $x$. Thus, a map $f : \Gr(A^P) \rightarrow \Gr(B^P)$ can be seen as a map
+		$f : \Gr(A) \rightarrow \Gr(B)$.
   \item $(S\{A\})^P = S^P\{A^P\}$.
@@
 \begin{center}
-	for each $x$-binder $b$ in $G(B^P)$, for each vertex $v \in V(G(A^P))$
+for each $x$-binder $b$ in $\Gr(B^P)$, for each vertex $v \in V(\Gr(A^P))$
 such that $g(v)$ is bound by $b$, there exists a unique binder $b'$ such
@@
 
-  Therefore, all of these maps are skew bifibrations and since skew bifibrations on fographs compose (Lemma 10.32, \cite{Hughes 2019}), there exists a skew bifibration from $G(A)$ to $G(B)$.
+  Therefore, all of these maps are skew bifibrations and since skew bifibrations
+on fographs compose (Lemma 10.32, \cite{Hughes 2019}), there exists a skew
+bifibration from $\Gr(A)$ to $\Gr(B)$.
 
@@
 \begin{theorem_}
-If a formula $\phi$ is provable in $\LK$, then it has a combinatorial proof.
+If a formula $A$ is provable in $\LK$, then it has a combinatorial proof.
 \end{theorem_}
@@
 \begin{proof}
-By Theorem \ref{thm1}, there exists a formula $\phi'$ such that there is a proof $\Pi$ of $\phi'$ in $\FOMLL$ and a derivation $D$ from $\phi'$ to $\phi$ consisting of the $\wD$ and $\cD$ rules only.
-The proof $\Pi$ corresponds to a unique unification net which is equivalent to the fonet corresponding to $\Pi$, i.e., the fograph $G(\phi')$ together with the links of $\Pi$.
-By Lemma \ref{mlem}, there exists a skew bifibration $G(\phi') \rightarrow G(\phi)$.
-We have thus a combinatorial proof of $\phi$.
+By Theorem \ref{thm1}, there exists a formula $A'$ such that there is a proof
+$\Pi$ of $A'$ in $\FOMLL$ and a derivation $D$ from $A'$ to $A$ consisting of
+the $\wD$ and $\cD$ rules only. The proof $\Pi$ corresponds to a unique
+unification net which is equivalent to the fonet corresponding to $\Pi$, i.e.,
+the fograph $\Gr(A')$ together with the links of $\Pi$. By Lemma \ref{mlem}, 
+there exists a skew bifibration $\Gr(A') \rightarrow \Gr(A)$. We have thus a
+combinatorial proof of $A$.
 

### 2021-01-03 main.tex
Fix the macros

@@
 \newcommand{\US}{\mathcal{U}}
+\newcommand{\PE}[1]{#1^P}
 
@@
 \begin{definition}
-The propositional encoding $A^P$ of a formula $A$ is defined inductively by:
+The propositional encoding $\PE{A}$ of a formula $A$ is defined inductively by:
 
 \begin{centering}
-	$a^P = a$ for every atom $a$
-
-	$(A \vee B)^P = A^P \vee B^P$ \hspace{2cm} $(A \wedge B)^P = A^P \wedge B^P$
-
-	$(\forall x A)^P = U_x \vee A^P$ \hspace{2cm} $(\exists x A)^P = E_x \wedge A^P$
+	$\PE{a} = a$ for every atom $a$
+
+	$\PE{(A \vee B)} = \PE{A} \vee \PE{B}$ \hspace{2cm} $\PE{(A \wedge B)} =
+	\PE{A} \wedge \PE{B}$
+
+	$\PE{(\forall x A)} = U_x \vee \PE{A}$ \hspace{2cm} $\PE{(\exists x A)}
+	= E_x \wedge \PE{A}$
 
@@
 
-Similarly, we can define the propositional encoding $S^P$ of a context $S$ inductively by setting $\Box^P = \Box$. Note that $S^P$ is also an encoding.
+Similarly, we can define the propositional encoding $\PE{S}$ of a context $S$
+inductively by setting $\PE{\Box} = \Box$. Note that $\PE{S}$ is also a context.
 
@@
 \begin{itemize}
-  \item $A^P$ is a formula containing no quantifier for any formula $A$.
-  \item $\Gr(A^P) = \Gr(A)$ by confounding the atoms $U_x$, $E_x$ with the variable
-	  $x$. Thus, a map $f : \Gr(A^P) \rightarrow \Gr(B^P)$ can be seen as a map
+  \item $\PE{A}$ is a formula containing no quantifier for any formula $A$.
+  \item $\Gr(\PE{A}) = \Gr(A)$ by confounding the atoms $U_x$, $E_x$ with the variable
+	  $x$. Thus, a map $f : \Gr(\PE{A}) \rightarrow \Gr(\PE{B})$ can be seen as a map
 		$f : \Gr(A) \rightarrow \Gr(B)$.
-  \item $(S\{A\})^P = S^P\{A^P\}$.
+  \item $\PE{(S\{A\})} = \PE{S}\{\PE{A}\}$.
 \end{itemize}
@@
 $\od{\odd{\odh {A}}{}{B}{\{\wD, \cD\}}}$. Then 
-$\od{\odd{\odh {A^P}}{}{B^P}{\{\wD, \cD\}}}$.
+$\od{\odd{\odh {\PE{A}}}{}{\PE{B}}{\{\wD, \cD\}}}$.
 \end{proposition}
-
-\iffalse
-\begin{proof}
-
-We say that a rule \begin{prooftree} \hypo{C} \infer1[]{D} \end{prooftree}
-is $P$-derivable for $\{\wD, \cD\}$ if
-        $\od{\odd{\odh {C^P}}{}{D^P}{\{\wD, \cD\}}}$.
-
-We now prove that $\wD$ and $\cD$ are
-	$P$-derivable for $\{\wD, \cD\}$.
-
-\begin{itemize}
-\item $\wD$ is $P$-derivable: we have
-  \begin{prooftree}
-    \hypo{S^P\{\fff\}}
-    \infer1[$\wD$]{S^P\{C^P\}}
-  \end{prooftree}
-
-\item $\cD$ is $P$-derivable: we have
-  \begin{prooftree}
-    \hypo{S^P\{C^P \vee C^P\}}
-    \infer1[$\cD$]{S^P\{C^P\}}
-  \end{prooftree}
-
-\end{itemize}
-
-Hence, $\od{\odd{\odh {A^P}}{}{B^P}{\{\wD, \cD\}}}$.
-
-\end{proof}
-\fi
 
@@
 \begin{center}
-for each $x$-binder $b$ in $\Gr(B^P)$, for each vertex $v \in V(\Gr(A^P))$
+for each $x$-binder $b$ in $\Gr(\PE{B})$, for each vertex $v \in V(\Gr(\PE{A}))$
 such that $g(v)$ is bound by $b$, there exists a unique binder $b'$ such
@@
 
-$f$ can be seen as a skew fibration from $G(A^P)$ to $G(B^P)$, which gives the existence of the propositions $A'$ and $B'$, and of the following derivation:
-  \[\od{\odd{\odd{\odd{\odh{A^P} }
+$f$ can be seen as a skew fibration from $G(\PE{A})$ to $G(\PE{B})$, which gives the existence of the propositions $A'$ and $B'$, and of the following derivation:
+  \[\od{\odd{\odd{\odd{\odh{\PE{A}} }
   {\Delta }{A'}{\me} }
   {\Delta' }{B'}{\acD} }
-  {\Delta''}{B^P}{\wD}} \]
-
-\begin{lemma} there exists $B''$ such that $B''^P$ = $B'$.
+  {\Delta''}{\PE{B}}{\wD}} \]
+
+\begin{lemma} there exists $B''$ such that $\PE{B''}$ = $B'$.
 
@@
 Consider the dervation $\Delta''$. If some $U_x$ (or $E_x$) is introduced
-via weakening, then all the atoms it binds in $B^P$ should also be introduced 
-via weakening. In fact, an atom of $B^P$ is introduced via weakening is 
+via weakening, then all the atoms it binds in $\PE{B}$ should also be introduced 
+via weakening. In fact, an atom of $\PE{B}$ is introduced via weakening is 
 equivalent to the fact that its corresponding vertex is not in the image of $f$. 
@@
 Then the derivation:
- \[\od{\odd{\odd{\odh{A^P} }
+ \[\od{\odd{\odd{\odh{\PE{A}} }
   {\Delta }{A'}{\me} }
@@
 can be translated to the derivation:
-\[\od{\odd{\odh{(A^P)^*} }
+\[\od{\odd{\odh{(\PE{A})^*} }
 {\Delta^* }{(B')^*}{}} \]
@@
 transformation rules above and by applying them in a bottom-up style:
-\[\od{\odd{\odh{(A^P)^*} }
+\[\od{\odd{\odh{(\PE{A})^*} }
 {\Delta_1 }{(B')^*}{\acD, \me, \me'}} \]
@@
 
-Suppose that $(C \vee E) \wedge (D \vee F) = G^P$ for some $G$.
+Suppose that $(C \vee E) \wedge (D \vee F) = \PE{G}$ for some $G$.
 Since $C \vee E$ cannot be $Q_x$ (otherwise, the rule applied would be
-$\me'$), $G$ can be written as $G_1 \wedge G_2$ with $C \vee E = G_1^P$ and $D
-\vee F = G_2^P$.
+$\me'$), $G$ can be written as $G_1 \wedge G_2$ with $C \vee E = \PE{G_1}$ and $D
+\vee F = \PE{G_2}$.
 
@@
 and some formula which can never be eliminated by the rules $\me$, $\me'$ and
-$\acD$. However, there exists no such conjunction in ${A^P}^*$, which leads to a
+$\acD$. However, there exists no such conjunction in ${\PE{A}}^*$, which leads to a
 contradiction.
@@
 Hence, $G_i$ can be written as $J_i \vee K_i$ for $i = 1, 2$. We now have $(C
-\wedge D) \vee (E \wedge F) = ((J_1 \wedge J_2) \vee (K_1 \wedge K_2))^P$.
+\wedge D) \vee (E \wedge F) = \PE{((J_1 \wedge J_2) \vee (K_1 \wedge
+K_2))}$.
 
@@
 
-Suppose that $Q_X^* \wedge (C \vee D)$ = $F^P$ for some $P$. It is clear
-that $Q_x^* = E_x^*$ and $F = \exists x G$ with $G^P = C \vee D$ for some $G$.
+Suppose that $Q_X^* \wedge (C \vee D)$ = $\PE{F}$ for some $F$. It is clear
+that $Q_x^* = E_x^*$ and $F = \exists x G$ with $\PE{G} = C \vee D$ for some $G$.
 We distinguish two cases:
@@
 D)$ has a subformula $(E_x^* \wedge U_y^*)$, which cannot be eliminated by the
-rules $\me$, $\me'$, $\acD$. It is clear that ${A^P}^*$ does not
+	rules $\me$, $\me'$, $\acD$. It is clear that ${\PE{A}}^*$ does not
 have a subformula of this form, which leads to a contradiction.
   \item $G = G_1 \vee G_2$: in this case, $(Q_x^* \wedge C) \vee (Q_x^* \wedge
-	  D) = ((\exists x G_1) \vee (\exists x G_2))^P$.
+  D) = \PE{((\exists x G_1) \vee (\exists x G_2))}$.
 \end{itemize}

### 2021-01-05 main.tex
Fix the macros
Fix some notations

@@
 
-We use the notation $\vlderivation{\vlde{}{\mathcal{P}}{B}{\vlhy {A}}}$ for denoting that there is a derivation from premise $\vdash S\{A\}$ to conclusion $\vdash S\{B\}$ in system $P$ for any context $S$.
+We use the notation $\vlderivation{\vlde{}{\mathcal{P}}{B}{\vlhy {A}}}$ for
+denoting that there is a derivation from premise $\vdash S\{A\}$ to conclusion
+$\vdash S\{B\}$ in system $\mathcal{P}$ for any context $S$.
 
@@
 
-We also consider the mix rule here:
-
-\begin{center}
-\begin{prooftree}
-\hypo{\vdash \Gamma}
-\hypo{\vdash \Delta}
-\infer2[$mix$]{\vdash \Gamma, \Delta}
-\end{prooftree}
-\end{center}
-
-Note that the mix rule is derivable via weakening in $\LK$.
-
-Consider the following deep rules \cite{BT 2001}:
+Note that the $\mix$ rule is derivable via weakening in $\LK$.
+
+Consider the following deep inference rules \cite{BT 2001}:
 \begin{center}
@@
 \end{proposition}
+\begin{proof}
+  Trivial by induction.
+\end{proof}
 
@@
 Since there is an edge from $U_x$ (resp. $E_x$) to all the literals it binds in the 
-binding graph $\overrightarrow{G(B)}$, if one of the atoms is in the image, 
+binding graph $\overrightarrow{\Gr(B)}$, if one of the atoms is in the image, 
 $U_x$ (resp. $E_x$) should also be in the image since $f$ is a fibration on binding graphs.
@@
 \begin{itemize}
-  \item $(E_x \vee \cdots \vee E_x)* = E_x^*$
-  \item $(U_x \vee \cdots \vee U_x)* = U_x^*$
+  \item $(E_x \vee \cdots \vee E_x)* = E_x$
+  \item $(U_x \vee \cdots \vee U_x)* = U_x$
   \item structural recursion in all the other cases.
@@
   {\Delta }{A'}{\me} }
-  {\Delta' }{B'}{\acD}} \]
+  {\Delta' }{\PE{B''}}{\acD}} \]
 can be translated to the derivation:
 \[\od{\odd{\odh{(\PE{A})^*} }
-{\Delta^* }{(B')^*}{}} \]
+{\Delta^* }{(\PE{B''})^*}{}} \]
 
 where $\Delta^*$ is the derivation obtained by replacing all the formulas $F$
-with $F^*$.
-
-Note that we should also introduce new rules in the derivation $\Delta^*$.
-Otherwise, the rule applications cannot work in general.
-
-To do that, we define the following rule transformation:
+with $F^*$ and by applying the following rule transformation:
 
@@
 \begin{prooftree}
-  \hypo{Q_x^*}
-  \infer1[$\acD$]{Q_x^*}
+  \hypo{Q_x}
+  \infer1[$\acD$]{Q_x}
 \end{prooftree}
@@
 \begin{prooftree}
-  \hypo{Q_x^*}
-  \infer1[$=$]{Q_x^*}
+  \hypo{Q_x}
+  \infer1[$=$]{Q_x}
 \end{prooftree}
@@
 \begin{prooftree}
-  \hypo{(Q_x^* \wedge C) \vee (Q_x^* \wedge D)}
-  \infer1[$\me$]{Q_x^* \wedge (C \vee D)}
+  \hypo{(E_x \wedge C) \vee (E_x \wedge D)}
+  \infer1[$\me$]{E_x \wedge (C \vee D)}
 \end{prooftree}
@@
 \begin{prooftree}
-  \hypo{(Q_x^* \wedge C) \vee (Q_x^* \wedge D)}
-  \infer1[$\me'$]{Q_x^* \wedge (C \vee D)}
+  \hypo{(E_x \wedge C) \vee (E_x \wedge D)}
+  \infer1[$\me'$]{E_x \wedge (C \vee D)}
 \end{prooftree}
@@
 \end{center}
-where $Q_x^*$ stands for $E_x^*$ or $U_x^*$.
+where $Q_x$ stands for $E_x$ or $U_x$.
 
@@
 \[\od{\odd{\odh{(\PE{A})^*} }
-{\Delta_1 }{(B')^*}{\acD, \me, \me'}} \]
+{\Delta_1 }{(\PE{B''})^*}{\acD, \me, \me'}} \]
 
 \begin{lemma}
-Every line of $\Delta_1$ is a propositional encoding (by
-confounding $Q_x^*$ with $Q_x$).
+Every line of $\Delta_1$ is a propositional encoding.
 
@@
 We proceed by bottom-up induction in the derivation.
-Clearly, $B'*$ is a propositional encoding as there is no disjunction of $Q_x$
+Clearly, $(\PE{B''})^*$ is a propositional encoding as there is no disjunction of $Q_x$
 in it.
@@
 
-If $G_i = \forall x H_i$ for some $i$, then there will be a conjunction of $U_x^*$
+If $G_i = \forall x H_i$ for some $i$, then there will be a conjunction of $U_x$
 and some formula which can never be eliminated by the rules $\me$, $\me'$ and
@@
 \begin{prooftree}
-  \hypo{(Q_x^* \wedge C) \vee (Q_x^* \wedge D)}
-  \infer1[$\me'$]{Q_x^* \wedge (C \vee D)}
-\end{prooftree}
-
-Suppose that $Q_X^* \wedge (C \vee D)$ = $\PE{F}$ for some $F$. It is clear
-that $Q_x^* = E_x^*$ and $F = \exists x G$ with $\PE{G} = C \vee D$ for some $G$.
+  \hypo{(E_x \wedge C) \vee (E_x \wedge D)}
+  \infer1[$\me'$]{E_x \wedge (C \vee D)}
+\end{prooftree}
+
+Suppose that $E_X \wedge (C \vee D)$ = $\PE{F}$ for some $F$. It is clear
+that $F = \exists x G$ with $\PE{G} = C \vee D$ for some $G$.
 We distinguish two cases:
 \begin{itemize}
-  \item $G = \forall y H$: in this case, $(Q_x^* \wedge C) \vee (Q_x^* \wedge
-D)$ has a subformula $(E_x^* \wedge U_y^*)$, which cannot be eliminated by the
+  \item $G = \forall y H$: in this case, $(E_x \wedge C) \vee (E_x \wedge
+D)$ has a subformula $(E_x \wedge U_y)$, which cannot be eliminated by the
 	rules $\me$, $\me'$, $\acD$. It is clear that ${\PE{A}}^*$ does not
 have a subformula of this form, which leads to a contradiction.
-  \item $G = G_1 \vee G_2$: in this case, $(Q_x^* \wedge C) \vee (Q_x^* \wedge
+  \item $G = G_1 \vee G_2$: in this case, $(E_x \wedge C) \vee (E_x \wedge
   D) = \PE{((\exists x G_1) \vee (\exists x G_2))}$.

### 2021-01-05 main.tex
Fix some typos

@@
 leaves whose atoms are pre-dual. A \bfit{linking} on $\Gamma$ is a set of 
-disjoint links such that each leaf of $\Gamma$ is in exacly one link. Similar
+disjoint links such that each leaf of $\Gamma$ is in exactly one link. Similar
 to the set of links in the linked fograph, a linking can be seen as a
@@
 A \bfit{switching graph} of a unification structure $\US(\lambda)$ is any
-derivative of $\US(\lambda)$ obtained by keeping only one edge into each $\parr$
+derivative of $\US(\lambda)$ obtained by keeping only one edge into each $\vee$
 and $\forall$ and undirecting remaining edges. A linking is \bfit{correct} if it
@@
 
-We also confound $\parr$ with $\vee$ and $\otimes$ with $\wedge$ as unification
-nets and first-order nets (fonets) are defined in different contexts.
-
 \begin{definition} A \textit{switching path} of a unification structure $U(\lambda)$ is a path in a switching graph of $U(\lambda)$.
@@
 \begin{definition} A \textit{switching path} of a  formula tree $\FT(A)$ is a
-	path in $\FT(A)$ that does not go through both incoming edges of a $\parr$.
+	path in $\FT(A)$ that does not go through both incoming edges of a $\vee$.
 \end{definition}
@@
   corresponding edge in the unification structure. \\
-  Now consider a $\parr$. We distinguish three cases:
+  Now consider a $\vee$. We distinguish three cases:
   \begin{itemize}
     \item the cycle goes through none of the two branches (incoming edges) of
-	    the $\parr$: we can choose an
-	    arbitrary switching for this $\parr$
+	    the $\vee$: we can choose an
+	    arbitrary switching for this $\vee$
     \item the cycle goes through exactly one branch: we choose the corresponding
@@
 		  (resp. right) branch, $u_L$, $u_R \in W$, such that
-		  $u_Lv_L, u_Rv_R \in E_W$ and that the corresponding switching path from $u_L$ to $v_L$ (resp. from $u_R$ to $v_R$) goes through the left (resp. right) edge of $\parr$.
+		  $u_Lv_L, u_Rv_R \in E_W$ and that the corresponding switching
+		  path from $u_L$ to $v_L$ (resp. from $u_R$ to $v_R$) goes
+		  through the left (resp. right) edge of $\vee$.
 
@@
     \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
-    \draw (0, 0) node (par) {$\parr$};
+    \draw (0, 0) node (par) {$\vee$};
     \draw (1, 1.7) node (dots1) {$\vdots$};
@@
 
-    {\bf Figure 7.} A schema showing that the two branches of the same $\parr$ cannot be used in the cycle at the same time. 
+    {\bf Figure 7.} A schema showing that the two branches of the same $\vee$ cannot be used in the cycle at the same time. 
     \end{center}
@@
     It is clear that $u_L$ (resp. $u_R$) is not in the branches of the
-	 $\parr$. Otherwise, there will be no switching path from $u_L$ to $v_L$
+	 $\vee$. Otherwise, there will be no switching path from $u_L$ to $v_L$
 
     By Proposition \ref{prop2}, we know that $u_L$ and $u_R$ are not
-	universal quantifiers which are ancestors the $\parr$
+	universal quantifiers which are ancestors the $\vee$
 	and that there exist one switching path from $u_L$ to $v_L$ and one
 	from $u_R$ to $v_R$. In particular, there exist one switching path from
-	$u_L$ to the $\parr$ and one from the $\parr$ to $v_R$, and by
+	$u_L$ to the $\vee$ and one from the $\vee$ to $v_R$, and by
 	concatenating the two, we obtain a switching path from $u_L$ to $v_R$. 
@@
 \begin{enumerate}
-  \item {\bf Encode dependencies as fresh links.} For each dependency $\exists x \rightarrow \forall y$, with corresponding subformulas $\exists x A$ and $\forall y B$, we add a fresh link as follows.
-Let $P$ be a fresh (nullary) predicate symbol.
-Replace $\exists x A$ with $P \otimes \exists x A$ and $\forall y B$ with $\overline{P} \parr \forall y B$, and add an axiom link between $P$ and $\overline{P}$.
+  \item {\bf Encode dependencies as fresh links.} For each dependency $\exists x
+	  \rightarrow \forall y$, with corresponding subformulas $\exists x A$
+		and $\forall y B$, we add a fresh link as follows. Let $P$ be a
+		fresh (nullary) predicate symbol. Replace $\exists x A$ with $P
+		\wedge \exists x A$ and $\forall y B$ with $\overline{P} \vee \forall y B$, and add an axiom link between $P$ and $\overline{P}$.
   \item {\bf Erase quantifiers.} After step 1, erase all the quantifiers. (We no longer need their leaps since they are encoded as links in step 1.
@@
   \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
-  \draw (0, 0) node (par1) {$\parr$};
+  \draw (0, 0) node (par1) {$\vee$};
   \draw (1.8, 1.2) node (z) {\color{blue} $\forall z$};
-  \draw (-1.8, 1.2) node (par2) {$\parr$};
+  \draw (-1.8, 1.2) node (par2) {$\vee$};
     \draw (-2.8, 2.4) node (x) {\color{red} $\exists x$};
@@
     \draw (-0.8, 3.6) node (qy) {$\overline{q}y$};
-    \draw (1.8, 2.4) node (tens) {$\otimes$};
+    \draw (1.8, 2.4) node (tens) {$\wedge$};
     \draw (0.8, 3.6) node (pz) {$pz$};
@@
   \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
-  \draw (0, 0) node (par1) {$\parr$};
-  \draw (1, 0.9) node (par3) {\color{blue} $\parr$};
-  \draw (-1.8, 1.2) node (par2) {$\parr$};
-  \draw (-2.6, 2.4) node (tens1) {\color{red} $\otimes$};
-  \draw (-1, 2.4) node (tens2) {$\otimes$};
+  \draw (0, 0) node (par1) {$\vee$};
+  \draw (1, 0.9) node (par3) {\color{blue} $\vee$};
+  \draw (-1.8, 1.2) node (par2) {$\vee$};
+  \draw (-2.6, 2.4) node (tens1) {\color{red} $\wedge$};
+  \draw (-1, 2.4) node (tens2) {$\wedge$};
   \draw (-2.2, 3.6) node (S) {\color{red} $S$};
@@
   \draw (0.4, 3.6) node (nS) {\color{blue} $\overline{S}$};
-  \draw (1.6, 1.8) node (par4) {$\parr$};
-  \draw (2.2, 2.7) node (tens3) {$\otimes$};
+  \draw (1.6, 1.8) node (par4) {$\vee$};
+  \draw (2.2, 2.7) node (tens3) {$\wedge$};
   \draw (2, 3.6) node (P) {$P$};

### 2021-01-06 main.tex
line numbers and page numbers
Fix the macros and reorganize the structure

@@
 
-% ** SYMBOLS **
+% ** RULES **
 
@@
 \newcommand{\mix}{\mathsf{mix}}
+\newcommand{\ctr}{\mathsf{ctr}}
+\newcommand{\wk}{\mathsf{wk}}
+
+% ** SYMBOLS **
+
+\newcommand{\cor}{\vee}
+\newcommand{\cand}{\wedge}
+
 % ** SPECIAL **
@@
 % Do not put math or special symbols in the title.
-\title{On First-order Proofs without syntax}
+\title{Combinatorial Proofs and Decomposition Theorem for First-order Logic}
 
@@
 \section{First-order Combinatorial Proofs}
-\subsection{First-order Logic and Graphs}
+\subsection{First-order Logic}
 
@@
 \fff$, and $\overline{\fff} = \ttt$. \bfit{Formulas} $A, B, C$ are generated inductively from atoms by binary
-connectives $\vee$ and $\wedge$ and quantifiers $\forall x$ and $\exists x$.
-The \bfit{negation} $\neg$ is defined in the usual way.
-A formula is \bfit{rectified} if all bound variables are distinct from one another and from all free variables.
-Without loss of generality, we assume that all formulas are rectifed throughtout the paper as every formula has a logically equivalent rectified form.
+connectives $\cor$ and $\cand$ and quantifiers $\forall x$ and $\exists x$.
+The \bfit{negation} $\neg$ is defined in the usual way. A formula is
+\bfit{rectified} if all bound variables are distinct from one another and from
+all free variables. Without loss of generality, we assume that all formulas are
+rectifed throughtout the paper as every formula has a logically equivalent
+rectified form. A formula is \bfit{semi-rectified} if it can be rectified in a
+unique way via variable renaming.
+
+We consider Gentzen's sequent calculus system $\LK$ \cite{Gentzen 1935}.
+
+A \bfit{sequent} is a multiset of formulas and sequents are proved using the
+following inference rules.
+\begin{center}
+
+\mbox{
+\begin{prooftree}
+  \infer0[$\ax$]{\vdash A, \neg A}
+\end{prooftree}
+\hspace{2cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A}
+  \hypo{\vdash \Delta, \neg A}
+  \infer2[$\cut$]{\vdash \Gamma, \Delta}
+\end{prooftree}}
+\vspace{0.2cm}
+
+\mbox{
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A}
+  \hypo{\vdash \Delta, B}
+  \infer2[$\cand$]{\vdash \Gamma, \Delta, A \cand B}
+\end{prooftree}
+\hspace{1.5cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A, B}
+  \infer1[$\cor$]{\vdash \Gamma, A \cor B}
+\end{prooftree}}
+\vspace{0.2cm}
+
+\mbox{
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A, A}
+  \infer1[$\ctr$]{\vdash \Gamma, A}
+\end{prooftree}
+	\hspace{2cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma}
+  \infer1[$\wk$]{\vdash \Gamma, A}
+\end{prooftree}}
+
+\mbox{
+\begin{prooftree}
+\infer0[$\ttt$]{\vdash \ttt}
+\end{prooftree}
+\hspace{2cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma}
+	\infer1[$\fff$]{\vdash \Gamma, \fff}
+\end{prooftree}}
+
+\mbox{
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A}
+  \infer1[$\forall$]{\vdash \Gamma, \forall x A}
+\end{prooftree}
+($x \notin fv(\Gamma)$)
+\hspace{1.2cm}
+
+\begin{prooftree}
+  \hypo{\vdash \Gamma, A[t/x]}
+  \infer1[$\exists$]{\vdash \Gamma, \exists x A}
+\end{prooftree}}
+
+\end{center}
+
+In this paper, we also use some \bfit{deep inference} \cite{BT 2001} rules that are in the
+following form:
+\begin{center}
+\begin{prooftree}
+  \hypo{\vdash S\{A\}}
+  \infer1[]{\vdash S\{B\}}
+\end{prooftree}
+\end{center}
+where $S\{ \ \}$ stands for a \bfit{context}, which corresponds to a sequent
+with a hole taking the place of an atom, and $S\{A\}$ represents
+the sequent or formula obtained by replacing the hole in $S\{ \ \}$ with the formula $A$. Formally,
+
+  \[C ::= \Box \ | \ A \cor C \ | \ C \cand A \ | \ \exists x C \ | \ \forall x C \].
+  \[S ::= C \ | \ A, S \ | \ S, A \] where $A$ is a formula.
+The above rule can be thus seen as the rewriting rule $A \rightarrow B$.
+
+We use the notation $\vlderivation{\vlde{}{\mathcal{P}}{B}{\vlhy {A}}}$ for
+denoting that there is a derivation from premise $\vdash S\{A\}$ to conclusion
+$\vdash S\{B\}$ in system $\mathcal{P}$ for any context $S$.
+
+\subsection{Graphs}
 
@@
 
-For a formula $A$, we can define its associated fograph $\Gr(A)$ inductively by: $\Gr(\alpha) = \cdot \alpha$ (a single-vertex graph whose vertex is labelled by $\alpha$); $\Gr(A \vee B) = \Gr(A) + \Gr(B)$ and $\Gr(A \wedge B) = \Gr(A) \times \Gr(B)$.
+For a formula $A$, we can define its associated fograph $\Gr(A)$ inductively by: $\Gr(\alpha) = \cdot \alpha$ (a single-vertex graph whose vertex is labelled by $\alpha$); $\Gr(A \cor B) = \Gr(A) + \Gr(B)$ and $\Gr(A \cand B) = \Gr(A) \times \Gr(B)$.
 The \bfit{binding graph} of a forgraph $G$ is the directed graph $(V_G, \{(b,
@@
 In $\FOMLL$, terms, atoms, formulas are defined as in first-order logic. For
-simplicity, we choose to use $\vee$ and $\wedge$ instead of $\parr$ and
+simplicity, we choose to use $\cor$ and $\cand$ instead of $\parr$ and
 $\otimes$ which are generally used in the presentation of linear logic.
@@
   \hypo{\vdash \Delta, B}
-  \infer2[$\conj$]{\vdash \Gamma, \Delta, A \wedge B}
+  \infer2[$\conj$]{\vdash \Gamma, \Delta, A \cand B}
 \end{prooftree}
@@
   \hypo{\vdash \Gamma, A, B}
-  \infer1[$\disj$]{\vdash \Gamma, A \vee B}
+  \infer1[$\disj$]{\vdash \Gamma, A \cor B}
 \end{prooftree}}
@@
 Let $\lambda$ is a unifiable linking on $\Gamma = A_1, \ldots, A_n$.
-Let $A = A_1 \vee \ldots \vee A_n$. The \bfit{unification structure}
+Let $A = A_1 \cor \ldots \cor A_n$. The \bfit{unification structure}
 $\US(\lambda)$
@@
 A \bfit{switching graph} of a unification structure $\US(\lambda)$ is any
-derivative of $\US(\lambda)$ obtained by keeping only one edge into each $\vee$
+derivative of $\US(\lambda)$ obtained by keeping only one edge into each $\cor$
 and $\forall$ and undirecting remaining edges. A linking is \bfit{correct} if it
@@
 
-\subsection{Deep Inference}
-In this paper we also use some \bfit{deep inference} \cite{BT 2001} rules that are in the
-following form:
-\begin{center}
-\begin{prooftree}
-  \hypo{\vdash S\{A\}}
-  \infer1[]{\vdash S\{B\}}
-\end{prooftree}
-\end{center}
-where $S\{ \ \}$ stands for a \bfit{context}, which corresponds to a sequent
-with a hole taking the place of an atom, and $S\{A\}$ represents
-the sequent or formula obtained by replacing the hole in $S\{ \ \}$ with the formula $A$. Formally,
-
-  \[C ::= \Box \ | \ A \vee C \ | \ C \wedge A \ | \ \exists x C \ | \ \forall x C \].
-  \[S ::= C \ | \ A, S \ | \ S, A \] where $A$ is a formula.
-The above rule can be thus seen as the rewriting rule $A \rightarrow B$.
-
-We use the notation $\vlderivation{\vlde{}{\mathcal{P}}{B}{\vlhy {A}}}$ for
-denoting that there is a derivation from premise $\vdash S\{A\}$ to conclusion
-$\vdash S\{B\}$ in system $\mathcal{P}$ for any context $S$.
-
 \section{From first-order logic to combinatorial proofs}
 
-\subsection{$\LK$}
-We start with Gentzen's sequent calculus system $\LK$ \cite{Gentzen 1935}.
-
-\begin{center}
-
-\mbox{
-\begin{prooftree}
-  \infer0[$ax$]{\vdash A, \neg A}
-\end{prooftree}
-\hspace{2cm}
-
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A}
-  \hypo{\vdash \Delta, \neg A}
-  \infer2[$cut$]{\vdash \Gamma, \Delta}
-\end{prooftree}}
-
-\mbox{
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A}
-  \hypo{\vdash \Delta, B}
-  \infer2[$\wedge$]{\vdash \Gamma, \Delta, A \wedge B}
-\end{prooftree}
-\hspace{1.5cm}
-
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A, B}
-  \infer1[$\vee$]{\vdash \Gamma, A \vee B}
-\end{prooftree}}
-
-\mbox{
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A, A}
-  \infer1[$ctr$]{\vdash \Gamma, A}
-\end{prooftree}
-	\hspace{2cm}
-
-\begin{prooftree}
-  \hypo{\vdash \Gamma}
-  \infer1[$wk$]{\vdash \Gamma, A}
-\end{prooftree}}
-
-\mbox{
-\begin{prooftree}
-\infer0[$\ttt$]{\vdash \ttt}
-\end{prooftree}
-\hspace{2cm}
-
-\begin{prooftree}
-  \hypo{\vdash \Gamma}
-	\infer1[$\fff$]{\vdash \Gamma, \fff}
-\end{prooftree}}
-
-\mbox{
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A}
-  \infer1[$\forall$]{\vdash \Gamma, \forall x A}
-\end{prooftree}
-($x \notin fv(\Gamma)$)
-\hspace{2cm}
-
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A[t/x]}
-  \infer1[$\exists$]{\vdash \Gamma, \exists x A}
-\end{prooftree}}
-
-\end{center}
-
-Note that the $\mix$ rule is derivable via weakening in $\LK$.
-
+\subsection{Decomposition Theorem}
 Consider the following deep inference rules \cite{BT 2001}:
@@
 \begin{prooftree}
-  \hypo{\vdash S\{A \vee A\}}
+  \hypo{\vdash S\{A \cor A\}}
   \infer1[$\cD$]{\vdash S\{A\}}
@@
 
-Note that the $ctr$ (resp. $wk$) rule in $\LK$ is derivable in $\{\cD, \vee\}$
+Note that the $\ctr$ (resp. $\wk$) rule in $\LK$ is derivable in $\{\cD, \cor\}$
 (resp. $\{\wD, \fff\}$) and that $\cD$ and $\wD$ rules
@@
   \hypo{\vdash \Gamma, A, A}
-  \infer1[$ctr$]{\vdash \Gamma, A}
+  \infer1[$\ctr$]{\vdash \Gamma, A}
 \end{prooftree}
@@
   \hypo{\vdash \Gamma, A, A}
-  \infer1[$\vee$]{\vdash \Gamma, A \vee A}
+  \infer1[$\cor$]{\vdash \Gamma, A \cor A}
   \infer1[$\cD$]{\vdash \Gamma, A}
@@
   \hypo{\vdash \Gamma}
-  \infer1[$wk$]{\vdash \Gamma, A}
+  \infer1[$\wk$]{\vdash \Gamma, A}
 \end{prooftree}
@@
 \begin{prooftree}
-\hypo{\Gamma,A \vee A}
+\hypo{\Gamma,A \cor A}
 \infer1[$\cD$]{\Gamma,A} 
 \hypo{\Delta,B}
-\infer2[$\wedge$]{\Gamma, \Delta, A \wedge B} 
+\infer2[$\cand$]{\Gamma, \Delta, A \cand B} 
 \end{prooftree}
@@
 \begin{prooftree}
-\hypo{\Gamma,A \vee A}
+\hypo{\Gamma,A \cor A}
 \hypo{\Delta,B}
-\infer2[$\wedge$]{\Gamma, \Delta, (A \vee A) \wedge B} 
-\infer1[$\cD$]{\Gamma, \Delta, A \wedge B} 
+\infer2[$\cand$]{\Gamma, \Delta, (A \cor A) \cand B} 
+\infer1[$\cD$]{\Gamma, \Delta, A \cand B} 
 \end{prooftree}}
@@
 Then we put the derivation consisting of only $\cD$ and $\wD$ under the proof in $\LKm$. Now we try to permute all the instances $\cD$ and $\wD$ upwards with the rules of LK and $mix$. 
-For the $\cD$ part, the only non-trivial case is the permutation with the $\vee$ rule where the formula generated is $A \vee A$.
+For the $\cD$ part, the only non-trivial case is the permutation with the $\cor$ rule where the formula generated is $A \cor A$.
 
@@
 \hypo{\vdash \Gamma, A, A}
-\infer1[$\vee$]{\vdash \Gamma, A \vee A}
+\infer1[$\cor$]{\vdash \Gamma, A \cor A}
 \infer1[$\cD$]{\vdash \Gamma, A}
@@
 \hypo{\vdash \Gamma, A, A}
-\infer1[$ctr$]{\vdash \Gamma, A}
+\infer1[$\ctr$]{\vdash \Gamma, A}
 \end{prooftree}
@@
 \hypo{\vdash \Gamma}
-\infer1[$wk$]{\vdash \Gamma, A}
+\infer1[$\wk$]{\vdash \Gamma, A}
 \end{prooftree}
@@
 
-\begin{definition} A \textit{switching path} of a unification structure $U(\lambda)$ is a path in a switching graph of $U(\lambda)$.
+\begin{definition} A \bfit{switching path} of a unification structure $U(\lambda)$ is a path in a switching graph of $U(\lambda)$.
 \end{definition}
 
-\begin{definition} A \textit{switching path} of a  formula tree $\FT(A)$ is a
-	path in $\FT(A)$ that does not go through both incoming edges of a $\vee$.
+\begin{definition} A \bfit{switching path} of a  formula tree $\FT(A)$ is a
+	path in $\FT(A)$ that does not go through both incoming edges of a $\cor$.
 \end{definition}
@@
   \item $u$ and $v$ are adjacent in $\Gr(A)$
-  \item $u$ and $v$ are connected by a switching path of $F(A)$, and if one of them is a universal quantifier, then the other is
+  \item $u$ and $v$ are connected by a switching path of $\FT(A)$, and if one of them is a universal quantifier, then the other is
 	not a descendant of the former.
@@
   \item If $A$ is an atom, trivial.
-  \item If $A = A_1 \wedge A_2$, then we distinguish two cases:
+  \item If $A = A_1 \cand A_2$, then we distinguish two cases:
     \begin{itemize}
@@
 		    vertex representing $A_1$ (resp. $A_2$) by a switching
-		    path. Together with the two edges incident to $A_1 \wedge
+		    path. Together with the two edges incident to $A_1 \cand
 		    A_2$, we obtain a switching path connecting $u$ and $v$.
     \end{itemize}
-  \item If $A = A_1 \vee A_2$, then we distinguish two cases:
+  \item If $A = A_1 \cor A_2$, then we distinguish two cases:
     \begin{itemize}
@@
   corresponding edge in the unification structure. \\
-  Now consider a $\vee$. We distinguish three cases:
+  Now consider a $\cor$. We distinguish three cases:
   \begin{itemize}
     \item the cycle goes through none of the two branches (incoming edges) of
-	    the $\vee$: we can choose an
-	    arbitrary switching for this $\vee$
+	    the $\cor$: we can choose an
+	    arbitrary switching for this $\cor$
     \item the cycle goes through exactly one branch: we choose the corresponding
@@
 		  path from $u_L$ to $v_L$ (resp. from $u_R$ to $v_R$) goes
-		  through the left (resp. right) edge of $\vee$.
+		  through the left (resp. right) edge of $\cor$.
 
@@
     \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
-    \draw (0, 0) node (par) {$\vee$};
+    \draw (0, 0) node (par) {$\cor$};
     \draw (1, 1.7) node (dots1) {$\vdots$};
@@
 
-    {\bf Figure 7.} A schema showing that the two branches of the same $\vee$ cannot be used in the cycle at the same time. 
+    {\bf Figure 7.} A schema showing that the two branches of the same $\cor$ cannot be used in the cycle at the same time. 
     \end{center}
@@
     It is clear that $u_L$ (resp. $u_R$) is not in the branches of the
-	 $\vee$. Otherwise, there will be no switching path from $u_L$ to $v_L$
+	 $\cor$. Otherwise, there will be no switching path from $u_L$ to $v_L$
 
     By Proposition \ref{prop2}, we know that $u_L$ and $u_R$ are not
-	universal quantifiers which are ancestors the $\vee$
+	universal quantifiers which are ancestors the $\cor$
 	and that there exist one switching path from $u_L$ to $v_L$ and one
 	from $u_R$ to $v_R$. In particular, there exist one switching path from
-	$u_L$ to the $\vee$ and one from the $\vee$ to $v_R$, and by
+	$u_L$ to the $\cor$ and one from the $\cor$ to $v_R$, and by
 	concatenating the two, we obtain a switching path from $u_L$ to $v_R$. 
@@
 Let $\theta$ be a unification structure on an $\FOMLL$ sequent $\Gamma$.
-We define the \textit{frame}  of $\theta$ by exhaustively applying the following subformula rewriting steps, to obtain a proof structure $\theta_m$ on an $\MLL$ sequent $\Gamma_m$:
+We define the \bfit{frame}  of $\theta$ by exhaustively applying the following subformula rewriting steps, to obtain a proof structure $\theta_m$ on an $\MLL$ sequent $\Gamma_m$:
 
@@
 		fresh (nullary) predicate symbol. Replace $\exists x A$ with $P
-		\wedge \exists x A$ and $\forall y B$ with $\overline{P} \vee \forall y B$, and add an axiom link between $P$ and $\overline{P}$.
+		\cand \exists x A$ and $\forall y B$ with $\overline{P} \cor \forall y B$, and add an axiom link between $P$ and $\overline{P}$.
   \item {\bf Erase quantifiers.} After step 1, erase all the quantifiers. (We no longer need their leaps since they are encoded as links in step 1.
@@
   \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
-  \draw (0, 0) node (par1) {$\vee$};
+  \draw (0, 0) node (par1) {$\cor$};
   \draw (1.8, 1.2) node (z) {\color{blue} $\forall z$};
-  \draw (-1.8, 1.2) node (par2) {$\vee$};
+  \draw (-1.8, 1.2) node (par2) {$\cor$};
     \draw (-2.8, 2.4) node (x) {\color{red} $\exists x$};
@@
     \draw (-0.8, 3.6) node (qy) {$\overline{q}y$};
-    \draw (1.8, 2.4) node (tens) {$\wedge$};
+    \draw (1.8, 2.4) node (tens) {$\cand$};
     \draw (0.8, 3.6) node (pz) {$pz$};
@@
   \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
-  \draw (0, 0) node (par1) {$\vee$};
-  \draw (1, 0.9) node (par3) {\color{blue} $\vee$};
-  \draw (-1.8, 1.2) node (par2) {$\vee$};
-  \draw (-2.6, 2.4) node (tens1) {\color{red} $\wedge$};
-  \draw (-1, 2.4) node (tens2) {$\wedge$};
+  \draw (0, 0) node (par1) {$\cor$};
+  \draw (1, 0.9) node (par3) {\color{blue} $\cor$};
+  \draw (-1.8, 1.2) node (par2) {$\cor$};
+  \draw (-2.6, 2.4) node (tens1) {\color{red} $\cand$};
+  \draw (-1, 2.4) node (tens2) {$\cand$};
   \draw (-2.2, 3.6) node (S) {\color{red} $S$};
@@
   \draw (0.4, 3.6) node (nS) {\color{blue} $\overline{S}$};
-  \draw (1.6, 1.8) node (par4) {$\vee$};
-  \draw (2.2, 2.7) node (tens3) {$\wedge$};
+  \draw (1.6, 1.8) node (par4) {$\cor$};
+  \draw (2.2, 2.7) node (tens3) {$\cand$};
   \draw (2, 3.6) node (P) {$P$};
@@
 \begin{prooftree}
-  \hypo{\vdash S\{a \vee a\}}
+  \hypo{\vdash S\{a \cor a\}}
   \infer1[$\acD$]{\vdash S\{a\}}
@@
 \begin{prooftree}
-  \hypo{\vdash S\{(A \wedge B) \vee (C \wedge D)\}}
-  \infer1[$\me$]{\vdash S\{(A \vee C) \wedge (B \vee D)\}}
+  \hypo{\vdash S\{(A \cand B) \cor (C \cand D)\}}
+  \infer1[$\me$]{\vdash S\{(A \cor C) \cand (B \cor D)\}}
 \end{prooftree}}
@@
 \begin{prooftree}
-  \hypo{\vdash S\{\exists x A \vee \exists x B\}}
-  \infer1[$\mee$]{\vdash S\{\exists x (A \vee B)\}}
+  \hypo{\vdash S\{\exists x A \cor \exists x B\}}
+  \infer1[$\mee$]{\vdash S\{\exists x (A \cor B)\}}
 \end{prooftree}	
@@
 \begin{prooftree}
-  \hypo{\vdash S\{\forall x A \vee \forall x B\}}
-  \infer1[$\meee$]{\vdash S\{\forall x (A \vee B)\}}
+  \hypo{\vdash S\{\forall x A \cor \forall x B\}}
+  \infer1[$\meee$]{\vdash S\{\forall x (A \cor B)\}}
 \end{prooftree}	
@@
 
-Here, we also consider the equivalence generated by the associativity, commutativity of $\vee$ and the equations $\ttt \vee A \equiv \ttt$ and $\fff \vee A \equiv A$.
+Here, we also consider the equivalence generated by the associativity, commutativity of $\cor$ and the equations $\ttt \cor A \equiv \ttt$ and $\fff \cor A \equiv A$.
 
@@
 	We prove that there is always $\vlderivation{\vlde{}{\{\acD, \me, \mee,
-	\meee\}}{A}{\vlhy {A \vee A}}}$ by structural induction on $A$.
+	\meee\}}{A}{\vlhy {A \cor A}}}$ by structural induction on $A$.
 \begin{itemize}
@@
 	  \begin{prooftree} 
-	    \hypo{\vdash S\{A \vee A\}}
+	    \hypo{\vdash S\{A \cor A\}}
 	    \infer1[$\equiv$]{\vdash S\{A\}}
@@
 	  \begin{prooftree}
-	    \hypo{\vdash S\{a \vee a\}}
+	    \hypo{\vdash S\{a \cor a\}}
 	    \infer1[$\acD$]{\vdash S\{a\}}.
 	  \end{prooftree}
-  \item If $A = A_1 \vee A_2$, then by the induction hypothesis, we have 
+  \item If $A = A_1 \cor A_2$, then by the induction hypothesis, we have 
 	  $\vlderivation{\vlde{}{\{\acD, \me, \mee,
-	\meee\}}{A_i}{\vlhy {A_i \vee A_i}}}$ for $i = 1, 2$.
+	\meee\}}{A_i}{\vlhy {A_i \cor A_i}}}$ for $i = 1, 2$.
 
@@
 	\begin{prooftree}
-	  \hypo{\vdash S\{(A_1 \vee A_2) \vee (A_1 \vee A_2)\}}
-	  \infer1[$\equiv$]{\vdash S\{(A_1 \vee A_1) \vee (A_2 \vee A_2)\}}
+	  \hypo{\vdash S\{(A_1 \cor A_2) \cor (A_1 \cor A_2)\}}
+	  \infer1[$\equiv$]{\vdash S\{(A_1 \cor A_1) \cor (A_2 \cor A_2)\}}
 	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
-		   {\vdash S\{A_1 \vee (A_2 \vee A_2)\}}
+		   {\vdash S\{A_1 \cor (A_2 \cor A_2)\}}
 	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
-		   {\vdash S\{A_1 \vee A_2\}}
-	\end{prooftree}
-  \item If $A = A_1 \wedge A_2$, then by the induction hypothesis, we have 
+		   {\vdash S\{A_1 \cor A_2\}}
+	\end{prooftree}
+  \item If $A = A_1 \cand A_2$, then by the induction hypothesis, we have 
 $\vlderivation{\vlde{}{\{\acD, \me, \mee, \meee\}}{A_i}
-	      {\vlhy {A_i \vee A_i}}}$ for $i = 1, 2$.
+	      {\vlhy {A_i \cor A_i}}}$ for $i = 1, 2$.
 
@@
 	\begin{prooftree}
-	  \hypo{\vdash S\{(A_1 \wedge A_2) \vee (A_1 \wedge A_2)\}}
-	  \infer1[$\me$]{\vdash S\{(A_1 \vee A_1) \wedge (A_2 \vee A_2)\}}
+	  \hypo{\vdash S\{(A_1 \cand A_2) \cor (A_1 \cand A_2)\}}
+	  \infer1[$\me$]{\vdash S\{(A_1 \cor A_1) \cand (A_2 \cor A_2)\}}
 	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
-		   {\vdash S\{A_1 \wedge (A_2 \vee A_2)\}}
+		   {\vdash S\{A_1 \cand (A_2 \cor A_2)\}}
 	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
-		   {\vdash S\{A_1 \wedge A_2\}}
+		   {\vdash S\{A_1 \cand A_2\}}
 	\end{prooftree}
   \item If $A = \exists x A'$, then by the induction hypothesis, we have $\vlderivation{\vlde{}{\{\acD, \me, \mee,
-	\meee\}}{A'}{\vlhy {A' \vee A'}}}$.
+	\meee\}}{A'}{\vlhy {A' \cor A'}}}$.
 
@@
 	\begin{prooftree}
-	  \hypo{\vdash S\{\exists x A' \vee \exists x A'\}}
- 	  \infer1[$\mee$]{\vdash S\{\exists x (A' \vee A')\}}
+	  \hypo{\vdash S\{\exists x A' \cor \exists x A'\}}
+ 	  \infer1[$\mee$]{\vdash S\{\exists x (A' \cor A')\}}
 	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
@@
   \item If $A = \forall x A'$, then by the induction hypothesis, we have $\vlderivation{\vlde{}{\{\acD, \me, \mee,
-	\meee\}}{A'}{\vlhy {A' \vee A'}}}$.
+	\meee\}}{A'}{\vlhy {A' \cor A'}}}$.
 
@@
 	\begin{prooftree}
-	  \hypo{\vdash S\{\forall x A' \vee \forall x A'\}}
- 	  \infer1[$\meee$]{\vdash S\{\forall x (A' \vee A')\}}
+	  \hypo{\vdash S\{\forall x A' \cor \forall x A'\}}
+ 	  \infer1[$\meee$]{\vdash S\{\forall x (A' \cor A')\}}
 	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
@@
 \begin{prooftree}
-\hypo{\exists x A}
-\infer1[$\equiv$]{\exists x (A \vee \fff)}
-\infer1[$\wD$]{\exists x (A \vee B)}
+  \hypo{\vdash S\{\exists x A\}}
+  \infer1[$\equiv$]{\vdash S\{\exists x (A \cor \fff)\}}
+  \infer1[$\wD$]{\vdash S\{\exists x (A \cor B)\}}
 \end{prooftree}
@@
 \begin{prooftree}
-\hypo{\exists x B}
-\infer1[$\equiv$]{\exists x (\fff \vee B)}
-\infer1[$\wD$]{\exists x (A \vee B)}
+  \hypo{\vdash S\{\exists x B\}}
+  \infer1[$\equiv$]{\vdash S\{\exists x (\fff \cor B)\}}
+  \infer1[$\wD$]{\vdash S\{\exists x (A \cor B)\}}
 \end{prooftree}
@@
 \begin{prooftree}
-\hypo{\exists x A \vee \exists x B}
-\ellipsis{}{\exists x (A \vee B) \vee \exists x (A \vee B)}
-\infer1[$\cD$]{\exists x (A \vee B)}
+  \hypo{\vdash S\{\exists x A \cor \exists x B\}}
+  \ellipsis{}{\vdash S\{\exists x (A \cor B) \cor \exists x (A \cor B)\}}
+  \infer1[$\cD$]{\vdash S\{\exists x (A \cor B)\}}
 \end{prooftree}
@@
 
-	$\PE{(A \vee B)} = \PE{A} \vee \PE{B}$ \hspace{2cm} $\PE{(A \wedge B)} =
-	\PE{A} \wedge \PE{B}$
-
-	$\PE{(\forall x A)} = U_x \vee \PE{A}$ \hspace{2cm} $\PE{(\exists x A)}
-	= E_x \wedge \PE{A}$
+	$\PE{(A \cor B)} = \PE{A} \cor \PE{B}$ \hspace{2cm} $\PE{(A \cand B)} =
+	\PE{A} \cand \PE{B}$
+
+	$\PE{(\forall x A)} = U_x \cor \PE{A}$ \hspace{2cm} $\PE{(\exists x A)}
+	= E_x \cand \PE{A}$
 
@@
     \begin{prooftree}
-      \hypo{\vdash S\{a \vee a\}}
+      \hypo{\vdash S\{a \cor a\}}
        \infer1[$\acD$]{\vdash S\{a\}} 
@@
     \begin{prooftree}
-      \hypo{\vdash S\{(A \wedge B) \vee (C \wedge D)\}}
-      \infer1[$\me$]{\vdash S\{(A \vee C) \wedge (B \vee D)\}}
+      \hypo{\vdash S\{(A \cand B) \cor (C \cand D)\}}
+      \infer1[$\me$]{\vdash S\{(A \cor C) \cand (B \cor D)\}}
     \end{prooftree}:
@@
     \begin{prooftree}
-      \hypo{\vdash S\{\exists x A \vee \exists x B\}}
-      \infer1[$\mee$]{\vdash S\{\exists x (A \vee B)\}}
+      \hypo{\vdash S\{\exists x A \cor \exists x B\}}
+      \infer1[$\mee$]{\vdash S\{\exists x (A \cor B)\}}
     \end{prooftree}:
@@
     \begin{prooftree}
-      \hypo{\vdash S\{\forall x A \vee \forall x B\}}
-      \infer1[$\meee$]{\vdash S\{\forall x (A \vee B)\}}
+      \hypo{\vdash S\{\forall x A \cor \forall x B\}}
+      \infer1[$\meee$]{\vdash S\{\forall x (A \cor B)\}}
     \end{prooftree}:
@@
   \item $ac$ is a fibration: suppose that $a$ that in the conclusion $a$ is bound by some quantifier $b$ in $S$, then for each of its preimages by $ac$, there exists exactly one binder (in fact, $b$) in $S$ that binds it.
-  \item $m_1$ and $m_2$ are fibrations: in the conclusion, for every atom $a$ in $A \vee B$ bound by the $x$-labelled quantifier, $a$ has exactly one preimage and it is bound by the $x$-llabelled quantifier in the premise.
+  \item $m_1$ and $m_2$ are fibrations: in the conclusion, for every atom $a$ in $A \cor B$ bound by the $x$-labelled quantifier, $a$ has exactly one preimage and it is bound by the $x$-llabelled quantifier in the premise.
 \end{itemize}
@@
 \begin{itemize}
-  \item $(E_x \vee \cdots \vee E_x)* = E_x$
-  \item $(U_x \vee \cdots \vee U_x)* = U_x$
+  \item $(E_x \cor \cdots \cor E_x)^* = E_x$
+  \item $(U_x \cor \cdots \cor U_x)^* = U_x$
   \item structural recursion in all the other cases.
@@
 \begin{prooftree}
-  \hypo{Q_x}
-  \infer1[$\acD$]{Q_x}
+  \hypo{S\{Q_x\}}
+  \infer1[$\acD$]{S\{Q_x\}}
 \end{prooftree}
@@
 \begin{prooftree}
-  \hypo{Q_x}
-  \infer1[$=$]{Q_x}
+  \hypo{S\{Q_x\}}
+  \infer1[$=$]{S\{Q_x\}}
 \end{prooftree}
@@
 \begin{prooftree}
-  \hypo{(E_x \wedge C) \vee (E_x \wedge D)}
-  \infer1[$\me$]{E_x \wedge (C \vee D)}
+  \hypo{S\{(E_x \cand C) \cor (E_x \cand D)\}}
+  \infer1[$\me$]{S\{E_x \cand (C \cor D)\}}
 \end{prooftree}
@@
 \begin{prooftree}
-  \hypo{(E_x \wedge C) \vee (E_x \wedge D)}
-  \infer1[$\me'$]{E_x \wedge (C \vee D)}
+  \hypo{S\{(E_x \cand C) \cor (E_x \cand D)\}}
+  \infer1[$\me'$]{S\{E_x \cand (C \cor D)\}}
 \end{prooftree}
@@
 \begin{prooftree}
-  \hypo{C \vee C}
+  \hypo{C \cor C}
   \infer1[$\acD$]{C}
@@
 
-It is clear that if $C$ is a propositional encoding, then so is $C \vee C$.
+It is clear that if $C$ is a propositional encoding, then so is $C \cor C$.
 
 Now consider the $\me$ rule:
-\begin{prooftree}
-  \hypo{(C \wedge D) \vee (E \wedge F)}
-  \infer1[$\me$]{(C \vee E) \wedge (D \vee F)}
-\end{prooftree}
-
-Suppose that $(C \vee E) \wedge (D \vee F) = \PE{G}$ for some $G$.
-Since $C \vee E$ cannot be $Q_x$ (otherwise, the rule applied would be
-$\me'$), $G$ can be written as $G_1 \wedge G_2$ with $C \vee E = \PE{G_1}$ and $D
-\vee F = \PE{G_2}$.
-
-We have thus $G_i = \forall x_i H_i$ or $J_i \vee K_i (i = 1, 2)$.
+\begin{center}
+\begin{prooftree}
+  \hypo{S\{(C \cand D) \cor (E \cand F)\}}
+  \infer1[$\me$]{S\{(C \cor E) \cand (D \cor F)\}}
+\end{prooftree}
+\end{center}
+Suppose that $(C \cor E) \cand (D \cor F) = \PE{G}$ for some $G$.
+Since $C \cor E$ cannot be $Q_x$ (otherwise, the rule applied would be
+$\me'$), $G$ can be written as $G_1 \cand G_2$ with $C \cor E = \PE{G_1}$ and $D
+\cor F = \PE{G_2}$.
+
+We have thus $G_i = \forall x_i H_i$ or $J_i \cor K_i (i = 1, 2)$.
 
@@
 
-Hence, $G_i$ can be written as $J_i \vee K_i$ for $i = 1, 2$. We now have $(C
-\wedge D) \vee (E \wedge F) = \PE{((J_1 \wedge J_2) \vee (K_1 \wedge
+Hence, $G_i$ can be written as $J_i \cor K_i$ for $i = 1, 2$. We now have $(C
+\cand D) \cor (E \cand F) = \PE{((J_1 \cand J_2) \cor (K_1 \cand
 K_2))}$.
@@
 Finally, consider the $\me'$ rule:
-
-\begin{prooftree}
-  \hypo{(E_x \wedge C) \vee (E_x \wedge D)}
-  \infer1[$\me'$]{E_x \wedge (C \vee D)}
-\end{prooftree}
-
-Suppose that $E_X \wedge (C \vee D)$ = $\PE{F}$ for some $F$. It is clear
-that $F = \exists x G$ with $\PE{G} = C \vee D$ for some $G$.
+\begin{center}
+\begin{prooftree}
+  \hypo{S\{(E_x \cand C) \cor (E_x \cand D)\}}
+  \infer1[$\me'$]{S\{E_x \cand (C \cor D)\}}
+\end{prooftree}
+\end{center}
+Suppose that $E_X \cand (C \cor D)$ = $\PE{F}$ for some $F$. It is clear
+that $F = \exists x G$ with $\PE{G} = C \cor D$ for some $G$.
 We distinguish two cases:
 \begin{itemize}
-  \item $G = \forall y H$: in this case, $(E_x \wedge C) \vee (E_x \wedge
-D)$ has a subformula $(E_x \wedge U_y)$, which cannot be eliminated by the
+  \item $G = \forall y H$: in this case, $(E_x \cand C) \cor (E_x \cand
+D)$ has a subformula $(E_x \cand U_y)$, which cannot be eliminated by the
 	rules $\me$, $\me'$, $\acD$. It is clear that ${\PE{A}}^*$ does not
 have a subformula of this form, which leads to a contradiction.
-  \item $G = G_1 \vee G_2$: in this case, $(E_x \wedge C) \vee (E_x \wedge
-  D) = \PE{((\exists x G_1) \vee (\exists x G_2))}$.
+  \item $G = G_1 \cor G_2$: in this case, $(E_x \cand C) \cor (E_x \cand
+  D) = \PE{((\exists x G_1) \cor (\exists x G_2))}$.
 \end{itemize}

### 2021-01-07 main.tex
Reorganize inference rules and figures

@@
 
-\documentclass[conference]{IEEEtran}
+\documentclass[conference,twosided,10pt]{IEEEtran}
 % Some Computer Society conferences also require the compsoc mode option,
@@
 % \documentclass[conference]{../sty/IEEEtran}
+
+%%line and pagenumbers to be removed for final version
+\usepackage[switch]{lineno}
+\pagestyle{plain}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\linenumbers
 \section{Introduction}
@@
 rectifed throughtout the paper as every formula has a logically equivalent
-rectified form. A formula is \bfit{semi-rectified} if it can be rectified in a
-unique way via variable renaming.
+rectified form.
 
@@
 A \bfit{sequent} is a multiset of formulas and sequents are proved using the
-following inference rules.
-\begin{center}
-
-\mbox{
+following inference rules:
+
+\begin{figure}[h]
+\begin{center}
 \begin{prooftree}
@@
 \end{prooftree}
-\hspace{2cm}
-
+\qquad
 \begin{prooftree}
@@
   \infer2[$\cut$]{\vdash \Gamma, \Delta}
-\end{prooftree}}
-\vspace{0.2cm}
-
-\mbox{
+\end{prooftree}
+\\[1.5ex]
 \begin{prooftree}
@@
 \end{prooftree}
-\hspace{1.5cm}
-
+\qquad
 \begin{prooftree}
@@
   \infer1[$\cor$]{\vdash \Gamma, A \cor B}
-\end{prooftree}}
-\vspace{0.2cm}
-
-\mbox{
+\end{prooftree}
+\\[1.5ex]
 \begin{prooftree}
@@
 \end{prooftree}
-	\hspace{2cm}
-
+\qquad
 \begin{prooftree}
@@
   \infer1[$\wk$]{\vdash \Gamma, A}
-\end{prooftree}}
-
-\mbox{
+\end{prooftree}
+\\[1.5ex]
 \begin{prooftree}
@@
 	\infer1[$\fff$]{\vdash \Gamma, \fff}
-\end{prooftree}}
-
-\mbox{
+\end{prooftree}
+\\[1.5ex]
 \begin{prooftree}
@@
 ($x \notin fv(\Gamma)$)
-\hspace{1.2cm}
-
+\qquad
 \begin{prooftree}
@@
   \infer1[$\exists$]{\vdash \Gamma, \exists x A}
-\end{prooftree}}
-
-\end{center}
+\end{prooftree}
+\caption{Gentzen's sequent calculus $\LK$}
+\end{center}
+\end{figure}
 
@@
 the sequent or formula obtained by replacing the hole in $S\{ \ \}$ with the formula $A$. Formally, 
-
-  \[C ::= \Box \ | \ A \cor C \ | \ C \cand A \ | \ \exists x C \ | \ \forall x C \].
-  \[S ::= C \ | \ A, S \ | \ S, A \] where $A$ is a formula.
+\begin{center}
+  $C ::= \Box \ | \ A \cor C \ | \ C \cand A \ | \ \exists x C \ | \ \forall x 
+C$.
+\\[1.5ex]
+  $S ::= C \ | \ A, S \ | \ S, A$ 
+\end{center}
+where $A$ is a formula.
 The above rule can be thus seen as the rewriting rule $A \rightarrow B$.
@@
 Sequents are proved using the inference rules of $\FOMLL$:
-\begin{center}
-
-\mbox{
+\begin{figure}[h]
+\begin{center}
 \begin{prooftree}
@@
   \infer2[$\cut$]{\vdash \Gamma, \Delta}
-\end{prooftree}}
-
-\mbox{
+\end{prooftree}
+\\[1.5ex]
 \begin{prooftree}
@@
   \infer1[$\disj$]{\vdash \Gamma, A \cor B}
-\end{prooftree}}
-
-\mbox{
+\end{prooftree}
+\\[1.5ex]
 \begin{prooftree}
@@
 ($x \notin fv(\Gamma)$)
-\hspace{2cm}
-
+\qquad
 \begin{prooftree}
@@
   \infer1[$\exist$]{\vdash \Gamma, \exists x A}
-\end{prooftree}}
-\end{center}
+\end{prooftree}
+\end{center}
+\caption{Sequent calculus for $\FOMLL$}
+\end{figure}
 
@@
 
+\begin{figure}[h]
     \begin{center}	
@@
 
-    {\bf Figure 7.} A schema showing that the two branches of the same $\cor$ cannot be used in the cycle at the same time. 
-    \end{center}
+    \caption{A schema showing that the two branches of the same $\cor$ cannot be
+	    used in the cycle at the same time.}
+\end{center}
+\end{figure}
 
@@
 
+\begin{figure}
 \begin{center}
@@
 \end{tikzpicture}
-\vspace{0.5cm}
+\vspace{1.5ex}
 
@@
 
-{\bf Figure 8.} A unification net and its frame. The colored part shows how the dependency ${\color{red} \exists x} \rightarrow {\color{blue} \forall z}$ is transformed.
-\end{center}
+\caption{A unification net and its frame. The colored part shows how the
+dependency ${\color{red} \exists x} \rightarrow {\color{blue} \forall z}$ is
+transformed.}
+\end{center}
+\end{figure}
 
@@
 \begin{center}
-\mbox{
 \begin{prooftree}
@@
 \end{prooftree}
-\hspace{0.3cm}
-
+\qquad
 \begin{prooftree}
@@
   \infer1[$\me$]{\vdash S\{(A \cor C) \cand (B \cor D)\}}
-\end{prooftree}}
-\vspace{0.2cm}
-
-\mbox{
+\end{prooftree}
+\\[1.5ex]
 \begin{prooftree}
@@
 \end{prooftree}	
-\hspace{0.3cm}
-
+\qquad
 \begin{prooftree}
@@
 \end{prooftree}	
-}
 \end{center}

### 2021-01-08 main.tex
beginning of intro

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\dominic}[1]{{\color{green}     \noindent[\![\![{\bf Dominic: }#1]\!]\!]}}
+\newcommand{\lutz}[1]{{\color{blue}     \noindent[\![\![{\bf Lutz: }#1]\!]\!]}}
+\newcommand{\juihsuan}[1]{{\color{violet}     \noindent[\![\![{\bf Jui-Hsuan: }#1]\!]\!]}}
+
+\newcommand{\todo}[1]{{\color{red}     \noindent[\![\![{\bf TODO: }#1]\!]\!]}}
+\newcommand{\TODO}[1]{\todo{#1}}
+\newcommand{\tocheck}[1][]{{\color{red}     \noindent[\![\![{\bf TO CHECK: }#1]\!]\!]}}
 
@@
 % Do not put math or special symbols in the title.
-\title{Combinatorial Proofs and Decomposition Theorem for First-order Logic}
+\title{Combinatorial Proofs and Decomposition Theorems for First-order Logic}
 
@@
 \IEEEauthorblockA{Inria, Equipe Partout\\
-Ecole Polytechnique\\
-LIX UMR 7161\\
+Ecole Polytechnique, LIX \\ %UMR 7161\\
 France}
@@
 \linenumbers
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
+
+First-order predicate logic is one of the cornerstones of modern
+logic. Since its formalisation by Frege~\cite{frege:79} it has seen a
+growing usage in many fields of mathematics and computer sience. Since
+the development of proof theory by Hilbert~\cite{hilbert:22},
+\emph{proofs} became first-class citizens as mathematical objects that
+could be studied on its own. Since Gentzen's \emph{sequent
+calculus}~\cite{gentzen:35:I,gentzen:35:II}, many other proof systems
+have been developed that allow the implementation of efficient proof
+search, for example \emph{analytic tableaux}~\cite{smullyan:68} or
+\emph{resolution}~\cite{robinson:65}. Despite the immense progress
+that has been made in proof theory in general and in the area of
+automated and interactive theorem provers in particular\cite{}\todo{find references}, we still have
+no satisfactory notion of proof identity for first-order logic. In
+this respect, proof theory is quite different from any other
+mathematical field. For example in group theory, two groups are
+\emph{the same} iff they are isomorphic; in topology, two spaces are
+\emph{the same} iff they are homeomorphic; etc. In proof theory, we
+have no such notion telling us when two proofs are \emph{the same},
+even though Hilbert was considering this problem as possible 24th
+problem for his famous lecture~\cite{hilbert:00} in
+1900~\cite{thiele:03}, before proof theory existed as a mathematical
+field.
+
+The main reason for this problem is that formal proofs, as they are
+usually studied in logic, are in inextricably tied to the syntactic
+(inference rule based) proof system in which they are carried out. And
+it is difficult to compare two proofs that are produced within two
+different sytactic proof systems, based on different sets of inference rules.
+\lutz{an example here?}
+
+This is where \emph{combinatorial proofs} come in. They have been
+introduced by Hughes~\cite{hughes:pws} for classical propositional
+logic as ``syntax-free'' notion of proof, and as a possible solution
+to Hilbert's 24th problem~\cite{hughes:invar} (see also~\cite{str:hilbert:24}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-01-08 main.tex
more of intro

@@
 \newcommand*{\FOMLLm}{\mathsf{MLL1 + mix}}
+\newcommand*{\FOKS}{\mathsf{KS1}}
 
@@
 logic as ``syntax-free'' notion of proof, and as a possible solution
-to Hilbert's 24th problem~\cite{hughes:invar} (see also~\cite{str:hilbert:24}).
+to Hilbert's 24th problem~\cite{hughes:invar} (see
+also~\cite{str:hilbert:24}). The basic idea is to abstract away from
+the syntax of the inference rules used in the proof and consider the
+proof as a combinatorial object, more precisely as a special kind
+homomorphism between two graphs obeying certain properties.
+\lutz{an example here?}
+
+It has been shown by several authors how syntactic proofs in various
+proof systems can be translated to propositional combinatorial proofs:
+for sequent proofs in~\cite{hughes:invar}, for deep inference proofs
+in~\cite{str:fscd17}, for Frege systems in~\cite{str:RR-9048}, and for
+tableaux systems and resolution in~\cite{acc:str:18}. This allows to
+define a natural notion of proof identity for propositional logic: two
+proofs are \emph{the same}, if they are mapped to the same
+combinatorial proof.
+
+Recently, Acclavio and Stra\ss burger extended this notion to relevant
+logics~\cite{acc:str:relevant} and to modal
+logics~\cite{acc:str:modal}; and Heijlties, Hughes and Stra\ss burger
+have provided combinatorial proofs for intuitionistic propositional
+logic~\cite{HHS:lics19}.
+
+In this paper we would like to push forward the idea that
+combinatorial proofs can also for first order logic be used as a
+notion of proof identity. \emph{First-order combinatorial proofs} have
+been introduced by Hughes in~\cite{hughes:fopws}. But even though
+Hughes shows that the conclusion of every first-order combinatorial
+proof is a valid formula, his proof is not really satisfactory, as (i)
+it is long and cumbersome, and (ii) it does not allow to read back a
+syntactic proof based inference rules. In fact, there is the
+fundamental problem that not all combinatorial proofs can be obtained
+as translations of sequent calculus proofs.
+
+In this paper we solve this issue by moving to a deep inference
+system. More precisely, we introduce a new proof system, called
+$\FOKS$, for first-order logic, that (i) reflects every combinatorial
+proof, i.e., there is a surjective mapping from proofs in $\FOKS$ to
+combinatorial proofs, that (ii) allows to provide simpler proofs of
+soundness and completeness of combinatorial proofs, and (iii) admits
+new decomposition theorems establishing a precise correspondence
+between certain syntactic inference rules and certain combinatiorial
+notions.
+
+In general, a \emph{decomposition theorem} provides normal forms of
+proofs, separating subsets of infernence rules of a proof system. A
+prominent example of a decomposion theorem is Herbrand's
+theorem~\cite{herbrand:phd}, which allows a separation between the
+proposotional part and the quantifier part in a first-order
+proof~\cite{gentzen:35:II,brunnler:06:herbrand}. Through the advent of
+deep inference, new kinds of proof decompositions became possible,
+most notably the separation between the linear part of a proof and the
+resource management of a proof. It has been shown by
+Stra{\ss}burger~\cite{str:07:RTA} that a proof in classical
+propositional logic can be decomposed into a proof of (multiplicative)
+linear logic, followed by a proof consisting only of contractions and
+weakenings. In this paper we show that the same is possible for
+first-order logic.
+
+In summary, this paper contains the following contributions:
 

### 2021-01-08 main.tex
done with first draft of intro

@@
 
-In summary, this paper contains the following contributions:
+Combinatorial proofs and deep infernence can be seen as opposite ends
+of a spectrum: whereas deep inference allows for a very fine
+franularity of inference rules---one inference rule in a standard
+formalism, like sequent calculus or semantic tableaux, is usually
+simulated by a sequence of different deep inference rules---have
+combinatorial proofs comletely abolished the concept of inference
+rule. Nonetheless, there is a close relationship between the two,
+realized through a decomposition theorem, as we establish it in this
+paper.
 

### 2021-01-08 main.tex
outline

@@
 \newcommand*{\LK}{\mathsf{LK}}
+\newcommand*{\FOLK}{\mathsf{LK1}}
 \newcommand*{\LKm}{\mathsf{LK + mix}}
 \newcommand*{\MLL}{\mathsf{MLL}}
-\newcommand*{\FOMLL}{\mathsf{MLL1}} 
-\newcommand*{\FOMLLm}{\mathsf{MLL1 + mix}}
+\newcommand*{\FOMLL}{\mathsf{MLL1^\times}} 
+\newcommand*{\FOMLLm}{\mathsf{MLL1+mix}}
 \newcommand*{\FOKS}{\mathsf{KS1}}
+\newcommand*{\FOMLS}{\mathsf{MLS1^\times}}
 
@@
 \DeclareTextFontCommand{\bfit}{\bfseries\itshape}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\set}[1]{\{#1\}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Preliminaries: First-order Logic}\label{sec:fologic}
+
+\subsection{Terms and Formulas}
+
+\subsection{Sequent Calculus $\FOLK$}
+
+\section{Preliminaries: First-order Graphs}\label{sec:fographs}
+
+\subsection{Graphs}
+
+\subsection{Cographs}
+
+\subsection{Fographs}
+
+\section{First-order Combinatorial Proofs}\label{sec:focp}
+
+\subsection{Fonets}
+
+\subsection{Skew Bifibrations}
+
+\section{First-order Deep Inference system $\FOKS$}\label{sec:foks}
+
+\section{Main Results}
+
+\section{Translating between $\FOLK$ and $\FOKS$}
+
+\subsection{The Linear Variants $\FOMLL$ and $\FOMLS$}
+
+\subsection{Contraction and Weakining}
+
+\subsection{A First Decomposition Theorem}
+
+$$
+\vlderivation{
+  \vlde{\set{\wD,\cD}}{}{C}{
+    \vlde{\FOMLS}{}{C'}{
+      \vlhy{\ttt}}}}
+$$
+
+\section{Fonets and Linear Proofs}
+
+\subsection{Unification Nets}
+
+\subsection{Translation between Unification Nets and $\FOMLL$}
+
+\subsection{Translation between Unification Nets and Fonets}
+
+\section{Skew Bifibrations and Resource Management}
+
+\subsection{From Contraction and Weakening to Skew Bifibrations}
+
+\subsection{From Skew Bifibrations to Contraction and Weakening}
+
+\section{Summary and Proofs of Main Results}
+
+\section{Conclusion}
+
+\bigskip
+\hrule
+\bigskip
 

### 2021-01-09 main.tex
Reorganize references

@@
 \usepackage{tikz}
-\usepackage{natbib}
 \usepackage{amsthm}\theoremstyle{plain}
@@
 \begin{document}
+\bstctlcite{refs:BSTcontrol}
 %
@@
 
-We consider Gentzen's sequent calculus system $\LK$ \cite{Gentzen 1935}.
+We consider Gentzen's sequent calculus system $\LK$ \cite{gentzen:35:I}.
 
@@
 
-In this paper, we also use some \bfit{deep inference} \cite{BT 2001} rules that are in the
+In this paper, we also use some \bfit{deep inference} \cite{brunnler:tiu:01} rules that are in the
 following form:
@@
 \subsection{Decomposition Theorem}
-Consider the following deep inference rules \cite{BT 2001}:
+Consider the following deep inference rules \cite{brunnler:tiu:01}:
 \begin{center}
@@
 
-D. Hughes proves in \cite{Hughes 2019} the soundness and completeness of
+D. Hughes proves in \cite{hughes:unifn} the soundness and completeness of
 unification nets with respect to $\FOMLLm$. In the following, we establish the
@@
 \begin{proof}
-We use frames introduced by D. Hughes in Section 4 of \cite{Hughes 2015}.
+We use frames introduced by D. Hughes in Section 4 of \cite{hughes:unifn}.
 
@@
 
-If $H$ contains a cycle, then the corresponding switching graph of $\theta_m$ also contains a cycle.
-Hence, by applying the propositional results (Theorem 7) from \cite{Retore 2003}, we conclude that there exists a chordless, alternating, and elementary cycle in the bicoloured graph ($W, E_W \uplus L_W$), which corresponds to an induced bimatching in the linked fograph.
+If $H$ contains a cycle, then the corresponding switching graph of $\theta_m$
+also contains a cycle. Hence, by applying the propositional results (Theorem 7)
+from \cite{retore:03}, we conclude that there exists a chordless, alternating, and elementary cycle in the bicoloured graph ($W, E_W \uplus L_W$), which corresponds to an induced bimatching in the linked fograph.
 (Note that the linked fograph (cograph) corresponding to $\theta_m$ is equivalent to the one corresponding to $\theta$.)
@@
 
-By considering propositional encodings, the maps defined are label-preserving skew fibrations on the underlying fographs according to \cite{Strassburger 2007}.
+By considering propositional encodings, the maps defined are label-preserving
+skew fibrations on the underlying fographs according to
+\cite{str:07:RTA}.
 
@@
   Therefore, all of these maps are skew bifibrations and since skew bifibrations
-on fographs compose (Lemma 10.32, \cite{Hughes 2019}), there exists a skew
+on fographs compose (Lemma 10.32, \cite{hughes:fopws}), there exists a skew
 bifibration from $\Gr(A)$ to $\Gr(B)$.
@@
 
-\input{bibliography}
+\bibliographystyle{IEEEtran}
+\bibliography{refs}
 

### 2021-01-09 main.tex
Reorganize paragraphs

@@
 that has been made in proof theory in general and in the area of
-automated and interactive theorem provers in particular\cite{}\todo{find references}, we still have
+automated and interactive theorem provers in particular\cite{paulson:isabelle}\todo{find references}, we still have
 no satisfactory notion of proof identity for first-order logic. In
@@
 \subsection{Terms and Formulas}
-
-\subsection{Sequent Calculus $\FOLK$}
-
-\section{Preliminaries: First-order Graphs}\label{sec:fographs}
-
-\subsection{Graphs}
-
-\subsection{Cographs}
-
-\subsection{Fographs}
-
-\section{First-order Combinatorial Proofs}\label{sec:focp}
-
-\subsection{Fonets}
-
-\subsection{Skew Bifibrations}
-
-\section{First-order Deep Inference system $\FOKS$}\label{sec:foks}
-
-\section{Main Results}
-
-\section{Translating between $\FOLK$ and $\FOKS$}
-
-\subsection{The Linear Variants $\FOMLL$ and $\FOMLS$}
-
-\subsection{Contraction and Weakining}
-
-\subsection{A First Decomposition Theorem}
-
-$$
-\vlderivation{
-  \vlde{\set{\wD,\cD}}{}{C}{
-    \vlde{\FOMLS}{}{C'}{
-      \vlhy{\ttt}}}}
-$$
-
-\section{Fonets and Linear Proofs}
-
-\subsection{Unification Nets}
-
-\subsection{Translation between Unification Nets and $\FOMLL$}
-
-\subsection{Translation between Unification Nets and Fonets}
-
-\section{Skew Bifibrations and Resource Management}
-
-\subsection{From Contraction and Weakening to Skew Bifibrations}
-
-\subsection{From Skew Bifibrations to Contraction and Weakening}
-
-\section{Summary and Proofs of Main Results}
-
-\section{Conclusion}
-
-\bigskip
-\hrule
-\bigskip
-
-\section{First-order Combinatorial Proofs}
-\subsection{First-order Logic}
 
@@
 
-We consider Gentzen's sequent calculus system $\LK$ \cite{gentzen:35:I}.
+\subsection{Sequent Calculus $\FOLK$}
+
+We consider Gentzen's sequent calculus system $\FOLK$ \cite{gentzen:35:I}.
 
@@
 \end{prooftree}
-\caption{Gentzen's sequent calculus $\LK$}
+\caption{Gentzen's sequent calculus $\FOLK$}
 \end{center}
@@
 
-In this paper, we also use some \bfit{deep inference} \cite{brunnler:tiu:01} rules that are in the
-following form:
-\begin{center}
-\begin{prooftree}
-  \hypo{\vdash S\{A\}}
-  \infer1[]{\vdash S\{B\}}
-\end{prooftree}
-\end{center}
-where $S\{ \ \}$ stands for a \bfit{context}, which corresponds to a sequent
-with a hole taking the place of an atom, and $S\{A\}$ represents
-the sequent or formula obtained by replacing the hole in $S\{ \ \}$ with the formula $A$. Formally, 
-\begin{center}
-  $C ::= \Box \ | \ A \cor C \ | \ C \cand A \ | \ \exists x C \ | \ \forall x 
-C$.
-\\[1.5ex]
-  $S ::= C \ | \ A, S \ | \ S, A$ 
-\end{center}
-where $A$ is a formula.
-The above rule can be thus seen as the rewriting rule $A \rightarrow B$.
-
-We use the notation $\vlderivation{\vlde{}{\mathcal{P}}{B}{\vlhy {A}}}$ for
-denoting that there is a derivation from premise $\vdash S\{A\}$ to conclusion
-$\vdash S\{B\}$ in system $\mathcal{P}$ for any context $S$.
+\section{Preliminaries: First-order Graphs}\label{sec:fographs}
 
@@
 
-\subsection{First-order combinatorial proofs}
+\subsection{Cographs}
+
+\subsection{Fographs}
+
 A cograph is \bfit{logical} if every vertex is labelled either by an atom or variable,
@@
 The \bfit{binding graph} of a forgraph $G$ is the directed graph $(V_G, \{(b,
-l) | b \text{ binds } l\})$.
+l) \ | \ b \text{ binds } l\})$.
+
+\section{First-order Combinatorial Proofs}\label{sec:focp}
+
+\subsection{Fonets}
 
@@
 
+\subsection{Skew Bifibrations}
+
 A graph homomorphism $f: (V, E) \rightarrow (V', E')$ is a \bfit{fibration} if
@@
 
+\subsection{First-order combinatorial proofs}
+
 \begin{definition}
@@
 \end{definition}
+
+\section{First-order Deep Inference system $\FOKS$}\label{sec:foks}
+
+\section{Main Results}
+
+\section{Translating between $\FOLK$ and $\FOKS$}
+
+\subsection{The Linear Variants $\FOMLL$ and $\FOMLS$}
+
+\subsection{Contraction and Weakining}
+
+\subsection{A First Decomposition Theorem}
+
+$$
+\vlderivation{
+  \vlde{\set{\wD,\cD}}{}{C}{
+    \vlde{\FOMLS}{}{C'}{
+      \vlhy{\ttt}}}}
+$$
+
+\section{Fonets and Linear Proofs}
+
+\subsection{Unification Nets}
+
+\subsection{Translation between Unification Nets and $\FOMLL$}
+
+\subsection{Translation between Unification Nets and Fonets}
+
+\section{Skew Bifibrations and Resource Management}
+
+\subsection{From Contraction and Weakening to Skew Bifibrations}
+
+\subsection{From Skew Bifibrations to Contraction and Weakening}
+
+\section{Summary and Proofs of Main Results}
+
+\section{Conclusion}
+
+\bigskip
+\hrule
+\bigskip
+
+\section{First-order Combinatorial Proofs}
+\subsection{First-order Logic}
+
+In this paper, we also use some \bfit{deep inference} \cite{brunnler:tiu:01} rules that are in the
+following form:
+\begin{center}
+\begin{prooftree}
+  \hypo{\vdash S\{A\}}
+  \infer1[]{\vdash S\{B\}}
+\end{prooftree}
+\end{center}
+where $S\{ \ \}$ stands for a \bfit{context}, which corresponds to a sequent
+with a hole taking the place of an atom, and $S\{A\}$ represents
+the sequent or formula obtained by replacing the hole in $S\{ \ \}$ with the formula $A$. Formally, 
+\begin{center}
+  $C ::= \Box \ | \ A \cor C \ | \ C \cand A \ | \ \exists x C \ | \ \forall x 
+C$.
+\\[1.5ex]
+  $S ::= C \ | \ A, S \ | \ S, A$ 
+\end{center}
+where $A$ is a formula.
+The above rule can be thus seen as the rewriting rule $A \rightarrow B$.
+
+We use the notation $\vlderivation{\vlde{}{\mathcal{P}}{B}{\vlhy {A}}}$ for
+denoting that there is a derivation from premise $\vdash S\{A\}$ to conclusion
+$\vdash S\{B\}$ in system $\mathcal{P}$ for any context $S$.
+
+\subsection{Graphs}
+
+\subsection{First-order combinatorial proofs}
 

### 2021-01-09 main.tex
formulas

--- 2021-01-08 main.tex
@@
 % (uncomment the ones you want to load)
-
+\makeatletter
+ \newcommand{\coloneqq}{%
+ \mathrel{%
+   \rlap{\raisebox{0.3ex}{$\m@th\cdot$}}\raisebox{-0.3ex}{$\m@th\cdot$}%
+   \rlap{\raisebox{0.3ex}{$\m@th\cdot$}}\raisebox{-0.3ex}{$\m@th\cdot$}%
+ }=}
+\makeatother
+
+\newcommand{\dual}[1]{\overline{#1}}
+\newcommand{\cneg}[1]{\dual{#1}}
+
+\newcommand{\VAR}{\textsc{var}}
+\newcommand{\FUN}{\textsc{fun}}
+\newcommand{\PRED}{\textsc{pred}}
+\newcommand{\ATOM}{\textsc{atom}}
+\newcommand{\FORM}{\textsc{form}}
+\newcommand{\TERM}{\textsc{term}}
 % *** MISC UTILITY PACKAGES ***
@@
 \subsection{Terms and Formulas}
+
+We start from a countable set $\VAR=\set{x,y,z,\ldots}$ of variables,
+a countable set $\FUN=\set{f,g,\ldots}$ of function symbols, and a
+counrable set $\PRED=\set{p,q,\ldots}$ of predicate symbols. Each function symbol and
+each predicate symbol has a finite arity. The grammars below generate
+the set $\TERM$ of \bfit{terms}, denoted by $s,t,u,\ldots$, the set
+$\ATOM$ of \bfit{atoms}, denoted by $a,b,c,\ldots$, and the set
+$\FORM$ of \bfit{formulas}, denoted by $A,B,C,\ldots$:
+\begin{equation*}
+  \begin{array}{r@{~}l}
+    t &\coloneqq~ x \mid f(t_1,\dots,t_n)
+    \\[.5ex]
+    a &\coloneqq~ \ttt\mid\fff\mid p(t_1,\dots,t_n) \mid \dual p(t_1,\dots,t_n)
+    \\[.5ex]
+    A &\coloneqq~ a \mid A\vlan A \mid A\vlor A \mid \exists x.A \mid \forall x.A
+\end{array}
+\end{equation*}
+where the arity of $t$ and $p$ is $n$. Note, that in this paper we
+consider the truth constants $\ttt$ (\emph{true}) and $\fff$
+(\emph{false}) as atoms, and we consider all formulas in negation
+normalform. The \bfit{negation} $(\dual\cdot)$ is defined for all
+atoms and formulas via the De Morgan laws as follows:
+\begin{equation*}
+  \dual\ttt =\fff
+  \quad
+  \dual\fff = \ttt
+  \quad
+  \dual{p(t_1 \ldots t_n)} = \dual{p}(t_1 \ldots t_n)
+  \quad
+  \dual{\dual p(t_1 \ldots t_n)} = p(t_1 \ldots t_n)
+\\
+  \dual{\dual a} = a
+\end{equation*}
+
+\todo{add missing equations and make it look nice}
+
+ A formula is
+\bfit{rectified} if all bound variables are distinct from one another and from
+all free variables. As every formula has a logically equivalent
+rectified form, we will most of the results in this paper to rectified formulas.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-01-09 main.tex

--- 2021-01-09 main.tex
@@
 \subsection{Terms and Formulas}
+
+We start from a countable set $\VAR=\set{x,y,z,\ldots}$ of variables,
+a countable set $\FUN=\set{f,g,\ldots}$ of function symbols, and a
+counrable set $\PRED=\set{p,q,\ldots}$ of predicate symbols. Each function symbol and
+each predicate symbol has a finite arity. The grammars below generate
+the set $\TERM$ of \bfit{terms}, denoted by $s,t,u,\ldots$, the set
+$\ATOM$ of \bfit{atoms}, denoted by $a,b,c,\ldots$, and the set
+$\FORM$ of \bfit{formulas}, denoted by $A,B,C,\ldots$:
+\begin{equation*}
+  \begin{array}{r@{~}l}
+    t &\coloneqq~ x \mid f(t_1,\dots,t_n)
+    \\[.5ex]
+    a &\coloneqq~ \ttt\mid\fff\mid p(t_1,\dots,t_n) \mid \dual p(t_1,\dots,t_n)
+    \\[.5ex]
+    A &\coloneqq~ a \mid A\vlan A \mid A\vlor A \mid \exists x.A \mid \forall x.A
+\end{array}
+\end{equation*}
+where the arity of $t$ and $p$ is $n$. Note, that in this paper we
+consider the truth constants $\ttt$ (\emph{true}) and $\fff$
+(\emph{false}) as atoms, and we consider all formulas in negation
+normalform. The \bfit{negation} $(\dual\cdot)$ is defined for all
+atoms and formulas via the De Morgan laws as follows:
+\begin{equation*}
+  \dual\ttt =\fff
+  \quad
+  \dual\fff = \ttt
+  \quad
+  \dual{p(t_1 \ldots t_n)} = \dual{p}(t_1 \ldots t_n)
+  \quad
+  \dual{\dual p(t_1 \ldots t_n)} = p(t_1 \ldots t_n)
+\\
+  \dual{\dual a} = a
+\end{equation*}
+
+\todo{add missing equations and make it look nice}
+
+ A formula is
+\bfit{rectified} if all bound variables are distinct from one another and from
+all free variables. As every formula has a logically equivalent
+rectified form, we will most of the results in this paper to rectified formulas.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Sequent Calculus $\FOLK$}
+
+\section{Preliminaries: First-order Graphs}\label{sec:fographs}
+
+\subsection{Graphs}
+
+\subsection{Cographs}
+
+\subsection{Fographs}
+
+\section{First-order Combinatorial Proofs}\label{sec:focp}
+
+\subsection{Fonets}
+
+\subsection{Skew Bifibrations}
+
+\section{First-order Deep Inference system $\FOKS$}\label{sec:foks}
+
+\section{Main Results}
+
+\section{Translating between $\FOLK$ and $\FOKS$}
+
+\subsection{The Linear Variants $\FOMLL$ and $\FOMLS$}
+
+\subsection{Contraction and Weakining}
+
+\subsection{A First Decomposition Theorem}
+
+$$
+\vlderivation{
+  \vlde{\set{\wD,\cD}}{}{C}{
+    \vlde{\FOMLS}{}{C'}{
+      \vlhy{\ttt}}}}
+$$
+
+\section{Fonets and Linear Proofs}
+
+\subsection{Unification Nets}
+
+\subsection{Translation between Unification Nets and $\FOMLL$}
+
+\subsection{Translation between Unification Nets and Fonets}
+
+\section{Skew Bifibrations and Resource Management}
+
+\subsection{From Contraction and Weakening to Skew Bifibrations}
+
+\subsection{From Skew Bifibrations to Contraction and Weakening}
+
+\section{Summary and Proofs of Main Results}
+
+\section{Conclusion}
+
+\bigskip
+\hrule
+\bigskip
+
+\section{First-order Combinatorial Proofs}
+\subsection{First-order Logic}
 

### 2021-01-09 main.tex
sequents

@@
 \usepackage[utf8]{inputenc}
+\usepackage{dashbox}
 \usepackage{ebproof}
@@
 \usepackage{virginialake}
+
 \usepackage{cmll}
+
 \usepackage{tikz}
@@
 
+\newcommand{\axr}{\mathsf{ax}}
+\newcommand{\cutr}{\mathsf{cut}}
+\newcommand{\mixr}{\mathsf{mix}}
+\newcommand{\conr}{\mathsf{ctr}}
+\newcommand{\weakr}{\mathsf{wk}}
+
 % ** SYMBOLS **
@@
 \newcommand{\set}[1]{\{#1\}}
+\newcommand{\sqn}[1]{\vdash#1}
+
+\newcommand{\sublist}[1]{\set{#1}}
+\newcommand{\subst}[2]{#1\mathord{\scriptstyle\mapsto} #2}
+\newcommand{\ssubst}[2]{\sublist{\subst{#1}{#2}}}
+
+\newcommand{\form}[1]{\mathrm{fm}(#1)}
 
@@
 \begin{document}
+\vlnosmallleftlabels
+
 \bstctlcite{refs:BSTcontrol}
@@
 
+A \bfit{substitution} is a function $\sigma\colon\VAR\to\TERM$ that is
+the identity almost everywhere. We denote substitutions as
+$\sigma=\sublist{\subst{x_1}{t_1},\ldots,\subst{x_n}{t_n}}$, where
+$\sigma(x_i)=t_i$ for $i=1..n$ and $\sigma(x)=x$ for all
+$x\notin\set{x_1,\ldots,x_n}$. 
+We write $A\sigma$ for the formula
+obtained from $A$ by applying $\sigma$, i.e., by simultaneously
+replacing all occurrences of $x_i$ by $t_i$.
+A \bfit{renaming} is a substitution $\sigma$ with $\sigma(x)\in\VAR$ for all variables.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Sequent Calculus $\FOLK$}
+
+\begin{figure}[!t]
+  \begin{center}
+    \framebox{%
+      $
+      \begin{array}{@{}c@{}}
+        \dbox{%
+          $
+          \begin{array}{c}
+            \vlinf{\axr}{}{\sqn{a,\cneg a}}{}
+            \qquad
+            \vlinf{\ttt}{}{\sqn{\ttt}}{}
+            \qquad
+            \vliinf{\mixr}{}{\sqn{\Gamma,\Delta}}{\sqn\Gamma}{\sqn\Delta}
+            \\ \\[-1ex]
+            \vlinf{\vlor}{}{\sqn{\Gamma,A\vlor B}}{\sqn{\Gamma,A,B}}
+            \qquad
+            \vliinf{\vlan}{}{\sqn{\Gamma,A\vlan B}}{\sqn{\Gamma,A}}{\sqn{B,\Delta}}
+            \\ \\[-1ex]
+            \vlinf{\exists}{}{\sqn{\Gamma,\exists x.A}}{\sqn{\Gamma,A\ssubst{x}{t}}}
+            \qquad
+            \vlinf{\forall}{\text{($x$ not free in $\Gamma$)}}{\sqn{\Gamma,\forall x.A}}{\sqn{\Gamma,A}}
+          \end{array}
+          $%
+        }%
+        \\\\[-1ex]
+        \vlinf{\conr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma,A,A}}
+        \qquad
+        \vlinf{\weakr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma}}
+      \end{array}
+      $
+    }
+  \end{center}
+  \caption{Sequent calculi $\FOLK$ (all rules) and $\FOMLL$ (rules in the dashed box)}
+  \label{fig:LK1}
+\end{figure}
+
+\bfit{Sequents}, denoted by $\Gamma,\Delta,\ldots$, are finite
+multisets of formulas, written as lists, separated by comma. The
+\bfit{corresponding formula} of a sequent $\Gamma=A_1,A_2,\ldots,A_n$
+is the disjunction of its formulas: $\form\Gamma=A_1\vlor
+A_2\vlor\cdots\vlor A_n$. A sequent is \bfit{rectified} iff its
+corresponding formula is.
 

### 2021-01-10 main.tex
Complete the negation part

@@
 new decomposition theorems establishing a precise correspondence
-between certain syntactic inference rules and certain combinatiorial
+between certain syntactic inference rules and certain combinatorial
 notions.
@@
 (\emph{false}) as atoms, and we consider all formulas in negation
-normalform. The \bfit{negation} $(\dual\cdot)$ is defined for all
+normal form. The \bfit{negation} $(\dual\cdot)$ is defined for all
 atoms and formulas via the De Morgan laws as follows:
 \begin{equation*}
-  \dual\ttt =\fff
-  \quad
-  \dual\fff = \ttt
-  \quad
-  \dual{p(t_1 \ldots t_n)} = \dual{p}(t_1 \ldots t_n)
-  \quad
-  \dual{\dual p(t_1 \ldots t_n)} = p(t_1 \ldots t_n)
-\\
-  \dual{\dual a} = a
+  \begin{array}{cc}
+  \dual\ttt =\fff &
+  \dual{p(t_1,\ldots,t_n)} = \dual{p}(t_1,\ldots,t_n) \\[.5ex]
+  \dual\fff = \ttt &
+  \dual{\dual p(t_1,\ldots,t_n)} = p(t_1,\ldots,t_n) \\[.5ex]
+  \dual{A \vlan B} = \dual{A} \ \vlor \ \dual{B} &
+  \dual{\exists x.A} = \forall x.\dual{A} \\[.5ex]
+  \dual{A \vlor B} = \dual{A} \ \vlan \ \dual{B} & 
+  \dual{\forall x.A} = \exists x.\dual{A} 
+  \end{array}
 \end{equation*}
@@
 all free variables. As every formula has a logically equivalent
-rectified form, we will most of the results in this paper to rectified formulas.
+rectified form, we will restrict most of the results in this paper to rectified formulas.
 

### 2021-01-10 main.tex
in sec.3 now

--- 2021-01-09 main.tex
@@
 \end{equation*}
-where the arity of $t$ and $p$ is $n$. Note, that in this paper we
+where the arity of $f$ and $p$ is $n$. Note, that in this paper we
 consider the truth constants $\ttt$ (\emph{true}) and $\fff$
@@
 
-\section{Preliminaries: First-order Graphs}\label{sec:fographs}
-
-\subsection{Graphs}
-
-\subsection{Cographs}
-
-\subsection{Fographs}
-
-\section{First-order Combinatorial Proofs}\label{sec:focp}
-
-\subsection{Fonets}
-
-\subsection{Skew Bifibrations}
-
-\section{First-order Deep Inference system $\FOKS$}\label{sec:foks}
-
-\section{Main Results}
-
-\section{Translating between $\FOLK$ and $\FOKS$}
-
-\subsection{The Linear Variants $\FOMLL$ and $\FOMLS$}
-
-\subsection{Contraction and Weakining}
-
-\subsection{A First Decomposition Theorem}
-
-$$
-\vlderivation{
-  \vlde{\set{\wD,\cD}}{}{C}{
-    \vlde{\FOMLS}{}{C'}{
-      \vlhy{\ttt}}}}
-$$
-
-\section{Fonets and Linear Proofs}
-
-\subsection{Unification Nets}
-
-\subsection{Translation between Unification Nets and $\FOMLL$}
-
-\subsection{Translation between Unification Nets and Fonets}
-
-\section{Skew Bifibrations and Resource Management}
-
-\subsection{From Contraction and Weakening to Skew Bifibrations}
-
-\subsection{From Skew Bifibrations to Contraction and Weakening}
-
-\section{Summary and Proofs of Main Results}
-
-\section{Conclusion}
-
-\bigskip
-\hrule
-\bigskip
-
-\section{First-order Combinatorial Proofs}
-\subsection{First-order Logic}
-
-\bfit{Terms} $s, t, u, \ldots$ and \bfit{atoms} (atomic formulas) $\alpha, \beta,
-\gamma, \ldots$ are generated inductively from variables $x, y, z, \ldots$: if
-$\delta$ (resp. $p$) is an $n$-ary function (resp. predicate) symbol and $t_1, \ldots,
-t_n$ are terms, then $\delta t_1 \ldots t_n$ (resp. $pt_1 \ldots t_n$) is a term
-(resp. atom). The set of atoms is extended with logical constant $\ttt$ and
-$\fff$. We also assume that each predicate symbol $p$ has a \bfit{dual}
-predicate symbol $\overline{p}$ with $\overline{p} \neq p$ and
-$\overline{\overline{p}} = p$. We extend the duality to atoms with
-$\overline{pt_1 \ldots t_n} = \overline{p}t_1 \ldots t_n$, $\overline{\ttt} =
-\fff$, and $\overline{\fff} = \ttt$. \bfit{Formulas} $A, B, C$ are generated inductively from atoms by binary
-connectives $\cor$ and $\cand$ and quantifiers $\forall x$ and $\exists x$.
-The \bfit{negation} $\neg$ is defined in the usual way. A formula is
-\bfit{rectified} if all bound variables are distinct from one another and from
-all free variables. Without loss of generality, we assume that all formulas are
-rectifed throughtout the paper as every formula has a logically equivalent
-rectified form.
-
-\subsection{Sequent Calculus $\FOLK$}
-
-We consider Gentzen's sequent calculus system $\FOLK$ \cite{gentzen:35:I}.
-
-A \bfit{sequent} is a multiset of formulas and sequents are proved using the
-following inference rules:
-
-\begin{figure}[h]
-\begin{center}
-\begin{prooftree}
-  \infer0[$\ax$]{\vdash A, \neg A}
-\end{prooftree}
-\qquad
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A}
-  \hypo{\vdash \Delta, \neg A}
-  \infer2[$\cut$]{\vdash \Gamma, \Delta}
-\end{prooftree}
-\\[1.5ex]
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A}
-  \hypo{\vdash \Delta, B}
-  \infer2[$\cand$]{\vdash \Gamma, \Delta, A \cand B}
-\end{prooftree}
-\qquad
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A, B}
-  \infer1[$\cor$]{\vdash \Gamma, A \cor B}
-\end{prooftree}
-\\[1.5ex]
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A, A}
-  \infer1[$\ctr$]{\vdash \Gamma, A}
-\end{prooftree}
-\qquad
-\begin{prooftree}
-  \hypo{\vdash \Gamma}
-  \infer1[$\wk$]{\vdash \Gamma, A}
-\end{prooftree}
-\\[1.5ex]
-\begin{prooftree}
-\infer0[$\ttt$]{\vdash \ttt}
-\end{prooftree}
-\qquad
-\begin{prooftree}
-  \hypo{\vdash \Gamma}
-	\infer1[$\fff$]{\vdash \Gamma, \fff}
-\end{prooftree}
-\\[1.5ex]
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A}
-  \infer1[$\forall$]{\vdash \Gamma, \forall x A}
-\end{prooftree}
-($x \notin fv(\Gamma)$)
-\qquad
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A[t/x]}
-  \infer1[$\exists$]{\vdash \Gamma, \exists x A}
-\end{prooftree}
-\caption{Gentzen's sequent calculus $\FOLK$}
-\end{center}
-\end{figure}
+In this paper we use the sequent calculus $\FOLK$, shown in
+Figure~\ref{fig:LK1}, which is a one-sided variant of Gentzen's
+original calculus~\cite{gentzen:35:I} for first-order logic. To
+simplify some technicalities later in this paper, we also include here
+the $\mixr$-rule. The linear fragment of $\FOLK$, i.e., the fragment
+without the rules $\conr$ (\emph{contraction}) and $\weakr$
+(\emph{weakening}) defines \emph{first-order multiplicative linear
+logic}~\cite{girard:87,girard:88} \emph{with
+mix}~\cite{fleury:retore:94,bellin:97}~(MLL1+mix). We denote that system
+here with $\FOMLL$ (shown in Figure~\ref{fig:LK1} in the dashed box).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 l) \ | \ b \text{ binds } l\})$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{First-order Combinatorial Proofs}\label{sec:focp}
+
+\subsection{Fonets}
+
+\subsection{Skew Bifibrations}
+
+\section{First-order Deep Inference system $\FOKS$}\label{sec:foks}
+
+\section{Main Results}
+
+\section{Translating between $\FOLK$ and $\FOKS$}
+
+\subsection{The Linear Variants $\FOMLL$ and $\FOMLS$}
+
+\subsection{Contraction and Weakining}
+
+\subsection{A First Decomposition Theorem}
+
+$$
+\vlderivation{
+  \vlde{\set{\wD,\cD}}{}{C}{
+    \vlde{\FOMLS}{}{C'}{
+      \vlhy{\ttt}}}}
+$$
+
+\section{Fonets and Linear Proofs}
+
+\subsection{Unification Nets}
+
+\subsection{Translation between Unification Nets and $\FOMLL$}
+
+\subsection{Translation between Unification Nets and Fonets}
+
+\section{Skew Bifibrations and Resource Management}
+
+\subsection{From Contraction and Weakening to Skew Bifibrations}
+
+\subsection{From Skew Bifibrations to Contraction and Weakening}
+
+\section{Summary and Proofs of Main Results}
+
+\section{Conclusion}
+
+\bigskip
+\hrule
+\bigskip
 

### 2021-01-10 main.tex
graphs

@@
 
+\usepackage{xifthen}
 \usepackage[utf8]{inputenc}
@@
 \newcommand{\TERM}{\textsc{term}}
+
+\newcommand{\fequ}{\equiv}
+\newcommand{\fequp}{\mathrel{\equiv'\mkern-2mu}}
+
+\newcommand{\graph}[1]{\mathcal{#1}}
+\newcommand{\vertices}[1][]{\ifthenelse{\isempty{#1}}{V}{V_{\graph{#1}}}}
+\newcommand{\edges}[1][]{\ifthenelse{\isempty{#1}}{E}{E_{\graph{#1}}}}
+
+\newcommand{\gA}{\graph{A}}
+\newcommand{\gC}{\graph{C}}
+\newcommand{\gG}{\graph{G}}
+\newcommand{\gH}{\graph{H}}
+
+\newcommand{\vA}{\vertices[A]}
+\newcommand{\vC}{\vertices[C]}
+\newcommand{\vG}{\vertices[G]}
+\newcommand{\vH}{\vertices[H]}
+
+\newcommand{\eA}{\edges[A]}
+\newcommand{\eC}{\edges[C]}
+\newcommand{\eG}{\edges[G]}
+\newcommand{\eH}{\edges[H]}
+
 % *** MISC UTILITY PACKAGES ***
@@
 
+\newcommand{\tuple}[1]{\langle#1\rangle}
+\newcommand{\pair}[1]{(#1)}
 \newcommand{\set}[1]{\{#1\}}
@@
 
+\newcommand{\compl}[1]{#1^\complement}
 \newcommand{\sublist}[1]{\set{#1}}
@@
 \end{equation*}
-
 \todo{add missing equations and make it look nice}
+\lutz{don't we need   $\dual{\dual a} = a$? (then it should follow that $\dual{\dual A} = A$)}
 
@@
 
-A \bfit{directed graph} $G = (V, E)$ consists of a finite set $V$ of
-\bfit{vertices} and a set of $E \subseteq V \times V$ of \bfit{direct edges}. An
+A \bfit{graph} $\gG=\tuple{\vG,\eG}$ is a pair where $\vG$ is a finite
+set of \bfit{vertices} and $\eG$ is a finite set of \bfit{edges},
+which are two-element subsets of $\vG$. We write $vw$ for an edge
+$\set{v,w}$.
+
+The \bfit{complement} of a graph $\gG=\tuple{\vG,\eG}$ is
+the graph $\compl\gG=\tuple{\vG,\compl\eG}$ where $vw\in\compl\eG$ iff
+$vw\neq\eG$.
+
+Let $\gG=\tuple{\vG,\eG}$ and $\gH=\tuple{\vH,\eH}$ be graphs such
+that $\vG\cap\vH=\emptyset$. A \bfit{homomorphism}
+$\phi\colon\gG\to\gH$ is a function $\phi\colon\vG\to\vH$ such that if
+$vw\in\eG$ then $\phi(v)\phi(w)\in\eH$. The \bfit{union} $\gG +\gH$ is
+the graph $\tuple{\vG \cup\vH,\eG\cup \eH}$ and the \bfit{join} $\gG
+\times \gH$ is the graph $\tuple{\vG \cup\vH,\eG \cup \eH \cup \set{vw
+    | v \in \vG, w \in \vH}}$.  A graph $\gG$ is \bfit{disconnected}
+if $\gG=\gG_1+\gG_2$ for two non-empty graphs $\gG_1,\gG_2$, otherwise
+it is \bfit{connected}. It is \emph{coconnected} if its complement is
+connected.
+
+A graph $\gG$ is \bfit{labelled} in a set $L$ if
+each vertex $v\in\vG$ has an element $\ell(v)\in L$ associated with it, its \bfit{label}.
+
+A \bfit{directed graph} $\gG =\tuple{\vG,\eG}$ is set $V$ of
+\bfit{vertices} and a set $\eG\subseteq \vG\times\vG$ of \bfit{direct edges}.
+A \bfit{directed graph homomorphism}
+$\phi\colon\tuple{\vG,\eG}\to\tuple{\vH,\eH}$ is function $\phi\colon\vG\to\vH$ such that if
+$\pair{v,w}\in\eG$ then $\pair{\phi(v),\phi(w)}\in\eH$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Cographs}
+
+An
 \bfit{undirected graph} $G = (V, E)$ consists of a finite set $V$ of vertices
@@
 \in E'$ whenever $vw \in E$.
-
-\subsection{Cographs}
-
 \subsection{Fographs}

### 2021-01-10 main.tex
graphs

@@
 \usepackage{amsthm}\theoremstyle{plain}
-\newtheorem{thm}{Theorem}[section]
+\newtheorem{thm}{Theorem}%[section]
 
@@
 
+\newcommand{\samecol}{\sim}
 \newcommand{\fequ}{\equiv}
@@
 \newcommand{\edges}[1][]{\ifthenelse{\isempty{#1}}{E}{E_{\graph{#1}}}}
+\newcommand{\bgraph}[1]{\mathcal{\vec{#1}}}
 
@@
 \newcommand{\gH}{\graph{H}}
+
+\newcommand{\bA}{\bgraph{A}}
+\newcommand{\bC}{\bgraph{C}}
+\newcommand{\bG}{\bgraph{G}}
+\newcommand{\bH}{\bgraph{H}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\Pfour}{\mathbf{P_4}}
 
@@
 
+\newcommand{\single}[1]{\bullet#1}
+
+\newcommand{\graphof}[1]{\llbracket#1\rrbracket}
 \newcommand{\compl}[1]{#1^\complement}
@@
 simplify some technicalities later in this paper, we also include here
-the $\mixr$-rule. The linear fragment of $\FOLK$, i.e., the fragment
+the $\mixr$-rule.
+
+\begin{thm}
+  A formula $A$ is a theorem of first-order logic iff the sequent $\sqn A$ is derivable in $\FOLK$.
+\end{thm}
+
+The linear fragment of $\FOLK$, i.e., the fragment
 without the rules $\conr$ (\emph{contraction}) and $\weakr$
@@
 
-A graph $\gG$ is \bfit{labelled} in a set $L$ if
-each vertex $v\in\vG$ has an element $\ell(v)\in L$ associated with it, its \bfit{label}.
+A graph $\gG$ is \bfit{labelled} in a set $L$ if each vertex $v\in\vG$
+has an element $\ell(v)\in L$ associated with it, its \bfit{label}.  A
+graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
+equivalence relation $\samcol$ on $\vG$; each equivalence class is a
+\bfit{colour}.  A \bfit{vertex renaming} of $\gG=\tuple{\vG,\eG}$
+along a bijection $(\hat\cdot)\colon\vG\to\hat\vG$ is the graph
+$\hat\gG=\tuple{\hat\vG,\set{\hat v\hat w\mid vw\in\eG}}$, with
+colouring and/or labelling inherited (i.e., $\hat v\samcol\hat w$ if
+$v\samecol w$, and $\ell(\hat v)=\ell(v)$). Following standard graph
+theory, we identify graphs modulo vertex renaming.
 
@@
 
-An
-\bfit{undirected graph} $G = (V, E)$ consists of a finite set $V$ of vertices
-and a set of $E$ of \bfit{undirected edges} (two-element subsets of $V$).
-For a given (directed or undirected) graph $G$, we write $V_G$ and $E_G$ for its
-vertex and edge sets respectively. We write $vw$ for an edge $(v, w)$ or $\{v,
-w\}$. Let $G = (V, E)$ and $G' = (V', E')$ be two undirected graphs. Without
-loss of generality, we assume that $V$ and $V'$ are disjoint. The \bfit{union}
-$G + G'$ is the graph $(V \cup V', E \cup E')$ and the \bfit{join} $G \times G'$
-is the graph $(V \cup V', E \cup E' \cup \{vv' | v \in V, v' \in V'\})$. A
-\bfit{cograph} is a $P_4$-free undireced grpah, i.e., for any distinct vertices $v_1,
-v_2, v_3, v_4 \in V$, the restriction of the edge sets on them is not equal to
-$\{v_1v_2, v_2v_3, v_3v_4\}$. In a graph $G = (V, E)$, the \bfit{neighbourhood}
-$N(v)$ of $v \in V$ is defined as the set $\{w | vw \in E\}$, a set $W \subseteq
-V$ induces a \bfit{matching} if for all $w \in W$, $N(w) \cap E$ is a singleton, and a module is a
-set $M \subseteq V$ such that $N(v) \ M = N(w) \ M$ for all $v, w \in M$. A
-\bfit{module} $M$ is strong if for every module $M'$, we have $M' \subseteq M$, $M
-\subseteq$ or $M \cap M' = \emptyset$. A \bfit{graph homomorphism} $f: (V, E)
-\rightarrow (V', E')$ is a function $f : V \rightarrow V'$ such that $f(v)f(w)
-\in E'$ whenever $vw \in E$.
+A graph $\gH=\tuple{\vH,\eH}$ is a \bfit{subgraph} of a graph
+$\gG=\tuple{\vG,\eG}$ if $\vH\subseteq\vG$ and $\eH\subseteq\eG$. It
+is \bfit{induced} if $v,w\in\vH$ and $vw\in\eG$ implies $vw\in\eH$.  A
+graph is \bfit{$\gH$-free} if it does not contain $\gH$ as an induced
+subgraph.  The graph $\Pfour$ is the (undirected) graph
+$\tuple{\set{v_1, v_2, v_3, v_4},\set{v_1v_2, v_2v_3, v_3v_4}}$.  A
+\bfit{cograph} is a $P_4$-free undirected graph. The interest in
+cographs for our paper comes from the following well-known fact.
+
+\begin{thm}[\cite{}]\label{thm:cograph}
+  A graph is a cograph iff it can be constructed from the singletons via the operations $+$ and~$\times$.
+\end{thm}
+\todo{ad the reference}
+
+In a graph $\gG$, the \bfit{neighbourhood} $N(v)$ of a vertex $v \in\vG$ is defined as
+the set $\set{w | vw \in\eG}$. 
+A \bfit{module} is a set $M \subseteq \vG$ such that $N(v) \ M = N(w) \ M$
+for all $v, w \in M$. A module $M$ is \bfit{strong} if for every
+module $M'$, we have $M' \subseteq M$, $M \subseteq$ or $M \cap M' =
+\emptyset$. A module is \bfit{proper} if it has two or more vertices.
+
+Modules in cographs correspond precisely to the subtrees of the
+cotrees (the term-trees constructing the graph via $+$ and~$\times$).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Fographs}
 
-A cograph is \bfit{logical} if every vertex is labelled either by an atom or variable,
-and it has at least one atom-labelled vertex. We denote by $label_G(v)$, or simply
-$label(v)$ the label of a vertex in a logical cograph $G$. An atom-labelled vertex is called
-a \bfit{literal} and a variable-labelled vertex is called a \bfit{binder}. A
-binder labelled with $x$ is called an \bfit{$x$-binder}. The \bfit{scope} of a binder
-$b$ is the smallest strong module containing at least two vertices, including
-the binder itself. An \bfit{$x$-literal} is a literal whose atom contains the variable $x$. An $x$-binder \bfit{binds} every $x$-literal in its scope.
-In a logical cograph $G$, a binder $b$ is \bfit{existential} (resp. \bfit{universal}) if, for every other
-vertex $v$ in its scope, we have $bv \in E_G$ (resp. $bv \notin E_G$). An
-$x$-binder is \bfit{legal} if its scope contains no other $x$-binder and at least one
-literal.
-
-We now introduce first-order graphs which are used to represent first-order formulas.
+A cograph is \bfit{logical} if every vertex is labelled either by an
+atom or variable, and it has at least one atom-labelled vertex. We
+write $\single\alpha$ for an $\alpha$-labelled vertex. An
+atom-labelled vertex is called a \bfit{literal} and a
+variable-labelled vertex is called a \bfit{binder}. A binder labelled
+with $x$ is called an \bfit{$x$-binder}. The \bfit{scope} of a binder
+$b$ is the smallest proper strong module containing $b$.
+An \bfit{$x$-literal} is a literal whose
+atom contains the variable $x$. An $x$-binder \bfit{binds} every
+$x$-literal in its scope.  In a logical cograph $G$, a binder $b$ is
+\bfit{existential} (resp. \bfit{universal}) if, for every other vertex
+$v$ in its scope, we have $bv \in E_G$ (resp. $bv \notin E_G$). An
+$x$-binder is \bfit{legal} if its scope contains no other $x$-binder
+and at least one literal.
 
 \begin{definition}
-A \bfit{first-order graph} or \bfit{fograph} is a logical cograph with legal binders.
+A \bfit{first-order graph} or \bfit{fograph} is a logical cograph with legal binders. The
+\bfit{binding graph} of a fograph $\gG$ is the directed graph $\bG=\tuple{\vG,
+\set{(b, l) \mid b \text{ binds } l}}$.
 \end{definition}
 
-For a formula $A$, we can define its associated fograph $\Gr(A)$ inductively by: $\Gr(\alpha) = \cdot \alpha$ (a single-vertex graph whose vertex is labelled by $\alpha$); $\Gr(A \cor B) = \Gr(A) + \Gr(B)$ and $\Gr(A \cand B) = \Gr(A) \times \Gr(B)$.
-The \bfit{binding graph} of a forgraph $G$ is the directed graph $(V_G, \{(b,
-l) \ | \ b \text{ binds } l\})$.
-
+We now define a mapping $\graphof\cdot$ from formulas to (labelled)
+graphs, inductively as follows:
+
+For a formula $A$, we can define its
+associated fograph $\graphof(A)$ inductively by: $\graphof(\alpha) =
+\cdot \alpha$ (a single-vertex graph whose vertex is labelled by
+$\alpha$); $\graphof(A \cor B) = \graphof(A) + \graphof(B)$ and
+$\graphof(A \cand B) = \graphof(A) \times \graphof(B)$.
+\todo{make look nice, use array}
+
+\begin{lemma}
+  If $A$ is a rectified formula then $\graphof A$ is a fograph.
+\end{lemma}
+
+\begin{proof}
+  That  $\graphof A$ is a logical cograph follows immediately from the definition and Theorem~\ref{thm:cograph}. 
+  \todo{}\lutz{maybe mention also fn 2-5 in arxiv-paper}
+\end{proof}
+
+\todo{def $\fequ$}
+
+\begin{thm}
+  Let $A,B$ be rectified formulas. Then
+  $$
+  A\fequ B \iff \graphof A =\graphof B
+  $$
+\end{thm}
+
+\begin{proof}
+  \todo{}
+\end{proof}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Skew Bifibrations}
-
-\section{First-order Deep Inference system $\FOKS$}\label{sec:foks}
-
-\section{Main Results}
-
-\section{Translating between $\FOLK$ and $\FOKS$}
-
-\subsection{The Linear Variants $\FOMLL$ and $\FOMLS$}
-
-\subsection{Contraction and Weakining}
-
-\subsection{A First Decomposition Theorem}
-
-$$
-\vlderivation{
-  \vlde{\set{\wD,\cD}}{}{C}{
-    \vlde{\FOMLS}{}{C'}{
-      \vlhy{\ttt}}}}
-$$
-
-\section{Fonets and Linear Proofs}
-
-\subsection{Unification Nets}
-
-\subsection{Translation between Unification Nets and $\FOMLL$}
-
-\subsection{Translation between Unification Nets and Fonets}
-
-\section{Skew Bifibrations and Resource Management}
-
-\subsection{From Contraction and Weakening to Skew Bifibrations}
-
-\subsection{From Skew Bifibrations to Contraction and Weakening}
-
-\section{Summary and Proofs of Main Results}
-
-\section{Conclusion}
-
-\bigskip
-\hrule
-\bigskip
-
-\section{First-order Combinatorial Proofs}\label{sec:focp}
-
-\subsection{Fonets}
-
-In a fograph, two atoms are \bfit{pre-dual} if their predicate symbols are dual
+Two atoms are \bfit{pre-dual} if their predicate symbols are dual
 (e.g. $pxy$ and $\overline{p}yz$) and two literals are \bfit{pre-dual} if their
@@
 
+\todo{define matching}
+
+\todo{adjust notation}
+
 \begin{definition}
@@
 
-\subsection{First-order combinatorial proofs}
+%%\subsection{First-order combinatorial proofs}
 
@@
 combinatorial proof} of a formula $A$ is a combinatorial proof of its graph
-$\Gr(A)$.
+$\graphof(A)$.
 \end{definition}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \label{prop2}
-Let $u$ and $v$ be two distinct vertices of a fograph $\Gr(A)$, then we have the equivalence
+Let $u$ and $v$ be two distinct vertices of a fograph $\graphof(A)$, then we have the equivalence
 between:
 \begin{itemize}
-  \item $u$ and $v$ are adjacent in $\Gr(A)$
+  \item $u$ and $v$ are adjacent in $\graphof(A)$
   \item $u$ and $v$ are connected by a switching path of $\FT(A)$, and if one of them is a universal quantifier, then the other is
@@
       \item one of them is in $A_1$ and the other is in $A_2$: they are
-	      adjacent in $\Gr(A)$ by definition. By Proposition \ref{prop1},
+	      adjacent in $\graphof(A)$ by definition. By Proposition \ref{prop1},
 		    the one in $A_1$ (resp. $A_2$) is connected to the
@@
       \item one of them is in $A_1$ and the other is in $A_2$: they are not
-	      adjacent in $\Gr(A)$ by definition. It is clear that they
+	      adjacent in $\graphof(A)$ by definition. It is clear that they
 		    are not connected by a switching path.
@@
       \item one of them is $\forall x$ and the other is in $A'$:
-	      they are not adjacent in $\Gr(A)$ by definition and it is clear that
+	      they are not adjacent in $\graphof(A)$ by definition and it is clear that
 		    the former is a descendant of $\forall x$.
@@
 \begin{proposition}
-If there exists an induced bimatching of the linked fograph $G = \Gr(A)$, then there exists a switching graph of the corresponding unification net which contains a cycle.
+If there exists an induced bimatching of the linked fograph $G = \graphof(A)$, then there exists a switching graph of the corresponding unification net which contains a cycle.
 \begin{proof}
@@
   \item $\PE{A}$ is a formula containing no quantifier for any formula $A$.
-  \item $\Gr(\PE{A}) = \Gr(A)$ by confounding the atoms $U_x$, $E_x$ with the variable
-	  $x$. Thus, a map $f : \Gr(\PE{A}) \rightarrow \Gr(\PE{B})$ can be seen as a map
-		$f : \Gr(A) \rightarrow \Gr(B)$.
+  \item $\graphof(\PE{A}) = \graphof(A)$ by confounding the atoms $U_x$, $E_x$ with the variable
+	  $x$. Thus, a map $f : \graphof(\PE{A}) \rightarrow \graphof(\PE{B})$ can be seen as a map
+		$f : \graphof(A) \rightarrow \graphof(B)$.
   \item $\PE{(S\{A\})} = \PE{S}\{\PE{A}\}$.
@@
 \begin{center}
-for each $x$-binder $b$ in $\Gr(\PE{B})$, for each vertex $v \in V(\Gr(\PE{A}))$
+for each $x$-binder $b$ in $\graphof(\PE{B})$, for each vertex $v \in V(\graphof(\PE{A}))$
 such that $g(v)$ is bound by $b$, there exists a unique binder $b'$ such
@@
 on fographs compose (Lemma 10.32, \cite{hughes:fopws}), there exists a skew
-bifibration from $\Gr(A)$ to $\Gr(B)$.
+bifibration from $\graphof(A)$ to $\graphof(B)$.
 
@@
 unification net which is equivalent to the fonet corresponding to $\Pi$, i.e.,
-the fograph $\Gr(A')$ together with the links of $\Pi$. By Lemma \ref{mlem}, 
-there exists a skew bifibration $\Gr(A') \rightarrow \Gr(A)$. We have thus a
+the fograph $\graphof(A')$ together with the links of $\Pi$. By Lemma \ref{mlem}, 
+there exists a skew bifibration $\graphof(A') \rightarrow \graphof(A)$. We have thus a
 combinatorial proof of $A$.
@@
 Since there is an edge from $U_x$ (resp. $E_x$) to all the literals it binds in the 
-binding graph $\overrightarrow{\Gr(B)}$, if one of the atoms is in the image, 
+binding graph $\overrightarrow{\graphof(B)}$, if one of the atoms is in the image, 
 $U_x$ (resp. $E_x$) should also be in the image since $f$ is a fibration on binding graphs.

### 2021-01-10 main.tex
graphs

@@
 graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
-equivalence relation $\samcol$ on $\vG$; each equivalence class is a
+equivalence relation $\samecol$ on $\vG$; each equivalence class is a
 \bfit{colour}.  A \bfit{vertex renaming} of $\gG=\tuple{\vG,\eG}$
@@
 $\hat\gG=\tuple{\hat\vG,\set{\hat v\hat w\mid vw\in\eG}}$, with
-colouring and/or labelling inherited (i.e., $\hat v\samcol\hat w$ if
+colouring and/or labelling inherited (i.e., $\hat v\samecol\hat w$ if
 $v\samecol w$, and $\ell(\hat v)=\ell(v)$). Following standard graph

### 2021-01-10 main.tex
Some modifications

--- 2021-01-10 main.tex
@@
 
+\juihsuan{isn't it given by the first four equations? I think that we use the
+notation of negation for atoms and formulas. We may also need to precise that each
+predicate symbol $p$ has a dual $\dual{p}$.}
+
  A formula is
@@
 replacing all occurrences of $x_i$ by $t_i$.
-A \bfit{renaming} is a substitution $\sigma$ with $\sigma(x)\in\VAR$ for all variables.
+A \bfit{renaming} is a substitution $\sigma$ with $\sigma(x)\in\VAR$ for all variable $x$.
 
@@
 the graph $\compl\gG=\tuple{\vG,\compl\eG}$ where $vw\in\compl\eG$ iff
-$vw\neq\eG$.
+$vw\notin\eG$.
 
@@
 
-A \bfit{directed graph} $\gG =\tuple{\vG,\eG}$ is set $V$ of
+A \bfit{directed graph} $\gG =\tuple{\vG,\eG}$ is a set $\vG$ of
 \bfit{vertices} and a set $\eG\subseteq \vG\times\vG$ of \bfit{direct edges}.

### 2021-01-10 main.tex
Make some modifications in the graph part

@@
 \newcommand{\bgraph}[1]{\mathcal{\vec{#1}}}
+\newcommand{\lgraph}[1]{\mathcal{L_{#1}}}
+\newcommand{\leaps}[1]{L_{#1}}
 
@@
 \newcommand{\eH}{\edges[H]}
+
+\newcommand{\lgG}{\lgraph{\gG}}
+
+\newcommand{\lpG}{\leaps{\gG}}
 
@@
 \newcommand{\Gr}{\mathcal{G}}
-\newcommand{\LG}{\mathcal{L}}
 \newcommand{\FT}{\mathcal{F}}
@@
 \times \gH$ is the graph $\tuple{\vG \cup\vH,\eG \cup \eH \cup \set{vw
-    | v \in \vG, w \in \vH}}$.  A graph $\gG$ is \bfit{disconnected}
+\mid v \in \vG, w \in \vH}}$.  A graph $\gG$ is \bfit{disconnected}
 if $\gG=\gG_1+\gG_2$ for two non-empty graphs $\gG_1,\gG_2$, otherwise
@@
 
-\begin{thm}[\cite{}]\label{thm:cograph}
+\begin{thm}[\cite{duffin:65}]\label{thm:cograph}
   A graph is a cograph iff it can be constructed from the singletons via the operations $+$ and~$\times$.
 \end{thm}
-\todo{ad the reference}
+\todo{ad the reference} \juihsuan{done}
 
 In a graph $\gG$, the \bfit{neighbourhood} $N(v)$ of a vertex $v \in\vG$ is defined as
-the set $\set{w | vw \in\eG}$. 
+the set $\set{w \mid vw \in\eG}$. A set $W \subseteq \vG$ induces a \bfit{matching} in
+$\gG$ if for all $w \in W$, $N(w) \cap W$ is a singleton.
 A \bfit{module} is a set $M \subseteq \vG$ such that $N(v) \ M = N(w) \ M$
@@
 atom contains the variable $x$. An $x$-binder \bfit{binds} every
-$x$-literal in its scope.  In a logical cograph $G$, a binder $b$ is
+$x$-literal in its scope.  In a logical cograph $\gG$, a binder $b$ is
 \bfit{existential} (resp. \bfit{universal}) if, for every other vertex
-$v$ in its scope, we have $bv \in E_G$ (resp. $bv \notin E_G$). An
+$v$ in its scope, we have $bv \in \eG$ (resp. $bv \notin \eG$). An
 $x$-binder is \bfit{legal} if its scope contains no other $x$-binder
@@
 For a formula $A$, we can define its
-associated fograph $\graphof(A)$ inductively by: $\graphof(\alpha) =
-\cdot \alpha$ (a single-vertex graph whose vertex is labelled by
-$\alpha$); $\graphof(A \cor B) = \graphof(A) + \graphof(B)$ and
-$\graphof(A \cand B) = \graphof(A) \times \graphof(B)$.
-\todo{make look nice, use array}
+associated fograph $\graphof(A)$ inductively by: 
+\begin{equation*}
+  \begin{array}{l}
+    \graphof{\alpha} = \cdot \alpha (\text{single-vertex graph whose vertex is 
+    labelled by } \alpha); \\[.5ex]
+    \graphof{A \cor B} = \graphof{A} + \graphof{B};
+    \graphof{A \cand B} = \graphof{A} \times \graphof{B}; \\[.5ex]
+    \graphof{\forall x . A} = \cdot x + \graphof{A};
+    \graphof{\exists x . A} = \cdot x \times \graphof{A}.
+  \end{array}
+\end{equation*}
+\todo{make look nice, use array} \juihsuan{done}
 
@@
 \todo{def $\fequ$}
+
+We define a congruence relation on formulas by the following equations:
+\begin{equation*}
+  \begin{array}{cc}
+    A \vlan B \fequ B \vlan A & \forall x . (A \vlor B) \fequ (\forall x . A)
+    \vlor B \\
+    A \vlor B \fequ B \vlor A & \exists x . (A \vlan B) \fequ (\exists x . A)
+    \vlan B \\
+    (A \vlan B) \vlan C \fequ A \vlan (B \vlan C) & \forall x . \forall y . A
+    \fequ \forall y . \forall x . A \\
+    (A \vlor B) \vlor C \fequ A \vlor (B \vlor C) & \exists x . \exists y . A
+    \fequ \exists y . \exists x . A \\
+  \end{array}
+\end{equation*}
 
@@
 Two atoms are \bfit{pre-dual} if their predicate symbols are dual
-(e.g. $pxy$ and $\overline{p}yz$) and two literals are \bfit{pre-dual} if their
+(e.g. $p(x, y)$ and $\dual{p}(y, z)$) and two literals are \bfit{pre-dual} if their
 labels (atoms) are pre-dual. A \bfit{linked fograph} is a coloured fograph such
@@
 
-Let $G$ be a linked fograph. The set of links can be seen as a unification problem
-by identifying dual predicate symbols. A \bfit{dualizer} of $G$ is an assignment
-unifying all the links of $G$. Since a first-order unification problem is either
+Let $\gG$ be a linked fograph. The set of links can be seen as a unification problem
+by identifying dual predicate symbols. A \bfit{dualizer} of $\gG$ is an assignment
+unifying all the links of $\gG$. Since a first-order unification problem is either
 solvable or has a most general unifier, we can define the notion of \bfit{most
@@
 general dualizer assigns to $x$ a term containing $y$. A \bfit{leap} is either a
-link or a dependency. The \bfit{leap graph} $\LG_G$ of $G$ is the undirected graph $(V_G,
-L_G)$ where $L_G$ is the set of leaps of $G$. A set $W \subseteq V_G$ induces a
-\bfit{bimatching} in $G$ if $W$ induces a matching in $G$ and in the leap graph
-$\LG_G$ as well.
-
-\todo{define matching}
+link or a dependency. The \bfit{leap graph} $\lgG$ of $\gG$ is the undirected
+graph $(\vG, \lpG)$ where $\lpG$ is the set of leaps of $\gG$. A set $W
+\subseteq \vG$ induces a
+\bfit{bimatching} in $\gG$ if $W$ induces a matching in $\gG$ and in the leap graph
+$\lgG$ as well.
+
+\todo{define matching} \juihsuan{done in the cograph part}
 

### 2021-01-10 main.tex
beginning of DI

--- 2021-01-10 main.tex
@@
 
+\newcommand\aiD {\mathsf{ai}}
+\newcommand\faD {\forall}
+\newcommand\exD {\exists}
+\newcommand\tttD {\ttt}
+\renewcommand\wD {\mathsf{w}}
+\renewcommand\cD {\mathsf{c}}
+\renewcommand\acD {\mathsf{ac}}
+\newcommand\mfaD {\mathsf{m_\forall}}
+\newcommand\mexD {\mathsf{m_\exists}}
+
+\newcommand{\cons}[1]{\{#1\}}
+\newcommand{\Scons}[1]{S\cons{#1}}
+\newcommand{\conhole}{\cons{~}}
+\newcommand{\Sconhole}{S\conhole}
+
 % ** SYMBOLS **
@@
 \newcommand{\compl}[1]{#1^\complement}
-\newcommand{\sublist}[1]{\set{#1}}
-\newcommand{\subst}[2]{#1\mathord{\scriptstyle\mapsto} #2}
+%\newcommand{\sublist}[1]{\set{#1}}
+%\newcommand{\subst}[2]{#1\mathord{\scriptstyle\mapsto} #2}
+\newcommand{\sublist}[1]{[#1]}
+\newcommand{\subst}[2]{#1/#2}
 \newcommand{\ssubst}[2]{\sublist{\subst{#1}{#2}}}
@@
 notation of negation for atoms and formulas. We may also need to precise that each
-predicate symbol $p$ has a dual $\dual{p}$.}
+predicate symbol $p$ has a dual $\dual{p}$.}\lutz{we either have to say $\dual{\dual a} = a$ or $\dual{\dual p} = p$. I prefer the first.}
 
@@
 
+For a proof we refer to reader to any standard textbook, e.g.~\cite{TS:00}.
+
 The linear fragment of $\FOLK$, i.e., the fragment
@@
   That  $\graphof A$ is a logical cograph follows immediately from the definition and Theorem~\ref{thm:cograph}. 
-  \todo{}\lutz{maybe mention also fn 2-5 in arxiv-paper}
+  \todo{}\lutz{maybe mention also fn 2-5 in Dominic's arxiv-paper}
 \end{proof}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\begin{figure}
+  \begin{center}
+    \framebox{%
+      $
+      \begin{array}{@{}c@{}}
+        \dbox{%
+          $
+          \begin{array}{c}
+            \vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}
+            \qquad
+            \vlinf{\aiD}{}{\Scons{a\vlor\cneg a}}{\Scons\ttt}
+            \qquad
+            \vlinf{\tttD}{}{\Scons{A\vlan\ttt}}{\Scons A}
+            \\ \\[-1ex]
+            \vlinf{\sw}{}{\Scons{(A\vlan B)\vlor C}}{\Scons{A\vlan (B\vlor C)}}
+            \qquad
+            \vlinf{\mix}{}{\Scons{A\vlor B}}{\Scons{A\vlan B}}            
+            \\ \\[-1ex]
+            \vlinf{\exD}{}{\Scons{\exists x.A}}{\Scons{A\ssubst x t}}
+            \qquad
+            \vlinf{\fequ}{\text{(where $A\fequ B$)}}{\Scons{A}}{\Scons{B}}
+          \end{array}
+          $
+        }
+        \\ \\[-1ex]
+        \vlinf{\mfaD}{}{\Scons{\forall x.(A\vlor B)}}{\Scons{(\forall x.A)\vlor(\forall x.B)}}
+        \qquad
+        \vlinf{\mexD}{}{\Scons{\exists x.(A\vlor B)}}{\Scons{(\exists x.A)\vlor(\exists x.B)}}        
+        \\ \\[-1ex]
+        \vlinf{\me}{}{\Scons{(A\vlor B)\vlan(C\vlor D)}}{\Scons{(A\vlan C)\vlor(B\vlan D)}}
+        \\ \\[-1ex]
+        \vlinf{\wD}{}{\Scons{A\vlor B}}{\Scons{A}}
+        \qquad
+        \vlinf{\acD}{}{\Scons{a}}{\Scons{a\vlor a}}
+      \end{array}
+      $
+    }
+  \end{center}
+  \caption{Deep inference systems $\FOKS$ (all rules) and $\FOMLS$ (rules in the dashed box)}
+  \label{fig:KS1}
+\end{figure}
+
+Contrary to standard proof formalisms, like sequent calculi or
+tableaux, where inference rules decompose the principal formula along
+its root connective, can \emph{deep inference rules} be applied like
+rewriting rules inside any (positve) formula or sequent
+\bfit{context}, which is denoted as $\Sconhole$, and which is a
+formula (resp.~sequent) with exactly one occurrence of the \bfit{hole}
+$\conhole$ in the position of an atom. Then $\Scons A$ is the result
+of replacing the hole $\conhole$ in $\Sconhole$ with $A$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Main Results}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Translating between $\FOLK$ and $\FOKS$}
 
-\subsection{The Linear Variants $\FOMLL$ and $\FOMLS$}
+\subsection{The Linear Fragments $\FOMLL$ and $\FOMLS$}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Fonets and Linear Proofs}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Skew Bifibrations and Resource Management}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Summary and Proofs of Main Results}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-01-10 main.tex
comments

@@
 \end{equation*}
-\todo{make look nice, use array} \juihsuan{done}
+\todo{make look nice, use array} \juihsuan{done}\lutz{use the single macro (see above), so that we can change the notation later if we need to (and make the array with two columns)}
 
@@
 
-\todo{define matching} \juihsuan{done in the cograph part}
+\todo{define matching} \juihsuan{done in the cograph part}\lutz{no, it should be here}
 

### 2021-01-10 main.tex
comments

@@
   \dual{\dual p(t_1,\ldots,t_n)} = p(t_1,\ldots,t_n) \\[.5ex]
-  \dual{A \vlan B} = \dual{A} \ \vlor \ \dual{B} &
-  \dual{\exists x.A} = \forall x.\dual{A} \\[.5ex]
+  \dual{\dual a} = a & \dual{\exists x.A} = \forall x.\dual{A} \\[.5ex]
+  \dual{A \vlan B} = \dual{A} \ \vlor \ \dual{B} & \dual{\forall x.A} = \exists x.\dual{A} 
+  \\[.5ex]
   \dual{A \vlor B} = \dual{A} \ \vlan \ \dual{B} &  
-  \dual{\forall x.A} = \exists x.\dual{A} 
   \end{array}
@@
 predicate symbol $p$ has a dual $\dual{p}$.}\lutz{we either have to say $\dual{\dual a} = a$ or $\dual{\dual p} = p$. I prefer the first.}
+\juihsuan{okay I see. I didn't realize that the negation is regarded as a
+connective for predicate symbols. The notation got me confused since $\dual{p}$
+is also a predicate symbol.}
 
@@
 In a graph $\gG$, the \bfit{neighbourhood} $N(v)$ of a vertex $v \in\vG$ is defined as
-the set $\set{w \mid vw \in\eG}$. A set $W \subseteq \vG$ induces a \bfit{matching} in
-$\gG$ if for all $w \in W$, $N(w) \cap W$ is a singleton.
-A \bfit{module} is a set $M \subseteq \vG$ such that $N(v) \ M = N(w) \ M$
+the set $\set{w \mid vw \in\eG}$. A \bfit{module} is a set $M \subseteq \vG$ such that $N(v) \ M = N(w) \ M$
 for all $v, w \in M$. A module $M$ is \bfit{strong} if for every
@@
 \begin{equation*}
-  \begin{array}{l}
-    \graphof{\alpha} = \cdot \alpha (\text{single-vertex graph whose vertex is 
-    labelled by } \alpha); \\[.5ex]
-    \graphof{A \cor B} = \graphof{A} + \graphof{B};
-    \graphof{A \cand B} = \graphof{A} \times \graphof{B}; \\[.5ex]
-    \graphof{\forall x . A} = \cdot x + \graphof{A};
-    \graphof{\exists x . A} = \cdot x \times \graphof{A}.
+  \begin{array}{cc}
+    \graphof{\alpha} = \single \alpha & 
+    \graphof{\forall x . A} = \single x + \graphof{A} \\[.5ex]
+    \graphof{A \cor B} = \graphof{A} + \graphof{B} &
+    \graphof{\exists x . A} = \single x \times \graphof{A} \\[.5ex]
+    \graphof{A \cand B} = \graphof{A} \times \graphof{B} &
+
   \end{array}
 \end{equation*}
-\todo{make look nice, use array} \juihsuan{done}\lutz{use the single macro (see above), so that we can change the notation later if we need to (and make the array with two columns)}
+where $\single \alpha$ (resp. $\single x$) is a single-vertex graph whose vertex is 
+    labelled by $\alpha$ (resp. $x$).
+\todo{make look nice, use array} \juihsuan{done}\lutz{use the single macro (see
+above), so that we can change the notation later if we need to (and make the
+array with two columns)} \juihsuan{fixed}
 
@@
 solvable or has a most general unifier, we can define the notion of \bfit{most
-general dualizer}. A \bfit{dependency} is a pair $(\cdot x, \cdot y)$ of an
-existential binder $\cdot x$ and a universal binder $\cdot y$ such that the most
+general dualizer}. A \bfit{dependency} is a pair $(\single x, \single y)$ of an
+existential binder $\single x$ and a universal binder $\single y$ such that the most
 general dualizer assigns to $x$ a term containing $y$. A \bfit{leap} is either a
 link or a dependency. The \bfit{leap graph} $\lgG$ of $\gG$ is the undirected
-graph $(\vG, \lpG)$ where $\lpG$ is the set of leaps of $\gG$. A set $W
-\subseteq \vG$ induces a
-\bfit{bimatching} in $\gG$ if $W$ induces a matching in $\gG$ and in the leap graph
+graph $(\vG, \lpG)$ where $\lpG$ is the set of leaps of $\gG$. A set $W \subseteq \vG$ induces a \bfit{matching} in
+$\gG$ if for all $w \in W$, $N(w) \cap W$ is a singleton, and induces a
+\bfit{bimatching} in $\gG$ if it induces a matching in $\gG$ and in the leap graph
 $\lgG$ as well.
@@
 \todo{define matching} \juihsuan{done in the cograph part}\lutz{no, it should be here}
+\juihsuan{fixed}
 
@@
 combinatorial proof} of a formula $A$ is a combinatorial proof of its graph
-$\graphof(A)$.
+$\graphof{A}$.
 \end{definition}

### 2021-01-11 main.tex
DI done

@@
 
+Figure~\ref{fig:KS1} shows the inference rule for the deep inference
+system~$\FOKS$ that we are using this paper. It is a slight variation
+of the systems presented by Br\"unnler~\cite{brunnler:phd} and
+Ralph~\cite{ralph:phd} in their PhD-theses. The main differences being
+that we (i) the explicit presence of the $\mixr$-rule, (ii) a
+different choice of how the formula equivalence $\fequ$ is defined,
+and (iii) an explicit rule for the equivalence.
+
+We consider here only the cut-free fragment, as cut-elimination for
+deep inference systems has already been discussed
+elsewhere~\cite{brunnler:,alertubella:}.\footnote{In the deep
+inference literature, the cut-free fragment is also called the
+\emph{down-fragment}. But as we do not discuss the \emph{up-fragment}
+here, we omit the down-arrows $\downarrow$ in the rule names.}
+
+As with the sequent system $\FOLK$, we also need for $\FOKS$ the
+\emph{linear fragment}, that we call here $\FOMLS$, and that is shown
+in Figure~\ref{fig:KS1} in the dashed box.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Main Results}
+
+We are now ready to see the main results of this paper.
 

### 2021-01-11 main.tex
small change
Add missing references

@@
 For a formula $A$, we can define its
-associated fograph $\graphof(A)$ inductively by: 
+associated fograph $\graphof{A}$ inductively by:
 \begin{equation*}
@@
   \todo{}
+  By a straightforward induction on $A$.
 \end{proof}
@@
 deep inference systems has already been discussed
-elsewhere~\cite{brunnler:,alertubella:}.\footnote{In the deep
+elsewhere~\cite{brunnler:06:herbrand,alertubella:guglielmi:18}.
+\juihsuan{references added. Please check if they are the right ones.}
+\footnote{In the deep
 inference literature, the cut-free fragment is also called the

### 2021-01-11 main.tex
Make some small changes

@@
 that has been made in proof theory in general and in the area of
-automated and interactive theorem provers in particular\cite{paulson:isabelle}\todo{find references}, we still have
+automated and interactive theorem provers in
+particular\cite{DSAV:15lean,paulson:isabelle}\todo{find
+references}\juihsuan{done}, we still have
 no satisfactory notion of proof identity for first-order logic. In
@@
 In this paper we use the sequent calculus $\FOLK$, shown in
-Figure~\ref{fig:LK1}, which is a one-sided variant of Gentzen's
+Figure~\ref{fig:LK1}, which is an one-sided variant of Gentzen's
 original calculus~\cite{gentzen:35:I} for first-order logic. To
@@
 A \bfit{directed graph homomorphism}
-$\phi\colon\tuple{\vG,\eG}\to\tuple{\vH,\eH}$ is function $\phi\colon\vG\to\vH$ such that if
+$\phi\colon\tuple{\vG,\eG}\to\tuple{\vH,\eH}$ is a function $\phi\colon\vG\to\vH$ such that if
 $\pair{v,w}\in\eG$ then $\pair{\phi(v),\phi(w)}\in\eH$.
@@
 In a graph $\gG$, the \bfit{neighbourhood} $N(v)$ of a vertex $v \in\vG$ is defined as
-the set $\set{w \mid vw \in\eG}$. A \bfit{module} is a set $M \subseteq \vG$ such that $N(v) \ M = N(w) \ M$
+the set $\set{w \mid vw \in\eG}$. A \bfit{module} is a set $M \subseteq \vG$
+such that $N(v) \setminus M = N(w) \setminus M$
 for all $v, w \in M$. A module $M$ is \bfit{strong} if for every
@@
   That $\graphof A$ is a logical cograph follows immediately from the definition and Theorem~\ref{thm:cograph}.
+  The fact that every binder of $\graphof A$ is legal can be proved by
+structural induction on $A$:
+  \begin{itemize}
+    \item Trivial if $A$ is an atom.
+    \item The induction step uses the following fact:
+	  if $M$ is a module of $\gG$ and $M' \subseteq M$, then $M'$ is a
+          module of $\gG$ if and only if it is a module of $\gG[X]$.
+  \end{itemize}
   \todo{}\lutz{maybe mention also fn 2-5 in Dominic's arxiv-paper}
 \end{proof}
+\juihsuan{I'm still looking for a simple proof}
+\footnote{Note that $\graphof A$ is not necessarily a fograph if $A$ is not
+rectified. If $A = (\forall x. p(x)) \vlor (\forall x. q(x))$, then $\graphof A = \single x \quad
+\single p(x) \quad \single x \quad \single q(x)$, the scope of each $x$-binder
+contains all the vertices, in particular, the two $x$-binders.}
 
@@
 
-Figure~\ref{fig:KS1} shows the inference rule for the deep inference
-system~$\FOKS$ that we are using this paper. It is a slight variation
+Figure~\ref{fig:KS1} shows the inference rules for the deep inference
+system~$\FOKS$ that we are using in this paper. It is a slight variation
 of the systems presented by Br\"unnler~\cite{brunnler:phd} and
 Ralph~\cite{ralph:phd} in their PhD-theses. The main differences being
-that we (i) the explicit presence of the $\mixr$-rule, (ii) a
+that we have (i) the explicit presence of the $\mixr$-rule, (ii) a
 different choice of how the formula equivalence $\fequ$ is defined,

### 2021-01-11 main.tex
Fix some typos

@@
 The main reason for this problem is that formal proofs, as they are
-usually studied in logic, are in inextricably tied to the syntactic
+usually studied in logic, are inextricably tied to the syntactic
 (inference rule based) proof system in which they are carried out. And
 it is difficult to compare two proofs that are produced within two
-different sytactic proof systems, based on different sets of inference rules.
+different syntactic proof systems, based on different sets of inference rules.
 \lutz{an example here?}
@@
 the syntax of the inference rules used in the proof and consider the
-proof as a combinatorial object, more precisely as a special kind
+proof as a combinatorial object, more precisely as a special kind of
 homomorphism between two graphs obeying certain properties.
@@
 of a spectrum: whereas deep inference allows for a very fine
-franularity of inference rules---one inference rule in a standard
+granularity of inference rules---one inference rule in a standard
 formalism, like sequent calculus or semantic tableaux, is usually
 simulated by a sequence of different deep inference rules---have
-combinatorial proofs comletely abolished the concept of inference
+combinatorial proofs completely abolished the concept of inference
 rule. Nonetheless, there is a close relationship between the two,
@@
 a countable set $\FUN=\set{f,g,\ldots}$ of function symbols, and a
-counrable set $\PRED=\set{p,q,\ldots}$ of predicate symbols. Each function symbol and
+countable set $\PRED=\set{p,q,\ldots}$ of predicate symbols. Each function symbol and
 each predicate symbol has a finite arity. The grammars below generate
@@
 \footnote{Note that $\graphof A$ is not necessarily a fograph if $A$ is not
-rectified. If $A = (\forall x. p(x)) \vlor (\forall x. q(x))$, then $\graphof A = \single x \quad
-\single p(x) \quad \single x \quad \single q(x)$, the scope of each $x$-binder
-contains all the vertices, in particular, the two $x$-binders.}
+rectified. If $A = (\forall x. p(x)) \vlor (\forall x. q(x))$, then $\graphof A
+= \single x \ \single p(x) \ \single x \ \single q(x)$, the scope of each
+$x$-binder contains all the vertices, in particular, the two $x$-binders.}
 
@@
   \begin{array}{cc}
-    A \vlan B \fequ B \vlan A & \forall x . (A \vlor B) \fequ (\forall x . A)
-    \vlor B \\
-    A \vlor B \fequ B \vlor A & \exists x . (A \vlan B) \fequ (\exists x . A)
-    \vlan B \\
-    (A \vlan B) \vlan C \fequ A \vlan (B \vlan C) & \forall x . \forall y . A
-    \fequ \forall y . \forall x . A \\
-    (A \vlor B) \vlor C \fequ A \vlor (B \vlor C) & \exists x . \exists y . A
-    \fequ \exists y . \exists x . A \\
+    A \vlan B \fequ B \vlan A & A \vlor B \fequ B \vlor A \\
+    (A \vlan B) \vlan C \fequ A \vlan (B \vlan C) &
+    (A \vlor B) \vlor C \fequ A \vlor (B \vlor C) \\
+    \forall x . \forall y . A \fequ \forall y . \forall x . A &
+    \exists x . \exists y . A \fequ \exists y . \exists x . A \\
+    \forall x . (A \vlor B) \fequ (\forall x . A) \vlor B &
+    \exists x . (A \vlan B) \fequ (\exists x . A) \vlan B
   \end{array}
 \end{equation*}
+where $x \notin fv(B)$ in the last two equations.
 
@@
 unifying all the links of $\gG$. Since a first-order unification problem is either
-solvable or has a most general unifier, we can define the notion of \bfit{most
+unsolvable or has a most general unifier, we can define the notion of \bfit{most
 general dualizer}. A \bfit{dependency} is a pair $(\single x, \single y)$ of an
@@
 
-A graph homomorphism $f: (V, E) \rightarrow (V', E')$ is a \bfit{fibration} if
-for all $v \in V$ and $wf(v) \in E'$, there exists a unique $\tilde{w}$ such
-that $\tilde{w}v \in E$ and $f(\tilde{w}) = w$, and is a \bfit{skew fibration}
-if for all $v \in V$ and $wf(v) \in E'$ there exists $\tilde{w}$ such that
-$\tilde{w}v \in E$ and $f(\tilde{w})w \notin E'$. A \bfit{fograph homomorphism}
+A graph homomorphism $f: (\vG, \eG) \rightarrow (\vH, \eH)$ is a \bfit{fibration} if
+for all $v \in \vG$ and $wf(v) \in \eH$, there exists a unique $\tilde{w} \in
+\vG$ such that $\tilde{w}v \in \eG$ and $f(\tilde{w}) = w$, and is a \bfit{skew fibration}
+if for all $v \in \vG$ and $wf(v) \in \eH$ there exists $\tilde{w} \in \vG$ such that
+$\tilde{w}v \in \eG$ and $f(\tilde{w})w \notin \eH$. A \bfit{fograph homomorphism}
 is a graph homomorphism between the underlying graphs of the fographs
-considered. A fograph homomorphism $f : G \rightarrow G'$ is
-\bfit{label-preserving} if forall $v \in V_G, label(v) = label(f(v))$, and is
-\bfit{existential-preserving} if for all existental binder $b$ in $G$, the
-vertex $f(b)$ is an existential binder in $G'$.
+considered. A fograph homomorphism $f : \gG \rightarrow \gH$ is
+\bfit{label-preserving} if for all $v \in \vG, label(v) = label(f(v))$, and is
+\bfit{existential-preserving} if for all existental binder $b$ in $\gG$, the
+vertex $f(b)$ is an existential binder in $\gH$.
 
@@
 A \bfit{first-order combinatorial proof} of a fograph $G$ is a skew
-bifibration $f: N \rightarrow G$ where $N$ is a fonet. A \bfit{first-order
+bifibration $f: N \rightarrow \gG$ where $N$ is a fonet. A \bfit{first-order
 combinatorial proof} of a formula $A$ is a combinatorial proof of its graph

### 2021-01-11 main.tex
decomp

--- 2021-01-11 main.tex
@@
 \newcommand{\eH}{\edges[H]}
+
+\newcommand{\sysS}{\mathsf{S}}
+\newcommand{\Deri}{\Phi}
 
@@
 \renewcommand\wD {\mathsf{w}}
+\newcommand\wlD {\mathsf{w_l}}
+\newcommand\wrD {\mathsf{w_r}}
 \renewcommand\cD {\mathsf{c}}
@@
 \begin{thm}
-  A formula $A$ is a theorem of first-order logic iff the sequent $\sqn A$ is derivable in $\FOLK$.
+  $\FOLK$ is sound and complete for first-order logic.
 \end{thm}
@@
 For a formula $A$, we can define its
-associated fograph $\graphof{A}$ inductively by:
+associated fograph $\graphof(A)$ inductively by: 
 \begin{equation*}
@@
   \todo{}
-  By a straightforward induction on $A$.
 \end{proof}
@@
         \\ \\[-1ex]
-        \vlinf{\wD}{}{\Scons{A\vlor B}}{\Scons{A}}
+        \vlinf{\wrD}{}{\Scons{A\vlor B}}{\Scons{A}}
+        \qquad
+        \vlinf{\wlD}{}{\Scons{B\vlor A}}{\Scons{A}}
         \qquad
@@
 deep inference systems has already been discussed
-elsewhere~\cite{brunnler:06:herbrand,alertubella:guglielmi:18}.
-\juihsuan{references added. Please check if they are the right ones.}
-\footnote{In the deep
+elsewhere~\cite{brunnler:,alertubella:}.\footnote{In the deep
 inference literature, the cut-free fragment is also called the
@@
 
+We write $\vlder{\sysS}{\Deri}{A}{B}$ to denote a derivation $\Deri$
+from $B$ to $A$ using the rules from system $\sysS$. A formula $A$ is
+\bfit{provable} in a system $\sysS$ if there is a derivation in
+$\sysS$ from $\ttt$ to $A$.
+
+In the course of this paper we are also going to make use of the
+general (non-atomic) version of the contraction rule:
+\begin{equation*}
+  \vlinf{\cD}{}{\Scons{A}}{\Scons{A\vlor A}}  
+\end{equation*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We are now ready to see the main results of this paper.
+We are now ready to see the main results of this paper. We only state
+them here and give the proofs in the later sections of the paper. The
+first one is routine and expected, but needs to be proved nonetheless:
+
+\begin{thm}\label{thm:KS1}
+  $\FOKS$ is sound and complete for first-order logic.
+\end{thm}
+
+Our second results is more surprising, as it is a very strong
+decomposition result for first order logic.
+
+\begin{thm}\label{thm:decomposition}
+  For every derivation $\vlder{\FOKS}{\Deri}{A}{\ttt}$ there are formulas $A_1,\ldots,A_5$, such that there is a derivation:
+  \begin{equation*}
+    \vlderivation{
+      \vlde{\set{\wlD,\wrD}}{}{A}{
+        \vlde{\set{\acD}}{}{A_1}{
+          \vlde{\set{\me,\mfaD,\mexD,\fequ}}{}{A_2}{
+            \vlde{\set{\exD}}{}{A_3}{
+              \vlde{\set{\sw,\mix,\fequ}}{}{A_4}{
+                \vlde{\set{\faD,\aiD,\tttD}}{}{A_5}{
+                  \vlhy{\ttt}}}}}}}}
+  \end{equation*}
+\end{thm}
+
+This theorem is stronger than the existing decompositions for
+first-order logic, which either separated only atomic contraction and
+atomic weakening~\cite{brunnler:phd} or only
+contraction~\cite{ralph:phd} or only the quantifiers in form of a
+Herbrand theorem~\cite{brunnler:06:locality,ralph:phd}.
+
+There is a weaker version of Theorem~\ref{thm:decomposition} that will
+also be useful:
+
+\begin{thm}\label{thm:decompositionA}
+  For every derivation $\vlder{\FOKS}{\Deri}{A}{\ttt}$ there is a formula $A_1$, such that there is a derivation:
+  \begin{equation*}
+    \vlderivation{
+      \vlde{\set{\wlD,\wrD,\cD}}{}{A}{
+        \vlde{\FOMLS}{}{A_1}{
+          \vlhy{\ttt}}}}}}}}
+  \end{equation*}
+\end{thm}
 

### 2021-01-12 main.tex
decomp+merge
tiny changes

@@
 $\gG=\tuple{\vG,\eG}$ if $\vH\subseteq\vG$ and $\eH\subseteq\eG$. It
-is \bfit{induced} if $v,w\in\vH$ and $vw\in\eG$ implies $vw\in\eH$.  A
-graph is \bfit{$\gH$-free} if it does not contain $\gH$ as an induced
+is \bfit{induced} if $v,w\in\vH$ and $vw\in\eG$ implies $vw\in\eH$. An induced
+subgraph of $\gG=\tuple{\vG,\eG}$ is uniquely determined by its set of vertices
+$V$ and we denote it by $\gG[V]$.
+A graph is \bfit{$\gH$-free} if it does not contain $\gH$ as an induced
 subgraph.  The graph $\Pfour$ is the (undirected) graph
@@
 
-Our second results is more surprising, as it is a very strong
+Our second result is more surprising, as it is a very strong
 decomposition result for first order logic.
@@
         \vlde{\FOMLS}{}{A_1}{
-          \vlhy{\ttt}}}}}}}}
+          \vlhy{\ttt}}}}
   \end{equation*}

### 2021-01-12 main.tex
sec.VI

@@
 
+\newcommand{\rectif}[1]{\widehat{#1}}
 \newcommand{\graphof}[1]{\llbracket#1\rrbracket}
@@
 
-A formula is
-\bfit{rectified} if all bound variables are distinct from one another and from
-all free variables. As every formula has a logically equivalent
-rectified form, we will restrict most of the results in this paper to rectified formulas.
+A formula is \bfit{rectified} if all bound variables are distinct from
+one another and from all free variables. Every formula can be
+transformed into a logically equivalent rectified form, by simply
+renaming the bound variables. If we consider formulas equivalent
+modulo $\alpha$-conversion (renaming of bound variables), then the
+rectified form of a formula $A$ is uniquely defined, and we denote it
+by $\rectif A$.
 
@@
 \begin{definition}
-A \bfit{first-order combinatorial proof} of a fograph $G$ is a skew
+A \bfit{first-order combinatorial proof} (\bfit{FOCP}) of a fograph $G$ is a skew
 bifibration $f: N \rightarrow \gG$ where $N$ is a fonet. A \bfit{first-order
@@
 \end{definition}
+
+\begin{thm}[\cite{hughes:fopws}]
+  \label{thm:FOCP}
+  FOCPs are sound and complete for first-order logic.
+\end{thm}
 
@@
 
+Let us now establish the connection between derivations in $\FOKS$ and
+combinatorial proofs.
+
+\begin{thm}\label{thm:CP-DI}
+  Let $A$ be a rectified formula, and assume we have a combinatorial proof $\phi\colon\gC\to\graphof A$. Then there is a derivation
+  \begin{equation}
+    \label{eq:decom}
+    \vlderivation{
+      \vlde{\set{\wlD,\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{
+        \vlde{\FOMLS}{\Deri_1}{A'}{
+          \vlhy{\ttt}}}}
+  \end{equation}
+  for some $A'$ such that $\graphof{\rectif{A'}}=\gC$. Conversely,
+  whenever we have a derivation as in~\eqref{eq:decom} above, then
+  there is a combinatiorial proof $\phi\colon\gC\to\graphof A$ such that $\gC=\graphof{\rectif{A'}}$.
+\end{thm}
+
+Furthermore, in the proof of Theorem~\ref{thm:CP-DI}, we will see that
+(i) the links in the fonet $\gC$ correspond precicely to the pairs of
+atoms that meet in the instances of the $\aiD$-rule in the derivation
+$\Deri_1$, and (ii) the ''flow-graph'' of $\Deri_2$ that traces the
+quatifier- and atom-occurrences in the derivation corresponds exactly
+to the vertex-mapping induced by $\phi$.
+
+Thus, combinatorial proofs are closely related to derivations of the
+form~\eqref{eq:decom}, and since by Theorem~\ref{thm:decomposition}
+every derivation can be transformed into that form, we can say that
+combinatorial proofs form a canononical proof representation for first
+order logic, similarly to what proof nets are for linear
+logic~\cite{girard:96:PN}.
+
+Finally, Theorems~\ref{thm:KS1}, \ref{thm:decomposition}
+and~\ref{thm:CP-DI} imply Theorem~\ref{thm:FOCP}, which means that we
+have here and alterantive proof of the soundness and competeness of
+first-order combinatorial proofs which is simpler than the one given
+in~\cite{hughes:fopws}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+In this section we prove Theorems
 \subsection{The Linear Fragments $\FOMLL$ and $\FOMLS$}

### 2021-01-12 main.tex
tiny changes

--- 2021-01-12 main.tex
@@
 
-We define a congruence relation on formulas by the following equations:
+We define a congruence relation $\fequ$ on formulas by the following equations:
 \begin{equation*}
@@
 where $x \notin fv(B)$ in the last two equations.
-
+Two formulas $A$ and $B$ are \bfit{equivalent} if $A \fequ B$. The following
+theorem shows that the set of fographs can been seen as the quotient
+$\FORM / \fequ$.
 \begin{thm}

### 2021-01-12 main.tex
typos and tiny changes

@@
 \newcommand{\gH}{\graph{H}}
+\newcommand{\gN}{\graph{N}}
 
@@
 logic. Since its formalisation by Frege~\cite{frege:79} it has seen a
-growing usage in many fields of mathematics and computer sience. Since
+growing usage in many fields of mathematics and computer science. Since
 the development of proof theory by Hilbert~\cite{hilbert:22},
@@
 In general, a \emph{decomposition theorem} provides normal forms of
-proofs, separating subsets of infernence rules of a proof system. A
-prominent example of a decomposion theorem is Herbrand's
+proofs, separating subsets of inference rules of a proof system. A
+prominent example of a decomposition theorem is Herbrand's
 theorem~\cite{herbrand:phd}, which allows a separation between the
-proposotional part and the quantifier part in a first-order
+propositional part and the quantifier part in a first-order
 proof~\cite{gentzen:35:II,brunnler:06:herbrand}. Through the advent of
@@
 
-Combinatorial proofs and deep infernence can be seen as opposite ends
+Combinatorial proofs and deep inference can be seen as opposite ends
 of a spectrum: whereas deep inference allows for a very fine
@@
 \bfit{label-preserving} if for all $v \in \vG, label(v) = label(f(v))$, and is
-\bfit{existential-preserving} if for all existental binder $b$ in $\gG$, the
+\bfit{existential-preserving} if for all existential binder $b$ in $\gG$, the
 vertex $f(b)$ is an existential binder in $\gH$.
@@
 \begin{definition}
-A \bfit{first-order combinatorial proof} (\bfit{FOCP}) of a fograph $G$ is a skew
-bifibration $f: N \rightarrow \gG$ where $N$ is a fonet. A \bfit{first-order
+A \bfit{first-order combinatorial proof} (\bfit{FOCP}) of a fograph $\gG$ is a skew
+bifibration $f: \gN \rightarrow \gG$ where $\gN$ is a fonet. A \bfit{first-order
 combinatorial proof} of a formula $A$ is a combinatorial proof of its graph
@@
 its root connective, can \emph{deep inference rules} be applied like
-rewriting rules inside any (positve) formula or sequent
+rewriting rules inside any (positive) formula or sequent
 \bfit{context}, which is denoted as $\Sconhole$, and which is a
@@
   whenever we have a derivation as in~\eqref{eq:decom} above, then
-  there is a combinatiorial proof $\phi\colon\gC\to\graphof A$ such that $\gC=\graphof{\rectif{A'}}$.
+  there is a combinatorial proof $\phi\colon\gC\to\graphof A$ such that $\gC=\graphof{\rectif{A'}}$.
 \end{thm}
@@
 Furthermore, in the proof of Theorem~\ref{thm:CP-DI}, we will see that
-(i) the links in the fonet $\gC$ correspond precicely to the pairs of
+(i) the links in the fonet $\gC$ correspond precisely to the pairs of
 atoms that meet in the instances of the $\aiD$-rule in the derivation
 $\Deri_1$, and (ii) the ''flow-graph'' of $\Deri_2$ that traces the
-quatifier- and atom-occurrences in the derivation corresponds exactly
+quantifier- and atom-occurrences in the derivation corresponds exactly
 to the vertex-mapping induced by $\phi$.
@@
 every derivation can be transformed into that form, we can say that
-combinatorial proofs form a canononical proof representation for first
+combinatorial proofs form a canonical proof representation for first
 order logic, similarly to what proof nets are for linear
@@
 and~\ref{thm:CP-DI} imply Theorem~\ref{thm:FOCP}, which means that we
-have here and alterantive proof of the soundness and competeness of
+have here an alternative proof of the soundness and completeness of
 first-order combinatorial proofs which is simpler than the one given
@@
 
-\subsection{Contraction and Weakining}
+\subsection{Contraction and Weakening}
 

### 2021-01-12 main.tex
sec.VII.A

--- 2021-01-12 main.tex
@@
 \newcommand*{\FOLK}{\mathsf{LK1}}
+\newcommand*{\FOLKcut}{\FOLK\mathord+\cut}
 \newcommand*{\LKm}{\mathsf{LK + mix}}
 \newcommand*{\MLL}{\mathsf{MLL}}
-\newcommand*{\FOMLL}{\mathsf{MLL1^\times}} 
+\newcommand*{\FOMLL}{\mathsf{MLL1^X}} 
+\newcommand*{\FOMLLcut}{\FOMLL\mathord+\cut}
 \newcommand*{\FOMLLm}{\mathsf{MLL1+mix}}
 \newcommand*{\FOKS}{\mathsf{KS1}}
-\newcommand*{\FOMLS}{\mathsf{MLS1^\times}}
+\newcommand*{\FOMLS}{\mathsf{MLS1^X}}
 
@@
 
+\newcommand{\rr}{\mathsf{r}}
 \newcommand{\ax}{\mathsf{ax}}
@@
 
+In this paper we make also use of the cut elimination theorem. The \bfit{cut} rule is
+\begin{equation}
+  \vliinf{\cutr}{}{\sqn{\Gamma,\Delta}}{\sqn{\Gamma,A}}{\sqn{\dual A,\Delta}}
+\end{equation}
+
+\begin{thm}
+  \label{thm:cutelim}
+  If a sequent $\sqn\Gamma$ is provable in $\FOLKcut$ then it is also
+  provable in $\FOLK$. Furthermore, if $\sqn\Gamma$ is provable in
+  $\FOMLLcut$ then it is also provable in $\FOMLL$.
+\end{thm}
+
+As before, this is standard, see e.g.~\cite{TS:00} for a proof.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We define a congruence relation $\fequ$ on formulas by the following equations:
+We define a congruence relation on formulas by the following equations:
 \begin{equation*}
@@
 where $x \notin fv(B)$ in the last two equations.
-Two formulas $A$ and $B$ are \bfit{equivalent} if $A \fequ B$. The following
-theorem shows that the set of fographs can been seen as the quotient
-$\FORM / \fequ$.
+
 \begin{thm}
@@
 
-In this section we prove Theorems
+In this section we prove Theorems~\ref{thm:KS1},
+\ref{thm:decomposition}, and~\ref{thm:decompositionA}, mainly by
+translating derivations to and from the sequent calculus, and by rule
+permutation arguments.
+
 \subsection{The Linear Fragments $\FOMLL$ and $\FOMLS$}
+
+In this section we show the equivalence of $\FOMLL$ and $\FOMLS$.
+
+\begin{lemma}\label{lem:MLL1->MLS1}
+  If $\sqn\Gamma$ is rectified and provable in $\FOMLL$ then $\form\Gamma$ is provable in  $\FOMLS$. \todo{check: do we need rectified here?}
+\end{lemma}
+
+\begin{proof}
+  This is a straightforward induction on the proof of $\sqn\Gamma$ in
+  $\FOMLL$, making a case analysis on the bottommost rule instance. We
+  show here only the case of $\vlinf{\forall}{}{\sqn{\Delta,\forall
+      x.A}}{\sqn{\Delta,A}}$ (all other cases are simpler and have
+  been shown before, e.g.~\cite{brunnler:phd}): By induction
+  hypothesis, there is a proof of $\form\Delta\vlor A$ in $\FOMLS$. We
+  can prefix every line in that proof by $\forall x$ and then compose
+  the following derivation:
+  \begin{equation*}
+    \vlderivation{
+      \vlin{\fequ}{}{\form\Delta\vlor\forall x.A}{
+        \vlde{\FOMLS}{}{\forall x.\form\Delta\vlor A}{
+          \vlin{\forall}{}{\forall x.\ttt}{
+            \vlhy{\ttt}}}}}
+  \end{equation*}
+  where we can apply the $\fequ$-rule because $x$ is not free in $\Delta$.
+\end{proof}
+
+\begin{lemma}\label{lem:shallow}
+  Let $\vlinf{\rr}{}{\Scons B}{\Scons A}$ be an inference rule in
+  $\FOMLS$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
+\end{lemma}
+
+\begin{proof}
+  This is a straightforward exercise that we leave to the reader.
+\end{proof}
+
+\begin{lemma}\label{lem:context}
+  Let $A,B$ be formulas, and let $\Sconhole$ be a (positive)
+  context. If $\sqn{\cneg A,B}$ is provable in $\FOMLL$, then so is
+  $\sqn{\cneg{\Scons A},\Scons B}$.
+\end{lemma}
+
+\begin{proof}
+  Straightforward induction on  $\Sconhole$. (see e.g. \cite{gug:str:01})
+\end{proof}
+
+\begin{lemma}\label{lem:MLS1->MLL1}
+  If a formula $C$ is provable in $\FOMLS$ then $\sqn C$ is provable in  $\FOMLL$. \todo{check: do we need rectified here?}
+\end{lemma}
+
+\begin{proof}
+  We proceed by induction on the number of inference steps in the
+  proof of $C$ in $\FOMLS$. Consider the bottommost rule instance
+  $\vlinf{\rr}{}{\Scons B}{\Scons A}$. By induction hypothesis we have
+  a $\FOMLL$ proof of $\sqn{\Scons A}$, and by
+  Lemma~\ref{lem:context}, we have a $\FOMLL$ proof of
+  $\sqn{\cneg{\Scons A},\Scons B}$. We can compose them via $\cutr$:
+  \begin{equation*}
+    \vliinf{\cutr}{}{\sqn{\Scons B}}{\sqn{\Scons A}}{\sqn{\cneg{\Scons
+          A},\Scons B}}
+  \end{equation*}
+  and then apply Theorem~\ref{thm:cutelim}.
+\end{proof}
 

### 2021-01-12 main.tex

--- 2021-01-12 main.tex
@@
 here with $\FOMLL$ (shown in Figure~\ref{fig:LK1} in the dashed box).
+
+In this paper we make also use of the cut elimination theorem. The \bfit{cut} rule is
+\begin{equation}
+  \vliinf{\cutr}{}{\sqn{\Gamma,\Delta}}{\sqn{\Gamma,A}}{\sqn{\dual A,\Delta}}
+\end{equation}
+
+\begin{thm}
+  \label{thm:cutelim}
+  If a sequent $\sqn\Gamma$ is provable in $\FOLKcut$ then it is also
+  provable in $\FOLK$. Furthermore, if $\sqn\Gamma$ is provable in
+  $\FOMLLcut$ then it is also provable in $\FOMLL$.
+\end{thm}
+
+As before, this is standard, see e.g.~\cite{TS:00} for a proof.
 
@@
 
-In this section we prove Theorems
+In this section we prove Theorems~\ref{thm:KS1},
+\ref{thm:decomposition}, and~\ref{thm:decompositionA}, mainly by
+translating derivations to and from the sequent calculus, and by rule
+permutation arguments.
+
 \subsection{The Linear Fragments $\FOMLL$ and $\FOMLS$}
 
-\subsection{Contraction and Weakening}
+In this section we show the equivalence of $\FOMLL$ and $\FOMLS$.
+
+\begin{lemma}\label{lem:MLL1->MLS1}
+  If $\sqn\Gamma$ is rectified and provable in $\FOMLL$ then $\form\Gamma$ is provable in  $\FOMLS$. \todo{check: do we need rectified here?}
+\end{lemma}
+
+\begin{proof}
+  This is a straightforward induction on the proof of $\sqn\Gamma$ in
+  $\FOMLL$, making a case analysis on the bottommost rule instance. We
+  show here only the case of $\vlinf{\forall}{}{\sqn{\Delta,\forall
+      x.A}}{\sqn{\Delta,A}}$ (all other cases are simpler and have
+  been shown before, e.g.~\cite{brunnler:phd}): By induction
+  hypothesis, there is a proof of $\form\Delta\vlor A$ in $\FOMLS$. We
+  can prefix every line in that proof by $\forall x$ and then compose
+  the following derivation:
+  \begin{equation*}
+    \vlderivation{
+      \vlin{\fequ}{}{\form\Delta\vlor\forall x.A}{
+        \vlde{\FOMLS}{}{\forall x.\form\Delta\vlor A}{
+          \vlin{\forall}{}{\forall x.\ttt}{
+            \vlhy{\ttt}}}}}
+  \end{equation*}
+  where we can apply the $\fequ$-rule because $x$ is not free in $\Delta$.
+\end{proof}
+
+\begin{lemma}\label{lem:shallow}
+  Let $\vlinf{\rr}{}{\Scons B}{\Scons A}$ be an inference rule in
+  $\FOMLS$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
+\end{lemma}
+
+\begin{proof}
+  This is a straightforward exercise that we leave to the reader.
+\end{proof}
+
+\begin{lemma}\label{lem:context}
+  Let $A,B$ be formulas, and let $\Sconhole$ be a (positive)
+  context. If $\sqn{\cneg A,B}$ is provable in $\FOMLL$, then so is
+  $\sqn{\cneg{\Scons A},\Scons B}$.
+\end{lemma}
+
+\begin{proof}
+  Straightforward induction on  $\Sconhole$. (see e.g. \cite{gug:str:01})
+\end{proof}
+
+\begin{lemma}\label{lem:MLS1->MLL1}
+  If a formula $C$ is provable in $\FOMLS$ then $\sqn C$ is provable in  $\FOMLL$. \todo{check: do we need rectified here?}
+\end{lemma}
+
+\begin{proof}
+  We proceed by induction on the number of inference steps in the
+  proof of $C$ in $\FOMLS$. Consider the bottommost rule instance
+  $\vlinf{\rr}{}{\Scons B}{\Scons A}$. By induction hypothesis we have
+  a $\FOMLL$ proof of $\sqn{\Scons A}$, and by
+  Lemma~\ref{lem:context}, we have a $\FOMLL$ proof of
+  $\sqn{\cneg{\Scons A},\Scons B}$. We can compose them via $\cutr$:
+  \begin{equation*}
+    \vliinf{\cutr}{}{\sqn{\Scons B}}{\sqn{\Scons A}}{\sqn{\cneg{\Scons
+          A},\Scons B}}
+  \end{equation*}
+  and then apply Theorem~\ref{thm:cutelim}.
+\end{proof}
+
+\subsection{Contraction and Weakining}
 

### 2021-01-13 main.tex
references and comments
now c and w

@@
   If $\sqn\Gamma$ is rectified and provable in $\FOMLL$ then $\form\Gamma$ is provable in  $\FOMLS$. \todo{check: do we need rectified here?}
+\juihsuan{no}
 \end{lemma}
@@
 \end{lemma}
-
+\juihsuan{For this, we need the introduction rule of $\fff$ in $\FOMLL$
+(consider the $\aiD$ rule). But if we add it, we'll need the
+$\mathsf{ai}\downarrow$ rule to have Lemma \ref{lem:MLL1->MLS1}}
+\lutz{shit. so, we need another way to prove lemma~\ref{lem:MLS1->MLL1}, I'd like to avoid $\fff$-intro.}
 \begin{proof}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Contraction and Weakining}
 
+The first observation here is that Lemmas~\ref{lem:MLL1->MLS1}--\ref{lem:MLS1->MLL1} from above also hold for $\FOLK$ and $\FOKS$. We therefore immediately have:
+
+\begin{thm}\label{thm:LK1-KS1}
+  For every sequent $\Gamma$, we have that $\sqn\Gamma$ is provable in
+  $\FOLK$ if and only if $\form\Gamma$ is provable in $\FOKS$.
+\end{thm}
+
+Then Theorem~\ref{thm:KS} is an immediate consequence. Let us now
+proceed with providing further lemmas that will be needed for the
+other results.
+
+\begin{lemma}
+  \label{lem:ac}
+  The $\cD$-rule is derivable in $\set{\acD,\me,\mfaD,\mexD,\fequ}$. 
+\end{lemma}
+
+\begin{proof}
+  \todo{}
+\end{proof}
+
+\begin{lemma}
+  \label{lem:me}
+  The rules $\me,\mfaD,\mexD$ are derivable in $\set{\wlD,\wrD,\cD}$. 
+\end{lemma}
+
+\begin{proof}
+  \todo{}\lutz{also check for the need of$\fequ$}
+\end{proof}
+
+\begin{lemma}
+  Let $A$ and $B$ be formulas. Then
+  \begin{equation}
+    x
+  \end{equation}
+\end{lemma}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{A First Decomposition Theorem}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Unification Nets}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Translation between Unification Nets and $\FOMLL$}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Translation between Unification Nets and Fonets}

### 2021-01-13 main.tex
Add proofs

@@
 \lutz{shit. so, we need another way to prove lemma~\ref{lem:MLS1->MLL1}, I'd like to avoid $\fff$-intro.}
+\juihsuan{This lemma holds for all the rules except $\aiD$ (we may need to
+mention that $A \fequ B \Rightarrow \ \vdash_{\FOMLL} \dual{B}, A$). The inductive
+step for $\aiD$ in the proof of Lemma \ref{lem:MLS1->MLL1} can be solved by
+replacing $t$ with $a \vlor \dual{a}$ and the $\ttt$-rule with the $\ax$
+ rule followed by the $\vlor$ rule}
 \begin{proof}
@@
 
-Then Theorem~\ref{thm:KS} is an immediate consequence. Let us now
+Then Theorem~\ref{thm:KS1} is an immediate consequence. Let us now
 proceed with providing further lemmas that will be needed for the
@@
 \begin{proof}
+  We show that there is always a derivation
+  $$
+  \vlderivation{
+    \vlde{\sysS}{}{A}{
+      \vlhy{A \vlor A}}}
+  $$, where $\sysS = \set{\acD,\me,\mfaD,\mexD,\fequ}$, by induction on $A$:
+  \begin{itemize}
+    \item If $A = a$, then we have
+      $
+      \vlderivation{
+        \vlin{\acD}{}{a}{
+          \vlhy{a \vlor a}}}
+      $.
+    \item If $A = B \vlan C$, then we have
+      $
+      \vlderivation{
+	\vlde{\sysS}{}{B \vlan C}{
+	  \vlde{\sysS}{}{B \vlan (C \vlor C)}{
+	    \vlin{\me}{}{(B \vlor B) \vlan (C \vlor C)}{
+	      \vlhy{(B \vlan C) \vlor (B \vlan C)}}}}}
+      $.\\[.5ex]
+    \item If $A = B \vlor C$, then we have
+      $
+      \vlderivation{
+	\vlde{\sysS}{}{B \vlor C}{
+	  \vlde{\sysS}{}{B \vlor (C \vlor C)}{
+	    \vlin{\fequ}{}{(B \vlor B) \vlor (C \vlor C)}{
+	      \vlhy{(B \vlor C) \vlor (B \vlor C)}}}}}
+      $.\\[.5ex]
+    \item If $A = \exists x.A'$, then we have
+      $
+      \vlderivation{
+	\vlde{\sysS}{}{\exists x.A'}{
+	  \vlin{\mexD}{}{\exists x.(A' \vlor A')}{
+	    \vlhy{(\exists x.A') \vlor (\exists x.A')}}}}
+      $.\\[.5ex]
+    \item If $A = \forall x.A'$, then we have
+      $
+      \vlderivation{
+	\vlde{\sysS}{}{\forall x.A'}{
+	  \vlin{\mexD}{}{\forall x.(A' \vlor A')}{
+	    \vlhy{(\forall x.A') \vlor (\forall x.A')}}}}
+      $.
+  \end{itemize}
   \todo{}
+  \juihsuan{done. Maybe just keep one case.}
 \end{proof}
@@
   \todo{}\lutz{also check for the need of$\fequ$}
+
+  We have the following derivations:
+  $$
+  \vlderivation{
+    \vlin{\cD}{}{(A \vlor B) \vlan (C \vlor D)}{
+      \vlin{\wlD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((A \vlor B) \vlan (C \vlor D))}{
+	\vlin{\wlD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((A \vlor B) \vlan D))}{
+	  \vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor (B \vlan D))}{
+	    \vlin{\wrD}{}{((A \vlor B) \vlan C) \vlor (B \vlan D)}{
+	      \vlhy{(A \vlan C) \vlor (B \vlan D)}}}}}}}
+  $$.
+  $$
+  \vlderivation{
+    \vlin{\cD}{}{\exists x.(A \vlor B)}{
+      \vlin{\wlD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.(A \vlor B))}{
+	\vlin{\wrD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.B)}{
+	  \vlhy{(\exists x.A) \vlor (\exists x.B)}}}}}
+  $$.
+  $$
+  \vlderivation{
+    \vlin{\cD}{}{\forall x.(A \vlor B)}{
+      \vlin{\wlD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.(A \vlor B))}{
+	\vlin{\wrD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.B)}{
+	  \vlhy{(\forall x.A) \vlor (\forall x.B)}}}}}
+  $$.
+  \juihsuan{done. If needed, we can introduce the notion of open deduction to
+reduce the size of derivations...}
 \end{proof}

### 2021-01-13 main.tex
sec.VII and VIII

--- 2021-01-13 main.tex
@@
 \usepackage{virginialake}
+\vlstemheight=12pt
 
@@
 \newcommand{\sqn}[1]{\vdash#1}
+\newcommand{\sqns}[1]{\vdash#1\phantom{\vdash}}
 
@@
 \newcommand{\ssubst}[2]{\sublist{\subst{#1}{#2}}}
+\newcommand{\substof}[1]{\sigma(#1)}
+\newcommand{\linkingof}[1]{\sim_{#1}}
 
@@
 
+\todo{Examples,examples,examples}
 \section{Introduction}
@@
   Let $A$ and $B$ be formulas. Then
-  \begin{equation}
-    x
-  \end{equation}
+  \begin{equation*}
+    \vlderivation{
+      \vlde{\set{\wlD,\wrD,\cD,\fequ}}{}{B}{
+        \vlhy{A}}}
+    \qquad
+    \iff
+    \qquad
+    \vlderivation{
+      \vlde{\set{\wlD,\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{}{B}{
+        \vlhy{A}}}
+  \end{equation*}
 \end{lemma}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{A First Decomposition Theorem}
-
-$$
+\begin{proof}
+  This follows immediately from Lemmas~\ref{lem:ac} and~\ref{lem:me}.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Rule Permutations}
+
+%All statements in this section are proved by rule permutation arguments.
+\begin{thm}\label{thm:LK1-decompose}
+  Let $\Gamma$ be a sequent. If\/ $\sqn\Gamma$ is provable in $\FOLK$ (as depicted on the left below) then there is a sequent
+  $\Gamma'$ such that there is a derivation as shown on the right below:\vadjust{\vskip-2ex}
+  \begin{equation*}
     \vlderivation{
-  \vlde{\set{\wD,\cD}}{}{C}{
-    \vlde{\FOMLS}{}{C'}{
-      \vlhy{\ttt}}}}
-$$
+        \vltrl{}{\FOLK}{\Deri}{\sqns{\Gamma}}{
+          \vlhy{\quad}}{
+          \vlhy{}}{
+          \vlhy{}}}
+    \qquad
+    \Longrightarrow
+    \qquad
+    \vlderivation{
+      \vlde{\set{\wlD,\wrD,\cD}}{\Deri_2}{\sqns\Gamma}{
+        \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\Gamma'}}{
+          \vlhy{\quad}}{
+          \vlhy{}}{
+          \vlhy{}}}}
+  \end{equation*}
+\end{thm}
+
+\begin{proof}
+  Note that the instances of $\wlD,\wrD,\cD$ in $\Deri_2$ are deep, but inside sequent contexts.
+  \todo{}
+\end{proof}
+
+\begin{lemma}\label{lem:MLS1-decomposition}
+  For every derivation
+  $\vlderivation{
+      \vlde{\FOMLS}{}{A}{
+        \vlhy{\ttt}}}$
+  there are formulas $A'$ and $A''$ such that 
+  \begin{equation*}
+    \vlderivation{
+      \vlde{\set{\exists}}{}{A}{
+        \vlde{\set{\sw,\mix,\fequ}}{}{A'}{
+          \vlde{\set{\forall,\aiD,\tttD}}{}{A''}{
+            \vlhy{\ttt}}}}}
+  \end{equation*}
+\end{lemma}
+
+\begin{proof}
+  \todo{}
+\end{proof}
+
+\begin{lemma}\label{lem:cw-decomposition}
+  For every derivation
+  $\vlderivation{
+      \vlde{\set{\wlD,\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{}{B}{
+        \vlhy{A}}}$
+  there are formulas $A'$ and $B'$ such that 
+  \begin{equation*}
+    \vlderivation{
+      \vlde{\set{\wlD,\wrD}}{}{B}{
+        \vlde{\set{\acD}}{}{B'}{
+          \vlde{\set{\me,\mfaD,\mexD,\fequ}}{}{A'}{
+            \vlhy{A}}}}}
+  \end{equation*}
+\end{lemma}
+
+\begin{proof}
+  \todo{}
+\end{proof}
+
+We can now complete the proof of Theorems~\ref{thm:decomposition} and~\ref{thm:decompositionA}.
+
+\begin{proof}[Proof of Theorem~\ref{thm:decompositionA}]
+  Assume we have a proof of $A$ in $\FOKS$. By
+  Theorem~\ref{thm:LK1-KS1} we have a proof of $\sqn A$ in $\FOLK$ to
+  which we can apply Theorem~\ref{thm:LK1-decompose}. Finally, we
+  apply Lemma~\ref{lem:MLL1->MLS1} to get the desired shape.
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{thm:decomposition}]
+  Assume we have a proof of $A$ in $\FOKS$. We first apply
+  Theorem~\ref{thm:decompositionA}, and then
+  Lemma~\ref{lem:MLS1-decomposition} to the upper half and
+  Lemma~\ref{lem:cw-decomposition} to the lower half.
+\end{proof}
 
@@
 
+\todo{}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Translation between Unification Nets and Fonets}
+
+\todo{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Translation between $\FOMLS$ and Fonets}
+
+\todo{define rectification $\rectif\Deri$ of a derivation  $~\vlder{\FOMLS}{\Deri}{A}{\ttt}$}
+\todo{define substitution of a derivation $\substof{\Deri}$ and linking of a derivation $\linkingof{\Deri}$ }
+
+\begin{thm}
+  Let the derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
+  the graph $\graphof{\rectif A}$ forms a fonet whose linking is
+  $\linkingof{\rectif\Deri}$ and whose dualizer is
+  $\substof{\rectif\Deri}$.
+\end{thm}
+
+\begin{proof}
+  \todo{}
+\end{proof}
+
+\begin{thm}
+  Let $\gC$ be a fonet with linking $\linkingof\gC$ and dualizer
+  $\delta$, and let $A$ be a formula with $\graphof A=\gC$.  Then
+  there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
+  $\linkingof\gC=\linkingof{\Deri}$ and $\delta=\substof{\Deri}$.
+\end{thm}
+
+\begin{proof}
+  \todo{}
+\end{proof}
 

### 2021-01-13 main.tex
main lemmas in IX

@@
 \newcommand{\gA}{\graph{A}}
+\newcommand{\gB}{\graph{B}}
 \newcommand{\gC}{\graph{C}}
@@
 \newcommand{\linkingof}[1]{\sim_{#1}}
+\newcommand{\mapof}[1]{\left\lfloor{#1}\right\rfloor}
 
@@
 \begin{lemma}\label{lem:MLL1->MLS1}
-  If $\sqn\Gamma$ is rectified and provable in $\FOMLL$ then $\form\Gamma$ is provable in  $\FOMLS$. \todo{check: do we need rectified here?}
-\juihsuan{no}
+  If $\sqn\Gamma$ is provable in $\FOMLL$ then $\form\Gamma$ is provable in  $\FOMLS$.
 \end{lemma}
@@
 replacing $t$ with $a \vlor \dual{a}$ and the $\ttt$-rule with the $\ax$
- rule followed by the $\vlor$ rule}
+ rule followed by the $\vlor$ rule}\lutz{yes! and similar for $\forall$. Can you do that?}
 \begin{proof}
@@
   \todo{}
-  \juihsuan{done. Maybe just keep one case.}
+  \juihsuan{done. Maybe just keep one case.}\lutz{yes, but we do that at the end. don't think about space right now.}
 \end{proof}
@@
   \juihsuan{done. If needed, we can introduce the notion of open deduction to
-reduce the size of derivations...}
+reduce the size of derivations...}\lutz{I was thinking about that, but (i) it is probably not worth the effort, as we wont have many derivation, and (ii) it is hard to define rectified derivations this way.}
 \end{proof}
@@
 
+A derivation $\Deri$ is \bfit{rectified} if every line in $\Deri$ is rectified.
+
 \todo{define rectification $\rectif\Deri$ of a derivation  $~\vlder{\FOMLS}{\Deri}{A}{\ttt}$}
@@
 
+\todo{define rules $\rectif\mfaD,\rectif\mexD$}
+
+\todo{define $\mapof\Deri$ (underlying map doing the flowgraph thing)}
+
+\begin{lemma}
+  Let $\vlderivation{
+    \vlde{\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
+      \vlhy{A}}}$ be a rectified derivation. Then the map
+  $\mapof\Deri\colon\graphof{A}\to\graphof{B}$ is a skew bifibration.
+\end{lemma}
+
 \subsection{From Skew Bifibrations to Contraction and Weakening}
+
+\begin{lemma}
+  Let $\phi\colon\gA\to\gB$ be a skew bifibration, and let $A$ and $B$ be formulas with $\graphof A=\gA$ and $\graphof B=\gB$. Then there is a derivation $\vlderivation{
+    \vlde{\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
+      \vlhy{A}}}$ with $\mapof\Deri=\phi$.
+\end{lemma}
 

### 2021-01-14 main.tex
Unification nets (part 1)

@@
 \newcommand{\Gr}{\mathcal{G}}
-\newcommand{\FT}{\mathcal{F}}
-\newcommand{\US}{\mathcal{U}}
 \newcommand{\PE}[1]{#1^P}
@@
 \newcommand{\form}[1]{\mathrm{fm}(#1)}
+\newcommand{\formtree}[1]{\mathcal{F}(#1)}
+
+\newcommand{\unifstr}[1]{\mathcal{U}(#1)}
 
@@
             \qquad
-            \vliinf{\vlan}{}{\sqn{\Gamma,A\vlan B}}{\sqn{\Gamma,A}}{\sqn{B,\Delta}}
+            \vliinf{\vlan}{}{\sqn{\Gamma,A\vlan B, \Delta}}{\sqn{\Gamma,A}}{\sqn{B,\Delta}}
             \\ \\[-1ex]
@@
 \todo{}
+
+In this paragraph, we associate to each formula $A$ its \bfit{formula tree}
+$\formtree{A}$, a directed
+tree with leaves labelled by atoms, internal nodes labelled by connectives and
+quantifiers, and edges directed from leaves to the root.
+
+Let $\Gamma$ be a sequent in $\FOMLL$. Consider the formula tree
+$\formtree{\form{\Gamma}}$. A \bfit{link} on $\Gamma$ is a pair of
+leaves whose atoms are pre-dual. A \bfit{linking} $\lambda$ on $\Gamma$ is a set
+of
+disjoint links such that each leaf of $\Gamma$ is either labelled by $\ttt$ or
+in exactly one link. Similar to the set of links in linked fographs, a linking can be seen as a
+unification problem, and a dualizer of the linking $\lambda$ is an assignment
+unifying all the links in $\lambda$. There exists a \bfit{most general dualizer}
+ of $\lambda$ if $\lambda$ has a dualizer. \juihsuan{Now I use the same terminology as for linked fographs}
+A \bfit{dependency} is a pair $(\single \exists x, \single \forall y)$ of nodes
+such that the most general dualizer assigns to $x$ a term containing $y$.
+
+Let $\lambda$ is a linking on $\Gamma$ that has a dualizer.
+The \bfit{unification structure} $\unifstr{\lambda}$
+associated to $\lambda$ is the formula tree $\formtree{\form{\Gamma}}$ together with an undirected
+edge between leaves $l$ and $l'$ for every link $\{l, l'\}$ in $\lambda$ and a
+directed edge from $\single \exists x$ to $\single \forall y$ for every
+dependency $(\single \exists x, \single \forall y)$.
+
+A \bfit{switching graph} of a unification structure $\unifstr{\lambda}$ is any
+derivative of $\unifstr{\lambda}$ obtained by keeping only one edge into each $\cor$
+and $\forall$ and undirecting remaining edges. A linking is \bfit{correct} if it
+is unifiable and all of the switching graphs of its associated unification
+structure are acyclic.
+
+\begin{definition}
+  A \bfit{unification net} on a sequent $\Gamma$ is a correct linking on $\Gamma$.
+\end{definition}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \todo{}
+\begin{thm}
+  If a sequent is provable in $\FOMLL$, then there exists a unification net
+  on it.
+\end{thm}
+
+\begin{proof}
+  We proceed by induction on the proof of $\sqn \Gamma$ in $\FOMLL$, making a
+  case analysis on the bottommost rule instance:
+  \begin{itemize}
+    \setlength\itemsep{.5em}
+    \item $\vlinf{\axr}{}{\sqn{a,\cneg a}}{}$ : the linking $\{a, \dual{a}\}$ is correct.
+    \item $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ : the empty linking is correct.
+    \item $\vliinf{\mixr}{}{\sqn{\Gamma,\Delta}}{\sqn\Gamma}{\sqn\Delta}$ :
+	  By induction hypothesis, there is a correct linking on
+	  $\Gamma$ and another one on $\Delta$, their union giving a
+	  correct linking on $\Gamma, \Delta$.
+    \item $\vlinf{\vlor}{}{\sqn{\Gamma,A\vlor B}}{\sqn{\Gamma,A,B}}$ : By
+	  induction hypothesis, there is a correct linking on $\Gamma, A, B$,
+	  and it is correct on $\Gamma, A \vlor B$ as well.
+    \item $\vliinf{\vlan}{}{\sqn{\Gamma,A\vlan B, \Delta}}{\sqn{\Gamma,A}}{\sqn{B,\Delta}}$ :
+          By induction hypothesis, there is a correct linking on $\Gamma, A$ and
+	  another one on $B, \Delta$, their union giving a correct linking on
+          $\Gamma,A \vlan B, \Delta$.
+    \item $\vlinf{\exists}{}{\sqn{\Gamma,\exists x.A}}
+	  {\sqn{\Gamma,A\ssubst{x}{t}}}$ : By induction hypothesis, there is a
+	  correct linking $\lambda$ on $\Gamma, A\ssubst{x}{t}$.
+	  For each atom in $\Gamma, A \ssubst{x}{t}$, there is a corresponding
+	  atom in $\Gamma, \exists x.A$. There is therefore a linking $\lambda'$
+          on $\Gamma, \exists x.A$ obtained from $\lambda$ via this
+	  correspondence, and it is not difficult to check that $\lambda'$ is
+	  correct as well.
+    \item $\vlinf{\forall}{\text{($x$ not free in
+	  $\Gamma$)}}{\sqn{\Gamma,\forall x.A}}{\sqn{\Gamma,A}}$ : By induction
+          hypothesis, there is a correct linking on $\Gamma, A$, and it is easy
+	  to see that it is a correct linking on $\Gamma, \forall x.A$ as well.
+
+  \end{itemize}
+\end{proof}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 $\otimes$ which are generally used in the presentation of linear logic.
-A formula $A$ is identified with its \bfit{formula tree} $\FT(A)$, a directed
+A formula $A$ is identified with its \bfit{formula tree} $\formtree{A}$, a directed
 tree with leaves labelled by atoms, internal nodes labelled by connectives and
@@
 
-Let $\lambda$ is a unifiable linking on $\Gamma = A_1, \ldots, A_n$.
-Let $A = A_1 \cor \ldots \cor A_n$. The \bfit{unification structure}
-$\US(\lambda)$
-associated to $\lambda$ is the formula tree $\FT(A)$ together with an undirected
-edge between leaves $l$ and $l'$ for every link $\{l, l'\}$ in $\lambda$ and a
-directed edge from $\exists x$ to $\forall y$ for every dependency $\exists x
-\rightarrow \forall y$.
-
-A \bfit{switching graph} of a unification structure $\US(\lambda)$ is any
-derivative of $\US(\lambda)$ obtained by keeping only one edge into each $\cor$
-and $\forall$ and undirecting remaining edges. A linking is \bfit{correct} if it
-is unifiable and all of the switching graphs of its associated unification
-structure are acyclic.
-
-\begin{definition}
-  A \bfit{unification net} on a sequent $\Gamma$ is a correct linking on $\Gamma$.
-\end{definition}
-
 \section{From first-order logic to combinatorial proofs}
@@
 
-\begin{definition} A \bfit{switching path} of a  formula tree $\FT(A)$ is a
-	path in $\FT(A)$ that does not go through both incoming edges of a $\cor$.
+\begin{definition} A \bfit{switching path} of a formula tree $\formtree{A}$ is a
+	path in $\formtree{A}$ that does not go through both incoming edges of a $\cor$.
 \end{definition}
@@
   \item $u$ and $v$ are adjacent in $\graphof(A)$
-  \item $u$ and $v$ are connected by a switching path of $\FT(A)$, and if one of them is a universal quantifier, then the other is
+  \item $u$ and $v$ are connected by a switching path of $\formtree{A}$, and if one of them is a universal quantifier, then the other is
 	not a descendant of the former.

### 2021-01-14 main.tex
fonet

@@
 \newcommand{\bgraph}[1]{\mathcal{\vec{#1}}}
-\newcommand{\lgraph}[1]{\mathcal{L_{#1}}}
+\newcommand{\lgraph}[1]{\mathcal{#1}^{\mathsf{L}}}
 \newcommand{\leaps}[1]{L_{#1}}
@@
 \newcommand{\lgG}{\lgraph{\gG}}
+\newcommand{\lgC}{\lgraph{\gC}}
 
 \newcommand{\lpG}{\leaps{\gG}}
+\newcommand{\lpC}{\leaps{\gC}}
 
@@
 graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
-equivalence relation $\samecol$ on $\vG$; each equivalence class is a
+equivalence relation $\linkingof\gG$ on $\vG$; each equivalence class is a
 \bfit{colour}.  A \bfit{vertex renaming} of $\gG=\tuple{\vG,\eG}$
@@
 (e.g. $p(x, y)$ and $\dual{p}(y, z)$) and two literals are \bfit{pre-dual} if their
-labels (atoms) are pre-dual. A \bfit{linked fograph} is a coloured fograph such
-that every colour, called a \bfit{link}, consists of two pre-dual literals, and
+labels (atoms) are pre-dual. A \bfit{linked fograph} is a coloured fograph $\gC$ such
+that every colour (i.e., equivalence class of~$\linkingof\gC$), called a \bfit{link}, consists of two pre-dual literals, and
 every literal is either $\ttt$-labelled or in a link.
 
-Let $\gG$ be a linked fograph. The set of links can be seen as a unification problem
-by identifying dual predicate symbols. A \bfit{dualizer} of $\gG$ is an assignment
-unifying all the links of $\gG$. Since a first-order unification problem is either
+Let $\gC$ be a linked fograph. The set of links can be seen as a unification problem
+by identifying dual predicate symbols. A \bfit{dualizer} of $\gC$ is a substitution
+unifying all the links of $\gC$. Since a first-order unification problem is either
 unsolvable or has a most general unifier, we can define the notion of \bfit{most
-general dualizer}. A \bfit{dependency} is a pair $(\single x, \single y)$ of an
+general dualizer}. A \bfit{dependency} is a pair $\set{\single x, \single y}$ of an
 existential binder $\single x$ and a universal binder $\single y$ such that the most
 general dualizer assigns to $x$ a term containing $y$. A \bfit{leap} is either a
-link or a dependency. The \bfit{leap graph} $\lgG$ of $\gG$ is the undirected
-graph $(\vG, \lpG)$ where $\lpG$ is the set of leaps of $\gG$. A set $W \subseteq \vG$ induces a \bfit{matching} in
-$\gG$ if for all $w \in W$, $N(w) \cap W$ is a singleton, and induces a
-\bfit{bimatching} in $\gG$ if it induces a matching in $\gG$ and in the leap graph
-$\lgG$ as well.
-
-\todo{define matching} \juihsuan{done in the cograph part}\lutz{no, it should be here}
-\juihsuan{fixed}
-
-\todo{adjust notation}
+link or a dependency. The \bfit{leap graph} $\lgC$ of $\gC$ is the undirected
+graph $\tuple{\vC, \lpC}$ where $\lpC$ is the set of leaps of $\gC$. A vetex set $W \subseteq \vC$ induces a \bfit{matching} in
+$\gC$ if for all $w \in W$, $N(w) \cap W$ is a singleton. We say that $W$ induces a
+\bfit{bimatching} in $\gC$ if it induces a matching in $\gC$ and a matching in $\lgC$.
 
@@
 \subsection{Skew Bifibrations}
-
-A graph homomorphism $f: (\vG, \eG) \rightarrow (\vH, \eH)$ is a \bfit{fibration} if
+\lutz{$\phi$ instead of $f$}
+A graph homomorphism $f: \tuple{\vG, \eG} \rightarrow \tuple{\vH, \eH}$ is a \bfit{fibration} if
 for all $v \in \vG$ and $wf(v) \in \eH$, there exists a unique $\tilde{w} \in
@@
 if for all $v \in \vG$ and $wf(v) \in \eH$ there exists $\tilde{w} \in \vG$ such that
-$\tilde{w}v \in \eG$ and $f(\tilde{w})w \notin \eH$. A \bfit{fograph homomorphism}
+$\tilde{w}v \in \eG$ and $f(\tilde{w})w \notin \eH$.
+A directed graph homomorphism is a \bfit{fibration} if \todo{}
+
+\lutz{do we really need that?
+A \bfit{fograph homomorphism}
 is a graph homomorphism between the underlying graphs of the fographs
@@
 vertex $f(b)$ is an existential binder in $\gH$.
+}
+
+\lutz{I think we need \bfit{fograph homomorphism} maps binders to binders and literals to literals, preserving the predicates.}
 
 \begin{definition}
-A \bfit{skew bifibration} between fographs is a label-preserving and
-existential-preserving fograph homomorphism whose restriction to the
-binding graphs is a fibration.
+  Let $\gG$ and $\gH$ be forgraphs.
+A \bfit{skew bifibration} $\phi\colon\gG\to\gH$ is a fograph homomorphism that is a skew fibration on $\tuple{\vG, \eG} \to \tuple{\vH, \eH}$ and a fibration on the binding graphs $\bG\to\bH$.
+  %etween fographs is a label-preserving and
+%existential-preserving fograph homomorphism whose restriction to the
+%binding graphs is a fibration.
 \end{definition}
@@
 A \bfit{first-order combinatorial proof} (\bfit{FOCP}) of a fograph $\gG$ is a skew
-bifibration $f: \gN \rightarrow \gG$ where $\gN$ is a fonet. A \bfit{first-order
+bifibration $\phi\colon \gC \rightarrow \gG$ where $\gC$ is a fonet. A \bfit{first-order
 combinatorial proof} of a formula $A$ is a combinatorial proof of its graph
@@
 unifying all the links in $\lambda$. There exists a \bfit{most general dualizer}
- of $\lambda$ if $\lambda$ has a dualizer. \juihsuan{Now I use the same terminology as for linked fographs}
+ of $\lambda$ if $\lambda$ has a dualizer. \juihsuan{Now I use the same terminology as for linked fographs}\lutz{use $\delta$ for the dualizer (or even better, make it a macro)}
 A \bfit{dependency} is a pair $(\single \exists x, \single \forall y)$ of nodes

### 2021-01-14 main.tex
tiny changes and merge

--- 2021-01-14 main.tex
@@
 \todo{}
-\begin{thm}
+\begin{thm}\label{thm:MLL1->Unet}
   If a sequent is provable in $\FOMLL$, then there exists a unification net
@@
 	  to see that it is a correct linking on $\Gamma, \forall x.A$ as well.
-
   \end{itemize}
+  This allows us to define a translation from proofs in $\FOMLL$ to unification
+  nets.
 \end{proof}
+
+\begin{thm}
+  Any unification net can be obtained via the translation given in Theorem
+  \ref{thm:MLL1->Unet}.
+\end{thm}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-14 main.tex
proof

@@
 \newcommand{\Deri}{\Phi}
+\newcommand{\Proof}{\Pi}
 
@@
 \newcommand{\lpC}{\leaps{\gC}}
+
+\newcommand{\dualizer}{\delta}
 
@@
 \lutz{$\phi$ instead of $f$}
-A graph homomorphism $f: \tuple{\vG, \eG} \rightarrow \tuple{\vH, \eH}$ is a \bfit{fibration} if
-for all $v \in \vG$ and $wf(v) \in \eH$, there exists a unique $\tilde{w} \in
-\vG$ such that $\tilde{w}v \in \eG$ and $f(\tilde{w}) = w$, and is a \bfit{skew fibration}
-if for all $v \in \vG$ and $wf(v) \in \eH$ there exists $\tilde{w} \in \vG$ such that
-$\tilde{w}v \in \eG$ and $f(\tilde{w})w \notin \eH$.
+A graph homomorphism $\phi\colon \tuple{\vG, \eG} \rightarrow \tuple{\vH, \eH}$ is a \bfit{fibration} if
+for all $v \in \vG$ and $w\phi(v) \in \eH$, there exists a unique $\tilde{w} \in
+\vG$ such that $\tilde{w}v \in \eG$ and $\phi(\tilde{w}) = w$, and is a \bfit{skew fibration}
+if for all $v \in \vG$ and $w\phi(v) \in \eH$ there exists $\tilde{w} \in \vG$ such that
+$\tilde{w}v \in \eG$ and $\phi(\tilde{w})w \notin \eH$.
 A directed graph homomorphism is a \bfit{fibration} if \todo{}
@@
 \begin{definition}
-  Let $\gG$ and $\gH$ be forgraphs.
+  Let $\gG$ and $\gH$ be fographs.
 A \bfit{skew bifibration} $\phi\colon\gG\to\gH$ is a fograph homomorphism that is a skew fibration on $\tuple{\vG, \eG} \to \tuple{\vH, \eH}$ and a fibration on the binding graphs $\bG\to\bH$.
@@
   Let $\vlinf{\rr}{}{\Scons B}{\Scons A}$ be an inference rule in
-  $\FOMLS$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
+  $\FOMLS$ other than $\aiD$ and $\forall$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
 \end{lemma}
@@
 
+$\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
+
+$\vlinf{\axr}{}{\sqn{a,\cneg a}}{}
+            \qquad
+            \vlinf{\ttt}{}{\sqn{\ttt}}{}
+$
+
 \begin{proof}
@@
   $\vlinf{\rr}{}{\Scons B}{\Scons A}$. By induction hypothesis we have
-  a $\FOMLL$ proof of $\sqn{\Scons A}$, and by
-  Lemma~\ref{lem:context}, we have a $\FOMLL$ proof of
+  a $\FOMLL$ proof $\Proof$ of $\sqn{\Scons A}$.
+  We now make a case analysis on $\rr$:
+  \begin{itemize}
+    \setlength\itemsep{.5em}
+    \item $\vlinf{\aiD}{}{\Scons{a\vlor\cneg a}}{\Scons\ttt}$ :
+      In this case, we replace simultaneously in $\Pi$ the corresponding
+      occurrences of $\ttt$ with $a \vlor \cneg a$ and the rule instance
+      $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
+      $
+        \vlderivation{
+          \vlin{\vlor}{}{\sqn{a \vlor \cneg a}}{
+            \vlin{\axr}{}{\sqn{a, \cneg a}}{
+              \vlhy{}}}}
+      $, and we get a proof $\Pi'$ of $\sqn{\Scons{a \vlor \cneg a}}$.
+    \item $\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
+      In this case, we replace simultaneously in $\Pi$ the corresponding
+      occurrences of $\ttt$ with $\forall x.\ttt$ and the rule instance
+      $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
+      $
+      \vlderivation{
+        \vlin{\forall}{}{\sqn{\forall x.\ttt}}{
+          \vlin{\axr}{}{\sqn{\ttt}}{
+            \vlhy{}}}}
+      $, and we get a proof $\Pi'$ of $\sqn{\Scons{\forall x.\ttt}}$.
+    \item $\rr \notin \set{\aiD, \faD}$ :
+      By Lemma~\ref{lem:context}, we have a $\FOMLL$ proof of
       $\sqn{\cneg{\Scons A},\Scons B}$. We can compose them via $\cutr$:
@@
       and then apply Theorem~\ref{thm:cutelim}.
+  \end{itemize}
+  \tocheck{}
   \end{proof}
@@
 
-In this paragraph, we associate to each formula $A$ its \bfit{formula tree}
+In this paragraph, we associate each formula $A$ with its \bfit{formula tree}
 $\formtree{A}$, a directed
@@
 in exactly one link. Similar to the set of links in linked fographs, a linking can be seen as a
-unification problem, and a dualizer of the linking $\lambda$ is an assignment
+unification problem, and a \bfit{dualizer} $\dualizer$ of the linking $\lambda$ is an assignment
 unifying all the links in $\lambda$. There exists a \bfit{most general dualizer}
@@
 The \bfit{unification structure} $\unifstr{\lambda}$
-associated to $\lambda$ is the formula tree $\formtree{\form{\Gamma}}$ together with an undirected
+associated with $\lambda$ is the formula tree $\formtree{\form{\Gamma}}$ together with an undirected
 edge between leaves $l$ and $l'$ for every link $\{l, l'\}$ in $\lambda$ and a
@@
   Let $\gC$ be a fonet with linking $\linkingof\gC$ and dualizer
-  $\delta$, and let $A$ be a formula with $\graphof A=\gC$.  Then
+  $\dualizer$, and let $A$ be a formula with $\graphof A=\gC$.  Then
   there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
-  $\linkingof\gC=\linkingof{\Deri}$ and $\delta=\substof{\Deri}$.
+  $\linkingof\gC=\linkingof{\Deri}$ and $\dualizer=\substof{\Deri}$.
 \end{thm}

### 2021-01-14 main.tex
some defs

--- 2021-01-14 main.tex
@@
 \newtheorem{thm}{Theorem}%[section]
+\newtheorem{lemma}[thm]{Lemma}
+\newtheorem{proposition}[thm]{Proposition}
+\newtheorem{theorem_}[thm]{Theorem}
 
@@
 \newtheorem{definition}[thm]{Definition}
-\newtheorem{lemma}[thm]{Lemma}
 \newtheorem{notation}[thm]{Notation}
-\newtheorem{proposition}[thm]{Proposition}
-\newtheorem{theorem_}[thm]{Theorem}
 \newtheorem{example}[thm]{Example}
@@
 
-A derivation $\Deri$ is \bfit{rectified} if every line in $\Deri$ is rectified.
-
-\todo{define rectification $\rectif\Deri$ of a derivation  $~\vlder{\FOMLS}{\Deri}{A}{\ttt}$}
-\todo{define substitution of a derivation $\substof{\Deri}$ and linking of a derivation $\linkingof{\Deri}$ }
+A derivation $\Deri$ is \bfit{rectified} if every line in $\Deri$ is
+rectified.  For a non-rectified derivation $\Deri$ in $\FOMLS$ we can
+define its \bfit{rectification} $\rectif\Deri$ by recifying each
+line. In $\FOMLS$ this can be done inductively, proceeding step-wise
+from conclusion to premise, as the only rules involving bound
+variables are $\forall$ and $\exists$ which both remove a binder (and
+all occurrences of the variable it binds).\footnote{As for formulas,
+the rectification of a derivation is unique up to renaming of bound
+variables.}\todo{check if we need that $\Deri$ has premise $\ttt$}.
+
+A derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ determines a
+substitution which maps the existential bound variables occurring in
+$A$ to the terms substituted for them in the instances of the
+$\exists$-rule in $\Phi$. We denote this substitution with
+$\substof\Phi$. Furthermore, every atom occuring in the conclusion $A$
+must be consumed by a unique instance of the rule $\aiD$ in
+$\Deri$. This allows us to define a (partial) equivalence relation
+$\linkingof\Deri$ on the atom occurrences in $A$ by $a\linkingof\Deri
+b$ if $a$ and $b$ are consumed by the same instance of $\aiD$
+in~$\Deri$. We call $\linkingof\Deri$ the \bfit{linking} of~$\Deri$.
+
+\todo{examle here}
+
+\begin{lemma}\label{lem:MLS1->fonet}
+  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a recified derivation. Then
+  the graph $\graphof{A}$ forms a fonet whose linking is
+  $\linkingof{\Deri}$ and whose dualizer is
+  $\substof{\Deri}$.
+\end{lemma}
+
+\begin{proof}
+  \todo{}  
+\end{proof}
 
 \begin{thm}
-  Let the derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
+  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
   the graph $\graphof{\rectif A}$ forms a fonet whose linking is
@@
 \begin{proof}
-  \todo{}
+  Apply Lemma~\ref{lem:MLS1->fonet} to the rectification $\rectif\Deri$ of $\Deri$.
 \end{proof}
@@
 \begin{thm}
-  Let $\gC$ be a fonet with linking $\linkingof\gC$ and dualizer
-  $\delta$, and let $A$ be a formula with $\graphof A=\gC$.  Then
+  Let $\gC$ be a fonet with linking $\linkingof\gC$, let $\delta$ be a dualizer
+  for $\gC$, and let $A$ be a formula with $\graphof A=\gC$.  Then
   there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
@@
 
-\begin{theorem_}
+\begin{thm}
 \label{thm1}
@@
 Then there is a proof of $\Pi$ in $\LKm$ iff there is a proof of some sequent $\Delta$ in $\FOMLLm$ and a derivation from $\Delta$ to $\Gamma$ consisting of the $\cD$ and $\wD$ rules only.
-\end{theorem_}
+\end{thm}
 

### 2021-01-14 main.tex

--- 2021-01-14 main.tex
@@
 \begin{thm}
-  Let $\gC$ be a fonet with linking $\linkingof\gC$ and dualizer
-  $\dualizer$, and let $A$ be a formula with $\graphof A=\gC$.  Then
+  Let $\gC$ be a fonet with linking $\linkingof\gC$, let $\dualizer$ be a dualizer
+  for $\gC$, and let $A$ be a formula with $\graphof A=\gC$.  Then
   there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that

### 2021-01-14 main.tex
some more defs

@@
 
-\todo{examle here}
+\todo{example here}
 
@@
 \subsection{From Contraction and Weakening to Skew Bifibrations}
+
+If a derivation $\Deri$ contains instances of the rules $\mfaD$ and
+$\mexD$ we can no longer naively define the rectification
+$\rectif\Deri$ as in the previous section for $\FOMLS$, as these two
+rules cannot be applied if premise and conclusion are rectified. For
+this reason we define here rectified versions $\rectif\mfaD$ and
+$\rectif\mexD$.
 

### 2021-01-15 main.tex
some more defs

@@
 
+\newcommand{\vgraphof}[1]{V_{\graphof{#1}}}
 \newcommand{\gA}{\graph{A}}
@@
 \newcommand{\Scons}[1]{S\cons{#1}}
-\newcommand{\conhole}{\cons{~}}
+\newcommand{\conhole}{\cons{\cdot}}
 \newcommand{\Sconhole}{S\conhole}
@@
 this reason we define here rectified versions $\rectif\mfaD$ and
-$\rectif\mexD$.
-
-\todo{define rules $\rectif\mfaD,\rectif\mexD$}
-
-\todo{define $\mapof\Deri$ (underlying map doing the flowgraph thing)}
-
+$\rectif\mexD$, show below:
+\begin{equation*}
+  \vlinf{\rectif\mfaD}{}{\Scons{\forall x.(Ax\vlor Bx)}}{\Scons{(\forall y.Ay)\vlor(\forall z.Bz)}}
+  \qquad
+  \vlinf{\rectif\mexD}{}{\Scons{\exists x.(Ax\vlor Bx)}}{\Scons{(\exists y.Ay)\vlor(\exists z.Bz)}}
+\end{equation*}
+Here, we use the notation $A\cdot$ for a formula $A$ with occurrences
+of a placeholder $\cdot$ for a variable. Then $Ax$ stands for the
+results of replacing that placeholder with $x$, and also indicating
+that $x$ must not occur in $A\cdot$. Then $\forall x.Ax$ and $\forall
+y.Ay$ are the same formula modulo renaming of the bound variable bound
+by the outermost $\forall$-quantifier. In the rules $\rectif\mfaD$ and
+$\rectif\mexD$ we also demand that the variables $x$, $y$, and $z$ do
+not occur in the context $\Sconhole$.
+
+For each instance $\vlinf{\rr}{}{P}{Q}$ of an inference rule in
+$\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can
+define the \bfit{induced map} $\mapof{\rr}\colon\vgraphof
+Q\to\vgraphof P$ which acts as the identity for
+$\rr\in\set{\me,\fequ}$ and as the canonical injection for
+$\rr\in\set{\wlD,\wrD}$. For $\rr=\acD$ it maps the vertices
+corresponding to the two atoms in the premise to vertex of the
+contracted atom in the conclusion, and for
+$\rr\in\set{\rectif\mfaD,\rectif\mexD}$ it maps the two vertices
+corresponding to the quantifiers in the premise to the one in the
+conclusion (as acts as the identity on all other vertices). For a
+derivation $\Deri$ in
+$\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we define
+the \bfit{induced map} $\mapof\Deri$ as the composition of the induced
+maps of the rule instances in $\Deri$.
+
+\todo{example}
 \begin{lemma}
@@
     \vlde{\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
-      \vlhy{A}}}$ be a rectified derivation. Then the map
+      \vlhy{A}}}$ be a rectified derivation. Then the induced map
   $\mapof\Deri\colon\graphof{A}\to\graphof{B}$ is a skew bifibration.

### 2021-01-15 main.tex
comment
prop encoding

@@
 \newcommand{\Gr}{\mathcal{G}}
-\newcommand{\PE}[1]{#1^P}
+\newcommand{\PE}[1]{#1^\circ}
 
@@
 \end{lemma}
-
-$\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
-
-$\vlinf{\axr}{}{\sqn{a,\cneg a}}{}
-            \qquad
-            \vlinf{\ttt}{}{\sqn{\ttt}}{}
-$
 
@@
 \end{thm}
+\juihsuan{maybe we should take $\form{\Gamma}$ instead? (consider the proof
+$\vlderivation{\vlin{\wk}{}{\sqn{\ttt, A}}{
+                 \vlin{\ttt}{}{\sqn\ttt}{
+                   \vlhy{}}}}$)}
 
@@
 
-\todo{}
+\todo{this has to be moved to the right place at some point}
+
+The \bfit{propositional encoding} $\PE{A}$ of a formula $A$ is defined inductively by:
+\begin{equation*}
+  \begin{array}{r@{\;=\;}l}
+    \PE{a} & a\\
+    \PE{(A \cor B)} &  \PE{A} \cor \PE{B} \\
+    \PE{(A \cand B)} & \PE{A} \cand \PE{B}
+  \end{array}
+  \qquad
+  \begin{array}{r@{\;=\;}l}
+    \PE{(\forall x A)} & u_x \cor \PE{A}\\
+    \PE{(\exists x A)} & e_x \cand \PE{A}
+  \end{array}
+\end{equation*}
+where $u_x$ and $e_x$ are fresh nullary atoms.
+The purpose of the propositional encoding is to simplify some arguments that do not depend on the variable bindings.
+In particular, observe that $\graphof A$ and $\graphof{\PE A}$ only differ in the labelling of certain vertices.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-15 main.tex
not much

@@
 
+\begin{proof}
+  For $\Deri$, we construct its propositional encoding $\PE\Deri$ by
+  translating every line into its proposional encoding. The rules
+  $\rectif\mfaD$ and $\rectif\mexD$ are replaced by:
+  \begin{equation*}
+    \vlderivation{
+      \vlin{\rectif\acD}{}{\Scons{u_x\vlor\PE{(Ax)}\vlor\PE{(Ax)}}}{
+        \vlin{\fequ}{}{\Scons{(u_y\vlor u_z)\vlor(\PE{(Ax)}\vlor\PE{(Ax)})}}{
+          \vlhy{\Scons{(u_y\vlor\PE{(Ax)})\vlor (u_z\vlor\PE{(Ax)})}}}}}
+  \end{equation*}
+  and
+  \begin{equation*}
+    \vlderivation{
+      \vlin{\rectif\acD}{}{\Scons{e_x\vlan\PE{(Ax)}\vlor\PE{(Ax)}}}{
+        \vlin{\me}{}{\Scons{(e_y\vlor e_z)\vlan(\PE{(Ax)}\vlor\PE{(Ax)})}}{
+          \vlhy{\Scons{(e_y\vlan\PE{(Ax)})\vlor (e_z\vlan\PE{(Ax)})}}}}}
+  \end{equation*}
+  respectively. This gives us a derivation $\vlderivation{
+    \vlde{\set{\wlD,\wrD,\acD,\rectif\acD,\me,\fequ}}{\PE\Deri}{\PE
+      B}{ \vlhy{\PE A}}}$ with $\mapof{\PE\Deri}$ being equal to
+  $\mapof\Deri$, modulo relabeling of of the binders. It has been
+  shown in~\cite{str:07:RTA} that $\mapof{\PE\Deri}$ is a skew
+  fibration (see
+  also~\cite{hughes:invar,str:ral:tableaux19,str:RR-9048}). Hence,
+  $\mapof\Deri$ is a skew fibration. \todo{show the other properties,
+    once they are fixed}
+\end{proof}
 \subsection{From Skew Bifibrations to Contraction and Weakening}
@@
 \begin{lemma}
-  Let $\phi\colon\gA\to\gB$ be a skew bifibration, and let $A$ and $B$ be formulas with $\graphof A=\gA$ and $\graphof B=\gB$. Then there is a derivation $\vlderivation{
+  Let $\phi\colon\gA\to\gB$ be a skew bifibration, and let $A$ and $B$
+  be formulas with $\graphof A=\gA$ and $\graphof B=\gB$. Then there
+  is a derivation $\vlderivation{
     \vlde{\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
@@
 
+\begin{proof}
+  Let $\PE\gA=\graphof{\PE A}$ and $\PE\gB=\graphof{\PE B}$ which are equal to $\gA$ and $\gB$, respectively, modulo relabeling of the binders.
+Thus, we can define $\PE\phi\colon\PE\gA\to\PE\gB$, which is a skew fibration as well.
+\end{proof}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-15 main.tex
unification nets

@@
 \newcommand{\unifstr}[1]{\mathcal{U}(#1)}
+\newcommand{\sqntl}[1]{\left\lceil{#1}\right\rceil}
 
@@
 tree with leaves labelled by atoms, internal nodes labelled by connectives and
-quantifiers, and edges directed from leaves to the root.
-
-Let $\Gamma$ be a sequent in $\FOMLL$. Consider the formula tree
-$\formtree{\form{\Gamma}}$. A \bfit{link} on $\Gamma$ is a pair of
+quantifiers, and edges directed from leaves to the root. For a sequent
+$\Gamma = A_1, \ldots, A_n$, we denote with $\formtree{\Gamma}$, the forest
+formed by $\formtree{A_1}, \ldots, \formtree{A_n}$, i.e., the disjoint union of
+$\formtree{A_i}$'s. The \bfit{roots} of $\formtree{\Gamma}$ are the roots of
+${A_i}$'s
+
+Let $\Gamma$ be a sequent in $\FOMLL$. Consider the forest
+$\formtree{\Gamma}$. A \bfit{link} on $\Gamma$ is a pair of
 leaves whose atoms are pre-dual. A \bfit{linking} $\lambda$ on $\Gamma$ is a set
 of
-disjoint links such that each leaf of $\Gamma$ is either labelled by $\ttt$ or
+disjoint links such that each leaf of $\formtree{\Gamma}$ is either labelled by $\ttt$ or
 in exactly one link. Similar to the set of links in linked fographs, a linking can be seen as a
@@
 The \bfit{unification structure} $\unifstr{\lambda}$
-associated with $\lambda$ is the formula tree $\formtree{\form{\Gamma}}$ together with an undirected
+associated with $\lambda$ is the forest $\formtree{\Gamma}$ together with an undirected
 edge between leaves $l$ and $l'$ for every link $\{l, l'\}$ in $\lambda$ and a
@@
   \end{itemize}
-  This allows us to define a translation from proofs in $\FOMLL$ to unification
+  This allows to define a translation $\sqntl\cdot$ from proofs in $\FOMLL$ to unification
   nets.
@@
 \begin{thm}
-  Any unification net can be obtained via the translation given in Theorem
+  Any unification net can be obtained via the translation $\sqntl\cdot$ given in Theorem
   \ref{thm:MLL1->Unet}.
 \end{thm}
+Let $\lambda$ be a unification net on $\Gamma$. We proceed by induction on the
+number of connectives in $\Gamma$. In the base case, $\Gamma$ is of the form
+\begin{align*}
+p_1(t_{11}, \ldots, t_{1n_1}), \dual{p_1}(t_{11}, \ldots, t_{1n_1}), \ldots, \\
+p_k(t_{k1}, \ldots, t_{kn_k}), \dual{p_k}(t_{k1}, \ldots, t_{kn_k}),
+\underbrace{\ttt, \ldots, \ttt}_\text{$m$ times}
+\end{align*} and
+$\lambda$ is the linking $\set{(a_1, \cneg{a_1}), \ldots, (a_k, \cneg{a_k})}$,
+where $a_i = p_i(t_{i1}, \ldots, t_{in_i})$, which equals to $\sqntl\Pi$, where
+$\Pi$ is the proof consisting of $m$ instances of the $\ttt$ rule, $n$ instances
+$\vlinf{\ax}{}{\sqn a_i, \cneg{a_i}}{}$ of the $\ax$ rule, and followed by
+$m+k-1$ instances of the $\mix$ rule.
+
+Now we consider the inductive cases:
+\begin{itemize}
+  \item $\Gamma = \Delta, A \vlor B$:
+  \item $\Gamma = \Delta \forall x.A$:
+\end{itemize}
 

### 2021-01-16 main.tex
still in IX

@@
 \newcommand{\graph}[1]{\mathcal{#1}}
-\newcommand{\vertices}[1][]{\ifthenelse{\isempty{#1}}{V}{V_{\graph{#1}}}}
+\newcommand{\vertices}[1][]{\ifthenelse{\isempty{#1}}{V}{V_{{\graph{#1}}}}}
 \newcommand{\edges}[1][]{\ifthenelse{\isempty{#1}}{E}{E_{\graph{#1}}}}
@@
 \newcommand{\gB}{\graph{B}}
+\newcommand{\gBone}{\graph{B}_1}
 \newcommand{\gC}{\graph{C}}
@@
 \newcommand{\bA}{\bgraph{A}}
+\newcommand{\bB}{\bgraph{B}}
 \newcommand{\bC}{\bgraph{C}}
@@
 \newcommand{\vA}{\vertices[A]}
+\newcommand{\vB}{\vertices[B]}
+\newcommand{\vBone}{V_{\mathcal{B}_1}}
 \newcommand{\vC}{\vertices[C]}
@@
 \renewcommand\acD {\mathsf{ac}}
+\newcommand\acDeq {\mathsf{ac}^\fequ}
 \newcommand\mfaD {\mathsf{m_\forall}}
@@
 
-\todo{this has to be moved to the right place at some point}
-
-The \bfit{propositional encoding} $\PE{A}$ of a formula $A$ is defined inductively by:
-\begin{equation*}
-  \begin{array}{r@{\;=\;}l}
-    \PE{a} & a\\
-    \PE{(A \cor B)} &  \PE{A} \cor \PE{B} \\
-    \PE{(A \cand B)} & \PE{A} \cand \PE{B}
-  \end{array}
-  \qquad
-  \begin{array}{r@{\;=\;}l}
-    \PE{(\forall x A)} & u_x \cor \PE{A}\\
-    \PE{(\exists x A)} & e_x \cand \PE{A}
-  \end{array}
-\end{equation*}
-where $u_x$ and $e_x$ are fresh nullary atoms.
-The purpose of the propositional encoding is to simplify some arguments that do not depend on the variable bindings.
-In particular, observe that $\graphof A$ and $\graphof{\PE A}$ only differ in the labelling of certain vertices.
+\todo{}
 
@@
 
-\subsection{From Contraction and Weakening to Skew Bifibrations}
-
-If a derivation $\Deri$ contains instances of the rules $\mfaD$ and
+In this section we establish the relation between ske bifibrations and derivations  in
+$\set{\wlD,\wrD,\acD,\me,\mfaD,\mexD,\fequ}$. However, 
+if a derivation $\Deri$ contains instances of the rules $\mfaD$ and
 $\mexD$ we can no longer naively define the rectification
@@
 derivation $\Deri$ in
-$\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we define
+$\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can then define
 the \bfit{induced map} $\mapof\Deri$ as the composition of the induced
@@
 \todo{example}
-\begin{lemma}
+
+\subsection{From Contraction and Weakening to Skew Bifibrations}
+
+\begin{lemma}\label{lem:cw->skew}
   Let $\vlderivation{
@@
 
+Before we show the proof of this lemma, we introduce another useful
+concept: the \bfit{propositional encoding} $\PE{A}$ of a formula $A$,
+which is a proposional formula with the property that $\graphof{\PE
+  A}=\graphof{A}$. For this, we introduce new propositional variables
+that have the same names as the (first-order) variables
+$x\in\VAR$. Then $\PE{A}$ is defined inductively by:
+\begin{equation*}
+  \begin{array}{r@{\;=\;}l}
+    \PE{a} & a\\
+    \PE{(A \cor B)} &  \PE{A} \cor \PE{B} \\
+    \PE{(A \cand B)} & \PE{A} \cand \PE{B}
+  \end{array}
+  \qquad
+  \begin{array}{r@{\;=\;}l}
+    \PE{(\forall x A)} & x \cor \PE{A}\\
+    \PE{(\exists x A)} & x \cand \PE{A}
+  \end{array}
+\end{equation*}
+
+\begin{lemma}
+  \label{lem:PE}
+  For every formula $A$, we have $\graphof{\PE A}=\graphof{A}$.
+\end{lemma}
+
 \begin{proof}
+  Straightforward induction on $A$. 
+\end{proof}
+
+We use $\PE\fequ$ to denote the restriction of $\fequ$ to
+propositional formulas, i.e., the first two lines in~\eqref{eq:fequ}.
+
+\begin{proof}[Proof of Lemma~\ref{lem:cw->skew}]
   For $\Deri$, we construct its propositional encoding $\PE\Deri$ by
-  translating every line into its proposional encoding. The rules
-  $\rectif\mfaD$ and $\rectif\mexD$ are replaced by:
+  translating every line into its proposional encoding. The instances of the rules
+  $\rectif\mfaD$ and $\rectif\mexD$ are replaced two steps by:
   \begin{equation*}
     \vlderivation{
-      \vlin{\rectif\acD}{}{\Scons{u_x\vlor\PE{(Ax)}\vlor\PE{(Ax)}}}{
-        \vlin{\fequ}{}{\Scons{(u_y\vlor u_z)\vlor(\PE{(Ax)}\vlor\PE{(Ax)})}}{
-          \vlhy{\Scons{(u_y\vlor\PE{(Ax)})\vlor (u_z\vlor\PE{(Ax)})}}}}}
+      \vlin{\rectif\acD}{}{\Scons{x\vlor(\PE{(Ax)}\vlor\PE{(Bx))}}}{
+        \vlin{\fequ}{}{\Scons{(y\vlor z)\vlor(\PE{(Ay)}\vlor\PE{(Bz)})}}{
+          \vlhy{\Scons{(y\vlor\PE{(Ay)})\vlor (z\vlor\PE{(Bz)})}}}}}
   \end{equation*}
@@
     \vlderivation{
-      \vlin{\rectif\acD}{}{\Scons{e_x\vlan\PE{(Ax)}\vlor\PE{(Ax)}}}{
-        \vlin{\me}{}{\Scons{(e_y\vlor e_z)\vlan(\PE{(Ax)}\vlor\PE{(Ax)})}}{
-          \vlhy{\Scons{(e_y\vlan\PE{(Ax)})\vlor (e_z\vlan\PE{(Ax)})}}}}}
+      \vlin{\rectif\acD}{}{\Scons{x\vlan\PE{(Ax)}\vlor\PE{(Bx)}}}{
+        \vlin{\me}{}{\Scons{(y\vlor z)\vlan(\PE{(Ay)}\vlor\PE{(Bz)})}}{
+          \vlhy{\Scons{(y\vlan\PE{(Ay)})\vlor (z\vlan\PE{(Bz)})}}}}}
   \end{equation*}
-  respectively. This gives us a derivation $\vlderivation{
-    \vlde{\set{\wlD,\wrD,\acD,\rectif\acD,\me,\fequ}}{\PE\Deri}{\PE
-      B}{ \vlhy{\PE A}}}$ with $\mapof{\PE\Deri}$ being equal to
-  $\mapof\Deri$, modulo relabeling of of the binders. It has been
+  respectively, where $\rectif\acD$ is a $\acD$ that renames the
+  variabes---the atom variable, as well as the first-order variable of
+  the same name---as everything is recified, there is no ambiguity
+  here.
+  This gives us a derivation $\vlderivation{
+    \vlde{\set{\wlD,\wrD,\acD,\rectif\acD,\me,\PE\fequ}}{\PE\Deri}{\PE
+      B}{ \vlhy{\PE A}}}$ such that  $\mapof{\PE\Deri}=\mapof\Deri$. It has been
   shown in~\cite{str:07:RTA} that $\mapof{\PE\Deri}$ is a skew
@@
 
-\begin{lemma}
+\begin{lemma}\label{skew->cw}
   Let $\phi\colon\gA\to\gB$ be a skew bifibration, and let $A$ and $B$
@@
 \begin{proof}
-  Let $\PE\gA=\graphof{\PE A}$ and $\PE\gB=\graphof{\PE B}$ which are equal to $\gA$ and $\gB$, respectively, modulo relabeling of the binders.
-Thus, we can define $\PE\phi\colon\PE\gA\to\PE\gB$, which is a skew fibration as well.
+  By Lemma~\ref{lem:PE} we have $\gA=\graphof{\PE A}$ and
+  $\gB=\graphof{\PE B}$.  Let $\vB'\subseteq\vB$ be the image of
+  $\phi$, and let $\gB_1$ be the subgraph of $\gB$ induced by
+  $\vB'$. Now let $\PE B_1$ be the propositional formula obtained from
+  $\PE B$ by removing all atoms that are not represented by vertices
+  in $\vB'$. Then $\graphof{\PE B_1}=\gB_1$. Furthermore, the map
+  $\phi'\colon \gB_1\to\gB$ is an injection that reflects
+  edges. Hence, by \cite[Proposition~7.6.1]{str:07:RTA}, we
+  have a derivation
+  $\vlder{\set{\wlD,\wrD}}{\PE\Deri_1}{\PE B}{\PE B_1}$. \todo{show that we have $B_1$ with $\graphof{B_1}=\gB_1$, so that we can can get
+  first order derivation $\vlder{\set{\wlD,\wrD}}{\Deri_1}{B}{B_1}$.}
+
+  Now, let $\sigma$ be the substitution induced by $\phi$, and let
+  $\gA_1=\gA\sigma$ be the graph obtained from $\gA$ by applying
+  $\sigma$ to all the labels. Note that $\gA_1$ is not neccesarily a
+  fograph, as binders might be illegal. But it still is a cograph, and
+  we have a surjective skew fibration $\phi''\colon\gA_1\to\gB_1$ that
+  preserves the labels. Therefore, by
+  \cite[Proposition~7.5]{str:ral:tableaux19}, there is a derivation
+  $\vlder{\set{\acD,\me,\PE\fequ}}{\PE\Deri_2}{\PE B_1}{\PE A_1}$,
+  where $\PE A_1 =\PE A\sigma$ is the result of applying $\sigma$
+  to~$\PE A$. To $\Deri_2$ we can apply a permutation argument,
+  permuting all instances of $\acD$ up until they either reach the top
+  of the derivation or an instance of $\me$ which separates the two
+  atoms in the premise. More precisely, we consider the following inferene rule
+  \begin{equation}
+    \vlinf{\acDeq}{}{\Scons{a}}{S_0\cons{S_1\cons{a}\vlor S_2\cons{a}}}
+  \end{equation}
+  where $S_1\conhole\fequ\conhole\vlor E$ and
+  $S_2\conhole\fequ\conhole\vlor F$ and $S\conhole\fequ
+  S_0\cons{\conhole\vlor E\vlor F}$ for some formulas $E$ and $F$. The
+  rule $\acDeq$ permutes over $\fequ$ and other instances of $\acDeq$,
+  and over instances of $\me$ if they occur inside $S_0$ or $S_1$ or
+  $S_2$. The only situation in which $\acDeq$ cannot be permuted up is
+  the following:
+  \begin{equation}
+    \vlderivation{
+      \vlin{\acDeq}{}{\Scons{R\cons{a}\vlan(C\vlor D)}}{
+        \vlin{\me}{}{\Scons{(R_1\cons{a}\vlor R_2\cons{a})\vlan(C\vlor D)}}{
+          \vlhy{\Scons{(R_1\cons{a}\vlan C)\vlor (R_2\cons{a}\vlor D)}}}}}
+  \end{equation}
+  Now we translate 
 \end{proof}

### 2021-01-17 main.tex
abstract

@@
 \begin{abstract}
+  In this paper we uncover a close relation between combinatorial and
+  syntactic proofs for first-order logic. Whereas syntactic proofs are
+  formalized in some deductive proof system based on inference rules,
+  a combinatorial proof is a ``syntax-free'' presentation of a proof
+  that is independent from any set of inference rules. We show that
+  the two proof representations are related via a deep inference
+  decomposition theorem that establishes a certain kind of normal form
+  of syntactic proofs. As a consequence, we obtain (i) a simple proof
+  of the soundness and completeness of first-order combinatorial
+  proofs, and (ii) a full completeness theorem: every combinatorial
+  proof is the image of a syntactic proof.
 \end{abstract}

### 2021-01-17 main.tex
sequentialisation

@@
 We define a congruence relation $\fequ$ on formulas by the following equations:
-\begin{equation*}
+\begin{equation}
+  \label{eq:fequ}
   \begin{array}{cc}
@@
   \end{array}
-\end{equation*}
+\end{equation}
 where $x \notin fv(B)$ in the last two equations.
@@
   \item $\Gamma = \Delta, A \vlor B$:
-  \item $\Gamma = \Delta \forall x.A$:
+    Let $\Gamma' = \Delta, A, B$. Define $\lambda'$ on $\Gamma'$ using the same
+    links as $\lambda$ by identifying the leaves of $\formtree{\Gamma'}$ with those
+    of $\formtree{\Gamma}$. We now check that $\lambda'$ is a unification net:
+    \begin{itemize}
+      \item The most general dualizer of $\lambda$ is also the most general
+dualizer of $\lambda'$ as they correspond to the same unification problem.
+Hence, the unification structure $\unifstr{\lambda'}$ is equal to the
+restriction of $\unifstr{\lambda}$ to the nodes of $\formtree{\Gamma'}$.
+      \item Every switching graph of $\lambda'$ is acyclic: if there were some
+switching graph of $\unifstr{\lambda'}$ containing a cycle, it would induce a switching
+graph of $\unifstr{\lambda}$ containing also a cycle, by adding an edge from the root of
+$\formtree{A}$ to the $\vlor$ node in question.
+    \end{itemize}
+  \item $\Gamma = \Delta, \forall x.A$:
+    Let $\Gamma' = \Delta, A$. Define $\lambda'$ on $\Gamma'$ using the same
+links as $\lambda$. We now check that $\lambda'$ is a unification net:
+  \begin{itemize}
+    \item The most general dualizer of $\lambda$ is also the most general
+dualizer of $\lambda'$ as they correspond to the same unification problem.
+    \item Every switching graph of $\unifstr{\lambda'}$ is acyclic: if there
+were some switching graph of $\unifstr{\lambda'}$ containing a cycle, it would
+induce a switching graph of $\unifstr{\lambda}$ contaiting also a cycle, by
+adding an edge from the root of $\formtree{A}$ to the $\forall$ node in
+question.
+  \end{itemize}
+  \item $\formtree{\Gamma}$ has a root $\exists x$ with no outgoing dependency
+edge:
 \end{itemize}

### 2021-01-17 main.tex
still in IX

--- 2021-01-17 main.tex
@@
 \renewcommand\wD {\mathsf{w}}
-\newcommand\wlD {\mathsf{w_l}}
-\newcommand\wrD {\mathsf{w_r}}
+\newcommand\wlD {\mathsf{w}}
+\newcommand\wrD {\mathsf{w}}
 \renewcommand\cD {\mathsf{c}}
@@
 \newcommand{\ssubst}[2]{\sublist{\subst{#1}{#2}}}
-\newcommand{\substof}[1]{\sigma(#1)}
+\newcommand{\substof}[1]{\sigma_{\!#1}}
 \newcommand{\linkingof}[1]{\sim_{#1}}
-\newcommand{\mapof}[1]{\left\lfloor{#1}\right\rfloor}
+\newcommand{\mapof}[1]{\lfloor{#1}\rfloor}
 
@@
 \newcommand{\sqntl}[1]{\left\lceil{#1}\right\rceil}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\quand}{\quad\mbox{and}\quad}
+
+\newcommand{\qquand}{\qquad\mbox{and}\qquad}
 
@@
         \vlinf{\wrD}{}{\Scons{A\vlor B}}{\Scons{A}}
-        \qquad
-        \vlinf{\wlD}{}{\Scons{B\vlor A}}{\Scons{A}}
+        %%\qquad
+        %%\vlinf{\wlD}{}{\Scons{B\vlor A}}{\Scons{A}}
         \qquad
@@
     \vlderivation{
-      \vlde{\set{\wlD,\wrD}}{}{A}{
+      \vlde{\set{\wrD,\fequ}}{}{A}{
         \vlde{\set{\acD}}{}{A_1}{
@@
     \vlderivation{
-      \vlde{\set{\wlD,\wrD,\cD}}{}{A}{
+      \vlde{\set{\wrD,\cD,\fequ}}{}{A}{
         \vlde{\FOMLS}{}{A_1}{
@@
     \vlderivation{
-      \vlde{\set{\wlD,\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{
+      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{
         \vlde{\FOMLS}{\Deri_1}{A'}{
@@
   \label{lem:me}
-  The rules $\me,\mfaD,\mexD$ are derivable in $\set{\wlD,\wrD,\cD}$. 
+  The rules $\me,\mfaD,\mexD$ are derivable in $\set{\wrD,\cD,\fequ}$. 
 \end{lemma}
@@
     \vlderivation{
-      \vlde{\set{\wlD,\wrD,\cD,\fequ}}{}{B}{
+      \vlde{\set{\wrD,\cD,\fequ}}{}{B}{
         \vlhy{A}}}
@@
     \vlderivation{
-      \vlde{\set{\wlD,\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{}{B}{
+      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{}{B}{
         \vlhy{A}}}
@@
     \vlderivation{
-      \vlde{\set{\wlD,\wrD,\cD}}{\Deri_2}{\sqns\Gamma}{
+      \vlde{\set{\wrD,\cD,\fequ}}{\Deri_2}{\sqns{\form{\Gamma}}}{
         \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\Gamma'}}{
@@
 \begin{proof}
-  Note that the instances of $\wlD,\wrD,\cD$ in $\Deri_2$ are deep, but inside sequent contexts.
+  Note that the instances of $\wrD,\cD$ in $\Deri_2$ are deep, but inside sequent contexts.
   \todo{}
@@
   $\vlderivation{
-      \vlde{\set{\wlD,\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{}{B}{
+      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{}{B}{
         \vlhy{A}}}$
@@
     \vlderivation{
-      \vlde{\set{\wlD,\wrD}}{}{B}{
+      \vlde{\set{\wrD,\fequ}}{}{B}{
         \vlde{\set{\acD}}{}{B'}{
@@
 In this section we establish the relation between ske bifibrations and derivations  in
-$\set{\wlD,\wrD,\acD,\me,\mfaD,\mexD,\fequ}$. However, 
+$\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}$. However, 
 if a derivation $\Deri$ contains instances of the rules $\mfaD$ and
@@
 
+Note that in an instance of $\rectif\mfaD$ or $\rectif\mexD$ (as shown
+above), we can have $x=y$ or $x=z$, but not both if the premise is
+rectified. If $x=y$ and $x=z$ we have $\mfaD$ and
+$\mexD$ as special cases of $\rectif\mfaD$ and $\rectif\mexD$, respectively.
+
+For a derivation $\Deri$ in
+$\set{\wlD,\wrD,\acD,\me,\mfaD,\mexD,\fequ}$, we can now construct the
+\bfit{recification} $\rectif\Deri$ by rectifying each line of $\Deri$, yielding a derivation in 
+$\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$.
+
 For each instance $\vlinf{\rr}{}{P}{Q}$ of an inference rule in
-$\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can
+$\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can
 define the \bfit{induced map} $\mapof{\rr}\colon\vgraphof
@@
 derivation $\Deri$ in
-$\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can then define
+$\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can then define
 the \bfit{induced map} $\mapof\Deri$ as the composition of the induced
@@
 
+\begin{lemma}
+  Let $\downsmash{\vlderivation{
+    \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
+      \vlhy{A}}}}$ be a derivation. Then there is a recified derivation
+  $\vlderivation{
+    \vlde{\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{\rectif
+      B}{ \vlhy{\rectif A}}}$, such that the induced maps
+  $\mapof\Deri\colon\graphof{A}\to\graphof{B}$ and
+  $\mapof{\rectif\Deri}\colon\graphof{\rectif A}\to\graphof{\rectif
+    B}$ are equal up to the relabeling of the vertices.
+\end{lemma}
+
+\begin{proof}
+  Immediate from the definition.
+\end{proof}
+
 \todo{example}
@@
   Let $\vlderivation{
-    \vlde{\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
-      \vlhy{A}}}$ be a rectified derivation. Then the induced map
+    \vlde{\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
+      \vlhy{A}}}$ be a recified derivation. Then the induced map
   $\mapof\Deri\colon\graphof{A}\to\graphof{B}$ is a skew bifibration.
@@
 \begin{proof}[Proof of Lemma~\ref{lem:cw->skew}]
-  For $\Deri$, we construct its propositional encoding $\PE\Deri$ by
-  translating every line into its proposional encoding. The instances of the rules
-  $\rectif\mfaD$ and $\rectif\mexD$ are replaced two steps by:
+  First, observe that for every inference rule
+  $\rr\in\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we
+  the induced map $\mapof{\rr}\colon\vgraphof Q\to\vgraphof P$ defines
+  a fibration on the corresponding binding graphs. Therefore, their
+  composition $\mapof\Deri$ is a fibration.
+
+  Now we construct for
+  $\Deri$ its propositional encoding $\PE\Deri$ by
+  translating every line into its proposional encoding. The instances
+  of the rules $\rectif\mfaD$ and $\rectif\mexD$ are replaced two
+  steps by:
   \begin{equation*}
@@
   This gives us a derivation $\vlderivation{
-    \vlde{\set{\wlD,\wrD,\acD,\rectif\acD,\me,\PE\fequ}}{\PE\Deri}{\PE
+    \vlde{\set{\wrD,\acD,\rectif\acD,\me,\PE\fequ}}{\PE\Deri}{\PE
       B}{ \vlhy{\PE A}}}$ such that  $\mapof{\PE\Deri}=\mapof\Deri$. It has been
@@
   also~\cite{hughes:invar,str:ral:tableaux19,str:RR-9048}). Hence,
-  $\mapof\Deri$ is a skew fibration. \todo{show the other properties,
-    once they are fixed}
+  $\mapof\Deri$ is a skew fibration.
 \end{proof}
@@
 \begin{lemma}\label{skew->cw}
-  Let $\phi\colon\gA\to\gB$ be a skew bifibration, and let $A$ and $B$
+  Let $\gA$ and $\gB$ be fographs, let $\phi\colon\gA\to\gB$ be a skew bifibration, and let $A$ and $B$
   be formulas with $\graphof A=\gA$ and $\graphof B=\gB$. Then there
-  is a derivation $\vlderivation{
-    \vlde{\set{\wlD,\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
-      \vlhy{A}}}$ with $\mapof\Deri=\phi$.
+  are derivations
+  \begin{equation*}
+    \vlderivation{
+      \vlde{\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{B}{
+        \vlhy{A}}}
+    \quand
+    \vlderivation{
+      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
+        \vlhy{A\substof\phi}}}
+  \end{equation*}
+  such that $\mapof{\rectif\Deri}=\phi$ and $\rectif{\Deri}$ is a
+  rectification of $\Deri$, and $\substof\phi$ is the substitution
+  induced by $\phi$.
 \end{lemma}
@@
   $\phi$, and let $\gB_1$ be the subgraph of $\gB$ induced by
-  $\vB'$. Now let $\PE B_1$ be the propositional formula obtained from
+  $\vB'$. Hence, we have two maps
+  $\phi''\colon\gA\to\gB_1$ being a surjection and $\phi'\colon
+  \gB_1\to\gB$ being an injection that reflects edges. Both, $\phi'$
+  and $\phi''$ remain skew bifibrations. Let us first look at $\phi'$.
+  Let $\PE B_1$ be the propositional formula obtained from
   $\PE B$ by removing all atoms that are not represented by vertices
-  in $\vB'$. Then $\graphof{\PE B_1}=\gB_1$. Furthermore, the map
-  $\phi'\colon \gB_1\to\gB$ is an injection that reflects
-  edges. Hence, by \cite[Proposition~7.6.1]{str:07:RTA}, we
-  have a derivation
-  $\vlder{\set{\wlD,\wrD}}{\PE\Deri_1}{\PE B}{\PE B_1}$. \todo{show that we have $B_1$ with $\graphof{B_1}=\gB_1$, so that we can can get
-  first order derivation $\vlder{\set{\wlD,\wrD}}{\Deri_1}{B}{B_1}$.}
-
-  Now, let $\sigma$ be the substitution induced by $\phi$, and let
-  $\gA_1=\gA\sigma$ be the graph obtained from $\gA$ by applying
-  $\sigma$ to all the labels. Note that $\gA_1$ is not neccesarily a
-  fograph, as binders might be illegal. But it still is a cograph, and
-  we have a surjective skew fibration $\phi''\colon\gA_1\to\gB_1$ that
-  preserves the labels. Therefore, by
+  in $\vB'$. Then $\graphof{\PE B_1}=\gB_1$. 
+  By \cite[Proposition~7.6.1]{str:07:RTA}, we have a derivation
+  $\vlder{\set{\wrD,\fequ}}{\PE\Deri_1}{\PE B}{\PE B_1}$.  A
+  subformula of $\PE B$ is called \emph{weak} if it has been
+  introduced by a weakening. All subformulas of a weak formula are
+  also weak. Two weak subformulas $B'$ and $B''$ of $\PE B$ form a
+  \emph{weak pair} if $B\fequ\Scons{B'\vlor B''}$ for some context
+  $\Sconhole$. We now can assume without loss of generality that
+  whenever weak subformulas $B'$ and $B''$ for a weak pair, they have
+  been introduced by the same instance of $\wlD$ or $\wrD$ in
+  $\PE\Deri_1$.\footnote{If $\PE\Deri_1$ is not of that shape, it can
+  brought into this form by simple rule permutations, and then
+  collapsing several weakenings into a single one.}  Now observe that
+  whenever a weakening in $\PE\Deri_1$ deletes an atom $x\in\VAR$, it
+  must also delete all atoms in the scope of the corresponding
+  quantifier, because $\phi$ is a fibration on the binding
+  graph. Hence, each line in $\PE\Deri_1$ is the propositional
+  encoding $\PE P$ of a first-order formula $P$. Thus we have a first
+  order derivation $\vlder{\set{\wrD,\fequ}}{\Deri_1}{B}{B_1}$. we now
+  have to show that each instance of $\wlD$ or $\wrD$ is indeed a
+  correct application in first-order logic. For this we have to
+  inspect the cases a weakening happens inside a subformula $x\vlor C$
+  or $x\vlan C$ in $\PE\Deri_1$. There are the following cases:
+  \begin{equation*}%\small
+    \vlinf{}{}{S\cons{x\vlor D\vlor C}}{S\cons{x\vlor C}}
+    \qquad
+    \vlinf{}{}{S\cons{x\vlan (D\vlor C)}}{S\cons{x\vlan C}}
+    \qquad
+    \vlinf{}{}{S\cons{(x\vlor D)\vlan C}}{S\cons{x\vlan C}}
+  \end{equation*}
+  In the first case the weakening happens inside the scope of a
+  $\forall$-quantifier, and in the second case inside the scope of a
+  $\exists$-quantifier. Both cases are unproblematic in first-order
+  logic. However, in the third case an $\exists$-quantifier would be
+  transformed into an $\forall$-quantifier. But as $\phi$ has to
+  preserve existentials, this third case cannot occur, and therefore
+  $\Deri_1$ is a valid first-order derivation in $\set{\wD,\fequ}$.
+
+  Let us now look at $\phi''$. Let $\gA_1=\gA\substof\phi$ be the
+  graph obtained from $\gA$ by applying $\substof\phi$ to all the
+  labels. Note that $\gA_1$ is not neccesarily a fograph, as binders
+  might be illegal. But it still is a cograph, and we have a
+  surjective skew fibration $\phi''\colon\gA_1\to\gB_1$ that preserves
+  the labels. Therefore, by
   \cite[Proposition~7.5]{str:ral:tableaux19}, there is a derivation
   $\vlder{\set{\acD,\me,\PE\fequ}}{\PE\Deri_2}{\PE B_1}{\PE A_1}$,
-  where $\PE A_1 =\PE A\sigma$ is the result of applying $\sigma$
-  to~$\PE A$. To $\Deri_2$ we can apply a permutation argument,
+  where $\PE A_1 =\PE A\substof\phi$ is the result of applying $\substof\phi$
+  to~$\PE A$. Note that $\PE A_1 = \PE{(A\substof\phi)}$. To $\Deri_2$ we can apply a permutation argument,
   permuting all instances of $\acD$ up until they either reach the top
   of the derivation or an instance of $\me$ which separates the two
-  atoms in the premise. More precisely, we consider the following inferene rule
+  atoms in the premise. More precisely, we consider the following
+  inferene rule
   \begin{equation}
@@
   \begin{equation}
+    \label{eq:mac}
     \vlderivation{
@@
   \end{equation}
-  Now we translate 
+  Now we translate $\PE\Deri_2$ into a first-order derivation
+  $\vlder{\set{\acD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{B_1}{A\substof\phi}$
+  by ``decoding'' every line in $\PE\Deri_2$. I.e., for each line $Q$
+  in $\PE\Deri_2$ we construct a formula $P$ with $\PE P\fequ Q$.  We
+  proceed by induction on the height of $\PE\Deri_2$, beginning at the
+  bottom.
+We already constructed the formula~$B_1$.
+Now consider the bottommost rule in $\PE\Deri_2$.
+If it is a $\fequ$, then we trivially can go to the next step.
+If it is a $\acD$ duplicating an atom that is not a $x\in\VAR$, then this $\acD$ is also a valid inference step in the first-order system.
+Similarly, any instance of $\me$ that is not in a situation as in~\eqref{eq:mac} can be i
 \end{proof}

### 2021-01-18 main.tex
abstract

@@
   the two proof representations are related via a deep inference
-  decomposition theorem that establishes a certain kind of normal form
+  decomposition theorem that establishes a new kind of normal form
   of syntactic proofs. As a consequence, we obtain (i) a simple proof

### 2021-01-18 main.tex
still in IX

@@
 \newcommand{\Deri}{\Phi}
+\newcommand{\DDeri}{\Psi}
 \newcommand{\Proof}{\Pi}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{From Contraction and Weakening to Skew Bifibrations}
@@
 \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{From Skew Bifibrations to Contraction and Weakening}
@@
 \begin{lemma}\label{skew->cw}
-  Let $\gA$ and $\gB$ be fographs, let $\phi\colon\gA\to\gB$ be a skew bifibration, and let $A$ and $B$
-  be formulas with $\graphof A=\gA$ and $\graphof B=\gB$. Then there
-  are derivations
+  Let $\gA$ and $\gB$ be fographs, let $\phi\colon\gA\to\gB$ be a skew
+  bifibration, and let $A$ and $B$ be formulas with $\graphof A=\gA$
+  and $\graphof B=\gB$. Then there are derivations
   \begin{equation*}
@@
 
-\begin{proof}
+In the proof of this lemma, we make use of the following concept: Let
+$\vlder{\sysS}{\DDeri}{Q}{P}$ be a derivation where $Q=\PE D$ is the
+propostional encoding of some formula~$D$. We say that $\DDeri$ can be
+\bfit{lifted} to $\sysS'$ if there is a formula $C$ such that
+$P\fequ\PE C$ and there is a derivation
+$\vlder{\sysS'}{\DDeri'}{D}{C}$.
+
+\begin{proof}[Proof of Lemma~\ref{skew->cw}]
   By Lemma~\ref{lem:PE} we have $\gA=\graphof{\PE A}$ and
@@
   $\phi$, and let $\gB_1$ be the subgraph of $\gB$ induced by
-  $\vB'$. Hence, we have two maps
-  $\phi''\colon\gA\to\gB_1$ being a surjection and $\phi'\colon
-  \gB_1\to\gB$ being an injection that reflects edges. Both, $\phi'$
-  and $\phi''$ remain skew bifibrations. Let us first look at $\phi'$.
-  Let $\PE B_1$ be the propositional formula obtained from
-  $\PE B$ by removing all atoms that are not represented by vertices
-  in $\vB'$. Then $\graphof{\PE B_1}=\gB_1$. 
-  By \cite[Proposition~7.6.1]{str:07:RTA}, we have a derivation
-  $\vlder{\set{\wrD,\fequ}}{\PE\Deri_1}{\PE B}{\PE B_1}$.  A
-  subformula of $\PE B$ is called \emph{weak} if it has been
+  $\vB'$. Hence, we have two maps $\phi''\colon\gA\to\gB_1$ being a
+  surjection and $\phi'\colon \gB_1\to\gB$ being an injection that
+  reflects edges. Both, $\phi'$ and $\phi''$ remain skew
+  bifibrations. Let us first look at $\phi'$.  Let $\PE B_1$ be the
+  propositional formula obtained from $\PE B$ by removing all atoms
+  that are not represented by vertices in $\vB'$. Then $\graphof{\PE
+    B_1}=\gB_1$.  By \cite[Proposition~7.6.1]{str:07:RTA}, we have a
+  derivation $\vlder{\set{\wrD,\fequ}}{\PE\Deri_1}{\PE B}{\PE B_1}$.
+  A subformula of $\PE B$ is called \emph{weak} if it has been
   introduced by a weakening. All subformulas of a weak formula are
@@
   brought into this form by simple rule permutations, and then
-  collapsing several weakenings into a single one.}  Now observe that
-  whenever a weakening in $\PE\Deri_1$ deletes an atom $x\in\VAR$, it
-  must also delete all atoms in the scope of the corresponding
-  quantifier, because $\phi$ is a fibration on the binding
-  graph. Hence, each line in $\PE\Deri_1$ is the propositional
-  encoding $\PE P$ of a first-order formula $P$. Thus we have a first
-  order derivation $\vlder{\set{\wrD,\fequ}}{\Deri_1}{B}{B_1}$. we now
-  have to show that each instance of $\wlD$ or $\wrD$ is indeed a
-  correct application in first-order logic. For this we have to
-  inspect the cases a weakening happens inside a subformula $x\vlor C$
-  or $x\vlan C$ in $\PE\Deri_1$. There are the following cases:
+  collapsing several weakenings into a single one.}  Now we show that
+  $\PE\Deri_1$ can be lifted. For this, observe that whenever a
+  weakening in $\PE\Deri_1$ deletes an atom $x\in\VAR$, it must also
+  delete all atoms in the scope of the corresponding quantifier,
+  because $\phi$ is a fibration on the binding graph. Hence, each line
+  in $\PE\Deri_1$ is the propositional encoding $\PE P$ of a
+  first-order formula $P$.  We now have to show
+  that each instance of $\wrD$ is indeed a correct
+  application in first-order logic. For this we have to inspect the
+  cases a weakening happens inside a subformula $x\vlor C$ or $x\vlan
+  C$ in $\PE\Deri_1$. There are the following cases:
   \begin{equation*}%\small
@@
   transformed into an $\forall$-quantifier. But as $\phi$ has to
-  preserve existentials, this third case cannot occur, and therefore
-  $\Deri_1$ is a valid first-order derivation in $\set{\wD,\fequ}$.
+  preserve existentials, this third case cannot occur.
+  Thus we have a first order derivation
+  $\vlder{\set{\wrD,\fequ}}{\Deri_1}{B}{B_1}$.
 
@@
   to~$\PE A$. Note that $\PE A_1 = \PE{(A\substof\phi)}$. To $\Deri_2$ we can apply a permutation argument,
-  permuting all instances of $\acD$ up until they either reach the top
+  permuting all instances of $\acD$, that duplicate an atom $x\in\VAR$, up until they either reach the top
   of the derivation or an instance of $\me$ which separates the two
@@
   \begin{equation}
-    \vlinf{\acDeq}{}{\Scons{a}}{S_0\cons{S_1\cons{a}\vlor S_2\cons{a}}}
+    \vlinf{\acDeq}{}{\Scons{x}}{S_0\cons{S_1\cons{x}\vlor S_2\cons{x}}}
   \end{equation}
@@
   $S_2\conhole\fequ\conhole\vlor F$ and $S\conhole\fequ
-  S_0\cons{\conhole\vlor E\vlor F}$ for some formulas $E$ and $F$. The
-  rule $\acDeq$ permutes over $\fequ$ and other instances of $\acDeq$,
+  S_0\cons{\conhole\vlor E\vlor F}$ for some formulas $E$ and $F$, where $E$ or $F$ or both might be empty. The
+  rule $\acDeq$ permutes over $\fequ$, $\acD$, and other instances of $\acDeq$,
   and over instances of $\me$ if they occur inside $S_0$ or $S_1$ or
@@
     \vlderivation{
-      \vlin{\acDeq}{}{\Scons{R\cons{a}\vlan(C\vlor D)}}{
-        \vlin{\me}{}{\Scons{(R_1\cons{a}\vlor R_2\cons{a})\vlan(C\vlor D)}}{
-          \vlhy{\Scons{(R_1\cons{a}\vlan C)\vlor (R_2\cons{a}\vlor D)}}}}}
+      \vlin{\acDeq}{}{\Scons{R\cons{x}\vlan(C\vlor D)}}{
+        \vlin{\me}{}{\Scons{(R_1\cons{x}\vlor R_2\cons{x})\vlan(C\vlor D)}}{
+          \vlhy{\Scons{(R_1\cons{x}\vlan C)\vlor (R_2\cons{x}\vlor D)}}}}}
   \end{equation}
-  Now we translate $\PE\Deri_2$ into a first-order derivation
-  $\vlder{\set{\acD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{B_1}{A\substof\phi}$
-  by ``decoding'' every line in $\PE\Deri_2$. I.e., for each line $Q$
-  in $\PE\Deri_2$ we construct a formula $P$ with $\PE P\fequ Q$.  We
-  proceed by induction on the height of $\PE\Deri_2$, beginning at the
-  bottom.
-We already constructed the formula~$B_1$.
-Now consider the bottommost rule in $\PE\Deri_2$.
-If it is a $\fequ$, then we trivially can go to the next step.
-If it is a $\acD$ duplicating an atom that is not a $x\in\VAR$, then this $\acD$ is also a valid inference step in the first-order system.
-Similarly, any instance of $\me$ that is not in a situation as in~\eqref{eq:mac} can be i
-\end{proof}
+  Now we show that $\PE\Deri_2$ can be lifted to
+  $\set{\acD,\me,\mfaD,\mexD,\fequ}$.  We proceed by induction on the
+  height of $\PE\Deri_2$, beginning at the bottom, as we already
+  constructed the formula~$B_1$.  Every instance of $\fequ$ or $\acD$
+  (duplicating an atom that is not a $x\in\VAR$), can trivially be
+  lifted. Similarly, an instance of $\me$, that is above an instance
+  of $\acDeq$ as indicated in~\eqref{eq:mac}, can be lifted as the
+  premise must also be a proposional encoding and the $\me$-inference
+  remains correct in the first-order case.  It remains to consider a
+  situation~\eqref{eq:mac}. Observe that we must have
+  $R_1\cons{x}\fequ x\vlor E$ for some $E$ and $R_2\cons{x}\fequ
+  x\vlor F$ for some $F$ with $R\cons{x}\fequ x\vlor E\vlor
+  F$. Otherwise, the application of $\acDeq$ would not be correct.
+  We have the following four cases: 
+  \begin{itemize}
+  \item   $E$ and $F$ are both empty: Then~\eqref{eq:mac} is
+    \begin{equation*}
+    \vlderivation{
+      \vlin{\acDeq}{}{\Scons{x\vlan(C\vlor D)}}{
+        \vlin{\me}{}{\Scons{(x\vlor x)\vlan(C\vlor D)}}{
+          \vlhy{\Scons{(x\vlan C)\vlor (x\vlor D)}}}}}
+    \end{equation*}
+    which can be lifted immediately to
+    \begin{equation*}
+      \vlinf{\mexD}{}{\Scons{\exists x.(C\vlor D)}}{\Scons{(\exists x.C)\vlor(\exists x.D)}}
+    \end{equation*}
+  \item $E$ and $F$ are both non-empty: Then~\eqref{eq:mac} is (modulo
+    omitted applications of $\fequ$):
+    \begin{equation*}
+    \vlderivation{
+      \vlin{\acDeq}{}{\Scons{(x\vlor E\vlor F)\vlan(C\vlor D)}}{
+        \vlin{\me}{}{\Scons{((x\vlor E)\vlor (x\vlor F))\vlan(C\vlor D)}}{
+          \vlhy{\Scons{((x\vlor E)\vlan C)\vlor ((x\vlor F)\vlor D)}}}}}
+    \end{equation*}
+    which can be lifted to
+    \begin{equation*}
+    \vlderivation{
+      \vlin{\mfaD}{}{\Scons{(\forall x.(E\vlor F))\vlan(C\vlor D)}}{
+        \vlin{\me}{}{\Scons{((\forall x. E)\vlor (\forall x. F))\vlan(C\vlor D)}}{
+          \vlhy{\Scons{((\forall x. E)\vlan C)\vlor ((\forall x. F)\vlor D)}}}}}
+    \end{equation*}
+  \item $E$ is empty and $F$ is not: Then~\eqref{eq:mac} becomes
+    \begin{equation*}
+    \vlderivation{
+      \vlin{\acDeq}{}{\Scons{(x\vlor F)\vlan(C\vlor D)}}{
+        \vlin{\me}{}{\Scons{(x\vlor (x\vlor F))\vlan(C\vlor D)}}{
+          \vlhy{\Scons{(x\vlan C)\vlor ((x\vlor F)\vlor D)}}}}}
+    \end{equation*}
+    The conclusion is the propositional encoding of $\Scons{(\forall
+      x. F)\vlan(C\vlor D)}$ and the premise is the propositional
+    encoding of $\Scons{(\exists x.C)\vlor ((\forall x. F)\vlor
+      D)}$. Also note that no $\me$-instance can break up the
+    conjunction in $x\vlan C$ in the premise. Hence, $\phi$ maps an
+    existential to a universal, which is ruled out by the
+    definition. Hence, this case cannot occur.
+  \item $E$ is non-empty and $F$ is empty: This case is similar to the
+    previous one.
+  \end{itemize}
+  Finally, we need to consider the instances of $\acDeq$ that are at the top of the derivation.
+\end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-18 main.tex
cfaD
Comments on IX.A

@@
 \newcommand\acDeq {\mathsf{ac}^\fequ}
+\newcommand\cfaD {\mathsf{c_\forall}}
 \newcommand\mfaD {\mathsf{m_\forall}}
@@
         \vlinf{\acD}{}{\Scons{a}}{\Scons{a\vlor a}}
+        \qquad
+        \vlinf{\cfaD}{}{\Scons{\forall x. A}}{\Scons{\forall x.\forall x.A}}
       \end{array}
@@
 
-In this section we establish the relation between ske bifibrations and derivations  in
+\todo{add $\cfaD$ everywhere}
+
+In this section we establish the relation between skew bifibrations and derivations  in
 $\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}$. However, 
@@
 this reason we define here rectified versions $\rectif\mfaD$ and
-$\rectif\mexD$, show below:
+$\rectif\mexD$, shown below:
 \begin{equation*}
@@
 \end{equation*}
+\todo{same for $\cfaD$}
 Here, we use the notation $A\cdot$ for a formula $A$ with occurrences
@@
 $\set{\wlD,\wrD,\acD,\me,\mfaD,\mexD,\fequ}$, we can now construct the
-\bfit{recification} $\rectif\Deri$ by rectifying each line of $\Deri$, yielding a derivation in 
+\bfit{rectification} $\rectif\Deri$ by rectifying each line of $\Deri$, yielding
+a derivation in
 $\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$.
@@
 the \bfit{induced map} $\mapof\Deri$ as the composition of the induced
-maps of the rule instances in $\Deri$.
+maps of the rule instances in $\Deri$. \juihsuan{maybe mention at least that the induced
+maps define graph homomorphisms. Do we need to talk about the contexts
+$\Sconhole$ here (induced maps act clearly as the identity on contexts but we need them for the composition)?}
 
@@
     \vlde{\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
-      \vlhy{A}}}$ be a recified derivation. Then the induced map
+      \vlhy{A}}}$ be a rectified derivation. Then the induced map
   $\mapof\Deri\colon\graphof{A}\to\graphof{B}$ is a skew bifibration.
@@
 concept: the \bfit{propositional encoding} $\PE{A}$ of a formula $A$,
-which is a proposional formula with the property that $\graphof{\PE
+which is a propositional formula with the property that $\graphof{\PE
   A}=\graphof{A}$. For this, we introduce new propositional variables
@@
   First, observe that for every inference rule
-  $\rr\in\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we
+  $\rr\in\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$
   the induced map $\mapof{\rr}\colon\vgraphof Q\to\vgraphof P$ defines
-  a fibration on the corresponding binding graphs. Therefore, their
+  a fibration on the corresponding binding graphs. \juihsuan{we may need to have
+some explication here.} Therefore, their
   composition $\mapof\Deri$ is a fibration.
@@
   $\Deri$ its propositional encoding $\PE\Deri$ by
-  translating every line into its proposional encoding. The instances
-  of the rules $\rectif\mfaD$ and $\rectif\mexD$ are replaced two
+  translating every line into its propositional encoding.
+  \juihsuan{maybe mention that an instance of one of the other rules can be translated
+into an instance of the same rule. It's trivial but may be worth mentioning.}
+  The instances
+  of the rules $\rectif\mfaD$ and $\rectif\mexD$ are replaced in two
   steps by:
@@
   respectively, where $\rectif\acD$ is a $\acD$ that renames the
-  variabes---the atom variable, as well as the first-order variable of
-  the same name---as everything is recified, there is no ambiguity
+  variables---the atom variable
+  \juihsuan{or propositional variable? maybe use just a single name}, as well as the first-order variable of
+  the same name---as everything is rectified, there is no ambiguity
   here.
@@
   of $\acDeq$ as indicated in~\eqref{eq:mac}, can be lifted as the
-  premise must also be a proposional encoding and the $\me$-inference
+  premise must also be a propositional encoding and the $\me$-inference
   remains correct in the first-order case.  It remains to consider a

### 2021-01-18 main.tex
First comments on IX.B

@@
   surjection and $\phi'\colon \gB_1\to\gB$ being an injection that
-  reflects edges. Both, $\phi'$ and $\phi''$ remain skew
+  reflects edges. \juihsuan{what do you mean by "reflect edges"?} Both, $\phi'$ and $\phi''$ remain skew
   bifibrations. Let us first look at $\phi'$.  Let $\PE B_1$ be the
@@
   whenever weak subformulas $B'$ and $B''$ for a weak pair, they have
-  been introduced by the same instance of $\wlD$ or $\wrD$ in
+  been introduced by the same instance of $\wrD$ in
   $\PE\Deri_1$.\footnote{If $\PE\Deri_1$ is not of that shape, it can
@@
   delete all atoms in the scope of the corresponding quantifier,
-  because $\phi$ is a fibration on the binding graph. Hence, each line
+  because $\phi$ \juihsuan{should be $\phi'$ here} is a fibration on the binding graph. Hence, each line
   in $\PE\Deri_1$ is the propositional encoding $\PE P$ of a
@@
   $\vlder{\set{\wrD,\fequ}}{\Deri_1}{B}{B_1}$.
-
+  \juihsuan{$B_1$ is not defined (The notation $\PE B_1$ suggests that it is the
+propositional encoding of some formula but we need to prove it). This can be
+proven using the fact that $\phi'$ is a skew bifibration here.}
   Let us now look at $\phi''$. Let $\gA_1=\gA\substof\phi$ be the
@@
   atoms in the premise. More precisely, we consider the following
-  inferene rule
+  inference rule
   \begin{equation}

### 2021-01-18 main.tex
done with IX

--- 2021-01-18 main.tex
@@
 \renewcommand\acD {\mathsf{ac}}
-\newcommand\acDeq {\mathsf{ac}^\fequ}
+\newcommand\acDx {\mathsf{ac}_x}
+\newcommand\acDeq {\mathsf{ac}_x^\fequ}
+\newcommand\cfaD {\mathsf{c_\forall}}
 \newcommand\mfaD {\mathsf{m_\forall}}
@@
 \newcommand{\PE}[1]{#1^\circ}
+\newcommand{\PEp}[1]{\tilde{#1}}
 
@@
 
+\todo{add $\cfaD$ everywhere}
+
 In this section we establish the relation between ske bifibrations and derivations  in
@@
   Let $\vlderivation{
-    \vlde{\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
+    \vlde{\set{\wrD,\acD,\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
       \vlhy{A}}}$ be a recified derivation. Then the induced map
@@
   First, observe that for every inference rule
-  $\rr\in\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we
+  $\rr\in\set{\wrD,\acD,\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we
   the induced map $\mapof{\rr}\colon\vgraphof Q\to\vgraphof P$ defines
@@
     \vlderivation{
-      \vlin{\rectif\acD}{}{\Scons{x\vlor(\PE{(Ax)}\vlor\PE{(Bx))}}}{
+      \vlin{\rectif\acD}{}{\Scons{x\vlor(\PE{(Ax)}\vlor\PE{(Bx)})}}{
         \vlin{\fequ}{}{\Scons{(y\vlor z)\vlor(\PE{(Ay)}\vlor\PE{(Bz)})}}{
@@
     \vlderivation{
-      \vlin{\rectif\acD}{}{\Scons{x\vlan\PE{(Ax)}\vlor\PE{(Bx)}}}{
+      \vlin{\rectif\acD}{}{\Scons{x\vlan(\PE{(Ax)}\vlor\PE{(Bx)})}}{
         \vlin{\me}{}{\Scons{(y\vlor z)\vlan(\PE{(Ay)}\vlor\PE{(Bz)})}}{
@@
   the same name---as everything is recified, there is no ambiguity
-  here.
-  This gives us a derivation $\vlderivation{
-    \vlde{\set{\wrD,\acD,\rectif\acD,\me,\PE\fequ}}{\PE\Deri}{\PE
-      B}{ \vlhy{\PE A}}}$ such that  $\mapof{\PE\Deri}=\mapof\Deri$. It has been
-  shown in~\cite{str:07:RTA} that $\mapof{\PE\Deri}$ is a skew
+  here.  This gives us a derivation $\vlderivation{
+    \vlde{\set{\wrD,\acD,\rectif\acD,\me,\PE\fequ}}{\PE\Deri}{\PE B}{
+      \vlhy{\PE A}}}$ such that $\mapof{\PE\Deri}=\mapof\Deri$. It has
+  been shown in~\cite{str:07:RTA} that $\mapof{\PE\Deri}$ is a skew
   fibration (see
   also~\cite{hughes:invar,str:ral:tableaux19,str:RR-9048}). Hence,
-  $\mapof\Deri$ is a skew fibration.
+  $\mapof\Deri$ is a skew fibration. That $\mapof{\PE\Deri}$ preserves
+  exponentials follows immediately from its construction.
 \end{proof}
@@
 In the proof of this lemma, we make use of the following concept: Let
-$\vlder{\sysS}{\DDeri}{Q}{P}$ be a derivation where $Q=\PE D$ is the
-propostional encoding of some formula~$D$. We say that $\DDeri$ can be
-\bfit{lifted} to $\sysS'$ if there is a formula $C$ such that
-$P\fequ\PE C$ and there is a derivation
-$\vlder{\sysS'}{\DDeri'}{D}{C}$.
+$\vlder{\sysS}{\DDeri}{Q}{P}$ be a derivation where $P$ and $Q$ are
+propositional formulas (possibly using variable $x\in\VAR$ at the
+places of atoms).  We say that $\DDeri$ can be \bfit{lifted} to
+$\sysS'$ if there are (first-order) formulas $C$ and $D$ such that $P=\PE C$ and
+$Q=\PE D$ and there is a derivation $\vlder{\sysS'}{\DDeri'}{D}{C}$.
 
@@
   reflects edges. Both, $\phi'$ and $\phi''$ remain skew
-  bifibrations. Let us first look at $\phi'$.  Let $\PE B_1$ be the
+  bifibrations. Let us first look at $\phi'$.  Let $\PEp B_1$ be the
   propositional formula obtained from $\PE B$ by removing all atoms
-  that are not represented by vertices in $\vB'$. Then $\graphof{\PE
+  that are not represented by vertices in $\vB'$. Then $\graphof{\PEp
     B_1}=\gB_1$.  By \cite[Proposition~7.6.1]{str:07:RTA}, we have a
-  derivation $\vlder{\set{\wrD,\fequ}}{\PE\Deri_1}{\PE B}{\PE B_1}$.
+  derivation $\vlder{\set{\wrD,\fequ}}{\PE\Deri_1}{\PE B}{\PEp B_1}$.
   A subformula of $\PE B$ is called \emph{weak} if it has been
@@
   Thus we have a first order derivation
-  $\vlder{\set{\wrD,\fequ}}{\Deri_1}{B}{B_1}$.
+  $\vlder{\set{\wrD,\fequ}}{\Deri_1}{B}{B_1}$ with $\PE B_1=\PEp B_1$.
 
@@
   $\vlder{\set{\acD,\me,\PE\fequ}}{\PE\Deri_2}{\PE B_1}{\PE A_1}$,
-  where $\PE A_1 =\PE A\substof\phi$ is the result of applying $\substof\phi$
-  to~$\PE A$. Note that $\PE A_1 = \PE{(A\substof\phi)}$. To $\Deri_2$ we can apply a permutation argument,
-  permuting all instances of $\acD$, that duplicate an atom $x\in\VAR$, up until they either reach the top
-  of the derivation or an instance of $\me$ which separates the two
-  atoms in the premise. More precisely, we consider the following
-  inferene rule
+  where $\PE A_1 =\PE A\substof\phi$ is the result of applying
+  $\substof\phi$ to~$\PE A$. Note that $\PE A_1 =
+  \PE{(A\substof\phi)}$ and $\PE B_1$ are both proposional
+  encodings. We plan to show that $\Deri_2$ can be lifted to
+  $\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$. However, observe that not
+  every formula occurring in $\Deri_2$ is a propositional
+  encoding. There are two reasons for this: (i) we might have $P\PE\fequ
+  Q$ where $P$ is a propositional encoding but $Q$ is not, and (ii)
+  the rule $\acD$ can duplicate an atom with name $x\in\VAR$. Let us write $\acDx$ for such instances. To
+  address (i), we consider here formulas equivalent modulo $\fequ$,
+  always knowing that we can add instances of $\fequ$ as needed. To
+  address (ii), we apply a permutation argument, permuting all
+  instances of $\acDx$ up until
+  they either reach the top of the derivation or an instance of $\me$
+  which separates the two atoms in the premise. More precisely, we
+  consider the following inferene rule
   \begin{equation}
+    \label{eq:acDeq}
     \vlinf{\acDeq}{}{\Scons{x}}{S_0\cons{S_1\cons{x}\vlor S_2\cons{x}}}
@@
   \end{equation}
-  Now we show that $\PE\Deri_2$ can be lifted to
-  $\set{\acD,\me,\mfaD,\mexD,\fequ}$.  We proceed by induction on the
-  height of $\PE\Deri_2$, beginning at the bottom, as we already
-  constructed the formula~$B_1$.  Every instance of $\fequ$ or $\acD$
-  (duplicating an atom that is not a $x\in\VAR$), can trivially be
-  lifted. Similarly, an instance of $\me$, that is above an instance
-  of $\acDeq$ as indicated in~\eqref{eq:mac}, can be lifted as the
-  premise must also be a proposional encoding and the $\me$-inference
-  remains correct in the first-order case.  It remains to consider a
-  situation~\eqref{eq:mac}. Observe that we must have
+  We can therefore assume that all instances of $\acDx$, that contract
+  an atom $x\in\VAR$ are either at the top of $\PE\Deri_2$ or below a
+  $\me$-instance as in~\eqref{eq:mac}. We now lift $\PE\Deri_2$ to
+  $\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$, proceed by induction on
+  the height of $\PE\Deri_2$, beginning at the top, making a case
+  analysis on the topmost rule that is not a $\fequ$.
+  \begin{itemize}
+  \item $\acDx$: We know that the premisse of~\eqref{eq:acDeq} is a
+    propositional encoding. Hence, $S_1\conhole=\conhole\vlor E$ and
+    $S_2\conhole=\conhole\vlor F$ and both $x$ are universals, and
+    $E\vlor F$ contains all occurrences of $x$ bound by that
+    universal. We have the following subcases:
+    \begin{itemize}
+    \item $E$ and $F$ are both non-empty: We have
+      \begin{equation*}
+        \vlinf{\acDeq}{}{\Scons{x\vlor (E\vlor F)}}{S\cons{(x\vlor E)\vlor (x\vlor F)}}
+      \end{equation*}
+      which can be lifted to
+      \begin{equation*}
+        \vlinf{\mfaD}{}{\Scons{\forall x.(E\vlor F)}}{S\cons{(\forall x.E)\vlor (\forall x.F)}}
+      \end{equation*}
+    \item $E$ is empty and $F$ is non-empty: We have
+      \begin{equation*}
+        \vlinf{\acDeq}{}{\Scons{x\vlor F)}}{S\cons{x\vlor (x\vlor F)}}
+      \end{equation*}
+      which can be lifted to
+      \begin{equation*}
+        \vlinf{\mfaD}{}{\Scons{\forall x.F}}{S\cons{\forall x.\forall x.F}}
+      \end{equation*}
+    \item $E$ is non-empty and $F$ is empty: This is similar to the previous case.
+    \item $E$ and $F$ are both empty: This is impossible as the
+      premise would not be a propositional encoding.
+    \end{itemize}
+  \item $\acD$ (contracting an ordinary atom): This can trivially be lifted.
+  \item $\me$ that is not in the situation of~\eqref{eq:mac}: Then now
+    encoding of a quantifier is affected and the instance of $\me$ can
+    be lifted.
+  \item $\me/\acDx$ as in situation~\eqref{eq:mac}: We must have
     $R_1\cons{x}\fequ x\vlor E$ for some $E$ and $R_2\cons{x}\fequ
@@
     \begin{itemize}
-  \item   $E$ and $F$ are both empty: Then~\eqref{eq:mac} is
-    \begin{equation*}
-    \vlderivation{
-      \vlin{\acDeq}{}{\Scons{x\vlan(C\vlor D)}}{
-        \vlin{\me}{}{\Scons{(x\vlor x)\vlan(C\vlor D)}}{
-          \vlhy{\Scons{(x\vlan C)\vlor (x\vlor D)}}}}}
-    \end{equation*}
-    which can be lifted immediately to
-    \begin{equation*}
-      \vlinf{\mexD}{}{\Scons{\exists x.(C\vlor D)}}{\Scons{(\exists x.C)\vlor(\exists x.D)}}
-    \end{equation*}
     \item $E$ and $F$ are both non-empty: Then~\eqref{eq:mac} is (modulo
@@
     \item $E$ is non-empty and $F$ is empty: This case is similar to the
-    previous one.
+      previous subcase.
+    \item   $E$ and $F$ are both empty: Then~\eqref{eq:mac} is
+      \begin{equation*}
+        \vlderivation{
+          \vlin{\acDeq}{}{\Scons{x\vlan(C\vlor D)}}{
+            \vlin{\me}{}{\Scons{(x\vlor x)\vlan(C\vlor D)}}{
+              \vlhy{\Scons{(x\vlan C)\vlor (x\vlor D)}}}}}
+      \end{equation*}
+      which can be lifted immediately to
+      \begin{equation*}
+        \vlinf{\mexD}{}{\Scons{\exists x.(C\vlor D)}}{\Scons{(\exists x.C)\vlor(\exists x.D)}}
+      \end{equation*}
     \end{itemize}
-  Finally, we need to consider the instances of $\acDeq$ that are at the top of the derivation.
+  \end{itemize}
+  Thus $\PE\Deri_2$ can be lifted to
+  $\vlder{\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{B_1}{A\substof\phi}$. We
+  construct $\Deri$ by composing $\Deri_2$ and $\Deri_1$. Then
+  $\rectif\Deri$ can be constructed by rectifying $\Deri$, where the
+  variables to be used in $A$ are already given. That
+  $\phi=\mapof{\rectif\Deri}$ follows immediately from the
+  construction.
 \end{proof}

### 2021-01-18 main.tex
tiny changes

--- 2021-01-18 main.tex
@@
     \vlin{\cD}{}{(A \vlor B) \vlan (C \vlor D)}{
-      \vlin{\wlD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((A \vlor B) \vlan (C \vlor D))}{
-	\vlin{\wlD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((A \vlor B) \vlan D))}{
+      \vlin{\fequ}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((A \vlor B) \vlan (C \vlor D))}{
+      \vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((B \vlor A) \vlan (D \vlor C))}{
+	\vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((B \vlor A) \vlan D))}{
 	  \vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor (B \vlan D))}{
 	    \vlin{\wrD}{}{((A \vlor B) \vlan C) \vlor (B \vlan D)}{
-	      \vlhy{(A \vlan C) \vlor (B \vlan D)}}}}}}}
+	      \vlhy{(A \vlan C) \vlor (B \vlan D)}}}}}}}}
   $$.
@@
     \vlin{\cD}{}{\exists x.(A \vlor B)}{
-      \vlin{\wlD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.(A \vlor B))}{
+      \vlin{\fequ}{}{\exists x.(A \vlor B)) \vlor (\exists x.(A \vlor B))}{
+      \vlin{\wrD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.(B \vlor A))}{
 	\vlin{\wrD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.B)}{
-	  \vlhy{(\exists x.A) \vlor (\exists x.B)}}}}}
+	  \vlhy{(\exists x.A) \vlor (\exists x.B)}}}}}}
   $$.
@@
     \vlin{\cD}{}{\forall x.(A \vlor B)}{
-      \vlin{\wlD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.(A \vlor B))}{
+      \vlin{\fequ}{}{(\forall x.(A \vlor B)) \vlor (\forall x.(A \vlor B))}{
+      \vlin{\wrD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.(B \vlor A))}{
 	\vlin{\wrD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.B)}{
-	  \vlhy{(\forall x.A) \vlor (\forall x.B)}}}}}
+	  \vlhy{(\forall x.A) \vlor (\forall x.B)}}}}}}
   $$.
@@
 For a derivation $\Deri$ in
-$\set{\wlD,\wrD,\acD,\me,\mfaD,\mexD,\fequ}$, we can now construct the
+$\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}$, we can now construct the
 \bfit{rectification} $\rectif\Deri$ by rectifying each line of $\Deri$, yielding
@@
 $\rr\in\set{\me,\fequ}$ and as the canonical injection for
-$\rr\in\set{\wlD,\wrD}$. For $\rr=\acD$ it maps the vertices
+$\rr=\wrD$. For $\rr=\acD$ it maps the vertices
 corresponding to the two atoms in the premise to vertex of the

### 2021-01-18 main.tex

--- 2021-01-18 main.tex
@@
 \renewcommand\acD {\mathsf{ac}}
-\newcommand\acDeq {\mathsf{ac}^\fequ}
+\newcommand\acDx {\mathsf{ac}_x}
+\newcommand\acDeq {\mathsf{ac}_x^\fequ}
 \newcommand\cfaD {\mathsf{c_\forall}}
@@
   Let $\vlderivation{
-    \vlde{\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
+    \vlde{\set{\wrD,\acD,\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
       \vlhy{A}}}$ be a rectified derivation. Then the induced map
@@
   First, observe that for every inference rule
-  $\rr\in\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$
+  $\rr\in\set{\wrD,\acD,\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ 
   the induced map $\mapof{\rr}\colon\vgraphof Q\to\vgraphof P$ defines
@@
   respectively, where $\rectif\acD$ is a $\acD$ that renames the
-  variables---the atom variable
-  \juihsuan{or propositional variable? maybe use just a single name}, as well as the first-order variable of
-  the same name---as everything is rectified, there is no ambiguity
-  here.
-  This gives us a derivation $\vlderivation{
-    \vlde{\set{\wrD,\acD,\rectif\acD,\me,\PE\fequ}}{\PE\Deri}{\PE
-      B}{ \vlhy{\PE A}}}$ such that  $\mapof{\PE\Deri}=\mapof\Deri$. It has been
-  shown in~\cite{str:07:RTA} that $\mapof{\PE\Deri}$ is a skew
+  variabes---the propositional variable, as well as the first-order variable of
+  the same name---as everything is recified, there is no ambiguity
+  here.  This gives us a derivation $\vlderivation{
+    \vlde{\set{\wrD,\acD,\rectif\acD,\me,\PE\fequ}}{\PE\Deri}{\PE B}{
+      \vlhy{\PE A}}}$ such that $\mapof{\PE\Deri}=\mapof\Deri$. It has
+  been shown in~\cite{str:07:RTA} that $\mapof{\PE\Deri}$ is a skew
   fibration (see
   also~\cite{hughes:invar,str:ral:tableaux19,str:RR-9048}). Hence,
-  $\mapof\Deri$ is a skew fibration.
+  $\mapof\Deri$ is a skew fibration. That $\mapof{\PE\Deri}$ preserves
+  exponentials follows immediately from its construction.
 \end{proof}
@@
   surjection and $\phi'\colon \gB_1\to\gB$ being an injection that
-  reflects edges. \juihsuan{what do you mean by "reflect edges"?} Both, $\phi'$ and $\phi''$ remain skew
+  reflects edges. \juihsuan{what do you mean by "reflect edges"?}\lutz{edge downstairs implies edge upstairs} Both, $\phi'$ and $\phi''$ remain skew
   bifibrations. Let us first look at $\phi'$.  Let $\PE B_1$ be the
   propositional formula obtained from $\PE B$ by removing all atoms
-  that are not represented by vertices in $\vB'$. Then $\graphof{\PE
+  that are not represented by vertices in $\vB'$. Then $\graphof{\PEp
     B_1}=\gB_1$.  By \cite[Proposition~7.6.1]{str:07:RTA}, we have a
-  derivation $\vlder{\set{\wrD,\fequ}}{\PE\Deri_1}{\PE B}{\PE B_1}$.
+  derivation $\vlder{\set{\wrD,\fequ}}{\PE\Deri_1}{\PE B}{\PEp B_1}$.
   A subformula of $\PE B$ is called \emph{weak} if it has been
@@
   Thus we have a first order derivation
-  $\vlder{\set{\wrD,\fequ}}{\Deri_1}{B}{B_1}$.
-  \juihsuan{$B_1$ is not defined (The notation $\PE B_1$ suggests that it is the
-propositional encoding of some formula but we need to prove it). This can be
-proven using the fact that $\phi'$ is a skew bifibration here.}
+  $\vlder{\set{\wrD,\fequ}}{\Deri_1}{B}{B_1}$ with $\PE B_1=\PEp B_1$.
   Let us now look at $\phi''$. Let $\gA_1=\gA\substof\phi$ be the
@@
   $\vlder{\set{\acD,\me,\PE\fequ}}{\PE\Deri_2}{\PE B_1}{\PE A_1}$,
-  where $\PE A_1 =\PE A\substof\phi$ is the result of applying $\substof\phi$
-  to~$\PE A$. Note that $\PE A_1 = \PE{(A\substof\phi)}$. To $\Deri_2$ we can apply a permutation argument,
-  permuting all instances of $\acD$, that duplicate an atom $x\in\VAR$, up until they either reach the top
-  of the derivation or an instance of $\me$ which separates the two
-  atoms in the premise. More precisely, we consider the following
-  inference rule
+  where $\PE A_1 =\PE A\substof\phi$ is the result of applying
+  $\substof\phi$ to~$\PE A$. Note that $\PE A_1 =
+  \PE{(A\substof\phi)}$ and $\PE B_1$ are both proposional
+  encodings. We plan to show that $\Deri_2$ can be lifted to
+  $\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$. However, observe that not
+  every formula occurring in $\Deri_2$ is a propositional
+  encoding. There are two reasons for this: (i) we might have $P\PE\fequ
+  Q$ where $P$ is a propositional encoding but $Q$ is not, and (ii)
+  the rule $\acD$ can duplicate an atom with name $x\in\VAR$. Let us write $\acDx$ for such instances. To
+  address (i), we consider here formulas equivalent modulo $\fequ$,
+  always knowing that we can add instances of $\fequ$ as needed. To
+  address (ii), we apply a permutation argument, permuting all
+  instances of $\acDx$ up until
+  they either reach the top of the derivation or an instance of $\me$
+  which separates the two atoms in the premise. More precisely, we
+  consider the following inferene rule
   \begin{equation}
+    \label{eq:acDeq}
     \vlinf{\acDeq}{}{\Scons{x}}{S_0\cons{S_1\cons{x}\vlor S_2\cons{x}}}
@@
   \end{equation}
-  Now we show that $\PE\Deri_2$ can be lifted to
-  $\set{\acD,\me,\mfaD,\mexD,\fequ}$.  We proceed by induction on the
-  height of $\PE\Deri_2$, beginning at the bottom, as we already
-  constructed the formula~$B_1$.  Every instance of $\fequ$ or $\acD$
-  (duplicating an atom that is not a $x\in\VAR$), can trivially be
-  lifted. Similarly, an instance of $\me$, that is above an instance
-  of $\acDeq$ as indicated in~\eqref{eq:mac}, can be lifted as the
-  premise must also be a propositional encoding and the $\me$-inference
-  remains correct in the first-order case.  It remains to consider a
-  situation~\eqref{eq:mac}. Observe that we must have
+  We can therefore assume that all instances of $\acDx$, that contract
+  an atom $x\in\VAR$ are either at the top of $\PE\Deri_2$ or below a
+  $\me$-instance as in~\eqref{eq:mac}. We now lift $\PE\Deri_2$ to
+  $\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$, proceed by induction on
+  the height of $\PE\Deri_2$, beginning at the top, making a case
+  analysis on the topmost rule that is not a $\fequ$.
+  \begin{itemize}
+  \item $\acDx$: We know that the premisse of~\eqref{eq:acDeq} is a
+    propositional encoding. Hence, $S_1\conhole=\conhole\vlor E$ and
+    $S_2\conhole=\conhole\vlor F$ and both $x$ are universals, and
+    $E\vlor F$ contains all occurrences of $x$ bound by that
+    universal. We have the following subcases:
+    \begin{itemize}
+    \item $E$ and $F$ are both non-empty: We have
+      \begin{equation*}
+        \vlinf{\acDeq}{}{\Scons{x\vlor (E\vlor F)}}{S\cons{(x\vlor E)\vlor (x\vlor F)}}
+      \end{equation*}
+      which can be lifted to
+      \begin{equation*}
+        \vlinf{\mfaD}{}{\Scons{\forall x.(E\vlor F)}}{S\cons{(\forall x.E)\vlor (\forall x.F)}}
+      \end{equation*}
+    \item $E$ is empty and $F$ is non-empty: We have
+      \begin{equation*}
+        \vlinf{\acDeq}{}{\Scons{x\vlor F)}}{S\cons{x\vlor (x\vlor F)}}
+      \end{equation*}
+      which can be lifted to
+      \begin{equation*}
+        \vlinf{\mfaD}{}{\Scons{\forall x.F}}{S\cons{\forall x.\forall x.F}}
+      \end{equation*}
+    \item $E$ is non-empty and $F$ is empty: This is similar to the previous case.
+    \item $E$ and $F$ are both empty: This is impossible as the
+      premise would not be a propositional encoding.
+    \end{itemize}
+  \item $\acD$ (contracting an ordinary atom): This can trivially be lifted.
+  \item $\me$ that is not in the situation of~\eqref{eq:mac}: Then now
+    encoding of a quantifier is affected and the instance of $\me$ can
+    be lifted.
+  \item $\me/\acDx$ as in situation~\eqref{eq:mac}: We must have
     $R_1\cons{x}\fequ x\vlor E$ for some $E$ and $R_2\cons{x}\fequ

### 2021-01-19 main.tex
Comments on IX and sequentialisation

@@
 \newcommand*{\MLL}{\mathsf{MLL}}
+\newcommand*{\MLLm}{\mathsf{MLL+mix}}
 \newcommand*{\FOMLL}{\mathsf{MLL1^X}} 
@@
 \end{thm}
+
+\begin{lemma}\label{lem:concomp}
+  The number of connected components of an acylic graph $\gG = \tuple{\vG, \eG}$ is
+equal to $|\eG| - |\vG|$.
+\end{lemma}
+
+\begin{proof}
+  By a straightforward induction on $|\vG|$.
+\end{proof}
+
+\begin{lemma}
+  The number of connected components is the same for any switching graph of a
+unification net.
+\end{lemma}
+
+\begin{proof}
+  An immediate consequence of Lemma \ref{lem:concomp}.
+\end{proof}
+
+In the proof, we also use the notion of \bfit{frame} introduced by Hughes in
+\cite{hughes:unifn}.
+
+\begin{definition}
+Let $\lambda$ be a unification net on an $\FOMLL$ sequent $\Gamma$.
+We define the \bfit{frame} of $\lambda$ by exhaustively applying the following
+subformula rewriting steps, to obtain a linking $\lambda_m$ on an $\MLLm$ sequent $\Gamma_m$:
+
+\begin{enumerate}
+  \item {\bf Encode dependencies as fresh links.} For each dependency $\exists x
+	  \rightarrow \forall y$, with corresponding subformulas $\exists x A$
+		and $\forall y B$, we add a fresh link as follows. Let $P$ be a
+		fresh (nullary) predicate symbol. Replace $\exists x A$ with $P
+		\cand \exists x A$ and $\forall y B$ with $\overline{P} \cor \forall y B$, and add an axiom link between $P$ and $\overline{P}$.
+  \item {\bf Erase quantifiers.} After step 1, erase all the quantifiers. (We no longer need their leaps since they are encoded as links in step 1.
+  \item {\bf Simplify atoms.} After step 2, replace every predicate $Pt_1 \cdots t_n$ with a nullary predicate symbol $P$.
+\end{enumerate}
+\end{definition}
+Note that the linking $\lambda_m$ is a valid $\MLLm$ proof net.
+
+\begin{lemma}\label{lem:concomp_switching}
+Suppose that $\lambda$ is a $\MLLm$ proof net which is connected and such that any of its
+switching graphs is not connected. Then there exists a $\vlor$ node in
+$\unifstr{\lambda}$ such that $\lambda$ is correct on the sequent $\Gamma'$
+obtained from $\Gamma$ by replacing this $\vlor$ by a $\vlan$.
+\end{lemma}
+
+\begin{proof}
+\todo{}
+\end{proof}
+
+\begin{lemma}
+Suppose that $\lambda$ is a $\FOMLL$ proof net which is connected and such that any of its
+switching graphs is not connected. Then there exists a $\vlor$ node in
+$\unifstr{\lambda}$ such that $\lambda$ is correct on the sequent $\Gamma'$
+obtained from $\Gamma$ by replacing this $\vlor$ by a $\vlan$.
+\end{lemma}
+
+\begin{proof}
+  Consider the frame $\lambda_m$ of $\lambda$. The number of any switching
+graph of $\unifstr{\lambda}$ is equal to that of $\unifstr{\lambda_m}$. Apply
+Lemma \ref{lem:concomp_switching} and it is clear that such $\vlor$ cannot be one
+of the fresh $\vlor$'s added during the frame construction.
+\todo{}
+\end{proof}
+
+\begin{proof}\label{lem:concomp_switching_fo}
 Let $\lambda$ be a unification net on $\Gamma$. We proceed by induction on the
+number of connected components of the unification structure $\unifstr{\lambda}$:
+\begin{itemize}
+  \item If there is only one connected component, we proceed by induction on the
+number $k$ of connected components of any switching graph of
+$\unifstr{\lambda}$. If $k = 1$, we obtain a proof $\Pi$ in $\FOMLL$ such that
+$\sqntl{\Pi} = \lambda$ by applying \cite[Theorem~3]{hughes:unifn}. If $k > 1$,
+using the Lemma \ref{lem:concomp_switching_fo}, we obtain a sequent $\Gamma'$ on
+which $\lambda$ is correct by transforming a $\vlor$ node into a $\vlan$. By
+induction hypothesis, there is a proof $\Pi'$ in $\FOMLL$ whose translation is
+$\lambda$. By considering the $\vlan$ rule instance corresponding to the $\vlan$
+node in $\Pi'$, we have:
+$
+\Pi' =
+\vlderivation{
+  \vlin{}{}{\sqns{\Gamma'}}{
+  \vlin{}{}{\vlvdots}{
+    \vliin{\vlan}{}{\sqns{\Delta_1, A \vlan B, \Delta_2}}{
+      \vltrl{\Pi_1}{}{}{\sqns{\Delta_1, A}}{
+        \vlhy{\quad}}{
+        \vlhy{}}{
+        \vlhy{}}}{
+      \vltrl{\Pi_2}{}{}{\sqns{B, \Delta_2}}{
+        \vlhy{\quad}}{
+        \vlhy{}}{
+        \vlhy{}}}
+}}}
+$.
+We can thus obtain a proof $\Pi$ of $\Gamma$:
+$
+\Pi =
+\vlderivation{
+  \vlin{}{}{\sqns{\Gamma}}{
+  \vlin{}{}{\vlvdots}{
+    \vlin{\vlor}{}{\sqns{\Delta_1, A \vlor B, \Delta_2}}{
+    \vliin{\mix}{}{\sqns{\Delta_1, A, B, \Delta_2}}{
+      \vltrl{\Pi_1}{}{}{\sqns{\Delta_1, A}}{
+        \vlhy{\quad}}{
+        \vlhy{}}{
+        \vlhy{}}}{
+      \vltrl{\Pi_2}{}{}{\sqns{B, \Delta_2}}{
+        \vlhy{\quad}}{
+        \vlhy{}}{
+        \vlhy{}}}
+}}}}
+$.
+
+\todo{}
+\end{itemize}
+
+\iffalse
+We proceed by induction on the
 number of connectives in $\Gamma$. In the base case, $\Gamma$ is of the form
@@
 \end{itemize}
+\fi
+\end{proof}
 
@@
   address (i), we consider here formulas equivalent modulo $\fequ$,
-  always knowing that we can add instances of $\fequ$ as needed. To
+  always knowing that we can add instances of $\fequ$ as needed. \juihsuan{this
+does not seem clear to me. What if from $\PE A_1$ to $\PE B_1$ there are just a
+bunch of $\PE\fequ$? What do we do in this case?} To
   address (ii), we apply a permutation argument, permuting all
@@
       \end{equation*}
+    \juihsuan{We should say that $\Sconhole, E, $ and $F$ are also propositional
+encodings. Here I think you kind of identify a formula with its prop. encoding.}
     \item $E$ is empty and $F$ is non-empty: We have
@@
       \begin{equation*}
-        \vlinf{\mfaD}{}{\Scons{\forall x.F}}{S\cons{\forall x.\forall x.F}}
+        \vlinf{\cfaD}{}{\Scons{\forall x.F}}{S\cons{\forall x.\forall x.F}}
       \end{equation*}
@@
       \end{equation*}
+    \juihsuan{maybe need some words to exclude the case in which $C$ (or $D$)
+is a propositional variable.}
     \item $E$ is empty and $F$ is not: Then~\eqref{eq:mac} becomes

### 2021-01-19 main.tex
sequentialization

@@
 \begin{proof}
+Suppose that such $\vlor$ node does not exist.
 \todo{}
@@
 of the fresh $\vlor$'s added during the frame construction.
-\todo{}
 \end{proof}
@@
 number $k$ of connected components of any switching graph of
-$\unifstr{\lambda}$. If $k = 1$, we obtain a proof $\Pi$ in $\FOMLL$ such that
-$\sqntl{\Pi} = \lambda$ by applying \cite[Theorem~3]{hughes:unifn}. If $k > 1$,
+$\unifstr{\lambda}$. If $k = 1$, we obtain a proof $\Deri$ in $\FOMLL$ such that
+$\sqntl{\Deri} = \lambda$ by applying \cite[Theorem~3]{hughes:unifn}. If $k > 1$,
 using the Lemma \ref{lem:concomp_switching_fo}, we obtain a sequent $\Gamma'$ on
 which $\lambda$ is correct by transforming a $\vlor$ node into a $\vlan$. By
-induction hypothesis, there is a proof $\Pi'$ in $\FOMLL$ whose translation is
+induction hypothesis, there is a proof $\Deri'$ in $\FOMLL$ whose translation is
 $\lambda$. By considering the $\vlan$ rule instance corresponding to the $\vlan$
-node in $\Pi'$, we have:
+node in $\Deri'$, we have:
 $
-\Pi' =
+\Deri' =
 \vlderivation{
@@
     \vliin{\vlan}{}{\sqns{\Delta_1, A \vlan B, \Delta_2}}{
-      \vltrl{\Pi_1}{}{}{\sqns{\Delta_1, A}}{
+      \vltrl{\Deri_1}{}{}{\sqns{\Delta_1, A}}{
         \vlhy{\quad}}{
@@
         \vlhy{}}}{
-      \vltrl{\Pi_2}{}{}{\sqns{B, \Delta_2}}{
+      \vltrl{\Deri_2}{}{}{\sqns{B, \Delta_2}}{
         \vlhy{\quad}}{
@@
 $.
-We can thus obtain a proof $\Pi$ of $\Gamma$:
+We can thus obtain a proof $\Deri$ of $\Gamma$:
 $
-\Pi =
+\Deri =
 \vlderivation{
@@
     \vliin{\mix}{}{\sqns{\Delta_1, A, B, \Delta_2}}{
-      \vltrl{\Pi_1}{}{}{\sqns{\Delta_1, A}}{
+      \vltrl{\Deri_1}{}{}{\sqns{\Delta_1, A}}{
         \vlhy{\quad}}{
@@
 }}}}
-$.
-
-\todo{}
+$ such that $\sqntl{\Deri} = \lambda$.
+
+  \item If there are $n > 1$ connected components, add a fresh $\vlor$ node
+connecting two formulas belonging to different connected components of $\Gamma$
+to get a new sequent $\Gamma'$. Define a unification net $\lambda'$ on $\Gamma'$
+using the same linking as $\lambda$. By induction hypothesis, since
+$\unifstr{\lambda'}$
+has $n-1$ connected components, there is a $\FOMLL$ proof $\Deri'$ such that
+$\sqntl{\Deri'} = \lambda'$. Consider the $\vlor$ rule instance corresponding
+to the $\vlor$ node in question. Since $\vlor$ is invertible, we can permute
+downwards this rule instance until it becomes the last rule of the proof (note
+that this transformation does not change the image of the proof by the
+translation $\sqntl\cdot$) to get a new proof $\Deri''$ of $\Gamma'$. By deleting the last rule
+instance from $\Deri''$, we obtain a proof $\Deri$ of $\Gamma$ such that
+$\sqntl{\Deri} = \lambda$.
+\tocheck{}
 \end{itemize}

### 2021-01-19 main.tex
comment
sequentialisation

@@
 \end{thm}
-\juihsuan{maybe we should take $\form{\Gamma}$ instead? (consider the proof
-$\vlderivation{\vlin{\wk}{}{\sqn{\ttt, A}}{
+\juihsuan{maybe there is still some problem... (consider the proof
+
+$\vlderivation{
+   \vliin{\vlan}{}{\sqn{\ttt, a \vlan b, \cneg b}}{
+   \vlin{\ax}{}{\sqn{b, \cneg b}}{
+     \vlhy{}}}{
+   \vlin{\wk}{}{\sqn{\ttt, a}}{
      \vlin{\ttt}{}{\sqn\ttt}{
-                   \vlhy{}}}}$)}
-
+       \vlhy{}}}}}
+$, it doesn't seem possible to get rid of the $\wk$ rule using deep weakening)}
 \begin{proof}
   Note that the instances of $\wrD,\cD$ in $\Deri_2$ are deep, but inside sequent contexts.
+  Suppose that $\Gamma$ is provable in $\FOLK$, then so is $\form{\Gamma}$.
+Consider a proof
+$ \vlderivation{
+        \vltrl{}{\FOLK}{\Deri}{\sqns{\form{\Gamma}}}{
+          \vlhy{\quad}}{
+          \vlhy{}}{
+          \vlhy{}}} $
+Note that the instances of $\ctr$ and $\wk$ in $\Deri$ can be transformed into
+derivations using $\cD$, $\wrD$ and the rules from $\FOMLL$.
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\ctr}{}{\sqns{\Gamma, A}}{
+    \vlhy{\sqns{\Gamma, A, A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cD}{}{\sqns{\Gamma, A}}{
+    \vlin{\vlor}{}{\sqns{\Gamma, A \vlor A}}{
+      \vlhy{\sqns{\Gamma, A, A}}}}}
+\end{equation*}
+
 \todo{}
@@
 
-\begin{thm}
+\begin{thm}\label{thm:sqntl}
   Any unification net can be obtained via the translation $\sqntl\cdot$ given in Theorem
@@
 \end{thm}
+
+To prove this theorem, we need some basic lemmas about connected components in
+switching graphs of unification nets.
 
@@
 \begin{proof}
-Suppose that such $\vlor$ node does not exist.
-\todo{}
-\end{proof}
-
-\begin{lemma}
+Suppose that such a $\vlor$ node does not exist. Then it is clear that for any
+two nodes, there exists a switching graph containing a path between them and
+this path corresponds to an $AE$-path in \cite{retore:03}. By
+\cite[Propostion~3]{retore:03}, $\lambda$ corresponds to a sequent proof that
+does not use $\mix$, which implies the connectedness of the switching graphs of
+$\lambda$. Contradiction.
+\tocheck{}
+\end{proof}
+
+\begin{lemma}\label{lem:concomp_switching_fo}
 Suppose that $\lambda$ is a $\FOMLL$ proof net which is connected and such that any of its
@@
 
-\begin{proof}\label{lem:concomp_switching_fo}
+We can now give the proof of Theorem \ref{thm:sqntl}.
+
+\begin{proof}[Proof of Theorem~\ref{thm:sqntl}]
 Let $\lambda$ be a unification net on $\Gamma$. We proceed by induction on the

### 2021-01-19 main.tex
minor fixes

@@
 \begin{equation*}
-  \begin{array}{cc}
-    \graphof{\alpha} = \single \alpha & 
-    \graphof{\forall x . A} = \single x + \graphof{A} \\[.5ex]
-    \graphof{A \cor B} = \graphof{A} + \graphof{B} &
-    \graphof{\exists x . A} = \single x \times \graphof{A} \\[.5ex]
-    \graphof{A \cand B} = \graphof{A} \times \graphof{B} &
-
+  \begin{array}{r@{\;}l@{\hskip4em}r@{\;}l}
+    \graphof{a} &= \single a \rlap{\hskip1em(for any atom $a$)}  \\[.9ex]
+    \graphof{A \cor B} &= \graphof{A} + \graphof{B} &
+    \graphof{\exists x . A} &= \single x \times \graphof{A} \\[.9ex]
+    \graphof{A \cand B} &= \graphof{A} \times \graphof{B} &
+    \graphof{\forall x . A} &= \single x + \graphof{A}    
   \end{array}
 \end{equation*}
-where $\single \alpha$ (resp. $\single x$) is a single-vertex graph whose vertex is 
-    labelled by $\alpha$ (resp. $x$).
-\todo{make look nice, use array} \juihsuan{done}\lutz{use the single macro (see
-above), so that we can change the notation later if we need to (and make the
-array with two columns)} \juihsuan{fixed}
+where $\single a$ (resp. $\single x$) is a single-vertex graph whose vertex is 
+    labelled by $a$ (resp. $x$).
 
@@
 
-\todo{def $\fequ$}
-
 We define a congruence relation $\fequ$ on formulas by the following equations:
@@
   \label{eq:fequ}
-  \begin{array}{cc}
-    A \vlan B \fequ B \vlan A & A \vlor B \fequ B \vlor A \\
-    (A \vlan B) \vlan C \fequ A \vlan (B \vlan C) &
-    (A \vlor B) \vlor C \fequ A \vlor (B \vlor C) \\
-    \forall x . \forall y . A \fequ \forall y . \forall x . A &
-    \exists x . \exists y . A \fequ \exists y . \exists x . A \\
-    \forall x . (A \vlor B) \fequ (\forall x . A) \vlor B &
+  \begin{array}{c@{\hskip1.5em}c}
+    A \vlan B \fequ B \vlan A
+    &
+    (A \vlan B) \vlan C \fequ A \vlan (B \vlan C) 
+    \\
+    A \vlor B \fequ B \vlor A
+    &
+    (A \vlor B) \vlor C \fequ A \vlor (B \vlor C)
+    \\
+    \forall x . \forall y . A \fequ \forall y . \forall x . A
+    &
+    \forall x . (A \vlor B) \fequ (\forall x . A) \vlor B
+    \\
+    \exists x . \exists y . A \fequ \exists y . \exists x . A
+    &
     \exists x . (A \vlan B) \fequ (\exists x . A) \vlan B
@@
 theorem shows that the set of fographs can been seen as the quotient
-$\FORM / \fequ$.
+$\FORM/\mathord\fequ$.
 \begin{thm}
@@
 \begin{proof}
-  \todo{}
   By a straightforward induction on $A$.
@@
         \vlin{\me}{}{\Scons{(R_1\cons{x}\vlor R_2\cons{x})\vlan(C\vlor D)}}{
-          \vlhy{\Scons{(R_1\cons{x}\vlan C)\vlor (R_2\cons{x}\vlor D)}}}}}
+          \vlhy{\Scons{(R_1\cons{x}\vlan C)\vlor (R_2\cons{x}\vlan D)}}}}}
   \end{equation}
@@
             \vlin{\me}{}{\Scons{((x\vlor E)\vlor (x\vlor F))\vlan(C\vlor D)}}{
-              \vlhy{\Scons{((x\vlor E)\vlan C)\vlor ((x\vlor F)\vlor D)}}}}}
+              \vlhy{\Scons{((x\vlor E)\vlan C)\vlor ((x\vlor F)\vlan D)}}}}}
       \end{equation*}
@@
             \vlin{\me}{}{\Scons{((\forall x. E)\vlor (\forall x. F))\vlan(C\vlor D)}}{
-              \vlhy{\Scons{((\forall x. E)\vlan C)\vlor ((\forall x. F)\vlor D)}}}}}
+              \vlhy{\Scons{((\forall x. E)\vlan C)\vlor ((\forall x. F)\vlan D)}}}}}
       \end{equation*}
     \juihsuan{maybe need some words to exclude the case in which $C$ (or $D$)
-is a propositional variable.}
+is a propositional variable.}\lutz{shit. (you mean a ``first order variable'') this actually can happen. then we have another $\mexD$}
     \item $E$ is empty and $F$ is not: Then~\eqref{eq:mac} becomes
@@
             \vlin{\me}{}{\Scons{(x\vlor (x\vlor F))\vlan(C\vlor D)}}{
-          \vlhy{\Scons{(x\vlan C)\vlor ((x\vlor F)\vlor D)}}}}}
+          \vlhy{\Scons{(x\vlan C)\vlor ((x\vlor F)\vlan D)}}}}}
       \end{equation*}
@@
             \vlin{\me}{}{\Scons{(x\vlor x)\vlan(C\vlor D)}}{
-              \vlhy{\Scons{(x\vlan C)\vlor (x\vlor D)}}}}}
+              \vlhy{\Scons{(x\vlan C)\vlor (x\vlan D)}}}}}
       \end{equation*}

### 2021-01-20 main.tex
rule permutation

@@
 \end{thm}
-\juihsuan{maybe there is still some problem... (consider the proof
-
-$\vlderivation{
-   \vliin{\vlan}{}{\sqn{\ttt, a \vlan b, \cneg b}}{
-   \vlin{\ax}{}{\sqn{b, \cneg b}}{
-     \vlhy{}}}{
-   \vlin{\wk}{}{\sqn{\ttt, a}}{
-     \vlin{\ttt}{}{\sqn\ttt}{
-       \vlhy{}}}}}
-$, it doesn't seem possible to get rid of the $\wk$ rule using deep weakening)}
+
 \begin{proof}
+
   Note that the instances of $\wrD,\cD$ in $\Deri_2$ are deep, but inside sequent contexts.
+
   Suppose that $\Gamma$ is provable in $\FOLK$, then so is $\form{\Gamma}$.
@@
           \vlhy{}}} $
-Note that the instances of $\ctr$ and $\wk$ in $\Deri$ can be transformed into
-derivations using $\cD$, $\wrD$ and the rules from $\FOMLL$.
+
+First, if an instance $\vlinf{\weakr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma}}$
+ of $\weakr$ is followed by a rule in which $A$ is not in the principal
+formula, it can be permuted downwards.
+Otherwise, the proof can be transformed using the following rewriting rules.
 
@@
 \vlderivation{
-  \vlin{\ctr}{}{\sqns{\Gamma, A}}{
+  \vliin{\vlan}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
+      \vlhy{\sqns{\Gamma}}}}{
+    \vlhy{\sqns{B, \Delta}}}}
+\leadsto
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
+    \vlin{\weakr}{}{\vlvdots}{
+      \vlhy{\sqns{\Gamma}}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\vlor}{}{\sqns{\Gamma, A \vlor B}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A, B}}{
+      \vlhy{\sqns{\Gamma, A}}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{\sqns{\Gamma, A \vlor B}}{
+    \vlhy{\sqns{\Gamma, A}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\exists}{}{\sqns{\Gamma, \exists x.A}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A\ssubst{x}{t}}}{
+      \vlhy{\sqns{\Gamma}}}}}
+\leadsto
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, A\ssubst{x}{t}}}{
+    \vlhy{\sqns{\Gamma}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\forall}{}{\sqns{\Gamma, \forall x.A}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
+      \vlhy{\sqns{\Gamma}}}}}
+\leadsto
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, \forall x.A}}{
+    \vlhy{\sqns{\Gamma}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\conr}{}{\sqns{\Gamma, A}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A, A}}{
+      \vlhy{\sqns{\Gamma, A}}}}}
+\leadsto
+\vlderivation{
+  \vlhy{\sqns{\Gamma, A}}}
+\end{equation*}
+Note that in the case of $\vlor$, we use the deep rule $\wrD$ which can be
+permuted down over all the rules. By using these rewriting rules, we can eventually get
+a derivation with all the instances of $\weakr$ and $\wrD$ at the bottom. Now observe
+that the instances of $\conr$ in $\Deri$ can be transformed using the following
+rule:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\conr}{}{\sqns{\Gamma, A}}{
     \vlhy{\sqns{\Gamma, A, A}}}}
@@
 
-\todo{}
+Knowing that $\cD$ can be permuted down over all the rules of $\FOMLL$, we
+eventually obtain a derivation:
+\begin{equation*}
+\vlderivation{
+  \vlde{\set{\weakr, \wrD,\cD,\fequ}}{\Deri'_2}{\sqns{\Gamma}}{
+    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma_0}}{
+      \vlhy{\quad}}{
+      \vlhy{}}{
+      \vlhy{}}}}
+\end{equation*}
+Note that $\fequ$ is required here since the permutaion of formulas is implicit
+in $\FOMLL$.
+
+By transforming each sequent of $\Deri'_2$ into its corresponding formula, and by
+considering the following rewriting rule:
+\begin{equation*}
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, A}}{
+    \vlhy{\sqns{\Gamma}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{\sqns{\form{\Gamma} \vlor A}}{
+    \vlhy{\sqns{\form{\Gamma}}}}}
+\end{equation*},
+we obtain a derivation
+\begin{equation*}
+\vlderivation{
+  \vlde{\set{\wrD,\cD,\fequ}}{\Deri_2}{\sqns{\form{\Gamma}}}{
+    \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\Gamma'}}{
+      \vlhy{\quad}}{
+      \vlhy{}}{
+      \vlhy{}}}}
+\end{equation*}
+where $\Gamma' = \form{\Gamma_0}$ and $\Deri_1$ can be obtained from $\Deri'_1$
+by applying the $\vlor$ rule.
+\tocheck{}
+\juihsuan{This might be a bit long...}
 \end{proof}

### 2021-01-20 main.tex
def of FOCP

@@
 \newcommand{\mapof}[1]{\lfloor{#1}\rfloor}
-
+\newcommand{\labelof}[1]{\ell(#1)}
 \newcommand{\form}[1]{\mathrm{fm}(#1)}
@@
 \begin{equation*}
-  \begin{array}{cc}
+  \begin{array}{ccc}
+    \dual{\dual a} = a
+    &
   \dual\ttt =\fff &
   \dual{p(t_1,\ldots,t_n)} = \dual{p}(t_1,\ldots,t_n) \\[.5ex]
+  &
   \dual\fff = \ttt &
   \dual{\dual p(t_1,\ldots,t_n)} = p(t_1,\ldots,t_n) \\[.5ex]
-  \dual{\dual a} = a & \dual{\exists x.A} = \forall x.\dual{A} \\[.5ex]
-  \dual{A \vlan B} = \dual{A} \ \vlor \ \dual{B} & \dual{\forall x.A} = \exists x.\dual{A} 
+  &
+  \dual{\exists x.A} = \forall x.\dual{A}
+  &
+  \dual{A \vlan B} = \dual{A} \ \vlor \ \dual{B} 
   \\[.5ex]
-  \dual{A \vlor B} = \dual{A} \ \vlan \ \dual{B} &  
+  &
+  \dual{\forall x.A} = \exists x.\dual{A}
+  &
+%  \\[.5ex]
+  \dual{A \vlor B} = \dual{A} \ \vlan \ \dual{B}
   \end{array}
 \end{equation*}
-\todo{add missing equations and make it look nice}
-\lutz{don't we need   $\dual{\dual a} = a$? (then it should follow that $\dual{\dual A} = A$)}
-
-\juihsuan{isn't it given by the first four equations? I think that we use the
-notation of negation for atoms and formulas. We may also need to precise that each
-predicate symbol $p$ has a dual $\dual{p}$.}\lutz{we either have to say $\dual{\dual a} = a$ or $\dual{\dual p} = p$. I prefer the first.}
-\juihsuan{okay I see. I didn't realize that the negation is regarded as a
-connective for predicate symbols. The notation got me confused since $\dual{p}$
-is also a predicate symbol.}
 
@@
 replacing all occurrences of $x_i$ by $t_i$.
-A \bfit{renaming} is a substitution $\sigma$ with $\sigma(x)\in\VAR$ for all variable $x$.
+A \bfit{variable renaming} is a substitution $\sigma$ with $\sigma(x)\in\VAR$ for all variables $x$.
 
@@
 A graph $\gG$ is \bfit{labelled} in a set $L$ if each vertex $v\in\vG$
-has an element $\ell(v)\in L$ associated with it, its \bfit{label}.  A
+has an element $\labelof v\in L$ associated with it, its \bfit{label}.  A
 graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Fonets}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Skew Bifibrations}
-\lutz{$\phi$ instead of $f$}
-A graph homomorphism $\phi\colon \tuple{\vG, \eG} \rightarrow \tuple{\vH, \eH}$ is a \bfit{fibration} if
-for all $v \in \vG$ and $w\phi(v) \in \eH$, there exists a unique $\tilde{w} \in
-\vG$ such that $\tilde{w}v \in \eG$ and $\phi(\tilde{w}) = w$, and is a \bfit{skew fibration}
-if for all $v \in \vG$ and $w\phi(v) \in \eH$ there exists $\tilde{w} \in \vG$ such that
-$\tilde{w}v \in \eG$ and $\phi(\tilde{w})w \notin \eH$.
-A directed graph homomorphism is a \bfit{fibration} if \todo{}
-
-\lutz{do we really need that?
-A \bfit{fograph homomorphism}
-is a graph homomorphism between the underlying graphs of the fographs
-considered. A fograph homomorphism $f : \gG \rightarrow \gH$ is
-\bfit{label-preserving} if for all $v \in \vG, label(v) = label(f(v))$, and is
-\bfit{existential-preserving} if for all existential binder $b$ in $\gG$, the
-vertex $f(b)$ is an existential binder in $\gH$.
-}
-
-\lutz{I think we need \bfit{fograph homomorphism} maps binders to binders and literals to literals, preserving the predicates.}
+
+A graph homomorphism $\phi\colon \tuple{\vG, \eG} \rightarrow
+\tuple{\vH, \eH}$ is a \bfit{fibration} if for all $v \in \vG$ and
+$w\phi(v) \in \eH$, there exists a unique $\tilde{w} \in \vG$ such
+that $\tilde{w}v \in \eG$ and $\phi(\tilde{w}) = w$, and is a
+\bfit{skew fibration} if for all $v \in \vG$ and $w\phi(v) \in \eH$
+there exists $\tilde{w} \in \vG$ such that $\tilde{w}v \in \eG$ and
+$\phi(\tilde{w})w \notin \eH$.  A directed graph homomorphism is a
+\bfit{fibration} if for all $v \in \vG$ and $\pair{w,\phi(v)} \in
+\eH$, there exists a unique $\tilde{w} \in \vG$ such that $\pair{\tilde{w},v}
+\in \eG$ and $\phi(\tilde{w}) = w$.
+
+A \bfit{fograph homomorphism} $\phi=\tuple{\phi,\substof\phi}$ is a
+pair where $\phi\colon\gG\to\gH$ is a graph homomorphism between the
+underlying graphs, and $\substof\phi$ is a variable renaming such that
+for all $v\in\vG$ we have
+$\labelof{\phi(v)}=\substof\phi(\labelof v)$. Note that this entails that
+$\phi$ maps binders to binders and literals to literals. We say that a
+fograph homomorphism $\phi\colon\gG \rightarrow \gH$ is
+%%\bfit{label-preserving} if for all $v \in \vG, label(v) = label(f(v))$, and is
+\bfit{existential-preserving} if for all existential binders $b$ in
+$\gG$, the vertex $\phi(b)$ is an existential binder in $\gH$.
 
 \begin{definition}
-  Let $\gG$ and $\gH$ be fographs.
-A \bfit{skew bifibration} $\phi\colon\gG\to\gH$ is a fograph homomorphism that is a skew fibration on $\tuple{\vG, \eG} \to \tuple{\vH, \eH}$ and a fibration on the binding graphs $\bG\to\bH$.
+  Let $\gG$ and $\gH$ be fographs. A \bfit{skew bifibration}
+  $\phi\colon\gG\to\gH$ is an existential-preserving fograph
+  homomorphism that is a skew fibration on $\tuple{\vG, \eG} \to
+  \tuple{\vH, \eH}$ and a fibration on the binding graphs $\bG\to\bH$.
   %etween fographs is a label-preserving and
@@
 
+\begin{remark}
+  In or definition of FOCP, we are slightly laxer than the original
+  definition of~\cite{hughes:fopws}, as we allow for a variable
+  renaming $\substof\phi$ which was forced to be the identity
+  in~\cite{hughes:fopws}.
+  %The reason for this relaxation in our case is that we want to cover a richer class of proofs, also allowing 
+\end{remark}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-20 main.tex
in IX again

@@
 
-\todo{add $\cfaD$ everywhere}
-
 In this section we establish the relation between skew bifibrations and derivations  in
-$\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}$. However, 
-if a derivation $\Deri$ contains instances of the rules $\mfaD$ and
+$\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$. However, 
+if a derivation $\Deri$ contains instances of the rules $\cfaD$, $\mfaD$, and
 $\mexD$ we can no longer naively define the rectification
@@
 rules cannot be applied if premise and conclusion are rectified. For
-this reason we define here rectified versions $\rectif\mfaD$ and
+this reason we define here rectified versions $\rectif\cfaD$,  $\rectif\mfaD$ and
 $\rectif\mexD$, shown below:
 \begin{equation*}
+  \vlinf{\rectif\cfaD}{}{\Scons{\forall x.Ax}}{\Scons{\forall y.\forall x.Ax}}
+  \hskip3em
+  \begin{array}{c}
     \vlinf{\rectif\mfaD}{}{\Scons{\forall x.(Ax\vlor Bx)}}{\Scons{(\forall y.Ay)\vlor(\forall z.Bz)}}
-  \qquad
+    \\ \\[-1ex]
     \vlinf{\rectif\mexD}{}{\Scons{\exists x.(Ax\vlor Bx)}}{\Scons{(\exists y.Ay)\vlor(\exists z.Bz)}}
+  \end{array}
 \end{equation*}
-\todo{same for $\cfaD$}
 Here, we use the notation $A\cdot$ for a formula $A$ with occurrences
@@
 y.Ay$ are the same formula modulo renaming of the bound variable bound
-by the outermost $\forall$-quantifier. In the rules $\rectif\mfaD$ and
-$\rectif\mexD$ we also demand that the variables $x$, $y$, and $z$ do
+by the outermost $\forall$-quantifier. We also demand that the variables $x$, $y$, and $z$ do
 not occur in the context $\Sconhole$.
@@
 rectified. If $x=y$ and $x=z$ we have $\mfaD$ and
-$\mexD$ as special cases of $\rectif\mfaD$ and $\rectif\mexD$, respectively.
+$\mexD$ as special cases of $\rectif\mfaD$ and $\rectif\mexD$, respectively. And similarly,  if $x=y$ then $\cfaD$
+is a special case of $\rectif\cfaD$.
 
@@
 contracted atom in the conclusion, and for
-$\rr\in\set{\rectif\mfaD,\rectif\mexD}$ it maps the two vertices
+$\rr\in\set{\rectif\cfaD,\rectif\mfaD,\rectif\mexD}$ it maps the two vertices
 corresponding to the quantifiers in the premise to the one in the
-conclusion (as acts as the identity on all other vertices). For a
+conclusion (as acts as the identity on all other vertices).
+For a
 derivation $\Deri$ in
-$\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can then define
+$\set{\wrD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can then define
 the \bfit{induced map} $\mapof\Deri$ as the composition of the induced
-maps of the rule instances in $\Deri$. \juihsuan{maybe mention at least that the induced
+maps of the rule instances in $\Deri$.
+\juihsuan{maybe mention at least that the induced
 maps define graph homomorphisms. Do we need to talk about the contexts
@@
   $\vlderivation{
-    \vlde{\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{\rectif
+    \vlde{\set{\wrD,\rectif\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{\rectif
       B}{ \vlhy{\rectif A}}}$, such that the induced maps
@@
   $\mapof{\rectif\Deri}\colon\graphof{\rectif A}\to\graphof{\rectif
-    B}$ are equal up to the relabeling of the vertices.
+    B}$ are equal up to a variable renaming of the vertex labels.
 \end{lemma}
@@
 \subsection{From Contraction and Weakening to Skew Bifibrations}
+
+We say that a derivation $\Deri$ is \bfit{sane} if for every line $Q$
+in $\Deri$ we have that $\graphof D$ is a fograph (i.e., all binders
+are legal). Clearly, every rectified derivation is sane, but not vice
+versa, as we might have multiple occurrences of bound varibles in $Q$,
+such that $\graphof D$ is still a fograph.
 
@@
     \vlde{\set{\wrD,\acD,\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
-      \vlhy{A}}}$ be a rectified derivation. Then the induced map
+      \vlhy{A}}}$ be a sane derivation. Then the induced map
   $\mapof\Deri\colon\graphof{A}\to\graphof{B}$ is a skew bifibration.

### 2021-01-20 main.tex
in IX again

@@
 pair where $\phi\colon\gG\to\gH$ is a graph homomorphism between the
-underlying graphs, and $\substof\phi$ is a variable renaming such that
+underlying graphs, and $\substof\phi$, also called the \bfit{substitution induced by $\phi$} is a variable renaming such that
 for all $v\in\vG$ we have
 $\labelof{\phi(v)}=\substof\phi(\labelof v)$. Note that this entails that
-$\phi$ maps binders to binders and literals to literals. We say that a
+$\phi$ maps binders to binders and literals to literals.
+We say that a
 fograph homomorphism $\phi\colon\gG \rightarrow \gH$ is
@@
 rule followed by the $\vlor$ rule}\lutz{yes! and similar for $\forall$. Can you do that?}
+
+\lutz{actually NO! we can prove $\sqn{\fff,\ttt}$ using $\ax$ without a special rule for $\fff$. So can you please undo the changes and delete the comments?}
 \begin{proof}
-  This is a straightforward exercise that we leave to the reader.
+  This is a straightforward exercise that we leave to the reader. (Note that the $\ax$-rule can be applied to $\sqn{\fff,\ttt}$ in the cases of $\rr \in \set{\aiD, \faD}$.)
 \end{proof}
@@
 \begin{lemma}\label{lem:MLS1->MLL1}
-  If a formula $C$ is provable in $\FOMLS$ then $\sqn C$ is provable in  $\FOMLL$. \todo{check: do we need rectified here?}
+  If a formula $C$ is provable in $\FOMLS$ then $\sqn C$ is provable in  $\FOMLL$. 
 \end{lemma}
@@
   \label{lem:me}
-  The rules $\me,\mfaD,\mexD$ are derivable in $\set{\wrD,\cD,\fequ}$. 
+  $\cfaD,\me,\mfaD,\mexD$ are derivable in \hbox{$\set{\wrD,\cD,\fequ}$}. 
 \end{lemma}
@@
 \begin{proof}
-  \todo{}\lutz{also check for the need of$\fequ$}
+  \todo{}
 
@@
     \vlderivation{
-      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{}{B}{
+      \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{}{B}{
         \vlhy{A}}}
@@
 For a derivation $\Deri$ in
-$\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}$, we can now construct the
+$\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$, we can now construct the
 \bfit{rectification} $\rectif\Deri$ by rectifying each line of $\Deri$, yielding
@@
 For each instance $\vlinf{\rr}{}{P}{Q}$ of an inference rule in
-$\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can
+$\set{\wrD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can
 define the \bfit{induced map} $\mapof{\rr}\colon\vgraphof
@@
 $\Sconhole$ here (induced maps act clearly as the identity on contexts but we need them for the composition)?}
+\lutz{For the context, I aleady say it is the identity. For the homom, it comes later}
 
@@
 are legal). Clearly, every rectified derivation is sane, but not vice
-versa, as we might have multiple occurrences of bound varibles in $Q$,
-such that $\graphof D$ is still a fograph.
+versa, as we might have multiple occurrences of bound variables in $Q$,
+such that $\graphof Q$ is still a fograph.
 
@@
   Let $\vlderivation{
-    \vlde{\set{\wrD,\acD,\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
+    \vlde{\set{\wrD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
       \vlhy{A}}}$ be a sane derivation. Then the induced map
@@
   First, observe that for every inference rule
-  $\rr\in\set{\wrD,\acD,\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ 
-  the induced map $\mapof{\rr}\colon\vgraphof Q\to\vgraphof P$ defines
-  a fibration on the corresponding binding graphs. \juihsuan{we may need to have
-some explication here.} Therefore, their
-  composition $\mapof\Deri$ is a fibration.
-
-  Now we construct for
+  $\rr\in\set{\wrD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ 
+  the induced map $\mapof{\rr}\colon\vgraphof Q\to\vgraphof P$ defines a existential preserving graph homomorphism $\graphof Q\to\graphof P$ and  a fibration on the corresponding binding graphs.
+\juihsuan{we may need to have
+some explication here.}\lutz{no} Therefore, their
+  composition $\mapof\Deri$ has the same properties fibration.
+
+  For showing that it is also a skew fibration, we construct for
   $\Deri$ its propositional encoding $\PE\Deri$ by
@@
   \juihsuan{maybe mention that an instance of one of the other rules can be translated
-into an instance of the same rule. It's trivial but may be worth mentioning.}
+into an instance of the same rule. It's trivial but may be worth mentioning.}\lutz{done below}
   The instances
@@
   respectively, where $\rectif\acD$ is a $\acD$ that renames the
-  variabes---the propositional variable, as well as the first-order variable of
-  the same name---as everything is recified, there is no ambiguity
-  here.  This gives us a derivation $\vlderivation{
+  variabes---the propositional variable, as well as the first-order
+  variable of the same name---as everything is recified, there is no
+  ambiguity here. Any instance of a rule $\wD$, $\acD$, $\me$, or
+  $\fequ$ is translated to an instance of the same rule, and
+  $\rectif\cfaD$ is translated to $\rectif\acD$.
+
+  This gives us a derivation $\vlderivation{
     \vlde{\set{\wrD,\acD,\rectif\acD,\me,\PE\fequ}}{\PE\Deri}{\PE B}{
@@
   also~\cite{hughes:invar,str:ral:tableaux19,str:RR-9048}). Hence,
-  $\mapof\Deri$ is a skew fibration. That $\mapof{\PE\Deri}$ preserves
-  exponentials follows immediately from its construction.
+  $\mapof\Deri$ is a skew fibration.
+  %%That $\mapof{\PE\Deri}$ preserves
+  %%exponentials follows immediately from its construction.
 \end{proof}
@@
     \vlderivation{
-      \vlde{\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{B}{
+      \vlde{\set{\wrD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{B}{
         \vlhy{A}}}
@@
     \vlderivation{
-      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
+      \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
         \vlhy{A\substof\phi}}}
@@
   reflects edges. \juihsuan{what do you mean by "reflect edges"?}\lutz{edge downstairs implies edge upstairs} Both, $\phi'$ and $\phi''$ remain skew
-  bifibrations. Let us first look at $\phi'$.  Let $\PE B_1$ be the
+  bifibrations. Let us first look at $\phi'$.  Let $\PEp B_1$ be the
   propositional formula obtained from $\PE B$ by removing all atoms
@@
   also weak. Two weak subformulas $B'$ and $B''$ of $\PE B$ form a
-  \emph{weak pair} if $B\fequ\Scons{B'\vlor B''}$ for some context
-  $\Sconhole$. We now can assume without loss of generality that
-  whenever weak subformulas $B'$ and $B''$ for a weak pair, they have
+  \emph{weak pair} if $\PE B\fequ\Scons{B'\vlor B''}$ for some context
+  $\Sconhole$. We can assume without loss of generality that
+  whenever weak subformulas $B'$ and $B''$ form a weak pair, they have
   been introduced by the same instance of $\wrD$ in
@@
   delete all atoms in the scope of the corresponding quantifier,
-  because $\phi$ \juihsuan{should be $\phi'$ here} is a fibration on the binding graph. Hence, each line
+  because $\phi'$ is a fibration on the binding graph. Hence, each line
   in $\PE\Deri_1$ is the propositional encoding $\PE P$ of a
@@
   $\vlder{\set{\wrD,\fequ}}{\Deri_1}{B}{B_1}$ with $\PE B_1=\PEp B_1$.
+
   Let us now look at $\phi''$. Let $\gA_1=\gA\substof\phi$ be the
@@
   every formula occurring in $\Deri_2$ is a propositional
-  encoding. There are two reasons for this: (i) we might have $P\PE\fequ
-  Q$ where $P$ is a propositional encoding but $Q$ is not, and (ii)
-  the rule $\acD$ can duplicate an atom with name $x\in\VAR$. Let us write $\acDx$ for such instances. To
-  address (i), we consider here formulas equivalent modulo $\fequ$,
-  always knowing that we can add instances of $\fequ$ as needed. \juihsuan{this
-does not seem clear to me. What if from $\PE A_1$ to $\PE B_1$ there are just a
-bunch of $\PE\fequ$? What do we do in this case?} To
+  encoding. There are two reasons for this: (i) we might have
+  $P\PE\fequ Q$ where $P$ is a propositional encoding but $Q$ is not,
+  and (ii) the rule $\acD$ can duplicate an atom
+  $x\in\VAR$. Let us write $\acDx$ for such instances. To address (i),
+  we consider here formulas equivalent modulo $\fequ$, always knowing
+  that we can add instances of $\fequ$ as needed.\footnote{Note that whenever we have formulas $P$ and $Q$ with $\PE P\PE\fequ\PE Q$ then $P\fequ Q$.} \juihsuan{this does
+    not seem clear to me. What if from $\PE A_1$ to $\PE B_1$ there
+    are just a bunch of $\PE\fequ$? What do we do in this case?}\lutz{see footnote} To
   address (ii), we apply a permutation argument, permuting all
-  instances of $\acDx$ up until
-  they either reach the top of the derivation or an instance of $\me$
-  which separates the two atoms in the premise. More precisely, we
-  consider the following inferene rule
+  instances of $\acDx$ up until they either reach the top of the
+  derivation or an instance of $\me$ which separates the two atoms in
+  the premise. More precisely, we consider the following inferene rule
   \begin{equation}
@@
   the height of $\PE\Deri_2$, beginning at the top, making a case
-  analysis on the topmost rule that is not a $\fequ$.
+  analysis on the topmost rule that is not a~$\fequ$.
   \begin{itemize}
   \item $\acDx$: We know that the premisse of~\eqref{eq:acDeq} is a
-    propositional encoding. Hence, $S_1\conhole=\conhole\vlor E$ and
-    $S_2\conhole=\conhole\vlor F$ and both $x$ are universals, and
-    $E\vlor F$ contains all occurrences of $x$ bound by that
+    propositional encoding. Hence, $S_1\conhole=\conhole\vlor \PE E$ and
+    $S_2\conhole=\conhole\vlor \PE F$ and both $x$ are universals, and
+    $\PE E\vlor \PE F$ contains all occurrences of $x$ bound by that
     universal. We have the following subcases:
@@
       \begin{equation*}
-        \vlinf{\acDeq}{}{\Scons{x\vlor (E\vlor F)}}{S\cons{(x\vlor E)\vlor (x\vlor F)}}
+        \vlinf{\acDeq}{}{\PE S\cons{x\vlor (\PE E\vlor \PE F)}}{\PE S\cons{(x\vlor \PE E)\vlor (x\vlor\PE F)}}
       \end{equation*}
@@
       \end{equation*}
-    \juihsuan{We should say that $\Sconhole, E, $ and $F$ are also propositional
-encodings. Here I think you kind of identify a formula with its prop. encoding.}
-    \item $E$ is empty and $F$ is non-empty: We have
+      where $\PE S\conhole, \PE E, \PE F$ are the propositional encodings of $\Sconhole,E,F$, respectively.
+    \item $\PE E$ is empty and $\PE F$ is non-empty: We have
       \begin{equation*}
-        \vlinf{\acDeq}{}{\Scons{x\vlor F)}}{S\cons{x\vlor (x\vlor F)}}
+        \vlinf{\acDeq}{}{\PE S\cons{x\vlor \PE F)}}{\PE S\cons{x\vlor (x\vlor \PE F)}}
       \end{equation*}
@@
       \end{equation*}
-    \item $E$ is non-empty and $F$ is empty: This is similar to the previous case.
-    \item $E$ and $F$ are both empty: This is impossible as the
+    \item $\PE E$ is non-empty and $\PE F$ is empty: This is similar to the previous case.
+    \item $\PE E$ and $\PE F$ are both empty: This is impossible as the
       premise would not be a propositional encoding.

### 2021-01-21 main.tex
def of clean

@@
 \newcommand{\substof}[1]{\sigma_{\!#1}}
+\newcommand{\rsubstof}[1]{\rho_{\!#1}}
+\newcommand{\dsubstof}[1]{\delta_{\!#1}}
 \newcommand{\linkingof}[1]{\sim_{#1}}
@@
 \newcommand{\formtree}[1]{\mathcal{F}(#1)}
+
+\renewcommand{\phi}{\varphi}
 
@@
 replacing all occurrences of $x_i$ by $t_i$.
-A \bfit{variable renaming} is a substitution $\sigma$ with $\sigma(x)\in\VAR$ for all variables $x$.
+A \bfit{variable renaming} is a substitution $\rho$ with $\rho(x)\in\VAR$ for all variables $x$.
 
@@
   The fact that every binder of $\graphof A$ is legal can be proved by
-structural induction on $A$:
-  \begin{itemize}
-    \item Trivial if $A$ is an atom.
-    \item The induction step uses the following fact:
-	  if $M$ is a module of $\gG$ and $M' \subseteq M$, then $M'$ is a
-          module of $\gG$ if and only if it is a module of $\gG[X]$.
-  \end{itemize}
-  \todo{}\lutz{maybe mention also fn 2-5 in Dominic's arxiv-paper}
-\end{proof}
-\juihsuan{I'm still looking for a simple proof}
-\footnote{Note that $\graphof A$ is not necessarily a fograph if $A$ is not
-rectified. If $A = (\forall x. p(x)) \vlor (\forall x. q(x))$, then $\graphof A
-= \single x \ \single p(x) \ \single x \ \single q(x)$, the scope of each
-$x$-binder contains all the vertices, in particular, the two $x$-binders.}
+  structural induction on $A$.
+  %% :
+  %% \begin{itemize}
+  %%   \item Trivial if $A$ is an atom.
+  %%   \item The induction step uses the following fact:
+  %%         if $M$ is a module of $\gG$ and $M' \subseteq M$, then $M'$ is a
+  %%         module of $\gG$ if and only if it is a module of $\gG[X]$.
+  %% \end{itemize}
+  %% \todo{}\lutz{maybe mention also fn 2-5 in Dominic's arxiv-paper}
+\end{proof}
+%%\juihsuan{I'm still looking for a simple proof}
+Note that $\graphof A$ is not necessarily a fograph if $A$ is not
+rectified. If $A = (\forall x. p(x)) \vlor (\forall x. q(x))$, then
+$\graphof A = \single x \ \single p(x) \ \single x \ \single q(x)$,
+the scope of each $x$-binder contains all the vertices, in particular,
+the two $x$-binders. On the other hand, there are non-rectified
+formulas which are translated to fographs by $\graphof\cdot$. For
+example, in $\graphof{(\exists x. p(x)) \vlor (\exists x. q(x))}$,
+both $x$-binders are legal, as they are not in each others
+scope.\todo{draw the picture}.  For this reason, we call a formula
+\bfit{clean} if it does not contain subformulas of the form $(\forall
+x.A)\vlor(\forall x.B)$ or $(\exists x.A)\vlan(\exists x.B)$, and no
+$x$-quantified formula occurs as subformula of another $x$-quantified
+formula. Then we have:
+
+\begin{lemma}
+  If $A$ is clean iff\/ $\graphof A$ is a fograph.
+\end{lemma}
+
+\begin{proof}
+  Induction on $A$, using  Theorem~\ref{thm:cograph}.
+\end{proof}
 
@@
 
-A \bfit{fograph homomorphism} $\phi=\tuple{\phi,\substof\phi}$ is a
+A \bfit{fograph homomorphism} $\phi=\tuple{\phi,\rsubstof\phi}$ is a
 pair where $\phi\colon\gG\to\gH$ is a graph homomorphism between the
-underlying graphs, and $\substof\phi$, also called the \bfit{substitution induced by $\phi$} is a variable renaming such that
+underlying graphs, and $\rsubstof\phi$, also called the \bfit{substitution induced by $\phi$} is a variable renaming such that
 for all $v\in\vG$ we have
-$\labelof{\phi(v)}=\substof\phi(\labelof v)$. Note that this entails that
+$\labelof{\phi(v)}=\rsubstof\phi(\labelof v)$. Note that this entails that
 $\phi$ maps binders to binders and literals to literals.
@@
       \vlde{\set{\wrD,\fequ}}{}{A}{
-        \vlde{\set{\acD}}{}{A_1}{
+        \vlde{\set{\acD,\cfaD}}{}{A_1}{
           \vlde{\set{\me,\mfaD,\mexD,\fequ}}{}{A_2}{
@@
     encoding of a quantifier is affected and the instance of $\me$ can
-    be lifted.
+    be lifted.\todo{medial permutation!!!}
   \item $\me/\acDx$ as in situation~\eqref{eq:mac}: We must have

### 2021-01-21 main.tex
linear

@@
 \newcommand{\rectif}[1]{\widehat{#1}}
+
+\newcommand{\fographof}[1]{\llbracket#1\rrbracket}
 \newcommand{\graphof}[1]{\llbracket#1\rrbracket}
+%\newcommand{\graphof}[1]{\mathbb{G}(#1)}
+
 \newcommand{\compl}[1]{#1^\complement}
@@
 \newcommand{\substof}[1]{\sigma_{\!#1}}
-\newcommand{\rsubstof}[1]{\rho_{\!#1}}
-\newcommand{\dsubstof}[1]{\delta_{\!#1}}
+\newcommand{\rsubstof}[1]{\rho_{#1}}
+\newcommand{\dsubstof}[1]{\delta_{#1}}
 \newcommand{\linkingof}[1]{\sim_{#1}}
@@
 formulas which are translated to fographs by $\graphof\cdot$. For
-example, in $\graphof{(\exists x. p(x)) \vlor (\exists x. q(x))}$,
+example, in the graph of $(\exists x. p(x)) \vlor (\exists x. q(x))$,
 both $x$-binders are legal, as they are not in each others
@@
 \end{proof}
+
+Note that even though for every formula $A$ we can obtain an
+equivalent clean formula by simply renaming some bound variables, this
+is not unique up to $\alpha$-conversion, as it is the case for
+rectified formulas.
 
@@
 (e.g. $p(x, y)$ and $\dual{p}(y, z)$) and two literals are \bfit{pre-dual} if their
-labels (atoms) are pre-dual. A \bfit{linked fograph} is a coloured fograph $\gC$ such
+labels (atoms) are pre-dual. A \bfit{linked fograph} $\tuple{\gC,\linkingof\gC}$ is a coloured fograph $\gC$ such
 that every colour (i.e., equivalence class of~$\linkingof\gC$), called a \bfit{link}, consists of two pre-dual literals, and
@@
 Let $\gC$ be a linked fograph. The set of links can be seen as a unification problem
-by identifying dual predicate symbols. A \bfit{dualizer} of $\gC$ is a substitution
-unifying all the links of $\gC$. Since a first-order unification problem is either
+by identifying dual predicate symbols. A \bfit{dualizer} of $\gC$ is a substitution $\delta$
+unifying all the links of~$\gC$. Since a first-order unification problem is either
 unsolvable or has a most general unifier, we can define the notion of \bfit{most
@@
 deep inference systems has already been discussed
-elsewhere~\cite{brunnler:06:herbrand,alertubella:guglielmi:18}.
-\juihsuan{references added. Please check if they are the right ones.}
+elsewhere (e.g.~\cite{brunnler:06:herbrand,alertubella:guglielmi:18}).%
+%\juihsuan{references added. Please check if they are the right ones.}
 \footnote{In the deep
@@
       \vlde{\set{\wrD,\fequ}}{}{B}{
-        \vlde{\set{\acD}}{}{B'}{
+        \vlde{\set{\acD,\cfaD}}{}{B'}{
           \vlde{\set{\me,\mfaD,\mexD,\fequ}}{}{A'}{
@@
 
+%%\todo{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{From $\FOMLL$ Proofs to Fonets}
+
+Let $\Pi$ be a $\FOMLL$ proof of a rectified sequent $\sqn\Gamma$. We now show
+how $\Pi$ is translated into a linked fograph
+$\fographof\Pi=\tuple{\graphof\Gamma,\linkingof\Pi}$. We proceed
+inductively, making a case analysis on the last rule in $\Pi$. At the
+same time we are constructing a dualizer $\dsubstof\Pi$, so that in the
+end we can conclude that $\fographof\Pi$ is in fact a fonet.
+\begin{enumerate}
+  %\setlength\itemsep{.5ex}
+\item $\Pi$ is $\vlinf{\axr}{}{\sqn{a,\cneg a}}{}$ : Then the only
+  link is $\set{a, \dual{a}}$, and $\dsubstof\Pi$ is empty.
+\item $\Pi$ is $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ : Then
+  $\linkingof\Pi$ and $\dsubstof\Pi$ are both empty.
+\item The last rule in $\Pi$ is $\vliinf{\mixr}{}{\sqn{\Gamma',\Gamma''}}{\sqn\Gamma'}{\sqn\Gamma''}$ :
+  By induction hypothesis, we have proofs $\Pi'$ and $\Pi''$ of $\Gamma'$ and $\Gamma''$, respectively. We have
+  $\graphof{\Gamma}=\graphof{\Gamma'}+\graphof{\Gamma''}$ and let
+  $$\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''}
+  \qquand
+  \dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$$
+\item The last rule in $\Pi$ is $\vlinf{\vlor}{}{\sqn{\Gamma_1,A\vlor
+    B}}{\sqn{\Gamma_1,A,B}}$ : By induction hypothesis, there is
+  proofs $\Pi'$ of $\Gamma'={\Gamma_1,A,B}$. We have
+  $\graphof{\Gamma}=\graphof{\Gamma'}$ and let
+  $\linkingof\Pi\;=\;\linkingof{\Pi'}$ and
+  $\dsubstof\Pi=\dsubstof{\Pi'}$.
+\item The last rule in $\Pi$ is $\vliinf{\vlan}{}{\sqn{\Gamma_1,A\vlan
+    B, \Gamma_2}}{\sqn{\Gamma_1,A}}{\sqn{B,\Gamma_2}}$ : By induction
+  hypothesis, we have proofs $\Pi'$ and $\Pi''$ of
+  $\Gamma'=\Gamma_1,A$ and $\Gamma''=B,\Gamma_2$, respectively. We
+  have $\graphof{\Gamma}=\graphof{\Gamma_1}+\mbox{$(\graphof A\times\graphof
+  B)$}+\graphof{\Gamma_2}$ and we let
+  $$\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''} \qquand
+  \dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$$
+\item The last rule in $\Pi$ is
+  $\vlinf{\exists}{}{\sqn{\Gamma_1,\exists x.A}}
+  {\sqn{\Gamma_1,A\ssubst{x}{t}}}$ : By induction hypothesis, there is
+  a $\Pi'$ of $\Gamma'={\Gamma_1,A\ssubst{x}{t}}$.  For each atom in
+  $\Gamma'=\Gamma_1, A \ssubst{x}{t}$, there is a corresponding atom
+  in $\Gamma=\Gamma_1, \exists x.A$. We can therefore define the
+  linking $\linkingof{\Pi}$ from the linking $\linkingof{\Pi'}$ via
+  this correspondence. Then, we let $\dsubstof\Pi$ be
+  $\dsubstof{\Pi'}+\ssubst{x}{t}$. Since $\Gamma$ is rectified $x$
+  does not yet occur in $\dsubstof{\Pi'}$. Hence $\dsubstof\Pi$ is a
+  dualizer of $\fographof\Pi$.
+\item The last rule in $\Pi$ is $\vlinf{\forall}{\text{($x$ not free
+    in $\Gamma_1$)}}{\sqn{\Gamma_1,\forall x.A}}{\sqn{\Gamma_1,A}}$ :
+  By induction hypothesis, there is a proof $\Pi'$ of
+  $\Gamma'={\Gamma_1,A}$, which has the same atoms as in
+  $\Gamma=\Gamma_1, \forall x.A$.  Hence, we can let
+  $\linkingof\Pi\;=\;\linkingof{\Pi'}$ and
+  $\dsubstof\Pi=\dsubstof{\Pi'}$. 
+\end{enumerate}
+%\end{itemize}
+
+\begin{thm}
+  \label{thm:MLL1->fonet}
+  If $\Pi$ is a $\FOMLL$ proof of a rectified sequent $\sqn\Gamma$,
+  then $\fographof\Pi$ is a fonet and $\dsubstof\Pi$ is a dualizer for it.
+\end{thm}
+
+\begin{proof}
+  We have to show that none of the operations above can introduce a
+  bimatching. For cases 1--6, this is immediate. For case 7, observe
+  that there is a potential dependency from each existential binder in
+  $\graphof{\Gamma'}$ to the new $x$-binder $\single x$ in
+  $\graphof{\Gamma}$. However, observe that this $\single x$ vertex is
+  not connected to any vertex in $\graphof{\Gamma'}$, and hence no
+  such new dependency can be extended to a bimatching. That
+  $\dsubstof\Pi$ is a dualizer for $\fographof\Pi$ follows immediately
+  from the construction. Hence,  $\fographof\Pi$ is a fonet.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{From $\FOMLS$ Proofs to Fonets}
+
+There is a more direct path from a $\FOMLL$ proof $\Pi$ of a rectified
+sequent $\Gamma$ to the linked fograph $\fographof\Pi$: simply take
+the fograph $\graphof\Gamma$, and let the equivalence classes of
+$\linkingof\Pi$ be all the atom pairs that meet in an instance of
+$\ax$, and $\dsubstof\Pi$ is simply the collection of all subtitutions
+of all the instances of the $\exists$-rule in $\Pi$.
+%
+We have chosen the more cumbersome path above because it gives us a
+direct proof of Theorem~\ref{thm:MLL1->fonet}.
+%
+However, for translating $\FOMLS$ derivation into fonets, we employ
+exactly that direct path.
+
+A derivation $\Deri$ in $\FOMLS$ is \bfit{rectified} if every line in $\Deri$ is
+rectified.
+
+\begin{lemma}
+  Let  $\Deri$ be a $\FOMLS$ proof of a formula $A$. Then $\Deri$ is rectified iff $A$ is rectified.
+\end{lemma}
+
+\begin{proof}
+   The only rules involving bound
+   variables are $\forall$ and $\exists$ which both remove a binder (and
+   all occurrences of the variable it binds).
+\end{proof}
+
+Hence, for a non-rectified  $\FOMLS$ derivation $\Deri$ in $\FOMLS$ we can
+define its \bfit{rectification} $\rectif\Deri$ inductively, by recifying each
+line, proceeding step-wise
+from conclusion to premise.\footnote{As for formulas,
+the rectification of a derivation is unique up to renaming of bound
+variables.}
+
+A rectified derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ determines a
+substitution which maps the existential bound variables occurring in
+$A$ to the terms substituted for them in the instances of the
+$\exists$-rule in $\Phi$. We denote this substitution with
+$\dsubstof\Phi$ and call it the \bfit{dualizer} of $\Deri$. Furthermore, every atom occuring in the conclusion $A$
+must be consumed by a unique instance of the rule $\aiD$ in
+$\Deri$. This allows us to define a (partial) equivalence relation
+$\linkingof\Deri$ on the atom occurrences in $A$ by $a\linkingof\Deri
+b$ if $a$ and $b$ are consumed by the same instance of $\aiD$
+in~$\Deri$. We call $\linkingof\Deri$ the \bfit{linking} of~$\Deri$.
+
+\todo{example here}
+
+\begin{thm}\label{thm:MLS1->fonet}
+  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a recified derivation. Then
+  $\tuple{\graphof{A},\linkingof{\Deri}}$ is fonet and $\dsubstof{\Deri}$ is a dualizer for it.
+\end{thm}
+
+\begin{proof}
+  We have to show that no inference rule in $\FOMLS$ can introduce a
+  bimatching. For the rules $\forall$, $\aiD$, $\tttD$, $\fequ$, and
+  $\mix$, this is immediate, as they do not introduce new edges in the
+  cograph connecting two vertices that are each incident to a leap
+  edge.
+The only rules that can do that are $\sw$ and $\exists$.
+For the $\sw$-rule, we refer reader to~\cite{retore:???} or \cite{gug:SIS} or \cite{dissvonlutz} where this property has been shown in detail.
+For the rule $\exists$, a potential bimatching can only be created by a dependency between the \todo{need frame?}
+\end{proof}
+
+\begin{remark}
+  There is an alternative path of proving Theorem~\ref{thm:MLS1->fonet}
+  by translating $\Deri$ to an $\FOMLL$-proof $\Pi$, observing that
+  this process preserves the linking and the dualizer. However, for
+  this, we have to extent the construction above to the $\cut$-rule,
+  and then show that linking and dualizer of a sequent proof $\Pi$ are
+  invariant under cut elimation. This can be done similarly to
+  unification nets in~\cite{hughes:unifn}.
+\end{remark}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{From Fonets to $\FOMLL$ Proofs}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{From Fonets to $\FOMLS$ Proofs}
+
+%% \begin{thm}
+%%   Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
+%%   the graph $\graphof{\rectif A}$ forms a fonet whose linking is
+%%   $\linkingof{\rectif\Deri}$ and whose dualizer is
+%%   $\substof{\rectif\Deri}$.
+%% \end{thm}
+
+%% \begin{proof}
+%%   Apply Lemma~\ref{lem:MLS1->fonet} to the rectification $\rectif\Deri$ of $\Deri$.
+%% \end{proof}
+
+\begin{thm}
+  Let $\gC$ be a fonet with linking $\linkingof\gC$, let $\dualizer$ be a dualizer
+  for $\gC$, and let $A$ be a formula with $\graphof A=\gC$.  Then
+  there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
+  $\linkingof\gC=\linkingof{\Deri}$ and $\dualizer=\substof{\Deri}$.
+\end{thm}
+
+\begin{proof}
   \todo{}
+\end{proof}
 
@@
 \todo{}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Translation between $\FOMLS$ and Fonets}
-
-A derivation $\Deri$ is \bfit{rectified} if every line in $\Deri$ is
-rectified.  For a non-rectified derivation $\Deri$ in $\FOMLS$ we can
-define its \bfit{rectification} $\rectif\Deri$ by recifying each
-line. In $\FOMLS$ this can be done inductively, proceeding step-wise
-from conclusion to premise, as the only rules involving bound
-variables are $\forall$ and $\exists$ which both remove a binder (and
-all occurrences of the variable it binds).\footnote{As for formulas,
-the rectification of a derivation is unique up to renaming of bound
-variables.}\todo{check if we need that $\Deri$ has premise $\ttt$}.
-
-A derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ determines a
-substitution which maps the existential bound variables occurring in
-$A$ to the terms substituted for them in the instances of the
-$\exists$-rule in $\Phi$. We denote this substitution with
-$\substof\Phi$. Furthermore, every atom occuring in the conclusion $A$
-must be consumed by a unique instance of the rule $\aiD$ in
-$\Deri$. This allows us to define a (partial) equivalence relation
-$\linkingof\Deri$ on the atom occurrences in $A$ by $a\linkingof\Deri
-b$ if $a$ and $b$ are consumed by the same instance of $\aiD$
-in~$\Deri$. We call $\linkingof\Deri$ the \bfit{linking} of~$\Deri$.
-
-\todo{example here}
-
-\begin{lemma}\label{lem:MLS1->fonet}
-  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a recified derivation. Then
-  the graph $\graphof{A}$ forms a fonet whose linking is
-  $\linkingof{\Deri}$ and whose dualizer is
-  $\substof{\Deri}$.
-\end{lemma}
-
-\begin{proof}
-  \todo{}  
-\end{proof}
-
-\begin{thm}
-  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
-  the graph $\graphof{\rectif A}$ forms a fonet whose linking is
-  $\linkingof{\rectif\Deri}$ and whose dualizer is
-  $\substof{\rectif\Deri}$.
-\end{thm}
-
-\begin{proof}
-  Apply Lemma~\ref{lem:MLS1->fonet} to the rectification $\rectif\Deri$ of $\Deri$.
-\end{proof}
-
-\begin{thm}
-  Let $\gC$ be a fonet with linking $\linkingof\gC$, let $\dualizer$ be a dualizer
-  for $\gC$, and let $A$ be a formula with $\graphof A=\gC$.  Then
-  there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
-  $\linkingof\gC=\linkingof{\Deri}$ and $\dualizer=\substof{\Deri}$.
-\end{thm}
-
-\begin{proof}
-  \todo{}
-\end{proof}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-21 main.tex
rule permutation

@@
   Let $\vlinf{\rr}{}{\Scons B}{\Scons A}$ be an inference rule in
-  $\FOMLS$ other than $\aiD$ and $\forall$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
+  $\FOMLS$ other than $\aiD$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
 \end{lemma}
-\juihsuan{For this, we need the introduction rule of $\fff$ in $\FOMLL$
-(consider the $\aiD$ rule). But if we add it, we'll need the
-$\mathsf{ai}\downarrow$ rule to have Lemma \ref{lem:MLL1->MLS1}}
-\lutz{shit. so, we need another way to prove lemma~\ref{lem:MLS1->MLL1}, I'd like to avoid $\fff$-intro.}
-\juihsuan{This lemma holds for all the rules except $\aiD$ (we may need to
-mention that $A \fequ B \Rightarrow \ \vdash_{\FOMLL} \dual{B}, A$). The inductive
-step for $\aiD$ in the proof of Lemma \ref{lem:MLS1->MLL1} can be solved by
-replacing $t$ with $a \vlor \dual{a}$ and the $\ttt$-rule with the $\ax$
-rule followed by the $\vlor$ rule}\lutz{yes! and similar for $\forall$. Can you do that?}
-
-\lutz{actually NO! we can prove $\sqn{\fff,\ttt}$ using $\ax$ without a special rule for $\fff$. So can you please undo the changes and delete the comments?}
 \begin{proof}
-  This is a straightforward exercise that we leave to the reader. (Note that the $\ax$-rule can be applied to $\sqn{\fff,\ttt}$ in the cases of $\rr \in \set{\aiD, \faD}$.)
+  This is a straightforward exercise that we leave to the reader. (Note that the
+$\ax$-rule can be applied to $\sqn{\fff,\ttt}$ in the cases of $\rr = \faD$.)
 \end{proof}
@@
       $, and we get a proof $\Pi'$ of $\sqn{\Scons{a \vlor \cneg a}}$.
-    \item $\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
-      In this case, we replace simultaneously in $\Pi$ the corresponding
-      occurrences of $\ttt$ with $\forall x.\ttt$ and the rule instance
-      $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
-      $
-      \vlderivation{
-        \vlin{\forall}{}{\sqn{\forall x.\ttt}}{
-          \vlin{\axr}{}{\sqn{\ttt}}{
-            \vlhy{}}}}
-      $, and we get a proof $\Pi'$ of $\sqn{\Scons{\forall x.\ttt}}$.
-    \item $\rr \notin \set{\aiD, \faD}$ :
-      By Lemma~\ref{lem:context}, we have a $\FOMLL$ proof of
+    %\item $\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
+     % In this case, we replace simultaneously in $\Pi$ the corresponding
+     % occurrences of $\ttt$ with $\forall x.\ttt$ and the rule instance
+     % $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
+     % $
+     % \vlderivation{
+     %   \vlin{\forall}{}{\sqn{\forall x.\ttt}}{
+     %     \vlin{\axr}{}{\sqn{\ttt}}{
+     %       \vlhy{}}}}
+     % $, and we get a proof $\Pi'$ of $\sqn{\Scons{\forall x.\ttt}}$.
+    \item In the other cases,
+      by Lemma~\ref{lem:context}, we have a $\FOMLL$ proof of
       $\sqn{\cneg{\Scons A},\Scons B}$. We can compose them via $\cutr$:
@@
 
-First, if an instance $\vlinf{\weakr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma}}$
- of $\weakr$ is followed by a rule in which $A$ is not in the principal
+First, if an instance of $\vlinf{\weakr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma}}$
+ is followed by a rule in which $A$ is not in the principal
 formula, it can be permuted downwards.
@@
 \begin{proof}
-  \todo{}
+  First, observe that the $\exists$ rule can be permuted downwards over all the
+other rules since $A\ssubst{x}{t}$ has the same structure as $A$ and none of the
+other rules has a premise of the form $\Scons{\exists x.A}$. It suffices now to
+prove that for all $r_1 \in \set{\forall, \aiD, \tttD}$, for all $r_2 \in
+\set{\sw, \mix, \fequ}$, we can permute $r_1$ upwards over $r_2$.
+  We show some cases here, and leave the other to the reader.
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\aiD}{}{\Scons{(A \vlan (a \vlor \cneg a)) \vlor C}}{
+      \vlin{\sw}{}{\Scons{(A \vlan \ttt) \vlor C}}{
+        \vlhy{\Scons{A \vlan (\ttt \vlor C)}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\sw}{}{\Scons{(A \vlan (a \vlor \cneg a)) \vlor C}}{
+      \vlin{\aiD}{}{\Scons{A \vlan ((a \vlor \cneg a) \vlor C)}}{
+        \vlhy{\Scons{A \vlan (\ttt \vlor C)}}}}}
+  \end{equation*}
+  \begin{equation*}
+    \vlderivation{
+      \vlin{\tttD}{}{\Scons{(A \vlor (B \vlan \ttt))}}{
+        \vlin{\mix}{}{\Scons{A \vlor B}}{
+          \vlhy{\Scons{A \vlan B}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\mix}{}{\Scons{(A \vlor (B \vlan \ttt)}}{
+      \vlin{\tttD}{}{\Scons{A \vlan (B \vlan \ttt)}}{
+        \vlhy{\Scons{A \vlan B}}}}}
+  \end{equation*}
+
+  \tocheck{}
 \end{proof}
@@
   $\vlderivation{
-      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{}{B}{
+      \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{}{B}{
         \vlhy{A}}}$

### 2021-01-22 main.tex
linear

--- 2021-01-21 main.tex
@@
 % *** PACKAGES *** %
+%\usepackage{fdsymbol}
 
@@
 \usepackage{ebproof}
+%\usepackage{stmaryrd}
 \usepackage{virginialake}
@@
 %\newcommand{\graphof}[1]{\mathbb{G}(#1)}
+
+\newcommand{\frameof}[1]{#1^\star}
 
@@
 
+Now we are going to show how from a given fonet
+$\tuple{\gC,\linkingof\gC}$ we can construct a sequent proof $\Pi$ in
+$\FOMLL$ such that $\fographof\Pi=\tuple{\gC,\linkingof\gC}$. In the
+proof net literature, this operation is also called
+\emph{sequentialization}. The basic idea behind our sequentialization
+is to construct a proposional linked cograph, called the \bfit{frame}~\cite{hughes:unifn}
+of $\gC$, in which the dependencies between the binders in $\gC$ are
+encoded as links. Then we can apply the \emph{splitting tensor
+theorem} to the frame, and then reconstruct the sequent proof $\Pi$.
+
+More formally, let $\Gamma$ be a sequent with $\graphof\Gamma=\gC$, to which we
+exhaustively apply the following
+subformula rewriting steps, to obtain a sequent $\frameof\Gamma$:
+\begin{enumerate}
+\item {\bf Encode dependencies as fresh links.} For each dependency
+  $\pair{\single x,\single y}$ in $\gC$, with corresponding
+  subformulas $\exists x A$ and $\forall y B$ in $\Gamma$, we pick a
+  fresh (nullary) predicate symbol $q$, and then replace $\exists
+  x. A$ by $q \cand \exists x. A$, and replace $\forall y. B$ by
+  $\dual q \cor \forall y. B$.
+\item {\bf Erase quantifiers.} After step 1, remove all the
+  quantifiers, i.e., replace $\exists x.A$ by $A$ and replace $\forall
+  y.B$ by $B$ everywhere.
+\item {\bf Simplify atoms.} After step 2, replace every predicate
+  $p(t_1 \cdots t_n)$ (resp. $\dual p(t_1 \cdots t_n)$) with a nullary
+  predicate symbol $p$ (resp.~$\dual p$)
+\end{enumerate}
+The $\linkingof{\frameof\Gamma}$ consists of the pairs induced by
+$\linkingof\gC$ and the new pairs $\set{q,\dual q}$ introduced in
+step~1 above.  Now we define the \bfit{frame} of $\gC$, denoted
+$\frameof\gC$, as
+$\tuple{\graphof{\frameof\Gamma},\linkingof{\frameof\Gamma}}$.
+
+\begin{lemma}\label{lem:frame}
+  A linked fograph $\gC$ induces a bimatching iff its frame $\frameof\gC$ induces a bimatching.
+\end{lemma}
+
+Note that the linking $\lambda_m$ is a valid $\MLLm$ proof net.
+
+We define the \bfit{frame} of a linked fograph to be the linked cograph defined as follows:
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-22 main.tex
rule permutation

@@
   \vlderivation{
+    \vlin{\cD}{}{\forall x.A}{
+      \vlin{\equiv}{(x \notin fv(\forall x.A))}{(\forall x.A) \vlor (\forall x.A)}{
+        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor A)}{
+          \vlhy{\forall x.\forall x.A}}}}}
+  $$.
+  $$
+  \vlderivation{
     \vlin{\cD}{}{(A \vlor B) \vlan (C \vlor D)}{
@@
 
-  Suppose that $\Gamma$ is provable in $\FOLK$, then so is $\form{\Gamma}$.
-Consider a proof
-$ \vlderivation{
-        \vltrl{}{\FOLK}{\Deri}{\sqns{\form{\Gamma}}}{
-          \vlhy{\quad}}{
-          \vlhy{}}{
-          \vlhy{}}} $
-
 First, if an instance of $\vlinf{\weakr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma}}$
@@
 \vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, A\ssubst{x}{t}}}{
+  \vlin{\weakr}{}{\sqns{\Gamma, \exists x.A}}{
     \vlhy{\sqns{\Gamma}}}}
@@
 \set{\sw, \mix, \fequ}$, we can permute $r_1$ upwards over $r_2$.
-  We show some cases here, and leave the other to the reader.
+  We show some cases here, and leave the others to the reader.
   \begin{equation*}
@@
 \begin{proof}
-  \todo{}
+  First, a derivation consisting of an instance of $\wrD$ followed by $\rr \in \set{\acD, \cfaD,
+\me, \mfaD, \mexD}$ can be either replaced by a derivation consisting of $\wrD$
+only or the instance of $\wrD$ can be permuted downwards. We show some cases
+here, and leave the others to the reader.
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
+      \vlin{\wrD}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
+        \vlhy{\Scons{\forall x.A}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{\Scons{\forall x.(A \vlor B)}}{
+      \vlhy{\Scons{\forall x.A}}}}
+  \end{equation*}
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\me}{}{\Scons{(A \vlor B) \vlan (C \vlor D)}}{
+      \vlin{\wrD}{}{\Scons{(A \vlan C) \vlor (B \vlan D)}}{
+        \vlhy{\Scons{A \vlan C}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{\Scons{(A \vlor B) \vlan (C \vlor D)}}{
+      \vlin{\wrD}{}{\Scons{(A \vlor B) \vlan C}}{
+        \vlhy{\Scons{A \vlan C}}}}}
+  \end{equation*}
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\acD}{}{\Scons{a}}{
+      \vlin{\wrD}{}{\Scons{a \vlor a}}{
+        \vlhy{\Scons{a}}}}}
+  \leadsto
+  \vlderivation{
+    \vlhy{\Scons{a}}}
+  \end{equation*}
+
+  For $\rr_1 \in \set{\me, \mfaD, \mexD}$, $\rr_2 \in \set{\acD, \cfaD}$,
+$\rr_1$ can be permuted upwards over $\rr_2$ (with some $\fequ$ inserted). The only non-trivial case is shown below:
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
+      \vlin{\cfaD}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
+        \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
+      \vlin{\fequ}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
+        \vlin{\mfaD}{}{\Scons{\forall x.(\forall x.A \vlor B)}}{
+          \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}}
+  \end{equation*}
+  \todo{permutation with $\fequ$}
 \end{proof}

### 2021-01-22 main.tex
fonet->MLL

--- 2021-01-22 main.tex
@@
 \newcommand{\linkingof}[1]{\sim_{#1}}
+\newcommand{\linking}{\sim}
 \newcommand{\mapof}[1]{\lfloor{#1}\rfloor}
@@
 
+%% \begin{thm}
+%%   Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
+%%   the graph $\graphof{\rectif A}$ forms a fonet whose linking is
+%%   $\linkingof{\rectif\Deri}$ and whose dualizer is
+%%   $\substof{\rectif\Deri}$.
+%% \end{thm}
+
+%% \begin{proof}
+%%   Apply Lemma~\ref{lem:MLS1->fonet} to the rectification $\rectif\Deri$ of $\Deri$.
+%% \end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 $\linkingof\gC$ and the new pairs $\set{q,\dual q}$ introduced in
-step~1 above.  Now we define the \bfit{frame} of $\gC$, denoted
+step~1 above. We call $\frameof\Gamma$ the \bfit{frame} of $\Gamma$ and we define the \bfit{frame} of $\gC$, denoted
 $\frameof\gC$, as
-$\tuple{\graphof{\frameof\Gamma},\linkingof{\frameof\Gamma}}$.
+$\tuple{\graphof{\frameof\Gamma},\linkingof{\frameof\Gamma}}$, and we immediately have the following:
 
@@
 
-Note that the linking $\lambda_m$ is a valid $\MLLm$ proof net.
-
-We define the \bfit{frame} of a linked fograph to be the linked cograph defined as follows:
+Let $\Gamma$ be a propositional sequent and $\linkingof\Gamma$ be a
+linking for $\graphof\Gamma$. A conjunction formula $A\vlan B$ is
+\bfit{splitting} or a \bfit{splitting tensor} if
+$\Gamma=\Gamma',A\vlan B,\Gamma''$ and
+$\mathord{\linkingof\Gamma}=\mathord{\linking_1}\cup\linking_2$, such
+that $\linking_1$ is a linking for $\graphof{\Gamma',A}$ and
+$\linking_2$ is a linking for $\graphof{B,\Gamma''}$, i.e., removing
+the $\vlan$ from $A\vlan B$ splits the linked fograph $\tuple{
+  \graphof\Gamma,\linkingof\Gamma}$ into two fographs.
+We say that $\tuple{
+  \graphof\Gamma,\linkingof\Gamma}$ is \bfit{mixed} iff 
+$\Gamma=\Gamma',\Gamma''$ and
+$\mathord{\linkingof\Gamma}=\mathord{\linking_1}\cup\linking_2$, such
+that $\linking_1$ is a linking for $\graphof{\Gamma'}$ and
+$\linking_2$ is a linking for $\graphof{\Gamma''}$.
+Finally, $\tuple{
+  \graphof\Gamma,\linkingof\Gamma}$ is \bfit{splittable} if it is mixed or has a splitting tensor.
+
+The purpose of introducing the frame is the following theorem.
+
+\begin{thm}
+  \label{thm:splitting}
+  Let $\Gamma$ be a propositional sequent containing only atoms
+  and $\vlan$-formulas, and $\linkingof\Gamma$ be a
+  linking for $\graphof\Gamma$. If $\tuple{
+    \graphof\Gamma,\linkingof\Gamma}$ does not induce a bimatching then it is splittable.
+\end{thm}
+
+This is the well-know splitting-tensor-theorem
+\cite{girard:87,danos:regnier:89}, adapted for the presence of
+$\mix$. In the setting of linked cographs, it has first been proved by
+Retor\'e~\cite{retore:03,retore:??}\lutz{that ``handsome'' report he mentioned in
+  the talk}. We use it now for our sequentialization:
+
+\begin{thm}
+  \label{thm:fonet->MLL}
+  Let $\tuple{\gC,\linkingof\gC}$ be a fonet, and let $\Gamma$ be a sequent with $\graphof\Gamma=\gC$. Then there is an
+  $\FOMLL$-proof $\Pi$ of $\Gamma$, such that
+  $\fographof\Pi=\tuple{\gC,\linkingof\gC}$.
+\end{thm}
+
+\begin{proof}
+  Let $\dsubstof\gC$ be the dualizer of $\tuple{\gC,\linkingof\gC}$.  We
+  proceed by induction on the size of $\Gamma$ (i.e., the number of
+  symbols in it, without counting the commas). If $\Gamma$ contains a
+  formula with $\vlor$-root, or a formula $\forall x.A$, we can
+  immediately apply the $\vlor$-rule or the $\forall$-rule of $\FOMLL$
+  and proceed by induction hypothesis. If $\Gamma$ contains a formula
+  $\exists x.A$ such that the correponding binder $\single x$ in $\gC$
+  has no dependency, then we can apply the $\exists$-rule, chosing the
+  term $t$ as determined by $\dsubstof\gC$, and proceed by induction
+  hypothesis.  Hence, we can now assume that $\Gamma$ contains only
+  atoms, $\vlan$-formulas, or formulas of shape $\exists x.A$, where
+  the vertex $\single x$ has dependencies. Then the frame
+  $\tuple{\graphof{\frameof\Gamma},\linkingof{\frameof\Gamma}}$ does
+  not induce a bimatching and contains only atoms and
+  $\vlan$-formulas, and is therefore splittable. If it is mixed, then
+  we can apply the $\mix$-rule to $\Gamma$ and apply the induction
+  hypothesis to the two components. If it is not mixed then there must
+  be a splitting tensor. If the splitting $\vlan$ is already in
+  $\Gamma$, then we can apply the $\vlan$-rule and proceed by
+  induction hypothesis on the two branches. However, if
+  $\frameof\Gamma$ is not mixed and all splitting tensors are
+  $\vlan$-formulas introduced in step~1 of the frame construction,
+  then we get a contradiction as in that case there must be a $\vlor$- or $\forall$-formula in $\Gamma$.
+  \lutz{can anyone give a good argument here?}
+\end{proof}
 
@@
 \subsection{From Fonets to $\FOMLS$ Proofs}
-
-%% \begin{thm}
-%%   Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
-%%   the graph $\graphof{\rectif A}$ forms a fonet whose linking is
-%%   $\linkingof{\rectif\Deri}$ and whose dualizer is
-%%   $\substof{\rectif\Deri}$.
-%% \end{thm}
-
-%% \begin{proof}
-%%   Apply Lemma~\ref{lem:MLS1->fonet} to the rectification $\rectif\Deri$ of $\Deri$.
-%% \end{proof}
 

### 2021-01-22 main.tex
fonet -> MLS

@@
 $\exists$-rule in $\Phi$. We denote this substitution with
-$\dsubstof\Phi$ and call it the \bfit{dualizer} of $\Deri$. Furthermore, every atom occuring in the conclusion $A$
-must be consumed by a unique instance of the rule $\aiD$ in
-$\Deri$. This allows us to define a (partial) equivalence relation
-$\linkingof\Deri$ on the atom occurrences in $A$ by $a\linkingof\Deri
-b$ if $a$ and $b$ are consumed by the same instance of $\aiD$
-in~$\Deri$. We call $\linkingof\Deri$ the \bfit{linking} of~$\Deri$.
+$\dsubstof\Phi$ and call it the \bfit{dualizer} of
+$\Deri$. Furthermore, every atom occuring in the conclusion $A$ must
+be consumed by a unique instance of the rule $\aiD$ in $\Deri$. This
+allows us to define a (partial) equivalence relation $\linkingof\Deri$
+on the atom occurrences in $A$ by $a\linkingof\Deri b$ if $a$ and $b$
+are consumed by the same instance of $\aiD$ in~$\Deri$. We call
+$\linkingof\Deri$ the \bfit{linking} of~$\Deri$, and define
+$\fographof\Deri=\tuple{\graphof{A},\linkingof{\Deri}}$.
 
@@
   Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a recified derivation. Then
-  $\tuple{\graphof{A},\linkingof{\Deri}}$ is fonet and $\dsubstof{\Deri}$ is a dualizer for it.
+  $\fographof\Deri$ is a fonet and $\dsubstof{\Deri}$ a dualizer for it.
 \end{thm}
@@
 \begin{thm}
-  \label{thm:fonet->MLL}
+  \label{thm:fonet->MLL1}
   Let $\tuple{\gC,\linkingof\gC}$ be a fonet, and let $\Gamma$ be a sequent with $\graphof\Gamma=\gC$. Then there is an
@@
 
+We can now straightforwardly obtain the same result for $\FOMLS$:
+
 \begin{thm}
-  Let $\gC$ be a fonet with linking $\linkingof\gC$, let $\dualizer$ be a dualizer
-  for $\gC$, and let $A$ be a formula with $\graphof A=\gC$.  Then
-  there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
-  $\linkingof\gC=\linkingof{\Deri}$ and $\dualizer=\substof{\Deri}$.
+  \label{thm:fonet->MLS1}
+  Let $\tuple{\gC,\linkingof\gC}$ be a fonet, and let $C$ be a formula with $\graphof C=\gC$. Then there is
+  a derivation $\vlder{\FOMLS}{\Deri}{C}{\ttt}$ such that $\fographof\Deri=\tuple{\gC,\linkingof\gC}$.
+  %% an
+  %% $\FOMLL$-proof $\Pi$ of $\Gamma$, such that
+  %% $\fographof\Pi=\tuple{\gC,\linkingof\gC}$.
+  %% Let $\gC$ be a fonet with linking $\linkingof\gC$, let $\dualizer$ be a dualizer
+  %% for $\gC$, and let $A$ be a formula with $\graphof A=\gC$.  Then
+  %% there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
+  %% $\linkingof\gC=\linkingof{\Deri}$ and $\dualizer=\substof{\Deri}$.
 \end{thm}
@@
 \begin{proof}
-  \todo{}
-\end{proof}
+  We apply Theorem~\ref{thm:fonet->MLL1} to obtain a sequent
+  proof~$\Pi$ of $\sqn C$ with
+  $\fographof\Pi=\tuple{\gC,\linkingof\gC}$. Then we apply
+  Lemma~\ref{lem:MLL1->MLS1}, observing that the translation from
+  $\FOMLL$ to $\FOMLS$ preserves linking and dualizer.
+\end{proof}
+
+\begin{remark}
+  Note that it is also possible to do a direct ``sequentialization''
+  into the deep inference system $\FOMLS$, using the techniques
+  presented in \cite{dissvonlutz} and \cite{str:MLL2}.
+\end{remark}
 

### 2021-01-23 main.tex
minor fixes

@@
 link or a dependency. The \bfit{leap graph} $\lgC$ of $\gC$ is the undirected
-graph $\tuple{\vC, \lpC}$ where $\lpC$ is the set of leaps of $\gC$. A vetex set $W \subseteq \vC$ induces a \bfit{matching} in
+graph $\tuple{\vC, \lpC}$ where $\lpC$ is the set of leaps of $\gC$. A vertex set $W \subseteq \vC$ induces a \bfit{matching} in
 $\gC$ if for all $w \in W$, $N(w) \cap W$ is a singleton. We say that $W$ induces a
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Contraction and Weakining}
+\subsection{Contraction and Weakening}
 
@@
 \end{equation*}
-Note that $\fequ$ is required here since the permutaion of formulas is implicit
+Note that $\fequ$ is required here since the permutation of formulas is implicit
 in $\FOMLL$.
@@
 $\linkingof\Pi$ be all the atom pairs that meet in an instance of
-$\ax$, and $\dsubstof\Pi$ is simply the collection of all subtitutions
+$\ax$, and $\dsubstof\Pi$ is simply the collection of all substitutions
 of all the instances of the $\exists$-rule in $\Pi$.
@@
 Hence, for a non-rectified  $\FOMLS$ derivation $\Deri$ in $\FOMLS$ we can
-define its \bfit{rectification} $\rectif\Deri$ inductively, by recifying each
+define its \bfit{rectification} $\rectif\Deri$ inductively, by rectifying each
 line, proceeding step-wise
@@
 $\dsubstof\Phi$ and call it the \bfit{dualizer} of
-$\Deri$. Furthermore, every atom occuring in the conclusion $A$ must
+$\Deri$. Furthermore, every atom occurring in the conclusion $A$ must
 be consumed by a unique instance of the rule $\aiD$ in $\Deri$. This
@@
 \begin{thm}\label{thm:MLS1->fonet}
-  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a recified derivation. Then
+  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a rectified derivation. Then
   $\fographof\Deri$ is a fonet and $\dsubstof{\Deri}$ a dualizer for it.
@@
   and then show that linking and dualizer of a sequent proof $\Pi$ are
-  invariant under cut elimation. This can be done similarly to
+  invariant under cut elimination. This can be done similarly to
   unification nets in~\cite{hughes:unifn}.
@@
 \emph{sequentialization}. The basic idea behind our sequentialization
-is to construct a proposional linked cograph, called the \bfit{frame}~\cite{hughes:unifn}
+is to construct a propositional linked cograph, called the \bfit{frame}~\cite{hughes:unifn}
 of $\gC$, in which the dependencies between the binders in $\gC$ are
@@
   A linked fograph $\gC$ induces a bimatching iff its frame $\frameof\gC$ induces a bimatching.
+\juihsuan{induces a bimatching $\rightarrow$ has an induced bimatching}
 \end{lemma}
@@
 $\mix$. In the setting of linked cographs, it has first been proved by
-Retor\'e~\cite{retore:03,retore:??}\lutz{that ``handsome'' report he mentioned in
-  the talk}. We use it now for our sequentialization:
+Retor\'e~\cite{retore:03,retore:99}\lutz{that ``handsome'' report he mentioned in
+  the talk}\juihsuan{added. Check if it's the good one.}. We use it now for our sequentialization:
 
@@
   and proceed by induction hypothesis. If $\Gamma$ contains a formula
-  $\exists x.A$ such that the correponding binder $\single x$ in $\gC$
-  has no dependency, then we can apply the $\exists$-rule, chosing the
+  $\exists x.A$ such that the corresponding binder $\single x$ in $\gC$
+  has no dependency, then we can apply the $\exists$-rule, choosing the
   term $t$ as determined by $\dsubstof\gC$, and proceed by induction
@@
   presented in \cite{dissvonlutz} and \cite{str:MLL2}.
+\juihsuan{missing reference added, check if it's the right one.}
 \end{remark}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\iffalse
+
 \subsection{Unification Nets}
@@
 
-\iffalse
 We proceed by induction on the
@@
 \end{itemize}
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Translation between Unification Nets and Fonets}
+
+\todo{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \fi
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Translation between Unification Nets and Fonets}
-
-\todo{}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   respectively, where $\rectif\acD$ is a $\acD$ that renames the
-  variabes---the propositional variable, as well as the first-order
+  variables---the propositional variable, as well as the first-order
   variable of the same name---as everything is recified, there is no
@@
   graph obtained from $\gA$ by applying $\substof\phi$ to all the
-  labels. Note that $\gA_1$ is not neccesarily a fograph, as binders
+  labels. Note that $\gA_1$ is not necessarily a fograph, as binders
   might be illegal. But it still is a cograph, and we have a
@@
   derivation or an instance of $\me$ which separates the two atoms in
-  the premise. More precisely, we consider the following inferene rule
+  the premise. More precisely, we consider the following inference rule
   \begin{equation}

### 2021-01-23 main.tex
moved stuff out of the way

@@
 \begin{lemma}\label{lem:frame}
-  A linked fograph $\gC$ induces a bimatching iff its frame $\frameof\gC$ induces a bimatching.
-\juihsuan{induces a bimatching $\rightarrow$ has an induced bimatching}
+  A linked fograph $\gC$ induces a bimatching iff its frame $\frameof\gC$ has an induced bimatching.
 \end{lemma}
@@
 $\mix$. In the setting of linked cographs, it has first been proved by
-Retor\'e~\cite{retore:03,retore:99}\lutz{that ``handsome'' report he mentioned in
-  the talk}\juihsuan{added. Check if it's the good one.}. We use it now for our sequentialization:
+Retor\'e~\cite{retore:03,retore:99}. We use it now for our sequentialization:
 
@@
   presented in \cite{dissvonlutz} and \cite{str:MLL2}.
-\juihsuan{missing reference added, check if it's the right one.}
 \end{remark}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\iffalse
-
-\subsection{Unification Nets}
-
-\todo{}
-
-In this paragraph, we associate each formula $A$ with its \bfit{formula tree}
-$\formtree{A}$, a directed
-tree with leaves labelled by atoms, internal nodes labelled by connectives and
-quantifiers, and edges directed from leaves to the root. For a sequent
-$\Gamma = A_1, \ldots, A_n$, we denote with $\formtree{\Gamma}$, the forest
-formed by $\formtree{A_1}, \ldots, \formtree{A_n}$, i.e., the disjoint union of
-$\formtree{A_i}$'s. The \bfit{roots} of $\formtree{\Gamma}$ are the roots of
-${A_i}$'s
-
-Let $\Gamma$ be a sequent in $\FOMLL$. Consider the forest
-$\formtree{\Gamma}$. A \bfit{link} on $\Gamma$ is a pair of
-leaves whose atoms are pre-dual. A \bfit{linking} $\lambda$ on $\Gamma$ is a set
-of
-disjoint links such that each leaf of $\formtree{\Gamma}$ is either labelled by $\ttt$ or
-in exactly one link. Similar to the set of links in linked fographs, a linking can be seen as a
-unification problem, and a \bfit{dualizer} $\dualizer$ of the linking $\lambda$ is an assignment
-unifying all the links in $\lambda$. There exists a \bfit{most general dualizer}
- of $\lambda$ if $\lambda$ has a dualizer. \juihsuan{Now I use the same terminology as for linked fographs}\lutz{use $\delta$ for the dualizer (or even better, make it a macro)}
-A \bfit{dependency} is a pair $(\single \exists x, \single \forall y)$ of nodes
-such that the most general dualizer assigns to $x$ a term containing $y$.
-
-Let $\lambda$ is a linking on $\Gamma$ that has a dualizer.
-The \bfit{unification structure} $\unifstr{\lambda}$
-associated with $\lambda$ is the forest $\formtree{\Gamma}$ together with an undirected
-edge between leaves $l$ and $l'$ for every link $\{l, l'\}$ in $\lambda$ and a
-directed edge from $\single \exists x$ to $\single \forall y$ for every
-dependency $(\single \exists x, \single \forall y)$.
-
-A \bfit{switching graph} of a unification structure $\unifstr{\lambda}$ is any
-derivative of $\unifstr{\lambda}$ obtained by keeping only one edge into each $\cor$
-and $\forall$ and undirecting remaining edges. A linking is \bfit{correct} if it
-is unifiable and all of the switching graphs of its associated unification
-structure are acyclic.
-
-\begin{definition}
-  A \bfit{unification net} on a sequent $\Gamma$ is a correct linking on $\Gamma$.
-\end{definition}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Translation between Unification Nets and $\FOMLL$}
-
-\todo{}
-\begin{thm}\label{thm:MLL1->Unet}
-  If a sequent is provable in $\FOMLL$, then there exists a unification net
-  on it.
-\end{thm}
-
-\begin{proof}
-  We proceed by induction on the proof of $\sqn \Gamma$ in $\FOMLL$, making a
-  case analysis on the bottommost rule instance:
-  \begin{itemize}
-    \setlength\itemsep{.5em}
-    \item $\vlinf{\axr}{}{\sqn{a,\cneg a}}{}$ : the linking $\{a, \dual{a}\}$ is correct.
-    \item $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ : the empty linking is correct.
-    \item $\vliinf{\mixr}{}{\sqn{\Gamma,\Delta}}{\sqn\Gamma}{\sqn\Delta}$ :
-	  By induction hypothesis, there is a correct linking on
-	  $\Gamma$ and another one on $\Delta$, their union giving a
-	  correct linking on $\Gamma, \Delta$.
-    \item $\vlinf{\vlor}{}{\sqn{\Gamma,A\vlor B}}{\sqn{\Gamma,A,B}}$ : By
-	  induction hypothesis, there is a correct linking on $\Gamma, A, B$,
-	  and it is correct on $\Gamma, A \vlor B$ as well.
-    \item $\vliinf{\vlan}{}{\sqn{\Gamma,A\vlan B, \Delta}}{\sqn{\Gamma,A}}{\sqn{B,\Delta}}$ :
-          By induction hypothesis, there is a correct linking on $\Gamma, A$ and
-	  another one on $B, \Delta$, their union giving a correct linking on
-          $\Gamma,A \vlan B, \Delta$.
-    \item $\vlinf{\exists}{}{\sqn{\Gamma,\exists x.A}}
-	  {\sqn{\Gamma,A\ssubst{x}{t}}}$ : By induction hypothesis, there is a
-	  correct linking $\lambda$ on $\Gamma, A\ssubst{x}{t}$.
-	  For each atom in $\Gamma, A \ssubst{x}{t}$, there is a corresponding
-	  atom in $\Gamma, \exists x.A$. There is therefore a linking $\lambda'$
-          on $\Gamma, \exists x.A$ obtained from $\lambda$ via this
-	  correspondence, and it is not difficult to check that $\lambda'$ is
-	  correct as well.
-    \item $\vlinf{\forall}{\text{($x$ not free in
-	  $\Gamma$)}}{\sqn{\Gamma,\forall x.A}}{\sqn{\Gamma,A}}$ : By induction
-          hypothesis, there is a correct linking on $\Gamma, A$, and it is easy
-	  to see that it is a correct linking on $\Gamma, \forall x.A$ as well.
-  \end{itemize}
-  This allows to define a translation $\sqntl\cdot$ from proofs in $\FOMLL$ to unification
-  nets.
-\end{proof}
-
-\begin{thm}\label{thm:sqntl}
-  Any unification net can be obtained via the translation $\sqntl\cdot$ given in Theorem
-  \ref{thm:MLL1->Unet}.
-\end{thm}
-
-To prove this theorem, we need some basic lemmas about connected components in
-switching graphs of unification nets.
-
-\begin{lemma}\label{lem:concomp}
-  The number of connected components of an acylic graph $\gG = \tuple{\vG, \eG}$ is
-equal to $|\eG| - |\vG|$.
-\end{lemma}
-
-\begin{proof}
-  By a straightforward induction on $|\vG|$.
-\end{proof}
-
-\begin{lemma}
-  The number of connected components is the same for any switching graph of a
-unification net.
-\end{lemma}
-
-\begin{proof}
-  An immediate consequence of Lemma \ref{lem:concomp}.
-\end{proof}
-
-In the proof, we also use the notion of \bfit{frame} introduced by Hughes in
-\cite{hughes:unifn}.
-
-\begin{definition}
-Let $\lambda$ be a unification net on an $\FOMLL$ sequent $\Gamma$.
-We define the \bfit{frame} of $\lambda$ by exhaustively applying the following
-subformula rewriting steps, to obtain a linking $\lambda_m$ on an $\MLLm$ sequent $\Gamma_m$:
-
-\begin{enumerate}
-  \item {\bf Encode dependencies as fresh links.} For each dependency $\exists x
-	  \rightarrow \forall y$, with corresponding subformulas $\exists x A$
-		and $\forall y B$, we add a fresh link as follows. Let $P$ be a
-		fresh (nullary) predicate symbol. Replace $\exists x A$ with $P
-		\cand \exists x A$ and $\forall y B$ with $\overline{P} \cor \forall y B$, and add an axiom link between $P$ and $\overline{P}$.
-  \item {\bf Erase quantifiers.} After step 1, erase all the quantifiers. (We no longer need their leaps since they are encoded as links in step 1.
-  \item {\bf Simplify atoms.} After step 2, replace every predicate $Pt_1 \cdots t_n$ with a nullary predicate symbol $P$.
-\end{enumerate}
-\end{definition}
-Note that the linking $\lambda_m$ is a valid $\MLLm$ proof net.
-
-\begin{lemma}\label{lem:concomp_switching}
-Suppose that $\lambda$ is a $\MLLm$ proof net which is connected and such that any of its
-switching graphs is not connected. Then there exists a $\vlor$ node in
-$\unifstr{\lambda}$ such that $\lambda$ is correct on the sequent $\Gamma'$
-obtained from $\Gamma$ by replacing this $\vlor$ by a $\vlan$.
-\end{lemma}
-
-\begin{proof}
-Suppose that such a $\vlor$ node does not exist. Then it is clear that for any
-two nodes, there exists a switching graph containing a path between them and
-this path corresponds to an $AE$-path in \cite{retore:03}. By
-\cite[Propostion~3]{retore:03}, $\lambda$ corresponds to a sequent proof that
-does not use $\mix$, which implies the connectedness of the switching graphs of
-$\lambda$. Contradiction.
-\tocheck{}
-\end{proof}
-
-\begin{lemma}\label{lem:concomp_switching_fo}
-Suppose that $\lambda$ is a $\FOMLL$ proof net which is connected and such that any of its
-switching graphs is not connected. Then there exists a $\vlor$ node in
-$\unifstr{\lambda}$ such that $\lambda$ is correct on the sequent $\Gamma'$
-obtained from $\Gamma$ by replacing this $\vlor$ by a $\vlan$.
-\end{lemma}
-
-\begin{proof}
-  Consider the frame $\lambda_m$ of $\lambda$. The number of any switching
-graph of $\unifstr{\lambda}$ is equal to that of $\unifstr{\lambda_m}$. Apply
-Lemma \ref{lem:concomp_switching} and it is clear that such $\vlor$ cannot be one
-of the fresh $\vlor$'s added during the frame construction.
-\end{proof}
-
-We can now give the proof of Theorem \ref{thm:sqntl}.
-
-\begin{proof}[Proof of Theorem~\ref{thm:sqntl}]
-Let $\lambda$ be a unification net on $\Gamma$. We proceed by induction on the
-number of connected components of the unification structure $\unifstr{\lambda}$:
-\begin{itemize}
-  \item If there is only one connected component, we proceed by induction on the
-number $k$ of connected components of any switching graph of
-$\unifstr{\lambda}$. If $k = 1$, we obtain a proof $\Deri$ in $\FOMLL$ such that
-$\sqntl{\Deri} = \lambda$ by applying \cite[Theorem~3]{hughes:unifn}. If $k > 1$,
-using the Lemma \ref{lem:concomp_switching_fo}, we obtain a sequent $\Gamma'$ on
-which $\lambda$ is correct by transforming a $\vlor$ node into a $\vlan$. By
-induction hypothesis, there is a proof $\Deri'$ in $\FOMLL$ whose translation is
-$\lambda$. By considering the $\vlan$ rule instance corresponding to the $\vlan$
-node in $\Deri'$, we have:
-$
-\Deri' =
-\vlderivation{
-  \vlin{}{}{\sqns{\Gamma'}}{
-  \vlin{}{}{\vlvdots}{
-    \vliin{\vlan}{}{\sqns{\Delta_1, A \vlan B, \Delta_2}}{
-      \vltrl{\Deri_1}{}{}{\sqns{\Delta_1, A}}{
-        \vlhy{\quad}}{
-        \vlhy{}}{
-        \vlhy{}}}{
-      \vltrl{\Deri_2}{}{}{\sqns{B, \Delta_2}}{
-        \vlhy{\quad}}{
-        \vlhy{}}{
-        \vlhy{}}}
-}}}
-$.
-We can thus obtain a proof $\Deri$ of $\Gamma$:
-$
-\Deri =
-\vlderivation{
-  \vlin{}{}{\sqns{\Gamma}}{
-  \vlin{}{}{\vlvdots}{
-    \vlin{\vlor}{}{\sqns{\Delta_1, A \vlor B, \Delta_2}}{
-    \vliin{\mix}{}{\sqns{\Delta_1, A, B, \Delta_2}}{
-      \vltrl{\Deri_1}{}{}{\sqns{\Delta_1, A}}{
-        \vlhy{\quad}}{
-        \vlhy{}}{
-        \vlhy{}}}{
-      \vltrl{\Deri_2}{}{}{\sqns{B, \Delta_2}}{
-        \vlhy{\quad}}{
-        \vlhy{}}{
-        \vlhy{}}}
-}}}}
-$ such that $\sqntl{\Deri} = \lambda$.
-
-  \item If there are $n > 1$ connected components, add a fresh $\vlor$ node
-connecting two formulas belonging to different connected components of $\Gamma$
-to get a new sequent $\Gamma'$. Define a unification net $\lambda'$ on $\Gamma'$
-using the same linking as $\lambda$. By induction hypothesis, since
-$\unifstr{\lambda'}$
-has $n-1$ connected components, there is a $\FOMLL$ proof $\Deri'$ such that
-$\sqntl{\Deri'} = \lambda'$. Consider the $\vlor$ rule instance corresponding
-to the $\vlor$ node in question. Since $\vlor$ is invertible, we can permute
-downwards this rule instance until it becomes the last rule of the proof (note
-that this transformation does not change the image of the proof by the
-translation $\sqntl\cdot$) to get a new proof $\Deri''$ of $\Gamma'$. By deleting the last rule
-instance from $\Deri''$, we obtain a proof $\Deri$ of $\Gamma$ such that
-$\sqntl{\Deri} = \lambda$.
-\tocheck{}
-\end{itemize}
-
-We proceed by induction on the
-number of connectives in $\Gamma$. In the base case, $\Gamma$ is of the form
-\begin{align*}
-p_1(t_{11}, \ldots, t_{1n_1}), \dual{p_1}(t_{11}, \ldots, t_{1n_1}), \ldots, \\
-p_k(t_{k1}, \ldots, t_{kn_k}), \dual{p_k}(t_{k1}, \ldots, t_{kn_k}),
-\underbrace{\ttt, \ldots, \ttt}_\text{$m$ times}
-\end{align*} and
-$\lambda$ is the linking $\set{(a_1, \cneg{a_1}), \ldots, (a_k, \cneg{a_k})}$,
-where $a_i = p_i(t_{i1}, \ldots, t_{in_i})$, which equals to $\sqntl\Pi$, where
-$\Pi$ is the proof consisting of $m$ instances of the $\ttt$ rule, $n$ instances
-$\vlinf{\ax}{}{\sqn a_i, \cneg{a_i}}{}$ of the $\ax$ rule, and followed by
-$m+k-1$ instances of the $\mix$ rule.
-
-Now we consider the inductive cases:
-\begin{itemize}
-  \item $\Gamma = \Delta, A \vlor B$:
-    Let $\Gamma' = \Delta, A, B$. Define $\lambda'$ on $\Gamma'$ using the same
-    links as $\lambda$ by identifying the leaves of $\formtree{\Gamma'}$ with those
-    of $\formtree{\Gamma}$. We now check that $\lambda'$ is a unification net:
-    \begin{itemize}
-      \item The most general dualizer of $\lambda$ is also the most general
-dualizer of $\lambda'$ as they correspond to the same unification problem.
-Hence, the unification structure $\unifstr{\lambda'}$ is equal to the
-restriction of $\unifstr{\lambda}$ to the nodes of $\formtree{\Gamma'}$.
-      \item Every switching graph of $\lambda'$ is acyclic: if there were some
-switching graph of $\unifstr{\lambda'}$ containing a cycle, it would induce a switching
-graph of $\unifstr{\lambda}$ containing also a cycle, by adding an edge from the root of
-$\formtree{A}$ to the $\vlor$ node in question.
-    \end{itemize}
-  \item $\Gamma = \Delta, \forall x.A$:
-    Let $\Gamma' = \Delta, A$. Define $\lambda'$ on $\Gamma'$ using the same
-links as $\lambda$. We now check that $\lambda'$ is a unification net:
-  \begin{itemize}
-    \item The most general dualizer of $\lambda$ is also the most general
-dualizer of $\lambda'$ as they correspond to the same unification problem.
-    \item Every switching graph of $\unifstr{\lambda'}$ is acyclic: if there
-were some switching graph of $\unifstr{\lambda'}$ containing a cycle, it would
-induce a switching graph of $\unifstr{\lambda}$ contaiting also a cycle, by
-adding an edge from the root of $\formtree{A}$ to the $\forall$ node in
-question.
-  \end{itemize}
-  \item $\formtree{\Gamma}$ has a root $\exists x$ with no outgoing dependency
-edge:
-\end{itemize}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Translation between Unification Nets and Fonets}
-
-\todo{}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+% conference papers do not normally have an appendix
+
+% use section* for acknowledgment
+%\section*{Acknowledgment}
+
+%The authors would like to thank...
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+%\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+%\bibliography{IEEEabrv,../bib/paper}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+
+\bibliographystyle{IEEEtran}
+\bibliography{refs}
+
+%\begin{thebibliography}{1}
+
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+
+%\end{thebibliography}
+
+% that's all folks
+%\end{document}
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\lutz{OLD STUFF, TO BE REMOVED EVENTUALLY}
+
+\subsection{Unification Nets}
+
+\todo{}
+
+In this paragraph, we associate each formula $A$ with its \bfit{formula tree}
+$\formtree{A}$, a directed
+tree with leaves labelled by atoms, internal nodes labelled by connectives and
+quantifiers, and edges directed from leaves to the root. For a sequent
+$\Gamma = A_1, \ldots, A_n$, we denote with $\formtree{\Gamma}$, the forest
+formed by $\formtree{A_1}, \ldots, \formtree{A_n}$, i.e., the disjoint union of
+$\formtree{A_i}$'s. The \bfit{roots} of $\formtree{\Gamma}$ are the roots of
+${A_i}$'s
+
+Let $\Gamma$ be a sequent in $\FOMLL$. Consider the forest
+$\formtree{\Gamma}$. A \bfit{link} on $\Gamma$ is a pair of
+leaves whose atoms are pre-dual. A \bfit{linking} $\lambda$ on $\Gamma$ is a set
+of
+disjoint links such that each leaf of $\formtree{\Gamma}$ is either labelled by $\ttt$ or
+in exactly one link. Similar to the set of links in linked fographs, a linking can be seen as a
+unification problem, and a \bfit{dualizer} $\dualizer$ of the linking $\lambda$ is an assignment
+unifying all the links in $\lambda$. There exists a \bfit{most general dualizer}
+ of $\lambda$ if $\lambda$ has a dualizer. \juihsuan{Now I use the same terminology as for linked fographs}\lutz{use $\delta$ for the dualizer (or even better, make it a macro)}
+A \bfit{dependency} is a pair $(\single \exists x, \single \forall y)$ of nodes
+such that the most general dualizer assigns to $x$ a term containing $y$.
+
+Let $\lambda$ is a linking on $\Gamma$ that has a dualizer.
+The \bfit{unification structure} $\unifstr{\lambda}$
+associated with $\lambda$ is the forest $\formtree{\Gamma}$ together with an undirected
+edge between leaves $l$ and $l'$ for every link $\{l, l'\}$ in $\lambda$ and a
+directed edge from $\single \exists x$ to $\single \forall y$ for every
+dependency $(\single \exists x, \single \forall y)$.
+
+A \bfit{switching graph} of a unification structure $\unifstr{\lambda}$ is any
+derivative of $\unifstr{\lambda}$ obtained by keeping only one edge into each $\cor$
+and $\forall$ and undirecting remaining edges. A linking is \bfit{correct} if it
+is unifiable and all of the switching graphs of its associated unification
+structure are acyclic.
+
+\begin{definition}
+  A \bfit{unification net} on a sequent $\Gamma$ is a correct linking on $\Gamma$.
+\end{definition}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Translation between Unification Nets and $\FOMLL$}
+
+\todo{}
+\begin{thm}\label{thm:MLL1->Unet}
+  If a sequent is provable in $\FOMLL$, then there exists a unification net
+  on it.
+\end{thm}
+
+\begin{proof}
+  We proceed by induction on the proof of $\sqn \Gamma$ in $\FOMLL$, making a
+  case analysis on the bottommost rule instance:
+  \begin{itemize}
+    \setlength\itemsep{.5em}
+    \item $\vlinf{\axr}{}{\sqn{a,\cneg a}}{}$ : the linking $\{a, \dual{a}\}$ is correct.
+    \item $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ : the empty linking is correct.
+    \item $\vliinf{\mixr}{}{\sqn{\Gamma,\Delta}}{\sqn\Gamma}{\sqn\Delta}$ :
+	  By induction hypothesis, there is a correct linking on
+	  $\Gamma$ and another one on $\Delta$, their union giving a
+	  correct linking on $\Gamma, \Delta$.
+    \item $\vlinf{\vlor}{}{\sqn{\Gamma,A\vlor B}}{\sqn{\Gamma,A,B}}$ : By
+	  induction hypothesis, there is a correct linking on $\Gamma, A, B$,
+	  and it is correct on $\Gamma, A \vlor B$ as well.
+    \item $\vliinf{\vlan}{}{\sqn{\Gamma,A\vlan B, \Delta}}{\sqn{\Gamma,A}}{\sqn{B,\Delta}}$ :
+          By induction hypothesis, there is a correct linking on $\Gamma, A$ and
+	  another one on $B, \Delta$, their union giving a correct linking on
+          $\Gamma,A \vlan B, \Delta$.
+    \item $\vlinf{\exists}{}{\sqn{\Gamma,\exists x.A}}
+	  {\sqn{\Gamma,A\ssubst{x}{t}}}$ : By induction hypothesis, there is a
+	  correct linking $\lambda$ on $\Gamma, A\ssubst{x}{t}$.
+	  For each atom in $\Gamma, A \ssubst{x}{t}$, there is a corresponding
+	  atom in $\Gamma, \exists x.A$. There is therefore a linking $\lambda'$
+          on $\Gamma, \exists x.A$ obtained from $\lambda$ via this
+	  correspondence, and it is not difficult to check that $\lambda'$ is
+	  correct as well.
+    \item $\vlinf{\forall}{\text{($x$ not free in
+	  $\Gamma$)}}{\sqn{\Gamma,\forall x.A}}{\sqn{\Gamma,A}}$ : By induction
+          hypothesis, there is a correct linking on $\Gamma, A$, and it is easy
+	  to see that it is a correct linking on $\Gamma, \forall x.A$ as well.
+  \end{itemize}
+  This allows to define a translation $\sqntl\cdot$ from proofs in $\FOMLL$ to unification
+  nets.
+\end{proof}
+
+\begin{thm}\label{thm:sqntl}
+  Any unification net can be obtained via the translation $\sqntl\cdot$ given in Theorem
+  \ref{thm:MLL1->Unet}.
+\end{thm}
+
+To prove this theorem, we need some basic lemmas about connected components in
+switching graphs of unification nets.
+
+\begin{lemma}\label{lem:concomp}
+  The number of connected components of an acylic graph $\gG = \tuple{\vG, \eG}$ is
+equal to $|\eG| - |\vG|$.
+\end{lemma}
+
+\begin{proof}
+  By a straightforward induction on $|\vG|$.
+\end{proof}
+
+\begin{lemma}
+  The number of connected components is the same for any switching graph of a
+unification net.
+\end{lemma}
+
+\begin{proof}
+  An immediate consequence of Lemma \ref{lem:concomp}.
+\end{proof}
+
+In the proof, we also use the notion of \bfit{frame} introduced by Hughes in
+\cite{hughes:unifn}.
+
+\begin{definition}
+Let $\lambda$ be a unification net on an $\FOMLL$ sequent $\Gamma$.
+We define the \bfit{frame} of $\lambda$ by exhaustively applying the following
+subformula rewriting steps, to obtain a linking $\lambda_m$ on an $\MLLm$ sequent $\Gamma_m$:
+
+\begin{enumerate}
+  \item {\bf Encode dependencies as fresh links.} For each dependency $\exists x
+	  \rightarrow \forall y$, with corresponding subformulas $\exists x A$
+		and $\forall y B$, we add a fresh link as follows. Let $P$ be a
+		fresh (nullary) predicate symbol. Replace $\exists x A$ with $P
+		\cand \exists x A$ and $\forall y B$ with $\overline{P} \cor \forall y B$, and add an axiom link between $P$ and $\overline{P}$.
+  \item {\bf Erase quantifiers.} After step 1, erase all the quantifiers. (We no longer need their leaps since they are encoded as links in step 1.
+  \item {\bf Simplify atoms.} After step 2, replace every predicate $Pt_1 \cdots t_n$ with a nullary predicate symbol $P$.
+\end{enumerate}
+\end{definition}
+Note that the linking $\lambda_m$ is a valid $\MLLm$ proof net.
+
+\begin{lemma}\label{lem:concomp_switching}
+Suppose that $\lambda$ is a $\MLLm$ proof net which is connected and such that any of its
+switching graphs is not connected. Then there exists a $\vlor$ node in
+$\unifstr{\lambda}$ such that $\lambda$ is correct on the sequent $\Gamma'$
+obtained from $\Gamma$ by replacing this $\vlor$ by a $\vlan$.
+\end{lemma}
+
+\begin{proof}
+Suppose that such a $\vlor$ node does not exist. Then it is clear that for any
+two nodes, there exists a switching graph containing a path between them and
+this path corresponds to an $AE$-path in \cite{retore:03}. By
+\cite[Propostion~3]{retore:03}, $\lambda$ corresponds to a sequent proof that
+does not use $\mix$, which implies the connectedness of the switching graphs of
+$\lambda$. Contradiction.
+\tocheck{}
+\end{proof}
+
+\begin{lemma}\label{lem:concomp_switching_fo}
+Suppose that $\lambda$ is a $\FOMLL$ proof net which is connected and such that any of its
+switching graphs is not connected. Then there exists a $\vlor$ node in
+$\unifstr{\lambda}$ such that $\lambda$ is correct on the sequent $\Gamma'$
+obtained from $\Gamma$ by replacing this $\vlor$ by a $\vlan$.
+\end{lemma}
+
+\begin{proof}
+  Consider the frame $\lambda_m$ of $\lambda$. The number of any switching
+graph of $\unifstr{\lambda}$ is equal to that of $\unifstr{\lambda_m}$. Apply
+Lemma \ref{lem:concomp_switching} and it is clear that such $\vlor$ cannot be one
+of the fresh $\vlor$'s added during the frame construction.
+\end{proof}
+
+We can now give the proof of Theorem \ref{thm:sqntl}.
+
+\begin{proof}[Proof of Theorem~\ref{thm:sqntl}]
+Let $\lambda$ be a unification net on $\Gamma$. We proceed by induction on the
+number of connected components of the unification structure $\unifstr{\lambda}$:
+\begin{itemize}
+  \item If there is only one connected component, we proceed by induction on the
+number $k$ of connected components of any switching graph of
+$\unifstr{\lambda}$. If $k = 1$, we obtain a proof $\Deri$ in $\FOMLL$ such that
+$\sqntl{\Deri} = \lambda$ by applying \cite[Theorem~3]{hughes:unifn}. If $k > 1$,
+using the Lemma \ref{lem:concomp_switching_fo}, we obtain a sequent $\Gamma'$ on
+which $\lambda$ is correct by transforming a $\vlor$ node into a $\vlan$. By
+induction hypothesis, there is a proof $\Deri'$ in $\FOMLL$ whose translation is
+$\lambda$. By considering the $\vlan$ rule instance corresponding to the $\vlan$
+node in $\Deri'$, we have:
+$
+\Deri' =
+\vlderivation{
+  \vlin{}{}{\sqns{\Gamma'}}{
+  \vlin{}{}{\vlvdots}{
+    \vliin{\vlan}{}{\sqns{\Delta_1, A \vlan B, \Delta_2}}{
+      \vltrl{\Deri_1}{}{}{\sqns{\Delta_1, A}}{
+        \vlhy{\quad}}{
+        \vlhy{}}{
+        \vlhy{}}}{
+      \vltrl{\Deri_2}{}{}{\sqns{B, \Delta_2}}{
+        \vlhy{\quad}}{
+        \vlhy{}}{
+        \vlhy{}}}
+}}}
+$.
+We can thus obtain a proof $\Deri$ of $\Gamma$:
+$
+\Deri =
+\vlderivation{
+  \vlin{}{}{\sqns{\Gamma}}{
+  \vlin{}{}{\vlvdots}{
+    \vlin{\vlor}{}{\sqns{\Delta_1, A \vlor B, \Delta_2}}{
+    \vliin{\mix}{}{\sqns{\Delta_1, A, B, \Delta_2}}{
+      \vltrl{\Deri_1}{}{}{\sqns{\Delta_1, A}}{
+        \vlhy{\quad}}{
+        \vlhy{}}{
+        \vlhy{}}}{
+      \vltrl{\Deri_2}{}{}{\sqns{B, \Delta_2}}{
+        \vlhy{\quad}}{
+        \vlhy{}}{
+        \vlhy{}}}
+}}}}
+$ such that $\sqntl{\Deri} = \lambda$.
+
+  \item If there are $n > 1$ connected components, add a fresh $\vlor$ node
+connecting two formulas belonging to different connected components of $\Gamma$
+to get a new sequent $\Gamma'$. Define a unification net $\lambda'$ on $\Gamma'$
+using the same linking as $\lambda$. By induction hypothesis, since
+$\unifstr{\lambda'}$
+has $n-1$ connected components, there is a $\FOMLL$ proof $\Deri'$ such that
+$\sqntl{\Deri'} = \lambda'$. Consider the $\vlor$ rule instance corresponding
+to the $\vlor$ node in question. Since $\vlor$ is invertible, we can permute
+downwards this rule instance until it becomes the last rule of the proof (note
+that this transformation does not change the image of the proof by the
+translation $\sqntl\cdot$) to get a new proof $\Deri''$ of $\Gamma'$. By deleting the last rule
+instance from $\Deri''$, we obtain a proof $\Deri$ of $\Gamma$ such that
+$\sqntl{\Deri} = \lambda$.
+\tocheck{}
+\end{itemize}
+
+We proceed by induction on the
+number of connectives in $\Gamma$. In the base case, $\Gamma$ is of the form
+\begin{align*}
+p_1(t_{11}, \ldots, t_{1n_1}), \dual{p_1}(t_{11}, \ldots, t_{1n_1}), \ldots, \\
+p_k(t_{k1}, \ldots, t_{kn_k}), \dual{p_k}(t_{k1}, \ldots, t_{kn_k}),
+\underbrace{\ttt, \ldots, \ttt}_\text{$m$ times}
+\end{align*} and
+$\lambda$ is the linking $\set{(a_1, \cneg{a_1}), \ldots, (a_k, \cneg{a_k})}$,
+where $a_i = p_i(t_{i1}, \ldots, t_{in_i})$, which equals to $\sqntl\Pi$, where
+$\Pi$ is the proof consisting of $m$ instances of the $\ttt$ rule, $n$ instances
+$\vlinf{\ax}{}{\sqn a_i, \cneg{a_i}}{}$ of the $\ax$ rule, and followed by
+$m+k-1$ instances of the $\mix$ rule.
+
+Now we consider the inductive cases:
+\begin{itemize}
+  \item $\Gamma = \Delta, A \vlor B$:
+    Let $\Gamma' = \Delta, A, B$. Define $\lambda'$ on $\Gamma'$ using the same
+    links as $\lambda$ by identifying the leaves of $\formtree{\Gamma'}$ with those
+    of $\formtree{\Gamma}$. We now check that $\lambda'$ is a unification net:
+    \begin{itemize}
+      \item The most general dualizer of $\lambda$ is also the most general
+dualizer of $\lambda'$ as they correspond to the same unification problem.
+Hence, the unification structure $\unifstr{\lambda'}$ is equal to the
+restriction of $\unifstr{\lambda}$ to the nodes of $\formtree{\Gamma'}$.
+      \item Every switching graph of $\lambda'$ is acyclic: if there were some
+switching graph of $\unifstr{\lambda'}$ containing a cycle, it would induce a switching
+graph of $\unifstr{\lambda}$ containing also a cycle, by adding an edge from the root of
+$\formtree{A}$ to the $\vlor$ node in question.
+    \end{itemize}
+  \item $\Gamma = \Delta, \forall x.A$:
+    Let $\Gamma' = \Delta, A$. Define $\lambda'$ on $\Gamma'$ using the same
+links as $\lambda$. We now check that $\lambda'$ is a unification net:
+  \begin{itemize}
+    \item The most general dualizer of $\lambda$ is also the most general
+dualizer of $\lambda'$ as they correspond to the same unification problem.
+    \item Every switching graph of $\unifstr{\lambda'}$ is acyclic: if there
+were some switching graph of $\unifstr{\lambda'}$ containing a cycle, it would
+induce a switching graph of $\unifstr{\lambda}$ contaiting also a cycle, by
+adding an edge from the root of $\formtree{A}$ to the $\forall$ node in
+question.
+  \end{itemize}
+  \item $\formtree{\Gamma}$ has a root $\exists x$ with no outgoing dependency
+edge:
+\end{itemize}
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Translation between Unification Nets and Fonets}
+
+\todo{}
+
 \bigskip
@@
 
-\section{Conclusion}
-
-% conference papers do not normally have an appendix
-
-% use section* for acknowledgment
-%\section*{Acknowledgment}
-
-%The authors would like to thank...
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-\bibliographystyle{IEEEtran}
-\bibliography{refs}
-
-%\begin{thebibliography}{1}
-
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-%\end{thebibliography}
-
-% that's all folks
 \end{document}

### 2021-01-23 main.tex
fixing some simple things

@@
   $\vlinf{\rr}{}{\Scons B}{\Scons A}$. By induction hypothesis we have
-  a $\FOMLL$ proof $\Proof$ of $\sqn{\Scons A}$.
-  We now make a case analysis on $\rr$:
-  \begin{itemize}
-    \setlength\itemsep{.5em}
-    \item $\vlinf{\aiD}{}{\Scons{a\vlor\cneg a}}{\Scons\ttt}$ :
-      In this case, we replace simultaneously in $\Pi$ the corresponding
-      occurrences of $\ttt$ with $a \vlor \cneg a$ and the rule instance
-      $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
-      $
-        \vlderivation{
-          \vlin{\vlor}{}{\sqn{a \vlor \cneg a}}{
-            \vlin{\axr}{}{\sqn{a, \cneg a}}{
-              \vlhy{}}}}
-      $, and we get a proof $\Pi'$ of $\sqn{\Scons{a \vlor \cneg a}}$.
+  a $\FOMLL$ proof $\Proof$ of $\sqn{\Scons A}$. If $\rr$ is
+  $\upsmash{\vlinf{\aiD}{}{\Scons{a\vlor\cneg a}}{\Scons\ttt}}$, we replace
+  in $\Pi$ all corresponding occurrences of $\ttt$ with
+  $a \vlor \cneg a$ and the rule instance
+  $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation $ \vlderivation{
+    \vlin{\vlor}{}{\sqn{a \vlor \cneg a}}{ \vlin{\axr}{}{\sqn{a, \cneg
+          a}}{ \vlhy{}}}} $. This gives us a proof of
+  $\sqn{\Scons{a \vlor \cneg a}}$. In all other cases, 
     %\item $\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
@@
      % $, and we get a proof $\Pi'$ of $\sqn{\Scons{\forall x.\ttt}}$.
-    \item In the other cases,
-      by Lemma~\ref{lem:context}, we have a $\FOMLL$ proof of
+      by Lemmas~\ref{lem:shallow} and~\ref{lem:context}, we have a $\FOMLL$ proof of
       $\sqn{\cneg{\Scons A},\Scons B}$. We can compose them via $\cutr$:
@@
       and then apply Theorem~\ref{thm:cutelim}.
-  \end{itemize}
-  \tocheck{}
   \end{proof}

### 2021-01-23 main.tex
in thm 30

@@
 
+For proving this theorem, we have to show that no inference rule in
+$\FOMLS$ can introduce a bimatching. To simplify the argument, we
+introduce the \bfit{frame}~\cite{hughes:unifn} of the fograph $\gC$,
+which is a linked (proposional) cograph in which the dependencies
+between the binders in $\gC$ are encoded as links.
+
+More formally, let $C$ be a formula with $\graphof C=\gC$, to which we
+exhaustively apply the following
+subformula rewriting steps, to obtain a sequent $\frameof C$:
+\begin{enumerate}
+\item {\bf Encode dependencies as fresh links.} For each dependency
+  $\set{\single {x_i},\single {y_j}}$ in $\gC$, with corresponding
+  subformulas $\exists x_i. A$ and $\forall y_j. B$ in $C$, we pick a
+  fresh (nullary) predicate symbol $q_{i,j}$, and then replace $\exists
+  x_i. A$ by $\dual q_{i,j} \cand \exists x_i. A$, and replace $\forall y_j. B$ by
+  $q_{i,j} \cor \forall y_j. B$.
+\item {\bf Erase quantifiers.} After step 1, remove all the
+  quantifiers, i.e., replace $\exists x_i.A$ by $A$ and replace $\forall
+  y_j.B$ by $B$ everywhere.
+\item {\bf Simplify atoms.} After step 2, replace every predicate
+  $p(t_1 \cdots t_n)$ (resp. $\dual p(t_1 \cdots t_n)$) with a nullary
+  predicate symbol $p$ (resp.~$\dual p$)
+\end{enumerate}
+The $\linkingof{\frameof C}$ consists of the pairs induced by
+$\linkingof\gC$ and the new pairs $\set{q_{i,j},\dual q_{i,j}}$ introduced in
+step~1 above. We call $\frameof C$ the \bfit{frame} of $C$ and we define the \bfit{frame} of $\gC$, denoted
+$\frameof\gC$, as
+$\tuple{\graphof{\frameof C},\linkingof{\frameof C}}$.
+
+\begin{lemma}\label{lem:frame}
+  A linked fograph $\gC$ has an induced bimatching iff its frame $\frameof\gC$ has an induced bimatching.
+\end{lemma}
+
 \begin{proof}
-  We have to show that no inference rule in $\FOMLS$ can introduce a
+  This immediately follows from the construction of the frame.\lutz{is it really an ``iff''?
+It is easy to construct from a bimatching in $\gC$ a bimatching in the frame.
+(and I think we only need that direction).
+But what about the other direction?}
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{thm:MLS1->fonet}]
+  From $\Deri$ we construct a derivation $\frameof\Deri$ of $\frameof
+  A$ in the propositional fragment of $\FOMLS$, such that
+  \hbox{$\fographof{\frameof\Deri}=\frameof{\fographof\Deri}$}.  The
+  rules $\aiD,\tttD,\mix$ and $\sw$ are translated trivially, and for
+  $\fequ$, it suffices to observe that the frame construction is
+  invariant under $\fequ$. Finally, for the rules $\forall$ and
+  $\exists$, proceed as follows. Every instance of $\forall$ is
+  replaced by the derivation on the right below:\footnote{For better
+  readability we omit superfluous parentheses, knowing that we always
+  have $\fequ$ incorporating associativity and commutativity of
+  $\vlan$ and $\vlor$.}
+  \begin{equation*}\small
+    \vlinf{\forall}{}{\Scons{\forall y_j.\ttt}}{\Scons{\ttt}}
+    %\qquad
+    \;\leadsto
+    %\qquad
+    \vlderivation{
+      \vlde{\set{\sw,\fequ}}{\DDeri_2}{\Scons{q_{h_1,j}\vlor\cdots\vlor
+          q_{h_j,j}\vlor(\dual q_{h_1,j}\vlan\cdots\vlan\dual
+          q_{h_j,j}\vlan\ttt)}}{
+        \vlde{\set{\aiD,\tttD}}{\DDeri_1}{
+          \Scons{(q_{h_1,j}\vlor \dual q_{h_1,j})\vlan\cdots\vlan(q_{h_j,j}\vlor \dual q_{h_j,j})\vlan\ttt}}{
+          \vlhy{\ttt}}}}
+  \end{equation*}
+  where $h_1,\ldots,h_j$ range over the indices of the existential
+  binders dependend on that $y_j$. It is easy to see how $\DDeri_1$ is
+  constructed, and for $\DDeri_2$ see,
+  e.g. \cite{ESSLI19-notes,gug:str:01,brunnler:tiu:01}\lutz{check if
+    it is really there. otherwise \cite{dissvonlutz}} Then, every
+  occurrence of $\forall y_j.F$ is replaced by
+  $q_{h_1,j}\vlor\cdots\vlor q_{h_j,j}\vlor (\dual
+  q_{h_1,j}\vlan\cdots\vlan\dual q_{h_j,j}\vlan F)$ in the derivation
+  below that $\forall$-instance. Now, observe that all instances of
+  the $\exists$-rule introducing $x_i$ dependend on $y_j$ must occur
+  below in the derivation (otherwise $\Deri$ would not be recified).
+  \lutz{to be cont.}
+
+  We have
+  to show that no inference rule in $\FOMLS$ can introduce a
   bimatching. For the rules $\forall$, $\aiD$, $\tttD$, $\fequ$, and
@@
   cograph connecting two vertices that are each incident to a leap
-  edge.
-The only rules that can do that are $\sw$ and $\exists$.
-For the $\sw$-rule, we refer reader to~\cite{retore:???} or \cite{gug:SIS} or \cite{dissvonlutz} where this property has been shown in detail.
-For the rule $\exists$, a potential bimatching can only be created by a dependency between the \todo{need frame?}
+  edge. The only rules that can do that are $\sw$ and $\exists$. For
+  the $\sw$-rule, we refer reader to~\cite{retore:???} or
+  \cite{gug:SIS} or \cite{dissvonlutz} where this property has been
+  shown in detail. For the rule $\exists$, a potential bimatching can
+  only be created by a dependency between the \todo{need frame?}
 \end{proof}

### 2021-01-23 main.tex
done with thm 30

@@
   predicate symbol $p$ (resp.~$\dual p$)
+%% \item {\bf Remove units.} All occurrences of $\ttt$ are replaced by
+%%   $q_0\vlor\dual q_0$ and all $\fff$ are replaced by $q_0\vlan\dual
+%%   q_0$ for some fresh nullary predicate $q_0$.
 \end{enumerate}
@@
 $\linkingof\gC$ and the new pairs $\set{q_{i,j},\dual q_{i,j}}$ introduced in
-step~1 above. We call $\frameof C$ the \bfit{frame} of $C$ and we define the \bfit{frame} of $\gC$, denoted
+step~1 above.
+We call $\frameof C$ the \bfit{frame} of $C$ and we define the \bfit{frame} of $\gC$, denoted
 $\frameof\gC$, as
@@
   below in the derivation (otherwise $\Deri$ would not be recified).
-  \lutz{to be cont.}
-
-  We have
-  to show that no inference rule in $\FOMLS$ can introduce a
-  bimatching. For the rules $\forall$, $\aiD$, $\tttD$, $\fequ$, and
-  $\mix$, this is immediate, as they do not introduce new edges in the
-  cograph connecting two vertices that are each incident to a leap
-  edge. The only rules that can do that are $\sw$ and $\exists$. For
-  the $\sw$-rule, we refer reader to~\cite{retore:???} or
-  \cite{gug:SIS} or \cite{dissvonlutz} where this property has been
-  shown in detail. For the rule $\exists$, a potential bimatching can
-  only be created by a dependency between the \todo{need frame?}
+  Now consider such an instance $\vlinf{\exists}{}{\Scons{\exists
+      x_i.B}}{\Scons{B\ssubst {x_i} t}}$.  Its context $\Sconhole$
+  must contain all the $\forall y_j$ the $\exists x_i$ depends on,
+  such that $B$ is in their scope. Following the translation of the
+  $\forall$ rules above, we can therefore translate the $\exists$-rule
+  instance by the following derivation
+  \begin{equation*}
+    \vlder{\set{\sw,\fequ}}{\DDeri_3}{ S_0\cons{S_1\cons{\cdots
+          S_{k_i-1}\cons{S_{k_i}\cons{\dual q_{i,k_1}\vlan\dual
+              q_{i,k_2}\vlan\cdots q_{i,k_i}\vlan B'}}\cdots}}}{
+      S_0\cons{\dual q_{i,k_1}\vlan S_1\cons{\dual
+          q_{i,k_2}\vlan\cdots S_{k_i-1}\cons{\dual q_{i,k_i}\vlan
+            S_{k_i}\cons{B'}}\cdots}}}
+  \end{equation*}
+  where $k_1,\ldots,k_i$ are the indices of of the universal binders
+  on which that $x_i$ depends, and $B'$ is $B$ in which all predicates
+  are replaced by nullary one (step~3 in the frame construction). The
+  derivation $\DDeri_3$ can be constructed in the same way as
+  $\DDeri_2$ above.
+
+  Doing this to all instances of the rules $\forall$ and $\exists$ in
+  $\Deri$ yields indeed a propositional derivation $\frameof\Deri$
+  with
+  \hbox{$\fographof{\frameof\Deri}=\frameof{\fographof\Deri}$}. It has
+  been shown by Retor\'e~\cite{some tech-report to be found} and
+  rediscovered by Stra{\ss}burger~\cite{dissvonlutz} that
+  $\fographof{\frameof\Deri}=\tuple{\graphof{\frameof
+      C},\linkingof{\frameof\Deri}}$ can not contain an induced
+  bimatching. By Lemma~\ref{lem:frame}, $\fographof{\Deri}$ does not
+  have an induced bimatching either. Furthemore, it followed from the
+  definition of $\dsubstof\Deri$ that it is a dualizer for
+  $\fographof{\Deri}$. Hence $\fographof{\Deri}$ is a fonet.
+  %% We have
+  %% to show that no inference rule in $\FOMLS$ can introduce a
+  %% bimatching. For the rules $\forall$, $\aiD$, $\tttD$, $\fequ$, and
+  %% $\mix$, this is immediate, as they do not introduce new edges in the
+  %% cograph connecting two vertices that are each incident to a leap
+  %% edge. The only rules that can do that are $\sw$ and $\exists$. For
+  %% the $\sw$-rule, we refer reader to~\cite{retore:???} or
+  %% \cite{gug:SIS} or \cite{dissvonlutz} where this property has been
+  %% shown in detail. For the rule $\exists$, a potential bimatching can
+  %% only be created by a dependency between the \todo{need frame?}
 \end{proof}

### 2021-01-23 main.tex
working in X

@@
 \section{Main Results}
+\label{sec:main}
 
@@
 \begin{thm}\label{thm:CP-DI}
-  Let $A$ be a rectified formula, and assume we have a combinatorial proof $\phi\colon\gC\to\graphof A$. Then there is a derivation
+  Let  $\phi\colon\gC\to\gA$ be a combinatorial proof and let $A$ be a formula with $\gA=\graphof A$. Then there is a derivation
   \begin{equation}
@@
     \vlderivation{
-      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{
+      \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{
         \vlde{\FOMLS}{\Deri_1}{A'}{
@@
   \end{equation}
-  for some $A'$ such that $\graphof{\rectif{A'}}=\gC$. Conversely,
+  for some $A'\fequ C\substof\phi$ where $C$ is a formula with $\graphof
+  C=\gC$ and $\substof\phi$ is the variable renaming substitution induced by~$\phi$.  Conversely,
   whenever we have a derivation as in~\eqref{eq:decom} above, then
-  there is a combinatorial proof $\phi\colon\gC\to\graphof A$ such that $\gC=\graphof{\rectif{A'}}$.
+  there is a combinatorial proof $\phi\colon\gC\to\graphof A$ such
+  that $\gC=\graphof{\rectif{A'}}$.
 \end{thm}
@@
 \section{Translating between $\FOLK$ and $\FOKS$}
+\label{sec:LK1-KS1}
 
@@
 \section{Fonets and Linear Proofs}
+\label{sec:linear}
 
@@
 theorem} to the frame, and then reconstruct the sequent proof $\Pi$.
+\lutz{if the proof of thm \ref{thm:MLS1->fonet} is verified, we can delete the frame-def here}
 
@@
 \section{Skew Bifibrations and Resource Management}
+\label{sec:skew}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:cw->rectif}
   Let $\downsmash{\vlderivation{
-    \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
+    \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
       \vlhy{A}}}}$ be a derivation. Then there is a recified derivation
   $\vlderivation{
-    \vlde{\set{\wrD,\rectif\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{\rectif
+    \vlde{\set{\wrD,\rectif\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{\rectif
       B}{ \vlhy{\rectif A}}}$, such that the induced maps
@@
 
-\begin{lemma}\label{skew->cw}
+\begin{lemma}\label{lem:skew->cw}
   Let $\gA$ and $\gB$ be fographs, let $\phi\colon\gA\to\gB$ be a skew
@@
 
-\begin{proof}[Proof of Lemma~\ref{skew->cw}]
+\begin{proof}[Proof of Lemma~\ref{lem:skew->cw}]
   By Lemma~\ref{lem:PE} we have $\gA=\graphof{\PE A}$ and
@@
 
-\section{Summary and Proofs of Main Results}
+\section{Summary and Proof of Main Result}
+\label{sec:summary}
+
+The only theorem of Section~\ref{sec:main} that has not yet been
+proved is Theorem~\ref{thm:CP-DI} establishing the full correspondence
+between decomposed proofs in $\FOKS$ and combinatorial proofs. We show
+the proof here, by summarizing the results of the previous two
+Sections~\ref{sec:linear} and~\ref{sec:skew}.
+
+\begin{proof}[Proof of Theorem~\ref{thm:CP-DI}]
+  First, asssume we have a combinatorial proof $\phi\colon\gC\to\gA$
+  be a combinatorial proof and a formula $A$ with $\gA=\graphof A$.
+  Let $C$ be a formula with $\graphof C=\gC$, and let $\substof\phi$
+  be the substitution induced by $\phi$.
+  By Lemma~\ref{lem:skew->cw} there is a derivation
+  \begin{equation*}
+    \vlder{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{C\substof\phi}
+  \end{equation*}
+  Since $\gC$ is a fonet, we have by Theorem~\ref{thm:fonet->MLS1} a derivation
+  \begin{equation*}
+    \vlder{\FOMLS}{\Deri'_1}{C}{\ttt}
+  \end{equation*}
+  This derivation remains valid if we apply the substitution
+  $\substof\phi$ to every line in $\Deri'_1$, yielding the derivation
+  $\Deri_1$ of $C\substof\phi$ as desired.
+
+  Conversely, assume we have a decomposed derivation
+  \begin{equation}
+    \label{eq:decom}
+    \vlderivation{
+      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{
+        \vlde{\FOMLS}{\Deri_1}{A'}{
+          \vlhy{\ttt}}}}
+  \end{equation}
+  Then we can transform $\Deri_1$ into a recified form
+  $\rectif\Deri_1$, proving $\rectif A'$. By
+  Theorem~\ref{thm:MLS1->fonet}, the linked fograph
+  $\fographof{\rectif\Deri_1}=\tuple{\fographof{\rectif
+      A'},\linkingof{\rectif\Deri_1}}$ is a fonet.  Then, by
+  Lemma~\ref{lem:cw->rectif}, there is a rectified derivation
+  $\vlderivation{
+    \vlde{\set{\wrD,\rectif\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif{\Deri_2}}{\rectif
+      A}{ \vlhy{\rectif{A'}}}}$ whose induced map
+  $\mapof{\rectif{\Deri_2}}\colon\graphof{\rectif{A'}}\to\graphof{\rectif
+    A}$ is the same a the induced map
+  $\mapof{\Deri_2}\colon\graphof{A'}\to\graphof{A}$ of $\Deri_2$. By
+  Lemma~\ref{lem:cw->skew}, this map is a skew bifibration. Hence, we have a combinatorial proof \lutz{shit, something's wrong...}
+
+  %% Let $\downsmash{\vlderivation{
+  %%   \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
+  %%     \vlhy{A}}}}$ be a derivation. Then there is a recified derivation
+  %% $\vlderivation{
+  %%   \vlde{\set{\wrD,\rectif\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{\rectif
+  %%     B}{ \vlhy{\rectif A}}}$, such that the induced maps
+  %% $\mapof\Deri\colon\graphof{A}\to\graphof{B}$ and
+  %% $\mapof{\rectif\Deri}\colon\graphof{\rectif A}\to\graphof{\rectif
+  %%   B}$ are equal up to a variable renaming of the vertex labels.
+
+  %% for some $A'\fequ C\sigma$ where $C$ is a formula with $\graphof
+  %% C=\gC$ and $\sigma$ is a variable renaming substitution.  Conversely,
+  %% whenever we have a derivation as in~\eqref{eq:decom} above, then
+  %% there is a combinatorial proof $\phi\colon\gC\to\graphof A$ such
+  %% that $\gC=\graphof{\rectif{A'}}$.
+
+\end{proof}
 

### 2021-01-24 main.tex
typo

@@
 \emph{proofs} became first-class citizens as mathematical objects that
-could be studied on its own. Since Gentzen's \emph{sequent
+could be studied on their own. Since Gentzen's \emph{sequent
 calculus}~\cite{gentzen:35:I,gentzen:35:II}, many other proof systems
@@
   $\mapof{\Deri_2}\colon\graphof{A'}\to\graphof{A}$ of $\Deri_2$. By
-  Lemma~\ref{lem:cw->skew}, this map is a skew bifibration. Hence, we have a combinatorial proof \lutz{shit, something's wrong...}
-
+  Lemma~\ref{lem:cw->skew}, this map is a skew bifibration. Hence, we
+  have a combinatorial proof $\phi\colon\gC\to\graphof{A}$ with
+  $\gC=\graphof{\rectif{A'}}$.
+  \lutz{shit, something's wrong...}
   %% Let $\downsmash{\vlderivation{
@@
   %%   B}$ are equal up to a variable renaming of the vertex labels.
-
   %% for some $A'\fequ C\sigma$ where $C$ is a formula with $\graphof
@@
   %% that $\gC=\graphof{\rectif{A'}}$.
-
-\end{proof}
+\end{proof}
+
+Note that Theorem~\ref{thm:CP-DI} shows at the same time soundness, completeness, and full completeness, as
+\begin{enumerate}
+\item every proof in $\FOKS$ can be translated into a combinatorial proof, and
+\item every combinatorial proof is the image of a $\FOKS$-proof under that translation.
+\end{enumerate}
 
@@
 \section{Conclusion}
+
+In this paper we have uncovered a close correspondence between
+first-order combinatorial proofs and decomposed deep inference
+derivations of system $\FOKS$, and we have shown that every proof in
+$\FOKS$ has such a decomposed form.
+
+The most surprising discovery for us was that all technical
+difficulties in our work could be reduced (in a non-trivial way) to
+the propositional setting.
+
+The obvious next step in our research is to investigate proof
+composition and normalisation of first-order combinatorial
+proofs. Even in the propositional setting, the normalization of
+combinatorial proofs is underdevelopped. There exist two different
+procedures for cut elimination~\cite{hughes:invar,str:FSCD17}, but
+both have their insufficiencies, and there is no general theory.
+
+\lutz{do we want/can say more here?}
 

### 2021-01-24 main.tex
backing up figures that have already been finished

@@
 \usepackage{ebproof}
+%\usepackage{mathtools}% mathtools = bug-fixed amsmath; includes variable length \mapsto as \xmapsto
 \usepackage{amsmath}
@@
 
+%%%%%%%%% PACKAGES DOMINIC USES FOR CP FIGURES
 \usepackage{tikz}
+\usetikzlibrary{arrows}% e.g. >=latex' or >=stealth'
+\usetikzlibrary{decorations}\usetikzlibrary{shapes.geometric}% better dot/dash in cp fibres
+\usetikzlibrary{chains}% for inline skew fibrations on formulas
+\usepackage{calculator}% e.g. \MULTIPLY{1.3}{4.2}{\resultmacroname} https://tug.org/TUGboat/tb33-3/tb105fuster.pdf  https://mirror.hmc.edu/ctan/macros/latex/contrib/calculator/calculator.pdf
+
 \usepackage{amsthm}\theoremstyle{plain}
@@
 paper.
+
+\subsection{Pictures}
+
+\input{pics.tex}
+The fograph of drinker formula $\drinkerformula=\veedrinkerformula$:
+%
+\begin{center}\vspace{2ex}\begin{tikzpicture}
+\drinkerbase
+\end{tikzpicture}\vspace{1ex}\end{center}
+%
+A combinatorial proof of drinker formula $\drinkerformula=\veedrinkerformula$:
+%
+\begin{center}\vspace{2ex}\begin{tikzpicture}
+\drinkerfibcoloured
+\end{tikzpicture}\vspace{1ex}\end{center}
+%
+Condensed combinatorial proof of drinker formula(s):
+%
+\begin{center}\vspace{3ex}\begin{math}
+\begin{tikzpicture}
+\drinkerInline
+\end{tikzpicture}
+\hspace{10ex}
+\begin{tikzpicture}
+\veedrinkerInline
+\end{tikzpicture}\end{math}\end{center}
+
+\figcps Fig.\,\ref{fig:cps} is a floating figure with four combinatorial proofs.
+
+\figcpscondensed Fig.\,\ref{fig:cps-condensed} is a floating figure with the condensed forms of the four combinatorial proofs in Fig.\,\ref{fig:cps}.
+
+Both $\veedrinkerformula$ and $\variantveedrinkerformula$ have the same
+rectified fograph $\drinkergraph$, shown below-left.
+%
+\begin{center}\begin{math}
+%
+\drinkergraphpic
+%
+\hspace{8ex}
+%
+\drinkercotreepic
+%
+\hspace{8ex}
+%
+\drinkerbindinggraphpic
+%
+\end{math}\end{center}
+
+Lifting diagrams:
+%
+\liftingdiagrams
+
+\figdrinkerbifib Fig.\,\ref{fig:drinkerbifib} shows the drinker bifibration, binding fibration, and skeleton.
 

### 2021-01-24 main.tex
managed to debug polar coordinate labelling of vertices; now skew bifib figure works
finished all potentially useful diagrams

@@
 \usepackage{cmll}
-
-%%%%%%%%% PACKAGES DOMINIC USES FOR CP FIGURES
-\usepackage{tikz}
-\usetikzlibrary{arrows}% e.g. >=latex' or >=stealth'
-\usetikzlibrary{decorations}\usetikzlibrary{shapes.geometric}% better dot/dash in cp fibres
-\usetikzlibrary{chains}% for inline skew fibrations on formulas
-\usepackage{calculator}% e.g. \MULTIPLY{1.3}{4.2}{\resultmacroname} https://tug.org/TUGboat/tb33-3/tb105fuster.pdf  https://mirror.hmc.edu/ctan/macros/latex/contrib/calculator/calculator.pdf
 
@@
 
+%%%%%%%%% PACKAGES DOMINIC USES FOR CP FIGURES
+\usepackage{tikz}
+\usetikzlibrary{arrows}% e.g. >=latex' or >=stealth'
+\usetikzlibrary{decorations}\usetikzlibrary{shapes.geometric}% better dot/dash in cp fibres
+\usetikzlibrary{chains}% for inline skew fibrations on formulas
+\usetikzlibrary{arrows}% e.g. >=latex' or >=stealth'
+% \usetikzlibrary{arrows.meta}% to easily adjust arrowhead style without adjusting the line style. Problem: no Latex' or Stealth'; package is stale.
+\usetikzlibrary{calc}
+% %	\usetikzlibrary{decorations.markings}
+\usetikzlibrary{matrix}
+\usetikzlibrary{positioning}
+\usepackage{calculator}% e.g. \MULTIPLY{1.3}{4.2}{\resultmacroname} https://tug.org/TUGboat/tb33-3/tb105fuster.pdf  https://mirror.hmc.edu/ctan/macros/latex/contrib/calculator/calculator.pdf
+
+\usepackage{pifont}% for \ding http://willbenton.com/wb-images/pifont.pdf  e.g. for \cross \ding{55} which matches \checkmark or \ding{51}
+\newcommand\cross{\text{\ding{55}}}
+
+%%%%% DOMINIC: THIS IS ONLY USED FOR THE TWIN COLLAPSE EXAMPLE; PACKAGE CAN BE KILLED
+%\usepackage{adjustbox}%% CONFLICT %% easier to align boxes (such as proofs) to top with, e.g. \begin{adjustbox}{valign=t,raise=-.6ex} <STUFF> \end{adjustbox} 
+\usepackage{prftree}% ftp://ftp.dante.de/tex-archive/macros/latex/contrib/prftree/prftreedoc.pdf http://get-software.net/macros/latex/contrib/prftree/prftree.sty
+\prflinethickness=.25pt% package default 0.2pt
+\prfinterspace=1.5em% increase default space between proof rule hypotheses
+\prflinepadbefore=0.2ex% default 0.3ex  above proof lines
+\prflinepadafter=0ex%  default 0.3ex  below proof lines
+\prflineextra=0pt% default 0.3em  proof line overhang each side
+
 \begin{document}
@@
 \figdrinkerbifib Fig.\,\ref{fig:drinkerbifib} shows the drinker bifibration, binding fibration, and skeleton.
+
+\leapfig Fig.\,\ref{fig:leap} shows a fonet with a unique dualizer, and its leap graph.
+
+Illustrating why we need to collapse twins during contraction, to preserve the target as a fograph:
+%
+\twincollapsepic
+%
+Aligning both $\singleton{}\mkern4mu\singleton[red]{}$ and
+$\singleton{}\mkern4mu\singleton[blue]{}$ over
+a single copy of $\forall y\mkern2mu\py$
+results in two uncoloured vertices
+\raisebox{2pt}[0ex][0ex]{$\column{\singleton{}\\[-1.6ex]\singleton{}}$\hspace{-2pt}}
+over $\forall y$.
+%
+The cover therefore fails to be a fograph: both uncoloured vertices are implicitly labelled with $y$ and
+so are outer $y$-binders in the scope of each other.
+%
+The correct operation is shown above-right,
+in which the troublesome pair is collapsed to a single uncoloured vertex $\singleton{}$ over $\forall y$.
 

### 2021-01-24 main.tex
tweaked intro

@@
 
+\input{pics.tex}
+
 \begin{document}
@@
 \begin{abstract}
-  In this paper we uncover a close relation between combinatorial and
+  We uncover a close relationship between combinatorial and
   syntactic proofs for first-order logic. Whereas syntactic proofs are
@@
   decomposition theorem that establishes a new kind of normal form
-  of syntactic proofs. As a consequence, we obtain (i) a simple proof
+  of syntactic proofs. This yields (a) a simple proof
   of the soundness and completeness of first-order combinatorial
-  proofs, and (ii) a full completeness theorem: every combinatorial
+  proofs, and (b) a full completeness theorem: every combinatorial
   proof is the image of a syntactic proof.
@@
 
-First-order predicate logic is one of the cornerstones of modern
+First-order predicate logic is a cornerstone of modern
 logic. Since its formalisation by Frege~\cite{frege:79} it has seen a
-growing usage in many fields of mathematics and computer science. Since
+growing usage in many fields of mathematics and computer science. Upon
 the development of proof theory by Hilbert~\cite{hilbert:22},
@@
 \emph{resolution}~\cite{robinson:65}. Despite the immense progress
-that has been made in proof theory in general and in the area of
+made in proof theory in general and in the area of
 automated and interactive theorem provers in
-particular\cite{DSAV:15lean,paulson:isabelle}\todo{find
-references}\juihsuan{done}, we still have
+particular, we still have
 no satisfactory notion of proof identity for first-order logic. In
@@
 have no such notion telling us when two proofs are \emph{the same},
-even though Hilbert was considering this problem as possible 24th
+even though Hilbert was considering this problem as a possible 24th
 problem for his famous lecture~\cite{hilbert:00} in
@@
 introduced by Hughes~\cite{hughes:pws} for classical propositional
-logic as ``syntax-free'' notion of proof, and as a possible solution
+logic as a ``syntax-free'' notion of proof, and as a potential solution
 to Hilbert's 24th problem~\cite{hughes:invar} (see
@@
 proof as a combinatorial object, more precisely as a special kind of
-homomorphism between two graphs obeying certain properties.
-\lutz{an example here?}
-
-It has been shown by several authors how syntactic proofs in various
+graph homomorphism. For example, a propositional combinatorial
+proof of Peirce's law $\peirceimpliesformula$ is depicted below-left.
+%
+\begin{center}\vspace{.5ex}\begin{tikzpicture}\newcommand\radius{2.3}
+  \begin{scope}[shift={(-\radius,0)}]{\peircecp}\end{scope}
+  \begin{scope}[shift={(\radius,0)}]{\drinkerfibcoloured}\end{scope}
+\end{tikzpicture}\vspace{0ex}\end{center}
+%
+Several authors have illustrated how syntactic proofs in various
 proof systems can be translated to propositional combinatorial proofs:
@@
 in~\cite{str:fscd17}, for Frege systems in~\cite{str:RR-9048}, and for
-tableaux systems and resolution in~\cite{acc:str:18}. This allows to
-define a natural notion of proof identity for propositional logic: two
+tableaux systems and resolution in~\cite{acc:str:18}. This enables a
+natural definition of proof identity for propositional logic: two
 proofs are \emph{the same}, if they are mapped to the same
@@
 logics~\cite{acc:str:relevant} and to modal
-logics~\cite{acc:str:modal}; and Heijlties, Hughes and Stra\ss burger
+logics~\cite{acc:str:modal}, and Heijlties, Hughes and Stra\ss burger
 have provided combinatorial proofs for intuitionistic propositional
@@
 
-In this paper we would like to push forward the idea that
-combinatorial proofs can also for first order logic be used as a
-notion of proof identity. \emph{First-order combinatorial proofs} have
-been introduced by Hughes in~\cite{hughes:fopws}. But even though
-Hughes shows that the conclusion of every first-order combinatorial
-proof is a valid formula, his proof is not really satisfactory, as (i)
-it is long and cumbersome, and (ii) it does not allow to read back a
-syntactic proof based inference rules. In fact, there is the
+In this paper we advance the idea that combinatorial proofs can provide
+a notion of proof identity for first order logic. \emph{First-order
+combinatorial proofs} were introduced by Hughes in~\cite{hughes:fopws}.
+However, even though Hughes proves soundness and completeness, the 
+proof is unsatisfactory: (1) the soundness argument is long and
+cumbersome, and (2) the completeness proof does not allow a syntactic
+proof to be read back from a combinatorial proof. In fact, there is the
 fundamental problem that not all combinatorial proofs can be obtained
@@
 system. More precisely, we introduce a new proof system, called
-$\FOKS$, for first-order logic, that (i) reflects every combinatorial
+$\FOKS$, for first-order logic, that (a) reflects every combinatorial
 proof, i.e., there is a surjective mapping from proofs in $\FOKS$ to
-combinatorial proofs, that (ii) allows to provide simpler proofs of
-soundness and completeness of combinatorial proofs, and (iii) admits
+combinatorial proofs, and (b) yields far simpler proofs of
+soundness and completeness of combinatorial proofs, and (c) admits
 new decomposition theorems establishing a precise correspondence
@@
 
-\input{pics.tex}
 The fograph of drinker formula $\drinkerformula=\veedrinkerformula$:
@@
 %
-A combinatorial proof of drinker formula $\drinkerformula=\veedrinkerformula$:
-%
-\begin{center}\vspace{2ex}\begin{tikzpicture}
-\drinkerfibcoloured
-\end{tikzpicture}\vspace{1ex}\end{center}
 %

### 2021-01-24 main.tex
tweaked intro

@@
 In this paper we advance the idea that combinatorial proofs can provide
-a notion of proof identity for first order logic. \emph{First-order
+a notion of proof identity for first-order logic. \emph{First-order
 combinatorial proofs} were introduced by Hughes in~\cite{hughes:fopws}.
+For example, a first-order combinatorial proof of Smullyan's 
+``drinker paradox'' $\drinkerformula$ is shown above-right.
 However, even though Hughes proves soundness and completeness, the 
-proof is unsatisfactory: (1) the soundness argument is long and
-cumbersome, and (2) the completeness proof does not allow a syntactic
+proof is unsatisfactory: (1) the soundness argument is extremely long,
+intricate and cumbersome, and (2) the completeness proof does not allow
+a syntactic
 proof to be read back from a combinatorial proof. In fact, there is the

### 2021-01-24 main.tex
tweaked intro

@@
 graph homomorphism. For example, a propositional combinatorial
-proof of Peirce's law $\peirceimpliesformula$ is depicted below-left.
+proof of Peirce's law $\peirceimpliesformula$ is depicted below-left,
+a homomorphism from a coloured graph to a graph labelled with
+propositional variables.
 %
@@
 For example, a first-order combinatorial proof of Smullyan's 
-``drinker paradox'' $\drinkerformula$ is shown above-right.
+``drinker paradox'' $\drinkerformula$ is shown above-right,
+a homomorphism from a partially coloured graph to a labelled graph.
 However, even though Hughes proves soundness and completeness, the 
-proof is unsatisfactory: (1) the soundness argument is extremely long,
-intricate and cumbersome, and (2) the completeness proof does not allow
-a syntactic
-proof to be read back from a combinatorial proof. In fact, there is the
-fundamental problem that not all combinatorial proofs can be obtained
-as translations of sequent calculus proofs.
+proof is highly unsatisfactory: (1) the soundness argument is extremely
+long, intricate and cumbersome, and (2) the completeness proof does not 
+allow a syntactic proof to be read back from a combinatorial proof, i.e.,
+completeness is not \emph{full}.
+A fundamental problem is that not all combinatorial
+proofs can be obtained as translations of sequent calculus proofs.
 

### 2021-01-24 main.tex
clear definition doesn't work, breaks Lemma 6

@@
 
-\newcommand{\dominic}[1]{{\color{green}     \noindent[\![\![{\bf Dominic: }#1]\!]\!]}}
+\usepackage[usenames,dvipsnames]{xcolor}% More colours (BrickRed, BlueViolet, ...). Must come before tikz or pstricks. Doc: http://en.wikibooks.org/wiki/LaTeX/Colors
+
+\newcommand{\dominic}[1]{{\color{green!60!black}     \noindent[\![\![{\bf Dominic: }#1]\!]\!]}}
 \newcommand{\lutz}[1]{{\color{blue}     \noindent[\![\![{\bf Lutz: }#1]\!]\!]}}
@@
 allow a syntactic proof to be read back from a combinatorial proof, i.e.,
-completeness is not \emph{full}.
+completeness is not \emph{full}.\todo{cite something for full comp?}
 A fundamental problem is that not all combinatorial
@@
 
-\subsection{Pictures}
+\subsection{Pictures that could be used elsewhere in the paper}
 
@@
 
-We start from a countable set $\VAR=\set{x,y,z,\ldots}$ of variables,
-a countable set $\FUN=\set{f,g,\ldots}$ of function symbols, and a
-countable set $\PRED=\set{p,q,\ldots}$ of predicate symbols. Each function symbol and
+Fix pairwise disjoint countable sets $\VAR=\set{x,y,z,\ldots}$ of variables,
+$\FUN=\set{f,g,\ldots}$ of function symbols, and 
+$\PRED=\set{p,q,\ldots}$ of predicate symbols. Each function symbol and
 each predicate symbol has a finite arity. The grammars below generate
@@
 \end{equation*}
-where the arity of $f$ and $p$ is $n$. Note, that in this paper we
-consider the truth constants $\ttt$ (\emph{true}) and $\fff$
-(\emph{false}) as atoms, and we consider all formulas in negation
-normal form. The \bfit{negation} $(\dual\cdot)$ is defined for all
-atoms and formulas via the De Morgan laws as follows:
+where the arity of $f$ and $p$ is $n$. We consider the truth constants
+$\ttt$ (\emph{true}) and $\fff$
+(\emph{false}) as additional atoms, and we consider all formulas in negation
+normal form, where \bfit{negation} $(\dual\cdot)$ is defined on
+atoms and formulas via De Morgan's laws:
 \begin{equation*}
@@
 multisets of formulas, written as lists, separated by comma. The
-\bfit{corresponding formula} of a sequent $\Gamma=A_1,A_2,\ldots,A_n$
+\bfit{corresponding formula} \todo{Case $n=0$!} of a sequent $\Gamma=A_1,A_2,\ldots,A_n$
 is the disjunction of its formulas: $\form\Gamma=A_1\vlor
@@
 In this paper we use the sequent calculus $\FOLK$, shown in
-Figure~\ref{fig:LK1}, which is an one-sided variant of Gentzen's
+Figure~\ref{fig:LK1}, which is a one-sided variant of Gentzen's
 original calculus~\cite{gentzen:35:I} for first-order logic. To
-simplify some technicalities later in this paper, we also include here
+simplify some technicalities later in this paper, we include
 the $\mixr$-rule.
-
+%
 \begin{thm}
@@
 \end{thm}
-
+%
 For a proof we refer to reader to any standard textbook, e.g.~\cite{TS:00}.
@@
 
-In this paper we make also use of the cut elimination theorem. The \bfit{cut} rule is
+We will employ the cut elimination theorem. The \bfit{cut} rule is
 \begin{equation}
@@
 \end{thm}
-
-As before, this is standard, see e.g.~\cite{TS:00} for a proof.
+%
+\noindent As before, this is standard, see e.g.~\cite{TS:00} for a proof.
 
@@
 if $\gG=\gG_1+\gG_2$ for two non-empty graphs $\gG_1,\gG_2$, otherwise
-it is \bfit{connected}. It is \emph{coconnected} if its complement is
+it is \bfit{connected}. It is \bfit{coconnected} if its complement is
 connected.
@@
 \begin{thm}[\cite{duffin:65}]\label{thm:cograph}
-  A graph is a cograph iff it can be constructed from the singletons via the operations $+$ and~$\times$.
+  A graph is a cograph iff it can be constructed from the singletons
+  via the operations $+$ and~$\times$.
 \end{thm}
-\todo{ad the reference} \juihsuan{done}
 
@@
 Modules in cographs correspond precisely to the subtrees of the
-cotrees (the term-trees constructing the graph via $+$ and~$\times$).
+cotrees (the term-trees constructing the graph via $+$ and~$\times$).\todo{Cotree
+must alternate $+$ and $\times$. Skip this comment completely?}
 
@@
 
-A cograph is \bfit{logical} if every vertex is labelled either by an
+A cograph is \bfit{logical} if every vertex is labelled by either an
 atom or variable, and it has at least one atom-labelled vertex. We
@@
 
-We now define a mapping $\graphof\cdot$ from formulas to (labelled)
+We define a mapping $\graphof\cdot$ from formulas to (labelled)
 graphs, inductively as follows:
@@
 For a formula $A$, we can define its
-associated fograph $\graphof{A}$ inductively by:
+associated fograph $\graphof{A}$ inductively by:\todo{duplicate two sentences above}
 \begin{equation*}
@@
 example, in the graph of $(\exists x. p(x)) \vlor (\exists x. q(x))$,
-both $x$-binders are legal, as they are not in each others
-scope.\todo{draw the picture}.  For this reason, we call a formula
+both $x$-binders are legal, as they are not in each other's
+scope:
+%
+$\edgepairpic{x}{px}\mkern9mu\edgepairpic{x}{qx}$.
+%
+For this reason, we call a formula
 \bfit{clean} if it does not contain subformulas of the form $(\forall
-x.A)\vlor(\forall x.B)$ or $(\exists x.A)\vlan(\exists x.B)$, and no
+x.A)\vlor(\forall x.B)$ or $(\exists x.A)\vlan(\exists x.B)$,
+\todo{need the four cases as in clear definition in fopws? Consider
+$(\forall x.A)\vlor(B\vlor (\forall x.C))$. But then Lemma 6 doesn't hold.
+(fopws proves only that there's a surjection from clear formulas onto fographs,
+whose kernel is the six formula equalities)} and no
 $x$-quantified formula occurs as subformula of another $x$-quantified
@@
 
-Note that even though for every formula $A$ we can obtain an
+Even though for every formula $A$ we can obtain an
 equivalent clean formula by simply renaming some bound variables, this
-is not unique up to $\alpha$-conversion, as it is the case for
+is not unique up to $\alpha$-conversion, as is the case for
 rectified formulas.

### 2021-01-24 main.tex
MLL1 and KS1 proofs
moved some figs

@@
 \newcommand{\gC}{\graph{C}}
+\newcommand{\gD}{\graph{D}}
 \newcommand{\gG}{\graph{G}}
@@
 \newcommand{\bC}{\bgraph{C}}
+\newcommand{\bD}{\bgraph{D}}
 \newcommand{\bG}{\bgraph{G}}
@@
 allow a syntactic proof to be read back from a combinatorial proof, i.e.,
-completeness is not \emph{full}.\todo{cite something for full comp?}
+completeness is not \emph{full}~\cite{abramsky:jagadeesan:94}.\todo{cite something for full comp?}\lutz{is that enough?}
 A fundamental problem is that not all combinatorial
@@
 
-The fograph of drinker formula $\drinkerformula=\veedrinkerformula$:
-%
-\begin{center}\vspace{2ex}\begin{tikzpicture}
-\drinkerbase
-\end{tikzpicture}\vspace{1ex}\end{center}
-%
-%
 Condensed combinatorial proof of drinker formula(s):
@@
 
-Both $\veedrinkerformula$ and $\variantveedrinkerformula$ have the same
-rectified fograph $\drinkergraph$, shown below-left.
-%
-\begin{center}\begin{math}
-%
-\drinkergraphpic
-%
-\hspace{8ex}
-%
-\drinkercotreepic
-%
-\hspace{8ex}
-%
-\drinkerbindinggraphpic
-%
-\end{math}\end{center}
-
-Lifting diagrams:
-%
-\liftingdiagrams
-
-\figdrinkerbifib Fig.\,\ref{fig:drinkerbifib} shows the drinker bifibration, binding fibration, and skeleton.
-
-\leapfig Fig.\,\ref{fig:leap} shows a fonet with a unique dualizer, and its leap graph.
-
 Illustrating why we need to collapse twins during contraction, to preserve the target as a fograph:
@@
 \end{equation*}
-where the arity of $f$ and $p$ is $n$. We consider the truth constants
+where the arity of $f$ and $p$ is $n$.
+For better readability of often omit parentheses and write simply $ft_1,\dots,t_n$ or $pt_1,\dots,t_n$.
+We consider the truth constants
 $\ttt$ (\emph{true}) and $\fff$
@@
 \end{equation*}
+Then we write $A\implies B$ as abbreviation for $\dual A\vlor B$.
 
@@
 multisets of formulas, written as lists, separated by comma. The
-\bfit{corresponding formula} \todo{Case $n=0$!} of a sequent $\Gamma=A_1,A_2,\ldots,A_n$
+\bfit{corresponding formula} of a (non-empty) sequent $\Gamma=A_1,A_2,\ldots,A_n$
 is the disjunction of its formulas: $\form\Gamma=A_1\vlor
@@
 
-Modules in cographs correspond precisely to the subtrees of the
-cotrees (the term-trees constructing the graph via $+$ and~$\times$).\todo{Cotree
-must alternate $+$ and $\times$. Skip this comment completely?}
+%% Modules in cographs correspond precisely to the subtrees of the
+%% cotrees (the term-trees constructing the graph via $+$ and~$\times$).\todo{Cotree
+%% must alternate $+$ and $\times$. Skip this comment completely?}
 
@@
 graphs, inductively as follows:
-
-For a formula $A$, we can define its
-associated fograph $\graphof{A}$ inductively by:\todo{duplicate two sentences above}
+%% For a formula $A$, we can define its
+%% associated fograph $\graphof{A}$ inductively by:\todo{duplicate two sentences above}
 \begin{equation*}
@@
 labelled by $a$ (resp. $x$).
+
+\begin{example}
+  Below is the fograph of drinker formula $\drinkerformula=\veedrinkerformula$:
+%
+\begin{center}\vspace{2ex}\begin{tikzpicture}
+\drinkerbase
+\end{tikzpicture}\vspace{1ex}\end{center}
+%
+%
+\end{example}
 
@@
 %%\juihsuan{I'm still looking for a simple proof}
+
+\begin{remark}
 Note that $\graphof A$ is not necessarily a fograph if $A$ is not
@@
 scope:
-%
 $\edgepairpic{x}{px}\mkern9mu\edgepairpic{x}{qx}$.
-%
-For this reason, we call a formula
-\bfit{clean} if it does not contain subformulas of the form $(\forall
-x.A)\vlor(\forall x.B)$ or $(\exists x.A)\vlan(\exists x.B)$,
-\todo{need the four cases as in clear definition in fopws? Consider
-$(\forall x.A)\vlor(B\vlor (\forall x.C))$. But then Lemma 6 doesn't hold.
-(fopws proves only that there's a surjection from clear formulas onto fographs,
-whose kernel is the six formula equalities)} and no
-$x$-quantified formula occurs as subformula of another $x$-quantified
-formula. Then we have:
-
-\begin{lemma}
-  If $A$ is clean iff\/ $\graphof A$ is a fograph.
-\end{lemma}
-
-\begin{proof}
-  Induction on $A$, using  Theorem~\ref{thm:cograph}.
-\end{proof}
-
-Even though for every formula $A$ we can obtain an
-equivalent clean formula by simply renaming some bound variables, this
-is not unique up to $\alpha$-conversion, as is the case for
-rectified formulas.
+\end{remark}
+
+%
+%% For this reason, we call a formula
+%% \bfit{clean} if it does not contain subformulas of the form $(\forall
+%% x.A)\vlor(\forall x.B)$ or $(\exists x.A)\vlan(\exists x.B)$,
+%% \todo{need the four cases as in clear definition in fopws? Consider
+%% $(\forall x.A)\vlor(B\vlor (\forall x.C))$. But then Lemma 6 doesn't hold.
+%% (fopws proves only that there's a surjection from clear formulas onto fographs,
+%% whose kernel is the six formula equalities)} and no
+%% $x$-quantified formula occurs as subformula of another $x$-quantified
+%% formula. Then we have:
+
+%% \begin{lemma}
+%%   If $A$ is clean iff\/ $\graphof A$ is a fograph.
+%% \end{lemma}
+
+%% \begin{proof}
+%%   Induction on $A$, using  Theorem~\ref{thm:cograph}.
+%% \end{proof}
+
+%% Even though for every formula $A$ we can obtain an
+%% equivalent clean formula by simply renaming some bound variables, this
+%% is not unique up to $\alpha$-conversion, as is the case for
+%% rectified formulas.
 
@@
 \end{proof}
+
+\begin{example}
+  Both $\veedrinkerformula$ and $\variantveedrinkerformula$ (which are
+  equivalent modulo $\fequ$) have the same (rectified) fograph
+  $\drinkergraph$, shown below-left.
+  %
+  \begin{equation*}
+      \drinkergraphpic
+      %
+      \hspace{8ex}
+      %
+      \drinkercotreepic
+      %
+      \hspace{8ex}
+      %
+      \drinkerbindinggraphpic
+  \end{equation*}
+  In the middle above we show the \emph{cotree} of the underlying
+  cograph (illustrating the idea behind Theorem~\ref{thm:cograph}) and
+  on the right above is its binding graph $\bD$.
+\end{example}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\begin{figure}[!t]
+  \begin{center}
+    \vspace{-1ex}
+    \begin{tikzpicture}[graph]
+      \begin{scope}[xshift=-2.2cm]\twolinkfograph\end{scope}
+        \begin{scope}[xshift=2.2cm]\twolinkleapgraph\end{scope}
+    \end{tikzpicture}\vspace{-4ex}
+  \end{center}%
+  \caption{\label{fig:leap}A fonet (left) with
+    dualizer $\protect\twolinkassignment$
+    and its
+    leap graph (right).}
+\end{figure}
+
+Figure~\ref{fig:leap} shows a fonet with a unique dualizer, and its leap graph.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 $w\phi(v) \in \eH$, there exists a unique $\tilde{w} \in \vG$ such
-that $\tilde{w}v \in \eG$ and $\phi(\tilde{w}) = w$, and is a
+that $\tilde{w}v \in \eG$ and $\phi(\tilde{w}) = w$ (indicated on the left below), and is a
 \bfit{skew fibration} if for all $v \in \vG$ and $w\phi(v) \in \eH$
 there exists $\tilde{w} \in \vG$ such that $\tilde{w}v \in \eG$ and
-$\phi(\tilde{w})w \notin \eH$.  A directed graph homomorphism is a
+$\phi(\tilde{w})w \notin \eH$ (indicated in the middle below).  A directed graph homomorphism is a
 \bfit{fibration} if for all $v \in \vG$ and $\pair{w,\phi(v)} \in
 \eH$, there exists a unique $\tilde{w} \in \vG$ such that $\pair{\tilde{w},v}
-\in \eG$ and $\phi(\tilde{w}) = w$.
+\in \eG$ and $\phi(\tilde{w}) = w$ (indicated o the right below).
+%
+\liftingdiagrams
 
@@
 \end{definition}
+
+\begin{example}
+  Below on the left is a skew bifibration, with its binding fibration
+  in the middle. We often omit the labeling in the upper graph, as
+  done on the right below.
+  $$
+  \scalebox{.9}{
+  \begin{tikzpicture}[graph]\drinkerfiblabelledpair{x}{x}
+  \end{tikzpicture}
+  \quad
+  \begin{tikzpicture}[graph]\drinkerbindingfiblabelled{x}{x}
+  \end{tikzpicture}
+  \quad
+  \begin{tikzpicture}[graph]\drinkerfib
+  \end{tikzpicture}}
+  $$
+\end{example}
 

### 2021-01-24 main.tex
Minor fixes
Add an example of decomposed KS1 proof

@@
 %
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\vlor}{}{\sqn{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor p}}{
+    \vlin{\conr}{}{\sqn{(\cneg{p} \vlor q) \vlan \cneg{p}, p}}{
+      \vliin{\vlan}{}{\sqn{(\cneg{p} \vlor q) \vlan \cneg{p}, p, p}}{
+        \vlin{\vlor}{}{\sqn{\cneg{p} \vlor q, p}}{
+          \vlin{\weakr}{}{\sqn{\cneg{p}, q, p}}{
+            \vlin{\axr}{}{\sqn{\cneg{p}, p}}{
+              \vlhy{}}}}}{
+        \vlin{\axr}{}{\sqn{\cneg{p}, p}}{
+          \vlhy{}}}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cD}{}{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor p}{
+    \vlin{\fequ}{}{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor (p \vlor p)}{
+      \vlin{\sw}{}{(\cneg{p} \vlan (\cneg{p} \vlor q)) \vlor p) \vlor p}{
+        \vlin{\fequ}{}{(\cneg{p} \vlan ((\cneg{p} \vlor q) \vlor p)) \vlor p)}{
+          \vlin{\sw}{}{(p \vlor (\cneg{p} \vlor q)) \vlan \cneg{p}) \vlor p}{
+            \vlin{\aiD}{}{(p \vlor (\cneg{p} \vlor q)) \vlan (\cneg{p} \vlor p)}{
+              \vlin{\tttD}{}{(p \vlor (\cneg{p} \vlor q)) \vlan \ttt}{
+                \vlin{\fequ}{}{p \vlor (\cneg{p} \vlor q)}{
+                  \vlin{\wrD}{}{(p \vlor \cneg{p}) \vlor q}{
+                    \vlin{\aiD}{}{p \vlor \cneg{p}}{
+                      \vlhy{\ttt}}}}}}}}}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\conr}{}{\sqn{\exists x.(\cneg{p}x \vlor (\forall y.py))}}{
+    \vlin{\exists}{}{\sqn{\exists x.(\cneg{p}x \vlor (\forall y.py)),\exists
+x.(\cneg{p}x \vlor (\forall y.py))}}{
+      \vlin{\vlor}{}{\sqn{\cneg{p}w \vlor (\forall y.py), \exists
+x.(\cneg{p}x \vlor (\forall y.p(y)))}}{
+        \vlin{\forall}{}{\sqn{\cneg{p}w, \forall y.py, \exists
+x.(\cneg{p}x \vlor (\forall y.py))}}{
+          \vlin{\exists}{}{\sqn{\cneg{p}w, pz, \exists
+x.(\cneg{p}x \vlor (\forall y.py))}}{
+            \vlin{\vlor}{}{\sqn{\cneg{p}w, pz, \cneg{p}z \vlor (\forall y.py))}}{
+              \vlin{\weakr}{}{\sqn{\cneg{p}w, pz, \cneg{p}z, (\forall y.py))}}{
+                \vlin{\weakr}{}{\sqn{\cneg{p}w, pz, \cneg{p}z}}{
+                \vlin{\axr}{}{\sqn{pz, \cneg{p}z}}{
+                  \vlhy{}}}}}}}}}}}
+\end{equation*}
+\juihsuan{LK1 and KS1 proofs of Peirce's law and LK1 proof of drinker formula}
+
 Several authors have illustrated how syntactic proofs in various
@@
 
+\begin{equation*}
+\vlderivation{
+  \vlin{\acD}{}{(\exists x. \cneg{p}x) \vlor (\forall y.(py \vlan pfy))}{
+    \vlin{\mexD}{}{(\exists x. (\cneg{p}x \vlor \cneg{p}x) \vlor (\forall
+y.(py \vlan pfy))}{
+      \vlin{\fequ}{}{((\exists x. \cneg{p}x) \vlor (\exists x.\cneg{p}x))
+\vlor (\forall y.(py \vlan pfy)}{
+        \vlin{\exists}{}{\forall y.(((\exists x. \cneg{p}x) \vlor (\exists
+x.\cneg{p}x)) \vlor (py \vlan pfy))}{
+          \vlin{\exists}{}{\forall y.((\cneg{p}y \vlor (\exists x.\cneg{p}x))
+\vlor (py \vlan pfy))}{
+            \vlin{\fequ}{}{\forall y.((\cneg{p}y \vlor \cneg{p}fy) \vlor
+(py \vlan pfy))}{
+              \vlin{\sw}{}{\forall y.(\cneg{p}y \vlor ((py \vlan pfy)
+\vlor \cneg{p}fy))}{
+                \vlin{\fequ}{}{\forall y.(\cneg{p}y \vlor (py \vlan (pfy
+\vlor \cneg{p}fy)))}{
+                  \vlin{\aiD}{}{\forall y.((\cneg{p}y \vlor py) \vlan (pfy
+\vlor \cneg{p}fy))}{
+                    \vlin{\aiD}{}{\forall y.((\cneg{p}y \vlor py) \vlan
+\ttt)}{
+                      \vlin{\ttt}{}{\forall y.(\ttt \vlan \ttt)}{
+                        \vlin{\forall}{}{\forall y.\ttt}{
+                          \vlhy{\ttt}}}}}}}}}}}}}}
+\end{equation*}
+\juihsuan{the decomposed KS1 proof of $(\exists x. \cneg{p}(x)) \vlor (\forall
+y.(p(y) \vlan p(f(y))))$}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 where the arity of $f$ and $p$ is $n$.
-For better readability of often omit parentheses and write simply $ft_1,\dots,t_n$ or $pt_1,\dots,t_n$.
+For better readability of often omit parentheses and write simply $ft_1 \dots t_n$ or $pt_1 \dots t_n$.
 We consider the truth constants
@@
 combinatorial proofs is underdevelopped. There exist two different
-procedures for cut elimination~\cite{hughes:invar,str:FSCD17}, but
+procedures for cut elimination~\cite{hughes:invar,str:fscd17}, but
 both have their insufficiencies, and there is no general theory.

### 2021-01-24 main.tex
moved example
Add an example and a reference
moved big figs

@@
 \juihsuan{LK1 and KS1 proofs of Peirce's law and LK1 proof of drinker formula}
+\lutz{can you also do the KS1 for the drinker?}
 
@@
 
-\figcps Fig.\,\ref{fig:cps} is a floating figure with four combinatorial proofs.
-
-\figcpscondensed Fig.\,\ref{fig:cps-condensed} is a floating figure with the condensed forms of the four combinatorial proofs in Fig.\,\ref{fig:cps}.
+%%\figcps Fig.\,\ref{fig:cps} is a floating figure with four combinatorial proofs.
+
+%%\figcpscondensed Fig.\,\ref{fig:cps-condensed} is a floating figure with the condensed forms of the four combinatorial proofs in Fig.\,\ref{fig:cps}.
 
@@
 in which the troublesome pair is collapsed to a single uncoloured vertex $\singleton{}$ over $\forall y$.
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\acD}{}{(\exists x. \cneg{p}x) \vlor (\forall y.(py \vlan pfy))}{
-    \vlin{\mexD}{}{(\exists x. (\cneg{p}x \vlor \cneg{p}x) \vlor (\forall
-y.(py \vlan pfy))}{
-      \vlin{\fequ}{}{((\exists x. \cneg{p}x) \vlor (\exists x.\cneg{p}x))
-\vlor (\forall y.(py \vlan pfy)}{
-        \vlin{\exists}{}{\forall y.(((\exists x. \cneg{p}x) \vlor (\exists
-x.\cneg{p}x)) \vlor (py \vlan pfy))}{
-          \vlin{\exists}{}{\forall y.((\cneg{p}y \vlor (\exists x.\cneg{p}x))
-\vlor (py \vlan pfy))}{
-            \vlin{\fequ}{}{\forall y.((\cneg{p}y \vlor \cneg{p}fy) \vlor
-(py \vlan pfy))}{
-              \vlin{\sw}{}{\forall y.(\cneg{p}y \vlor ((py \vlan pfy)
-\vlor \cneg{p}fy))}{
-                \vlin{\fequ}{}{\forall y.(\cneg{p}y \vlor (py \vlan (pfy
-\vlor \cneg{p}fy)))}{
-                  \vlin{\aiD}{}{\forall y.((\cneg{p}y \vlor py) \vlan (pfy
-\vlor \cneg{p}fy))}{
-                    \vlin{\aiD}{}{\forall y.((\cneg{p}y \vlor py) \vlan
-\ttt)}{
-                      \vlin{\ttt}{}{\forall y.(\ttt \vlan \ttt)}{
-                        \vlin{\forall}{}{\forall y.\ttt}{
-                          \vlhy{\ttt}}}}}}}}}}}}}}
-\end{equation*}
-\juihsuan{the decomposed KS1 proof of $(\exists x. \cneg{p}(x)) \vlor (\forall
-y.(p(y) \vlan p(f(y))))$}
 
@@
 
+\begin{figure*}
+  $$
+  \begin{tikzpicture}\cponeonformula
+  \end{tikzpicture}
+  \qquad
+  \begin{tikzpicture}\cptwoonformula
+  \end{tikzpicture}
+  \qquad
+  \begin{tikzpicture}\cpthreeonformula
+  \end{tikzpicture}
+  \qquad
+  \begin{tikzpicture}\cpfouronformula
+  \end{tikzpicture}
+  $$
+  \vskip-2ex
+  \caption{Four combinatorial proofs, each shown
+    above the formula proved.  Here $x$ and $y$ are variables, $f$ is
+    a unary function symbol, $a$ and $b$ are constants (nullary
+    function symbols), $p$ is a unary predicate symbol, and $q$ is a
+    binary predicate symbol.}
+  \label{fig:cps}
+\end{figure*}
+
+\begin{figure*}
+  $$
+  \begin{tikzpicture}
+    \cponeinline
+  \end{tikzpicture}
+  \qquad\;
+  \begin{tikzpicture}
+    \cptwoinline
+  \end{tikzpicture}
+  \qquad\;
+  \begin{tikzpicture}
+    \cpthreeinline
+  \end{tikzpicture}
+  \qquad\;
+  \begin{tikzpicture}
+    \cpfourinline
+  \end{tikzpicture}
+  $$
+  \vskip-2ex
+  \caption{Condensed forms of the four combinatorial proofs in Fig.\,\ref{fig:cps}.}
+  \label{fig:cps-condensed}
+  %\vspace{-4ex}
+\end{figure*}
+
 \subsection{Skew Bifibrations}
@@
 
+To give some examples, we show in Figure~\ref{fig:cps} for examples of
+FOCPs, each above the formula it proves.  The same FOCPs are shown in
+Figure~\ref{fig:cps-condensed} in a more condensed notation.
+
 \begin{thm}[\cite{hughes:fopws}]
@@
 \end{remark}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Herbrand theorem~\cite{brunnler:06:locality,ralph:phd}.
+
+\begin{example}
+  Below is an example of a decomposed derivation in $\FOKS$ of the
+  formula $(\exists x. \cneg{p}(x)) \vlor (\forall y.(p(y) \vlan
+  p(f(y))))$:
+  \begin{equation*}
+    \vlderivation{
+      \vlin{\acD}{}{(\exists x. \cneg{p}x) \vlor (\forall y.(py \vlan pfy))}{
+        \vlin{\mexD}{}{(\exists x. (\cneg{p}x \vlor \cneg{p}x) \vlor (\forall
+          y.(py \vlan pfy))}{
+          \vlin{\fequ}{}{((\exists x. \cneg{p}x) \vlor (\exists x.\cneg{p}x))
+            \vlor (\forall y.(py \vlan pfy)}{
+            \vlin{\exists}{}{\forall y.(((\exists x. \cneg{p}x) \vlor (\exists
+              x.\cneg{p}x)) \vlor (py \vlan pfy))}{
+              \vlin{\exists}{}{\forall y.((\cneg{p}y \vlor (\exists x.\cneg{p}x))
+                \vlor (py \vlan pfy))}{
+                \vlin{\fequ}{}{\forall y.((\cneg{p}y \vlor \cneg{p}fy) \vlor
+                  (py \vlan pfy))}{
+              \vlin{\sw}{}{\forall y.(\cneg{p}y \vlor ((py \vlan pfy)
+                \vlor \cneg{p}fy))}{
+                \vlin{\fequ}{}{\forall y.(\cneg{p}y \vlor (py \vlan (pfy
+                  \vlor \cneg{p}fy)))}{
+                  \vlin{\aiD}{}{\forall y.((\cneg{p}y \vlor py) \vlan (pfy
+                    \vlor \cneg{p}fy))}{
+                    \vlin{\aiD}{}{\forall y.((\cneg{p}y \vlor py) \vlan
+                      \ttt)}{
+                      \vlin{\ttt}{}{\forall y.(\ttt \vlan \ttt)}{
+                        \vlin{\forall}{}{\forall y.\ttt}{
+                          \vlhy{\ttt}}}}}}}}}}}}}}
+  \end{equation*}
+\end{example}
 

### 2021-01-24 main.tex
new version of 45

@@
 % affiliations
-\author{\IEEEauthorblockN{Dominic J. D. Hughes}
-\IEEEauthorblockA{}
-\and
-\IEEEauthorblockN{Lutz Straßburger}
-\IEEEauthorblockA{Inria, Equipe Partout\\
-Ecole Polytechnique, LIX \\ %UMR 7161\\
-France}
-\and
-\IEEEauthorblockN{Jui-Hsuan Wu}
-\IEEEauthorblockA{Ecole Normale Supérieure\\
-France}}
+
+%% \author{\IEEEauthorblockN{Dominic J. D. Hughes}
+%% \IEEEauthorblockA{}
+%% \and
+%% \IEEEauthorblockN{Lutz Straßburger}
+%% \IEEEauthorblockA{Inria, Equipe Partout\\
+%% Ecole Polytechnique, LIX \\ %UMR 7161\\
+%% France}
+%% \and
+%% \IEEEauthorblockN{Jui-Hsuan Wu}
+%% \IEEEauthorblockA{Ecole Normale Supérieure\\
+%% France}}
 
@@
 
-\todo{Examples,examples,examples}
+%\todo{Examples,examples,examples}
 \section{Introduction}
@@
 different syntactic proof systems, based on different sets of inference rules.
+
+\begin{figure}
+  $$
+  \scalebox{.9}{$
+\vlderivation{
+  \vlin{\vlor}{}{\sqn{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor p}}{
+    \vlin{\conr}{}{\sqn{(\cneg{p} \vlor q) \vlan \cneg{p}, p}}{
+      \vliin{\vlan}{}{\sqn{(\cneg{p} \vlor q) \vlan \cneg{p}, p, p}}{
+        \vlin{\vlor}{}{\sqn{\cneg{p} \vlor q, p}}{
+          \vlin{\weakr}{}{\sqn{\cneg{p}, q, p}}{
+            \vlin{\axr}{}{\sqn{\cneg{p}, p}}{
+              \vlhy{}}}}}{
+        \vlin{\axr}{}{\sqn{\cneg{p}, p}}{
+          \vlhy{}}}}}}
+\hskip3em
+\vlderivation{
+  \vlin{\acD}{}{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor p}{
+    \vlin{\fequ}{}{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor (p \vlor p)}{
+      \vlin{\sw}{}{(\cneg{p} \vlan (\cneg{p} \vlor q)) \vlor p) \vlor p}{
+        \vlin{\fequ}{}{(\cneg{p} \vlan ((\cneg{p} \vlor q) \vlor p)) \vlor p)}{
+          \vlin{\sw}{}{(p \vlor (\cneg{p} \vlor q)) \vlan \cneg{p}) \vlor p}{
+            \vlin{\aiD}{}{(p \vlor (\cneg{p} \vlor q)) \vlan (\cneg{p} \vlor p)}{
+              \vlin{\tttD}{}{(p \vlor (\cneg{p} \vlor q)) \vlan \ttt}{
+                \vlin{\fequ}{}{p \vlor (\cneg{p} \vlor q)}{
+                  \vlin{\wrD}{}{(p \vlor \cneg{p}) \vlor q}{
+                    \vlin{\aiD}{}{p \vlor \cneg{p}}{
+                      \vlhy{\ttt}}}}}}}}}}}}
+$}
+  $$
+  \caption{Two syntactic proofs of the same formula, in in the sequent calculus (left) and in the calculus of structures (right)}
+  \label{fig:exa-synt}
+\end{figure}
+
 \lutz{an example here?}
@@
 \begin{equation*}
-\vlderivation{
-  \vlin{\vlor}{}{\sqn{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor p}}{
-    \vlin{\conr}{}{\sqn{(\cneg{p} \vlor q) \vlan \cneg{p}, p}}{
-      \vliin{\vlan}{}{\sqn{(\cneg{p} \vlor q) \vlan \cneg{p}, p, p}}{
-        \vlin{\vlor}{}{\sqn{\cneg{p} \vlor q, p}}{
-          \vlin{\weakr}{}{\sqn{\cneg{p}, q, p}}{
-            \vlin{\axr}{}{\sqn{\cneg{p}, p}}{
-              \vlhy{}}}}}{
-        \vlin{\axr}{}{\sqn{\cneg{p}, p}}{
-          \vlhy{}}}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cD}{}{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor p}{
-    \vlin{\fequ}{}{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor (p \vlor p)}{
-      \vlin{\sw}{}{(\cneg{p} \vlan (\cneg{p} \vlor q)) \vlor p) \vlor p}{
-        \vlin{\fequ}{}{(\cneg{p} \vlan ((\cneg{p} \vlor q) \vlor p)) \vlor p)}{
-          \vlin{\sw}{}{(p \vlor (\cneg{p} \vlor q)) \vlan \cneg{p}) \vlor p}{
-            \vlin{\aiD}{}{(p \vlor (\cneg{p} \vlor q)) \vlan (\cneg{p} \vlor p)}{
-              \vlin{\tttD}{}{(p \vlor (\cneg{p} \vlor q)) \vlan \ttt}{
-                \vlin{\fequ}{}{p \vlor (\cneg{p} \vlor q)}{
-                  \vlin{\wrD}{}{(p \vlor \cneg{p}) \vlor q}{
-                    \vlin{\aiD}{}{p \vlor \cneg{p}}{
-                      \vlhy{\ttt}}}}}}}}}}}}
-\end{equation*}
-
-\begin{equation*}
+  \scalebox{.7}{$
 \vlderivation{
@@
                   \vlhy{}}}}}}}}}}}
-\end{equation*}
+%\qquad
+\vlderivation{
+  \vlin{\acD}{}{\exists x.(\cneg{p}x \vlor (\forall y.py))}{
+    \vlin{\mfaD}{}{\exists x.(\cneg{p}x \vlor (\forall y.(py \vlor py)))}{
+      \vlin{\acD}{}{\exists x.(\cneg{p}x \vlor ((\forall y.py) \vlor (\forall
+y.py)))}{
+        \vlin{\fequ}{}{\exists x.((\cneg{p}x \vlor \cneg{p}x) \vlor ((\forall
+y.py) \vlor (\forall y.py)))}{
+          \vlin{\mexD}{}{\exists x.((\cneg{p}x \vlor (\forall y.py)) \vlor
+(\cneg{p}x \vlor (\forall y.py)))}{
+            \vlin{\exists}{}{(\exists x.(\cneg{p}x \vlor (\forall y.py))) \vlor
+(\exists x.(\cneg{p}x \vlor (\forall y.py)))}{
+              \vlin{\fequ}{}{(\cneg{p}w \vlor (\forall y.py)) \vlor (\exists
+x.(\cneg{p}x \vlor (\forall y.py)))}{
+                \vlin{\exists}{}{\forall y.((\cneg{p}w \vlor py) \vlor (\exists
+x.(\cneg{p}x \vlor (\forall y.py))))}{
+                  \vlin{\fequ}{}{\forall y.((\cneg{p}w \vlor py) \vlor
+(\cneg{p}y \vlor (\forall y.py)))}{
+                    \vlin{\wD}{}{\forall y.((py \vlor \cneg{p}y) \vlor
+(\cneg{p}w \vlor (\forall y.py)))}{
+                      \vlin{\aiD}{}{\forall y.(py \vlor \cneg{p}y)}{
+                        \vlin{\forall}{}{\forall y.\ttt}{
+                          \vlhy{\ttt}}}}}}}}}}}}}}
+$}
+\end{equation*}
+
 \juihsuan{LK1 and KS1 proofs of Peirce's law and LK1 proof of drinker formula}
 \lutz{can you also do the KS1 for the drinker?}
+\juihsuan{done}
 
@@
 To give some examples, we show in Figure~\ref{fig:cps} for examples of
-FOCPs, each above the formula it proves.  The same FOCPs are shown in
+FOCPs (taken from~\cite{hughes:fopws}), each above the formula it proves.  The same FOCPs are shown in
 Figure~\ref{fig:cps-condensed} in a more condensed notation.
@@
   and (ii) the rule $\acD$ can duplicate an atom
-  $x\in\VAR$. Let us write $\acDx$ for such instances. To address (i),
-  we consider here formulas equivalent modulo $\fequ$, always knowing
-  that we can add instances of $\fequ$ as needed.\footnote{Note that whenever we have formulas $P$ and $Q$ with $\PE P\PE\fequ\PE Q$ then $P\fequ Q$.} \juihsuan{this does
-    not seem clear to me. What if from $\PE A_1$ to $\PE B_1$ there
-    are just a bunch of $\PE\fequ$? What do we do in this case?}\lutz{see footnote} To
-  address (ii), we apply a permutation argument, permuting all
+  $x\in\VAR$. Let us write $\acDx$ for such instances.
+  The problem with (i) is that we could have the following situation
+  \begin{equation}
+    \label{eq:m-illegal}
+    \vlderivation{
+      \vlin{\me}{}{\Scons{((x\vlan E)\vlor(x\vlan F))\vlan(C\vlor D)}}{
+        \vlin{\PE\fequ}{}{\Scons{((x\vlan E)\vlan C)\vlor((x\vlan F)\vlan D)}}{
+          \vlhy{\Scons{(x\vlan (E\vlan C))\vlor(x\vlan (F\vlan D))}}}}}
+  \end{equation}
+  where $x$ occurs in $C\vlor D$. Then premise and conclusion are both
+  proposional encodings, but the whole derivation cannot be
+  lifted. However, since we demand that the the mapping is a fibration
+  (and therefore a momomorphism) on the binding graphs, there must be
+  another instance of $\me$ further below in the derivation:
+  \begin{equation}
+    \vlderivation{
+      \vlin{\me}{}{S'\cons{(x\vlor x)\vlan(E\vlor F)}}{
+        \vlhy{S'\cons{(x\vlan E)\vlor(x\vlan F)}}}}
+  \end{equation}
+  We can permute both instances via the following more general scheme
+  (see~\cite{str:medial,lamarche:gap} for a general discussion on
+  permutations of the $\me$-rule):
+  \begin{equation}
+    \label{eq:m-permutation}
+    \scalebox{.66}{$
+    \vlderivation{
+      \vlin{\me}{}{\Scons{(G\vlor H)\vlan(E\vlor F)\vlan(C\vlor D)}}{
+        \vlin{\me}{}{\Scons{((G\vlan E)\vlor(H\vlan F))\vlan(C\vlor D)}}{
+          \vlhy{\Scons{(G\vlan E\vlan C)\vlor(G\vlan F\vlan D)}}}}}
+    \;
+    \leftrightarrow
+    \;
+    \vlderivation{
+      \vlin{\me}{}{\Scons{(G\vlor H)\vlan(E\vlor F)\vlan(C\vlor D)}}{
+        \vlin{\me}{}{\Scons{(G\vlor H)\vlan((E\vlan C)\vlor(F\vlan D))}}{
+          \vlhy{\Scons{(G\vlan E\vlan C)\vlor(G\vlan F\vlan D)}}}}}    
+    $}
+  \end{equation}
+  We omitted some instances of $\PE\fequ$ and some parentheses.  We
+  now call instances of $\me$ as in~\eqref{eq:m-illegal}
+  \bfit{illegal}, and we can transform $\PE\Deri_2$ through
+  $\me$-permutations~\eqref{eq:m-permutation} into a derivation that
+  does not contain any illegal $\me$-instances.
+  To
+  address (ii),
+  we also apply a permutation argument, permuting all
   instances of $\acDx$ up until they either reach the top of the
@@
   \item $\acD$ (contracting an ordinary atom): This can trivially be lifted.
-  \item $\me$ that is not in the situation of~\eqref{eq:mac}: Then now
-    encoding of a quantifier is affected and the instance of $\me$ can
-    be lifted.\todo{medial permutation!!!}
-  \item $\me/\acDx$ as in situation~\eqref{eq:mac}: We must have
+  \item $\me$: There are several cases to consider.
+    \begin{itemize}
+    \item If none of the four principal formulas in the premise is $x$
+      or $x\vlor F$ for some formula $F$ and $x\in\VAR$, then this
+      instance of $\me$ can trivially be lifted, and and we can
+      proceed by induction hypothesis.
+  \item If exactly one of the four principal formulas in the premise
+    is $x$ for some $x\in\VAR$, then this $x$ is the encoding of an existential in the
+    premise and of an universal in the conclusion. This is impossible,
+    as $\phi$ has to preserve existentials.
+  \item If two of the four principal formulas in the premise
+    are $x$ for some $x\in\VAR$, then we are in the following special case of~\eqref{eq:mac}:
+    \begin{equation*}
+      \vlderivation{
+        \vlin{\acDeq}{}{\Scons{x\vlan(C\vlor D)}}{
+          \vlin{\me}{}{\Scons{(x\vlor x)\vlan(C\vlor D)}}{
+            \vlhy{\Scons{(x\vlan C)\vlor (x\vlan D)}}}}}
+    \end{equation*}
+    which can be lifted immediately to
+    \begin{equation*}
+      \vlinf{\mexD}{}{\Scons{\exists x.(C\vlor D)}}{\Scons{(\exists x.C)\vlor(\exists x.D)}}
+    \end{equation*}
+  \item We have a situation~\eqref{eq:mac} where
     $R_1\cons{x}\fequ x\vlor E$ for some $E$ and $R_2\cons{x}\fequ
     x\vlor F$ for some $F$ with $R\cons{x}\fequ x\vlor E\vlor
-    F$. Otherwise, the application of $\acDeq$ would not be correct.
-    We have the following four cases: 
-    \begin{itemize}
-    \item $E$ and $F$ are both non-empty: Then~\eqref{eq:mac} is (modulo
-      omitted applications of $\fequ$):
+    F$ (Otherwise, the application of $\acDeq$ would not be correct.)
+    That means, we have: 
     \begin{equation*}
@@
     \end{equation*}
-    \juihsuan{maybe need some words to exclude the case in which $C$ (or $D$)
-is a propositional variable.}\lutz{shit. (you mean a ``first order variable'') this actually can happen. then we have another $\mexD$}
-    \item $E$ is empty and $F$ is not: Then~\eqref{eq:mac} becomes
-      \begin{equation*}
-        \vlderivation{
-          \vlin{\acDeq}{}{\Scons{(x\vlor F)\vlan(C\vlor D)}}{
-            \vlin{\me}{}{\Scons{(x\vlor (x\vlor F))\vlan(C\vlor D)}}{
-          \vlhy{\Scons{(x\vlan C)\vlor ((x\vlor F)\vlan D)}}}}}
-      \end{equation*}
-      The conclusion is the propositional encoding of $\Scons{(\forall
-        x. F)\vlan(C\vlor D)}$ and the premise is the propositional
-      encoding of $\Scons{(\exists x.C)\vlor ((\forall x. F)\vlor
-        D)}$. Also note that no $\me$-instance can break up the
-      conjunction in $x\vlan C$ in the premise. Hence, $\phi$ maps an
-      existential to a universal, which is ruled out by the
-      definition. Hence, this case cannot occur.
-    \item $E$ is non-empty and $F$ is empty: This case is similar to the
-      previous subcase.
-    \item   $E$ and $F$ are both empty: Then~\eqref{eq:mac} is
-      \begin{equation*}
-        \vlderivation{
-          \vlin{\acDeq}{}{\Scons{x\vlan(C\vlor D)}}{
-            \vlin{\me}{}{\Scons{(x\vlor x)\vlan(C\vlor D)}}{
-              \vlhy{\Scons{(x\vlan C)\vlor (x\vlan D)}}}}}
-      \end{equation*}
-      which can be lifted immediately to
-      \begin{equation*}
-        \vlinf{\mexD}{}{\Scons{\exists x.(C\vlor D)}}{\Scons{(\exists x.C)\vlor(\exists x.D)}}
-      \end{equation*}
+  \item In all other cases (e.g. exactly one of the principal formulas
+    is of shape $x\vlor F$ (and none is $x$), we can trivially lift
+    the $\me$-instance, as the quantifier structure is not affected.
     \end{itemize}
@@
 
+\hrule
+    \begin{itemize}
+    \item If none of
+    the four principal formulas in the premise is $x$ or $x\vlor F$ or
+    $x\vlan F$ for some formula $F$ and $x\in\VAR$, then this instance
+    of $\me$ can trivially be lifted, and and we can proceed by
+    induction hypothesis.
+  \item If exactly one of the four principal formulas in the premise
+    is $x$ for some $x\in\VAR$, then this $x$ is the encoding of an existential in the
+    premise and of an universal in the conclusion. This is impossible,
+    as $\phi$ has to preserve existentials.
+  \item If two of the four principal formulas in the premise
+    are $x$ for some $x\in\VAR$, then we are in the following special case of~\eqref{eq:mac}:
+      \begin{equation*}
+        \vlderivation{
+          \vlin{\acDeq}{}{\Scons{x\vlan(C\vlor D)}}{
+            \vlin{\me}{}{\Scons{(x\vlor x)\vlan(C\vlor D)}}{
+              \vlhy{\Scons{(x\vlan C)\vlor (x\vlan D)}}}}}
+      \end{equation*}
+      which can be lifted immediately to
+      \begin{equation*}
+        \vlinf{\mexD}{}{\Scons{\exists x.(C\vlor D)}}{\Scons{(\exists x.C)\vlor(\exists x.D)}}
+      \end{equation*}
+
+  \item $\me/\acDx$ as in situation~\eqref{eq:mac}: We must have
+    $R_1\cons{x}\fequ x\vlor E$ for some $E$ and $R_2\cons{x}\fequ
+    x\vlor F$ for some $F$ with $R\cons{x}\fequ x\vlor E\vlor
+    F$. Otherwise, the application of $\acDeq$ would not be correct.
+    We have the following four cases: 
+%    \begin{itemize}
+    \item $E$ and $F$ are both non-empty: Then~\eqref{eq:mac} is (modulo
+      omitted applications of $\fequ$):
+      \begin{equation*}
+        \vlderivation{
+          \vlin{\acDeq}{}{\Scons{(x\vlor E\vlor F)\vlan(C\vlor D)}}{
+            \vlin{\me}{}{\Scons{((x\vlor E)\vlor (x\vlor F))\vlan(C\vlor D)}}{
+              \vlhy{\Scons{((x\vlor E)\vlan C)\vlor ((x\vlor F)\vlan D)}}}}}
+      \end{equation*}
+      which can be lifted to
+      \begin{equation*}
+        \vlderivation{
+          \vlin{\mfaD}{}{\Scons{(\forall x.(E\vlor F))\vlan(C\vlor D)}}{
+            \vlin{\me}{}{\Scons{((\forall x. E)\vlor (\forall x. F))\vlan(C\vlor D)}}{
+              \vlhy{\Scons{((\forall x. E)\vlan C)\vlor ((\forall x. F)\vlan D)}}}}}
+      \end{equation*}
+    \juihsuan{maybe need some words to exclude the case in which $C$ (or $D$)
+is a propositional variable.}\lutz{shit. (you mean a ``first order variable'') this actually can happen. then we have another $\mexD$}
+    \item $E$ is empty and $F$ is not: Then~\eqref{eq:mac} becomes
+      \begin{equation*}
+        \vlderivation{
+          \vlin{\acDeq}{}{\Scons{(x\vlor F)\vlan(C\vlor D)}}{
+            \vlin{\me}{}{\Scons{(x\vlor (x\vlor F))\vlan(C\vlor D)}}{
+          \vlhy{\Scons{(x\vlan C)\vlor ((x\vlor F)\vlan D)}}}}}
+      \end{equation*}
+      The conclusion is the propositional encoding of $\Scons{(\forall
+        x. F)\vlan(C\vlor D)}$ and the premise is the propositional
+      encoding of $\Scons{(\exists x.C)\vlor ((\forall x. F)\vlor
+        D)}$. Also note that no $\me$-instance can break up the
+      conjunction in $x\vlan C$ in the premise. Hence, $\phi$ maps an
+      existential to a universal, which is ruled out by the
+      definition. Hence, this case cannot occur.
+    \item $E$ is non-empty and $F$ is empty: This case is similar to the
+      previous subcase.
+    \item   $E$ and $F$ are both empty: Then~\eqref{eq:mac} is
+      \begin{equation*}
+        \vlderivation{
+          \vlin{\acDeq}{}{\Scons{x\vlan(C\vlor D)}}{
+            \vlin{\me}{}{\Scons{(x\vlor x)\vlan(C\vlor D)}}{
+              \vlhy{\Scons{(x\vlan C)\vlor (x\vlan D)}}}}}
+      \end{equation*}
+      which can be lifted immediately to
+      \begin{equation*}
+        \vlinf{\mexD}{}{\Scons{\exists x.(C\vlor D)}}{\Scons{(\exists x.C)\vlor(\exists x.D)}}
+      \end{equation*}
+    \end{itemize}
+
 % An example of a floating figure using the graphicx package.

### 2021-01-25 main.tex
typo
todo
backing up changes to section 1

@@
 \begin{document}
-\vlnosmallleftlabels
-
-\bstctlcite{refs:BSTcontrol}
+\vlnosmallleftlabels%
+\bstctlcite{refs:BSTcontrol}%
 %
@@
 % Do not put math or special symbols in the title.
-\title{Combinatorial Proofs and Decomposition Theorems for First-order Logic}
+\title{Combinatorial Proofs and Decomposition Theorems for First-order Logic\vspace{-3ex}}
 
@@
   syntactic proofs for first-order logic. Whereas syntactic proofs are
-  formalized in some deductive proof system based on inference rules,
-  a combinatorial proof is a ``syntax-free'' presentation of a proof
+  formalized in a deductive proof system based on inference rules,
+  a combinatorial proof is a syntax-fre presentation of a proof
   that is independent from any set of inference rules. We show that
@@
   decomposition theorem that establishes a new kind of normal form
-  of syntactic proofs. This yields (a) a simple proof
-  of the soundness and completeness of first-order combinatorial
+  for syntactic proofs. This yields (a) a simple proof
+  of soundness and completeness for first-order combinatorial
   proofs, and (b) a full completeness theorem: every combinatorial
@@
 different syntactic proof systems, based on different sets of inference rules.
-
-\begin{figure}
-  $$
-  \scalebox{.9}{$
-\vlderivation{
-  \vlin{\vlor}{}{\sqn{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor p}}{
+%
+\newcommand\lkpeirceproof{
+\vlderivation{
+  \vlin{\vlor}{}{\sqn{\peirceformula}}{
     \vlin{\conr}{}{\sqn{(\cneg{p} \vlor q) \vlan \cneg{p}, p}}{
@@
           \vlhy{}}}}}}
-\hskip3em
-\vlderivation{
-  \vlin{\acD}{}{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor p}{
+}
+\newcommand\dipeirceproof{
+\vlderivation{
+  \vlin{\acD}{}{\peirceformula}{
     \vlin{\fequ}{}{((\cneg{p} \vlor q) \vlan \cneg{p}) \vlor (p \vlor p)}{
@@
                       \vlhy{\ttt}}}}}}}}}}}}
-$}
-  $$
-  \caption{Two syntactic proofs of the same formula, in in the sequent calculus (left) and in the calculus of structures (right)}
-  \label{fig:exa-synt}
-\end{figure}
-
-\lutz{an example here?}
-
-This is where \emph{combinatorial proofs} come in. They have been
-introduced by Hughes~\cite{hughes:pws} for classical propositional
-logic as a ``syntax-free'' notion of proof, and as a potential solution
-to Hilbert's 24th problem~\cite{hughes:invar} (see
-also~\cite{str:hilbert:24}). The basic idea is to abstract away from
-the syntax of the inference rules used in the proof and consider the
-proof as a combinatorial object, more precisely as a special kind of
-graph homomorphism. For example, a propositional combinatorial
-proof of Peirce's law $\peirceimpliesformula$ is depicted below-left,
-a homomorphism from a coloured graph to a graph labelled with
-propositional variables.
-%
-\begin{center}\vspace{.5ex}\begin{tikzpicture}\newcommand\radius{2.3}
-  \begin{scope}[shift={(-\radius,0)}]{\peircecp}\end{scope}
-  \begin{scope}[shift={(\radius,0)}]{\drinkerfibcoloured}\end{scope}
-\end{tikzpicture}\vspace{0ex}\end{center}
-%
-
-\begin{equation*}
-  \scalebox{.7}{$
+}
+\newcommand\lkdrinkerproof{
 \vlderivation{
@@
                   \vlhy{}}}}}}}}}}}
-%\qquad
+}
+\newcommand\ksonedrinkerproof{
 \vlderivation{
@@
     \vlin{\mfaD}{}{\exists x.(\cneg{p}x \vlor (\forall y.(py \vlor py)))}{
-      \vlin{\acD}{}{\exists x.(\cneg{p}x \vlor ((\forall y.py) \vlor (\forall
-y.py)))}{
-        \vlin{\fequ}{}{\exists x.((\cneg{p}x \vlor \cneg{p}x) \vlor ((\forall
-y.py) \vlor (\forall y.py)))}{
-          \vlin{\mexD}{}{\exists x.((\cneg{p}x \vlor (\forall y.py)) \vlor
-(\cneg{p}x \vlor (\forall y.py)))}{
-            \vlin{\exists}{}{(\exists x.(\cneg{p}x \vlor (\forall y.py))) \vlor
-(\exists x.(\cneg{p}x \vlor (\forall y.py)))}{
-              \vlin{\fequ}{}{(\cneg{p}w \vlor (\forall y.py)) \vlor (\exists
-x.(\cneg{p}x \vlor (\forall y.py)))}{
-                \vlin{\exists}{}{\forall y.((\cneg{p}w \vlor py) \vlor (\exists
-x.(\cneg{p}x \vlor (\forall y.py))))}{
-                  \vlin{\fequ}{}{\forall y.((\cneg{p}w \vlor py) \vlor
-(\cneg{p}y \vlor (\forall y.py)))}{
-                    \vlin{\wD}{}{\forall y.((py \vlor \cneg{p}y) \vlor
-(\cneg{p}w \vlor (\forall y.py)))}{
+      \vlin{\acD}{}{\exists x.(\cneg{p}x \vlor ((\forall y.py) \vlor (\forall y.py)))}{
+        \vlin{\fequ}{}{\exists x.((\cneg{p}x \vlor \cneg{p}x) \vlor ((\forall y.py) \vlor (\forall y.py)))}{
+          \vlin{\mexD}{}{\exists x.((\cneg{p}x \vlor (\forall y.py)) \vlor (\cneg{p}x \vlor (\forall y.py)))}{
+            \vlin{\exists}{}{(\exists x.(\cneg{p}x \vlor (\forall y.py))) \vlor (\exists x.(\cneg{p}x \vlor (\forall y.py)))}{
+              \vlin{\fequ}{}{(\cneg{p}w \vlor (\forall y.py)) \vlor (\exists x.(\cneg{p}x \vlor (\forall y.py)))}{
+                \vlin{\exists}{}{\forall y.((\cneg{p}w \vlor py) \vlor (\exists x.(\cneg{p}x \vlor (\forall y.py))))}{
+                  \vlin{\fequ}{}{\forall y.((\cneg{p}w \vlor py) \vlor (\cneg{p}y \vlor (\forall y.py)))}{
+                    \vlin{\wD}{}{\forall y.((py \vlor \cneg{p}y) \vlor (\cneg{p}w \vlor (\forall y.py)))}{
                       \vlin{\aiD}{}{\forall y.(py \vlor \cneg{p}y)}{
@@
                           \vlhy{\ttt}}}}}}}}}}}}}}
-$}
-\end{equation*}
-
-\juihsuan{LK1 and KS1 proofs of Peirce's law and LK1 proof of drinker formula}
-\lutz{can you also do the KS1 for the drinker?}
-\juihsuan{done}
+}
+\begin{figure}\vspace{-2ex}\begin{center}\hspace*{-0ex}\begin{math}
+\newcommand\peircescale{.75}
+\newcommand\drinkerscale{\peircescale}
+\newcommand\cpscale{.9}
+\begin{array}{@{}c@{\hspace{4ex}}c@{}}
+{}\scalebox{\peircescale}{$\lkpeirceproof$}
+&
+{}\scalebox{\drinkerscale}{$\lkdrinkerproof$}
+\\[13ex]
+\downarrow
+&
+\downarrow
+\\[1ex]
+\vctr{\scalebox{\cpscale}{\peircecppic}}
+&
+\vctr{\raisebox{-2ex}[16.5ex]{\scalebox{\cpscale}{\drinkerfibcolouredpic}}}
+\\[10ex]
+\uparrow
+&
+\uparrow
+\\[2ex]
+{}\scalebox{\peircescale}{$\dipeirceproof$}
+&
+{}\scalebox{\drinkerscale}{$\ksonedrinkerproof$}
+%
+\end{array}
+\end{math}\hspace*{-8ex}\end{center}\caption{Left:
+syntactic proofs in sequent calculus (above)
+and the calculus of structures (below)
+which translate to the same propositional combinatorial proof (centre).
+%
+Right:
+syntactic proofs 
+in sequent calculus (above)
+and the new calculus $\FOKS$ introduced in this paper (below),
+which translate to the same first-order combinatorial proof (centre).%
+% two syntactic proofs of 
+% $\protect\peirceformula$,
+% in the sequent calculus (above)
+% and in the calculus of structures (below),
+% which translate to the same propositional combinatorial proof (centre).
+% %
+% Right:
+% two syntactic proofs of 
+% $\protect\veedrinkerformula$,
+% in the sequent calculus (above)
+% and the new calculus $\FOKS$ introduced in this paper (below),
+% which translate to the same first-order combinatorial proof (centre).%
+}\label{fig:translate}\vspace{-4ex}\end{figure}%
+
+This is where \emph{combinatorial proofs} come in. They were
+introduced by Hughes~\cite{hughes:pws} for classical propositional
+logic as a syntax-free notion of proof, and as a potential solution
+to Hilbert's 24th problem~\cite{hughes:invar} (see
+also~\cite{str:hilbert:24}). The basic idea is to abstract away from
+the syntax of the inference rules used in inductively-generated proofs
+and consider the proof as a combinatorial object, more precisely
+as a special kind of
+graph homomorphism. For example, a propositional combinatorial
+proof of Peirce's law $\peirceimpliesformula=\peirceformula$ is shown mid-left in
+Fig.\,\ref{fig:translate},
+%depicted below-left,
+a homomorphism from a coloured graph to a graph labelled with
+propositional variables.
+%
+% \begin{center}\vspace{.5ex}\begin{tikzpicture}\newcommand\radius{2.3}
+%   \begin{scope}[shift={(-\radius,0)}]{\peircecp}\end{scope}
+%   \begin{scope}[shift={(\radius,0)}]{\drinkerfibcoloured}\end{scope}
+% \end{tikzpicture}\vspace{0ex}\end{center}
+% %
+% 
+% \begin{equation*}
+%   \scalebox{.7}{$\lkdrinkerproof
+% %\qquad
+% \ksonedrinkerproof
+% $}
+% \end{equation*}
+% 
+% \juihsuan{LK1 and KS1 proofs of Peirce's law and LK1 proof of drinker formula}
+% \lutz{can you also do the KS1 for the drinker?}
+% \juihsuan{done}
 
@@
 combinatorial proof.
+%
+For example, the left side of Fig.\,\ref{fig:translate} translates
+syntactic proofs from sequent calculus and the calculus of structures into
+the same combinatorial proofs, witnessing that the two syntactic proofs,
+from different systems, are \emph{the same}.
 
@@
 For example, a first-order combinatorial proof of Smullyan's 
-``drinker paradox'' $\drinkerformula$ is shown above-right,
+``drinker paradox'' $\drinkerformula=\veedrinkerformula$ is shown on the
+right of Fig.\,\ref{fig:translate},
 a homomorphism from a partially coloured graph to a labelled graph.
@@
 allow a syntactic proof to be read back from a combinatorial proof, i.e.,
-completeness is not \emph{full}~\cite{abramsky:jagadeesan:94}.\todo{cite something for full comp?}\lutz{is that enough?}
+completeness is not
+\emph{sequentializable} \cite{girard:87} or
+\emph{full}~\cite{abramsky:jagadeesan:94}.\dominic{ok to say sequentializable too?}
+%
 A fundamental problem is that not all combinatorial
@@
 
-In this paper we solve this issue by moving to a deep inference
+In this paper we solve these issues by moving to a deep inference
 system. More precisely, we introduce a new proof system, called
 $\FOKS$, for first-order logic, that (a) reflects every combinatorial
-proof, i.e., there is a surjective mapping from proofs in $\FOKS$ to
-combinatorial proofs, and (b) yields far simpler proofs of
+proof, i.e., there is a surjection from $\FOKS$ proofs to
+combinatorial proofs, (b) yields far simpler proofs of
 soundness and completeness of combinatorial proofs, and (c) admits
@@
 notions.
+%
+The right side of Fig.\,\ref{fig:translate}
+illustrates the surjection in (a), and since the syntactic proofs 
+of the two systems both translate the same combinatorial proof,
+they can be considered \emph{the same}.
 
@@
 formalism, like sequent calculus or semantic tableaux, is usually
-simulated by a sequence of different deep inference rules---have
-combinatorial proofs completely abolished the concept of inference
-rule. Nonetheless, there is a close relationship between the two,
-realized through a decomposition theorem, as we establish it in this
+simulated by a sequence of different deep inference rules---
+combinatorial proofs have completely abolished the concept of inference
+rule. And yet, there is a close relationship between the two,
+realized through a decomposition theorem, as we establish in this
 paper.
 
-\subsection{Pictures that could be used elsewhere in the paper}
-
-Condensed combinatorial proof of drinker formula(s):
-%
-\begin{center}\vspace{3ex}\begin{math}
-\begin{tikzpicture}
-\drinkerInline
-\end{tikzpicture}
-\hspace{10ex}
-\begin{tikzpicture}
-\veedrinkerInline
-\end{tikzpicture}\end{math}\end{center}
+% \subsection{Pictures that could be used elsewhere in the paper}
+% 
+% 
+% Condensed combinatorial proof of drinker formula(s):
+% %
+% \begin{center}\vspace{3ex}\begin{math}
+% \begin{tikzpicture}
+% \drinkerInline
+% \end{tikzpicture}
+% \hspace{10ex}
+% \begin{tikzpicture}
+% \veedrinkerInline
+% \end{tikzpicture}\end{math}\end{center}
 
@@
 
-Illustrating why we need to collapse twins during contraction, to preserve the target as a fograph:
-%
-\twincollapsepic
-%
-Aligning both $\singleton{}\mkern4mu\singleton[red]{}$ and
-$\singleton{}\mkern4mu\singleton[blue]{}$ over
-a single copy of $\forall y\mkern2mu\py$
-results in two uncoloured vertices
-\raisebox{2pt}[0ex][0ex]{$\column{\singleton{}\\[-1.6ex]\singleton{}}$\hspace{-2pt}}
-over $\forall y$.
-%
-The cover therefore fails to be a fograph: both uncoloured vertices are implicitly labelled with $y$ and
-so are outer $y$-binders in the scope of each other.
-%
-The correct operation is shown above-right,
-in which the troublesome pair is collapsed to a single uncoloured vertex $\singleton{}$ over $\forall y$.
+% Illustrating why we need to collapse twins during contraction, to preserve the target as a fograph:
+% %
+% \twincollapsepic
+% %
+% Aligning both $\singleton{}\mkern4mu\singleton[red]{}$ and
+% $\singleton{}\mkern4mu\singleton[blue]{}$ over
+% a single copy of $\forall y\mkern2mu\py$
+% results in two uncoloured vertices
+% \raisebox{2pt}[0ex][0ex]{$\column{\singleton{}\\[-1.6ex]\singleton{}}$\hspace{-2pt}}
+% over $\forall y$.
+% %
+% The cover therefore fails to be a fograph: both uncoloured vertices are implicitly labelled with $y$ and
+% so are outer $y$-binders in the scope of each other.
+% %
+% The correct operation is shown above-right,
+% in which the troublesome pair is collapsed to a single uncoloured vertex $\singleton{}$ over $\forall y$.
 
@@
 %
-For a proof we refer to reader to any standard textbook, e.g.~\cite{TS:00}.
+\noindent For a proof, see any standard textbook, e.g.~\cite{TS:00}.
 
@@
 \begin{example}
-  Below is the fograph of drinker formula $\drinkerformula=\veedrinkerformula$:
+  Below is the fograph of the drinker formula $\drinkerformula=\veedrinkerformula$:
 %
@@
 proofs. Even in the propositional setting, the normalization of
-combinatorial proofs is underdevelopped. There exist two different
+combinatorial proofs is underdeveloped. There exist two different
 procedures for cut elimination~\cite{hughes:invar,str:fscd17}, but
@@
 \lutz{do we want/can say more here?}
+
+\todo{mention CERES}
 

### 2021-01-25 main.tex
multiple changes

@@
 \newcommand{\labelof}[1]{\ell(#1)}
-\newcommand{\form}[1]{\mathrm{fm}(#1)}
+%\newcommand{\form}[1]{\mathrm{fm}(#1)}
+\newcommand{\form}[1]{\bigvee\mkern-1mu(\mkern-2mu #1\mkern-2mu)}
 \newcommand{\formtree}[1]{\mathcal{F}(#1)}
@@
 ``drinker paradox'' $\drinkerformula=\veedrinkerformula$ is shown on the
-right of Fig.\,\ref{fig:translate},
+right of Fig.\,\ref{fig:translate},\todo{wrong implies symbol in drinkerformula?}
 a homomorphism from a partially coloured graph to a labelled graph.
@@
 
-In this paper we solve these issues by moving to a deep inference
+We solve these issues by moving to a deep inference
 system. More precisely, we introduce a new proof system, called
@@
 combinatorial proofs, (b) yields far simpler proofs of
-soundness and completeness of combinatorial proofs, and (c) admits
+soundness and completeness for combinatorial proofs, and (c) admits
 new decomposition theorems establishing a precise correspondence
@@
 Stra{\ss}burger~\cite{str:07:RTA} that a proof in classical
-propositional logic can be decomposed into a proof of (multiplicative)
+propositional logic can be decomposed into a proof of multiplicative
 linear logic, followed by a proof consisting only of contractions and
@@
 $x\notin\set{x_1,\ldots,x_n}$. 
-We write $A\sigma$ for the formula
+Write $A\sigma$ for the formula
 obtained from $A$ by applying $\sigma$, i.e., by simultaneously
@@
 A_2\vlor\cdots\vlor A_n$. A sequent is \bfit{rectified} iff its
-corresponding formula is.
+corresponding formula is.\dominic{I changed fm$(\Gamma)$ to $\form\Gamma$,
+easier for referee to understand/intuit/remember later in the paper}
 
@@
 and at least one literal.
-
+%
 \begin{definition}
@@
 \end{definition}
-
-We define a mapping $\graphof\cdot$ from formulas to (labelled)
+%
+\noindent We define a mapping $\graphof\cdot$ from formulas to (labelled)
 graphs, inductively as follows:
@@
 %%\juihsuan{I'm still looking for a simple proof}
-
+%
 \begin{remark}
@@
 the scope of each $x$-binder contains all the vertices, in particular,
-the two $x$-binders. On the other hand, there are non-rectified
+the other $x$-binder. On the other hand, there are non-rectified
 formulas which are translated to fographs by $\graphof\cdot$. For
@@
 \end{remark}
-
 %
@@
 %% formula. Then we have:
-
+%
 %% \begin{lemma}
@@
 %% \end{lemma}
-
+%
 %% \begin{proof}
@@
 %% \end{proof}
-
+%
 %% Even though for every formula $A$ we can obtain an
@@
 %% rectified formulas.
-
-We define a congruence relation $\fequ$ on formulas by the following equations:
+%
+\noindent We define a congruence relation $\fequ$ on formulas by the following equations:
 \begin{equation}
@@
 where $x \notin fv(B)$ in the last two equations.
+\todo{Define $fv$; used later too, e.g.\ proof of Lem.\,\ref{lem:me}}
 Two formulas $A$ and $B$ are \bfit{equivalent} if $A \fequ B$. The following
@@
 \begin{example}
-  Both $\veedrinkerformula$ and $\variantveedrinkerformula$ (which are
-  equivalent modulo $\fequ$) have the same (rectified) fograph
+  Both $\veedrinkerformula$ and $\variantveedrinkerformula$, which are
+  equivalent modulo $\fequ$, have the same (rectified) fograph
   $\drinkergraph$, shown below-left.
@@
   \end{equation*}
-  In the middle above we show the \emph{cotree} of the underlying
+  Above-left we show the \emph{cotree} of the underlying
   cograph (illustrating the idea behind Theorem~\ref{thm:cograph}) and
-  on the right above is its binding graph $\bD$.
+  above-right is its binding graph $\bD$.
 \end{example}
@@
 link or a dependency. The \bfit{leap graph} $\lgC$ of $\gC$ is the undirected
-graph $\tuple{\vC, \lpC}$ where $\lpC$ is the set of leaps of $\gC$. A vertex set $W \subseteq \vC$ induces a \bfit{matching} in
-$\gC$ if for all $w \in W$, $N(w) \cap W$ is a singleton. We say that $W$ induces a
+graph $\tuple{\vC, \lpC}$ where $\lpC$ is the set of leaps of $\gC$.
+A vertex set $W \subseteq \vC$ induces a \bfit{matching} in
+$\gC$ if 
+it is non-empty\dominic{added non-empty (necessary, right?)}
+for all $w \in W$, $N(w) \cap W$ is a singleton. We say that $W$ induces a
 \bfit{bimatching} in $\gC$ if it induces a matching in $\gC$ and a matching in $\lgC$.
@@
 \begin{definition}
-A \bfit{first-order net} or \bfit{fonet} is a linked fograph which has
-dualizer but no induced bimatching.  
+A \bfit{first-order net} or \bfit{fonet} is a linked fograph which
+has a dualizer but no induced bimatching.  
 \end{definition}
-
+%
 \begin{figure}[!t]
@@
     leap graph (right).}
-\end{figure}
-
+\end{figure}%
+%
 Figure~\ref{fig:leap} shows a fonet with a unique dualizer, and its leap graph.
@@
 $w\phi(v) \in \eH$, there exists a unique $\tilde{w} \in \vG$ such
-that $\tilde{w}v \in \eG$ and $\phi(\tilde{w}) = w$ (indicated on the left below), and is a
+that $\tilde{w}v \in \eG$ and $\phi(\tilde{w}) = w$ (indicated below-left),
+and is a
 \bfit{skew fibration} if for all $v \in \vG$ and $w\phi(v) \in \eH$
 there exists $\tilde{w} \in \vG$ such that $\tilde{w}v \in \eG$ and
-$\phi(\tilde{w})w \notin \eH$ (indicated in the middle below).  A directed graph homomorphism is a
+$\phi(\tilde{w})w \notin \eH$ (indicated below-centre).
+A directed graph homomorphism is a
 \bfit{fibration} if for all $v \in \vG$ and $\pair{w,\phi(v)} \in
 \eH$, there exists a unique $\tilde{w} \in \vG$ such that $\pair{\tilde{w},v}
-\in \eG$ and $\phi(\tilde{w}) = w$ (indicated o the right below).
+\in \eG$ and $\phi(\tilde{w}) = w$ (indicated below-right).
 %
 \liftingdiagrams
-
+%
 A \bfit{fograph homomorphism} $\phi=\tuple{\phi,\rsubstof\phi}$ is a
 pair where $\phi\colon\gG\to\gH$ is a graph homomorphism between the
-underlying graphs, and $\rsubstof\phi$, also called the \bfit{substitution induced by $\phi$} is a variable renaming such that
+underlying graphs, and $\rsubstof\phi$, also called the
+\bfit{substitution induced by $\phi$} is a variable renaming 
+such that
 for all $v\in\vG$ we have
-$\labelof{\phi(v)}=\rsubstof\phi(\labelof v)$. Note that this entails that
-$\phi$ maps binders to binders and literals to literals.
-We say that a
-fograph homomorphism $\phi\colon\gG \rightarrow \gH$ is
+$\labelof{\phi(v)}=\rsubstof\phi(\labelof v)$,
+and $\rsubstof\phi$ is the identity on variables not in $\gG$.
+%
+Note that $\phi$ necessarily maps binders to binders
+and literals to literals.
+%
+Since $\rsubstof\phi$ is fully determined by $\phi$ alone, we often
+leave $\rsubstof\phi$ implicit.
+A fograph homomorphism $\phi\colon\gG \rightarrow \gH$
 %%\bfit{label-preserving} if for all $v \in \vG, label(v) = label(f(v))$, and is
-\bfit{existential-preserving} if for all existential binders $b$ in
-$\gG$, the vertex $\phi(b)$ is an existential binder in $\gH$.
-
+% is \bfit{existential-preserving} 
+\bfit{preserves existentials}
+if for all existential binders $b$ in
+$\gG$, the binder $\phi(b)$ is a existential in $\gH$.\dominic{tweaked this paragraph}
+%
 \begin{definition}
@@
 \end{definition}
-
+%
 \begin{example}
-  Below on the left is a skew bifibration, with its binding fibration
-  in the middle. We often omit the labeling in the upper graph, as
-  done on the right below.
-  $$
+  Below-left is a skew bifibration, whose binding fibration
+  is below-centre. When the labels on the source fograph can be inferred
+  (modulo renaming),
+  we often omit the labeling in the upper graph, as below-right, which refer to as 
+  \bfit{condensed form}.\dominic{I said ``can be inferred'' to account for 
+  e.g.\
+  $\graphof{\forall x_1\forall x_2 (px_i\vee px_j\vee px_k\vee px_l)} \to \forall x px$ whose
+  unlabelled skeleton is the skeleton of many distinct formula variants (``who binds who?'').}
+  \begin{center}\begin{math}
   \scalebox{.9}{
@@
   \end{tikzpicture}}
-  $$
-\end{example}
-
+\end{math}\end{center}\end{example}
+%
 %%\subsection{First-order combinatorial proofs}
-
+%
 \begin{definition}
@@
 \end{definition}
-
-To give some examples, we show in Figure~\ref{fig:cps} for examples of
-FOCPs (taken from~\cite{hughes:fopws}), each above the formula it proves.  The same FOCPs are shown in
-Figure~\ref{fig:cps-condensed} in a more condensed notation.
-
+%
+Figure~\ref{fig:cps} shows examples of
+FOCPs (taken from~\cite{hughes:fopws}), each above the formula it proves.
+The same FOCPs are shown in
+Figure~\ref{fig:cps-condensed} in condensed form.
+%
 \begin{thm}[\cite{hughes:fopws}]
@@
 \end{thm}
-
+%
 \begin{remark}
-  In or definition of FOCP, we are slightly laxer than the original
+  Our definition of FOCP is slightly more lax than the original
   definition of~\cite{hughes:fopws}, as we allow for a variable
@@
 \end{figure}
-
-Contrary to standard proof formalisms, like sequent calculi or
+%
+In contrast to to standard proof formalisms, like sequent calculi or
 tableaux, where inference rules decompose the principal formula along
-its root connective, can \emph{deep inference rules} be applied like
+its root connective, \emph{deep inference rules} apply like
 rewriting rules inside any (positive) formula or sequent
@@
 Figure~\ref{fig:KS1} shows the inference rules for the deep inference
-system~$\FOKS$ that we are using in this paper. It is a slight variation
+system~$\FOKS$ that we introduce in this paper. It is a slight variation
 of the systems presented by Br\"unnler~\cite{brunnler:phd} and
-Ralph~\cite{ralph:phd} in their PhD-theses. The main differences being
-that we have (i) the explicit presence of the $\mixr$-rule, (ii) a
+Ralph~\cite{ralph:phd} in their PhD-theses. The main differences are
+(i) the explicit presence of the $\mixr$-rule, (ii) a
 different choice of how the formula equivalence $\fequ$ is defined,
@@
 As with the sequent system $\FOLK$, we also need for $\FOKS$ the
-\emph{linear fragment}, that we call here $\FOMLS$, and that is shown
+\emph{linear fragment}, $\FOMLS$, and that is shown
 in Figure~\ref{fig:KS1} in the dashed box.
 
-We write $\vlder{\sysS}{\Deri}{A}{B}$ to denote a derivation $\Deri$
+Write $\vlder{\sysS}{\Deri}{A}{B}$ to denote a derivation $\Deri$
 from $B$ to $A$ using the rules from system $\sysS$. A formula $A$ is
@@
 
-In the course of this paper we are also going to make use of the
+In the course of this paper we will employ the
 general (non-atomic) version of the contraction rule:
@@
 
-We are now ready to see the main results of this paper. We only state
-them here and give the proofs in the later sections of the paper. The
-first one is routine and expected, but needs to be proved nonetheless:
+We state the main results of this paper here,
+and prove them in later sections. The
+first is routine and expected, but needs to be proved nonetheless:
 
@@
 \end{example}
-
+%
 There is a weaker version of Theorem~\ref{thm:decomposition} that will
 also be useful:
-
+%
 \begin{thm}\label{thm:decompositionA}
@@
   for some $A'\fequ C\substof\phi$ where $C$ is a formula with $\graphof
-  C=\gC$ and $\substof\phi$ is the variable renaming substitution induced by~$\phi$.  Conversely,
+  C=\gC$ and $\substof\phi$ is the variable renaming substitution
+  induced by~$\phi$.  Conversely,
   whenever we have a derivation as in~\eqref{eq:decom} above, then
@@
   the following derivation:
-  \begin{equation*}
+  \begin{center}\vspace{-2ex}\begin{math}
     \vlderivation{
@@
             \vlhy{\ttt}}}}}
-  \end{equation*}
+  \end{math}\end{center}
   where we can apply the $\fequ$-rule because $x$ is not free in $\Delta$.

### 2021-01-25 main.tex
tweak

@@
   e.g.\
-  $\graphof{\forall x_1\forall x_2 (px_i\vee px_j\vee px_k\vee px_l)} \to \forall x px$ whose
+  $\graphof{\forall x_1\forall x_2 (px_i\vee px_j\vee px_k\vee px_l)}
+  \to \graphof{\forall x\mkern2mu px}$ whose
   unlabelled skeleton is the skeleton of many distinct formula variants (``who binds who?'').}

### 2021-01-25 main.tex
rule permutation
appendix
new rules

@@
 \newcommand\acDeq {\mathsf{ac}_x^\fequ}
+\newcommand\wfaD {\mathsf{w_\forall}}
 \newcommand\cfaD {\mathsf{c_\forall}}
@@
 different syntactic proof systems, based on different sets of inference rules.
+Just consider the derivations in Figure~\ref{fig:translate}, showing two proofs of the formula $\peirceformula$ and two proofs of the formula $\veedrinkerformula$, one in the sequent calculus (top) and one in a deep inference system (bottom).
+It is, \emph{a priori}, not clear how to compare them.
 %
@@
 ``drinker paradox'' $\drinkerformula=\veedrinkerformula$ is shown on the
-right of Fig.\,\ref{fig:translate},\todo{wrong implies symbol in drinkerformula?}
+right of Fig.\,\ref{fig:translate}, %\todo{wrong implies symbol in drinkerformula?}
 a homomorphism from a partially coloured graph to a labelled graph.
@@
 completeness is not
-\emph{sequentializable} \cite{girard:87} or
-\emph{full}~\cite{abramsky:jagadeesan:94}.\dominic{ok to say sequentializable too?}
+\emph{sequentializable} \cite{girard:87} nor
+\emph{full}~\cite{abramsky:jagadeesan:94}. %\dominic{ok to say sequentializable too?}
 %
@@
 formalism, like sequent calculus or semantic tableaux, is usually
-simulated by a sequence of different deep inference rules---
-combinatorial proofs have completely abolished the concept of inference
-rule. And yet, there is a close relationship between the two,
-realized through a decomposition theorem, as we establish in this
+simulated by a sequence of different deep inference
+rules---combinatorial proofs have completely abolished the concept of
+inference rule. And yet, there is a close relationship between the
+two, realized through a decomposition theorem, as we establish in this
 paper.
@@
     \\[.5ex]
-    a &\coloneqq~ \ttt\mid\fff\mid p(t_1,\dots,t_n) \mid \dual p(t_1,\dots,t_n)
+    a &\coloneqq~ p(t_1,\dots,t_n) \mid \dual p(t_1,\dots,t_n)
     \\[.5ex]
-    A &\coloneqq~ a \mid A\vlan A \mid A\vlor A \mid \exists x.A \mid \forall x.A
+    A &\coloneqq~ a \mid \ttt\mid\fff\mid A\vlan A \mid A\vlor A \mid \exists x.A \mid \forall x.A
 \end{array}
@@
             \qquad
-            \vlinf{\ttt}{}{\sqn{\ttt}}{}
-            \qquad
-            \vliinf{\mixr}{}{\sqn{\Gamma,\Delta}}{\sqn\Gamma}{\sqn\Delta}
-            \\ \\[-1ex]
             \vlinf{\vlor}{}{\sqn{\Gamma,A\vlor B}}{\sqn{\Gamma,A,B}}
@@
             \vliinf{\vlan}{}{\sqn{\Gamma,A\vlan B, \Delta}}{\sqn{\Gamma,A}}{\sqn{B,\Delta}}
+            \\ \\[-1ex]
+            \vlinf{\ttt}{}{\sqn{\ttt}}{}
+            \qquad\;
+            \vlinf{\fff}{}{\sqn{\Gamma,\fff}}{\sqn{\Gamma}}
+            \qquad\;
+            \vliinf{\mixr}{}{\sqn{\Gamma,\Delta}}{\sqn\Gamma}{\sqn\Delta}
             \\ \\[-1ex]
@@
 A_2\vlor\cdots\vlor A_n$. A sequent is \bfit{rectified} iff its
-corresponding formula is.\dominic{I changed fm$(\Gamma)$ to $\form\Gamma$,
-easier for referee to understand/intuit/remember later in the paper}
+corresponding formula is.
+%\dominic{I changed fm$(\Gamma)$ to $\form\Gamma$,
+%easier for referee to understand/intuit/remember later in the paper}
 
@@
 
-The linear fragment of $\FOLK$, i.e., the fragment
-without the rules $\conr$ (\emph{contraction}) and $\weakr$
-(\emph{weakening}) defines \emph{first-order multiplicative linear
+The linear fragment of $\FOLK$, i.e., the fragment without the rules
+$\conr$ (\emph{contraction}) and $\weakr$ (\emph{weakening}) defines
+\emph{first-order multiplicative linear
 logic}~\cite{girard:87,girard:88} \emph{with
-mix}~\cite{fleury:retore:94,bellin:97}~(MLL1+mix). We denote that system
-here with $\FOMLL$ (shown in Figure~\ref{fig:LK1} in the dashed box).
-
-We will employ the cut elimination theorem. The \bfit{cut} rule is
+mix}~\cite{fleury:retore:94,bellin:97}~(MLL1+mix). We denote that
+system here with $\FOMLL$ (shown in Figure~\ref{fig:LK1} in the dashed
+box).
+
+We will use the cut elimination theorem. The \bfit{cut} rule is
 \begin{equation}
@@
 A cograph is \bfit{logical} if every vertex is labelled by either an
-atom or variable, and it has at least one atom-labelled vertex. We
-write $\single\alpha$ for an $\alpha$-labelled vertex. An
+atom or variable, and it has at least one atom-labelled vertex. An
 atom-labelled vertex is called a \bfit{literal} and a
@@
   \begin{array}{r@{\;}l@{\hskip4em}r@{\;}l}
-    \graphof{a} &= \single a \rlap{\hskip1em(for any atom $a$)}  \\[.9ex]
+    \multicolumn{4}{c}{
+      \quad\graphof{\ttt}=\single\ttt
+      \qquad
+      \graphof{\fff}=\single\fff
+      \qquad
+    \graphof{a} = \single a \hbox{\hskip1em(for any atom $a$)} } \\[1.1ex]
     \graphof{A \cor B} &= \graphof{A} + \graphof{B} &
@@
 \end{equation*}
-where $\single a$ (resp. $\single x$) is a single-vertex graph whose vertex is 
-labelled by $a$ (resp. $x$).
+where we
+write $\single\alpha$ for a single-vertex  labelled by $\alpha$.
 
 \begin{example}
-  Below is the fograph of the drinker formula $\drinkerformula=\veedrinkerformula$:
-%
-\begin{center}\vspace{2ex}\begin{tikzpicture}
+  Here is the fograph of the drinker formula $\drinkerformula=\veedrinkerformula$:
+  \;\;
+  \hbox{\begin{tikzpicture}[baseline={([yshift={-1.5ex}]current bounding box.north)}]
       \drinkerbase
-\end{tikzpicture}\vspace{1ex}\end{center}
-%
-%
+  \end{tikzpicture}}
 \end{example}
@@
 \end{equation}
-where $x \notin fv(B)$ in the last two equations.
-\todo{Define $fv$; used later too, e.g.\ proof of Lem.\,\ref{lem:me}}
+where $x$ must not be free in $B$ in the last two equations.
 Two formulas $A$ and $B$ are \bfit{equivalent} if $A \fequ B$. The following
@@
   \end{equation*}
-  Above-left we show the \emph{cotree} of the underlying
+  Above-middle we show the \emph{cotree} of the underlying
   cograph (illustrating the idea behind Theorem~\ref{thm:cograph}) and
@@
         \\ \\[-1ex]
+        \vlinf{\wrD}{}{\Scons{A\vlor B}}{\Scons{A}}
+        \quad\;
+        \vlinf{\me}{}{\Scons{(A\vlor B)\vlan(C\vlor D)}}{\Scons{(A\vlan C)\vlor(B\vlan D)}}
+        \quad\;
+        \vlinf{\acD}{}{\Scons{a}}{\Scons{a\vlor a}}
+        \\ \\[-1ex]
         \vlinf{\mfaD}{}{\Scons{\forall x.(A\vlor B)}}{\Scons{(\forall x.A)\vlor(\forall x.B)}}
@@
         \\ \\[-1ex]
-        \vlinf{\me}{}{\Scons{(A\vlor B)\vlan(C\vlor D)}}{\Scons{(A\vlan C)\vlor(B\vlan D)}}
-        \\ \\[-1ex]
-        \vlinf{\wrD}{}{\Scons{A\vlor B}}{\Scons{A}}
-        %%\qquad
-        %%\vlinf{\wlD}{}{\Scons{B\vlor A}}{\Scons{A}}
-        \qquad
-        \vlinf{\acD}{}{\Scons{a}}{\Scons{a\vlor a}}
+        \vlinf{\wfaD}{\text{($x$ not free in $A$)}}{\Scons{\forall x.A}}{\Scons{A}}
         \qquad
@@
     \vlderivation{
-      \vlde{\set{\wrD,\fequ}}{}{A}{
+      \vlde{\set{\wrD,\wfaD,\fequ}}{}{A}{
         \vlde{\set{\acD,\cfaD}}{}{A_1}{
@@
 Herbrand theorem~\cite{brunnler:06:locality,ralph:phd}.
+
+Theorem~\ref{thm:decomposition} is also the reason why we have te rule
+$\wfaD$ and $\cfaD$ in system $\FOKS$, as these rules are derivable
+with the other rules. However, they are needed to obtain this
+decomposition.
 
@@
     \vlderivation{
-      \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{
+      \vlde{\set{\wrD,\wfaD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{
         \vlde{\FOMLS}{\Deri_1}{A'}{
@@
   \label{lem:me}
-  $\cfaD,\me,\mfaD,\mexD$ are derivable in \hbox{$\set{\wrD,\cD,\fequ}$}. 
+  $\wfaD,\cfaD,\me,\mfaD,\mexD$ are derivable in \hbox{$\set{\wrD,\cD,\fequ}$}. 
 \end{lemma}
@@
     \vlderivation{
-      \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{}{B}{
+      \vlde{\set{\wrD,\wfaD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{}{B}{
         \vlhy{A}}}
@@
   \todo{permutation with $\fequ$}
+
+($\cfaD/\fequ$)
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall y.\forall x.A}{
+    \vlin{\cfaD}{}{\forall x.\forall y.A}{
+      \vlhy{\forall x.\forall x.\forall y.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cfaD}{}{\forall y.\forall x.A}{
+    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
+      \vlhy{\forall x.\forall x.\forall y.A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
+    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x. A) \vlor B}{
+      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{(x \notin fv(B))}{\forall x.(A \vlor B)}{
+    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
+      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
+\end{equation*}
+
+($\wrD/\fequ$)
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{B \vlor A}{
+    \vlin{\wrD}{}{A \vlor B}{
+      \vlhy{A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{A \vlor (B \vlor C)}{
+    \vlin{\wrD}{}{(A \vlor B) \vlor C)}{
+      \vlhy{A \vlor C}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
+    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+      \vlhy{\forall x.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{(\forall x. A) \vlor B}{
+    \vlhy{\forall x.A}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{(x \notin fv(B))}{\forall x.(A \vlor B)}{
+    \vlin{\wrD}{}{(\forall x.A) \vlor B}{
+      \vlhy{\forall x.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+    \vlhy{\forall x.A}}}
+\end{equation*}
+
+($\fequ/\cfaD$)
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{\forall x.\forall y.A}{
+    \vlin{\fequ}{}{\forall x.\forall x.\forall y. A}{
+      \vlhy{\forall x.\forall y.\forall x.A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{\forall y.\forall x.A}{
+    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
+      \vlhy{\forall x.\forall y.\forall x.A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x.A) \vlor B}{
+      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
+      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
+\end{equation*}
+
+($\fequ/\me$)
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
+      \vlhy{(C \vlan A) \vlor (B \vlan D)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
+      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
+\leadsto
+\vlderivation{
+  \vlin{\fequ}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\me}{}{(B \vlor A) \vlan (D \vlor C)}{
+      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{(A \vlor B) \vlan ((C \vlan E) \vlor D)}{
+    \vlin{\fequ}{}{(A \vlan (C \vlan E)) \vlor (B \vlan D)}{
+      \vlhy{((A \vlan C) \vlan E) \vlor (B \vlan D)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
+    \vlin{\fequ}{(x \notin fv(B \vlan D))}{\forall x.((A \vlan C) \vlor (B \vlan D))}{
+      \vlhy{(forall x.(A \vlan C)) \vlor (B \vlan D)}}}}
+\end{equation*}
+
+($\fequ/\mfaD$)
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
+      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
+\leadsto
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+    \vlin{\mfaD}{}{\forall x.(B \vlor A)}{
+      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.((\forall y.A) \vlor B)}{
+    \vlin{\fequ}{}{(\forall x.\forall y.A) \vlor (\forall x.B)}{
+      \vlhy{(\forall y.\forall x.A) \vlor (\forall x.B)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
+      \vlhy{\forall x.(A \vlor (\forall x.B))}}}}
+\end{equation*}
+
+($\fequ/\mexD$): similar to $\fequ/\mfaD$
+
 \end{proof}
@@
 
+%\clearhalfpage
+
+\vskip3em
+
+\appendix
+
+\subsection{Rule permutation for the proof of Lemma~\ref{lem:cw-decomposition}}
+
 % that's all folks

### 2021-01-25 main.tex
minor

@@
 A vertex set $W \subseteq \vC$ induces a \bfit{matching} in
-$\gC$ if 
-it is non-empty\dominic{added non-empty (necessary, right?)}
+$\gC$ if $W\neq\emptyset$ and 
 for all $w \in W$, $N(w) \cap W$ is a singleton. We say that $W$ induces a
@@
 %
+%\noindent
 Figure~\ref{fig:leap} shows a fonet with a unique dualizer, and its leap graph.
@@
 if for all existential binders $b$ in
-$\gG$, the binder $\phi(b)$ is a existential in $\gH$.\dominic{tweaked this paragraph}
+$\gG$, the binder $\phi(b)$ is a existential in $\gH$.
 %

### 2021-01-25 main.tex
rule permutation

@@
   \todo{permutation with $\fequ$}
-
-($\cfaD/\fequ$)
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall y.\forall x.A}{
-    \vlin{\cfaD}{}{\forall x.\forall y.A}{
-      \vlhy{\forall x.\forall x.\forall y.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cfaD}{}{\forall y.\forall x.A}{
-    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
-      \vlhy{\forall x.\forall x.\forall y.A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
-    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x. A) \vlor B}{
-      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{(x \notin fv(B))}{\forall x.(A \vlor B)}{
-    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
-      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
-\end{equation*}
-
-($\wrD/\fequ$)
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{B \vlor A}{
-    \vlin{\wrD}{}{A \vlor B}{
-      \vlhy{A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{A \vlor (B \vlor C)}{
-    \vlin{\wrD}{}{(A \vlor B) \vlor C)}{
-      \vlhy{A \vlor C}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
-    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-      \vlhy{\forall x.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{(\forall x. A) \vlor B}{
-    \vlhy{\forall x.A}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{(x \notin fv(B))}{\forall x.(A \vlor B)}{
-    \vlin{\wrD}{}{(\forall x.A) \vlor B}{
-      \vlhy{\forall x.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-    \vlhy{\forall x.A}}}
-\end{equation*}
-
-($\fequ/\cfaD$)
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{\forall x.\forall y.A}{
-    \vlin{\fequ}{}{\forall x.\forall x.\forall y. A}{
-      \vlhy{\forall x.\forall y.\forall x.A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{\forall y.\forall x.A}{
-    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
-      \vlhy{\forall x.\forall y.\forall x.A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x.A) \vlor B}{
-      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
-      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
-\end{equation*}
-
-($\fequ/\me$)
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
-      \vlhy{(C \vlan A) \vlor (B \vlan D)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
-      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
-\leadsto
-\vlderivation{
-  \vlin{\fequ}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\me}{}{(B \vlor A) \vlan (D \vlor C)}{
-      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{(A \vlor B) \vlan ((C \vlan E) \vlor D)}{
-    \vlin{\fequ}{}{(A \vlan (C \vlan E)) \vlor (B \vlan D)}{
-      \vlhy{((A \vlan C) \vlan E) \vlor (B \vlan D)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
-    \vlin{\fequ}{(x \notin fv(B \vlan D))}{\forall x.((A \vlan C) \vlor (B \vlan D))}{
-      \vlhy{(forall x.(A \vlan C)) \vlor (B \vlan D)}}}}
-\end{equation*}
-
-($\fequ/\mfaD$)
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
-      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
-\leadsto
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlin{\mfaD}{}{\forall x.(B \vlor A)}{
-      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.((\forall y.A) \vlor B)}{
-    \vlin{\fequ}{}{(\forall x.\forall y.A) \vlor (\forall x.B)}{
-      \vlhy{(\forall y.\forall x.A) \vlor (\forall x.B)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
-      \vlhy{\forall x.(A \vlor (\forall x.B))}}}}
-\end{equation*}
-
-($\fequ/\mexD$): similar to $\fequ/\mfaD$
 
@@
   We can permute both instances via the following more general scheme
-  (see~\cite{str:medial,lamarche:gap} for a general discussion on
+  (see~\cite{str:07:RTA,lamarche:gap} for a general discussion on
   permutations of the $\me$-rule):
@@
 \subsection{Rule permutation for the proof of Lemma~\ref{lem:cw-decomposition}}
+
+Interaction between two rules:
+\begin{itemize}
+\item $\cfaD/\fequ$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall y.\forall x.A}{
+    \vlin{\cfaD}{}{\forall x.\forall y.A}{
+      \vlhy{\forall x.\forall x.\forall y.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cfaD}{}{\forall y.\forall x.A}{
+    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
+      \vlhy{\forall x.\forall x.\forall y.A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
+    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x. A) \vlor B}{
+      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{(x \notin fv(B))}{\forall x.(A \vlor B)}{
+    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
+      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
+\end{equation*}
+
+\item $\wrD/\fequ$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{B \vlor A}{
+    \vlin{\wrD}{}{A \vlor B}{
+      \vlhy{A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{A \vlor (B \vlor C)}{
+    \vlin{\wrD}{}{(A \vlor B) \vlor C)}{
+      \vlhy{A \vlor C}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
+    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+      \vlhy{\forall x.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{(\forall x. A) \vlor B}{
+    \vlhy{\forall x.A}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{(x \notin fv(B))}{\forall x.(A \vlor B)}{
+    \vlin{\wrD}{}{(\forall x.A) \vlor B}{
+      \vlhy{\forall x.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+    \vlhy{\forall x.A}}}
+\end{equation*}
+
+\item $\fequ/\cfaD$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{\forall x.\forall y.A}{
+    \vlin{\fequ}{}{\forall x.\forall x.\forall y. A}{
+      \vlhy{\forall x.\forall y.\forall x.A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{\forall y.\forall x.A}{
+    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
+      \vlhy{\forall x.\forall y.\forall x.A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x.A) \vlor B}{
+      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
+      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
+\end{equation*}
+
+\item $\fequ/\me$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
+      \vlhy{(C \vlan A) \vlor (B \vlan D)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
+      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
+\leadsto
+\vlderivation{
+  \vlin{\fequ}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\me}{}{(B \vlor A) \vlan (D \vlor C)}{
+      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{(A \vlor B) \vlan ((C \vlan E) \vlor D)}{
+    \vlin{\fequ}{}{(A \vlan (C \vlan E)) \vlor (B \vlan D)}{
+      \vlhy{((A \vlan C) \vlan E) \vlor (B \vlan D)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
+    \vlin{\fequ}{(x \notin fv(B \vlan D))}{\forall x.((A \vlan C) \vlor (B \vlan D))}{
+      \vlhy{(\forall x.(A \vlan C)) \vlor (B \vlan D)}}}}
+\end{equation*}
+
+\item $\fequ/\mfaD$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
+      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
+\leadsto
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+    \vlin{\mfaD}{}{\forall x.(B \vlor A)}{
+      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.((\forall y.A) \vlor B)}{
+    \vlin{\fequ}{}{(\forall x.\forall y.A) \vlor (\forall x.B)}{
+      \vlhy{(\forall y.\forall x.A) \vlor (\forall x.B)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
+      \vlhy{\forall x.(A \vlor (\forall x.B))}}}}
+\end{equation*}
+
+\item $\fequ/\mexD$: similar to $\fequ/\mfaD$
+
+\end{itemize}
+
+Interactions between two non-$\fequ$ rules with the presence of $\fequ$ in
+between:
+
+\begin{itemize}
+\item $\cfaD/\fequ/\rr$ where $\rr \in \set{\me, \mfaD, \mexD}$: First permute
+$\cfaD$ under $\fequ$ and then permute $\cfaD$ under $\rr$.
+
+\item $\acD/\fequ/\rr$ where $\rr \in \set{\me, \mfaD, \mexD}$: First permute
+$\acD$ under $\fequ$ and then permute $\acD$ under $\rr$.
+
+\item $\wrD/\fequ/\cfaD$: We only list non-trivial cases here:
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+      \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x.A) \vlor B}{
+        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
+          \vlhy{\forall x.\forall x.A}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{(\forall x.A) \vlor B}{
+      \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+        \vlhy{\forall x.\forall x.A}}}}
+  \end{equation*}
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+      \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x.A) \vlor B}{
+        \vlin{\wrD}{}{\forall x.(B \vlor (\forall x.A))}{
+          \vlhy{\forall x.B}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
+      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
+        \vlhy{\forall x.B}}}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+      \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
+        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
+          \vlhy{\forall x.\forall x.A}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+      \vlin{\cfaD}{}{\forall x.A}{
+        \vlhy{\forall x.\forall x.A}}}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+      \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
+        \vlin{\wrD}{}{\forall x.(B \vlor (\forall x.A))}{
+          \vlhy{\forall x.B}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
+        \vlhy{\forall x.B}}}}
+  \end{equation*}
+
+\item $\wrD/\fequ/\acD$:
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\acD}{}{a \vlor B}{
+      \vlin{\fequ}{}{(a \vlor a) \vlor B}{
+        \vlin{\wrD}{}{(a \vlor B) \vlor a}{
+          \vlhy{a \vlor B}}}}}
+  \leadsto
+  \vlderivation{
+    \vlhy{a \vlor B}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\acD}{}{a \vlor B}{
+      \vlin{\fequ}{}{(a \vlor a) vlor B}{
+        \vlin{\wrD}{}{a \vlor (a \vlor B)}{
+          \vlhy{a}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{a \vlor B}{
+      \vlhy{a}}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\acD}{}{\forall x.a}{
+      \vlin{\fequ}{(x \notin fv(a))}{\forall x.(a \vlor a)}{
+        \vlin{\wrD}{}{(\forall x.a) \vlor a}{
+          \vlhy{\forall x.a}}}}}
+  \leadsto
+  \vlderivation{
+    \vlhy{\forall x.a}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\acD}{}{\forall x.a}{
+      \vlin{\fequ}{(x \notin fv(a))}{\forall x.(a \vlor a)}{
+        \vlin{\wrD}{}{a \vlor (\forall x.a)}{
+          \vlhy{a}}}}}
+  \leadsto     
+  \end{equation*}
+
+\item $\wrD/\fequ/\me$:
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
+      \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
+        \vlin{\wrD}{}{(C \vlan A) \vlor (B \vlan D)}{
+          \vlhy{C \vlan A}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{(A \vlor B) \vlan (C \vlor D)}{
+      \vlin{\wrD}{}{(A \vlor B) \vlan C}{
+        \vlin{\fequ}{}{A \vlan C}{
+          \vlhy{C \vlan A}}}}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
+      \vlin{\fequ}{x \notin fv(B \vlan D)}{\forall x.((A \vlan C) \vlor (B \vlan
+D))}{
+        \vlin{\wrD}{}{(B \vlan D) \vlor (\forall x.(A \vlan C))}{
+          \vlhy{B \vlan D}}}}}
+  \leadsto
+  \end{equation*}
+
+\item $\wrD/\fequ/\mfaD$:
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+      \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
+        \vlin{\wrD}{}{(\forall x.B) \vlor (\forall x.A)}{
+          \vlhy{\forall x.B}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
+        \vlhy{\forall x.B}}}}
+  \end{equation*}
+
+\item $\wrD/\fequ/\mexD$:
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\mexD}{}{\exists x.(A \vlor B)}{
+      \vlin{\fequ}{}{(\exists x.A) \vlor (\exists x.B)}{
+        \vlin{\wrD}{}{(\exists x.B) \vlor (\exists x.A)}{
+          \vlhy{\exists x.B}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\fequ}{}{\exists x.(A \vlor B)}{
+      \vlin{\wrD}{}{\exists x.(B \vlor A)}{
+        \vlhy{\exists x.B}}}}
+  \end{equation*}
+
+\end{itemize}
 

### 2021-01-25 main.tex
minor

--- 2021-01-25 main.tex
@@
   \vskip-2ex
-  \caption{Condensed forms of the four combinatorial proofs in Fig.\,\ref{fig:cps}.}
+  \caption{Condensed forms of the four combinatorial proofs in Figure~\ref{fig:cps}. We do not show the lower graph, and indicate the mapping by the position of the vertices of the upper graph.}
   \label{fig:cps-condensed}
@@
   (modulo renaming),
-  we often omit the labeling in the upper graph, as below-right, which refer to as 
-  \bfit{condensed form}.\dominic{I said ``can be inferred'' to account for 
-  e.g.\
-  $\graphof{\forall x_1\forall x_2 (px_i\vee px_j\vee px_k\vee px_l)}
-  \to \graphof{\forall x\mkern2mu px}$ whose
-  unlabelled skeleton is the skeleton of many distinct formula variants (``who binds who?'').}
+  we often omit the labeling in the upper graph, as below-right.
+  %% , which refer to as 
+  %% \bfit{condensed form}.\dominic{I said ``can be inferred'' to account for 
+  %% e.g.\
+  %% $\graphof{\forall x_1\forall x_2 (px_i\vee px_j\vee px_k\vee px_l)}
+  %% \to \graphof{\forall x\mkern2mu px}$ whose
+  %% unlabelled skeleton is the skeleton of many distinct formula variants (``who binds who?'').}
   \begin{center}\begin{math}
@@
 The same FOCPs are shown in
-Figure~\ref{fig:cps-condensed} in condensed form.
+Figure~\ref{fig:cps-condensed} in a ``condensed form''.
 %
@@
   definition of~\cite{hughes:fopws}, as we allow for a variable
-  renaming $\substof\phi$ which was forced to be the identity
+  renaming $\rsubstof\phi$ which was forced to be the identity
   in~\cite{hughes:fopws}.
@@
   \label{fig:KS1}
+  \vskip-.2ex
 \end{figure}
@@
 here, we omit the down-arrows $\downarrow$ in the rule names.}
-
+%
 As with the sequent system $\FOLK$, we also need for $\FOKS$ the
@@
 
-Write $\vlder{\sysS}{\Deri}{A}{B}$ to denote a derivation $\Deri$
+We write $\vlder{\sysS}{\Deri}{A}{B}$ to denote a derivation $\Deri$
 from $B$ to $A$ using the rules from system $\sysS$. A formula $A$ is
@@
 general (non-atomic) version of the contraction rule:
-\begin{equation*}
+\begin{equation}
   \vlinf{\cD}{}{\Scons{A}}{\Scons{A\vlor A}}  
-\end{equation*}
+\end{equation}
 
@@
 \end{thm}
-
+\noindent
 This theorem is stronger than the existing decompositions for
-first-order logic, which either separated only atomic contraction and
+first-order logic, which either separate only atomic contraction and
 atomic weakening~\cite{brunnler:phd} or only
@@
 
-Theorem~\ref{thm:decomposition} is also the reason why we have te rule
+Theorem~\ref{thm:decomposition} is also the reason why we have the rules
 $\wfaD$ and $\cfaD$ in system $\FOKS$, as these rules are derivable

### 2021-01-25 main.tex
fixed units

@@
     \\[.5ex]
-    a &\coloneqq~ p(t_1,\dots,t_n) \mid \dual p(t_1,\dots,t_n)
+    a &\coloneqq~ \ttt\mid\fff\mid p(t_1,\dots,t_n) \mid \dual p(t_1,\dots,t_n)
     \\[.5ex]
-    A &\coloneqq~ a \mid \ttt\mid\fff\mid A\vlan A \mid A\vlor A \mid \exists x.A \mid \forall x.A
+    A &\coloneqq~ a \mid A\vlan A \mid A\vlor A \mid \exists x.A \mid \forall x.A
 \end{array}
@@
   \begin{array}{r@{\;}l@{\hskip4em}r@{\;}l}
-    \multicolumn{4}{c}{
-      \quad\graphof{\ttt}=\single\ttt
-      \qquad
-      \graphof{\fff}=\single\fff
-      \qquad
-    \graphof{a} = \single a \hbox{\hskip1em(for any atom $a$)} } \\[1.1ex]
+    %% \multicolumn{4}{c}{
+    %%   \quad\graphof{\ttt}=\single\ttt
+    %%   \qquad
+    %%   \graphof{\fff}=\single\fff
+    %%   \qquad
+    %% \graphof{a} = \single a \hbox{\hskip1em(for any atom $a$)} } \\[1.1ex]
+    \graphof{a} &= \single a \rlap{\hskip1em(for any atom $a$)}  \\[.9ex]
     \graphof{A \cor B} &= \graphof{A} + \graphof{B} &
@@
 
-Two atoms are \bfit{pre-dual} if their predicate symbols are dual
+Two atoms are \bfit{pre-dual} if they are not $\ttt$ or $\fff$, and their predicate symbols are dual
 (e.g. $p(x, y)$ and $\dual{p}(y, z)$) and two literals are \bfit{pre-dual} if their
@@
 that every colour (i.e., equivalence class of~$\linkingof\gC$), called a \bfit{link}, consists of two pre-dual literals, and
-every literal is either $\ttt$-labelled or in a link.
+every literal is either $\ttt$-labelled or in a link. Hence, in a linked fograph no vertex is labeled~$\fff$.
 
@@
 \begin{thm}\label{thm:decomposition}
-  For every derivation $\vlder{\FOKS}{\Deri}{A}{\ttt}$ there are formulas $A_1,\ldots,A_5$, such that there is a derivation:
-  \begin{equation*}
+  For every derivation $\vlder{\FOKS}{\Deri}{A}{\ttt}$ there are $\fff$-free formulas $A_1,\ldots,A_5$, such that there is a derivation:
+  \begin{equation*}
+    \scalebox{.9}{$
     \vlderivation{
@@
                   \vlhy{\ttt}}}}}}}}
+    $}
   \end{equation*}
@@
 
-\begin{example}
-  Below is an example of a decomposed derivation in $\FOKS$ of the
+%\begin{example}
+  Figure~\ref{fig:example-decompose} shows an example of a decomposed derivation in $\FOKS$ of the
   formula $(\exists x. \cneg{p}(x)) \vlor (\forall y.(p(y) \vlan
-  p(f(y))))$:
-  \begin{equation*}
+  p(f(y))))$.
+%\end{example}
+
+\begin{figure}
+  \begin{equation*}
+    \scalebox{.9}{$
     \vlderivation{
@@
                           \vlhy{\ttt}}}}}}}}}}}}}}
-  \end{equation*}
-\end{example}
+    $}
+  \end{equation*}    
+    \caption{Example derivation in decomposed form of Theorem~\ref{thm:decomposition}}
+    \label{fig:example-decompose}
+  \end{figure}
 %
@@
 \begin{thm}\label{thm:decompositionA}
-  For every derivation $\vlder{\FOKS}{\Deri}{A}{\ttt}$ there is a formula $A_1$, such that there is a derivation:
-  \begin{equation*}
+  For every derivation $\upsmash{\vlder{\FOKS}{\Deri}{A}{\ttt}}$ there is a formula~$A_1$ not containing any occurence of $\fff$, such that there is a derivation:
+  \begin{equation*}
+    %\scalebox{.9}{$
     \vlderivation{
@@
           \vlhy{\ttt}}}}
+   % $}
   \end{equation*}
@@
   \end{equation}
-  for some $A'\fequ C\substof\phi$ where $C$ is a formula with $\graphof
-  C=\gC$ and $\substof\phi$ is the variable renaming substitution
+  for some $A'\fequ C\rsubstof\phi$ where $C$ is a formula with $\graphof
+  C=\gC$ and $\rsubstof\phi$ is the variable renaming substitution
   induced by~$\phi$.  Conversely,
-  whenever we have a derivation as in~\eqref{eq:decom} above, then
+  whenever we have a derivation as in~\eqref{eq:decom} above, such that $\fff$ does not occur in~$A_1$, then
   there is a combinatorial proof $\phi\colon\gC\to\graphof A$ such
@@
   $\FOMLL$, making a case analysis on the bottommost rule instance. We
-  show here only the case of $\vlinf{\forall}{}{\sqn{\Delta,\forall
-      x.A}}{\sqn{\Delta,A}}$ (all other cases are simpler and have
-  been shown before, e.g.~\cite{brunnler:phd}): By induction
-  hypothesis, there is a proof of $\form\Delta\vlor A$ in $\FOMLS$. We
-  can prefix every line in that proof by $\forall x$ and then compose
-  the following derivation:
+  show here only the case of
+%%  $\downsmash{\vlinf{\fff}{}{\sqn{\Delta,\fff}}{\sqn\Delta}}$ and
+  $\vlinf{\forall}{}{\sqn{\Delta,\forall x.A}}{\sqn{\Delta,A}}$ (all
+  other cases are simpler or have been shown before,
+  e.g.~\cite{brunnler:phd}): By induction hypothesis, there is a proof
+  of $\form\Delta\vlor A$ in $\FOMLS$. We can prefix every line in
+  that proof by $\forall x$ and then compose the following derivation:
   \begin{center}\vspace{-2ex}\begin{math}
@@
   Let $\vlinf{\rr}{}{\Scons B}{\Scons A}$ be an inference rule in
-  $\FOMLS$ other than $\aiD$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
+  $\FOMLS$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
 \end{lemma}
 \begin{proof}
-  This is a straightforward exercise that we leave to the reader. (Note that the
-$\ax$-rule can be applied to $\sqn{\fff,\ttt}$ in the cases of $\rr = \faD$.)
+  This is a straightforward exercise.
+%%  that we leave to the reader. (Note that the
+%%$\ax$-rule can be applied to $\sqn{\fff,\ttt}$ in the cases of $\rr = \faD$.)
 \end{proof}
@@
   $\vlinf{\rr}{}{\Scons B}{\Scons A}$. By induction hypothesis we have
-  a $\FOMLL$ proof $\Proof$ of $\sqn{\Scons A}$. If $\rr$ is
-  $\upsmash{\vlinf{\aiD}{}{\Scons{a\vlor\cneg a}}{\Scons\ttt}}$, we replace
-  in $\Pi$ all corresponding occurrences of $\ttt$ with
-  $a \vlor \cneg a$ and the rule instance
-  $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation $ \vlderivation{
-    \vlin{\vlor}{}{\sqn{a \vlor \cneg a}}{ \vlin{\axr}{}{\sqn{a, \cneg
-          a}}{ \vlhy{}}}} $. This gives us a proof of
-  $\sqn{\Scons{a \vlor \cneg a}}$. In all other cases, 
-    %\item $\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
-     % In this case, we replace simultaneously in $\Pi$ the corresponding
-     % occurrences of $\ttt$ with $\forall x.\ttt$ and the rule instance
-     % $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
-     % $
-     % \vlderivation{
-     %   \vlin{\forall}{}{\sqn{\forall x.\ttt}}{
-     %     \vlin{\axr}{}{\sqn{\ttt}}{
-     %       \vlhy{}}}}
-     % $, and we get a proof $\Pi'$ of $\sqn{\Scons{\forall x.\ttt}}$.
-      by Lemmas~\ref{lem:shallow} and~\ref{lem:context}, we have a $\FOMLL$ proof of
+  a $\FOMLL$ proof $\Proof$ of $\sqn{\Scons A}$.
+  %% If $\rr$ is
+  %% $\upsmash{\vlinf{\aiD}{}{\Scons{a\vlor\cneg a}}{\Scons\ttt}}$, we replace
+  %% in $\Pi$ all corresponding occurrences of $\ttt$ with
+  %% $a \vlor \cneg a$ and the rule instance
+  %% $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation $ \vlderivation{
+  %%   \vlin{\vlor}{}{\sqn{a \vlor \cneg a}}{ \vlin{\axr}{}{\sqn{a, \cneg
+  %%         a}}{ \vlhy{}}}} $. This gives us a proof of
+  %% $\sqn{\Scons{a \vlor \cneg a}}$. In all other cases, 
+  %%   %\item $\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
+  %%    % In this case, we replace simultaneously in $\Pi$ the corresponding
+  %%    % occurrences of $\ttt$ with $\forall x.\ttt$ and the rule instance
+  %%    % $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
+  %%    % $
+  %%    % \vlderivation{
+  %%    %   \vlin{\forall}{}{\sqn{\forall x.\ttt}}{
+  %%    %     \vlin{\axr}{}{\sqn{\ttt}}{
+  %%    %       \vlhy{}}}}
+  %%    % $, and we get a proof $\Pi'$ of $\sqn{\Scons{\forall x.\ttt}}$.
+      By Lemmas~\ref{lem:shallow} and~\ref{lem:context}, we have a $\FOMLL$ proof of
       $\sqn{\cneg{\Scons A},\Scons B}$. We can compose them via $\cutr$:
@@
 \begin{proof}
-  We show that there is always a derivation
-  $$
-  \vlderivation{
-    \vlde{\sysS}{}{A}{
-      \vlhy{A \vlor A}}}
-  $$, where $\sysS = \set{\acD,\me,\mfaD,\mexD,\fequ}$, by induction on $A$:
-  \begin{itemize}
-    \item If $A = a$, then we have
-      $
-      \vlderivation{
-        \vlin{\acD}{}{a}{
-          \vlhy{a \vlor a}}}
-      $.
-    \item If $A = B \vlan C$, then we have
-      $
-      \vlderivation{
-	\vlde{\sysS}{}{B \vlan C}{
-	  \vlde{\sysS}{}{B \vlan (C \vlor C)}{
-	    \vlin{\me}{}{(B \vlor B) \vlan (C \vlor C)}{
-	      \vlhy{(B \vlan C) \vlor (B \vlan C)}}}}}
-      $.\\[.5ex]
-    \item If $A = B \vlor C$, then we have
-      $
-      \vlderivation{
-	\vlde{\sysS}{}{B \vlor C}{
-	  \vlde{\sysS}{}{B \vlor (C \vlor C)}{
-	    \vlin{\fequ}{}{(B \vlor B) \vlor (C \vlor C)}{
-	      \vlhy{(B \vlor C) \vlor (B \vlor C)}}}}}
-      $.\\[.5ex]
-    \item If $A = \exists x.A'$, then we have
-      $
-      \vlderivation{
-	\vlde{\sysS}{}{\exists x.A'}{
-	  \vlin{\mexD}{}{\exists x.(A' \vlor A')}{
-	    \vlhy{(\exists x.A') \vlor (\exists x.A')}}}}
-      $.\\[.5ex]
-    \item If $A = \forall x.A'$, then we have
-      $
-      \vlderivation{
-	\vlde{\sysS}{}{\forall x.A'}{
-	  \vlin{\mexD}{}{\forall x.(A' \vlor A')}{
-	    \vlhy{(\forall x.A') \vlor (\forall x.A')}}}}
-      $.
-  \end{itemize}
-  \todo{}
-  \juihsuan{done. Maybe just keep one case.}\lutz{yes, but we do that at the end. don't think about space right now.}
+  This can be shown by a straightforward induction on $A$ (for details, see e.g.~\cite{brunnler:phd}).
+  %% We show that there is always a derivation
+  %% $$
+  %% \vlderivation{
+  %%   \vlde{\sysS}{}{A}{
+  %%     \vlhy{A \vlor A}}}
+  %% $$, where $\sysS = \set{\acD,\me,\mfaD,\mexD,\fequ}$, by induction on $A$:
+  %% \begin{itemize}
+  %%   \item If $A = a$, then we have
+  %%     $
+  %%     \vlderivation{
+  %%       \vlin{\acD}{}{a}{
+  %%         \vlhy{a \vlor a}}}
+  %%     $.
+  %%   \item If $A = B \vlan C$, then we have
+  %%     $
+  %%     \vlderivation{
+  %%       \vlde{\sysS}{}{B \vlan C}{
+  %%         \vlde{\sysS}{}{B \vlan (C \vlor C)}{
+  %%           \vlin{\me}{}{(B \vlor B) \vlan (C \vlor C)}{
+  %%             \vlhy{(B \vlan C) \vlor (B \vlan C)}}}}}
+  %%     $.\\[.5ex]
+  %%   \item If $A = B \vlor C$, then we have
+  %%     $
+  %%     \vlderivation{
+  %%       \vlde{\sysS}{}{B \vlor C}{
+  %%         \vlde{\sysS}{}{B \vlor (C \vlor C)}{
+  %%           \vlin{\fequ}{}{(B \vlor B) \vlor (C \vlor C)}{
+  %%             \vlhy{(B \vlor C) \vlor (B \vlor C)}}}}}
+  %%     $.\\[.5ex]
+  %%   \item If $A = \exists x.A'$, then we have
+  %%     $
+  %%     \vlderivation{
+  %%       \vlde{\sysS}{}{\exists x.A'}{
+  %%         \vlin{\mexD}{}{\exists x.(A' \vlor A')}{
+  %%           \vlhy{(\exists x.A') \vlor (\exists x.A')}}}}
+  %%     $.\\[.5ex]
+  %%   \item If $A = \forall x.A'$, then we have
+  %%     $
+  %%     \vlderivation{
+  %%       \vlde{\sysS}{}{\forall x.A'}{
+  %%         \vlin{\mexD}{}{\forall x.(A' \vlor A')}{
+  %%           \vlhy{(\forall x.A') \vlor (\forall x.A')}}}}
+  %%     $.
+  %% \end{itemize}
+  %% \todo{}
+  %% \juihsuan{done. Maybe just keep one case.}\lutz{yes, but we do that at the end. don't think about space right now.}
 \end{proof}
@@
 \begin{proof}
+  We only show the cases for $\wfaD$ and $\cfaD$:
+  $$
   \todo{}
-
-  We have the following derivations:
-  $$
   \vlderivation{
@@
           \vlhy{\forall x.\forall x.A}}}}}
-  $$.
   $$
-  \vlderivation{
-    \vlin{\cD}{}{(A \vlor B) \vlan (C \vlor D)}{
-      \vlin{\fequ}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((A \vlor B) \vlan (C \vlor D))}{
-      \vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((B \vlor A) \vlan (D \vlor C))}{
-	\vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((B \vlor A) \vlan D))}{
-	  \vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor (B \vlan D))}{
-	    \vlin{\wrD}{}{((A \vlor B) \vlan C) \vlor (B \vlan D)}{
-	      \vlhy{(A \vlan C) \vlor (B \vlan D)}}}}}}}}
-  $$.
-  $$
-  \vlderivation{
-    \vlin{\cD}{}{\exists x.(A \vlor B)}{
-      \vlin{\fequ}{}{\exists x.(A \vlor B)) \vlor (\exists x.(A \vlor B))}{
-      \vlin{\wrD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.(B \vlor A))}{
-	\vlin{\wrD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.B)}{
-	  \vlhy{(\exists x.A) \vlor (\exists x.B)}}}}}}
-  $$.
-  $$
-  \vlderivation{
-    \vlin{\cD}{}{\forall x.(A \vlor B)}{
-      \vlin{\fequ}{}{(\forall x.(A \vlor B)) \vlor (\forall x.(A \vlor B))}{
-      \vlin{\wrD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.(B \vlor A))}{
-	\vlin{\wrD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.B)}{
-	  \vlhy{(\forall x.A) \vlor (\forall x.B)}}}}}}
-  $$.
-  \juihsuan{done. If needed, we can introduce the notion of open deduction to
-reduce the size of derivations...}\lutz{I was thinking about that, but (i) it is probably not worth the effort, as we wont have many derivation, and (ii) it is hard to define rectified derivations this way.}
+  The other cases have been shown before (e.g.~\cite{brunnler:phd}).
+%%   We have the following derivations:
+%%   $$
+%%   \vlderivation{
+%%     \vlin{\cD}{}{\forall x.A}{
+%%       \vlin{\equiv}{(x \notin fv(\forall x.A))}{(\forall x.A) \vlor (\forall x.A)}{
+%%         \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor A)}{
+%%           \vlhy{\forall x.\forall x.A}}}}}
+%%   $$.
+%%   $$
+%%   \vlderivation{
+%%     \vlin{\cD}{}{(A \vlor B) \vlan (C \vlor D)}{
+%%       \vlin{\fequ}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((A \vlor B) \vlan (C \vlor D))}{
+%%       \vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((B \vlor A) \vlan (D \vlor C))}{
+%% 	\vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((B \vlor A) \vlan D))}{
+%% 	  \vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor (B \vlan D))}{
+%% 	    \vlin{\wrD}{}{((A \vlor B) \vlan C) \vlor (B \vlan D)}{
+%% 	      \vlhy{(A \vlan C) \vlor (B \vlan D)}}}}}}}}
+%%   $$.
+%%   $$
+%%   \vlderivation{
+%%     \vlin{\cD}{}{\exists x.(A \vlor B)}{
+%%       \vlin{\fequ}{}{\exists x.(A \vlor B)) \vlor (\exists x.(A \vlor B))}{
+%%       \vlin{\wrD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.(B \vlor A))}{
+%% 	\vlin{\wrD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.B)}{
+%% 	  \vlhy{(\exists x.A) \vlor (\exists x.B)}}}}}}
+%%   $$.
+%%   $$
+%%   \vlderivation{
+%%     \vlin{\cD}{}{\forall x.(A \vlor B)}{
+%%       \vlin{\fequ}{}{(\forall x.(A \vlor B)) \vlor (\forall x.(A \vlor B))}{
+%%       \vlin{\wrD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.(B \vlor A))}{
+%% 	\vlin{\wrD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.B)}{
+%% 	  \vlhy{(\forall x.A) \vlor (\forall x.B)}}}}}}
+%%   $$.
+%%   \juihsuan{done. If needed, we can introduce the notion of open deduction to
+%% reduce the size of derivations...}\lutz{I was thinking about that, but (i) it is probably not worth the effort, as we wont have many derivation, and (ii) it is hard to define rectified derivations this way.}
 \end{proof}
@@
 \begin{proof}
-  This follows immediately from Lemmas~\ref{lem:ac} and~\ref{lem:me}.
+  Immediately from Lemmas~\ref{lem:ac} and~\ref{lem:me}.
 \end{proof}
@@
   \begin{equation}
-    \label{eq:decom}
+    \label{eq:decomx}
     \vlderivation{

### 2021-01-25 main.tex
fix the rule permutation part

--- 2021-01-25 main.tex
@@
     \vlin{\cD}{}{\forall x.A}{
+      \vlin{\fequ}{(x \notin fv(A))}{\forall x.(A \vlor A)}{
+        \vlin{\wrD}{}{A \vlor (\forall x.A)}{
+          \vlhy{A}}}}}
+  $$.
+  $$
+  \vlderivation{
+    \vlin{\cD}{}{\forall x.A}{
       \vlin{\equiv}{(x \notin fv(\forall x.A))}{(\forall x.A) \vlor (\forall x.A)}{
@@
 \begin{proof}
-  First, a derivation consisting of an instance of $\wrD$ followed by $\rr \in \set{\acD, \cfaD,
-\me, \mfaD, \mexD}$ can be either replaced by a derivation consisting of $\wrD$
-only or the instance of $\wrD$ can be permuted downwards. We show some cases
-here, and leave the others to the reader.
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
-      \vlin{\wrD}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
-        \vlhy{\Scons{\forall x.A}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{\Scons{\forall x.(A \vlor B)}}{
-      \vlhy{\Scons{\forall x.A}}}}
-  \end{equation*}
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\me}{}{\Scons{(A \vlor B) \vlan (C \vlor D)}}{
-      \vlin{\wrD}{}{\Scons{(A \vlan C) \vlor (B \vlan D)}}{
-        \vlhy{\Scons{A \vlan C}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{\Scons{(A \vlor B) \vlan (C \vlor D)}}{
-      \vlin{\wrD}{}{\Scons{(A \vlor B) \vlan C}}{
-        \vlhy{\Scons{A \vlan C}}}}}
-  \end{equation*}
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\acD}{}{\Scons{a}}{
-      \vlin{\wrD}{}{\Scons{a \vlor a}}{
-        \vlhy{\Scons{a}}}}}
-  \leadsto
-  \vlderivation{
-    \vlhy{\Scons{a}}}
-  \end{equation*}
-
-  For $\rr_1 \in \set{\me, \mfaD, \mexD}$, $\rr_2 \in \set{\acD, \cfaD}$,
-$\rr_1$ can be permuted upwards over $\rr_2$ (with some $\fequ$ inserted). The only non-trivial case is shown below:
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
-      \vlin{\cfaD}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
-        \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
-      \vlin{\fequ}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
-        \vlin{\mfaD}{}{\Scons{\forall x.(\forall x.A \vlor B)}}{
-          \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}}
-  \end{equation*}
+
   \todo{permutation with $\fequ$}
@@
 
-Interaction between two rules:
+We first study the interactions between two rules (only non-trivial cases are
+presented here):
 \begin{itemize}
+\item $\rr_1/\rr_2$, where $\rr_1 \in \set{\wrD, \wfaD}$ and $\rr_2 \in
+\set{\acD, \cfaD, \me, \mfaD, \mexD}$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\acD}{}{a}{
+    \vlin{\wrD}{}{a \vlor a}{ 
+      \vlhy{a}}}}
+\leadsto
+\vlderivation{
+  \vlhy{a}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\wrD}{}{(A \vlan C) \vlor (B \vlan D)}{
+      \vlhy{A \vlan C}}}}
+\leadsto 
+\vlderivation{
+  \vlin{\wrD}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\wrD}{}{(A \vlor B) \vlan C}{
+      \vlhy{A \vlan C}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\wrD}{}{(\forall x.A) \vlor (\forall x.B)}{
+      \vlhy{\forall x.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+    \vlhy{\forall x.A}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{\forall x.A}{
+    \vlin{\wfaD}{(x \notin fv(\forall x.A))}{\forall x.\forall x.A}{
+      \vlhy{\forall x.A}}}}
+\leadsto
+\vlderivation{
+  \vlhy{\forall x.A}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\wfaD}{(x \notin fv(A))}{(\forall x.A) \vlor (\forall x.B)}{
+      \vlhy{A \vlor (\forall x.B)}}}}
+\leadsto
+\vlderivation{
+  \vlin{\fequ}{(x \notin fv(A))}{\forall x.(A \vlor B)}{
+    \vlhy{A \vlor (\forall x.B)}}} 
+\end{equation*}
+
+\item $\rr_1/\rr_2$, where $\rr_1 \in \set{\acD, \cfaD}$ and $\rr_2 \in
+\set{\me, \mfaD, \mexD}$: 
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
+      \vlin{\cfaD}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
+        \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
+      \vlin{\fequ}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
+        \vlin{\mfaD}{}{\Scons{\forall x.(\forall x.A \vlor B)}}{
+          \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}}
+  \end{equation*}
+
 \item $\cfaD/\fequ$:
@@
     \vlhy{\forall x.A}}}
+\end{equation*}
+
+\item $\wfaD/\fequ$:
+
+In the following two cases, we assume $x \neq y$ (otherwise they are trivial).
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall y.\forall x.A}{
+    \vlin{\wfaD}{(x \notin fv(\forall y.A))}{\forall x.\forall y.A}{
+      \vlhy{\forall y.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wfaD}{(x \notin fv(A))}{\forall y.\forall x.A}{
+    \vlhy{\forall y.A}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.\forall y.A}{
+    \vlin{\wfaD}{(x \notin fv(A))}{\forall y.\forall x.A}{
+      \vlhy{\forall y.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wfaD}{(x \notin fv(\forall y.A))}{\forall x.\forall y.A}{
+    \vlhy{\forall y.A}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
+    \vlin{\wfaD}{(x \notin fv(A \vlor B))}{\forall x.(A \vlor B)}{
+      \vlhy{A \vlor B}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wfaD}{(x \notin fv(A))}{(\forall x.A) \vlor B}{
+    \vlhy{A \vlor B}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{(x \notin fv(B))}{\forall x.(A \vlor B)}{
+    \vlin{\wfaD}{(x \notin fv(A))}{(\forall x.A) \vlor B}{
+      \vlhy{A \vlor B}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wfaD}{(x \notin fv(A \vlor B))}{\forall x.(A \vlor B)}{
+    \vlhy{A \vlor B}}}
 \end{equation*}
@@
     \vlin{\acD}{}{a \vlor B}{
-      \vlin{\fequ}{}{(a \vlor a) vlor B}{
+      \vlin{\fequ}{}{(a \vlor a) \vlor B}{
         \vlin{\wrD}{}{a \vlor (a \vlor B)}{
@@
   \leadsto
+  \vlderivation{
+    \vlin{\wfaD}{(x \notin fv(a))}{\forall x.a}{
+      \vlhy{a}}}
   \end{equation*}
@@
     \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
-      \vlin{\fequ}{x \notin fv(B \vlan D)}{\forall x.((A \vlan C) \vlor (B \vlan
+      \vlin{\fequ}{(x \notin fv(B \vlan D))}{\forall x.((A \vlan C) \vlor (B \vlan
 D))}{
@@
   \leadsto
+  \vlderivation{
+    \vlin{\fequ}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
+      \vlin{\wrD}{}{\forall x.((B \vlor A) \vlan (D \vlor C))}{
+        \vlin{\wrD}{}{\forall x.((B \vlor A) \vlan D)}{
+          \vlin{\faD}{(x \notin fv(B \vlan D))}{\forall x.(B \vlan D)}{
+            \vlhy{B \vlan D}}}}}}
   \end{equation*}

### 2021-01-25 main.tex
LK

--- 2021-01-25 main.tex
@@
   Let $\Gamma$ be a sequent. If\/ $\sqn\Gamma$ is provable in $\FOLK$ (as depicted on the left below) then there is a sequent
-  $\Gamma'$ such that there is a derivation as shown on the right below:\vadjust{\vskip-2ex}
+  $\Gamma'$ not containing any $\fff$, such that there is a derivation as shown on the right below:\vadjust{\vskip-2ex}
   \begin{equation*}
@@
       \vlde{\set{\wrD,\cD,\fequ}}{\Deri_2}{\sqns{\form{\Gamma}}}{
-        \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\Gamma'}}{
+        \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\form{\Gamma'}}}{
           \vlhy{\quad}}{
@@
 \begin{proof}
-
-  Note that the instances of $\wrD,\cD$ in $\Deri_2$ are deep, but inside sequent contexts.
-
-First, if an instance of $\vlinf{\weakr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma}}$
- is followed by a rule in which $A$ is not in the principal
-formula, it can be permuted downwards.
-Otherwise, the proof can be transformed using the following rewriting rules.
-
-\begin{equation*}
-\vlderivation{
-  \vliin{\vlan}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
-      \vlhy{\sqns{\Gamma}}}}{
-    \vlhy{\sqns{B, \Delta}}}}
-\leadsto
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
-    \vlin{\weakr}{}{\vlvdots}{
-      \vlhy{\sqns{\Gamma}}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\vlor}{}{\sqns{\Gamma, A \vlor B}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A, B}}{
-      \vlhy{\sqns{\Gamma, A}}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{\sqns{\Gamma, A \vlor B}}{
-    \vlhy{\sqns{\Gamma, A}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\exists}{}{\sqns{\Gamma, \exists x.A}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A\ssubst{x}{t}}}{
-      \vlhy{\sqns{\Gamma}}}}}
-\leadsto
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, \exists x.A}}{
-    \vlhy{\sqns{\Gamma}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\forall}{}{\sqns{\Gamma, \forall x.A}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
-      \vlhy{\sqns{\Gamma}}}}}
-\leadsto
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, \forall x.A}}{
-    \vlhy{\sqns{\Gamma}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\conr}{}{\sqns{\Gamma, A}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A, A}}{
-      \vlhy{\sqns{\Gamma, A}}}}}
-\leadsto
-\vlderivation{
-  \vlhy{\sqns{\Gamma, A}}}
-\end{equation*}
-Note that in the case of $\vlor$, we use the deep rule $\wrD$ which can be
-permuted down over all the rules. By using these rewriting rules, we can eventually get
-a derivation with all the instances of $\weakr$ and $\wrD$ at the bottom. Now observe
-that the instances of $\conr$ in $\Deri$ can be transformed using the following
-rule:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\conr}{}{\sqns{\Gamma, A}}{
-    \vlhy{\sqns{\Gamma, A, A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cD}{}{\sqns{\Gamma, A}}{
-    \vlin{\vlor}{}{\sqns{\Gamma, A \vlor A}}{
-      \vlhy{\sqns{\Gamma, A, A}}}}}
-\end{equation*}
-
-Knowing that $\cD$ can be permuted down over all the rules of $\FOMLL$, we
-eventually obtain a derivation:
-\begin{equation*}
-\vlderivation{
-  \vlde{\set{\weakr, \wrD,\cD,\fequ}}{\Deri'_2}{\sqns{\Gamma}}{
-    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma_0}}{
-      \vlhy{\quad}}{
-      \vlhy{}}{
-      \vlhy{}}}}
-\end{equation*}
-Note that $\fequ$ is required here since the permutation of formulas is implicit
-in $\FOMLL$.
-
-By transforming each sequent of $\Deri'_2$ into its corresponding formula, and by
-considering the following rewriting rule:
-\begin{equation*}
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, A}}{
-    \vlhy{\sqns{\Gamma}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{\sqns{\form{\Gamma} \vlor A}}{
-    \vlhy{\sqns{\form{\Gamma}}}}}
-\end{equation*},
-we obtain a derivation
-\begin{equation*}
-\vlderivation{
-  \vlde{\set{\wrD,\cD,\fequ}}{\Deri_2}{\sqns{\form{\Gamma}}}{
-    \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\Gamma'}}{
-      \vlhy{\quad}}{
-      \vlhy{}}{
-      \vlhy{}}}}
-\end{equation*}
-where $\Gamma' = \form{\Gamma_0}$ and $\Deri_1$ can be obtained from $\Deri'_1$
-by applying the $\vlor$ rule.
-\tocheck{}
-\juihsuan{This might be a bit long...}
+  First, we can replace every instance of the $\fff$-rule by
+  $\weakr$. Then the instances of $\weakr$ and $\conr$ are replaced by
+  $\wD$ and $\cD$, which can then be permuted down. (Details are in
+  Appendix~\ref{app:LK1-decompose}.
 \end{proof}
@@
 
+\subsection{Proof of Theorem~\ref{thm:LK1-decompose}}
+\label{app:LK1-decompose}
+
+\begin{proof}[Proof of Theorem~\ref{thm:LK1-decompose}]
+
+  Note that the instances of $\wrD,\cD$ in $\Deri_2$ are deep, but inside sequent contexts.
+
+First, if an instance of $\vlinf{\weakr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma}}$
+ is followed by a rule in which $A$ is not in the principal
+formula, it can be permuted downwards.
+Otherwise, the proof can be transformed using the following rewriting rules.
+
+\begin{equation*}
+\vlderivation{
+  \vliin{\vlan}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
+      \vlhy{\sqns{\Gamma}}}}{
+    \vlhy{\sqns{B, \Delta}}}}
+\leadsto
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
+    \vlin{\weakr}{}{\vlvdots}{
+      \vlhy{\sqns{\Gamma}}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\vlor}{}{\sqns{\Gamma, A \vlor B}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A, B}}{
+      \vlhy{\sqns{\Gamma, A}}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{\sqns{\Gamma, A \vlor B}}{
+    \vlhy{\sqns{\Gamma, A}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\exists}{}{\sqns{\Gamma, \exists x.A}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A\ssubst{x}{t}}}{
+      \vlhy{\sqns{\Gamma}}}}}
+\leadsto
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, \exists x.A}}{
+    \vlhy{\sqns{\Gamma}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\forall}{}{\sqns{\Gamma, \forall x.A}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
+      \vlhy{\sqns{\Gamma}}}}}
+\leadsto
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, \forall x.A}}{
+    \vlhy{\sqns{\Gamma}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\conr}{}{\sqns{\Gamma, A}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A, A}}{
+      \vlhy{\sqns{\Gamma, A}}}}}
+\leadsto
+\vlderivation{
+  \vlhy{\sqns{\Gamma, A}}}
+\end{equation*}
+Note that in the case of $\vlor$, we use the deep rule $\wrD$ which can be
+permuted down over all the rules. By using these rewriting rules, we can eventually get
+a derivation with all the instances of $\weakr$ and $\wrD$ at the bottom. Now observe
+that the instances of $\conr$ in $\Deri$ can be transformed using the following
+rule:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\conr}{}{\sqns{\Gamma, A}}{
+    \vlhy{\sqns{\Gamma, A, A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cD}{}{\sqns{\Gamma, A}}{
+    \vlin{\vlor}{}{\sqns{\Gamma, A \vlor A}}{
+      \vlhy{\sqns{\Gamma, A, A}}}}}
+\end{equation*}
+
+Knowing that $\cD$ can be permuted down over all the rules of $\FOMLL$, we
+eventually obtain a derivation:
+\begin{equation*}
+\vlderivation{
+  \vlde{\set{\weakr, \wrD,\cD,\fequ}}{\Deri'_2}{\sqns{\Gamma}}{
+    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma_0}}{
+      \vlhy{\quad}}{
+      \vlhy{}}{
+      \vlhy{}}}}
+\end{equation*}
+Note that $\fequ$ is required here since the permutation of formulas is implicit
+in $\FOMLL$.
+
+By transforming each sequent of $\Deri'_2$ into its corresponding formula, and by
+considering the following rewriting rule:
+\begin{equation*}
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, A}}{
+    \vlhy{\sqns{\Gamma}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{\sqns{\form{\Gamma} \vlor A}}{
+    \vlhy{\sqns{\form{\Gamma}}}}}
+\end{equation*},
+we obtain a derivation
+\begin{equation*}
+\vlderivation{
+  \vlde{\set{\wrD,\cD,\fequ}}{\Deri_2}{\sqns{\form{\Gamma}}}{
+    \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\Gamma'}}{
+      \vlhy{\quad}}{
+      \vlhy{}}{
+      \vlhy{}}}}
+\end{equation*}
+where $\Gamma' = \form{\Gamma_0}$ and $\Deri_1$ can be obtained from $\Deri'_1$
+by applying the $\vlor$ rule.
+\end{proof}
+
 \subsection{Rule permutation for the proof of Lemma~\ref{lem:cw-decomposition}}

### 2021-01-25 main.tex
Minor fixes

@@
   Figure~\ref{fig:example-decompose} shows an example of a decomposed derivation in $\FOKS$ of the
-  formula $(\exists x. \cneg{p}(x)) \vlor (\forall y.(p(y) \vlan
-  p(f(y))))$.
+  formula $(\exists x. \cneg{p}x) \vlor (\forall y.(py \vlan pfy))$.
 %\end{example}
@@
 \begin{thm}\label{thm:decompositionA}
-  For every derivation $\upsmash{\vlder{\FOKS}{\Deri}{A}{\ttt}}$ there is a formula~$A_1$ not containing any occurence of $\fff$, such that there is a derivation:
+  For every derivation $\upsmash{\vlder{\FOKS}{\Deri}{A}{\ttt}}$ there is a formula~$A_1$ not containing any occurrence of $\fff$, such that there is a derivation:
   \begin{equation*}
@@
   induced by~$\phi$.  Conversely,
-  whenever we have a derivation as in~\eqref{eq:decom} above, such that $\fff$ does not occur in~$A_1$, then
+  whenever we have a derivation as in~\eqref{eq:decom} above, such that $\fff$ does not occur in~$A'$, then
   there is a combinatorial proof $\phi\colon\gC\to\graphof A$ such
@@
   $$
-  \todo{}
   \vlderivation{
@@
   the $\exists$-rule introducing $x_i$ dependend on $y_j$ must occur
-  below in the derivation (otherwise $\Deri$ would not be recified).
+  below in the derivation (otherwise $\Deri$ would not be rectified).
   Now consider such an instance $\vlinf{\exists}{}{\Scons{\exists
@@
     \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
-      \vlhy{A}}}}$ be a derivation. Then there is a recified derivation
+      \vlhy{A}}}}$ be a derivation. Then there is a rectified derivation
   $\vlderivation{
@@
   variables---the propositional variable, as well as the first-order
-  variable of the same name---as everything is recified, there is no
+  variable of the same name---as everything is rectified, there is no
   ambiguity here. Any instance of a rule $\wD$, $\acD$, $\me$, or
@@
   \end{equation}
-  Then we can transform $\Deri_1$ into a recified form
+  Then we can transform $\Deri_1$ into a rectified form
   $\rectif\Deri_1$, proving $\rectif A'$. By

### 2021-01-25 main.tex
done up to VII

--- 2021-01-25 main.tex
@@
 quantifier- and atom-occurrences in the derivation corresponds exactly
-to the vertex-mapping induced by $\phi$.
+to the vertex-mapping induced by $\phi$. To give an example, consider
+the derivation in Figure~\ref{fig:example-decompose} which corresponds
+to the right-most combinatorial proof in Figures~\ref{fig:cps}
+and~\ref{fig:cps-condensed}.
 
@@
 \begin{proof}
-  We only show the cases for $\wfaD$ and $\cfaD$:
-  $$
-  \todo{}
+  We only show the cases for $\wfaD$ and $\cfaD$ (for the others see~\cite{brunnler:phd}):
+  \vadjust{\vskip-2ex}
+  \begin{equation}
+    \label{eq:wfa-cfa}
+  \qquad
   \vlderivation{
     \vlin{\cD}{}{\forall x.A}{
-      \vlin{\fequ}{(x \notin fv(A))}{\forall x.(A \vlor A)}{
+      \vlin{\fequ}{}{\forall x.(A \vlor A)}{
         \vlin{\wrD}{}{A \vlor (\forall x.A)}{
           \vlhy{A}}}}}
-  $$.
-  $$
+  \qquad
+  \quad
   \vlderivation{
     \vlin{\cD}{}{\forall x.A}{
-      \vlin{\equiv}{(x \notin fv(\forall x.A))}{(\forall x.A) \vlor (\forall x.A)}{
+      \vlin{\equiv}{}{(\forall x.A) \vlor (\forall x.A)}{
         \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor A)}{
           \vlhy{\forall x.\forall x.A}}}}}
-  $$
-  The other cases have been shown before (e.g.~\cite{brunnler:phd}).
+  \end{equation}
+  where in the first derivation, $x$ is not free in $A$, and in the second one not free in $\forall x.A$.
+%  The other cases have been shown before (e.g.~\cite{brunnler:phd}).
 %%   We have the following derivations:
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:cw-atomic}
   Let $A$ and $B$ be formulas. Then
@@
 \begin{proof}
-  First, we can replace every instance of the $\fff$-rule by
+  First, we can replace every instance of the $\fff$-rule in $\Deri$ by
   $\weakr$. Then the instances of $\weakr$ and $\conr$ are replaced by
@@
 \begin{proof}
-  First, observe that the $\exists$ rule can be permuted downwards over all the
-other rules since $A\ssubst{x}{t}$ has the same structure as $A$ and none of the
-other rules has a premise of the form $\Scons{\exists x.A}$. It suffices now to
-prove that for all $r_1 \in \set{\forall, \aiD, \tttD}$, for all $r_2 \in
-\set{\sw, \mix, \fequ}$, we can permute $r_1$ upwards over $r_2$.
-  We show some cases here, and leave the others to the reader.
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\aiD}{}{\Scons{(A \vlan (a \vlor \cneg a)) \vlor C}}{
-      \vlin{\sw}{}{\Scons{(A \vlan \ttt) \vlor C}}{
-        \vlhy{\Scons{A \vlan (\ttt \vlor C)}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\sw}{}{\Scons{(A \vlan (a \vlor \cneg a)) \vlor C}}{
-      \vlin{\aiD}{}{\Scons{A \vlan ((a \vlor \cneg a) \vlor C)}}{
-        \vlhy{\Scons{A \vlan (\ttt \vlor C)}}}}}
-  \end{equation*}
-  \begin{equation*}
-    \vlderivation{
-      \vlin{\tttD}{}{\Scons{(A \vlor (B \vlan \ttt))}}{
-        \vlin{\mix}{}{\Scons{A \vlor B}}{
-          \vlhy{\Scons{A \vlan B}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\mix}{}{\Scons{(A \vlor (B \vlan \ttt)}}{
-      \vlin{\tttD}{}{\Scons{A \vlan (B \vlan \ttt)}}{
-        \vlhy{\Scons{A \vlan B}}}}}
-  \end{equation*}
-
-  \tocheck{}
+  First, observe that the $\exists$ rule can be permuted downwards
+  over all the other rules since $A\ssubst{x}{t}$ has the same
+  structure as $A$ and none of the other rules has a premise of the
+  form $\Scons{\exists x.A}$. It suffices now to prove that all rules
+  in $\set{\forall, \aiD, \tttD}$ can be permuted over the rules in
+  $\set{\sw, \mix, \fequ}$, which is straightforward
+  (see~\cite{dissvonlutz} for details).
 \end{proof}
+%% we can permute $r_1$ upwards over $r_2$.
+%%   We show some cases here, and leave the others to the reader.
+%%   \begin{equation*}
+%%   \vlderivation{
+%%     \vlin{\aiD}{}{\Scons{(A \vlan (a \vlor \cneg a)) \vlor C}}{
+%%       \vlin{\sw}{}{\Scons{(A \vlan \ttt) \vlor C}}{
+%%         \vlhy{\Scons{A \vlan (\ttt \vlor C)}}}}}
+%%   \leadsto
+%%   \vlderivation{
+%%     \vlin{\sw}{}{\Scons{(A \vlan (a \vlor \cneg a)) \vlor C}}{
+%%       \vlin{\aiD}{}{\Scons{A \vlan ((a \vlor \cneg a) \vlor C)}}{
+%%         \vlhy{\Scons{A \vlan (\ttt \vlor C)}}}}}
+%%   \end{equation*}
+%%   \begin{equation*}
+%%     \vlderivation{
+%%       \vlin{\tttD}{}{\Scons{(A \vlor (B \vlan \ttt))}}{
+%%         \vlin{\mix}{}{\Scons{A \vlor B}}{
+%%           \vlhy{\Scons{A \vlan B}}}}}
+%%   \leadsto
+%%   \vlderivation{
+%%     \vlin{\mix}{}{\Scons{(A \vlor (B \vlan \ttt)}}{
+%%       \vlin{\tttD}{}{\Scons{A \vlan (B \vlan \ttt)}}{
+%%         \vlhy{\Scons{A \vlan B}}}}}
+%%   \end{equation*}
+
+%%   \tocheck{}
+%% \end{proof}
 
@@
   $\vlderivation{
-      \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{}{B}{
+      \vlde{\set{\wrD,\wfaD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{}{B}{
         \vlhy{A}}}$
@@
     \vlderivation{
-      \vlde{\set{\wrD,\fequ}}{}{B}{
+      \vlde{\set{\wrD,\wfaD,\fequ}}{}{B}{
         \vlde{\set{\acD,\cfaD}}{}{B'}{
@@
 \begin{proof}
-
-  \todo{permutation with $\fequ$}
-
+  We first permute all instances of $\wD$ and $\wfaD$ to the bottom of
+  the derivation and then permute in a second step the rules $\cD$ and
+  $\cfaD$ below $\set{\me,\mfaD,\mexD}$. This involves a tedious but
+  straightforward case analysis. However, unlike most other rule
+  permutations in this paper this has not been done before in the deep
+  inference literature. For this reason, we give the full case
+  analysis in Appendix~\ref{app:cw-decomposition}. Note that this
+  Lemma is the reason for the presence of the rules $\wfaD$ and
+  $\cfaD$, as without them the permutation cases in~\eqref{eq:wfa-cfa}
+  could not be resolved.
 \end{proof}
@@
   Lemma~\ref{lem:MLS1-decomposition} to the upper half and
-  Lemma~\ref{lem:cw-decomposition} to the lower half.
+  Lemmas~\ref{lem:cw-atomic} and~\ref{lem:cw-decomposition} to the lower half.
 \end{proof}
@@
 \subsection{Rule permutation for the proof of Lemma~\ref{lem:cw-decomposition}}
+\label{app:cw-decomposition}
 

### 2021-01-25 main.tex
up to VIII.B

@@
 
-Let $\Pi$ be a $\FOMLL$ proof of a rectified sequent $\sqn\Gamma$. We now show
+Let $\Pi$ be a $\FOMLL$ proof of a rectified sequent $\sqn\Gamma$ not containing $\fff$. We now show
 how $\Pi$ is translated into a linked fograph
@@
 \begin{enumerate}
-  %\setlength\itemsep{.5ex}
-\item $\Pi$ is $\vlinf{\axr}{}{\sqn{a,\cneg a}}{}$ : Then the only
+  \addtolength\itemsep{.7ex}
+\item $\Pi$ is $\upsmash{\vlinf{\axr}{}{\sqn{a,\cneg a}}{}}$ : Then the only
   link is $\set{a, \dual{a}}$, and $\dsubstof\Pi$ is empty.
-\item $\Pi$ is $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ : Then
+\item $\Pi$ is $\smash{\vlinf{\ttt}{}{\sqn{\ttt}}{}}$ : Then
   $\linkingof\Pi$ and $\dsubstof\Pi$ are both empty.
@@
   By induction hypothesis, we have proofs $\Pi'$ and $\Pi''$ of $\Gamma'$ and $\Gamma''$, respectively. We have
-  $\graphof{\Gamma}=\graphof{\Gamma'}+\graphof{\Gamma''}$ and let
-  $$\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''}
-  \qquand
-  \dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$$
+  $\graphof{\Gamma}=\graphof{\Gamma'}+\graphof{\Gamma''}$ and we can let
+  $\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''}$ and
+  $\dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$.
 \item The last rule in $\Pi$ is $\vlinf{\vlor}{}{\sqn{\Gamma_1,A\vlor
@@
   B)$}+\graphof{\Gamma_2}$ and we let
-  $$\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''} \qquand
-  \dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$$
+  $\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''}$ and
+  $\dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$.
 \item The last rule in $\Pi$ is
@@
   \label{thm:MLL1->fonet}
-  If $\Pi$ is a $\FOMLL$ proof of a rectified sequent $\sqn\Gamma$,
-  then $\fographof\Pi$ is a fonet and $\dsubstof\Pi$ is a dualizer for it.
+  If $\Pi$ is a $\FOMLL$ proof of a rectified $\fff$-free sequent $\sqn\Gamma$,
+  then $\fographof\Pi$ is a fonet and $\dsubstof\Pi$ a dualizer for it.
 \end{thm}
@@
 
-A derivation $\Deri$ in $\FOMLS$ is \bfit{rectified} if every line in $\Deri$ is
-rectified.
-
-\begin{lemma}
-  Let  $\Deri$ be a $\FOMLS$ proof of a formula $A$. Then $\Deri$ is rectified iff $A$ is rectified.
-\end{lemma}
-
-\begin{proof}
-   The only rules involving bound
-   variables are $\forall$ and $\exists$ which both remove a binder (and
-   all occurrences of the variable it binds).
-\end{proof}
-
-Hence, for a non-rectified  $\FOMLS$ derivation $\Deri$ in $\FOMLS$ we can
+First observe that in a derivation in $\FOMLS$
+where the conclusion is rectified, every line is also rectified, as
+the only rules involving bound variables are $\forall$ and $\exists$
+which both remove a binder.
+Therefore, we can call such a derivation \bfit{rectified}, and
+%% if every line in $\Deri$ is
+%% rectified.
+
+%% \begin{lemma}
+%%   Let  $\Deri$ be a $\FOMLS$ proof of a formula $A$. Then $\Deri$ is rectified iff $A$ is rectified.
+%% \end{lemma}
+
+%% \begin{proof}
+%%    The only rules involving bound
+%%    variables are $\forall$ and $\exists$ which both remove a binder (and
+%%    all occurrences of the variable it binds).
+%% \end{proof}
+
+%% Hence,
+for a non-rectified  $\FOMLS$ derivation $\Deri$ we can
 define its \bfit{rectification} $\rectif\Deri$ inductively, by rectifying each
@@
 
-\todo{example here}
+%\todo{example here}
 
 \begin{thm}\label{thm:MLS1->fonet}
-  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a rectified derivation. Then
+  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a rectified derivation where $A$ is $\fff$-free. Then
   $\fographof\Deri$ is a fonet and $\dsubstof{\Deri}$ a dualizer for it.
@@
 \end{enumerate}
-The $\linkingof{\frameof C}$ consists of the pairs induced by
+Then $\linkingof{\frameof C}$ consists of the pairs induced by
 $\linkingof\gC$ and the new pairs $\set{q_{i,j},\dual q_{i,j}}$ introduced in
@@
 \begin{lemma}\label{lem:frame}
-  A linked fograph $\gC$ has an induced bimatching iff its frame $\frameof\gC$ has an induced bimatching.
+  If a linked fograph $\gC$ has an induced bimatching then so does its frame $\frameof\gC$. % has an induced bimatching.
 \end{lemma}
@@
 \begin{proof}
-  This immediately follows from the construction of the frame.\lutz{is it really an ``iff''?
-It is easy to construct from a bimatching in $\gC$ a bimatching in the frame.
-(and I think we only need that direction).
-But what about the other direction?}
+  Immediately from the construction of the frame.
+  %%\lutz{is it really an ``iff''? It is easy to construct from a bimatching in $\gC$ a bimatching in the frame. (and I think we only need that direction). But what about the other direction?}
 \end{proof}
@@
   have $\fequ$ incorporating associativity and commutativity of
-  $\vlan$ and $\vlor$.}
-  \begin{equation*}\small
+  $\vlan$ and $\vlor$.} \vadjust{\vskip-2ex}
+  \begin{equation*}
+    \scalebox{.95}{$
     \vlinf{\forall}{}{\Scons{\forall y_j.\ttt}}{\Scons{\ttt}}
@@
           \vlhy{\ttt}}}}
+    $}
   \end{equation*}
@@
   constructed, and for $\DDeri_2$ see,
-  e.g. \cite{ESSLI19-notes,gug:str:01,brunnler:tiu:01}\lutz{check if
-    it is really there. otherwise \cite{dissvonlutz}} Then, every
+  e.g. \cite{ATS:esslli2019,gug:str:01,brunnler:tiu:01,dissvonlutz}. Then, every
   occurrence of $\forall y_j.F$ is replaced by
@@
   on which that $x_i$ depends, and $B'$ is $B$ in which all predicates
-  are replaced by nullary one (step~3 in the frame construction). The
+  are replaced by a nullary one (step~3 in the frame construction). The
   derivation $\DDeri_3$ can be constructed in the same way as
-  $\DDeri_2$ above.
+  $\DDeri_2$.
 
@@
   \hbox{$\fographof{\frameof\Deri}=\frameof{\fographof\Deri}$}. It has
-  been shown by Retor\'e~\cite{some tech-report to be found} and
+  been shown by Retor\'e~\cite{retore:pomset:RR} and
   rediscovered by Stra{\ss}burger~\cite{dissvonlutz} that
@@
   definition of $\dsubstof\Deri$ that it is a dualizer for
-  $\fographof{\Deri}$. Hence $\fographof{\Deri}$ is a fonet.
+  $\fographof{\Deri}$.
+  %Hence $\fographof{\Deri}$ is a fonet.
   %% We have

### 2021-01-25 main.tex
done with VIII

@@
 \emph{sequentialization}. The basic idea behind our sequentialization
-is to construct a propositional linked cograph, called the \bfit{frame}~\cite{hughes:unifn}
-of $\gC$, in which the dependencies between the binders in $\gC$ are
-encoded as links. Then we can apply the \emph{splitting tensor
-theorem} to the frame, and then reconstruct the sequent proof $\Pi$.
-\lutz{if the proof of thm \ref{thm:MLS1->fonet} is verified, we can delete the frame-def here}
-
-More formally, let $\Gamma$ be a sequent with $\graphof\Gamma=\gC$, to which we
-exhaustively apply the following
-subformula rewriting steps, to obtain a sequent $\frameof\Gamma$:
-\begin{enumerate}
-\item {\bf Encode dependencies as fresh links.} For each dependency
-  $\pair{\single x,\single y}$ in $\gC$, with corresponding
-  subformulas $\exists x A$ and $\forall y B$ in $\Gamma$, we pick a
-  fresh (nullary) predicate symbol $q$, and then replace $\exists
-  x. A$ by $q \cand \exists x. A$, and replace $\forall y. B$ by
-  $\dual q \cor \forall y. B$.
-\item {\bf Erase quantifiers.} After step 1, remove all the
-  quantifiers, i.e., replace $\exists x.A$ by $A$ and replace $\forall
-  y.B$ by $B$ everywhere.
-\item {\bf Simplify atoms.} After step 2, replace every predicate
-  $p(t_1 \cdots t_n)$ (resp. $\dual p(t_1 \cdots t_n)$) with a nullary
-  predicate symbol $p$ (resp.~$\dual p$)
-\end{enumerate}
-The $\linkingof{\frameof\Gamma}$ consists of the pairs induced by
-$\linkingof\gC$ and the new pairs $\set{q,\dual q}$ introduced in
-step~1 above. We call $\frameof\Gamma$ the \bfit{frame} of $\Gamma$ and we define the \bfit{frame} of $\gC$, denoted
-$\frameof\gC$, as
-$\tuple{\graphof{\frameof\Gamma},\linkingof{\frameof\Gamma}}$, and we immediately have the following:
-
-\begin{lemma}\label{lem:frame}
-  A linked fograph $\gC$ induces a bimatching iff its frame $\frameof\gC$ has an induced bimatching.
-\end{lemma}
+is to use the frame of $\gC$, to which  we can apply the \emph{splitting tensor
+theorem}, and then reconstruct the sequent proof $\Pi$.
 
@@
 
-The purpose of introducing the frame is the following theorem.
-
 \begin{thm}
   \label{thm:splitting}
-  Let $\Gamma$ be a propositional sequent containing only atoms
+  Let $\Gamma$ be a $\fff$-free propositional sequent containing only atoms
   and $\vlan$-formulas, and $\linkingof\Gamma$ be a
@@
 
-This is the well-know splitting-tensor-theorem
+This is the well-known splitting-tensor-theorem
 \cite{girard:87,danos:regnier:89}, adapted for the presence of
 $\mix$. In the setting of linked cographs, it has first been proved by
-Retor\'e~\cite{retore:03,retore:99}. We use it now for our sequentialization:
+Retor\'e~\cite{retore:03,retore:99} and then rediscovered by Hughes~\cite{hughes:pws}.
+We use it now for our sequentialization:
 
@@
   then we get a contradiction as in that case there must be a $\vlor$- or $\forall$-formula in $\Gamma$.
-  \lutz{can anyone give a good argument here?}
+%  \lutz{can anyone give a good argument here?}
 \end{proof}
@@
   We apply Theorem~\ref{thm:fonet->MLL1} to obtain a sequent
-  proof~$\Pi$ of $\sqn C$ with
+  proof~$\Pi$ of \hbox{$\sqn C$} with
   $\fographof\Pi=\tuple{\gC,\linkingof\gC}$. Then we apply

### 2021-01-25 main.tex
up to IX.A

@@
 In this section we establish the relation between skew bifibrations and derivations  in
-$\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$. However, 
+$\set{\wrD,\wfaD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$. However, 
 if a derivation $\Deri$ contains instances of the rules $\cfaD$, $\mfaD$, and
@@
 this reason we define here rectified versions $\rectif\cfaD$,  $\rectif\mfaD$ and
-$\rectif\mexD$, shown below:
-\begin{equation*}
+$\rectif\mexD$, shown below:%\vadjust{\vskip-1ex}
+\begin{equation*}
+  \scalebox{.9}{$
   \vlinf{\rectif\cfaD}{}{\Scons{\forall x.Ax}}{\Scons{\forall y.\forall x.Ax}}
@@
   \end{array}
+  $}
 \end{equation*}
@@
 For a derivation $\Deri$ in
-$\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$, we can now construct the
+$\set{\wrD,\wfaD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$, we can now construct the
 \bfit{rectification} $\rectif\Deri$ by rectifying each line of $\Deri$, yielding
 a derivation in
-$\set{\wrD,\acD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$.
+$\set{\wrD,\wfaD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$.
 
@@
 $\rr\in\set{\me,\fequ}$ and as the canonical injection for
-$\rr=\wrD$. For $\rr=\acD$ it maps the vertices
+$\rr\in\set{\wrD,\wfaD}$. For $\rr=\acD$ it maps the vertices
 corresponding to the two atoms in the premise to vertex of the
@@
 corresponding to the quantifiers in the premise to the one in the
-conclusion (as acts as the identity on all other vertices).
+conclusion (and acts as the identity on all other vertices).
 For a
 derivation $\Deri$ in
-$\set{\wrD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can then define
+$\set{\wrD,\wfaD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can then define
 the \bfit{induced map} $\mapof\Deri$ as the composition of the induced
 maps of the rule instances in $\Deri$.
-\juihsuan{maybe mention at least that the induced
-maps define graph homomorphisms. Do we need to talk about the contexts
-$\Sconhole$ here (induced maps act clearly as the identity on contexts but we need them for the composition)?}
-\lutz{For the context, I aleady say it is the identity. For the homom, it comes later}
+%% \juihsuan{maybe mention at least that the induced
+%% maps define graph homomorphisms. Do we need to talk about the contexts
+%% $\Sconhole$ here (induced maps act clearly as the identity on contexts but we need them for the composition)?}
+%% \lutz{For the context, I aleady say it is the identity. For the homom, it comes later}
 
@@
   Let $\downsmash{\vlderivation{
-    \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
-      \vlhy{A}}}}$ be a derivation. Then there is a rectified derivation
+    \vlde{\set{\wrD,\wfaD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
+      \vlhy{A}}}}$ be given.
+  %%a derivation.
+  Then there is a rectified derivation
   $\vlderivation{
-    \vlde{\set{\wrD,\rectif\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{\rectif
+    \vlde{\set{\wrD,\wfaD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{\rectif
       B}{ \vlhy{\rectif A}}}$, such that the induced maps
@@
 
-\todo{example}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We say that a derivation $\Deri$ is \bfit{sane} if for every line $Q$
-in $\Deri$ we have that $\graphof D$ is a fograph (i.e., all binders
-are legal). Clearly, every rectified derivation is sane, but not vice
-versa, as we might have multiple occurrences of bound variables in $Q$,
-such that $\graphof Q$ is still a fograph.
+%% We say that a derivation $\Deri$ is \bfit{sane} if for every line $Q$
+%% in $\Deri$ we have that $\graphof D$ is a fograph (i.e., all binders
+%% are legal). Clearly, every rectified derivation is sane, but not vice
+%% versa, as we might have multiple occurrences of bound variables in $Q$,
+%% such that $\graphof Q$ is still a fograph.
 
@@
     \vlde{\set{\wrD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
-      \vlhy{A}}}$ be a sane derivation. Then the induced map
+      \vlhy{A}}}$ be a rectified derivation. Then the induced map
   $\mapof\Deri\colon\graphof{A}\to\graphof{B}$ is a skew bifibration.
@@
   First, observe that for every inference rule
-  $\rr\in\set{\wrD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ 
-  the induced map $\mapof{\rr}\colon\vgraphof Q\to\vgraphof P$ defines a existential preserving graph homomorphism $\graphof Q\to\graphof P$ and  a fibration on the corresponding binding graphs.
-\juihsuan{we may need to have
-some explication here.}\lutz{no} Therefore, their
-  composition $\mapof\Deri$ has the same properties fibration.
+  $\rr\in\set{\wrD,\wfaD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$
+  the induced map $\mapof{\rr}\colon\vgraphof Q\to\vgraphof P$ defines
+  a existential preserving graph homomorphism $\graphof Q\to\graphof
+  P$ and a fibration on the corresponding binding graphs.  Therefore,
+  their composition $\mapof\Deri$ has the same properties fibration.
 
@@
   translating every line into its propositional encoding.
-  \juihsuan{maybe mention that an instance of one of the other rules can be translated
-into an instance of the same rule. It's trivial but may be worth mentioning.}\lutz{done below}
   The instances
-  of the rules $\rectif\mfaD$ and $\rectif\mexD$ are replaced in two
-  steps by:
-  \begin{equation*}
+  of the rules $\rectif\mfaD$ and $\rectif\mexD$ are replaced by:
+  \begin{equation*}
+    \scalebox{.85}{$
     \vlderivation{
@@
           \vlhy{\Scons{(y\vlor\PE{(Ay)})\vlor (z\vlor\PE{(Bz)})}}}}}
-  \end{equation*}
-  and
-  \begin{equation*}
+    \qquad\!
     \vlderivation{
@@
           \vlhy{\Scons{(y\vlan\PE{(Ay)})\vlor (z\vlan\PE{(Bz)})}}}}}
+    $}
   \end{equation*}
@@
   been shown in~\cite{str:07:RTA} that $\mapof{\PE\Deri}$ is a skew
-  fibration (see
-  also~\cite{hughes:invar,str:ral:tableaux19,str:RR-9048}). Hence,
+  fibration.
+  %(see
+  %also~\cite{hughes:invar,str:ral:tableaux19}).
+  Hence,
   $\mapof\Deri$ is a skew fibration.
@@
       \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
-        \vlhy{A\substof\phi}}}
+        \vlhy{A\rsubstof\phi}}}
   \end{equation*}
   such that $\mapof{\rectif\Deri}=\phi$ and $\rectif{\Deri}$ is a
-  rectification of $\Deri$, and $\substof\phi$ is the substitution
+  rectification of $\Deri$, and $\rsubstof\phi$ is the substitution
   induced by $\phi$.
@@
   surjection and $\phi'\colon \gB_1\to\gB$ being an injection that
-  reflects edges. \juihsuan{what do you mean by "reflect edges"?}\lutz{edge downstairs implies edge upstairs} Both, $\phi'$ and $\phi''$ remain skew
+  reflects edges.  Both, $\phi'$ and $\phi''$ remain skew
   bifibrations. Let us first look at $\phi'$.  Let $\PEp B_1$ be the
@@
     B_1}=\gB_1$.  By \cite[Proposition~7.6.1]{str:07:RTA}, we have a
-  derivation $\vlder{\set{\wrD,\fequ}}{\PE\Deri_1}{\PE B}{\PEp B_1}$.
+  derivation $\vlder{\set{\wrD,\PE\fequ}}{\PE\Deri_1}{\PE B}{\PEp B_1}$.
   A subformula of $\PE B$ is called \emph{weak} if it has been
@@
 \end{itemize}
+
+\end{document}
 

### 2021-01-25 main.tex
Minor changes

--- 2021-01-25 main.tex
@@
 Note that $\graphof A$ is not necessarily a fograph if $A$ is not
-rectified. If $A = (\forall x. p(x)) \vlor (\forall x. q(x))$, then
-$\graphof A = \single x \ \single p(x) \ \single x \ \single q(x)$,
+rectified. If $A = (\forall x. px) \vlor (\forall x. qx)$, then
+$\graphof A = \single x \ \single px \ \single x \ \single qx$,
 the scope of each $x$-binder contains all the vertices, in particular,
@@
 formulas which are translated to fographs by $\graphof\cdot$. For
-example, in the graph of $(\exists x. p(x)) \vlor (\exists x. q(x))$,
+example, in the graph of $(\exists x. px) \vlor (\exists x. qx)$,
 both $x$-binders are legal, as they are not in each other's
@@
     B}}{\sqn{\Gamma_1,A,B}}$ : By induction hypothesis, there is
-  proofs $\Pi'$ of $\Gamma'={\Gamma_1,A,B}$. We have
+  a proof $\Pi'$ of $\Gamma'={\Gamma_1,A,B}$. We have
   $\graphof{\Gamma}=\graphof{\Gamma'}$ and let
@@
   {\sqn{\Gamma_1,A\ssubst{x}{t}}}$ : By induction hypothesis, there is
-  a $\Pi'$ of $\Gamma'={\Gamma_1,A\ssubst{x}{t}}$.  For each atom in
+  a proof $\Pi'$ of $\Gamma'={\Gamma_1,A\ssubst{x}{t}}$.  For each atom in
   $\Gamma'=\Gamma_1, A \ssubst{x}{t}$, there is a corresponding atom
@@
 Note that in the case of $\vlor$, we use the deep rule $\wrD$ which can be
-permuted down over all the rules. By using these rewriting rules, we can eventually get
+permuted under all the rules. By using these rewriting rules, we can eventually get
 a derivation with all the instances of $\weakr$ and $\wrD$ at the bottom. Now observe
@@
 
-Knowing that $\cD$ can be permuted down over all the rules of $\FOMLL$, we
+Knowing that $\cD$ can be permuted under all the rules of $\FOMLL$, we
 eventually obtain a derivation:
@@
   \vlde{\set{\weakr, \wrD,\cD,\fequ}}{\Deri'_2}{\sqns{\Gamma}}{
-    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma_0}}{
+    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma'}}{
       \vlhy{\quad}}{
@@
   \vlde{\set{\wrD,\cD,\fequ}}{\Deri_2}{\sqns{\form{\Gamma}}}{
-    \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\Gamma'}}{
+    \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\form{\Gamma'}}}{
       \vlhy{\quad}}{
@@
 \end{equation*}
-where $\Gamma' = \form{\Gamma_0}$ and $\Deri_1$ can be obtained from $\Deri'_1$
+where $\Deri_1$ can be obtained from $\Deri'_1$
 by applying the $\vlor$ rule.

### 2021-01-25 main.tex
tweak

@@
 
-Fix pairwise disjoint countable sets $\VAR=\set{x,y,z,\ldots}$ of variables,
+Fix pairwise disjoint countably infinite sets $\VAR=\set{x,y,z,\ldots}$ of variables,
 $\FUN=\set{f,g,\ldots}$ of function symbols, and 

### 2021-01-25 main.tex
in a mess

--- 2021-01-25 main.tex
@@
 Note that $\graphof A$ is not necessarily a fograph if $A$ is not
-rectified. If $A = (\forall x. px) \vlor (\forall x. qx)$, then
-$\graphof A = \single x \ \single px \ \single x \ \single qx$,
+rectified. If $A = (\forall x. p(x)) \vlor (\forall x. q(x))$, then
+$\graphof A = \single x \ \single p(x) \ \single x \ \single q(x)$,
 the scope of each $x$-binder contains all the vertices, in particular,
@@
 formulas which are translated to fographs by $\graphof\cdot$. For
-example, in the graph of $(\exists x. px) \vlor (\exists x. qx)$,
+example, in the graph of $(\exists x. p(x)) \vlor (\exists x. q(x))$,
 both $x$-binders are legal, as they are not in each other's
@@
     B}}{\sqn{\Gamma_1,A,B}}$ : By induction hypothesis, there is
-  a proof $\Pi'$ of $\Gamma'={\Gamma_1,A,B}$. We have
+  proofs $\Pi'$ of $\Gamma'={\Gamma_1,A,B}$. We have
   $\graphof{\Gamma}=\graphof{\Gamma'}$ and let
@@
   {\sqn{\Gamma_1,A\ssubst{x}{t}}}$ : By induction hypothesis, there is
-  a proof $\Pi'$ of $\Gamma'={\Gamma_1,A\ssubst{x}{t}}$.  For each atom in
+  a $\Pi'$ of $\Gamma'={\Gamma_1,A\ssubst{x}{t}}$.  For each atom in
   $\Gamma'=\Gamma_1, A \ssubst{x}{t}$, there is a corresponding atom
@@
     \vlderivation{
-      \vlde{\set{\wrD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{B}{
+      \vlde{\set{\wrD,\wfaD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{B}{
         \vlhy{A}}}
@@
     \vlderivation{
-      \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
+      \vlde{\set{\wrD,\wfaD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
         \vlhy{A\rsubstof\phi}}}
@@
 
-\begin{proof}[Proof of Lemma~\ref{lem:skew->cw}]
-  By Lemma~\ref{lem:PE} we have $\gA=\graphof{\PE A}$ and
-  $\gB=\graphof{\PE B}$.  Let $\vB'\subseteq\vB$ be the image of
-  $\phi$, and let $\gB_1$ be the subgraph of $\gB$ induced by
-  $\vB'$. Hence, we have two maps $\phi''\colon\gA\to\gB_1$ being a
-  surjection and $\phi'\colon \gB_1\to\gB$ being an injection that
-  reflects edges.  Both, $\phi'$ and $\phi''$ remain skew
-  bifibrations. Let us first look at $\phi'$.  Let $\PEp B_1$ be the
-  propositional formula obtained from $\PE B$ by removing all atoms
-  that are not represented by vertices in $\vB'$. Then $\graphof{\PEp
-    B_1}=\gB_1$.  By \cite[Proposition~7.6.1]{str:07:RTA}, we have a
-  derivation $\vlder{\set{\wrD,\PE\fequ}}{\PE\Deri_1}{\PE B}{\PEp B_1}$.
+We say a fograph homomorphism $\phi\colon\gG\to\gH$ is \bfit{full} if
+for all $v,w\in\vG$, we have that $\phi(v)\phi(w)\in\eH$ implies
+$vw\in\eG$.
+
+\begin{lemma}\label{lem:fullinj->w}
+  Let $\phi\colon\gG\to\gH$ be full and injective skew bifibration
+  such that $\rsubstof\phi$ is the identity substitution, and let $G$
+  and $H$ be formulas with $\graphof G=\gG$ and $\graphof H=\gH$. Then
+  There is a derivation $\vlder{\set{\wrD,\wfaD,\fequ}}{}{H}{G}$.
+\end{lemma}
+
+\begin{proof}
+   By \cite[Proposition~7.6.1]{str:07:RTA}, we have a
+  derivation $\vlder{\set{\wrD,\PE\fequ}}{\DDeri}{\PE H}{\PE G}$.
   A subformula of $\PE B$ is called \emph{weak} if it has been
@@
   $\vlder{\set{\wrD,\fequ}}{\Deri_1}{B}{B_1}$ with $\PE B_1=\PEp B_1$.
+\end{proof}
+
+\begin{proof}[Proof of Lemma~\ref{lem:skew->cw}]
+  By Lemma~\ref{lem:PE} we have $\gA=\graphof{\PE A}$ and
+  $\gB=\graphof{\PE B}$.  Let $\vB'\subseteq\vB$ be the image of
+  $\phi$, and let $\gB_1$ be the subgraph of $\gB$ induced by
+  $\vB'$. Hence, we have two maps $\phi''\colon\gA\to\gB_1$ being a
+  surjection and $\phi'\colon \gB_1\to\gB$ being an injection that
+  reflects edges.  Both, $\phi'$ and $\phi''$ remain skew
+  bifibrations. Let us first look at $\phi'$.  Let $\PEp B_1$ be the
+  propositional formula obtained from $\PE B$ by removing all atoms
+  that are not represented by vertices in $\vB'$. Then $\graphof{\PEp
+    B_1}=\gB_1$.
 
@@
 Note that in the case of $\vlor$, we use the deep rule $\wrD$ which can be
-permuted under all the rules. By using these rewriting rules, we can eventually get
+permuted down over all the rules. By using these rewriting rules, we can eventually get
 a derivation with all the instances of $\weakr$ and $\wrD$ at the bottom. Now observe
@@
 
-Knowing that $\cD$ can be permuted under all the rules of $\FOMLL$, we
+Knowing that $\cD$ can be permuted down over all the rules of $\FOMLL$, we
 eventually obtain a derivation:
@@
   \vlde{\set{\weakr, \wrD,\cD,\fequ}}{\Deri'_2}{\sqns{\Gamma}}{
-    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma'}}{
+    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma_0}}{
       \vlhy{\quad}}{
@@
   \vlde{\set{\wrD,\cD,\fequ}}{\Deri_2}{\sqns{\form{\Gamma}}}{
-    \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\form{\Gamma'}}}{
+    \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\Gamma'}}{
       \vlhy{\quad}}{
@@
 \end{equation*}
-where $\Deri_1$ can be obtained from $\Deri'_1$
+where $\Gamma' = \form{\Gamma_0}$ and $\Deri_1$ can be obtained from $\Deri'_1$
 by applying the $\vlor$ rule.

### 2021-01-25 main.tex
rule permutation

--- 2021-01-25 main.tex
@@
 
-Fix pairwise disjoint countably infinite sets $\VAR=\set{x,y,z,\ldots}$ of variables,
+Fix pairwise disjoint countable sets $\VAR=\set{x,y,z,\ldots}$ of variables,
 $\FUN=\set{f,g,\ldots}$ of function symbols, and 
@@
 \label{app:cw-decomposition}
-
-We first study the interactions between two rules (only non-trivial cases are
-presented here):
+We construct a rewriting system based on rule permutation on derivations in $\set{\wrD, \wfaD, \acD,
+\cfaD, \me, \mfaD, \mexD, \fequ}$ that allows us to reach a derivation of the
+form 
+\begin{equation*}
+    \vlderivation{
+      \vlde{\set{\wrD,\wfaD,\fequ}}{}{B}{
+        \vlde{\set{\acD,\cfaD}}{}{B'}{
+          \vlde{\set{\me,\mfaD,\mexD,\fequ}}{}{A'}{
+            \vlhy{A}}}}}
+\end{equation*}
+from any derivation. Intuitively, we want to move all the instances of $\rr \in
+\set{\wrD, \wfaD}$ downwards and all the instances of $\rr' \in \set{\me,
+\mfaD, \mexD}$ upwards.
+
+We first study the interactions between two rules. Certain cases are unsolved at
+this stage, and they are considered later when we study the interactions between
+two non-$\fequ$ rule instances seperated by $\fequ$. Only non-trivial cases are
+considered here:
 \begin{itemize}
@@
   \vlin{\cfaD}{}{\forall x.A}{
-    \vlin{\wfaD}{(x \notin fv(\forall x.A))}{\forall x.\forall x.A}{
+    \vlin{\wfaD}{}{\forall x.\forall x.A}{
       \vlhy{\forall x.A}}}}
@@
   \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\wfaD}{(x \notin fv(A))}{(\forall x.A) \vlor (\forall x.B)}{
+    \vlin{\wfaD}{}{(\forall x.A) \vlor (\forall x.B)}{
       \vlhy{A \vlor (\forall x.B)}}}}
@@
 \vlderivation{
-  \vlin{\fequ}{(x \notin fv(A))}{\forall x.(A \vlor B)}{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
     \vlhy{A \vlor (\forall x.B)}}} 
 \end{equation*}
+where in the last case, $x$ is not free in $A$.
 
@@
 \vlderivation{
-  \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
+  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
     \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
@@
   \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x. A) \vlor B}{
+    \vlin{\fequ}{}{(\forall x.\forall x. A) \vlor B}{
       \vlhy{\forall x.\forall x.(A \vlor B)}}}}
@@
 \vlderivation{
-  \vlin{\fequ}{(x \notin fv(B))}{\forall x.(A \vlor B)}{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
     \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
@@
   \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
+    \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
       \vlhy{(\forall x.\forall x.A) \vlor B}}}}
 \end{equation*}
+where in the last two cases, $x$ is not free in $B$.
 
@@
 \vlderivation{
-  \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
+  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
     \vlin{\wrD}{}{\forall x.(A \vlor B)}{
@@
 \vlderivation{
-  \vlin{\fequ}{(x \notin fv(B))}{\forall x.(A \vlor B)}{
+  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
+    \vlin{\wrD}{}{\forall x.(B \vlor A)}{
+      \vlhy{\forall x.B}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
     \vlin{\wrD}{}{(\forall x.A) \vlor B}{
@@
 
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+    \vlin{\wrD}{}{B \vlor (\forall x.A)}{
+      \vlhy{B}}}}
+\end{equation*}
+where in the last four cases, $x$ is not free in $B$.
 \item $\wfaD/\fequ$:
@@
 \vlderivation{
-  \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
-    \vlin{\wfaD}{(x \notin fv(A \vlor B))}{\forall x.(A \vlor B)}{
+  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
+    \vlin{\wfaD}{}{\forall x.(A \vlor B)}{
       \vlhy{A \vlor B}}}}
@@
 \vlderivation{
-  \vlin{\wfaD}{(x \notin fv(A))}{(\forall x.A) \vlor B}{
+  \vlin{\wfaD}{}{(\forall x.A) \vlor B}{
     \vlhy{A \vlor B}}}
@@
 \vlderivation{
-  \vlin{\fequ}{(x \notin fv(B))}{\forall x.(A \vlor B)}{
-    \vlin{\wfaD}{(x \notin fv(A))}{(\forall x.A) \vlor B}{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+    \vlin{\wfaD}{}{(\forall x.A) \vlor B}{
       \vlhy{A \vlor B}}}}
@@
 \vlderivation{
-  \vlin{\wfaD}{(x \notin fv(A \vlor B))}{\forall x.(A \vlor B)}{
+  \vlin{\wfaD}{}{\forall x.(A \vlor B)}{
     \vlhy{A \vlor B}}}
 \end{equation*}
+where in the last two cases, the constraint on $x$ on the left-hand side implies
+that of the right-hand side.
 
@@
 
-\item $\wrD/\fequ/\cfaD$: We only list non-trivial cases here:
+\item $\wrD/\fequ/\cfaD$:
   \begin{equation*}
@@
     \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-      \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x.A) \vlor B}{
+      \vlin{\fequ}{}{(\forall x.\forall x.A) \vlor B}{
         \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
@@
     \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-      \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x.A) \vlor B}{
+      \vlin{\fequ}{}{(\forall x.\forall x.A) \vlor B}{
         \vlin{\wrD}{}{\forall x.(B \vlor (\forall x.A))}{
@@
   \vlderivation{
-    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.A) \vlor B}{
+    \vlin{\fequ}{}{(\forall x.A) \vlor B}{
       \vlin{\wrD}{}{\forall x.(B \vlor A)}{
@@
     \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-      \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
+      \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
         \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
@@
     \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-      \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
+      \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
         \vlin{\wrD}{}{\forall x.(B \vlor (\forall x.A))}{
@@
   \end{equation*}
-
+  where in all four cases, $x$ is not free in $B$.
 \item $\wrD/\fequ/\acD$:
@@
     \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
-      \vlin{\fequ}{(x \notin fv(B \vlan D))}{\forall x.((A \vlan C) \vlor (B \vlan
+      \vlin{\fequ}{}{\forall x.((A \vlan C) \vlor (B \vlan
 D))}{
@@
         \vlin{\wrD}{}{\forall x.((B \vlor A) \vlan D)}{
-          \vlin{\faD}{(x \notin fv(B \vlan D))}{\forall x.(B \vlan D)}{
+          \vlin{\faD}{}{\forall x.(B \vlan D)}{
             \vlhy{B \vlan D}}}}}}
   \end{equation*}
+  where in the second case, $x$ is free in $B \vlan D$.
 
@@
         \vlhy{\forall x.B}}}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+      \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
+        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
+          \vlhy{\forall x.\forall x.A}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+      \vlin{\cfaD}{}{\forall x.A}{
+        \vlhy{\forall x.\forall x.A}}}}
   \end{equation*}

### 2021-01-25 main.tex
Minor fixes
in a mess

@@
 \newcommand{\quand}{\quad\mbox{and}\quad}
-
 \newcommand{\qquand}{\qquad\mbox{and}\qquad}
+
+\newcommand{\quor}{\quad\mbox{or}\quad}
+\newcommand{\qquor}{\qquad\mbox{or}\qquad}
 
@@
 \begin{proof}
-   By \cite[Proposition~7.6.1]{str:07:RTA}, we have a
-  derivation $\vlder{\set{\wrD,\PE\fequ}}{\DDeri}{\PE H}{\PE G}$.
-  A subformula of $\PE B$ is called \emph{weak} if it has been
-  introduced by a weakening. All subformulas of a weak formula are
-  also weak. Two weak subformulas $B'$ and $B''$ of $\PE B$ form a
-  \emph{weak pair} if $\PE B\fequ\Scons{B'\vlor B''}$ for some context
-  $\Sconhole$. We can assume without loss of generality that
-  whenever weak subformulas $B'$ and $B''$ form a weak pair, they have
-  been introduced by the same instance of $\wrD$ in
-  $\PE\Deri_1$.\footnote{If $\PE\Deri_1$ is not of that shape, it can
-  brought into this form by simple rule permutations, and then
-  collapsing several weakenings into a single one.}  Now we show that
-  $\PE\Deri_1$ can be lifted. For this, observe that whenever a
-  weakening in $\PE\Deri_1$ deletes an atom $x\in\VAR$, it must also
-  delete all atoms in the scope of the corresponding quantifier,
-  because $\phi'$ is a fibration on the binding graph. Hence, each line
-  in $\PE\Deri_1$ is the propositional encoding $\PE P$ of a
+   By \cite[Proposition~7.6.1]{str:07:RTA}, we have a derivation
+   $\vlder{\set{\wrD,\PE\fequ}}{\DDeri}{\PE H}{\PE G}$. In order to
+   lift $\DDeri$, we might need to reorganize the instancese of
+   $\wD$. If $H$ contains a subformula $\forall x.A$ which is not
+   present in $G$, the $\wD$-instances in $\DDeri$ could introduce the
+   parts of the propositional encoding $x\vlor A$ independently.  We
+   say that an instance $\rr_1$ of $\wD$ in $\Deri$ is \emph{in the
+   scope} of an instance $\rr_2$ of $\wD$ if $\rr_1$ introduced
+   formulas that contain a free variable $x$ (i.e., $x$ occurs in a
+   term in a predicate) and $\rr_2$ introduces the atom $x$ as a
+   subformula (i.e. the propositional encoding of the binder $x$).  We
+   can now permute the $\wD$-instances in $\DDeri$ such that whenever
+   a rule instance $\rr_1$ depends on an instance $\rr_2$, then
+   $\rr_2$ occurs below $\rr_1$ in $\DDeri$.
+   We can now lift $\DDeri$ stepwise. First, observe that each line of
+   in $\DDeri$ is $\PE\fequ$-equivalent to the propositional encoding $\PE P$ of a
    first-order formula $P$.  We now have to show
-  that each instance of $\wrD$ is indeed a correct
-  application in first-order logic. For this we have to inspect the
-  cases a weakening happens inside a subformula $x\vlor C$ or $x\vlan
-  C$ in $\PE\Deri_1$. There are the following cases:
+   that each other instance of $\wrD$ in $\DDeri$ is indeed the image of a correct
+   application of $\wD$ or $\wfaD$ in first-order logic.
+   If we have a $\wD$
+   \begin{equation*}
+     \vlinf{\wD}{}{\PE S\cons{x\vlor \PE A}}{\PE S\cons{\PE A}}
+     \qquor
+     \vlinf{\wD}{}{\PE S\cons{(x\vlor \PE B)\vlor \PE A}}{\PE S\cons{\PE A}}
+   \end{equation*}
+   then $x$ cannot occur freely in $A$, as otherwise the fibration
+   property would be violated. We can therefore lift these instances to
+   \begin{equation*}
+     \vlinf{\wfaD}{}{S\cons{\forall x. A}}{S\cons{A}}
+     \qquor
+     \vlinf{\wD}{}{S\cons{(\forall x. B)\vlor A}}{S\cons{A}}
+   \end{equation*}
+   respectively.     
+  %% A subformula of $\PE B$ is called \emph{weak} if it has been
+  %% introduced by a weakening. All subformulas of a weak formula are
+  %% also weak. Two weak subformulas $B'$ and $B''$ of $\PE B$ form a
+  %% \emph{weak pair} if $\PE B\fequ\Scons{B'\vlor B''}$ for some context
+  %% $\Sconhole$. We can assume without loss of generality that
+  %% whenever weak subformulas $B'$ and $B''$ form a weak pair, they have
+  %% been introduced by the same instance of $\wrD$ in
+  %% $\PE\Deri_1$.\footnote{If $\PE\Deri_1$ is not of that shape, it can
+  %% brought into this form by simple rule permutations, and then
+  %% collapsing several weakenings into a single one.}  Now we show that
+  %% $\PE\Deri_1$ can be lifted. For this, observe that whenever a
+  %% weakening in $\PE\Deri_1$ deletes an atom $x\in\VAR$, it must also
+  %% delete all atoms in the scope of the corresponding quantifier,
+  %% because $\phi'$ is a fibration on the binding graph. Hence, each line
+  If a  weakening happens inside a subformula $x\vlor \PE C$ or $x\vlan
+  \PE C$ in $\DDeri$, then there are the following cases:
   \begin{equation*}%\small
-    \vlinf{}{}{S\cons{x\vlor D\vlor C}}{S\cons{x\vlor C}}
-    \qquad
-    \vlinf{}{}{S\cons{x\vlan (D\vlor C)}}{S\cons{x\vlan C}}
-    \qquad
-    \vlinf{}{}{S\cons{(x\vlor D)\vlan C}}{S\cons{x\vlan C}}
-  \end{equation*}
-  In the first case the weakening happens inside the scope of a
-  $\forall$-quantifier, and in the second case inside the scope of a
-  $\exists$-quantifier. Both cases are unproblematic in first-order
-  logic. However, in the third case an $\exists$-quantifier would be
+    \scalebox{.9}{$
+    \vlinf{\wD}{}{\PE S\cons{x\vlor\PE  D\vlor \PE C}}{\PE S\cons{x\vlor\PE  C}}
+    \quad
+    \vlinf{\wD}{}{\PE S\cons{x\vlan (\PE D\vlor \PE C)}}{\PE S\cons{x\vlan\PE  C}}
+    \quad
+    \vlinf{\wD}{}{\PE S\cons{(x\vlor\PE  D)\vlan \PE C}}{\PE S\cons{x\vlan \PE C}}
+    $}
+  \end{equation*}
+  The first two cases can be lifted to
+  \begin{equation*}
+    \vlinf{\wD}{}{S\cons{\forall x.( D\vlor C)}}{S\cons{\forall x.  C}}
+    \quand
+     \vlinf{\wD}{}{S\cons{\exists x.( D\vlor C)}}{S\cons{\exists x.  C}}
+  \end{equation*}
+  respectively. But in the third case,  an $\exists$-quantifier would be
   transformed into an $\forall$-quantifier. But as $\phi$ has to
-  preserve existentials, this third case cannot occur.
-  Thus we have a first order derivation
-  $\vlder{\set{\wrD,\fequ}}{\Deri_1}{B}{B_1}$ with $\PE B_1=\PEp B_1$.
+  preserve existentials, this third case cannot occur. All other situations can be lifted trivially, giving us
+  $\vlder{\set{\wrD,\wfaD\fequ}}{\Deri}{H}{G}$ as desired.
 \end{proof}

### 2021-01-25 main.tex
thm 32

@@
       \vlin{\vlor}{}{\sqn{\cneg{p}w \vlor (\forall y.py), \exists
-x.(\cneg{p}x \vlor (\forall y.p(y)))}}{
+x.(\cneg{p}x \vlor (\forall y.py))}}{
         \vlin{\forall}{}{\sqn{\cneg{p}w, \forall y.py, \exists
@@
 x.(\cneg{p}x \vlor (\forall y.py))}}{
-            \vlin{\vlor}{}{\sqn{\cneg{p}w, pz, \cneg{p}z \vlor (\forall y.py))}}{
-              \vlin{\weakr}{}{\sqn{\cneg{p}w, pz, \cneg{p}z, (\forall y.py))}}{
+            \vlin{\vlor}{}{\sqn{\cneg{p}w, pz, \cneg{p}z \vlor (\forall y.py)}}{
+              \vlin{\weakr}{}{\sqn{\cneg{p}w, pz, \cneg{p}z, \forall y.py}}{
                 \vlin{\weakr}{}{\sqn{\cneg{p}w, pz, \cneg{p}z}}{
@@
 where $x$ must not be free in $B$ in the last two equations.
-Two formulas $A$ and $B$ are \bfit{equivalent} if $A \fequ B$. The following
-theorem shows that the set of fographs can been seen as the quotient
-$\FORM/\mathord\fequ$.
+Two formulas $A$ and $B$ are \bfit{equivalent} if $A \fequ B$. We have the
+following theorem:
 \begin{thm}
@@
 $\FOMLS$ can introduce a bimatching. To simplify the argument, we
-introduce the \bfit{frame}~\cite{hughes:unifn} of the fograph $\gC$,
+introduce the \bfit{frame}~\cite{hughes:unifn} of the linked fograph $\gC$,
 which is a linked (proposional) cograph in which the dependencies
@@
       \vlde{\set{\sw,\fequ}}{\DDeri_2}{\Scons{q_{h_1,j}\vlor\cdots\vlor
-          q_{h_j,j}\vlor(\dual q_{h_1,j}\vlan\cdots\vlan\dual
-          q_{h_j,j}\vlan\ttt)}}{
+          q_{h_n,j}\vlor(\dual q_{h_1,j}\vlan\cdots\vlan\dual
+          q_{h_n,j}\vlan\ttt)}}{
         \vlde{\set{\aiD,\tttD}}{\DDeri_1}{
-          \Scons{(q_{h_1,j}\vlor \dual q_{h_1,j})\vlan\cdots\vlan(q_{h_j,j}\vlor \dual q_{h_j,j})\vlan\ttt}}{
+          \Scons{(q_{h_1,j}\vlor \dual q_{h_1,j})\vlan\cdots\vlan(q_{h_n,j}\vlor \dual q_{h_n,j})\vlan\ttt}}{
           \vlhy{\ttt}}}}
@@
   \end{equation*}
-  where $h_1,\ldots,h_j$ range over the indices of the existential
+  where $h_1,\ldots,h_n$ range over the indices of the existential
   binders dependend on that $y_j$. It is easy to see how $\DDeri_1$ is
@@
     \vlder{\set{\sw,\fequ}}{\DDeri_3}{ S_0\cons{S_1\cons{\cdots
-          S_{k_i-1}\cons{S_{k_i}\cons{\dual q_{i,k_1}\vlan\dual
-              q_{i,k_2}\vlan\cdots q_{i,k_i}\vlan B'}}\cdots}}}{
+          S_{k_l-1}\cons{S_{k_l}\cons{\dual q_{i,k_1}\vlan\dual
+              q_{i,k_2}\vlan\cdots q_{i,k_l}\vlan B'}}\cdots}}}{
       S_0\cons{\dual q_{i,k_1}\vlan S_1\cons{\dual
-          q_{i,k_2}\vlan\cdots S_{k_i-1}\cons{\dual q_{i,k_i}\vlan
-            S_{k_i}\cons{B'}}\cdots}}}
-  \end{equation*}
-  where $k_1,\ldots,k_i$ are the indices of of the universal binders
+          q_{i,k_2}\vlan\cdots S_{k_l-1}\cons{\dual q_{i,k_k}\vlan
+            S_{k_l}\cons{B'}}\cdots}}}
+  \end{equation*}
+  where $k_1,\ldots,k_l$ are the indices of of the universal binders
   on which that $x_i$ depends, and $B'$ is $B$ in which all predicates
@@
   preserve existentials, this third case cannot occur. All other situations can be lifted trivially, giving us
-  $\vlder{\set{\wrD,\wfaD\fequ}}{\Deri}{H}{G}$ as desired.
+  $\vlder{\set{\wrD,\wfaD,\fequ}}{\Deri}{H}{G}$ as desired.
 \end{proof}
@@
 two non-$\fequ$ rule instances seperated by $\fequ$. Only non-trivial cases are
-considered here:
+presented here:
 \begin{itemize}

### 2021-01-25 main.tex
Minor fixes and typos

@@
   formalized in a deductive proof system based on inference rules,
-  a combinatorial proof is a syntax-fre presentation of a proof
+  a combinatorial proof is a syntax-free presentation of a proof
   that is independent from any set of inference rules. We show that
@@
 introduce the \bfit{frame}~\cite{hughes:unifn} of the linked fograph $\gC$,
-which is a linked (proposional) cograph in which the dependencies
+which is a linked (propositional) cograph in which the dependencies
 between the binders in $\gC$ are encoded as links.
@@
   where $h_1,\ldots,h_n$ range over the indices of the existential
-  binders dependend on that $y_j$. It is easy to see how $\DDeri_1$ is
+  binders dependent on that $y_j$. It is easy to see how $\DDeri_1$ is
   constructed, and for $\DDeri_2$ see,
@@
   below that $\forall$-instance. Now, observe that all instances of
-  the $\exists$-rule introducing $x_i$ dependend on $y_j$ must occur
+  the $\exists$-rule introducing $x_i$ dependent on $y_j$ must occur
   below in the derivation (otherwise $\Deri$ would not be rectified).
@@
   $\fographof{\frameof\Deri}=\tuple{\graphof{\frameof
-      C},\linkingof{\frameof\Deri}}$ can not contain an induced
+      C},\linkingof{\frameof\Deri}}$ cannot contain an induced
   bimatching. By Lemma~\ref{lem:frame}, $\fographof{\Deri}$ does not
-  have an induced bimatching either. Furthemore, it followed from the
+  have an induced bimatching either. Furthermore, it followed from the
   definition of $\dsubstof\Deri$ that it is a dualizer for
@@
    $\vlder{\set{\wrD,\PE\fequ}}{\DDeri}{\PE H}{\PE G}$. In order to
-   lift $\DDeri$, we might need to reorganize the instancese of
+   lift $\DDeri$, we might need to reorganize the instances of
    $\wD$. If $H$ contains a subformula $\forall x.A$ which is not
@@
   $\substof\phi$ to~$\PE A$. Note that $\PE A_1 =
-  \PE{(A\substof\phi)}$ and $\PE B_1$ are both proposional
+  \PE{(A\substof\phi)}$ and $\PE B_1$ are both propositional
   encodings. We plan to show that $\Deri_2$ can be lifted to
@@
   where $x$ occurs in $C\vlor D$. Then premise and conclusion are both
-  proposional encodings, but the whole derivation cannot be
+  propositional encodings, but the whole derivation cannot be
   lifted. However, since we demand that the the mapping is a fibration
-  (and therefore a momomorphism) on the binding graphs, there must be
+  (and therefore a homomorphism) on the binding graphs, there must be
   another instance of $\me$ further below in the derivation:
@@
   \begin{itemize}
-  \item $\acDx$: We know that the premisse of~\eqref{eq:acDeq} is a
+  \item $\acDx$: We know that the premise of~\eqref{eq:acDeq} is a
     propositional encoding. Hence, $S_1\conhole=\conhole\vlor \PE E$ and
@@
 this stage, and they are considered later when we study the interactions between
-two non-$\fequ$ rule instances seperated by $\fequ$. Only non-trivial cases are
+two non-$\fequ$ rule instances separated by $\fequ$. Only non-trivial cases are
 presented here:
@@
   \begin{equation*}
+  \scalebox{.9}{$
   \vlderivation{
@@
         \vlin{\mfaD}{}{\Scons{\forall x.(\forall x.A \vlor B)}}{
-          \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}}
+          \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}}$}
   \end{equation*}
@@
 \begin{equation*}
+\scalebox{.9}{$
 \vlderivation{
@@
   \vlin{\wfaD}{(x \notin fv(A))}{\forall y.\forall x.A}{
-    \vlhy{\forall y.A}}}
-\end{equation*}
-
-\begin{equation*}
+    \vlhy{\forall y.A}}}$}
+\end{equation*}
+
+\begin{equation*}
+\scalebox{.9}{$
 \vlderivation{
@@
   \vlin{\wfaD}{(x \notin fv(\forall y.A))}{\forall x.\forall y.A}{
-    \vlhy{\forall y.A}}}
+    \vlhy{\forall y.A}}}$}
 \end{equation*}
@@
           \vlin{\faD}{}{\forall x.(B \vlan D)}{
-            \vlhy{B \vlan D}}}}}}
+            \vlhy{B \vlan D}}}}}}$}
   \end{equation*}

### 2021-01-25 main.tex
done...

--- 2021-01-25 main.tex
@@
    application of $\wD$ or $\wfaD$ in first-order logic.
-   If we have a $\wD$
+   If we have a $\wD$ of the form
    \begin{equation*}
@@
 
+\begin{lemma}\label{lem:surj->cm}
+  Let $\phi\colon\gG\to\gH$ be a surjective skew
+  bifibration, and let $G$ and $H$ be formulas with $\graphof G=\gG$
+  and $\graphof H=\gH$. Then there is a derivation
+  \begin{equation*}
+    \vlderivation{
+      \vlde{\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{H}{
+        \vlhy{G\rsubstof\phi}}}
+  \end{equation*}
+  where  $\rsubstof\phi$ is the substitution
+  induced by $\phi$.
+\end{lemma}
+
+\begin{proof}
+  By \cite[Proposition~7.5]{str:ral:tableaux19}, there is a derivation
+  $\vlder{\set{\acD,\me,\PE\fequ}}{\DDeri}{\PE
+    H}{\PE{(G\substof\phi)}}$.  We can lift $\DDeri$ to a first-order
+  derivation in $\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$, in a similar
+  way as in the previous lemma. The technical details are in
+  Appendix~\ref{app:surj->cm}.
+\end{proof}
+
 \begin{proof}[Proof of Lemma~\ref{lem:skew->cw}]
-  By Lemma~\ref{lem:PE} we have $\gA=\graphof{\PE A}$ and
-  $\gB=\graphof{\PE B}$.  Let $\vB'\subseteq\vB$ be the image of
-  $\phi$, and let $\gB_1$ be the subgraph of $\gB$ induced by
-  $\vB'$. Hence, we have two maps $\phi''\colon\gA\to\gB_1$ being a
-  surjection and $\phi'\colon \gB_1\to\gB$ being an injection that
-  reflects edges.  Both, $\phi'$ and $\phi''$ remain skew
-  bifibrations. Let us first look at $\phi'$.  Let $\PEp B_1$ be the
-  propositional formula obtained from $\PE B$ by removing all atoms
-  that are not represented by vertices in $\vB'$. Then $\graphof{\PEp
-    B_1}=\gB_1$.
-
-  Let us now look at $\phi''$. Let $\gA_1=\gA\substof\phi$ be the
-  graph obtained from $\gA$ by applying $\substof\phi$ to all the
-  labels. Note that $\gA_1$ is not necessarily a fograph, as binders
-  might be illegal. But it still is a cograph, and we have a
-  surjective skew fibration $\phi''\colon\gA_1\to\gB_1$ that preserves
-  the labels. Therefore, by
+  Let $\vB'\subseteq\vB$ be the image of $\phi$, and let $\gB_1$ be
+  the subgraph of $\gB$ induced by $\vB'$. Hence, we have two maps
+  $\phi''\colon\gA\to\gB_1$ being a surjection and $\phi'\colon
+  \gB_1\to\gB$ being a full injection.  Both, $\phi'$ and $\phi''$
+  remain skew bifibrations.  Furthermore, $\gB_1$ is also a fograph.
+  Let $B_1$ be a formula with $\graphof{B_1}=\gB_1$.
+    We can apply Lemmas~\ref{lem:fullinj->w}
+  and~\ref{lem:surj->cm} to obtain derivations
+  \begin{equation*}
+    \vlder{\set{\wrD,\wfaD,\fequ}}{\Deri'}{B}{B_1}
+    \qquand
+     \vlder{\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri''}{B_1}{
+        A\rsubstof{\phi''}}
+  \end{equation*}
+  As $\rsubstof{\phi'}$ is the identity, we have
+  $\rsubstof{\phi''}=\rsubstof{\phi}$. Hence, the composition of
+  $\Deri''$ and $\Deri'$ is the desired derivation $\Deri$.  Then
+  $\rectif\Deri$ can be constructed by rectifying $\Deri$, where the
+  variables to be used in $A$ are already given. That
+  $\phi=\mapof{\rectif\Deri}$ follows immediately from the
+  construction.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Summary and Proof of Main Result}
+\label{sec:summary}
+
+The only theorem of Section~\ref{sec:main} that has not yet been
+proved is Theorem~\ref{thm:CP-DI} establishing the full correspondence
+between decomposed proofs in $\FOKS$ and combinatorial proofs. We show
+the proof here, by summarizing the results of the previous two
+Sections~\ref{sec:linear} and~\ref{sec:skew}.
+
+\begin{proof}[Proof of Theorem~\ref{thm:CP-DI}]
+  First, assume we have a combinatorial proof $\phi\colon\gC\to\gA$
+   and a formula $A$ with $\gA=\graphof A$.
+  Let $C$ be a formula with $\graphof C=\gC$, and let $\rsubstof\phi$
+  be the substitution induced by $\phi$.
+  By Lemma~\ref{lem:skew->cw} there is a derivation
+  \begin{equation*}
+    \vlder{\set{\wrD,\wfaD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{C\rsubstof\phi}
+  \end{equation*}
+  Since $\gC$ is a fonet, we have by Theorem~\ref{thm:fonet->MLS1} a derivation
+  \begin{equation*}
+    \vlder{\FOMLS}{\Deri'_1}{C}{\ttt}
+  \end{equation*}
+  This derivation remains valid if we apply the substitution
+  $\rsubstof\phi$ to every line in $\Deri'_1$, yielding the derivation
+  $\Deri_1$ of $C\rsubstof\phi$ as desired.
+
+  Conversely, assume we have a decomposed derivation
+  \begin{equation}
+    \label{eq:decomx}
+    \vlderivation{
+      \vlde{\set{\wrD,\wfaD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{
+        \vlde{\FOMLS}{\Deri_1}{A'}{
+          \vlhy{\ttt}}}}
+  \end{equation}
+  Then we can transform $\Deri_1$ into a rectified form
+  $\rectif\Deri_1$, proving $\rectif A'$. By
+  Theorem~\ref{thm:MLS1->fonet}, the linked fograph
+  $\fographof{\rectif\Deri_1}=\tuple{\fographof{\rectif
+      A'},\linkingof{\rectif\Deri_1}}$ is a fonet.  Then, by
+  Lemma~\ref{lem:cw->rectif}, there is a rectified derivation
+  $\vlderivation{
+    \vlde{\set{\wrD,\wfaD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif{\Deri_2}}{\rectif
+      A}{ \vlhy{\rectif{A'}}}}$ whose induced map
+  $\mapof{\rectif{\Deri_2}}\colon\graphof{\rectif{A'}}\to\graphof{\rectif
+    A}$ is the same as the induced map
+  $\mapof{\Deri_2}\colon\graphof{A'}\to\graphof{A}$ of $\Deri_2$. By
+  Lemma~\ref{lem:cw->skew}, this map is a skew bifibration. Hence, we
+  have a combinatorial proof $\phi\colon\gC\to\graphof{A}$ with
+  $\gC=\graphof{\rectif{A'}}$.
+%%  \lutz{shit, something's wrong...}
+  %% Let $\downsmash{\vlderivation{
+  %%   \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
+  %%     \vlhy{A}}}}$ be a derivation. Then there is a recified derivation
+  %% $\vlderivation{
+  %%   \vlde{\set{\wrD,\rectif\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{\rectif
+  %%     B}{ \vlhy{\rectif A}}}$, such that the induced maps
+  %% $\mapof\Deri\colon\graphof{A}\to\graphof{B}$ and
+  %% $\mapof{\rectif\Deri}\colon\graphof{\rectif A}\to\graphof{\rectif
+  %%   B}$ are equal up to a variable renaming of the vertex labels.
+  %% for some $A'\fequ C\sigma$ where $C$ is a formula with $\graphof
+  %% C=\gC$ and $\sigma$ is a variable renaming substitution.  Conversely,
+  %% whenever we have a derivation as in~\eqref{eq:decom} above, then
+  %% there is a combinatorial proof $\phi\colon\gC\to\graphof A$ such
+  %% that $\gC=\graphof{\rectif{A'}}$.
+\end{proof}
+
+Note that Theorem~\ref{thm:CP-DI} shows at the same time soundness, completeness, and full completeness, as
+\begin{enumerate}
+\item every proof in $\FOKS$ can be translated into a combinatorial proof, and
+\item every combinatorial proof is the image of a $\FOKS$-proof under that translation.
+\end{enumerate}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusion}
+
+In this paper we have uncovered a close correspondence between
+first-order combinatorial proofs and decomposed deep inference
+derivations of system $\FOKS$, and we have shown that every proof in
+$\FOKS$ has such a decomposed form.
+
+The most surprising discovery for us was that all technical
+difficulties in our work could be reduced (in a non-trivial way) to
+the propositional setting.
+
+The obvious next step in our research is to investigate proof
+composition and normalisation of first-order combinatorial
+proofs. Even in the propositional setting, the normalization of
+combinatorial proofs is underdeveloped. There exist two different
+procedures for cut elimination~\cite{hughes:invar,str:fscd17}, but
+both have their insufficiencies, and there is no general theory.
+
+Nonetheless, we hope to get new insights in the normalization of
+classical first-order proofs through our work on combinatorial proofs.
+
+%% We conjecture cut-elimination for first-order combinatorial proofs can be achieved via a method that is similar to the 
+%% \emph{cut-elimination by resolution} method for the sequent calculusthat via the step to first-
+%% \lutz{do we want/can say more here?}
+
+%% \todo{mention CERES}
+
+% conference papers do not normally have an appendix
+
+% use section* for acknowledgment
+%\section*{Acknowledgment}
+
+%The authors would like to thank...
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+%\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+%\bibliography{IEEEabrv,../bib/paper}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+
+\bibliographystyle{IEEEtran}
+\bibliography{refs}
+
+%\begin{thebibliography}{1}
+
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+
+%\end{thebibliography}
+
+%\clearhalfpage
+
+\vskip3em
+
+\appendix
+
+\subsection{Proof of Theorem~\ref{thm:LK1-decompose}}
+\label{app:LK1-decompose}
+
+\begin{proof}[Proof of Theorem~\ref{thm:LK1-decompose}]
+
+  Note that the instances of $\wrD,\cD$ in $\Deri_2$ are deep, but inside sequent contexts.
+
+First, if an instance of $\vlinf{\weakr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma}}$
+ is followed by a rule in which $A$ is not in the principal
+formula, it can be permuted downwards.
+Otherwise, the proof can be transformed using the following rewriting rules.
+
+\begin{equation*}
+\vlderivation{
+  \vliin{\vlan}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
+      \vlhy{\sqns{\Gamma}}}}{
+    \vlhy{\sqns{B, \Delta}}}}
+\leadsto
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
+    \vlin{\weakr}{}{\vlvdots}{
+      \vlhy{\sqns{\Gamma}}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\vlor}{}{\sqns{\Gamma, A \vlor B}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A, B}}{
+      \vlhy{\sqns{\Gamma, A}}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{\sqns{\Gamma, A \vlor B}}{
+    \vlhy{\sqns{\Gamma, A}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\exists}{}{\sqns{\Gamma, \exists x.A}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A\ssubst{x}{t}}}{
+      \vlhy{\sqns{\Gamma}}}}}
+\leadsto
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, \exists x.A}}{
+    \vlhy{\sqns{\Gamma}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\forall}{}{\sqns{\Gamma, \forall x.A}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
+      \vlhy{\sqns{\Gamma}}}}}
+\leadsto
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, \forall x.A}}{
+    \vlhy{\sqns{\Gamma}}}}
+\end{equation*}
+\begin{equation*}
+\vlderivation{
+  \vlin{\conr}{}{\sqns{\Gamma, A}}{
+    \vlin{\weakr}{}{\sqns{\Gamma, A, A}}{
+      \vlhy{\sqns{\Gamma, A}}}}}
+\leadsto
+\vlderivation{
+  \vlhy{\sqns{\Gamma, A}}}
+\end{equation*}
+Note that in the case of $\vlor$, we use the deep rule $\wrD$ which can be
+permuted under all the rules. By using these rewriting rules, we can eventually get
+a derivation with all the instances of $\weakr$ and $\wrD$ at the bottom. Now observe
+that the instances of $\conr$ in $\Deri$ can be transformed using the following
+rule:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\conr}{}{\sqns{\Gamma, A}}{
+    \vlhy{\sqns{\Gamma, A, A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cD}{}{\sqns{\Gamma, A}}{
+    \vlin{\vlor}{}{\sqns{\Gamma, A \vlor A}}{
+      \vlhy{\sqns{\Gamma, A, A}}}}}
+\end{equation*}
+
+Knowing that $\cD$ can be permuted under all the rules of $\FOMLL$, we
+eventually obtain a derivation:
+\begin{equation*}
+\vlderivation{
+  \vlde{\set{\weakr, \wrD,\cD,\fequ}}{\Deri'_2}{\sqns{\Gamma}}{
+    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma'}}{
+      \vlhy{\quad}}{
+      \vlhy{}}{
+      \vlhy{}}}}
+\end{equation*}
+Note that $\fequ$ is required here since the permutation of formulas is implicit
+in $\FOMLL$.
+
+By transforming each sequent of $\Deri'_2$ into its corresponding formula, and by
+considering the following rewriting rule:
+\begin{equation*}
+\vlderivation{
+  \vlin{\weakr}{}{\sqns{\Gamma, A}}{
+    \vlhy{\sqns{\Gamma}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{\sqns{\form{\Gamma} \vlor A}}{
+    \vlhy{\sqns{\form{\Gamma}}}}}
+\end{equation*},
+we obtain a derivation
+\begin{equation*}
+\vlderivation{
+  \vlde{\set{\wrD,\cD,\fequ}}{\Deri_2}{\sqns{\form{\Gamma}}}{
+    \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\form{\Gamma'}}}{
+      \vlhy{\quad}}{
+      \vlhy{}}{
+      \vlhy{}}}}
+\end{equation*}
+where $\Deri_1$ can be obtained from $\Deri'_1$
+by applying the $\vlor$ rule.
+\end{proof}
+
+\subsection{Rule permutation for the proof of Lemma~\ref{lem:cw-decomposition}}
+\label{app:cw-decomposition}
+We construct a rewriting system based on rule permutation on derivations in $\set{\wrD, \wfaD, \acD,
+\cfaD, \me, \mfaD, \mexD, \fequ}$ that allows us to reach a derivation of the
+form 
+\begin{equation*}
+    \vlderivation{
+      \vlde{\set{\wrD,\wfaD,\fequ}}{}{B}{
+        \vlde{\set{\acD,\cfaD}}{}{B'}{
+          \vlde{\set{\me,\mfaD,\mexD,\fequ}}{}{A'}{
+            \vlhy{A}}}}}
+\end{equation*}
+from any derivation. Intuitively, we want to move all the instances of $\rr \in
+\set{\wrD, \wfaD}$ downwards and all the instances of $\rr' \in \set{\me,
+\mfaD, \mexD}$ upwards.
+
+We first study the interactions between two rules. Certain cases are unsolved at
+this stage, and they are considered later when we study the interactions between
+two non-$\fequ$ rule instances seperated by $\fequ$. Only non-trivial cases are
+presented here:
+\begin{itemize}
+\item $\rr_1/\rr_2$, where $\rr_1 \in \set{\wrD, \wfaD}$ and $\rr_2 \in
+\set{\acD, \cfaD, \me, \mfaD, \mexD}$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\acD}{}{a}{
+    \vlin{\wrD}{}{a \vlor a}{ 
+      \vlhy{a}}}}
+\leadsto
+\vlderivation{
+  \vlhy{a}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\wrD}{}{(A \vlan C) \vlor (B \vlan D)}{
+      \vlhy{A \vlan C}}}}
+\leadsto 
+\vlderivation{
+  \vlin{\wrD}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\wrD}{}{(A \vlor B) \vlan C}{
+      \vlhy{A \vlan C}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\wrD}{}{(\forall x.A) \vlor (\forall x.B)}{
+      \vlhy{\forall x.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+    \vlhy{\forall x.A}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{\forall x.A}{
+    \vlin{\wfaD}{}{\forall x.\forall x.A}{
+      \vlhy{\forall x.A}}}}
+\leadsto
+\vlderivation{
+  \vlhy{\forall x.A}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\wfaD}{}{(\forall x.A) \vlor (\forall x.B)}{
+      \vlhy{A \vlor (\forall x.B)}}}}
+\leadsto
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+    \vlhy{A \vlor (\forall x.B)}}} 
+\end{equation*}
+where in the last case, $x$ is not free in $A$.
+
+\item $\rr_1/\rr_2$, where $\rr_1 \in \set{\acD, \cfaD}$ and $\rr_2 \in
+\set{\me, \mfaD, \mexD}$: 
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
+      \vlin{\cfaD}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
+        \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
+      \vlin{\fequ}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
+        \vlin{\mfaD}{}{\Scons{\forall x.(\forall x.A \vlor B)}}{
+          \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}}
+  \end{equation*}
+
+\item $\cfaD/\fequ$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall y.\forall x.A}{
+    \vlin{\cfaD}{}{\forall x.\forall y.A}{
+      \vlhy{\forall x.\forall x.\forall y.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cfaD}{}{\forall y.\forall x.A}{
+    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
+      \vlhy{\forall x.\forall x.\forall y.A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
+    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+    \vlin{\fequ}{}{(\forall x.\forall x. A) \vlor B}{
+      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
+\leadsto
+\vlderivation{
+  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
+      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
+\end{equation*}
+where in the last two cases, $x$ is not free in $B$.
+
+\item $\wrD/\fequ$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{B \vlor A}{
+    \vlin{\wrD}{}{A \vlor B}{
+      \vlhy{A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{A \vlor (B \vlor C)}{
+    \vlin{\wrD}{}{(A \vlor B) \vlor C)}{
+      \vlhy{A \vlor C}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
+    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+      \vlhy{\forall x.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{(\forall x. A) \vlor B}{
+    \vlhy{\forall x.A}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
+    \vlin{\wrD}{}{\forall x.(B \vlor A)}{
+      \vlhy{\forall x.B}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+    \vlin{\wrD}{}{(\forall x.A) \vlor B}{
+      \vlhy{\forall x.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+    \vlhy{\forall x.A}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+    \vlin{\wrD}{}{B \vlor (\forall x.A)}{
+      \vlhy{B}}}}
+\end{equation*}
+where in the last four cases, $x$ is not free in $B$.
+\item $\wfaD/\fequ$:
+
+In the following two cases, we assume $x \neq y$ (otherwise they are trivial).
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall y.\forall x.A}{
+    \vlin{\wfaD}{(x \notin fv(\forall y.A))}{\forall x.\forall y.A}{
+      \vlhy{\forall y.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wfaD}{(x \notin fv(A))}{\forall y.\forall x.A}{
+    \vlhy{\forall y.A}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.\forall y.A}{
+    \vlin{\wfaD}{(x \notin fv(A))}{\forall y.\forall x.A}{
+      \vlhy{\forall y.A}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wfaD}{(x \notin fv(\forall y.A))}{\forall x.\forall y.A}{
+    \vlhy{\forall y.A}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
+    \vlin{\wfaD}{}{\forall x.(A \vlor B)}{
+      \vlhy{A \vlor B}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wfaD}{}{(\forall x.A) \vlor B}{
+    \vlhy{A \vlor B}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+    \vlin{\wfaD}{}{(\forall x.A) \vlor B}{
+      \vlhy{A \vlor B}}}}
+\leadsto
+\vlderivation{
+  \vlin{\wfaD}{}{\forall x.(A \vlor B)}{
+    \vlhy{A \vlor B}}}
+\end{equation*}
+where in the last two cases, the constraint on $x$ on the left-hand side implies
+that of the right-hand side.
+
+\item $\fequ/\cfaD$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{\forall x.\forall y.A}{
+    \vlin{\fequ}{}{\forall x.\forall x.\forall y. A}{
+      \vlhy{\forall x.\forall y.\forall x.A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{\forall y.\forall x.A}{
+    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
+      \vlhy{\forall x.\forall y.\forall x.A}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x.A) \vlor B}{
+      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
+      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
+\end{equation*}
+
+\item $\fequ/\me$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
+      \vlhy{(C \vlan A) \vlor (B \vlan D)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
+      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
+\leadsto
+\vlderivation{
+  \vlin{\fequ}{}{(A \vlor B) \vlan (C \vlor D)}{
+    \vlin{\me}{}{(B \vlor A) \vlan (D \vlor C)}{
+      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{(A \vlor B) \vlan ((C \vlan E) \vlor D)}{
+    \vlin{\fequ}{}{(A \vlan (C \vlan E)) \vlor (B \vlan D)}{
+      \vlhy{((A \vlan C) \vlan E) \vlor (B \vlan D)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
+    \vlin{\fequ}{(x \notin fv(B \vlan D))}{\forall x.((A \vlan C) \vlor (B \vlan D))}{
+      \vlhy{(\forall x.(A \vlan C)) \vlor (B \vlan D)}}}}
+\end{equation*}
+
+\item $\fequ/\mfaD$:
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
+      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
+\leadsto
+\vlderivation{
+  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+    \vlin{\mfaD}{}{\forall x.(B \vlor A)}{
+      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.((\forall y.A) \vlor B)}{
+    \vlin{\fequ}{}{(\forall x.\forall y.A) \vlor (\forall x.B)}{
+      \vlhy{(\forall y.\forall x.A) \vlor (\forall x.B)}}}}
+\end{equation*}
+
+\begin{equation*}
+\vlderivation{
+  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
+      \vlhy{\forall x.(A \vlor (\forall x.B))}}}}
+\end{equation*}
+
+\item $\fequ/\mexD$: similar to $\fequ/\mfaD$
+
+\end{itemize}
+
+Interactions between two non-$\fequ$ rules with the presence of $\fequ$ in
+between:
+
+\begin{itemize}
+\item $\cfaD/\fequ/\rr$ where $\rr \in \set{\me, \mfaD, \mexD}$: First permute
+$\cfaD$ under $\fequ$ and then permute $\cfaD$ under $\rr$.
+
+\item $\acD/\fequ/\rr$ where $\rr \in \set{\me, \mfaD, \mexD}$: First permute
+$\acD$ under $\fequ$ and then permute $\acD$ under $\rr$.
+
+\item $\wrD/\fequ/\cfaD$:
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+      \vlin{\fequ}{}{(\forall x.\forall x.A) \vlor B}{
+        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
+          \vlhy{\forall x.\forall x.A}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{(\forall x.A) \vlor B}{
+      \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+        \vlhy{\forall x.\forall x.A}}}}
+  \end{equation*}
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
+      \vlin{\fequ}{}{(\forall x.\forall x.A) \vlor B}{
+        \vlin{\wrD}{}{\forall x.(B \vlor (\forall x.A))}{
+          \vlhy{\forall x.B}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\fequ}{}{(\forall x.A) \vlor B}{
+      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
+        \vlhy{\forall x.B}}}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+      \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
+        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
+          \vlhy{\forall x.\forall x.A}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+      \vlin{\cfaD}{}{\forall x.A}{
+        \vlhy{\forall x.\forall x.A}}}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
+      \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
+        \vlin{\wrD}{}{\forall x.(B \vlor (\forall x.A))}{
+          \vlhy{\forall x.B}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
+        \vlhy{\forall x.B}}}}
+  \end{equation*}
+  where in all four cases, $x$ is not free in $B$.
+\item $\wrD/\fequ/\acD$:
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\acD}{}{a \vlor B}{
+      \vlin{\fequ}{}{(a \vlor a) \vlor B}{
+        \vlin{\wrD}{}{(a \vlor B) \vlor a}{
+          \vlhy{a \vlor B}}}}}
+  \leadsto
+  \vlderivation{
+    \vlhy{a \vlor B}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\acD}{}{a \vlor B}{
+      \vlin{\fequ}{}{(a \vlor a) \vlor B}{
+        \vlin{\wrD}{}{a \vlor (a \vlor B)}{
+          \vlhy{a}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{a \vlor B}{
+      \vlhy{a}}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\acD}{}{\forall x.a}{
+      \vlin{\fequ}{(x \notin fv(a))}{\forall x.(a \vlor a)}{
+        \vlin{\wrD}{}{(\forall x.a) \vlor a}{
+          \vlhy{\forall x.a}}}}}
+  \leadsto
+  \vlderivation{
+    \vlhy{\forall x.a}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\acD}{}{\forall x.a}{
+      \vlin{\fequ}{(x \notin fv(a))}{\forall x.(a \vlor a)}{
+        \vlin{\wrD}{}{a \vlor (\forall x.a)}{
+          \vlhy{a}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wfaD}{(x \notin fv(a))}{\forall x.a}{
+      \vlhy{a}}}
+  \end{equation*}
+
+\item $\wrD/\fequ/\me$:
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
+      \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
+        \vlin{\wrD}{}{(C \vlan A) \vlor (B \vlan D)}{
+          \vlhy{C \vlan A}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{(A \vlor B) \vlan (C \vlor D)}{
+      \vlin{\wrD}{}{(A \vlor B) \vlan C}{
+        \vlin{\fequ}{}{A \vlan C}{
+          \vlhy{C \vlan A}}}}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
+      \vlin{\fequ}{}{\forall x.((A \vlan C) \vlor (B \vlan
+D))}{
+        \vlin{\wrD}{}{(B \vlan D) \vlor (\forall x.(A \vlan C))}{
+          \vlhy{B \vlan D}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\fequ}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
+      \vlin{\wrD}{}{\forall x.((B \vlor A) \vlan (D \vlor C))}{
+        \vlin{\wrD}{}{\forall x.((B \vlor A) \vlan D)}{
+          \vlin{\faD}{}{\forall x.(B \vlan D)}{
+            \vlhy{B \vlan D}}}}}}
+  \end{equation*}
+  where in the second case, $x$ is free in $B \vlan D$.
+
+\item $\wrD/\fequ/\mfaD$:
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+      \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
+        \vlin{\wrD}{}{(\forall x.B) \vlor (\forall x.A)}{
+          \vlhy{\forall x.B}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\fequ}{}{\forall x.(A \vlor B)}{
+      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
+        \vlhy{\forall x.B}}}}
+  \end{equation*}
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
+      \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
+        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
+          \vlhy{\forall x.\forall x.A}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
+      \vlin{\cfaD}{}{\forall x.A}{
+        \vlhy{\forall x.\forall x.A}}}}
+  \end{equation*}
+
+\item $\wrD/\fequ/\mexD$:
+
+  \begin{equation*}
+  \vlderivation{
+    \vlin{\mexD}{}{\exists x.(A \vlor B)}{
+      \vlin{\fequ}{}{(\exists x.A) \vlor (\exists x.B)}{
+        \vlin{\wrD}{}{(\exists x.B) \vlor (\exists x.A)}{
+          \vlhy{\exists x.B}}}}}
+  \leadsto
+  \vlderivation{
+    \vlin{\fequ}{}{\exists x.(A \vlor B)}{
+      \vlin{\wrD}{}{\exists x.(B \vlor A)}{
+        \vlhy{\exists x.B}}}}
+  \end{equation*}
+
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Proof of Lemma~\ref{lem:surj->cm}}
+\label{app:surj->cm}
+
+\begin{proof}[Proof of Lemma~\ref{lem:surj->cm}]
+  By
   \cite[Proposition~7.5]{str:ral:tableaux19}, there is a derivation
-  $\vlder{\set{\acD,\me,\PE\fequ}}{\PE\Deri_2}{\PE B_1}{\PE A_1}$,
-  where $\PE A_1 =\PE A\substof\phi$ is the result of applying
-  $\substof\phi$ to~$\PE A$. Note that $\PE A_1 =
-  \PE{(A\substof\phi)}$ and $\PE B_1$ are both proposional
-  encodings. We plan to show that $\Deri_2$ can be lifted to
+  $\vlder{\set{\acD,\me,\PE\fequ}}{\DDeri}{\PE H}{\PE{(G\rsubstof\phi)}}$,
+   We plan to show that $\DDeri$ can be lifted to
   $\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$. However, observe that not
-  every formula occurring in $\Deri_2$ is a propositional
+  every formula occurring in $\DDeri$ is a propositional
   encoding. There are two reasons for this: (i) we might have
@@
   now call instances of $\me$ as in~\eqref{eq:m-illegal}
-  \bfit{illegal}, and we can transform $\PE\Deri_2$ through
+  \bfit{illegal}, and we can transform $\DDeri$ through
   $\me$-permutations~\eqref{eq:m-permutation} into a derivation that
@@
   We can therefore assume that all instances of $\acDx$, that contract
-  an atom $x\in\VAR$ are either at the top of $\PE\Deri_2$ or below a
-  $\me$-instance as in~\eqref{eq:mac}. We now lift $\PE\Deri_2$ to
+  an atom $x\in\VAR$ are either at the top of $\DDeri$ or below a
+  $\me$-instance as in~\eqref{eq:mac}. We now lift $\DDeri$ to
   $\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$, proceed by induction on
-  the height of $\PE\Deri_2$, beginning at the top, making a case
+  the height of $\DDeri$, beginning at the top, making a case
   analysis on the topmost rule that is not a~$\fequ$.
@@
   \end{itemize}
-  Thus $\PE\Deri_2$ can be lifted to
-  $\vlder{\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{B_1}{A\substof\phi}$. We
-  construct $\Deri$ by composing $\Deri_2$ and $\Deri_1$. Then
-  $\rectif\Deri$ can be constructed by rectifying $\Deri$, where the
-  variables to be used in $A$ are already given. That
-  $\phi=\mapof{\rectif\Deri}$ follows immediately from the
-  construction.
+  Thus $\DDeri$ can be lifted to
+  $\vlder{\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{H}{G\rsubstof\phi}$. 
 \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Summary and Proof of Main Result}
-\label{sec:summary}
-
-The only theorem of Section~\ref{sec:main} that has not yet been
-proved is Theorem~\ref{thm:CP-DI} establishing the full correspondence
-between decomposed proofs in $\FOKS$ and combinatorial proofs. We show
-the proof here, by summarizing the results of the previous two
-Sections~\ref{sec:linear} and~\ref{sec:skew}.
-
-\begin{proof}[Proof of Theorem~\ref{thm:CP-DI}]
-  First, asssume we have a combinatorial proof $\phi\colon\gC\to\gA$
-  be a combinatorial proof and a formula $A$ with $\gA=\graphof A$.
-  Let $C$ be a formula with $\graphof C=\gC$, and let $\substof\phi$
-  be the substitution induced by $\phi$.
-  By Lemma~\ref{lem:skew->cw} there is a derivation
-  \begin{equation*}
-    \vlder{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{C\substof\phi}
-  \end{equation*}
-  Since $\gC$ is a fonet, we have by Theorem~\ref{thm:fonet->MLS1} a derivation
-  \begin{equation*}
-    \vlder{\FOMLS}{\Deri'_1}{C}{\ttt}
-  \end{equation*}
-  This derivation remains valid if we apply the substitution
-  $\substof\phi$ to every line in $\Deri'_1$, yielding the derivation
-  $\Deri_1$ of $C\substof\phi$ as desired.
-
-  Conversely, assume we have a decomposed derivation
-  \begin{equation}
-    \label{eq:decomx}
-    \vlderivation{
-      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{\Deri_2}{A}{
-        \vlde{\FOMLS}{\Deri_1}{A'}{
-          \vlhy{\ttt}}}}
-  \end{equation}
-  Then we can transform $\Deri_1$ into a rectified form
-  $\rectif\Deri_1$, proving $\rectif A'$. By
-  Theorem~\ref{thm:MLS1->fonet}, the linked fograph
-  $\fographof{\rectif\Deri_1}=\tuple{\fographof{\rectif
-      A'},\linkingof{\rectif\Deri_1}}$ is a fonet.  Then, by
-  Lemma~\ref{lem:cw->rectif}, there is a rectified derivation
-  $\vlderivation{
-    \vlde{\set{\wrD,\rectif\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif{\Deri_2}}{\rectif
-      A}{ \vlhy{\rectif{A'}}}}$ whose induced map
-  $\mapof{\rectif{\Deri_2}}\colon\graphof{\rectif{A'}}\to\graphof{\rectif
-    A}$ is the same a the induced map
-  $\mapof{\Deri_2}\colon\graphof{A'}\to\graphof{A}$ of $\Deri_2$. By
-  Lemma~\ref{lem:cw->skew}, this map is a skew bifibration. Hence, we
-  have a combinatorial proof $\phi\colon\gC\to\graphof{A}$ with
-  $\gC=\graphof{\rectif{A'}}$.
-  \lutz{shit, something's wrong...}
-  %% Let $\downsmash{\vlderivation{
-  %%   \vlde{\set{\wrD,\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{B}{
-  %%     \vlhy{A}}}}$ be a derivation. Then there is a recified derivation
-  %% $\vlderivation{
-  %%   \vlde{\set{\wrD,\rectif\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\rectif\Deri}{\rectif
-  %%     B}{ \vlhy{\rectif A}}}$, such that the induced maps
-  %% $\mapof\Deri\colon\graphof{A}\to\graphof{B}$ and
-  %% $\mapof{\rectif\Deri}\colon\graphof{\rectif A}\to\graphof{\rectif
-  %%   B}$ are equal up to a variable renaming of the vertex labels.
-  %% for some $A'\fequ C\sigma$ where $C$ is a formula with $\graphof
-  %% C=\gC$ and $\sigma$ is a variable renaming substitution.  Conversely,
-  %% whenever we have a derivation as in~\eqref{eq:decom} above, then
-  %% there is a combinatorial proof $\phi\colon\gC\to\graphof A$ such
-  %% that $\gC=\graphof{\rectif{A'}}$.
-\end{proof}
-
-Note that Theorem~\ref{thm:CP-DI} shows at the same time soundness, completeness, and full completeness, as
-\begin{enumerate}
-\item every proof in $\FOKS$ can be translated into a combinatorial proof, and
-\item every combinatorial proof is the image of a $\FOKS$-proof under that translation.
-\end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-In this paper we have uncovered a close correspondence between
-first-order combinatorial proofs and decomposed deep inference
-derivations of system $\FOKS$, and we have shown that every proof in
-$\FOKS$ has such a decomposed form.
-
-The most surprising discovery for us was that all technical
-difficulties in our work could be reduced (in a non-trivial way) to
-the propositional setting.
-
-The obvious next step in our research is to investigate proof
-composition and normalisation of first-order combinatorial
-proofs. Even in the propositional setting, the normalization of
-combinatorial proofs is underdeveloped. There exist two different
-procedures for cut elimination~\cite{hughes:invar,str:fscd17}, but
-both have their insufficiencies, and there is no general theory.
-
-\lutz{do we want/can say more here?}
-
-\todo{mention CERES}
-
-% conference papers do not normally have an appendix
-
-% use section* for acknowledgment
-%\section*{Acknowledgment}
-
-%The authors would like to thank...
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-\bibliographystyle{IEEEtran}
-\bibliography{refs}
-
-%\begin{thebibliography}{1}
-
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-%\end{thebibliography}
-
-%\clearhalfpage
-
-\vskip3em
-
-\appendix
-
-\subsection{Proof of Theorem~\ref{thm:LK1-decompose}}
-\label{app:LK1-decompose}
-
-\begin{proof}[Proof of Theorem~\ref{thm:LK1-decompose}]
-
-  Note that the instances of $\wrD,\cD$ in $\Deri_2$ are deep, but inside sequent contexts.
-
-First, if an instance of $\vlinf{\weakr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma}}$
- is followed by a rule in which $A$ is not in the principal
-formula, it can be permuted downwards.
-Otherwise, the proof can be transformed using the following rewriting rules.
-
-\begin{equation*}
-\vlderivation{
-  \vliin{\vlan}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
-      \vlhy{\sqns{\Gamma}}}}{
-    \vlhy{\sqns{B, \Delta}}}}
-\leadsto
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
-    \vlin{\weakr}{}{\vlvdots}{
-      \vlhy{\sqns{\Gamma}}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\vlor}{}{\sqns{\Gamma, A \vlor B}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A, B}}{
-      \vlhy{\sqns{\Gamma, A}}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{\sqns{\Gamma, A \vlor B}}{
-    \vlhy{\sqns{\Gamma, A}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\exists}{}{\sqns{\Gamma, \exists x.A}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A\ssubst{x}{t}}}{
-      \vlhy{\sqns{\Gamma}}}}}
-\leadsto
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, \exists x.A}}{
-    \vlhy{\sqns{\Gamma}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\forall}{}{\sqns{\Gamma, \forall x.A}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
-      \vlhy{\sqns{\Gamma}}}}}
-\leadsto
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, \forall x.A}}{
-    \vlhy{\sqns{\Gamma}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\conr}{}{\sqns{\Gamma, A}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A, A}}{
-      \vlhy{\sqns{\Gamma, A}}}}}
-\leadsto
-\vlderivation{
-  \vlhy{\sqns{\Gamma, A}}}
-\end{equation*}
-Note that in the case of $\vlor$, we use the deep rule $\wrD$ which can be
-permuted under all the rules. By using these rewriting rules, we can eventually get
-a derivation with all the instances of $\weakr$ and $\wrD$ at the bottom. Now observe
-that the instances of $\conr$ in $\Deri$ can be transformed using the following
-rule:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\conr}{}{\sqns{\Gamma, A}}{
-    \vlhy{\sqns{\Gamma, A, A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cD}{}{\sqns{\Gamma, A}}{
-    \vlin{\vlor}{}{\sqns{\Gamma, A \vlor A}}{
-      \vlhy{\sqns{\Gamma, A, A}}}}}
-\end{equation*}
-
-Knowing that $\cD$ can be permuted under all the rules of $\FOMLL$, we
-eventually obtain a derivation:
-\begin{equation*}
-\vlderivation{
-  \vlde{\set{\weakr, \wrD,\cD,\fequ}}{\Deri'_2}{\sqns{\Gamma}}{
-    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma'}}{
-      \vlhy{\quad}}{
-      \vlhy{}}{
-      \vlhy{}}}}
-\end{equation*}
-Note that $\fequ$ is required here since the permutation of formulas is implicit
-in $\FOMLL$.
-
-By transforming each sequent of $\Deri'_2$ into its corresponding formula, and by
-considering the following rewriting rule:
-\begin{equation*}
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, A}}{
-    \vlhy{\sqns{\Gamma}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{\sqns{\form{\Gamma} \vlor A}}{
-    \vlhy{\sqns{\form{\Gamma}}}}}
-\end{equation*},
-we obtain a derivation
-\begin{equation*}
-\vlderivation{
-  \vlde{\set{\wrD,\cD,\fequ}}{\Deri_2}{\sqns{\form{\Gamma}}}{
-    \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\form{\Gamma'}}}{
-      \vlhy{\quad}}{
-      \vlhy{}}{
-      \vlhy{}}}}
-\end{equation*}
-where $\Deri_1$ can be obtained from $\Deri'_1$
-by applying the $\vlor$ rule.
-\end{proof}
-
-\subsection{Rule permutation for the proof of Lemma~\ref{lem:cw-decomposition}}
-\label{app:cw-decomposition}
-We construct a rewriting system based on rule permutation on derivations in $\set{\wrD, \wfaD, \acD,
-\cfaD, \me, \mfaD, \mexD, \fequ}$ that allows us to reach a derivation of the
-form 
-\begin{equation*}
-    \vlderivation{
-      \vlde{\set{\wrD,\wfaD,\fequ}}{}{B}{
-        \vlde{\set{\acD,\cfaD}}{}{B'}{
-          \vlde{\set{\me,\mfaD,\mexD,\fequ}}{}{A'}{
-            \vlhy{A}}}}}
-\end{equation*}
-from any derivation. Intuitively, we want to move all the instances of $\rr \in
-\set{\wrD, \wfaD}$ downwards and all the instances of $\rr' \in \set{\me,
-\mfaD, \mexD}$ upwards.
-
-We first study the interactions between two rules. Certain cases are unsolved at
-this stage, and they are considered later when we study the interactions between
-two non-$\fequ$ rule instances seperated by $\fequ$. Only non-trivial cases are
-presented here:
-\begin{itemize}
-\item $\rr_1/\rr_2$, where $\rr_1 \in \set{\wrD, \wfaD}$ and $\rr_2 \in
-\set{\acD, \cfaD, \me, \mfaD, \mexD}$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\acD}{}{a}{
-    \vlin{\wrD}{}{a \vlor a}{ 
-      \vlhy{a}}}}
-\leadsto
-\vlderivation{
-  \vlhy{a}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\wrD}{}{(A \vlan C) \vlor (B \vlan D)}{
-      \vlhy{A \vlan C}}}}
-\leadsto 
-\vlderivation{
-  \vlin{\wrD}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\wrD}{}{(A \vlor B) \vlan C}{
-      \vlhy{A \vlan C}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\wrD}{}{(\forall x.A) \vlor (\forall x.B)}{
-      \vlhy{\forall x.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-    \vlhy{\forall x.A}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{\forall x.A}{
-    \vlin{\wfaD}{}{\forall x.\forall x.A}{
-      \vlhy{\forall x.A}}}}
-\leadsto
-\vlderivation{
-  \vlhy{\forall x.A}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\wfaD}{}{(\forall x.A) \vlor (\forall x.B)}{
-      \vlhy{A \vlor (\forall x.B)}}}}
-\leadsto
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlhy{A \vlor (\forall x.B)}}} 
-\end{equation*}
-where in the last case, $x$ is not free in $A$.
-
-\item $\rr_1/\rr_2$, where $\rr_1 \in \set{\acD, \cfaD}$ and $\rr_2 \in
-\set{\me, \mfaD, \mexD}$: 
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
-      \vlin{\cfaD}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
-        \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
-      \vlin{\fequ}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
-        \vlin{\mfaD}{}{\Scons{\forall x.(\forall x.A \vlor B)}}{
-          \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}}
-  \end{equation*}
-
-\item $\cfaD/\fequ$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall y.\forall x.A}{
-    \vlin{\cfaD}{}{\forall x.\forall y.A}{
-      \vlhy{\forall x.\forall x.\forall y.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cfaD}{}{\forall y.\forall x.A}{
-    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
-      \vlhy{\forall x.\forall x.\forall y.A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
-    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-    \vlin{\fequ}{}{(\forall x.\forall x. A) \vlor B}{
-      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
-      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
-\end{equation*}
-where in the last two cases, $x$ is not free in $B$.
-
-\item $\wrD/\fequ$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{B \vlor A}{
-    \vlin{\wrD}{}{A \vlor B}{
-      \vlhy{A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{A \vlor (B \vlor C)}{
-    \vlin{\wrD}{}{(A \vlor B) \vlor C)}{
-      \vlhy{A \vlor C}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
-    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-      \vlhy{\forall x.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{(\forall x. A) \vlor B}{
-    \vlhy{\forall x.A}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
-    \vlin{\wrD}{}{\forall x.(B \vlor A)}{
-      \vlhy{\forall x.B}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlin{\wrD}{}{(\forall x.A) \vlor B}{
-      \vlhy{\forall x.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-    \vlhy{\forall x.A}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlin{\wrD}{}{B \vlor (\forall x.A)}{
-      \vlhy{B}}}}
-\end{equation*}
-where in the last four cases, $x$ is not free in $B$.
-\item $\wfaD/\fequ$:
-
-In the following two cases, we assume $x \neq y$ (otherwise they are trivial).
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall y.\forall x.A}{
-    \vlin{\wfaD}{(x \notin fv(\forall y.A))}{\forall x.\forall y.A}{
-      \vlhy{\forall y.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wfaD}{(x \notin fv(A))}{\forall y.\forall x.A}{
-    \vlhy{\forall y.A}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.\forall y.A}{
-    \vlin{\wfaD}{(x \notin fv(A))}{\forall y.\forall x.A}{
-      \vlhy{\forall y.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wfaD}{(x \notin fv(\forall y.A))}{\forall x.\forall y.A}{
-    \vlhy{\forall y.A}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
-    \vlin{\wfaD}{}{\forall x.(A \vlor B)}{
-      \vlhy{A \vlor B}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wfaD}{}{(\forall x.A) \vlor B}{
-    \vlhy{A \vlor B}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlin{\wfaD}{}{(\forall x.A) \vlor B}{
-      \vlhy{A \vlor B}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wfaD}{}{\forall x.(A \vlor B)}{
-    \vlhy{A \vlor B}}}
-\end{equation*}
-where in the last two cases, the constraint on $x$ on the left-hand side implies
-that of the right-hand side.
-
-\item $\fequ/\cfaD$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{\forall x.\forall y.A}{
-    \vlin{\fequ}{}{\forall x.\forall x.\forall y. A}{
-      \vlhy{\forall x.\forall y.\forall x.A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{\forall y.\forall x.A}{
-    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
-      \vlhy{\forall x.\forall y.\forall x.A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x.A) \vlor B}{
-      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
-      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
-\end{equation*}
-
-\item $\fequ/\me$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
-      \vlhy{(C \vlan A) \vlor (B \vlan D)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
-      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
-\leadsto
-\vlderivation{
-  \vlin{\fequ}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\me}{}{(B \vlor A) \vlan (D \vlor C)}{
-      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{(A \vlor B) \vlan ((C \vlan E) \vlor D)}{
-    \vlin{\fequ}{}{(A \vlan (C \vlan E)) \vlor (B \vlan D)}{
-      \vlhy{((A \vlan C) \vlan E) \vlor (B \vlan D)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
-    \vlin{\fequ}{(x \notin fv(B \vlan D))}{\forall x.((A \vlan C) \vlor (B \vlan D))}{
-      \vlhy{(\forall x.(A \vlan C)) \vlor (B \vlan D)}}}}
-\end{equation*}
-
-\item $\fequ/\mfaD$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
-      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
-\leadsto
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlin{\mfaD}{}{\forall x.(B \vlor A)}{
-      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.((\forall y.A) \vlor B)}{
-    \vlin{\fequ}{}{(\forall x.\forall y.A) \vlor (\forall x.B)}{
-      \vlhy{(\forall y.\forall x.A) \vlor (\forall x.B)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
-      \vlhy{\forall x.(A \vlor (\forall x.B))}}}}
-\end{equation*}
-
-\item $\fequ/\mexD$: similar to $\fequ/\mfaD$
-
-\end{itemize}
-
-Interactions between two non-$\fequ$ rules with the presence of $\fequ$ in
-between:
-
-\begin{itemize}
-\item $\cfaD/\fequ/\rr$ where $\rr \in \set{\me, \mfaD, \mexD}$: First permute
-$\cfaD$ under $\fequ$ and then permute $\cfaD$ under $\rr$.
-
-\item $\acD/\fequ/\rr$ where $\rr \in \set{\me, \mfaD, \mexD}$: First permute
-$\acD$ under $\fequ$ and then permute $\acD$ under $\rr$.
-
-\item $\wrD/\fequ/\cfaD$:
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-      \vlin{\fequ}{}{(\forall x.\forall x.A) \vlor B}{
-        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
-          \vlhy{\forall x.\forall x.A}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{(\forall x.A) \vlor B}{
-      \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-        \vlhy{\forall x.\forall x.A}}}}
-  \end{equation*}
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-      \vlin{\fequ}{}{(\forall x.\forall x.A) \vlor B}{
-        \vlin{\wrD}{}{\forall x.(B \vlor (\forall x.A))}{
-          \vlhy{\forall x.B}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\fequ}{}{(\forall x.A) \vlor B}{
-      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
-        \vlhy{\forall x.B}}}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-      \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
-        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
-          \vlhy{\forall x.\forall x.A}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-      \vlin{\cfaD}{}{\forall x.A}{
-        \vlhy{\forall x.\forall x.A}}}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-      \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
-        \vlin{\wrD}{}{\forall x.(B \vlor (\forall x.A))}{
-          \vlhy{\forall x.B}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
-        \vlhy{\forall x.B}}}}
-  \end{equation*}
-  where in all four cases, $x$ is not free in $B$.
-\item $\wrD/\fequ/\acD$:
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\acD}{}{a \vlor B}{
-      \vlin{\fequ}{}{(a \vlor a) \vlor B}{
-        \vlin{\wrD}{}{(a \vlor B) \vlor a}{
-          \vlhy{a \vlor B}}}}}
-  \leadsto
-  \vlderivation{
-    \vlhy{a \vlor B}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\acD}{}{a \vlor B}{
-      \vlin{\fequ}{}{(a \vlor a) \vlor B}{
-        \vlin{\wrD}{}{a \vlor (a \vlor B)}{
-          \vlhy{a}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{a \vlor B}{
-      \vlhy{a}}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\acD}{}{\forall x.a}{
-      \vlin{\fequ}{(x \notin fv(a))}{\forall x.(a \vlor a)}{
-        \vlin{\wrD}{}{(\forall x.a) \vlor a}{
-          \vlhy{\forall x.a}}}}}
-  \leadsto
-  \vlderivation{
-    \vlhy{\forall x.a}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\acD}{}{\forall x.a}{
-      \vlin{\fequ}{(x \notin fv(a))}{\forall x.(a \vlor a)}{
-        \vlin{\wrD}{}{a \vlor (\forall x.a)}{
-          \vlhy{a}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wfaD}{(x \notin fv(a))}{\forall x.a}{
-      \vlhy{a}}}
-  \end{equation*}
-
-\item $\wrD/\fequ/\me$:
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
-      \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
-        \vlin{\wrD}{}{(C \vlan A) \vlor (B \vlan D)}{
-          \vlhy{C \vlan A}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{(A \vlor B) \vlan (C \vlor D)}{
-      \vlin{\wrD}{}{(A \vlor B) \vlan C}{
-        \vlin{\fequ}{}{A \vlan C}{
-          \vlhy{C \vlan A}}}}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
-      \vlin{\fequ}{}{\forall x.((A \vlan C) \vlor (B \vlan
-D))}{
-        \vlin{\wrD}{}{(B \vlan D) \vlor (\forall x.(A \vlan C))}{
-          \vlhy{B \vlan D}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\fequ}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
-      \vlin{\wrD}{}{\forall x.((B \vlor A) \vlan (D \vlor C))}{
-        \vlin{\wrD}{}{\forall x.((B \vlor A) \vlan D)}{
-          \vlin{\faD}{}{\forall x.(B \vlan D)}{
-            \vlhy{B \vlan D}}}}}}
-  \end{equation*}
-  where in the second case, $x$ is free in $B \vlan D$.
-
-\item $\wrD/\fequ/\mfaD$:
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-      \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
-        \vlin{\wrD}{}{(\forall x.B) \vlor (\forall x.A)}{
-          \vlhy{\forall x.B}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
-        \vlhy{\forall x.B}}}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-      \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
-        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
-          \vlhy{\forall x.\forall x.A}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-      \vlin{\cfaD}{}{\forall x.A}{
-        \vlhy{\forall x.\forall x.A}}}}
-  \end{equation*}
-
-\item $\wrD/\fequ/\mexD$:
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\mexD}{}{\exists x.(A \vlor B)}{
-      \vlin{\fequ}{}{(\exists x.A) \vlor (\exists x.B)}{
-        \vlin{\wrD}{}{(\exists x.B) \vlor (\exists x.A)}{
-          \vlhy{\exists x.B}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\fequ}{}{\exists x.(A \vlor B)}{
-      \vlin{\wrD}{}{\exists x.(B \vlor A)}{
-        \vlhy{\exists x.B}}}}
-  \end{equation*}
-
-\end{itemize}
-
 \end{document}

### 2021-01-26 main.tex
Minor fixes

@@
 illustrates the surjection in (a), and since the syntactic proofs 
-of the two systems both translate the same combinatorial proof,
+of the two systems both translate to the same combinatorial proof,
 they can be considered \emph{the same}.
@@
 where the arity of $f$ and $p$ is $n$.
-For better readability of often omit parentheses and write simply $ft_1 \dots t_n$ or $pt_1 \dots t_n$.
+For better readability we often omit parentheses and write simply $ft_1 \dots t_n$ or $pt_1 \dots t_n$.
 We consider the truth constants
@@
 for all $v, w \in M$. A module $M$ is \bfit{strong} if for every
-module $M'$, we have $M' \subseteq M$, $M \subseteq$ or $M \cap M' =
+module $M'$, we have $M' \subseteq M$, $M \subseteq M'$ or $M \cap M' =
 \emptyset$. A module is \bfit{proper} if it has two or more vertices.
@@
 \begin{proof}
-  By a straightforward induction on $A$.
+  Straightforward induction on $A$.
 \end{proof}
@@
 that every colour (i.e., equivalence class of~$\linkingof\gC$), called a \bfit{link}, consists of two pre-dual literals, and
-every literal is either $\ttt$-labelled or in a link. Hence, in a linked fograph no vertex is labeled~$\fff$.
+every literal is either $\ttt$-labelled or in a link. Hence, in a linked fograph no vertex is labelled~$\fff$.
 
@@
 underlying graphs, and $\rsubstof\phi$, also called the
-\bfit{substitution induced by $\phi$} is a variable renaming 
+\bfit{substitution induced by $\phi$}, is a variable renaming
 such that
@@
 if for all existential binders $b$ in
-$\gG$, the binder $\phi(b)$ is a existential in $\gH$.
+$\gG$, the binder $\phi(b)$ is existential in $\gH$.
 %
@@
   (modulo renaming),
-  we often omit the labeling in the upper graph, as below-right.
+  we often omit the labelling in the upper graph, as below-right.
   %% , which refer to as 
@@
 %
-In contrast to to standard proof formalisms, like sequent calculi or
+In contrast to standard proof formalisms, like sequent calculi or
 tableaux, where inference rules decompose the principal formula along
@@
 Our second result is more surprising, as it is a very strong
-decomposition result for first order logic.
+decomposition result for first-order logic.
 
@@
 every derivation can be transformed into that form, we can say that
-combinatorial proofs form a canonical proof representation for first
-order logic, similarly to what proof nets are for linear
+combinatorial proofs form a canonical proof representation for first-order
+logic, similarly to what proof nets are for linear
 logic~\cite{girard:96:PN}.
@@
 and~\ref{thm:CP-DI} imply Theorem~\ref{thm:FOCP}, which means that we
-have here an alternative proof of the soundness and completeness of
+have here an alternative proof of the soundness and completeness for
 first-order combinatorial proofs which is simpler than the one given
@@
   $\weakr$. Then the instances of $\weakr$ and $\conr$ are replaced by
-  $\wD$ and $\cD$, which can then be permuted down. (Details are in
+  $\wD$ and $\cD$, which can then be permuted down. Details are in
   Appendix~\ref{app:LK1-decompose}.
@@
 \begin{proof}
-  First, observe that the $\exists$ rule can be permuted downwards
-  over all the other rules since $A\ssubst{x}{t}$ has the same
+  First, observe that the $\exists$ rule can be permuted under all the other rules since $A\ssubst{x}{t}$ has the same
   structure as $A$ and none of the other rules has a premise of the
@@
   occurrence of $\forall y_j.F$ is replaced by
-  $q_{h_1,j}\vlor\cdots\vlor q_{h_j,j}\vlor (\dual
-  q_{h_1,j}\vlan\cdots\vlan\dual q_{h_j,j}\vlan F)$ in the derivation
+  $q_{h_1,j}\vlor\cdots\vlor q_{h_n,j}\vlor (\dual
+  q_{h_1,j}\vlan\cdots\vlan\dual q_{h_n,j}\vlan F)$ in the derivation
   below that $\forall$-instance. Now, observe that all instances of
@@
     \vlder{\set{\sw,\fequ}}{\DDeri_3}{ S_0\cons{S_1\cons{\cdots
-          S_{k_l-1}\cons{S_{k_l}\cons{\dual q_{i,k_1}\vlan\dual
+          S_{l-1}\cons{S_{l}\cons{\dual q_{i,k_1}\vlan\dual
               q_{i,k_2}\vlan\cdots q_{i,k_l}\vlan B'}}\cdots}}}{
       S_0\cons{\dual q_{i,k_1}\vlan S_1\cons{\dual
-          q_{i,k_2}\vlan\cdots S_{k_l-1}\cons{\dual q_{i,k_k}\vlan
-            S_{k_l}\cons{B'}}\cdots}}}
-  \end{equation*}
-  where $k_1,\ldots,k_l$ are the indices of of the universal binders
+          q_{i,k_2}\vlan\cdots S_{l-1}\cons{\dual q_{i,k_l}\vlan
+            S_{l}\cons{B'}}\cdots}}}
+  \end{equation*}
+  where $k_1,\ldots,k_l$ are the indices of the universal binders
   on which that $x_i$ depends, and $B'$ is $B$ in which all predicates
@@
   bimatching. By Lemma~\ref{lem:frame}, $\fographof{\Deri}$ does not
-  have an induced bimatching either. Furthermore, it followed from the
+  have an induced bimatching either. Furthermore, it follows from the
   definition of $\dsubstof\Deri$ that it is a dualizer for
@@
 For each instance $\vlinf{\rr}{}{P}{Q}$ of an inference rule in
-$\set{\wrD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can
+$\set{\wrD,\wfaD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}$ we can
 define the \bfit{induced map} $\mapof{\rr}\colon\vgraphof
@@
   Let $\vlderivation{
-    \vlde{\set{\wrD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
+    \vlde{\set{\wrD,\wfaD,\acD,\rectif\cfaD,\me,\rectif\mfaD,\rectif\mexD,\fequ}}{\Deri}{B}{
       \vlhy{A}}}$ be a rectified derivation. Then the induced map
@@
   ambiguity here. Any instance of a rule $\wD$, $\acD$, $\me$, or
-  $\fequ$ is translated to an instance of the same rule, and
-  $\rectif\cfaD$ is translated to $\rectif\acD$.
+  $\fequ$ is translated to an instance of the same rule,
+  $\rectif\cfaD$ is translated to $\rectif\acD$, and $\wfaD$ is
+  translated to $\wD$.
 

### 2021-01-26 main.tex
A few more fixes

@@
 
-The \bfit{complement} of a graph $\gG=\tuple{\vG,\eG}$ is
-the graph $\compl\gG=\tuple{\vG,\compl\eG}$ where $vw\in\compl\eG$ iff
-$vw\notin\eG$.
+%The \bfit{complement} of a graph $\gG=\tuple{\vG,\eG}$ is
+%the graph $\compl\gG=\tuple{\vG,\compl\eG}$ where $vw\in\compl\eG$ iff
+%$vw\notin\eG$.
 
@@
 if $\gG=\gG_1+\gG_2$ for two non-empty graphs $\gG_1,\gG_2$, otherwise
-it is \bfit{connected}. It is \bfit{coconnected} if its complement is
-connected.
+it is \bfit{connected}.
+%It is \bfit{coconnected} if its complement is connected.
 
@@
 \item {\bf Simplify atoms.} After step 2, replace every predicate
-  $p(t_1 \cdots t_n)$ (resp. $\dual p(t_1 \cdots t_n)$) with a nullary
+  $pt_1 \ldots t_n$ (resp. $\dual{p}t_1 \ldots t_n$) with a nullary
   predicate symbol $p$ (resp.~$\dual p$)
@@
   this process preserves the linking and the dualizer. However, for
-  this, we have to extent the construction above to the $\cut$-rule,
+  this, we have to extend the construction above to the $\cut$-rule,
   and then show that linking and dualizer of a sequent proof $\Pi$ are
@@
 $\rr\in\set{\wrD,\wfaD}$. For $\rr=\acD$ it maps the vertices
-corresponding to the two atoms in the premise to vertex of the
+corresponding to the two atoms in the premise to the vertex of the
 contracted atom in the conclusion, and for
@@
   the induced map $\mapof{\rr}\colon\vgraphof Q\to\vgraphof P$ defines
-  a existential preserving graph homomorphism $\graphof Q\to\graphof
+  an existential-preserving graph homomorphism $\graphof Q\to\graphof
   P$ and a fibration on the corresponding binding graphs.  Therefore,
-  their composition $\mapof\Deri$ has the same properties fibration.
+  their composition $\mapof\Deri$ has the same properties of fibration.
 
@@
    We can now lift $\DDeri$ stepwise. First, observe that each line of
-   in $\DDeri$ is $\PE\fequ$-equivalent to the propositional encoding $\PE P$ of a
+   $\DDeri$ is $\PE\fequ$-equivalent to the propositional encoding $\PE P$ of a
    first-order formula $P$.  We now have to show
-   that each other instance of $\wrD$ in $\DDeri$ is indeed the image of a correct
+   that each instance of $\wrD$ in $\DDeri$ is indeed the image of a correct
    application of $\wD$ or $\wfaD$ in first-order logic.
@@
 composition and normalisation of first-order combinatorial
-proofs. Even in the propositional setting, the normalization of
+proofs. Even in the propositional setting, the normalisation of
 combinatorial proofs is underdeveloped. There exist two different
@@
 
-Nonetheless, we hope to get new insights in the normalization of
+Nonetheless, we hope to get new insights in the normalisation of
 classical first-order proofs through our work on combinatorial proofs.
@@
       or $x\vlor F$ for some formula $F$ and $x\in\VAR$, then this
-      instance of $\me$ can trivially be lifted, and and we can
+      instance of $\me$ can trivially be lifted, and we can
       proceed by induction hypothesis.

### 2021-01-26 main.tex
page break
fixes

@@
 \newcommand{\PEp}[1]{\tilde{#1}}
+\newcommand\fv{\textsf{\small fv}}
 
@@
   $$
-  \begin{tikzpicture}\cponeonformula
+  \begin{tikzpicture}\cptwoonformula
   \end{tikzpicture}
   \qquad
-  \begin{tikzpicture}\cptwoonformula
+  \begin{tikzpicture}\cponeonformula
   \end{tikzpicture}
@@
   \begin{tikzpicture}
-    \cponeinline
+    \cptwoinline
   \end{tikzpicture}
@@
   \begin{tikzpicture}
-    \cptwoinline
+    \cponeinline
   \end{tikzpicture}
@@
 FOCPs (taken from~\cite{hughes:fopws}), each above the formula it proves.
-The same FOCPs are shown in
-Figure~\ref{fig:cps-condensed} in a ``condensed form''.
+The same FOCPs are in
+Figure~\ref{fig:cps-condensed} in \emph{condensed form}, with the formula
+graph left implicit.
+%  (No information is lost, since 
+% atom/quantifier-occurrences in a formula
+% are in bijection with vertices of its graph.)
 %
@@
 
-In the course of this paper we will employ the
+We will sometimes employ the
 general (non-atomic) version of the contraction rule:
@@
 \begin{thm}\label{thm:decomposition}
-  For every derivation $\vlder{\FOKS}{\Deri}{A}{\ttt}$ there are $\fff$-free formulas $A_1,\ldots,A_5$, such that there is a derivation:
+  For every derivation $\vlder{\FOKS}{\Deri}{A}{\ttt}$ there are $\fff$-free formulas $A_1,\ldots,A_5$ and a derivation
   \begin{equation*}
@@
 decomposition.
-
+%
 %\begin{example}
@@
 %\end{example}
-
+%
 \begin{figure}
@@
   \end{figure}
-%
-There is a weaker version of Theorem~\ref{thm:decomposition} that will
+
+A weaker version of Theorem~\ref{thm:decomposition} will
 also be useful:
@@
 \begin{thm}\label{thm:decompositionA}
-  For every derivation $\upsmash{\vlder{\FOKS}{\Deri}{A}{\ttt}}$ there is a formula~$A_1$ not containing any occurrence of $\fff$, such that there is a derivation:
+  For every derivation $\rule{0ex}{4.7ex}\upsmash{\vlder{\FOKS}{\Deri}{A}{\ttt}}$
+there is a formula~$A'$ with no occurrence of $\fff$ and a derivation
   \begin{equation*}
@@
       \vlde{\set{\wrD,\cD,\fequ}}{}{A}{
-        \vlde{\FOMLS}{}{A_1}{
+        \vlde{\FOMLS}{}{A'}{
           \vlhy{\ttt}}}}
@@
 \end{thm}
-
-Let us now establish the connection between derivations in $\FOKS$ and
+%
+\noindent Here $A'$ corresponds to $A_3$ of Theorem~\ref{thm:decomposition}.
+
+We now establish the connection between derivations in $\FOKS$ and
 combinatorial proofs.
@@
 the derivation in Figure~\ref{fig:example-decompose} which corresponds
-to the right-most combinatorial proof in Figures~\ref{fig:cps}
+to the left-most combinatorial proof in Figures~\ref{fig:cps}
 and~\ref{fig:cps-condensed}.
@@
 every derivation can be transformed into that form, we can say that
-combinatorial proofs form a canonical proof representation for first-order
+combinatorial proofs provide a canonical proof representation for first-order
 logic, similarly to what proof nets are for linear
@@
 first-order combinatorial proofs which is simpler than the one given
-in~\cite{hughes:fopws}.
+in~\cite{hughes:fopws}, and improves with completeness being full
+(a surjection from syntactic KS1 proofs onto combinatorial proofs).
 
@@
 
-In this section we prove Theorems~\ref{thm:KS1},
+We prove Theorems~\ref{thm:KS1},
 \ref{thm:decomposition}, and~\ref{thm:decompositionA}, mainly by
@@
 
-In this section we show the equivalence of $\FOMLL$ and $\FOMLS$.
+% We show the equivalence of $\FOMLL$ and $\FOMLS$.
+% 
+% We show that $\FOMLL$ is equivalent to $\FOMLS$.
+We show that $\FOMLL$ and $\FOMLS$ are equivalent.
 
@@
 %%     \vlin{\cD}{}{\forall x.A}{
-%%       \vlin{\equiv}{(x \notin fv(\forall x.A))}{(\forall x.A) \vlor (\forall x.A)}{
+%%       \vlin{\equiv}{(x \notin \fv(\forall x.A))}{(\forall x.A) \vlor (\forall x.A)}{
 %%         \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor A)}{
@@
 
+Write $\fv(A)$ for the set of variables which occur free in $A$.
+
 Note that the instances of $\wrD,\cD$ in $\Deri_2$ are deep, but inside sequent contexts.
@@
   \vlin{\fequ}{}{\forall y.\forall x.A}{
-    \vlin{\wfaD}{(x \notin fv(\forall y.A))}{\forall x.\forall y.A}{
+    \vlin{\wfaD}{(x \notin \fv(\forall y.A))}{\forall x.\forall y.A}{
       \vlhy{\forall y.A}}}}
@@
 \vlderivation{
-  \vlin{\wfaD}{(x \notin fv(A))}{\forall y.\forall x.A}{
+  \vlin{\wfaD}{(x \notin \fv(A))}{\forall y.\forall x.A}{
     \vlhy{\forall y.A}}}$}
@@
   \vlin{\fequ}{}{\forall x.\forall y.A}{
-    \vlin{\wfaD}{(x \notin fv(A))}{\forall y.\forall x.A}{
+    \vlin{\wfaD}{(x \notin \fv(A))}{\forall y.\forall x.A}{
       \vlhy{\forall y.A}}}}
@@
 \vlderivation{
-  \vlin{\wfaD}{(x \notin fv(\forall y.A))}{\forall x.\forall y.A}{
+  \vlin{\wfaD}{(x \notin \fv(\forall y.A))}{\forall x.\forall y.A}{
     \vlhy{\forall y.A}}}$}
@@
   \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-    \vlin{\fequ}{(x \notin fv(B))}{(\forall x.\forall x.A) \vlor B}{
+    \vlin{\fequ}{(x \notin \fv(B))}{(\forall x.\forall x.A) \vlor B}{
       \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
@@
   \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{(x \notin fv(B))}{\forall x.\forall x.(A \vlor B)}{
+    \vlin{\fequ}{(x \notin \fv(B))}{\forall x.\forall x.(A \vlor B)}{
       \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
@@
   \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
-    \vlin{\fequ}{(x \notin fv(B \vlan D))}{\forall x.((A \vlan C) \vlor (B \vlan D))}{
+    \vlin{\fequ}{(x \notin \fv(B \vlan D))}{\forall x.((A \vlan C) \vlor (B \vlan D))}{
       \vlhy{(\forall x.(A \vlan C)) \vlor (B \vlan D)}}}}
@@
     \vlin{\acD}{}{\forall x.a}{
-      \vlin{\fequ}{(x \notin fv(a))}{\forall x.(a \vlor a)}{
+      \vlin{\fequ}{(x \notin \fv(a))}{\forall x.(a \vlor a)}{
         \vlin{\wrD}{}{(\forall x.a) \vlor a}{
@@
     \vlin{\acD}{}{\forall x.a}{
-      \vlin{\fequ}{(x \notin fv(a))}{\forall x.(a \vlor a)}{
+      \vlin{\fequ}{(x \notin \fv(a))}{\forall x.(a \vlor a)}{
         \vlin{\wrD}{}{a \vlor (\forall x.a)}{
@@
   \vlderivation{
-    \vlin{\wfaD}{(x \notin fv(a))}{\forall x.a}{
+    \vlin{\wfaD}{(x \notin \fv(a))}{\forall x.a}{
       \vlhy{a}}}
@@
 \end{prooftree}
-($x \notin fv(\Gamma)$)
+($x \notin \fv(\Gamma)$)
 \qquad

### 2021-01-26 main.tex
fixes

@@
    can now permute the $\wD$-instances in $\DDeri$ such that whenever
-   a rule instance $\rr_1$ depends on an instance $\rr_2$, then
+   a rule instance $\rr_1$ is in the scope of an instance $\rr_2$, then
    $\rr_2$ occurs below $\rr_1$ in $\DDeri$.
@@
   where $x$ occurs in $C\vlor D$. Then premise and conclusion are both
-  proposional encodings, but the whole derivation cannot be
-  lifted. However, since we demand that the the mapping is a fibration
-  (and therefore a momomorphism) on the binding graphs, there must be
+  propositional encodings, but the whole derivation cannot be
+  lifted. However, since we demand that the mapping is a fibration
+  (and therefore a homomorphism) on the binding graphs, there must be
   another instance of $\me$ further below in the derivation:

### 2021-01-26 main.tex
final stitches

--- 2021-01-26 main.tex
@@
 even though Hilbert was considering this problem as a possible 24th
-problem for his famous lecture~\cite{hilbert:00} in
-1900~\cite{thiele:03}, before proof theory existed as a mathematical
+problem~\cite{thiele:03} for his famous lecture in
+1900~\cite{hilbert:00}, before proof theory existed as a mathematical
 field.
@@
 \begin{definition}
-A \bfit{first-order graph} or \bfit{fograph} is a logical cograph with legal binders. The
+A \bfit{first-order graph} or \bfit{fograph} is a logical cograph in which all binders are legal. The
 \bfit{binding graph} of a fograph $\gG$ is the directed graph $\bG=\tuple{\vG,
@@
 Figure~\ref{fig:KS1} shows the inference rules for the deep inference
-system~$\FOKS$ that we introduce in this paper. It is a slight variation
-of the systems presented by Br\"unnler~\cite{brunnler:phd} and
-Ralph~\cite{ralph:phd} in their PhD-theses. The main differences are
-(i) the explicit presence of the $\mixr$-rule, (ii) a
-different choice of how the formula equivalence $\fequ$ is defined,
-and (iii) an explicit rule for the equivalence.
+system~$\FOKS$ that we introduce in this paper. It is a slight
+variation of the systems presented by Br\"unnler~\cite{brunnler:phd}
+and Ralph~\cite{ralph:phd} in their PhD-theses. The main differences
+are (i) the explicit presence of the $\mixr$-rule, (ii) a different
+choice of how the formula equivalence $\fequ$ is defined, (iii) an
+explicit rule for the equivalence, and (iv) new inference rules
+$\wfaD$ and $\cfaD$. The reason behind these design choices is to
+obtain the correspondence with combinatorial proofs and the full
+completeness result.
 
@@
 
-We will sometimes employ the
+We will for some results also employ the
 general (non-atomic) version of the contraction rule:
@@
   that proof by $\forall x$ and then compose the following derivation:
-  \begin{center}\vspace{-2ex}\begin{math}
+  \begin{center}\vspace{-2ex}\scalebox{.9}{\begin{math}
     \vlderivation{
@@
             \vlhy{\ttt}}}}}
-  \end{math}\end{center}
+  \end{math}}\end{center}
   where we can apply the $\fequ$-rule because $x$ is not free in $\Delta$.
@@
 
+\begin{remark}
+  Observe that Lemma~\ref{lem:cw-atomic} would also hold with the rules $\wfaD$ and~$\cfaD$ removed.
+\end{remark}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   straightforward case analysis. However, unlike most other rule
-  permutations in this paper this has not been done before in the deep
+  permutations in this paper, this has not been done before in the deep
   inference literature. For this reason, we give the full case
@@
 %% rectified.
-
+%
 %% \begin{lemma}
@@
 %% \end{proof}
-
+%
 %% Hence,
@@
   have $\fequ$ incorporating associativity and commutativity of
-  $\vlan$ and $\vlor$.} \vadjust{\vskip-2ex}
+  $\vlan$ and $\vlor$.} \vadjust{\vskip-4ex}
   \begin{equation*}
@@
   binders dependent on that $y_j$. It is easy to see how $\DDeri_1$ is
-  constructed, and for $\DDeri_2$ see,
+  constructed. The construction of $\DDeri_2$, using $\sw$ and $\fequ$, is standard, see,
   e.g. \cite{ATS:esslli2019,gug:str:01,brunnler:tiu:01,dissvonlutz}. Then, every
@@
   this process preserves the linking and the dualizer. However, for
-  this, we have to extend the construction above to the $\cut$-rule,
+  this, we have to extend the construction from the previous subsection to the $\cut$-rule,
   and then show that linking and dualizer of a sequent proof $\Pi$ are
@@
 this reason we define here rectified versions $\rectif\cfaD$,  $\rectif\mfaD$ and
-$\rectif\mexD$, shown below:%\vadjust{\vskip-1ex}
-\begin{equation*}
-  \scalebox{.9}{$
+$\rectif\mexD$, shown below:\vadjust{\vskip-1ex}
+\begin{equation*}
+  \scalebox{1}{$
   \vlinf{\rectif\cfaD}{}{\Scons{\forall x.Ax}}{\Scons{\forall y.\forall x.Ax}}
@@
   and $H$ be formulas with $\graphof G=\gG$ and $\graphof H=\gH$. Then
-  There is a derivation $\vlder{\set{\wrD,\wfaD,\fequ}}{}{H}{G}$.
+  there is a derivation $\vlder{\set{\wrD,\wfaD,\fequ}}{\Deri}{H}{G}$.
 \end{lemma}
@@
    $\vlder{\set{\wrD,\PE\fequ}}{\DDeri}{\PE H}{\PE G}$. In order to
-   lift $\DDeri$, we might need to reorganize the instances of
+   lift $\DDeri$, we need to reorganize the instances of
    $\wD$. If $H$ contains a subformula $\forall x.A$ which is not
@@
    can now permute the $\wD$-instances in $\DDeri$ such that whenever
-   a rule instance $\rr_1$ depends on an instance $\rr_2$, then
+   a rule instance $\rr_1$ is in the scope on an instance $\rr_2$, then
    $\rr_2$ occurs below $\rr_1$ in $\DDeri$.
-   We can now lift $\DDeri$ stepwise. First, observe that each line of
+   Then we can lift $\DDeri$ stepwise. First, observe that each line of
    $\DDeri$ is $\PE\fequ$-equivalent to the propositional encoding $\PE P$ of a
@@
    \begin{equation*}
+     \scalebox{1}{$
      \vlinf{\wD}{}{\PE S\cons{x\vlor \PE A}}{\PE S\cons{\PE A}}
@@
      \vlinf{\wD}{}{\PE S\cons{(x\vlor \PE B)\vlor \PE A}}{\PE S\cons{\PE A}}
+     $}
    \end{equation*}
@@
    \begin{equation*}
+      \scalebox{1}{$
     \vlinf{\wfaD}{}{S\cons{\forall x. A}}{S\cons{A}}
@@
      \vlinf{\wD}{}{S\cons{(\forall x. B)\vlor A}}{S\cons{A}}
+     $}
    \end{equation*}
@@
 combinatorial proofs is underdeveloped. There exist two different
-procedures for cut elimination~\cite{hughes:invar,str:fscd17}, but
-both have their insufficiencies, and there is no general theory.
+procedures for cut elimination for combinatorial proofs in classical
+propositional logic~\cite{hughes:invar,str:fscd17}, but both have
+their insufficiencies, and they have not been extended to other
+logics.
 
@@
 
-\vskip3em
+%\vskip3em
+
+\clearpage
 

### 2021-03-13 resp-email.tex
Add the response

----------------------- REVIEW 1 ---------------------
SUBMISSION: 51
TITLE: Combinatorial Proofs and Decomposition Theorems for First-order Logic
AUTHORS: Dominic Hughes, Lutz Straßburger and Jui-Hsuan Wu

----------- Overall evaluation -----------
This paper presents a new proof system, called combinatorial proofs, for FO (without the equality predicate).
The author(s) shows that it is complete and sound and "syntax free".
Intuitively, combinatorial proofs are proofs/derivations that are represented as graph homomorophisms.
This is in contrast with traditional systems (such as sequent calculus, resolution, etc)
which are syntax based.

The motivation is that combinatorial proofs can be used as the notion for equivalence between derivations in different systems.
That is, two derivations in different systems can be considered ``equal'' if they are translated into the same combinatorial proof.

Similar result has been established by Hughes in [18], which is published as ArXiv paper.
But the proof in the current paper is much simpler.
It also allows a translation from combinatorial proofs back to syntactic proofs.
It should be stressed that the paper only considers FO without the equality predicate.

The outline of the paper is as follows.
Sect. II introduces sequent calculus which is known to be complete and sound.
Sect. III introduces fographs, which is a way of representing FO formulas as graphs.
Sect. IV introduces fonets and combinatorial proofs, where fonets themselves are graph representations of derivations.
Sect. V introduces a new system called KS1.
Sect. VI contains the statement of the main results (Theorem 19) along with its decomposition result for the system KS1.
Roughly, the decomposition result states that every derivation in KS1 can be decomposed into two parts:
the first part uses only the "linear fragment" of KS1 and the second part uses the rules outside the linear fragment and the equivalent rule \equiv.
Theorem 19 states that combinatorial proofs are complete and sound,
where completeness is obtained by applying the decomposition result and show that each part of the derivations can be translated into Combinatorial proofs.
Sect. VII presents the translation between the sequent calculus and KS1.
Sect. VIII shows the construction between fonets and proofs using only the linear fragment of KS1.
Sect. IX shows the construction between fonets and proofs using rules outside the linear fragment.

I find the result interesting and I think it fits LICS well.
The technical presentation is reasonable enough for me to be convinced of its correctness.

I have some complaints though.

a) The presentation is very dry.
It is mainly a sequence of definitions, lemmas, theorems, proofs with very little justification/explanation in between.
For example, fonets, which I think is the most important part, are presented as a definition without any intuitive explanation
on how they can be used to represent proofs. (See below for more details.)
Some examples are presented in Figure 4 and 5, but I find them useless due to lack of explanation.

I also suggest the author(s) to provide some broad overview of the proof.
There is also no description of "the organization of the paper".
The readers are left to figure out themselves how sections in the paper connect to each other.

b) Some of the definitions, esp. in Sect. III and IV, are very confusing.
(See below for more details.)
I have to go back to [18] which use almost the same terminology and definition as the current paper,
and I find it easier to understand them in [18].

More detailed comments:

I think it should be stressed early (as early as in the abstract) that the paper is about FO without the equality predicate,
since it is usually considered in standard proof systems.

p.3, left: The notion of colored graphs here does not require adjacent vertices to have different colors, but the one in [18] does.
Is there a mistake here, since the one in [18] requires different colors?

-> There is no mistake. The requirement mentioned here is never used in the
paper.

p.3, right: I suppose for fographs it is possible that different vertices have the same label?
I also find the definition of fographs a bit confusing, since it starts with abstract graph theoretic properties of fographs,
before presenting the construction of fographs from formulas.
I suggest to reverse it, by first presenting the construction of fographs (from formulas) before enumerating all the properties of fographs.
In fact, this is how forgraphs are presented in [18].

->

p3,right: What about the atoms True and False in the fographs?
They are part of the definition of FO formulas, but are they really needed?
Almost all results in the paper require that False does not appear in the proof.
Maybe they can be omitted.

-> The atoms are needed for establishing the equivalence between KS1 and MLS1*.
(TO CHECK)

p.4, left: The notion of "dual" is not defined yet.
Again, it is already defined nicely in [18].
I also suggest to present here some intuitive explanation on how fonets represent proofs.
The same for the other notions here such as links, leaps, (bi)fibration, skew (bi)fibration, and their relations with derivations in KS1 and LK1.
Figures 4 and 5 can be easily expand to provide intuitive explanation.

-> Yes, the notion of duality is implicitly suggested by the notation
\overline{p}.

p.6, Theorem 19: I think it is safe to assume that formulas are rectified, thus, there is no need for \hat{A} here.
Otherwise, there will be too many notations to remember here.

->

p.7, Lemma 22: \overline{S{A}} is not defined yet.
I assume it is the complement of the corresponding formula for S{A}?

-> Yes, it is.

p.10, right: A\cdot here is just "variable renaming"?

-> We use this notation to simplify the rectified version of rules for
quantifiers. Variable renaming is a more general notion as it allows rename more
than one variable.

p.10, left: Why "resource management" in the title of Sect. IX?

-> Like combinatorial proofs for propositional logic, the skew bifibration part
corresponds to the linear part of the sequent proof. That's why we mention
resource management in the title though it is not explicitly discussed in the
paper.

p.11, right: on full fograph homomorphism.
There is something missing here since the homomorphism is not necessarily injective?
Or, it is meant to be "strong" homomorphism?

-> The notion of fullness is well defined in category theory and that is exactly
what we need here.

----------------------- REVIEW 2 ---------------------
SUBMISSION: 51
TITLE: Combinatorial Proofs and Decomposition Theorems for First-order Logic
AUTHORS: Dominic Hughes, Lutz Straßburger and Jui-Hsuan Wu

----------- Overall evaluation -----------
This paper addresses an important question in proof theory -- when are two proofs considered equivalent. In this case, the logic in question is classical first-order logic. This paper builds on a notion of classical proofs, developed by Hughes, that is based on a graph structure called first-order nets (fonets). Greatly simplified, a fonet can be seen as 'a formula with links between dual atoms', with the formula part represented as a graph encoding series-parallel orders.
Hughes's technical report (cited as [19]) on this subject lays out much of the foundations for fonets, including a soundness and a completeness theorem w.r.t. a version of LK. However, there is no direct 'sequentialization' theorem for fonets, in the sense that it is not possible to directly extract a sequent proof from a fonet. This paper proposes a different approach to sequentialization by relating fonets, not with sequent calculus, but with a deep-inference proof system called KS1, formulated in the calculus of structures (CoS).

A key technical idea to obtain a tight correspondence between fonets and KS1 is to first obtain a decomposition result for KS1, which decomposes KS1 proofs into a 'linear' part, followed by a classical part in contraction and weakening are applied, and quantifier scopes are rearranged.
The correspondence between fonets and the linear part of the decomposed proof is then proved by adapting known techniques for proving the correspondence between first-order MLL (multiplicative linear logic) and fonets; whereas the classical part requires new proof techniques but is more manageable.

The sequentialization theorem is one of the important questions surrounding proofnet-like proof representations, so in this sense the result of the paper is of some significance. It is possible to have a proofnet calculi that have no corresponding sequent proofs (e.g., Retore's pomset logic). In this case, it is unlikely sequentialization, in the sense of directly translating fonet to cut-free sequent proofs, is possible. A compromise here is to use a different proof calculus, based on deep inference. In principle, we can translate deep inference proofs to cut-free sequent proofs, using cuts and cut-elimination, but this would likely obscure the structures of the original fonets.

Another interesting aspect of the paper is that it contains probably one of the more interesting applications of the decomposition theorem for calculus of structures. The technical results are believable. I didn't check all the proofs, but a lot of intermediate lemmas, particularly those dealing with decomposition are mostly proved along the standard lines in this area so I don't particularly doubt their correctness.

On the negative side: there is still no theory of cut-elimination for fonets.
The paper is very dense, with lots of technical lemmas that are hand-waived through. I think it might be better to just omit some of these lemmas and dedicate more space to provide intuitive examples. A slight nitpick on notations for proofs/derivations: the vertical figures for derivations of CoS waste a lot of space that could have been used to improve presentation.

Overall this looks like a solid paper with an interesting and non-trivial result. I recommend acceptance.

Minor comments for the author(s):
- Lemma 30: you cite [35] for the proof of this lemma, but as far as I know [35] does not discuss first-order quantifiers. I can see a possibility of quantifiers interferring with the atomic interaction rule. For example,

(forall x. A) \/ B
-------------------
forall x.(A \/ B)
---------------------------------
forall x.(A \/ (px \/ ~px) /\ B))

where x is vacuous in B. It doesn't seem straightforward that ai can be permuted directly above structural equivalence.

->

----------------------- REVIEW 3 ---------------------
SUBMISSION: 51
TITLE: Combinatorial Proofs and Decomposition Theorems for First-order Logic
AUTHORS: Dominic Hughes, Lutz Straßburger and Jui-Hsuan Wu

----------- Overall evaluation -----------
The paper is concerned with canonically representing first-order logic proofs in various proof systems in a more abstract system of "combinatorial proofs". This is a fundamental question in proof theory and hence in computer science. The contribution of the paper is a new deep inference system KS1  for first-order logic. KS1 is closer to combinatorial proofs and the paper provides simpler and more complete results linking the two systems.

  The paper is well written and an enjoyable read. Though not an expert, I believe the contribution is significant and deserves acceptance at LICS.

### 2021-03-14 lics2021-rebuttal-51.txt
another rebuttal version

All three reviewers see the paper in a positive light, and we thank
them for their feedback. The complaints of reviewer 1 concern only the
presentation, which can easily improved with all the helpful comments
of reviewer 1.

Below we give more detailed answers to the questions raised by
reviewers 1 and 2.

*********************************************************************
Answer to review 1:
===================

We are very grateful for the detailed comments, and we will happily
follow all suggestions. In particular, we will include an outline of
the paper, give more intuitive explanations and a broader overview of
the proof. Also the remark about equality is helpful.

> Question p.3: require that adjacent vertices to have different colors?

Indeed, in [18] there is this requirement, but it is not needed
because of the correctness criterion. Therefore we did not include it.

> Question p.3: can different vertices have the same label?

Yes.

> Question p.3: What about the atoms True and False in the fographs?

Indeed, in classical logic they are not needed for semantic
soundness and completeness, because

True = a v -a  and  False = a ^ -a

However, they are part of the language, and they also make the proof
systems simpler to use. Therefore we decided to include them.

> Question p.7: is \overline{S{A}} the complement of S{A} ?

Yes.

> Question p.10: A\cdot is variable renaming?

Yes.

> Question p.10: why "resource management"?

We see a combinatorial proof as a way to separate the linear part of a
proof (in the sense of linear logic) from the resource management of a
proof (in the sense that contraction and weakening duplicate and
delete resources). As this section is about contraction and weakening,
we chose this title. We agree that this needs to be better explained.

> Question p.11: "strong" homomorphism?

No, we do not have this condition. Note that this lemma is only about
weakening, and therefore the needed conditions are full and
injective. The next lemma is about contraction, where we need
surjectivity.

*********************************************************************
Answer to review 2:
===================

Question about the proof of Lemma 30:

Indeed, the structural equivalences concerning the quantifiers are not
discussed in [35]. But in our case, the equivalences concerning the
quantifiers are admissible in the system without the exists-rule. In
particular, in the example given in the review, a proof of

(forall x. A) \/ B

can be straightforwardly transformed into a proof of

forall x. (A \/ B)

(if x is vacuous in B)

We agree that this should be explained better.

### 2021-03-15 lics2021-rebuttal-51.txt
tweaked rebuttal

@@
 We are very grateful for the detailed comments, and we will happily
-follow all suggestions. In particular, we will include an outline of
-the paper, give more intuitive explanations and a broader overview of
-the proof. Also the remark about equality is helpful.
+follow all suggestions. We will include an outline of the paper, give
+more intuitive explanations, and provide a broad overview of
+the proof. The remark about equality is helpful.
 
@@
 
-Indeed, in [18] there is this requirement, but it is not needed
-because of the correctness criterion. Therefore we did not include it.
+It was included in [18] because it is part of the standard definition of
+colouring in graph theory. However, it is redundant, hence optional,
+since it is implied by the preclusion of bimatchings: if vw is edge
+between like-coloured vertices (v~w), then {v,w} is a bimatching.
 
@@
 
-Yes.
+Yes. (See the left of Fig. 1, for example.)
 
@@
 However, they are part of the language, and they also make the proof
-systems simpler to use. Therefore we decided to include them.
+systems simpler to use. Therefore we kept them.
 
@@
 
-No, we do not have this condition. Note that this lemma is only about
-weakening, and therefore the needed conditions are full and
-injective. The next lemma is about contraction, where we need
-surjectivity.
+No, we do not have this condition. This lemma is only about
+weakening, so the requisite conditions are full and injective. The next
+lemma is about contraction, where we need surjectivity.
 

### 2021-03-15 lics2021-rebuttal-51.txt
???

--- 2021-03-14 lics2021-rebuttal-51.txt
@@
 the paper, give more intuitive explanations and a broader overview of
-the proof. Also the remark about equality is helpful.
+the main proof. Also the remark about equality is helpful.
 
@@
 delete resources). As this section is about contraction and weakening,
-we chose this title. We agree that this needs to be better explained.
+we chose this title. We now see that this needs to be better
+explained.
 

### 2021-03-15 lics2021-rebuttal-51.txt

--- 2021-03-15 lics2021-rebuttal-51.txt
@@
 more intuitive explanations, and provide a broad overview of
-the proof. The remark about equality is helpful.
+the main proof. The remark about equality is helpful.
 

### 2021-04-21 LICS2021-final.tex
starting the final version
tiny modifications

--- 2021-01-26 main.tex
@@
 %%line and pagenumbers to be removed for final version
-\usepackage[switch]{lineno}
+%\usepackage[switch]{lineno}
 \pagestyle{plain}
@@
 % Do not put math or special symbols in the title.
-\title{Combinatorial Proofs and Decomposition Theorems for First-order Logic\vspace{-3ex}}
+\title{Combinatorial Proofs and Decomposition Theorems for First-order Logic}
 
@@
 
-%% \author{\IEEEauthorblockN{Dominic J. D. Hughes}
-%% \IEEEauthorblockA{}
-%% \and
-%% \IEEEauthorblockN{Lutz Straßburger}
-%% \IEEEauthorblockA{Inria, Equipe Partout\\
-%% Ecole Polytechnique, LIX \\ %UMR 7161\\
-%% France}
-%% \and
-%% \IEEEauthorblockN{Jui-Hsuan Wu}
-%% \IEEEauthorblockA{Ecole Normale Supérieure\\
-%% France}}
+\author{\IEEEauthorblockN{Dominic J. D. Hughes}
+\IEEEauthorblockA{}
+\and
+\IEEEauthorblockN{Lutz Straßburger}
+\IEEEauthorblockA{Inria, Equipe Partout\\
+Ecole Polytechnique, LIX \\ %UMR 7161\\
+France}
+\and
+\IEEEauthorblockN{Jui-Hsuan Wu}
+\IEEEauthorblockA{Ecole Normale Supérieure\\
+France}}
 
@@
 % creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\linenumbers
+%\IEEEpeerreviewmaketitle
+
+%\linenumbers
 
@@
 $\PRED=\set{p,q,\ldots}$ of predicate symbols. Each function symbol and
-each predicate symbol has a finite arity. The grammars below generate
+each predicate symbol has a finite arity. Each predicate symbol $p$ has a
+\bfit{dual}
+$\dual{p}$. The grammars below generate
 the set $\TERM$ of \bfit{terms}, denoted by $s,t,u,\ldots$, the set
@@
    can now permute the $\wD$-instances in $\DDeri$ such that whenever
-   a rule instance $\rr_1$ is in the scope on an instance $\rr_2$, then
+   a rule instance $\rr_1$ is in the scope of an instance $\rr_2$, then
    $\rr_2$ occurs below $\rr_1$ in $\DDeri$.

### 2021-04-25 LICS2021-final-for-arxiv-HAL.tex
almost final

--- 2021-04-21 LICS2021-final.tex
@@
 
-%%%%% DOMINIC: THIS IS ONLY USED FOR THE TWIN COLLAPSE EXAMPLE; PACKAGE CAN BE KILLED
 %\usepackage{adjustbox}%% CONFLICT %% easier to align boxes (such as proofs) to top with, e.g. \begin{adjustbox}{valign=t,raise=-.6ex} <STUFF> \end{adjustbox} 
@@
 
-\author{\IEEEauthorblockN{Dominic J. D. Hughes}
-\IEEEauthorblockA{}
+\author{
+  \IEEEauthorblockN{Dominic J.\ D.\ Hughes}
+  \IEEEauthorblockA{%
+	Logic Group\\
+	U.C.\ Berkeley\\
+	USA}
 \and
@@
 
+%% \newcommand{\longer}[2]{#1}
+%% \newcommand{\shorter}[2]{#2}
+
+%% %\let\choice=\longer
+%% \let\choice=\shorter
+
+\IEEEoverridecommandlockouts
+\IEEEpubid{\makebox[\columnwidth]{\emph{[Long version of the LICS 2021 paper, with proofs in the appendix.]}\hfill}
+    \hspace{\columnsep}\makebox[\columnwidth]{ }}
+%\IEEEpubid{\makebox[\columnwidth]{978-1-6654-4895-6/21/\$31.00~
+%\copyright2021 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
+
 % make the title area
@@
   We uncover a close relationship between combinatorial and
-  syntactic proofs for first-order logic. Whereas syntactic proofs are
+  syntactic proofs for first-order logic (without equality). Whereas syntactic proofs are
   formalized in a deductive proof system based on inference rules,
@@
 
-%\todo{Examples,examples,examples}
 \section{Introduction}
@@
 which translate to the same first-order combinatorial proof (centre).%
-% two syntactic proofs of 
-% $\protect\peirceformula$,
-% in the sequent calculus (above)
-% and in the calculus of structures (below),
-% which translate to the same propositional combinatorial proof (centre).
-% %
-% Right:
-% two syntactic proofs of 
-% $\protect\veedrinkerformula$,
-% in the sequent calculus (above)
-% and the new calculus $\FOKS$ introduced in this paper (below),
-% which translate to the same first-order combinatorial proof (centre).%
 }\label{fig:translate}\vspace{-4ex}\end{figure}%
@@
 %
-% \begin{center}\vspace{.5ex}\begin{tikzpicture}\newcommand\radius{2.3}
-%   \begin{scope}[shift={(-\radius,0)}]{\peircecp}\end{scope}
-%   \begin{scope}[shift={(\radius,0)}]{\drinkerfibcoloured}\end{scope}
-% \end{tikzpicture}\vspace{0ex}\end{center}
-% %
-% 
-% \begin{equation*}
-%   \scalebox{.7}{$\lkdrinkerproof
-% %\qquad
-% \ksonedrinkerproof
-% $}
-% \end{equation*}
-% 
-% \juihsuan{LK1 and KS1 proofs of Peirce's law and LK1 proof of drinker formula}
-% \lutz{can you also do the KS1 for the drinker?}
-% \juihsuan{done}
 
@@
 ``drinker paradox'' $\drinkerformula=\veedrinkerformula$ is shown on the
-right of Fig.\,\ref{fig:translate}, %\todo{wrong implies symbol in drinkerformula?}
+right of Fig.\,\ref{fig:translate}, 
 a homomorphism from a partially coloured graph to a labelled graph.
@@
 \emph{sequentializable} \cite{girard:87} nor
-\emph{full}~\cite{abramsky:jagadeesan:94}. %\dominic{ok to say sequentializable too?}
+\emph{full}~\cite{abramsky:jagadeesan:94}. 
 %
@@
 
-% \subsection{Pictures that could be used elsewhere in the paper}
-% 
-% 
-% Condensed combinatorial proof of drinker formula(s):
-% %
-% \begin{center}\vspace{3ex}\begin{math}
-% \begin{tikzpicture}
-% \drinkerInline
-% \end{tikzpicture}
-% \hspace{10ex}
-% \begin{tikzpicture}
-% \veedrinkerInline
-% \end{tikzpicture}\end{math}\end{center}
-
-%%\figcps Fig.\,\ref{fig:cps} is a floating figure with four combinatorial proofs.
-
-%%\figcpscondensed Fig.\,\ref{fig:cps-condensed} is a floating figure with the condensed forms of the four combinatorial proofs in Fig.\,\ref{fig:cps}.
-
-% Illustrating why we need to collapse twins during contraction, to preserve the target as a fograph:
-% %
-% \twincollapsepic
-% %
-% Aligning both $\singleton{}\mkern4mu\singleton[red]{}$ and
-% $\singleton{}\mkern4mu\singleton[blue]{}$ over
-% a single copy of $\forall y\mkern2mu\py$
-% results in two uncoloured vertices
-% \raisebox{2pt}[0ex][0ex]{$\column{\singleton{}\\[-1.6ex]\singleton{}}$\hspace{-2pt}}
-% over $\forall y$.
-% %
-% The cover therefore fails to be a fograph: both uncoloured vertices are implicitly labelled with $y$ and
-% so are outer $y$-binders in the scope of each other.
-% %
-% The correct operation is shown above-right,
-% in which the troublesome pair is collapsed to a single uncoloured vertex $\singleton{}$ over $\forall y$.
+\medskip
+\noindent
+    {\bf Outline:} This paper has three parts. First,
+    in Sections~\ref{sec:fologic}--\ref{sec:foks} we present the
+    preliminaries on first-order logic, first-order graphs,
+    first-order combinatorial proofs, and the first-order proof system
+    $\FOKS$. Second, in Section~\ref{sec:main} we state the main
+    results. And third, in
+    Sections~\ref{sec:LK1-KS1}--\ref{sec:summary} we give their
+    proofs.
 
@@
 \subsection{Sequent Calculus $\FOLK$}
+
+\bfit{Sequents}, denoted by $\Gamma,\Delta,\ldots$, are finite
+multisets of formulas, written as lists, separated by comma. The
+\bfit{corresponding formula} of a (non-empty) sequent $\Gamma=A_1,A_2,\ldots,A_n$
+is the disjunction of its formulas: $\form\Gamma=A_1\vlor
+A_2\vlor\cdots\vlor A_n$. A sequent is \bfit{rectified} iff its
+corresponding formula is.
+
+In this paper we use the sequent calculus $\FOLK$, shown in
+Figure~\ref{fig:LK1}, which is a one-sided variant of Gentzen's
+original calculus~\cite{gentzen:35:I} for first-order logic. To
+simplify some technicalities later in this paper, we include
+the $\mixr$-rule.
+%
+\begin{thm}
+  $\FOLK$ is sound and complete for first-order logic.
+\end{thm}
+%
+\noindent For a proof, see any standard textbook, e.g.~\cite{TS:00}.
+
+The linear fragment of $\FOLK$, i.e., the fragment without the rules
+$\conr$ (\emph{contraction}) and $\weakr$ (\emph{weakening}) defines
+\emph{first-order multiplicative linear
+logic}~\cite{girard:87,girard:88} \emph{with
+mix}~\cite{fleury:retore:94,bellin:97}~(MLL1+mix). We denote that
+system here with $\FOMLL$ (shown in Figure~\ref{fig:LK1} in the dashed
+box).
+
+We will use the cut elimination theorem. The \bfit{cut} rule is
+\begin{equation}
+  \vliinf{\cutr}{}{\sqn{\Gamma,\Delta}}{\sqn{\Gamma,A}}{\sqn{\dual A,\Delta}}
+\end{equation}
+
+\begin{thm}
+  \label{thm:cutelim}
+  If a sequent $\sqn\Gamma$ is provable in $\FOLKcut$ then it is also
+  provable in $\FOLK$. Furthermore, if $\sqn\Gamma$ is provable in
+  $\FOMLLcut$ then it is also provable in $\FOMLL$.
+\end{thm}
+%
+\noindent As before, this is standard, see e.g.~\cite{TS:00} for a proof.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Preliminaries: First-order Graphs}\label{sec:fographs}
+
+\subsection{Graphs}
+
+A \bfit{graph} $\gG=\tuple{\vG,\eG}$ is a pair where $\vG$ is a finite
+set of \bfit{vertices} and $\eG$ is a finite set of \bfit{edges},
+which are two-element subsets of $\vG$. We write $vw$ for an edge
+$\set{v,w}$.
+
+Let $\gG=\tuple{\vG,\eG}$ and $\gH=\tuple{\vH,\eH}$ be graphs such
+that $\vG\cap\vH=\emptyset$. A \bfit{homomorphism}
+$\phi\colon\gG\to\gH$ is a function $\phi\colon\vG\to\vH$ such that if
+$vw\in\eG$ then $\phi(v)\phi(w)\in\eH$. The \bfit{union} $\gG +\gH$ is
+the graph $\tuple{\vG \cup\vH,\eG\cup \eH}$ and the \bfit{join} $\gG
+\times \gH$ is the graph $\tuple{\vG \cup\vH,\eG \cup \eH \cup \set{vw
+\mid v \in \vG, w \in \vH}}$.  A graph $\gG$ is \bfit{disconnected}
+if $\gG=\gG_1+\gG_2$ for two non-empty graphs $\gG_1,\gG_2$, otherwise
+it is \bfit{connected}.
+%It is \bfit{coconnected} if its complement is connected.
+
+A graph $\gG$ is \bfit{labelled} in a set $L$ if each vertex $v\in\vG$
+has an element $\labelof v\in L$ associated with it, its \bfit{label}.
+A graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
+equivalence relation $\linkingof\gG$ on $\vG$; each equivalence class
+is a \bfit{colour}.\footnote{In~\cite{hughes:fopws} it is also
+required that adjacent vertices have different colours, because it
+is part of the standard definition of colouring in graph
+theory.
+However, this condition is redundant (and therefore ommitted here), since it is implied
+by the preclusion of bimatchings in the next section.}
+%Therefore we do not have this additional condition here.}
+A \bfit{vertex renaming} of
+$\gG=\tuple{\vG,\eG}$ along a bijection
+$(\hat\cdot)\colon\vG\to\hat\vG$ is the graph
+$\hat\gG=\tuple{\hat\vG,\set{\hat v\hat w\mid vw\in\eG}}$, with
+colouring and/or labelling inherited (i.e., $\hat v\samecol\hat w$ if
+$v\samecol w$, and $\ell(\hat v)=\ell(v)$). Following standard graph
+theory, we identify graphs modulo vertex renaming.
+
+A \bfit{directed graph} $\gG =\tuple{\vG,\eG}$ is a set $\vG$ of
+\bfit{vertices} and a set $\eG\subseteq \vG\times\vG$ of \bfit{direct edges}.
+A \bfit{directed graph homomorphism}
+$\phi\colon\tuple{\vG,\eG}\to\tuple{\vH,\eH}$ is a function $\phi\colon\vG\to\vH$ such that if
+$\pair{v,w}\in\eG$ then $\pair{\phi(v),\phi(w)}\in\eH$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\bfit{Sequents}, denoted by $\Gamma,\Delta,\ldots$, are finite
-multisets of formulas, written as lists, separated by comma. The
-\bfit{corresponding formula} of a (non-empty) sequent $\Gamma=A_1,A_2,\ldots,A_n$
-is the disjunction of its formulas: $\form\Gamma=A_1\vlor
-A_2\vlor\cdots\vlor A_n$. A sequent is \bfit{rectified} iff its
-corresponding formula is.
-%\dominic{I changed fm$(\Gamma)$ to $\form\Gamma$,
-%easier for referee to understand/intuit/remember later in the paper}
-
-In this paper we use the sequent calculus $\FOLK$, shown in
-Figure~\ref{fig:LK1}, which is a one-sided variant of Gentzen's
-original calculus~\cite{gentzen:35:I} for first-order logic. To
-simplify some technicalities later in this paper, we include
-the $\mixr$-rule.
-%
-\begin{thm}
-  $\FOLK$ is sound and complete for first-order logic.
-\end{thm}
-%
-\noindent For a proof, see any standard textbook, e.g.~\cite{TS:00}.
-
-The linear fragment of $\FOLK$, i.e., the fragment without the rules
-$\conr$ (\emph{contraction}) and $\weakr$ (\emph{weakening}) defines
-\emph{first-order multiplicative linear
-logic}~\cite{girard:87,girard:88} \emph{with
-mix}~\cite{fleury:retore:94,bellin:97}~(MLL1+mix). We denote that
-system here with $\FOMLL$ (shown in Figure~\ref{fig:LK1} in the dashed
-box).
-
-We will use the cut elimination theorem. The \bfit{cut} rule is
-\begin{equation}
-  \vliinf{\cutr}{}{\sqn{\Gamma,\Delta}}{\sqn{\Gamma,A}}{\sqn{\dual A,\Delta}}
-\end{equation}
-
-\begin{thm}
-  \label{thm:cutelim}
-  If a sequent $\sqn\Gamma$ is provable in $\FOLKcut$ then it is also
-  provable in $\FOLK$. Furthermore, if $\sqn\Gamma$ is provable in
-  $\FOMLLcut$ then it is also provable in $\FOMLL$.
-\end{thm}
-%
-\noindent As before, this is standard, see e.g.~\cite{TS:00} for a proof.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Preliminaries: First-order Graphs}\label{sec:fographs}
-
-\subsection{Graphs}
-
-A \bfit{graph} $\gG=\tuple{\vG,\eG}$ is a pair where $\vG$ is a finite
-set of \bfit{vertices} and $\eG$ is a finite set of \bfit{edges},
-which are two-element subsets of $\vG$. We write $vw$ for an edge
-$\set{v,w}$.
-
-%The \bfit{complement} of a graph $\gG=\tuple{\vG,\eG}$ is
-%the graph $\compl\gG=\tuple{\vG,\compl\eG}$ where $vw\in\compl\eG$ iff
-%$vw\notin\eG$.
-
-Let $\gG=\tuple{\vG,\eG}$ and $\gH=\tuple{\vH,\eH}$ be graphs such
-that $\vG\cap\vH=\emptyset$. A \bfit{homomorphism}
-$\phi\colon\gG\to\gH$ is a function $\phi\colon\vG\to\vH$ such that if
-$vw\in\eG$ then $\phi(v)\phi(w)\in\eH$. The \bfit{union} $\gG +\gH$ is
-the graph $\tuple{\vG \cup\vH,\eG\cup \eH}$ and the \bfit{join} $\gG
-\times \gH$ is the graph $\tuple{\vG \cup\vH,\eG \cup \eH \cup \set{vw
-\mid v \in \vG, w \in \vH}}$.  A graph $\gG$ is \bfit{disconnected}
-if $\gG=\gG_1+\gG_2$ for two non-empty graphs $\gG_1,\gG_2$, otherwise
-it is \bfit{connected}.
-%It is \bfit{coconnected} if its complement is connected.
-
-A graph $\gG$ is \bfit{labelled} in a set $L$ if each vertex $v\in\vG$
-has an element $\labelof v\in L$ associated with it, its \bfit{label}.  A
-graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
-equivalence relation $\linkingof\gG$ on $\vG$; each equivalence class is a
-\bfit{colour}.  A \bfit{vertex renaming} of $\gG=\tuple{\vG,\eG}$
-along a bijection $(\hat\cdot)\colon\vG\to\hat\vG$ is the graph
-$\hat\gG=\tuple{\hat\vG,\set{\hat v\hat w\mid vw\in\eG}}$, with
-colouring and/or labelling inherited (i.e., $\hat v\samecol\hat w$ if
-$v\samecol w$, and $\ell(\hat v)=\ell(v)$). Following standard graph
-theory, we identify graphs modulo vertex renaming.
-
-A \bfit{directed graph} $\gG =\tuple{\vG,\eG}$ is a set $\vG$ of
-\bfit{vertices} and a set $\eG\subseteq \vG\times\vG$ of \bfit{direct edges}.
-A \bfit{directed graph homomorphism}
-$\phi\colon\tuple{\vG,\eG}\to\tuple{\vH,\eH}$ is a function $\phi\colon\vG\to\vH$ such that if
-$\pair{v,w}\in\eG$ then $\pair{\phi(v),\phi(w)}\in\eH$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Cographs}
@@
 \emptyset$. A module is \bfit{proper} if it has two or more vertices.
-
-%% Modules in cographs correspond precisely to the subtrees of the
-%% cotrees (the term-trees constructing the graph via $+$ and~$\times$).\todo{Cotree
-%% must alternate $+$ and $\times$. Skip this comment completely?}
 
@@
 graphs, inductively as follows:
-%% For a formula $A$, we can define its
-%% associated fograph $\graphof{A}$ inductively by:\todo{duplicate two sentences above}
+
 \begin{equation*}
@@
   structural induction on $A$.
-  %% :
-  %% \begin{itemize}
-  %%   \item Trivial if $A$ is an atom.
-  %%   \item The induction step uses the following fact:
-  %%         if $M$ is a module of $\gG$ and $M' \subseteq M$, then $M'$ is a
-  %%         module of $\gG$ if and only if it is a module of $\gG[X]$.
-  %% \end{itemize}
-  %% \todo{}\lutz{maybe mention also fn 2-5 in Dominic's arxiv-paper}
 \end{proof}
-%%\juihsuan{I'm still looking for a simple proof}
 %
@@
 \end{remark}
-%
-%% For this reason, we call a formula
-%% \bfit{clean} if it does not contain subformulas of the form $(\forall
-%% x.A)\vlor(\forall x.B)$ or $(\exists x.A)\vlan(\exists x.B)$,
-%% \todo{need the four cases as in clear definition in fopws? Consider
-%% $(\forall x.A)\vlor(B\vlor (\forall x.C))$. But then Lemma 6 doesn't hold.
-%% (fopws proves only that there's a surjection from clear formulas onto fographs,
-%% whose kernel is the six formula equalities)} and no
-%% $x$-quantified formula occurs as subformula of another $x$-quantified
-%% formula. Then we have:
-%
-%% \begin{lemma}
-%%   If $A$ is clean iff\/ $\graphof A$ is a fograph.
-%% \end{lemma}
-%
-%% \begin{proof}
-%%   Induction on $A$, using  Theorem~\ref{thm:cograph}.
-%% \end{proof}
-%
-%% Even though for every formula $A$ we can obtain an
-%% equivalent clean formula by simply renaming some bound variables, this
-%% is not unique up to $\alpha$-conversion, as is the case for
-%% rectified formulas.
 %
@@
 %\noindent
-Figure~\ref{fig:leap} shows a fonet with a unique dualizer, and its leap graph.
+Figure~\ref{fig:leap} shows a fonet with its dualizer and leap graph.
 
@@
 A fograph homomorphism $\phi\colon\gG \rightarrow \gH$
-%%\bfit{label-preserving} if for all $v \in \vG, label(v) = label(f(v))$, and is
-% is \bfit{existential-preserving} 
 \bfit{preserves existentials}
@@
   \tuple{\vH, \eH}$ and a fibration on the binding graphs $\bG\to\bH$.
-  %etween fographs is a label-preserving and
-%existential-preserving fograph homomorphism whose restriction to the
-%binding graphs is a fibration.
 \end{definition}
@@
   we often omit the labelling in the upper graph, as below-right.
-  %% , which refer to as 
-  %% \bfit{condensed form}.\dominic{I said ``can be inferred'' to account for 
-  %% e.g.\
-  %% $\graphof{\forall x_1\forall x_2 (px_i\vee px_j\vee px_k\vee px_l)}
-  %% \to \graphof{\forall x\mkern2mu px}$ whose
-  %% unlabelled skeleton is the skeleton of many distinct formula variants (``who binds who?'').}
   \begin{center}\begin{math}
@@
 %
-%%\subsection{First-order combinatorial proofs}
 %
@@
 graph left implicit.
-%  (No information is lost, since 
-% atom/quantifier-occurrences in a formula
-% are in bijection with vertices of its graph.)
-%
+
 \begin{thm}[\cite{hughes:fopws}]
@@
   in~\cite{hughes:fopws}.
-  %The reason for this relaxation in our case is that we want to cover a richer class of proofs, also allowing 
 \end{remark}
@@
 elsewhere (e.g.~\cite{brunnler:06:herbrand,alertubella:guglielmi:18}).%
-%\juihsuan{references added. Please check if they are the right ones.}
 \footnote{In the deep
@@
 
-% We show the equivalence of $\FOMLL$ and $\FOMLS$.
-% 
-% We show that $\FOMLL$ is equivalent to $\FOMLS$.
 We show that $\FOMLL$ and $\FOMLS$ are equivalent.
@@
   This is a straightforward exercise.
-%%  that we leave to the reader. (Note that the
-%%$\ax$-rule can be applied to $\sqn{\fff,\ttt}$ in the cases of $\rr = \faD$.)
 \end{proof}
@@
   a $\FOMLL$ proof $\Proof$ of $\sqn{\Scons A}$.
-  %% If $\rr$ is
-  %% $\upsmash{\vlinf{\aiD}{}{\Scons{a\vlor\cneg a}}{\Scons\ttt}}$, we replace
-  %% in $\Pi$ all corresponding occurrences of $\ttt$ with
-  %% $a \vlor \cneg a$ and the rule instance
-  %% $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation $ \vlderivation{
-  %%   \vlin{\vlor}{}{\sqn{a \vlor \cneg a}}{ \vlin{\axr}{}{\sqn{a, \cneg
-  %%         a}}{ \vlhy{}}}} $. This gives us a proof of
-  %% $\sqn{\Scons{a \vlor \cneg a}}$. In all other cases, 
-  %%   %\item $\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
-  %%    % In this case, we replace simultaneously in $\Pi$ the corresponding
-  %%    % occurrences of $\ttt$ with $\forall x.\ttt$ and the rule instance
-  %%    % $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
-  %%    % $
-  %%    % \vlderivation{
-  %%    %   \vlin{\forall}{}{\sqn{\forall x.\ttt}}{
-  %%    %     \vlin{\axr}{}{\sqn{\ttt}}{
-  %%    %       \vlhy{}}}}
-  %%    % $, and we get a proof $\Pi'$ of $\sqn{\Scons{\forall x.\ttt}}$.
       By Lemmas~\ref{lem:shallow} and~\ref{lem:context}, we have a $\FOMLL$ proof of
@@
   This can be shown by a straightforward induction on $A$ (for details, see e.g.~\cite{brunnler:phd}).
-  %% We show that there is always a derivation
-  %% $$
-  %% \vlderivation{
-  %%   \vlde{\sysS}{}{A}{
-  %%     \vlhy{A \vlor A}}}
-  %% $$, where $\sysS = \set{\acD,\me,\mfaD,\mexD,\fequ}$, by induction on $A$:
-  %% \begin{itemize}
-  %%   \item If $A = a$, then we have
-  %%     $
-  %%     \vlderivation{
-  %%       \vlin{\acD}{}{a}{
-  %%         \vlhy{a \vlor a}}}
-  %%     $.
-  %%   \item If $A = B \vlan C$, then we have
-  %%     $
-  %%     \vlderivation{
-  %%       \vlde{\sysS}{}{B \vlan C}{
-  %%         \vlde{\sysS}{}{B \vlan (C \vlor C)}{
-  %%           \vlin{\me}{}{(B \vlor B) \vlan (C \vlor C)}{
-  %%             \vlhy{(B \vlan C) \vlor (B \vlan C)}}}}}
-  %%     $.\\[.5ex]
-  %%   \item If $A = B \vlor C$, then we have
-  %%     $
-  %%     \vlderivation{
-  %%       \vlde{\sysS}{}{B \vlor C}{
-  %%         \vlde{\sysS}{}{B \vlor (C \vlor C)}{
-  %%           \vlin{\fequ}{}{(B \vlor B) \vlor (C \vlor C)}{
-  %%             \vlhy{(B \vlor C) \vlor (B \vlor C)}}}}}
-  %%     $.\\[.5ex]
-  %%   \item If $A = \exists x.A'$, then we have
-  %%     $
-  %%     \vlderivation{
-  %%       \vlde{\sysS}{}{\exists x.A'}{
-  %%         \vlin{\mexD}{}{\exists x.(A' \vlor A')}{
-  %%           \vlhy{(\exists x.A') \vlor (\exists x.A')}}}}
-  %%     $.\\[.5ex]
-  %%   \item If $A = \forall x.A'$, then we have
-  %%     $
-  %%     \vlderivation{
-  %%       \vlde{\sysS}{}{\forall x.A'}{
-  %%         \vlin{\mexD}{}{\forall x.(A' \vlor A')}{
-  %%           \vlhy{(\forall x.A') \vlor (\forall x.A')}}}}
-  %%     $.
-  %% \end{itemize}
-  %% \todo{}
-  %% \juihsuan{done. Maybe just keep one case.}\lutz{yes, but we do that at the end. don't think about space right now.}
 \end{proof}
@@
   where in the first derivation, $x$ is not free in $A$, and in the second one not free in $\forall x.A$.
-%  The other cases have been shown before (e.g.~\cite{brunnler:phd}).
-%%   We have the following derivations:
-%%   $$
-%%   \vlderivation{
-%%     \vlin{\cD}{}{\forall x.A}{
-%%       \vlin{\equiv}{(x \notin \fv(\forall x.A))}{(\forall x.A) \vlor (\forall x.A)}{
-%%         \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor A)}{
-%%           \vlhy{\forall x.\forall x.A}}}}}
-%%   $$.
-%%   $$
-%%   \vlderivation{
-%%     \vlin{\cD}{}{(A \vlor B) \vlan (C \vlor D)}{
-%%       \vlin{\fequ}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((A \vlor B) \vlan (C \vlor D))}{
-%%       \vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((B \vlor A) \vlan (D \vlor C))}{
-%% 	\vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((B \vlor A) \vlan D))}{
-%% 	  \vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor (B \vlan D))}{
-%% 	    \vlin{\wrD}{}{((A \vlor B) \vlan C) \vlor (B \vlan D)}{
-%% 	      \vlhy{(A \vlan C) \vlor (B \vlan D)}}}}}}}}
-%%   $$.
-%%   $$
-%%   \vlderivation{
-%%     \vlin{\cD}{}{\exists x.(A \vlor B)}{
-%%       \vlin{\fequ}{}{\exists x.(A \vlor B)) \vlor (\exists x.(A \vlor B))}{
-%%       \vlin{\wrD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.(B \vlor A))}{
-%% 	\vlin{\wrD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.B)}{
-%% 	  \vlhy{(\exists x.A) \vlor (\exists x.B)}}}}}}
-%%   $$.
-%%   $$
-%%   \vlderivation{
-%%     \vlin{\cD}{}{\forall x.(A \vlor B)}{
-%%       \vlin{\fequ}{}{(\forall x.(A \vlor B)) \vlor (\forall x.(A \vlor B))}{
-%%       \vlin{\wrD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.(B \vlor A))}{
-%% 	\vlin{\wrD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.B)}{
-%% 	  \vlhy{(\forall x.A) \vlor (\forall x.B)}}}}}}
-%%   $$.
-%%   \juihsuan{done. If needed, we can introduce the notion of open deduction to
-%% reduce the size of derivations...}\lutz{I was thinking about that, but (i) it is probably not worth the effort, as we wont have many derivation, and (ii) it is hard to define rectified derivations this way.}
 \end{proof}
@@
 
-%All statements in this section are proved by rule permutation arguments.
 \begin{thm}\label{thm:LK1-decompose}
@@
   $\weakr$. Then the instances of $\weakr$ and $\conr$ are replaced by
-  $\wD$ and $\cD$, which can then be permuted down. Details are in
+  $\wD$ and $\cD$, which can then be permuted down.
+  Details are in
   Appendix~\ref{app:LK1-decompose}.
@@
 \begin{proof}
-  First, observe that the $\exists$ rule can be permuted under all the other rules since $A\ssubst{x}{t}$ has the same
-  structure as $A$ and none of the other rules has a premise of the
-  form $\Scons{\exists x.A}$. It suffices now to prove that all rules
-  in $\set{\forall, \aiD, \tttD}$ can be permuted over the rules in
-  $\set{\sw, \mix, \fequ}$, which is straightforward
-  (see~\cite{dissvonlutz} for details).
+  First, observe that the $\exists$ rule can be permuted under all the
+  other rules since $A\ssubst{x}{t}$ has the same structure as $A$ and
+  none of the other rules has a premise of the form $\Scons{\exists
+    x.A}$. It suffices now to prove that all rules in $\set{\forall,
+    \aiD, \tttD}$ can be permuted over the rules in $\set{\sw, \mix,
+    \fequ}$, which is straightforward. For the $\fequ$-instances that
+  do not involve the quantifiers, the details can be found
+  in~\cite{dissvonlutz}, and the $\fequ$-instances concerning the
+  quantifiers are admissible in the system without the $\exists$-rule.
 \end{proof}
-%% we can permute $r_1$ upwards over $r_2$.
-%%   We show some cases here, and leave the others to the reader.
-%%   \begin{equation*}
-%%   \vlderivation{
-%%     \vlin{\aiD}{}{\Scons{(A \vlan (a \vlor \cneg a)) \vlor C}}{
-%%       \vlin{\sw}{}{\Scons{(A \vlan \ttt) \vlor C}}{
-%%         \vlhy{\Scons{A \vlan (\ttt \vlor C)}}}}}
-%%   \leadsto
-%%   \vlderivation{
-%%     \vlin{\sw}{}{\Scons{(A \vlan (a \vlor \cneg a)) \vlor C}}{
-%%       \vlin{\aiD}{}{\Scons{A \vlan ((a \vlor \cneg a) \vlor C)}}{
-%%         \vlhy{\Scons{A \vlan (\ttt \vlor C)}}}}}
-%%   \end{equation*}
-%%   \begin{equation*}
-%%     \vlderivation{
-%%       \vlin{\tttD}{}{\Scons{(A \vlor (B \vlan \ttt))}}{
-%%         \vlin{\mix}{}{\Scons{A \vlor B}}{
-%%           \vlhy{\Scons{A \vlan B}}}}}
-%%   \leadsto
-%%   \vlderivation{
-%%     \vlin{\mix}{}{\Scons{(A \vlor (B \vlan \ttt)}}{
-%%       \vlin{\tttD}{}{\Scons{A \vlan (B \vlan \ttt)}}{
-%%         \vlhy{\Scons{A \vlan B}}}}}
-%%   \end{equation*}
-
-%%   \tocheck{}
-%% \end{proof}
 
@@
 Therefore, we can call such a derivation \bfit{rectified}, and
-%% if every line in $\Deri$ is
-%% rectified.
-%
-%% \begin{lemma}
-%%   Let  $\Deri$ be a $\FOMLS$ proof of a formula $A$. Then $\Deri$ is rectified iff $A$ is rectified.
-%% \end{lemma}
-%
-%% \begin{proof}
-%%    The only rules involving bound
-%%    variables are $\forall$ and $\exists$ which both remove a binder (and
-%%    all occurrences of the variable it binds).
-%% \end{proof}
-%
-%% Hence,
 for a non-rectified  $\FOMLS$ derivation $\Deri$ we can
@@
   predicate symbol $p$ (resp.~$\dual p$)
-%% \item {\bf Remove units.} All occurrences of $\ttt$ are replaced by
-%%   $q_0\vlor\dual q_0$ and all $\fff$ are replaced by $q_0\vlan\dual
-%%   q_0$ for some fresh nullary predicate $q_0$.
 \end{enumerate}
@@
 \begin{lemma}\label{lem:frame}
-  If a linked fograph $\gC$ has an induced bimatching then so does its frame $\frameof\gC$. % has an induced bimatching.
+  If a linked fograph $\gC$ has an induced bimatching then so does its frame $\frameof\gC$. 
 \end{lemma}
@@
   Immediately from the construction of the frame.
-  %%\lutz{is it really an ``iff''? It is easy to construct from a bimatching in $\gC$ a bimatching in the frame. (and I think we only need that direction). But what about the other direction?}
 \end{proof}
@@
   $\fographof{\Deri}$.
-  %Hence $\fographof{\Deri}$ is a fonet.
-  %% We have
-  %% to show that no inference rule in $\FOMLS$ can introduce a
-  %% bimatching. For the rules $\forall$, $\aiD$, $\tttD$, $\fequ$, and
-  %% $\mix$, this is immediate, as they do not introduce new edges in the
-  %% cograph connecting two vertices that are each incident to a leap
-  %% edge. The only rules that can do that are $\sw$ and $\exists$. For
-  %% the $\sw$-rule, we refer reader to~\cite{retore:???} or
-  %% \cite{gug:SIS} or \cite{dissvonlutz} where this property has been
-  %% shown in detail. For the rule $\exists$, a potential bimatching can
-  %% only be created by a dependency between the \todo{need frame?}
 \end{proof}
@@
 \end{remark}
-
-%% \begin{thm}
-%%   Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
-%%   the graph $\graphof{\rectif A}$ forms a fonet whose linking is
-%%   $\linkingof{\rectif\Deri}$ and whose dualizer is
-%%   $\substof{\rectif\Deri}$.
-%% \end{thm}
-
-%% \begin{proof}
-%%   Apply Lemma~\ref{lem:MLS1->fonet} to the rectification $\rectif\Deri$ of $\Deri$.
-%% \end{proof}
 
@@
   then we get a contradiction as in that case there must be a $\vlor$- or $\forall$-formula in $\Gamma$.
-%  \lutz{can anyone give a good argument here?}
 \end{proof}
@@
   a derivation $\vlder{\FOMLS}{\Deri}{C}{\ttt}$ such that $\fographof\Deri=\tuple{\gC,\linkingof\gC}$.
-  %% an
-  %% $\FOMLL$-proof $\Pi$ of $\Gamma$, such that
-  %% $\fographof\Pi=\tuple{\gC,\linkingof\gC}$.
-  %% Let $\gC$ be a fonet with linking $\linkingof\gC$, let $\dualizer$ be a dualizer
-  %% for $\gC$, and let $A$ be a formula with $\graphof A=\gC$.  Then
-  %% there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
-  %% $\linkingof\gC=\linkingof{\Deri}$ and $\dualizer=\substof{\Deri}$.
 \end{thm}
@@
 maps of the rule instances in $\Deri$.
-%% \juihsuan{maybe mention at least that the induced
-%% maps define graph homomorphisms. Do we need to talk about the contexts
-%% $\Sconhole$ here (induced maps act clearly as the identity on contexts but we need them for the composition)?}
-%% \lutz{For the context, I aleady say it is the identity. For the homom, it comes later}
 
@@
 
-%% We say that a derivation $\Deri$ is \bfit{sane} if for every line $Q$
-%% in $\Deri$ we have that $\graphof D$ is a fograph (i.e., all binders
-%% are legal). Clearly, every rectified derivation is sane, but not vice
-%% versa, as we might have multiple occurrences of bound variables in $Q$,
-%% such that $\graphof Q$ is still a fograph.
-
 \begin{lemma}\label{lem:cw->skew}
@@
   fibration.
-  %(see
-  %also~\cite{hughes:invar,str:ral:tableaux19}).
   Hence,
   $\mapof\Deri$ is a skew fibration.
-  %%That $\mapof{\PE\Deri}$ preserves
-  %%exponentials follows immediately from its construction.
 \end{proof}
@@
    respectively.     
-  %% A subformula of $\PE B$ is called \emph{weak} if it has been
-  %% introduced by a weakening. All subformulas of a weak formula are
-  %% also weak. Two weak subformulas $B'$ and $B''$ of $\PE B$ form a
-  %% \emph{weak pair} if $\PE B\fequ\Scons{B'\vlor B''}$ for some context
-  %% $\Sconhole$. We can assume without loss of generality that
-  %% whenever weak subformulas $B'$ and $B''$ form a weak pair, they have
-  %% been introduced by the same instance of $\wrD$ in
-  %% $\PE\Deri_1$.\footnote{If $\PE\Deri_1$ is not of that shape, it can
-  %% brought into this form by simple rule permutations, and then
-  %% collapsing several weakenings into a single one.}  Now we show that
-  %% $\PE\Deri_1$ can be lifted. For this, observe that whenever a
-  %% weakening in $\PE\Deri_1$ deletes an atom $x\in\VAR$, it must also
-  %% delete all atoms in the scope of the corresponding quantifier,
-  %% because $\phi'$ is a fibration on the binding graph. Hence, each line
   If a  weakening happens inside a subformula $x\vlor \PE C$ or $x\vlan
@@
 
-\clearpage
-
+%\clearpage
+\newpage
 \appendix
@@
 %\end{document}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\lutz{OLD STUFF, TO BE REMOVED EVENTUALLY}
-
-\subsection{Unification Nets}
-
-\todo{}
-
-In this paragraph, we associate each formula $A$ with its \bfit{formula tree}
-$\formtree{A}$, a directed
-tree with leaves labelled by atoms, internal nodes labelled by connectives and
-quantifiers, and edges directed from leaves to the root. For a sequent
-$\Gamma = A_1, \ldots, A_n$, we denote with $\formtree{\Gamma}$, the forest
-formed by $\formtree{A_1}, \ldots, \formtree{A_n}$, i.e., the disjoint union of
-$\formtree{A_i}$'s. The \bfit{roots} of $\formtree{\Gamma}$ are the roots of
-${A_i}$'s
-
-Let $\Gamma$ be a sequent in $\FOMLL$. Consider the forest
-$\formtree{\Gamma}$. A \bfit{link} on $\Gamma$ is a pair of
-leaves whose atoms are pre-dual. A \bfit{linking} $\lambda$ on $\Gamma$ is a set
-of
-disjoint links such that each leaf of $\formtree{\Gamma}$ is either labelled by $\ttt$ or
-in exactly one link. Similar to the set of links in linked fographs, a linking can be seen as a
-unification problem, and a \bfit{dualizer} $\dualizer$ of the linking $\lambda$ is an assignment
-unifying all the links in $\lambda$. There exists a \bfit{most general dualizer}
- of $\lambda$ if $\lambda$ has a dualizer. \juihsuan{Now I use the same terminology as for linked fographs}\lutz{use $\delta$ for the dualizer (or even better, make it a macro)}
-A \bfit{dependency} is a pair $(\single \exists x, \single \forall y)$ of nodes
-such that the most general dualizer assigns to $x$ a term containing $y$.
-
-Let $\lambda$ is a linking on $\Gamma$ that has a dualizer.
-The \bfit{unification structure} $\unifstr{\lambda}$
-associated with $\lambda$ is the forest $\formtree{\Gamma}$ together with an undirected
-edge between leaves $l$ and $l'$ for every link $\{l, l'\}$ in $\lambda$ and a
-directed edge from $\single \exists x$ to $\single \forall y$ for every
-dependency $(\single \exists x, \single \forall y)$.
-
-A \bfit{switching graph} of a unification structure $\unifstr{\lambda}$ is any
-derivative of $\unifstr{\lambda}$ obtained by keeping only one edge into each $\cor$
-and $\forall$ and undirecting remaining edges. A linking is \bfit{correct} if it
-is unifiable and all of the switching graphs of its associated unification
-structure are acyclic.
-
-\begin{definition}
-  A \bfit{unification net} on a sequent $\Gamma$ is a correct linking on $\Gamma$.
-\end{definition}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Translation between Unification Nets and $\FOMLL$}
-
-\todo{}
-\begin{thm}\label{thm:MLL1->Unet}
-  If a sequent is provable in $\FOMLL$, then there exists a unification net
-  on it.
-\end{thm}
-
-\begin{proof}
-  We proceed by induction on the proof of $\sqn \Gamma$ in $\FOMLL$, making a
-  case analysis on the bottommost rule instance:
-  \begin{itemize}
-    \setlength\itemsep{.5em}
-    \item $\vlinf{\axr}{}{\sqn{a,\cneg a}}{}$ : the linking $\{a, \dual{a}\}$ is correct.
-    \item $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ : the empty linking is correct.
-    \item $\vliinf{\mixr}{}{\sqn{\Gamma,\Delta}}{\sqn\Gamma}{\sqn\Delta}$ :
-	  By induction hypothesis, there is a correct linking on
-	  $\Gamma$ and another one on $\Delta$, their union giving a
-	  correct linking on $\Gamma, \Delta$.
-    \item $\vlinf{\vlor}{}{\sqn{\Gamma,A\vlor B}}{\sqn{\Gamma,A,B}}$ : By
-	  induction hypothesis, there is a correct linking on $\Gamma, A, B$,
-	  and it is correct on $\Gamma, A \vlor B$ as well.
-    \item $\vliinf{\vlan}{}{\sqn{\Gamma,A\vlan B, \Delta}}{\sqn{\Gamma,A}}{\sqn{B,\Delta}}$ :
-          By induction hypothesis, there is a correct linking on $\Gamma, A$ and
-	  another one on $B, \Delta$, their union giving a correct linking on
-          $\Gamma,A \vlan B, \Delta$.
-    \item $\vlinf{\exists}{}{\sqn{\Gamma,\exists x.A}}
-	  {\sqn{\Gamma,A\ssubst{x}{t}}}$ : By induction hypothesis, there is a
-	  correct linking $\lambda$ on $\Gamma, A\ssubst{x}{t}$.
-	  For each atom in $\Gamma, A \ssubst{x}{t}$, there is a corresponding
-	  atom in $\Gamma, \exists x.A$. There is therefore a linking $\lambda'$
-          on $\Gamma, \exists x.A$ obtained from $\lambda$ via this
-	  correspondence, and it is not difficult to check that $\lambda'$ is
-	  correct as well.
-    \item $\vlinf{\forall}{\text{($x$ not free in
-	  $\Gamma$)}}{\sqn{\Gamma,\forall x.A}}{\sqn{\Gamma,A}}$ : By induction
-          hypothesis, there is a correct linking on $\Gamma, A$, and it is easy
-	  to see that it is a correct linking on $\Gamma, \forall x.A$ as well.
-  \end{itemize}
-  This allows to define a translation $\sqntl\cdot$ from proofs in $\FOMLL$ to unification
-  nets.
-\end{proof}
-
-\begin{thm}\label{thm:sqntl}
-  Any unification net can be obtained via the translation $\sqntl\cdot$ given in Theorem
-  \ref{thm:MLL1->Unet}.
-\end{thm}
-
-To prove this theorem, we need some basic lemmas about connected components in
-switching graphs of unification nets.
-
-\begin{lemma}\label{lem:concomp}
-  The number of connected components of an acylic graph $\gG = \tuple{\vG, \eG}$ is
-equal to $|\eG| - |\vG|$.
-\end{lemma}
-
-\begin{proof}
-  By a straightforward induction on $|\vG|$.
-\end{proof}
-
-\begin{lemma}
-  The number of connected components is the same for any switching graph of a
-unification net.
-\end{lemma}
-
-\begin{proof}
-  An immediate consequence of Lemma \ref{lem:concomp}.
-\end{proof}
-
-In the proof, we also use the notion of \bfit{frame} introduced by Hughes in
-\cite{hughes:unifn}.
-
-\begin{definition}
-Let $\lambda$ be a unification net on an $\FOMLL$ sequent $\Gamma$.
-We define the \bfit{frame} of $\lambda$ by exhaustively applying the following
-subformula rewriting steps, to obtain a linking $\lambda_m$ on an $\MLLm$ sequent $\Gamma_m$:
-
-\begin{enumerate}
-  \item {\bf Encode dependencies as fresh links.} For each dependency $\exists x
-	  \rightarrow \forall y$, with corresponding subformulas $\exists x A$
-		and $\forall y B$, we add a fresh link as follows. Let $P$ be a
-		fresh (nullary) predicate symbol. Replace $\exists x A$ with $P
-		\cand \exists x A$ and $\forall y B$ with $\overline{P} \cor \forall y B$, and add an axiom link between $P$ and $\overline{P}$.
-  \item {\bf Erase quantifiers.} After step 1, erase all the quantifiers. (We no longer need their leaps since they are encoded as links in step 1.
-  \item {\bf Simplify atoms.} After step 2, replace every predicate $Pt_1 \cdots t_n$ with a nullary predicate symbol $P$.
-\end{enumerate}
-\end{definition}
-Note that the linking $\lambda_m$ is a valid $\MLLm$ proof net.
-
-\begin{lemma}\label{lem:concomp_switching}
-Suppose that $\lambda$ is a $\MLLm$ proof net which is connected and such that any of its
-switching graphs is not connected. Then there exists a $\vlor$ node in
-$\unifstr{\lambda}$ such that $\lambda$ is correct on the sequent $\Gamma'$
-obtained from $\Gamma$ by replacing this $\vlor$ by a $\vlan$.
-\end{lemma}
-
-\begin{proof}
-Suppose that such a $\vlor$ node does not exist. Then it is clear that for any
-two nodes, there exists a switching graph containing a path between them and
-this path corresponds to an $AE$-path in \cite{retore:03}. By
-\cite[Propostion~3]{retore:03}, $\lambda$ corresponds to a sequent proof that
-does not use $\mix$, which implies the connectedness of the switching graphs of
-$\lambda$. Contradiction.
-\tocheck{}
-\end{proof}
-
-\begin{lemma}\label{lem:concomp_switching_fo}
-Suppose that $\lambda$ is a $\FOMLL$ proof net which is connected and such that any of its
-switching graphs is not connected. Then there exists a $\vlor$ node in
-$\unifstr{\lambda}$ such that $\lambda$ is correct on the sequent $\Gamma'$
-obtained from $\Gamma$ by replacing this $\vlor$ by a $\vlan$.
-\end{lemma}
-
-\begin{proof}
-  Consider the frame $\lambda_m$ of $\lambda$. The number of any switching
-graph of $\unifstr{\lambda}$ is equal to that of $\unifstr{\lambda_m}$. Apply
-Lemma \ref{lem:concomp_switching} and it is clear that such $\vlor$ cannot be one
-of the fresh $\vlor$'s added during the frame construction.
-\end{proof}
-
-We can now give the proof of Theorem \ref{thm:sqntl}.
-
-\begin{proof}[Proof of Theorem~\ref{thm:sqntl}]
-Let $\lambda$ be a unification net on $\Gamma$. We proceed by induction on the
-number of connected components of the unification structure $\unifstr{\lambda}$:
-\begin{itemize}
-  \item If there is only one connected component, we proceed by induction on the
-number $k$ of connected components of any switching graph of
-$\unifstr{\lambda}$. If $k = 1$, we obtain a proof $\Deri$ in $\FOMLL$ such that
-$\sqntl{\Deri} = \lambda$ by applying \cite[Theorem~3]{hughes:unifn}. If $k > 1$,
-using the Lemma \ref{lem:concomp_switching_fo}, we obtain a sequent $\Gamma'$ on
-which $\lambda$ is correct by transforming a $\vlor$ node into a $\vlan$. By
-induction hypothesis, there is a proof $\Deri'$ in $\FOMLL$ whose translation is
-$\lambda$. By considering the $\vlan$ rule instance corresponding to the $\vlan$
-node in $\Deri'$, we have:
-$
-\Deri' =
-\vlderivation{
-  \vlin{}{}{\sqns{\Gamma'}}{
-  \vlin{}{}{\vlvdots}{
-    \vliin{\vlan}{}{\sqns{\Delta_1, A \vlan B, \Delta_2}}{
-      \vltrl{\Deri_1}{}{}{\sqns{\Delta_1, A}}{
-        \vlhy{\quad}}{
-        \vlhy{}}{
-        \vlhy{}}}{
-      \vltrl{\Deri_2}{}{}{\sqns{B, \Delta_2}}{
-        \vlhy{\quad}}{
-        \vlhy{}}{
-        \vlhy{}}}
-}}}
-$.
-We can thus obtain a proof $\Deri$ of $\Gamma$:
-$
-\Deri =
-\vlderivation{
-  \vlin{}{}{\sqns{\Gamma}}{
-  \vlin{}{}{\vlvdots}{
-    \vlin{\vlor}{}{\sqns{\Delta_1, A \vlor B, \Delta_2}}{
-    \vliin{\mix}{}{\sqns{\Delta_1, A, B, \Delta_2}}{
-      \vltrl{\Deri_1}{}{}{\sqns{\Delta_1, A}}{
-        \vlhy{\quad}}{
-        \vlhy{}}{
-        \vlhy{}}}{
-      \vltrl{\Deri_2}{}{}{\sqns{B, \Delta_2}}{
-        \vlhy{\quad}}{
-        \vlhy{}}{
-        \vlhy{}}}
-}}}}
-$ such that $\sqntl{\Deri} = \lambda$.
-
-  \item If there are $n > 1$ connected components, add a fresh $\vlor$ node
-connecting two formulas belonging to different connected components of $\Gamma$
-to get a new sequent $\Gamma'$. Define a unification net $\lambda'$ on $\Gamma'$
-using the same linking as $\lambda$. By induction hypothesis, since
-$\unifstr{\lambda'}$
-has $n-1$ connected components, there is a $\FOMLL$ proof $\Deri'$ such that
-$\sqntl{\Deri'} = \lambda'$. Consider the $\vlor$ rule instance corresponding
-to the $\vlor$ node in question. Since $\vlor$ is invertible, we can permute
-downwards this rule instance until it becomes the last rule of the proof (note
-that this transformation does not change the image of the proof by the
-translation $\sqntl\cdot$) to get a new proof $\Deri''$ of $\Gamma'$. By deleting the last rule
-instance from $\Deri''$, we obtain a proof $\Deri$ of $\Gamma$ such that
-$\sqntl{\Deri} = \lambda$.
-\tocheck{}
-\end{itemize}
-
-We proceed by induction on the
-number of connectives in $\Gamma$. In the base case, $\Gamma$ is of the form
-\begin{align*}
-p_1(t_{11}, \ldots, t_{1n_1}), \dual{p_1}(t_{11}, \ldots, t_{1n_1}), \ldots, \\
-p_k(t_{k1}, \ldots, t_{kn_k}), \dual{p_k}(t_{k1}, \ldots, t_{kn_k}),
-\underbrace{\ttt, \ldots, \ttt}_\text{$m$ times}
-\end{align*} and
-$\lambda$ is the linking $\set{(a_1, \cneg{a_1}), \ldots, (a_k, \cneg{a_k})}$,
-where $a_i = p_i(t_{i1}, \ldots, t_{in_i})$, which equals to $\sqntl\Pi$, where
-$\Pi$ is the proof consisting of $m$ instances of the $\ttt$ rule, $n$ instances
-$\vlinf{\ax}{}{\sqn a_i, \cneg{a_i}}{}$ of the $\ax$ rule, and followed by
-$m+k-1$ instances of the $\mix$ rule.
-
-Now we consider the inductive cases:
-\begin{itemize}
-  \item $\Gamma = \Delta, A \vlor B$:
-    Let $\Gamma' = \Delta, A, B$. Define $\lambda'$ on $\Gamma'$ using the same
-    links as $\lambda$ by identifying the leaves of $\formtree{\Gamma'}$ with those
-    of $\formtree{\Gamma}$. We now check that $\lambda'$ is a unification net:
-    \begin{itemize}
-      \item The most general dualizer of $\lambda$ is also the most general
-dualizer of $\lambda'$ as they correspond to the same unification problem.
-Hence, the unification structure $\unifstr{\lambda'}$ is equal to the
-restriction of $\unifstr{\lambda}$ to the nodes of $\formtree{\Gamma'}$.
-      \item Every switching graph of $\lambda'$ is acyclic: if there were some
-switching graph of $\unifstr{\lambda'}$ containing a cycle, it would induce a switching
-graph of $\unifstr{\lambda}$ containing also a cycle, by adding an edge from the root of
-$\formtree{A}$ to the $\vlor$ node in question.
-    \end{itemize}
-  \item $\Gamma = \Delta, \forall x.A$:
-    Let $\Gamma' = \Delta, A$. Define $\lambda'$ on $\Gamma'$ using the same
-links as $\lambda$. We now check that $\lambda'$ is a unification net:
-  \begin{itemize}
-    \item The most general dualizer of $\lambda$ is also the most general
-dualizer of $\lambda'$ as they correspond to the same unification problem.
-    \item Every switching graph of $\unifstr{\lambda'}$ is acyclic: if there
-were some switching graph of $\unifstr{\lambda'}$ containing a cycle, it would
-induce a switching graph of $\unifstr{\lambda}$ contaiting also a cycle, by
-adding an edge from the root of $\formtree{A}$ to the $\forall$ node in
-question.
-  \end{itemize}
-  \item $\formtree{\Gamma}$ has a root $\exists x$ with no outgoing dependency
-edge:
-\end{itemize}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Translation between Unification Nets and Fonets}
-
-\todo{}
-
-\bigskip
-\hrule
-\bigskip
-
-\section{First-order Combinatorial Proofs}
-\subsection{First-order Logic}
-
-In this paper, we also use some \bfit{deep inference} \cite{brunnler:tiu:01} rules that are in the
-following form:
-\begin{center}
-\begin{prooftree}
-  \hypo{\vdash S\{A\}}
-  \infer1[]{\vdash S\{B\}}
-\end{prooftree}
-\end{center}
-where $S\{ \ \}$ stands for a \bfit{context}, which corresponds to a sequent
-with a hole taking the place of an atom, and $S\{A\}$ represents
-the sequent or formula obtained by replacing the hole in $S\{ \ \}$ with the formula $A$. Formally, 
-\begin{center}
-  $C ::= \Box \ | \ A \cor C \ | \ C \cand A \ | \ \exists x C \ | \ \forall x 
-C$.
-\\[1.5ex]
-  $S ::= C \ | \ A, S \ | \ S, A$ 
-\end{center}
-where $A$ is a formula.
-The above rule can be thus seen as the rewriting rule $A \rightarrow B$.
-
-We use the notation $\vlderivation{\vlde{}{\mathcal{P}}{B}{\vlhy {A}}}$ for
-denoting that there is a derivation from premise $\vdash S\{A\}$ to conclusion
-$\vdash S\{B\}$ in system $\mathcal{P}$ for any context $S$.
-
-\subsection{Graphs}
-
-\subsection{First-order combinatorial proofs}
-
-\subsection{$\FOMLL$ and Unification Nets}
-
-In $\FOMLL$, terms, atoms, formulas are defined as in first-order logic. For
-simplicity, we choose to use $\cor$ and $\cand$ instead of $\parr$ and
-$\otimes$ which are generally used in the presentation of linear logic.
-A formula $A$ is identified with its \bfit{formula tree} $\formtree{A}$, a directed
-tree with leaves labelled by atoms, internal nodes labelled by connectives and
-quantifiers, and edges directed from leaves to the root. A \bfit{sequent} $\Gamma$ is simply a disjoint union of formulas. We write
-comma for disjoint union.
-
-Sequents are proved using the inference rules of $\FOMLL$:
-\begin{figure}[h]
-\begin{center}
-\begin{prooftree}
-  \infer0[$\ax$]{\vdash A, \neg A}
-\end{prooftree}
-\qquad
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A}
-  \hypo{\vdash \Delta, \neg A}
-  \infer2[$\cut$]{\vdash \Gamma, \Delta}
-\end{prooftree}
-\\[1.5ex]
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A}
-  \hypo{\vdash \Delta, B}
-  \infer2[$\conj$]{\vdash \Gamma, \Delta, A \cand B}
-\end{prooftree}
-\qquad
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A, B}
-  \infer1[$\disj$]{\vdash \Gamma, A \cor B}
-\end{prooftree}
-\\[1.5ex]
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A}
-  \infer1[$\univ$]{\vdash \Gamma, \forall x A}
-\end{prooftree}
-($x \notin \fv(\Gamma)$)
-\qquad
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A[t/x]}
-  \infer1[$\exist$]{\vdash \Gamma, \exists x A}
-\end{prooftree}
-\end{center}
-\caption{Sequent calculus for $\FOMLL$}
-\end{figure}
-
-We also consider the $\mix$ rule:
-
-\begin{center}
-\begin{prooftree}
-\hypo{\vdash \Gamma}
-\hypo{\vdash \Delta}
-\infer2[$\mix$]{\vdash \Gamma, \Delta}
-\end{prooftree}
-\end{center}
-
-Let $\Gamma$ be a sequent in $\FOMLLm$. A \bfit{link} on $\Gamma$ is a pair of
-leaves whose atoms are pre-dual. A \bfit{linking} on $\Gamma$ is a set of 
-disjoint links such that each leaf of $\Gamma$ is in exactly one link. Similar
-to the set of links in the linked fograph, a linking can be seen as a
-unification problem, and a link is said \bfit{unifiable} if the corresponding
-unification problem is solvable. \bfit{Dependencies} are defined as previously.
-
-\section{From first-order logic to combinatorial proofs}
-
-\subsection{Decomposition Theorem}
-Consider the following deep inference rules \cite{brunnler:tiu:01}:
-\begin{center}
-\mbox{
-\begin{prooftree}
-  \hypo{\vdash S\{A \cor A\}}
-  \infer1[$\cD$]{\vdash S\{A\}}
-\end{prooftree}
-\hspace{2cm}
-
-\begin{prooftree}
-  \hypo{\vdash S\{\fff \}}
-  \infer1[$\wD$]{\vdash S\{A\}}
-\end{prooftree}
-}
-\end{center}
-
-Note that the $\ctr$ (resp. $\wk$) rule in $\LK$ is derivable in $\{\cD, \cor\}$
-(resp. $\{\wD, \fff\}$) and that $\cD$ and $\wD$ rules
-permute downwards with the non-structural rules of $\LK$.
-
-\begin{center}
-\mbox{
-
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A, A}
-  \infer1[$\ctr$]{\vdash \Gamma, A}
-\end{prooftree}
-
-$\ \leadsto \ $
-
-\begin{prooftree}
-  \hypo{\vdash \Gamma, A, A}
-  \infer1[$\cor$]{\vdash \Gamma, A \cor A}
-  \infer1[$\cD$]{\vdash \Gamma, A}
-\end{prooftree}}
-\vspace{0.2cm}
-
-\mbox{
-\begin{prooftree}
-  \hypo{\vdash \Gamma}
-  \infer1[$\wk$]{\vdash \Gamma, A}
-\end{prooftree}
-
-$\ \leadsto \ $
-
-\begin{prooftree}
-  \hypo{\vdash \Gamma}
-  \infer1[$\fff$]{\vdash \Gamma, \fff}
-  \infer1[$\wD$]{\vdash \Gamma, A}
-\end{prooftree}}
-
-\end{center}
-
-We also give an example to show how rule permutation works:
-
-\begin{center}
-
-\mbox{
-\begin{prooftree}
-\hypo{\Gamma,A \cor A}
-\infer1[$\cD$]{\Gamma,A} 
-\hypo{\Delta,B}
-\infer2[$\cand$]{\Gamma, \Delta, A \cand B} 
-\end{prooftree}
-
-$\ \leadsto \ $
-
-\begin{prooftree}
-\hypo{\Gamma,A \cor A}
-\hypo{\Delta,B}
-\infer2[$\cand$]{\Gamma, \Delta, (A \cor A) \cand B} 
-\infer1[$\cD$]{\Gamma, \Delta, A \cand B} 
-\end{prooftree}}
-
-\end{center}
-
-We want to establish the following theorem:
-
-\begin{thm}
-\label{thm1}
-Let $\Gamma$ be a sequent.
-Then there is a proof of $\Pi$ in $\LKm$ iff there is a proof of some sequent $\Delta$ in $\FOMLLm$ and a derivation from $\Delta$ to $\Gamma$ consisting of the $\cD$ and $\wD$ rules only.
-\end{thm}
-
-\begin{proof}
-($\Rightarrow$) This direction comes from the above observation: it suffices to permute downwards all the instances of the $\cD$ and $\wD$ rules.
-
-($\Leftarrow$)
-We regard the proof in $\FOMLLm$ as a proof in $\LKm$.
-Then we put the derivation consisting of only $\cD$ and $\wD$ under the proof in $\LKm$. Now we try to permute all the instances $\cD$ and $\wD$ upwards with the rules of LK and $mix$. 
-For the $\cD$ part, the only non-trivial case is the permutation with the $\cor$ rule where the formula generated is $A \cor A$.
-
-\begin{center}
-\mbox{
-\begin{prooftree}
-\hypo{\vdash \Gamma, A, A}
-\infer1[$\cor$]{\vdash \Gamma, A \cor A}
-\infer1[$\cD$]{\vdash \Gamma, A}
-\end{prooftree}
-
-$\ \leadsto \ $
-
-\begin{prooftree}
-\hypo{\vdash \Gamma, A, A}
-\infer1[$\ctr$]{\vdash \Gamma, A}
-\end{prooftree}
-
-} 
-\end{center}
-
-In this case, the permutation of this instance of $\cD$ stops and we continue with the remaining instances.
-
-For the $\wD$ part, the only non-trivial case is the permutation with the $\fff$ rule (or the instance of $wk$ where $\fff$ is introduced):
-
-\begin{center}
-\mbox{
-\begin{prooftree}
-\hypo{\vdash \Gamma}
-\infer1[$\fff$]{\vdash \Gamma, f}
-\infer1[$\wD$]{\vdash \Gamma, A}
-\end{prooftree}
-
-$\ \leadsto \ $
-
-\begin{prooftree}
-\hypo{\vdash \Gamma}
-\infer1[$\wk$]{\vdash \Gamma, A}
-\end{prooftree}
-
-} 
-\end{center}
-
-In this case, the permutation of this instance of $\wD$ stops and we continue with the remaining instances.
-
-\end{proof}
-
-D. Hughes proves in \cite{hughes:unifn} the soundness and completeness of
-unification nets with respect to $\FOMLLm$. In the following, we establish the
-equivalence between unification nets and fonets.
-
-\subsection{Equivalence between unification nets and fonets}
-In the following, we usually confound a vertex with its label.
-
-\begin{definition} A \bfit{switching path} of a unification structure $U(\lambda)$ is a path in a switching graph of $U(\lambda)$.
-\end{definition}
-
-\begin{definition} A \bfit{switching path} of a formula tree $\formtree{A}$ is a
-	path in $\formtree{A}$ that does not go through both incoming edges of a $\cor$.
-\end{definition}
-
-\begin{proposition}
-\label{prop1}
-In a formula tree, the root is connected to every vertex by a switching path.
-\end{proposition}
-
-Now we give the key proposition relating a fograph to its corresponding formula
-tree.
-
-\begin{proposition}
-\label{prop2}
-Let $u$ and $v$ be two distinct vertices of a fograph $\graphof(A)$, then we have the equivalence
-between:
-\begin{itemize}
-  \item $u$ and $v$ are adjacent in $\graphof(A)$
-  \item $u$ and $v$ are connected by a switching path of $\formtree{A}$, and if one of them is a universal quantifier, then the other is
-	not a descendant of the former.
-  \end{itemize}
-\begin{proof}
-By induction on $A$.
-\begin{itemize}
-  \item If $A$ is an atom, trivial.
-  \item If $A = A_1 \cand A_2$, then we distinguish two cases:
-    \begin{itemize}
-      \item $u$ and $v$ are both in $A_1$ (resp. $A_2$): trivial by
-	      the induction hypothesis.
-      \item one of them is in $A_1$ and the other is in $A_2$: they are
-	      adjacent in $\graphof(A)$ by definition. By Proposition \ref{prop1},
-		    the one in $A_1$ (resp. $A_2$) is connected to the
-		    vertex representing $A_1$ (resp. $A_2$) by a switching
-		    path. Together with the two edges incident to $A_1 \cand
-		    A_2$, we obtain a switching path connecting $u$ and $v$.
-    \end{itemize}
-  \item If $A = A_1 \cor A_2$, then we distinguish two cases:
-    \begin{itemize}
-      \item $u$ and $v$ are both in $A_1$ (resp. $A_2$): trivial by
-	      the induction hypothesis.
-      \item one of them is in $A_1$ and the other is in $A_2$: they are not
-	      adjacent in $\graphof(A)$ by definition. It is clear that they
-		    are not connected by a switching path.
-    \end{itemize}
-  \item If $A = \exists x \ A'$, then we distinguish two cases:
-    \begin{itemize}
-      \item $u$ and $v$ are both in $A'$: trivial by the induction
-	      hypothesis.
-      \item one of them is $\exists x$ and the other is in $A'$: trivial
-	      by Proposition \ref{prop1}
-
-    \end{itemize}
-  \item If $A = \forall x \ A'$, then we distinguish two cases:
-    \begin{itemize}
-      \item $u$ and $v$ are both in $A'$: trivial by the induction
-	      hypothesis.
-      \item one of them is $\forall x$ and the other is in $A'$:
-	      they are not adjacent in $\graphof(A)$ by definition and it is clear that
-		    the former is a descendant of $\forall x$.
-    \end{itemize}
-\end{itemize}
-\end{proof}
-\end{proposition}
-
-\begin{proposition}
-If there exists an induced bimatching of the linked fograph $G = \graphof(A)$, then there exists a switching graph of the corresponding unification net which contains a cycle.
-\begin{proof}
-  Suppose that there exists a set $W$ inducing a bimatching in $G$.
-  Then $(W, E_G)$ and $(W, L_G)$ are matchings.\\
-  Let $E_W$ (resp. $L_W$) be the restriction of $E_G$ (resp. $L_G$) to $W$. \\
-  If $E_W \cap L_W \neq \emptyset$, then there exist $u$ and $v$ such that $uv
-  \in E_G$ and $uv \in L_G$. By Proposition \ref{prop2}, there exists a
-  switching path of the formula tree of $A$. Together with the leap
-  $uv$, this path induces a cycle in a switching graph of the
-  corresponding unification structure. \\
-  We can now suppose that $E_W$ and $L_W$ are disjoint. It is not difficult to
-  see the existence of an alternating and elementary cycle in the bicoloured graph $(W, E_W \uplus L_W)$, i.e.
-a cycle of which the edges are alternately in $E_W$ and $L_W$ and containing no two equal vertices.
-  By Proposition \ref{prop2}, this cycle induces a cycle in the unification
-  structure. Now we want to construct a switching graph that contains this cycle.\\
-  Consider a universal quantifier $\forall x$. If $\forall x \notin W$, then        
-  we keep the incoming edge from its direct subformula and remove all the 
-  dependencies. Otherwise, since $(W, L_G)$ is a matching, there exists a
-  unique existential quantifier adjacent to $\forall x$ and we keep thus the
-  corresponding edge in the unification structure. \\
-  Now consider a $\cor$. We distinguish three cases:
-  \begin{itemize}
-    \item the cycle goes through none of the two branches (incoming edges) of
-	    the $\cor$: we can choose an
-	    arbitrary switching for this $\cor$
-    \item the cycle goes through exactly one branch: we choose the corresponding
-	    switching
-    \item the cycle goes through both branches:
-	    this means that there exist $v_L \in W$ (resp. $v_R$) in the left
-		  (resp. right) branch, $u_L$, $u_R \in W$, such that
-		  $u_Lv_L, u_Rv_R \in E_W$ and that the corresponding switching
-		  path from $u_L$ to $v_L$ (resp. from $u_R$ to $v_R$) goes
-		  through the left (resp. right) edge of $\cor$.
-
-\begin{figure}[h]
-    \begin{center}	
-    \begin{tikzpicture}
-    \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
-    \draw (0, 0) node (par) {$\cor$};
-    \draw (1, 1.7) node (dots1) {$\vdots$};
-    \draw (-1, 1.7) node (dots2) {$\vdots$};
-    \draw (1, 3.4) node (vr) {$v_R$};
-    \draw (-1, 3.4) node (vl) {$v_L$};
-    \draw (1.5, -1) node (dots3) {$\vdots$};
-    \draw (-1.5, -1) node (dots4) {$\vdots$};
-    \draw (2.9, -1) node (ul) {$u_L$};
-    \draw (-2.9, -1) node (ur) {$u_R$};
-    \draw (par) -- (dots1) [color=blue];
-    \draw (par) -- (dots2) [color=red];
-    \draw (dots1) -- (vr) [color=blue]; 
-    \draw (dots2) -- (vl) [color=red];
-    \draw (dots4) -- (ur) [color=blue]; 
-    \draw (dots3) -- (ul) [color=red];
-    \draw (dots4) -- (par) [color=blue]; 
-    \draw (dots3) -- (par) [color=red];
-    \end{tikzpicture}
-
-    \caption{A schema showing that the two branches of the same $\cor$ cannot be
-	    used in the cycle at the same time.}
-\end{center}
-\end{figure}
-
-    The red (resp. blue) path is the switching path corresponding to the edge $u_Lv_L$ (resp. $u_Rv_R$) in $E_W$.
-
-    It is clear that $u_L$ (resp. $u_R$) is not in the branches of the
-	 $\cor$. Otherwise, there will be no switching path from $u_L$ to $v_L$
-
-    By Proposition \ref{prop2}, we know that $u_L$ and $u_R$ are not
-	universal quantifiers which are ancestors the $\cor$
-	and that there exist one switching path from $u_L$ to $v_L$ and one
-	from $u_R$ to $v_R$. In particular, there exist one switching path from
-	$u_L$ to the $\cor$ and one from the $\cor$ to $v_R$, and by
-	concatenating the two, we obtain a switching path from $u_L$ to $v_R$. 
-	By Proposition \ref{prop2}, $u_L$ and $v_R$ are thus adjacent in $(W,
-	E_G)$, which is impossible since $(W, E_W)$ is a matching.
-  \end{itemize}
-  Notice that the switching paths here are in the underlying formula tree. We
-  have to verify that they are compatible with the choices of switching made for
-  universal quantifiers. That is, if $uv \in E_W$, then for all the
-  universal quantifiers $\forall x$ on the switching path (in the formula
-	tree), we have chosen in the first part of the proof to keep the only
-	edge from the child of $\forall x$ to itself. In fact, if there exists
-	a universal quantifier $w \in W$ on the switching path $u \rightarrow
-	v$, then one of $u$ and $v$ is not a descendant of $w$. Moreover, if
-	$u$ (resp. $v$) is a universal quantifier, then $w$ is not in its scope.
-	By Proposition \ref{prop2}, $\{wu, wv\} \cap E_W \neq \emptyset$, which
-	is impossible since $(W, E_W)$ is a matching.
-  We have thus constructed a switching graph containing this cycle.
-\end{proof}
-\end{proposition}
-
-\begin{proposition}
-If one of the switching graphs of the unification structure of $A$
-contains a cycle or is not connected, then there exists an induced bimatching of the
-corresponding linked fograph.
-\begin{proof}
-We use frames introduced by D. Hughes in Section 4 of \cite{hughes:unifn}.
-
-\begin{definition}
-Let $\theta$ be a unification structure on an $\FOMLL$ sequent $\Gamma$.
-We define the \bfit{frame}  of $\theta$ by exhaustively applying the following subformula rewriting steps, to obtain a proof structure $\theta_m$ on an $\MLL$ sequent $\Gamma_m$:
-
-\begin{enumerate}
-  \item {\bf Encode dependencies as fresh links.} For each dependency $\exists x
-	  \rightarrow \forall y$, with corresponding subformulas $\exists x A$
-		and $\forall y B$, we add a fresh link as follows. Let $P$ be a
-		fresh (nullary) predicate symbol. Replace $\exists x A$ with $P
-		\cand \exists x A$ and $\forall y B$ with $\overline{P} \cor \forall y B$, and add an axiom link between $P$ and $\overline{P}$.
-  \item {\bf Erase quantifiers.} After step 1, erase all the quantifiers. (We no longer need their leaps since they are encoded as links in step 1.
-  \item {\bf Simplify atoms.} After step 2, replace every predicate $Pt_1 \cdots t_n$ with a nullary predicate symbol $P$.
-\end{enumerate}
-\end{definition}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}
-  \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
-  \draw (0, 0) node (par1) {$\cor$};
-  \draw (1.8, 1.2) node (z) {\color{blue} $\forall z$};
-  \draw (-1.8, 1.2) node (par2) {$\cor$};
-    \draw (-2.8, 2.4) node (x) {\color{red} $\exists x$};
-    \draw (-0.8, 2.4) node (y) {$\exists y$};
-    \draw (-2.8, 3.6) node (px) {$\overline{p}x$};
-    \draw (-0.8, 3.6) node (qy) {$\overline{q}y$};
-    \draw (1.8, 2.4) node (tens) {$\cand$};
-    \draw (0.8, 3.6) node (pz) {$pz$};
-    \draw (2.8, 3.6) node (qfz) {$qfz$};
-    \draw (par1) -- (par2) [<-];
-    \draw (par1) -- (z) [<-];
-    \draw (par2) -- (x) [<-]; 
-    \draw (par2) -- (y) [<-];
-    \draw (x) -- (px) [<-]; 
-    \draw (y) -- (qy) [<-];
-    \draw (z) -- (tens) [<-]; 
-    \draw (tens) -- (pz) [<-];
-    \draw (tens) -- (qfz) [<-];
-    \draw (y) -- (z) [dotted, ->];
-    \draw (x) -- (z) [dotted, ->];
-    \draw[color=blue, dashed] (px) to [bend left] (pz);
-    \draw[color=red, dashed] (qy) to [bend left] (qfz);
-\end{tikzpicture}
-\vspace{1.5ex}
-
-\begin{tikzpicture}
-  \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
-  \draw (0, 0) node (par1) {$\cor$};
-  \draw (1, 0.9) node (par3) {\color{blue} $\cor$};
-  \draw (-1.8, 1.2) node (par2) {$\cor$};
-  \draw (-2.6, 2.4) node (tens1) {\color{red} $\cand$};
-  \draw (-1, 2.4) node (tens2) {$\cand$};
-  \draw (-2.2, 3.6) node (S) {\color{red} $S$};
-  \draw (-0.6, 3.6) node (R) {$R$};
-  \draw (-3, 3.6) node (nP) {$\overline{P}$};
-  \draw (-1.4, 3.6) node (nQ) {$\overline{Q}$};
-  \draw (0.4, 3.6) node (nS) {\color{blue} $\overline{S}$};
-  \draw (1.6, 1.8) node (par4) {$\cor$};
-  \draw (2.2, 2.7) node (tens3) {$\cand$};
-  \draw (2, 3.6) node (P) {$P$};
-  \draw (2.8, 3.6) node (Q) {$Q$};
-  \draw (1.2, 3.6) node (nR) {$\overline{R}$};
-  \draw (par2) -- (par1) [->];
-  \draw (par3) -- (par1) [->];
-  \draw (tens1) -- (par2) [->];
-  \draw (tens2) -- (par2) [->];
-  \draw (nP) -- (tens1) [->];
-  \draw (S) -- (tens1) [->, color=red];
-  \draw (nQ) -- (tens2) [->];
-  \draw (R) -- (tens2) [->];
-  \draw (nS) -- (par3) [->, color=blue];
-  \draw (nR) -- (par4) [->];
-  \draw (tens3) -- (par4) [->];
-  \draw (P) -- (tens3) [->];
-  \draw (Q) -- (tens3) [->];
-  \draw (par4) -- (par3) [->];
-  \draw (nP) to [bend left] (P);
-  \draw (nQ) to [bend left] (Q);
-  \draw (S) to [bend left] (nS);
-  \draw (R) to [bend left] (nR);
-\end{tikzpicture}
-
-\caption{A unification net and its frame. The colored part shows how the
-dependency ${\color{red} \exists x} \rightarrow {\color{blue} \forall z}$ is
-transformed.}
-\end{center}
-\end{figure}
-
-We have the following results:
-
-Let $u$ and $v$ be atoms or quantifiers in a unification structure $\theta$.
-Then they are connected by a switching path in the unification structure if, and only if, their corresponding nodes are connected by a switching path in $\theta_m$.
-
-Consider now a switching graph $H$ of a unification structure $\theta$ of $A$.
-
-If $H$ contains a cycle, then the corresponding switching graph of $\theta_m$
-also contains a cycle. Hence, by applying the propositional results (Theorem 7)
-from \cite{retore:03}, we conclude that there exists a chordless, alternating, and elementary cycle in the bicoloured graph ($W, E_W \uplus L_W$), which corresponds to an induced bimatching in the linked fograph.
-(Note that the linked fograph (cograph) corresponding to $\theta_m$ is equivalent to the one corresponding to $\theta$.)
-
-\end{proof}
-\end{proposition}
-
-\subsection{From contraction/weakening to skew bifibrations}
-
-We first introduce the atomic contraction rule, the medial rule, and two rules
-on quantifiers.
-
-\begin{center}
-\begin{prooftree}
-  \hypo{\vdash S\{a \cor a\}}
-  \infer1[$\acD$]{\vdash S\{a\}}
-\end{prooftree}
-\qquad
-\begin{prooftree}
-  \hypo{\vdash S\{(A \cand B) \cor (C \cand D)\}}
-  \infer1[$\me$]{\vdash S\{(A \cor C) \cand (B \cor D)\}}
-\end{prooftree}
-\\[1.5ex]
-\begin{prooftree}
-  \hypo{\vdash S\{\exists x A \cor \exists x B\}}
-  \infer1[$\mee$]{\vdash S\{\exists x (A \cor B)\}}
-\end{prooftree}	
-\qquad
-\begin{prooftree}
-  \hypo{\vdash S\{\forall x A \cor \forall x B\}}
-  \infer1[$\meee$]{\vdash S\{\forall x (A \cor B)\}}
-\end{prooftree}	
-\end{center}
-
-Here, we also consider the equivalence generated by the associativity, commutativity of $\cor$ and the equations $\ttt \cor A \equiv \ttt$ and $\fff \cor A \equiv A$.
-
-Now we have the following lemma:
-
-\begin{lemma}
-\label{lemma_ctr}
-The contraction rule $\cD$ is derivable for $\{\acD, \me, \mee, \meee\}$.
-\end{lemma}
-\begin{proof}
-	We prove that there is always $\vlderivation{\vlde{}{\{\acD, \me, \mee,
-	\meee\}}{A}{\vlhy {A \cor A}}}$ by structural induction on $A$.
-\begin{itemize}
-  \item If $A = \ttt$ or $A = \fff$, we have 
-	  \begin{prooftree} 
-	    \hypo{\vdash S\{A \cor A\}}
-	    \infer1[$\equiv$]{\vdash S\{A\}}
-	  \end{prooftree}. (the premiss and the conclusion are equivalent)
-  \item If $A = a$, then we have 
-	  \begin{prooftree}
-	    \hypo{\vdash S\{a \cor a\}}
-	    \infer1[$\acD$]{\vdash S\{a\}}.
-	  \end{prooftree}
-  \item If $A = A_1 \cor A_2$, then by the induction hypothesis, we have 
-	  $\vlderivation{\vlde{}{\{\acD, \me, \mee,
-	\meee\}}{A_i}{\vlhy {A_i \cor A_i}}}$ for $i = 1, 2$.
-
-	Hence, we have
-	\begin{prooftree}
-	  \hypo{\vdash S\{(A_1 \cor A_2) \cor (A_1 \cor A_2)\}}
-	  \infer1[$\equiv$]{\vdash S\{(A_1 \cor A_1) \cor (A_2 \cor A_2)\}}
-	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
-		   {\vdash S\{A_1 \cor (A_2 \cor A_2)\}}
-	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
-		   {\vdash S\{A_1 \cor A_2\}}
-	\end{prooftree}
-  \item If $A = A_1 \cand A_2$, then by the induction hypothesis, we have 
-$\vlderivation{\vlde{}{\{\acD, \me, \mee, \meee\}}{A_i}
-	      {\vlhy {A_i \cor A_i}}}$ for $i = 1, 2$.
-
- 	Hence, we have
-	\begin{prooftree}
-	  \hypo{\vdash S\{(A_1 \cand A_2) \cor (A_1 \cand A_2)\}}
-	  \infer1[$\me$]{\vdash S\{(A_1 \cor A_1) \cand (A_2 \cor A_2)\}}
-	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
-		   {\vdash S\{A_1 \cand (A_2 \cor A_2)\}}
-	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
-		   {\vdash S\{A_1 \cand A_2\}}
-	\end{prooftree}
-  \item If $A = \exists x A'$, then by the induction hypothesis, we have $\vlderivation{\vlde{}{\{\acD, \me, \mee,
-	\meee\}}{A'}{\vlhy {A' \cor A'}}}$.
-
-	Hence, we have
-	\begin{prooftree}
-	  \hypo{\vdash S\{\exists x A' \cor \exists x A'\}}
- 	  \infer1[$\mee$]{\vdash S\{\exists x (A' \cor A')\}}
-	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
-		   {\vdash S\{\exists x A'\}}
-	\end{prooftree}
-  \item If $A = \forall x A'$, then by the induction hypothesis, we have $\vlderivation{\vlde{}{\{\acD, \me, \mee,
-	\meee\}}{A'}{\vlhy {A' \cor A'}}}$.
-
-	Hence, we have
-	\begin{prooftree}
-	  \hypo{\vdash S\{\forall x A' \cor \forall x A'\}}
- 	  \infer1[$\meee$]{\vdash S\{\forall x (A' \cor A')\}}
-	  \ellipsis{$\{\acD, \me, \mee, \meee\}$}
-		   {\vdash S\{\forall x A'\}}
-	\end{prooftree}
-
-\end{itemize}
-
-\end{proof}
-
-\begin{lemma}
-The rules $\mee$ and $\meee$ are derivable for $\{\wD, \cD\}$.
-\end{lemma}
-
-\begin{proof}
-We have:
-\begin{center}
-\begin{prooftree}
-  \hypo{\vdash S\{\exists x A\}}
-  \infer1[$\equiv$]{\vdash S\{\exists x (A \cor \fff)\}}
-  \infer1[$\wD$]{\vdash S\{\exists x (A \cor B)\}}
-\end{prooftree}
-\hspace{0.5cm}
-and 
-\hspace{0.5cm}
-\begin{prooftree}
-  \hypo{\vdash S\{\exists x B\}}
-  \infer1[$\equiv$]{\vdash S\{\exists x (\fff \cor B)\}}
-  \infer1[$\wD$]{\vdash S\{\exists x (A \cor B)\}}
-\end{prooftree}
-\end{center}
-Thus, we have:
-
-\begin{center}
-\begin{prooftree}
-  \hypo{\vdash S\{\exists x A \cor \exists x B\}}
-  \ellipsis{}{\vdash S\{\exists x (A \cor B) \cor \exists x (A \cor B)\}}
-  \infer1[$\cD$]{\vdash S\{\exists x (A \cor B)\}}
-\end{prooftree}
-\end{center}
-Similar for $\meee$.
-\end{proof}
-
-Now we define a propositional encoding for first-order formulas.
-
-\begin{definition}
-The propositional encoding $\PE{A}$ of a formula $A$ is defined inductively by:
-
-\begin{centering}
-	$\PE{a} = a$ for every atom $a$
-
-	$\PE{(A \cor B)} = \PE{A} \cor \PE{B}$ \hspace{2cm} $\PE{(A \cand B)} =
-	\PE{A} \cand \PE{B}$
-
-	$\PE{(\forall x A)} = U_x \cor \PE{A}$ \hspace{2cm} $\PE{(\exists x A)}
-	= E_x \cand \PE{A}$
-
-\end{centering}
-where $U_x$ and $E_x$ are fresh nullary atoms.
-
-\end{definition}
-
-Similarly, we can define the propositional encoding $\PE{S}$ of a context $S$
-inductively by setting $\PE{\Box} = \Box$. Note that $\PE{S}$ is also a context.
-
-We have the following facts:
-
-\begin{proposition}
-For any context $S$ and any formula $A$:
-\begin{itemize}
-  \item $\PE{A}$ is a formula containing no quantifier for any formula $A$.
-  \item $\graphof(\PE{A}) = \graphof(A)$ by confounding the atoms $U_x$, $E_x$ with the variable
-	  $x$. Thus, a map $f : \graphof(\PE{A}) \rightarrow \graphof(\PE{B})$ can be seen as a map
-		$f : \graphof(A) \rightarrow \graphof(B)$.
-  \item $\PE{(S\{A\})} = \PE{S}\{\PE{A}\}$.
-\end{itemize}
-
-\end{proposition}
-
-\begin{proposition}
-\label{prop311}
-Let $A$ and $B$ be two formulas such that
-$\od{\odd{\odh {A}}{}{B}{\{\wD, \cD\}}}$. Then 
-$\od{\odd{\odh {\PE{A}}}{}{\PE{B}}{\{\wD, \cD\}}}$.
-\end{proposition}
-\begin{proof}
-  Trivial by induction.
-\end{proof}
-
-\begin{lemma}
-\label{mlem}
-	Given two formulas $A$ and $B$ and a derivation $\od{\odd{\odh {A}}
-	{\Delta}{B}{\{\wD, \cD\}}}$, then there exists a skew bifibration $G(A)
-	\rightarrow G(B)$.
-\end{lemma}
-
-\begin{proof}
-By Lemma \ref{lemma_ctr}, there exists a derivation $\od{\odd{\odh {A}}
-	{\Delta}{B}{\{\wD, \acD, \me, \mee, \meee \}}}$.
-
-For each rule from $\{\wD, \acD, \me, \mee, \meee \}$, we define a map and show that it is a skew fibration.
-
-\begin{itemize}
-  \item \begin{prooftree}
-  \hypo{\vdash S\{\fff \}}
-  \infer1[$\wD$]{\vdash S\{A\}}
-\end{prooftree}:
-
-  the map $wk$ maps $\fff$ to anything and is identity elsewhere.
-
-  \item
-    \begin{prooftree}
-      \hypo{\vdash S\{a \cor a\}}
-       \infer1[$\acD$]{\vdash S\{a\}} 
-    \end{prooftree}:
-
-    the map $ac$ maps the two $a$-labelled literals in the premise to the $a$-labelled literal in the conclusion.
-
-  \item 
-    \begin{prooftree}
-      \hypo{\vdash S\{(A \cand B) \cor (C \cand D)\}}
-      \infer1[$\me$]{\vdash S\{(A \cor C) \cand (B \cor D)\}}
-    \end{prooftree}:
-
-    the map $m$ is the canonical identity that maps $A$ to $A$, $\cdots$, $D$ to $D$.
-  \item 
-    \begin{prooftree}
-      \hypo{\vdash S\{\exists x A \cor \exists x B\}}
-      \infer1[$\mee$]{\vdash S\{\exists x (A \cor B)\}}
-    \end{prooftree}:
-
-    the map $m_1$ maps the two $x$-labelled binders in the premise to the $x$-labelled binder in the conclusion,  $A$ to $A$ and $B$ to $B$.
-  \item
-    \begin{prooftree}
-      \hypo{\vdash S\{\forall x A \cor \forall x B\}}
-      \infer1[$\meee$]{\vdash S\{\forall x (A \cor B)\}}
-    \end{prooftree}:
-
-    the map $m_2$ maps the two $x$-labelled binders in the premise to the $x$-labelled binder in the conclusion,  $A$ to $A$ and $B$ to $B$.
-
-\end{itemize}
-
-By considering propositional encodings, the maps defined are label-preserving
-skew fibrations on the underlying fographs according to
-\cite{str:07:RTA}.
-
-Now we prove that each map $g \in \{wk, ac, m, m_1, m_2 \}$ is a skew bifibration.
-To do that, it suffices to prove that $g$ is a fibration between the corresponding binding graphs since it is already a skew fibration on the corresponding fographs and it is label-preserving and existential-preserving.
-\begin{center}
-for each $x$-binder $b$ in $\graphof(\PE{B})$, for each vertex $v \in V(\graphof(\PE{A}))$
-such that $g(v)$ is bound by $b$, there exists a unique binder $b'$ such
-that $b'$ binds $v$.
-\end{center}
-
-\begin{itemize}
-  \item $wk$ and $m$ are clearly fibrations: the binding relations of the premise and the conclusion are exactly the same.
-  \item $ac$ is a fibration: suppose that $a$ that in the conclusion $a$ is bound by some quantifier $b$ in $S$, then for each of its preimages by $ac$, there exists exactly one binder (in fact, $b$) in $S$ that binds it.
-  \item $m_1$ and $m_2$ are fibrations: in the conclusion, for every atom $a$ in $A \cor B$ bound by the $x$-labelled quantifier, $a$ has exactly one preimage and it is bound by the $x$-llabelled quantifier in the premise.
-\end{itemize}
-
-  Therefore, all of these maps are skew bifibrations and since skew bifibrations
-on fographs compose (Lemma 10.32, \cite{hughes:fopws}), there exists a skew
-bifibration from $\graphof(A)$ to $\graphof(B)$.
-
-\end{proof}
-
-\begin{theorem_}
-If a formula $A$ is provable in $\LK$, then it has a combinatorial proof.
-\end{theorem_}
-
-\begin{proof}
-By Theorem \ref{thm1}, there exists a formula $A'$ such that there is a proof
-$\Pi$ of $A'$ in $\FOMLL$ and a derivation $D$ from $A'$ to $A$ consisting of
-the $\wD$ and $\cD$ rules only. The proof $\Pi$ corresponds to a unique
-unification net which is equivalent to the fonet corresponding to $\Pi$, i.e.,
-the fograph $\graphof(A')$ together with the links of $\Pi$. By Lemma \ref{mlem}, 
-there exists a skew bifibration $\graphof(A') \rightarrow \graphof(A)$. We have thus a
-combinatorial proof of $A$.
-
-\end{proof}
-
-\subsection{From skew bifibrations to contraction/weakening}
-
-\begin{theorem_}
-Let $A$ and $B$ be two formulas and $f: G(A) \rightarrow G(B)$ a skew bifibration. Then there exists a derivation $\od{\odd{\odh {A}}{\Delta}{B}{\{\wD, \cD\}}}$.
-\end{theorem_}
-
-$f$ can be seen as a skew fibration from $G(\PE{A})$ to $G(\PE{B})$, which gives the existence of the propositions $A'$ and $B'$, and of the following derivation:
-  \[\od{\odd{\odd{\odd{\odh{\PE{A}} }
-  {\Delta }{A'}{\me} }
-  {\Delta' }{B'}{\acD} }
-  {\Delta''}{\PE{B}}{\wD}} \]
-
-\begin{lemma} there exists $B''$ such that $\PE{B''}$ = $B'$.
-
-\begin{proof}
-Consider the dervation $\Delta''$. If some $U_x$ (or $E_x$) is introduced
-via weakening, then all the atoms it binds in $\PE{B}$ should also be introduced 
-via weakening. In fact, an atom of $\PE{B}$ is introduced via weakening is 
-equivalent to the fact that its corresponding vertex is not in the image of $f$. 
-Since there is an edge from $U_x$ (resp. $E_x$) to all the literals it binds in the 
-binding graph $\overrightarrow{\graphof(B)}$, if one of the atoms is in the image, 
-$U_x$ (resp. $E_x$) should also be in the image since $f$ is a fibration on binding graphs.
-
-This means that a such $B''$ can be obtained from $B$ by erasing all the $U_x$ and $E_x$ introduced via weakening and all the atoms they bind.
-\end{proof}
-\end{lemma}
-
-We introduce new (atomic) symbols $E_x^*$ and $U_x^*$ which are used to
-represent disjunctions of $E_x$ and $U_x$ respectiveley.
-
-We define a translation $(\cdot)^*$ inductively by:
-\begin{itemize}
-  \item $(E_x \cor \cdots \cor E_x)^* = E_x$
-  \item $(U_x \cor \cdots \cor U_x)^* = U_x$
-  \item structural recursion in all the other cases.
-\end{itemize}
-
-Then the derivation:
- \[\od{\odd{\odd{\odh{\PE{A}} }
-  {\Delta }{A'}{\me} }
-  {\Delta' }{\PE{B''}}{\acD}} \]
-can be translated to the derivation:
-\[\od{\odd{\odh{(\PE{A})^*} }
-{\Delta^* }{(\PE{B''})^*}{}} \]
-
-where $\Delta^*$ is the derivation obtained by replacing all the formulas $F$
-with $F^*$ and by applying the following rule transformation:
-
-\begin{center}
-\mbox{
-\begin{prooftree}
-  \hypo{S\{Q_x\}}
-  \infer1[$\acD$]{S\{Q_x\}}
-\end{prooftree}
-
-$\leadsto$
-
-\begin{prooftree}
-  \hypo{S\{Q_x\}}
-  \infer1[$=$]{S\{Q_x\}}
-\end{prooftree}
-
-}
-\vspace{0.4cm}
-
-\mbox{
-\begin{prooftree}
-  \hypo{S\{(E_x \cand C) \cor (E_x \cand D)\}}
-  \infer1[$\me$]{S\{E_x \cand (C \cor D)\}}
-\end{prooftree}
-
-$\leadsto$
-
-\begin{prooftree}
-  \hypo{S\{(E_x \cand C) \cor (E_x \cand D)\}}
-  \infer1[$\me'$]{S\{E_x \cand (C \cor D)\}}
-\end{prooftree}
-
-}
-
-\end{center}
-where $Q_x$ stands for $E_x$ or $U_x$.
-
-$\Delta^*$ can now be transformed into a valid derivation $\Delta_1$ by using the two
-transformation rules above and by applying them in a bottom-up style:
-\[\od{\odd{\odh{(\PE{A})^*} }
-{\Delta_1 }{(\PE{B''})^*}{\acD, \me, \me'}} \]
-
-\begin{lemma}
-Every line of $\Delta_1$ is a propositional encoding.
-
-\begin{proof}
-We proceed by bottom-up induction in the derivation.
-Clearly, $(\PE{B''})^*$ is a propositional encoding as there is no disjunction of $Q_x$
-in it.
-
-First consider the $\acD$ rule:
-\begin{prooftree}
-  \hypo{C \cor C}
-  \infer1[$\acD$]{C}
-\end{prooftree}
-
-It is clear that if $C$ is a propositional encoding, then so is $C \cor C$.
-
-Now consider the $\me$ rule:
-\begin{center}
-\begin{prooftree}
-  \hypo{S\{(C \cand D) \cor (E \cand F)\}}
-  \infer1[$\me$]{S\{(C \cor E) \cand (D \cor F)\}}
-\end{prooftree}
-\end{center}
-Suppose that $(C \cor E) \cand (D \cor F) = \PE{G}$ for some $G$.
-Since $C \cor E$ cannot be $Q_x$ (otherwise, the rule applied would be
-$\me'$), $G$ can be written as $G_1 \cand G_2$ with $C \cor E = \PE{G_1}$ and $D
-\cor F = \PE{G_2}$.
-
-We have thus $G_i = \forall x_i H_i$ or $J_i \cor K_i (i = 1, 2)$.
-
-If $G_i = \forall x H_i$ for some $i$, then there will be a conjunction of $U_x$
-and some formula which can never be eliminated by the rules $\me$, $\me'$ and
-$\acD$. However, there exists no such conjunction in ${\PE{A}}^*$, which leads to a
-contradiction.
-
-Hence, $G_i$ can be written as $J_i \cor K_i$ for $i = 1, 2$. We now have $(C
-\cand D) \cor (E \cand F) = \PE{((J_1 \cand J_2) \cor (K_1 \cand
-K_2))}$.
-
-Finally, consider the $\me'$ rule:
-\begin{center}
-\begin{prooftree}
-  \hypo{S\{(E_x \cand C) \cor (E_x \cand D)\}}
-  \infer1[$\me'$]{S\{E_x \cand (C \cor D)\}}
-\end{prooftree}
-\end{center}
-Suppose that $E_X \cand (C \cor D)$ = $\PE{F}$ for some $F$. It is clear
-that $F = \exists x G$ with $\PE{G} = C \cor D$ for some $G$.
-We distinguish two cases:
-\begin{itemize}
-  \item $G = \forall y H$: in this case, $(E_x \cand C) \cor (E_x \cand
-D)$ has a subformula $(E_x \cand U_y)$, which cannot be eliminated by the
-	rules $\me$, $\me'$, $\acD$. It is clear that ${\PE{A}}^*$ does not
-have a subformula of this form, which leads to a contradiction.
-  \item $G = G_1 \cor G_2$: in this case, $(E_x \cand C) \cor (E_x \cand
-  D) = \PE{((\exists x G_1) \cor (\exists x G_2))}$.
-\end{itemize}
-
-\end{proof}	
-\end{lemma}
-
-\hrule
-    \begin{itemize}
-    \item If none of
-    the four principal formulas in the premise is $x$ or $x\vlor F$ or
-    $x\vlan F$ for some formula $F$ and $x\in\VAR$, then this instance
-    of $\me$ can trivially be lifted, and and we can proceed by
-    induction hypothesis.
-  \item If exactly one of the four principal formulas in the premise
-    is $x$ for some $x\in\VAR$, then this $x$ is the encoding of an existential in the
-    premise and of an universal in the conclusion. This is impossible,
-    as $\phi$ has to preserve existentials.
-  \item If two of the four principal formulas in the premise
-    are $x$ for some $x\in\VAR$, then we are in the following special case of~\eqref{eq:mac}:
-      \begin{equation*}
-        \vlderivation{
-          \vlin{\acDeq}{}{\Scons{x\vlan(C\vlor D)}}{
-            \vlin{\me}{}{\Scons{(x\vlor x)\vlan(C\vlor D)}}{
-              \vlhy{\Scons{(x\vlan C)\vlor (x\vlan D)}}}}}
-      \end{equation*}
-      which can be lifted immediately to
-      \begin{equation*}
-        \vlinf{\mexD}{}{\Scons{\exists x.(C\vlor D)}}{\Scons{(\exists x.C)\vlor(\exists x.D)}}
-      \end{equation*}
-
-  \item $\me/\acDx$ as in situation~\eqref{eq:mac}: We must have
-    $R_1\cons{x}\fequ x\vlor E$ for some $E$ and $R_2\cons{x}\fequ
-    x\vlor F$ for some $F$ with $R\cons{x}\fequ x\vlor E\vlor
-    F$. Otherwise, the application of $\acDeq$ would not be correct.
-    We have the following four cases: 
-%    \begin{itemize}
-    \item $E$ and $F$ are both non-empty: Then~\eqref{eq:mac} is (modulo
-      omitted applications of $\fequ$):
-      \begin{equation*}
-        \vlderivation{
-          \vlin{\acDeq}{}{\Scons{(x\vlor E\vlor F)\vlan(C\vlor D)}}{
-            \vlin{\me}{}{\Scons{((x\vlor E)\vlor (x\vlor F))\vlan(C\vlor D)}}{
-              \vlhy{\Scons{((x\vlor E)\vlan C)\vlor ((x\vlor F)\vlan D)}}}}}
-      \end{equation*}
-      which can be lifted to
-      \begin{equation*}
-        \vlderivation{
-          \vlin{\mfaD}{}{\Scons{(\forall x.(E\vlor F))\vlan(C\vlor D)}}{
-            \vlin{\me}{}{\Scons{((\forall x. E)\vlor (\forall x. F))\vlan(C\vlor D)}}{
-              \vlhy{\Scons{((\forall x. E)\vlan C)\vlor ((\forall x. F)\vlan D)}}}}}
-      \end{equation*}
-    \juihsuan{maybe need some words to exclude the case in which $C$ (or $D$)
-is a propositional variable.}\lutz{shit. (you mean a ``first order variable'') this actually can happen. then we have another $\mexD$}
-    \item $E$ is empty and $F$ is not: Then~\eqref{eq:mac} becomes
-      \begin{equation*}
-        \vlderivation{
-          \vlin{\acDeq}{}{\Scons{(x\vlor F)\vlan(C\vlor D)}}{
-            \vlin{\me}{}{\Scons{(x\vlor (x\vlor F))\vlan(C\vlor D)}}{
-          \vlhy{\Scons{(x\vlan C)\vlor ((x\vlor F)\vlan D)}}}}}
-      \end{equation*}
-      The conclusion is the propositional encoding of $\Scons{(\forall
-        x. F)\vlan(C\vlor D)}$ and the premise is the propositional
-      encoding of $\Scons{(\exists x.C)\vlor ((\forall x. F)\vlor
-        D)}$. Also note that no $\me$-instance can break up the
-      conjunction in $x\vlan C$ in the premise. Hence, $\phi$ maps an
-      existential to a universal, which is ruled out by the
-      definition. Hence, this case cannot occur.
-    \item $E$ is non-empty and $F$ is empty: This case is similar to the
-      previous subcase.
-    \item   $E$ and $F$ are both empty: Then~\eqref{eq:mac} is
-      \begin{equation*}
-        \vlderivation{
-          \vlin{\acDeq}{}{\Scons{x\vlan(C\vlor D)}}{
-            \vlin{\me}{}{\Scons{(x\vlor x)\vlan(C\vlor D)}}{
-              \vlhy{\Scons{(x\vlan C)\vlor (x\vlan D)}}}}}
-      \end{equation*}
-      which can be lifted immediately to
-      \begin{equation*}
-        \vlinf{\mexD}{}{\Scons{\exists x.(C\vlor D)}}{\Scons{(\exists x.C)\vlor(\exists x.D)}}
-      \end{equation*}
-    \end{itemize}
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
-
-\end{document}

### 2021-04-26 LICS2021-final.tex
Add the copyright notice
tweaked lics final version

@@
 
-\documentclass[conference,twosided,10pt]{IEEEtran}
+\documentclass[conference,10pt]{IEEEtran}
 % Some Computer Society conferences also require the compsoc mode option,
@@
 
+%% \newcommand{\longer}[2]{#1}
+%% \newcommand{\shorter}[2]{#2}
+
+%% %\let\choice=\longer
+%% \let\choice=\shorter
+
+\IEEEoverridecommandlockouts
+%\IEEEpubid{\makebox[\columnwidth]{\emph{[Long version of the LICS 2021 paper, with proofs in the appendix.]}\hfill}
+%    \hspace{\columnsep}\makebox[\columnwidth]{ }}
+\IEEEpubid{\makebox[\columnwidth]{978-1-6654-4895-6/21/\$31.00~
+\copyright2021 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
+
 % make the title area
@@
 different syntactic proof systems, based on different sets of inference rules.
-Just consider the derivations in Figure~\ref{fig:translate}, showing two proofs of the formula $\peirceformula$ and two proofs of the formula $\veedrinkerformula$, one in the sequent calculus (top) and one in a deep inference system (bottom).
-It is, \emph{a priori}, not clear how to compare them.
+Consider the derivations in Figure~\ref{fig:translate}, showing two proofs of the
+formula $\peirceformula$ and two proofs of the formula $\veedrinkerformula$,
+in sequent calculus (top) and in a deep inference system (bottom).
+It is, \emph{a priori}, not clear how to compare them.%
 %
@@
           \vlhy{}}}}}}
-}
+}%
 \newcommand\dipeirceproof{
@@
                       \vlhy{\ttt}}}}}}}}}}}}
-}
+}%
 \newcommand\lkdrinkerproof{
@@
                   \vlhy{}}}}}}}}}}}
-}
+}%
 \newcommand\ksonedrinkerproof{
@@
                           \vlhy{\ttt}}}}}}}}}}}}}}
-}
-\begin{figure}\vspace{-2ex}\begin{center}\hspace*{-0ex}\begin{math}
+}%
+\begin{figure}\vspace{-4ex}\begin{center}\hspace*{-0ex}\begin{math}
 \newcommand\peircescale{.75}
@@
 natural definition of proof identity for propositional logic: two
-proofs are \emph{the same}, if they are mapped to the same
+proofs are \emph{the same} if they are mapped to the same
 combinatorial proof.
@@
 For example, a first-order combinatorial proof of Smullyan's 
-``drinker paradox'' $\drinkerformula=\veedrinkerformula$ is shown on the
-right of Fig.\,\ref{fig:translate}, %\todo{wrong implies symbol in drinkerformula?}
+\emph{drinker paradox} \mbox{$\drinkerformula$} $=$ \mbox{$\veedrinkerformula$}
+is shown on the right of Fig.\,\ref{fig:translate}, 
 a homomorphism from a partially coloured graph to a labelled graph.
 However, even though Hughes proves soundness and completeness, the 
-proof is highly unsatisfactory: (1) the soundness argument is extremely
-long, intricate and cumbersome, and (2) the completeness proof does not 
+proof is unsatisfactory: (1) the soundness argument is long, intricate
+and cumbersome, and (2) the completeness proof does not 
 allow a syntactic proof to be read back from a combinatorial proof, i.e.,
@@
 We solve these issues by moving to a deep inference
-system. More precisely, we introduce a new proof system, called
+system. More precisely, we introduce a new proof system,
 $\FOKS$, for first-order logic, that (a) reflects every combinatorial
 proof, i.e., there is a surjection from $\FOKS$ proofs to
-combinatorial proofs, (b) yields far simpler proofs of
+combinatorial proofs, (b) yields simpler proofs of
 soundness and completeness for combinatorial proofs, and (c) admits
@@
 %
-The right side of Fig.\,\ref{fig:translate}
-illustrates the surjection in (a), and since the syntactic proofs 
-of the two systems both translate to the same combinatorial proof,
+The right of Fig.\,\ref{fig:translate}
+illustrates surjection in (a), and since the syntactic proofs 
+in the two systems translate to the same combinatorial proof,
 they can be considered \emph{the same}.
@@
 linear logic, followed by a proof consisting only of contractions and
-weakenings. In this paper we show that the same is possible for
+weakenings (see also \cite[\S4]{hughes:invar}).
+In this paper we show that the same is possible for
 first-order logic.
@@
 \bfit{dual}
-$\dual{p}$. The grammars below generate
+$\dual{p}$ with $\dual{\dual p}\mkern6mu{\neq}\mkern5mu\dual p$. The grammars below generate
 the set $\TERM$ of \bfit{terms}, denoted by $s,t,u,\ldots$, the set
@@
 where the arity of $f$ and $p$ is $n$.
-For better readability we often omit parentheses and write simply $ft_1 \dots t_n$ or $pt_1 \dots t_n$.
+For better readability we often omit parentheses and write $ft_1 \dots t_n$ or $pt_1 \dots t_n$.
 We consider the truth constants
 $\ttt$ (\emph{true}) and $\fff$
-(\emph{false}) as additional atoms, and we consider all formulas in negation
+(\emph{false}) as additional atoms, and consider all formulas in negation
 normal form, where \bfit{negation} $(\dual\cdot)$ is defined on
@@
 \begin{equation*}
-  \begin{array}{ccc}
-    \dual{\dual a} = a
-    &
+  \begin{array}{c@{\hspace{6ex}}c}
+%    \dual{\dual a} = a
+%    &
   \dual\ttt =\fff &
   \dual{p(t_1,\ldots,t_n)} = \dual{p}(t_1,\ldots,t_n) \\[.5ex]
-  &
+%  &
   \dual\fff = \ttt &
   \dual{\dual p(t_1,\ldots,t_n)} = p(t_1,\ldots,t_n) \\[.5ex]
-  &
+%  &
   \dual{\exists x.A} = \forall x.\dual{A}
   &
-  \dual{A \vlan B} = \dual{A} \ \vlor \ \dual{B} 
-  \\[.5ex]
-  &
+  \dual{A \vlan B} = \dual{A} \ \vlor \ \dual{B} \\[.5ex]
+%  &
   \dual{\forall x.A} = \exists x.\dual{A}
@@
 \end{equation*}
-Then we write $A\implies B$ as abbreviation for $\dual A\vlor B$.
+Note that $\dual{\dual a} = a$.
+We write $A\implies B$ as abbreviation for $\dual A\vlor B$.
 
@@
 one another and from all free variables. Every formula can be
-transformed into a logically equivalent rectified form, by simply
-renaming the bound variables. If we consider formulas equivalent
-modulo $\alpha$-conversion (renaming of bound variables), then the
+transformed into a logically equivalent rectified form by
+bound variable renaming, e.g.\
+%
+\mbox{$(px \vee \exists xqx) \wedge \exists x r$} $\mapsto$ \mbox{$(px \vee \exists yqy) \wedge \exists zrz$}.
+%
+If we consider formulas equivalent
+modulo bound variable renaming, the
 rectified form of a formula $A$ is uniquely defined, and we denote it
@@
 \subsection{Sequent Calculus $\FOLK$}
+
+\bfit{Sequents}, denoted by $\Gamma,\Delta,\ldots$, are finite
+multisets of formulas, written as lists, separated by comma. The
+\bfit{corresponding formula} of a (non-empty) sequent $\Gamma=A_1,A_2,\ldots,A_n$
+is the disjunction of its formulas: $\form\Gamma=A_1\vlor
+A_2\vlor\cdots\vlor A_n$. A sequent is \bfit{rectified} iff its
+corresponding formula is.
+
+In this paper we use the sequent calculus $\FOLK$, shown in
+Figure~\ref{fig:LK1}, which is a one-sided variant of Gentzen's
+original calculus~\cite{gentzen:35:I} for first-order logic. To
+simplify some technicalities later in this paper, we include
+the $\mixr$ rule.
+%
+\begin{thm}
+  $\FOLK$ is sound and complete for first-order logic.
+\end{thm}
+%
+\noindent For a proof, see any standard textbook, e.g.~\cite{TS:00}.
+
+The linear fragment of $\FOLK$, i.e., the fragment without the rules
+$\conr$ (\emph{contraction}) and $\weakr$ (\emph{weakening}) defines
+\emph{first-order multiplicative linear
+logic}~\cite{girard:87,girard:88} \emph{with
+mix}~\cite{fleury:retore:94,bellin:97}~(MLL1+mix). We denote that
+system here with $\FOMLL$ (shown in Figure~\ref{fig:LK1} in the dashed
+box).
+
+We will use the cut elimination theorem. The \bfit{cut} rule is
+\begin{equation}
+  \vliinf{\cutr}{}{\sqn{\Gamma,\Delta}}{\sqn{\Gamma,A}}{\sqn{\dual A,\Delta}}
+\end{equation}
+
+\begin{thm}
+  \label{thm:cutelim}
+  If a sequent $\sqn\Gamma$ is provable in $\FOLKcut$ then it is also
+  provable in $\FOLK$. Furthermore, if $\sqn\Gamma$ is provable in
+  $\FOMLLcut$ then it is also provable in $\FOMLL$.
+\end{thm}
+%
+\noindent As before, this is standard, see e.g.~\cite{TS:00} for a proof.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Preliminaries: First-order Graphs}\label{sec:fographs}
+
+% We recall the definition of \emph{first-order graph} or \emph{fograph}
+% \cite[\S3]{hughes:fopws}, used to represent first-order formulas.
+
+\subsection{Graphs}
+
+A \bfit{graph} $\gG=\tuple{\vG,\eG}$ is a pair where $\vG$ is a finite
+set of \bfit{vertices} and $\eG$ is a finite set of \bfit{edges},
+which are two-element subsets of $\vG$. We write $vw$ for an edge
+$\set{v,w}$.
+
+Let $\gG=\tuple{\vG,\eG}$ and $\gH=\tuple{\vH,\eH}$ be graphs such
+that $\vG\cap\vH=\emptyset$. A \bfit{homomorphism}
+$\phi\colon\gG\to\gH$ is a function $\phi\colon\vG\to\vH$ such that if
+$vw\in\eG$ then $\phi(v)\phi(w)\in\eH$. The \bfit{union} $\gG +\gH$ is
+the graph $\tuple{\vG \cup\vH,\eG\cup \eH}$ and the \bfit{join} $\gG
+\times \gH$ is the graph $\tuple{\vG \cup\vH,\eG \cup \eH \cup \set{vw
+\mid v \in \vG, w \in \vH}}$.  A graph $\gG$ is \bfit{disconnected}
+if $\gG=\gG_1+\gG_2$ for two non-empty graphs $\gG_1,\gG_2$, otherwise
+it is \bfit{connected}.
+%It is \bfit{coconnected} if its complement is connected.
+
+A graph $\gG$ is \bfit{labelled} in a set $L$ if each vertex $v\in\vG$
+has a \bfit{label} $\labelof v\in L$ associated with it.
+A graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
+equivalence relation $\linkingof\gG$ on $\vG$; each equivalence class
+is a \bfit{colour}.\footnote{In \cite{hughes:fopws}
+adjacent vertices are required to have distinct colours, since it
+is part of the standard definition of colouring in graph
+theory.
+However, this condition is redundant (ommitted here), since it is implied
+by the preclusion of bimatchings in the next section.}
+%Therefore we do not have this additional condition here.}
+A \bfit{vertex renaming} of
+$\gG=\tuple{\vG,\eG}$ along a bijection
+$(\hat\cdot)\colon\vG\to\hat\vG$ is the graph
+$\hat\gG=\tuple{\hat\vG,\set{\hat v\hat w\mid vw\in\eG}}$, with
+colouring and/or labelling inherited (i.e., $\hat v\samecol\hat w$ if
+$v\samecol w$, and $\ell(\hat v)=\ell(v)$). Following standard graph
+theory, we identify graphs modulo vertex renaming.
+
+A \bfit{directed graph} $\gG =\tuple{\vG,\eG}$ is a set $\vG$ of
+\bfit{vertices} and a set $\eG\subseteq \vG\times\vG$ of \bfit{direct edges}.
+A \bfit{directed graph homomorphism}
+$\phi\colon\tuple{\vG,\eG}\to\tuple{\vH,\eH}$ is a function $\phi\colon\vG\to\vH$ such that if
+$\pair{v,w}\in\eG$ then $\pair{\phi(v),\phi(w)}\in\eH$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-In a graph $\gG$, the \bfit{neighbourhood} $N(v)$ of a vertex $v \in\vG$ is defined as
-the set $\set{w \mid vw \in\eG}$. A \bfit{module} is a set $M \subseteq \vG$
-such that $N(v) \setminus M = N(w) \setminus M$
+In a graph $\gG$, the \bfit{neighbourhood} $N(v)$ of a vertex $v \in\vG$ is
+$\set{w \mkern-2mu\mid\mkern-2mu vw \mkern-2mu\in\mkern-2mu\eG}$. A \bfit{module} is a set $M \mkern-2mu\subseteq\mkern-2mu \vG$
+with $N(v) \mkern-1mu\setminus\mkern-1mu M = N(w) \mkern-1mu\setminus\mkern-1mu M$
 for all $v, w \in M$. A module $M$ is \bfit{strong} if for every
-module $M'$, we have $M' \subseteq M$, $M \subseteq M'$ or $M \cap M' =
+module $M'$ we have $M' \mkern-2mu\subseteq\mkern-2mu M$, $M \mkern-2mu\subseteq\mkern-2mu M'$ or $M \cap M' =
 \emptyset$. A module is \bfit{proper} if it has two or more vertices.
-
-%% Modules in cographs correspond precisely to the subtrees of the
-%% cotrees (the term-trees constructing the graph via $+$ and~$\times$).\todo{Cotree
-%% must alternate $+$ and $\times$. Skip this comment completely?}
 
@@
 atom or variable, and it has at least one atom-labelled vertex. An
-atom-labelled vertex is called a \bfit{literal} and a
-variable-labelled vertex is called a \bfit{binder}. A binder labelled
-with $x$ is called an \bfit{$x$-binder}. The \bfit{scope} of a binder
+atom-labelled vertex is a \bfit{literal} and a
+variable-labelled vertex is a \bfit{binder}. A binder labelled
+with $x$ is an \bfit{$x$-binder}. The \bfit{scope} of a binder
 $b$ is the smallest proper strong module containing $b$.
@@
 %
-\begin{definition}
-A \bfit{first-order graph} or \bfit{fograph} is a logical cograph in which all binders are legal. The
-\bfit{binding graph} of a fograph $\gG$ is the directed graph $\bG=\tuple{\vG,
+\begin{definition}[{\cite[\S3]{hughes:fopws}}]
+A \bfit{first-order graph} or \bfit{fograph} $\gG$ is a logical cograph whose binders are all legal. The
+\bfit{binding graph} of $\gG$ is the directed graph $\bG=\tuple{\vG,
 \set{(b, l) \mid b \text{ binds } l}}$.
@@
 graphs, inductively as follows:
-%% For a formula $A$, we can define its
-%% associated fograph $\graphof{A}$ inductively by:\todo{duplicate two sentences above}
+%
 \begin{equation*}
@@
   structural induction on $A$.
-  %% :
-  %% \begin{itemize}
-  %%   \item Trivial if $A$ is an atom.
-  %%   \item The induction step uses the following fact:
-  %%         if $M$ is a module of $\gG$ and $M' \subseteq M$, then $M'$ is a
-  %%         module of $\gG$ if and only if it is a module of $\gG[X]$.
-  %% \end{itemize}
-  %% \todo{}\lutz{maybe mention also fn 2-5 in Dominic's arxiv-paper}
 \end{proof}
-%%\juihsuan{I'm still looking for a simple proof}
 %
 \begin{remark}
-Note that $\graphof A$ is not necessarily a fograph if $A$ is not
+Note that $\graphof A$ need not be a fograph if $A$ is not
 rectified. If $A = (\forall x. px) \vlor (\forall x. qx)$, then
@@
 %
-%% For this reason, we call a formula
-%% \bfit{clean} if it does not contain subformulas of the form $(\forall
-%% x.A)\vlor(\forall x.B)$ or $(\exists x.A)\vlan(\exists x.B)$,
-%% \todo{need the four cases as in clear definition in fopws? Consider
-%% $(\forall x.A)\vlor(B\vlor (\forall x.C))$. But then Lemma 6 doesn't hold.
-%% (fopws proves only that there's a surjection from clear formulas onto fographs,
-%% whose kernel is the six formula equalities)} and no
-%% $x$-quantified formula occurs as subformula of another $x$-quantified
-%% formula. Then we have:
-%
-%% \begin{lemma}
-%%   If $A$ is clean iff\/ $\graphof A$ is a fograph.
-%% \end{lemma}
-%
-%% \begin{proof}
-%%   Induction on $A$, using  Theorem~\ref{thm:cograph}.
-%% \end{proof}
-%
-%% Even though for every formula $A$ we can obtain an
-%% equivalent clean formula by simply renaming some bound variables, this
-%% is not unique up to $\alpha$-conversion, as is the case for
-%% rectified formulas.
-%
-\noindent We define a congruence relation $\fequ$ on formulas by the following equations:
+\noindent We define a congruence relation $\fequ$ on formulas, called \bfit{equivalence},
+by the following equations:
 \begin{equation}
@@
 where $x$ must not be free in $B$ in the last two equations.
-Two formulas $A$ and $B$ are \bfit{equivalent} if $A \fequ B$. We have the
-following theorem:
-\begin{thm}
+%Two formulas $A$ and $B$ are \bfit{equivalent} if $A \fequ B$.
+%We have the following theorem:
+\begin{thm}[{\cite[\S10]{hughes:fopws}}]
   Let $A,B$ be rectified formulas. Then
@@
 \begin{proof}
-  Straightforward induction on $A$.
+  A straightforward structural induction on formulas.
 \end{proof}
@@
 \begin{example}
-  Both $\veedrinkerformula$ and $\variantveedrinkerformula$, which are
-  equivalent modulo $\fequ$, have the same (rectified) fograph
-  $\drinkergraph$, shown below-left.
+  \mbox{$\veedrinkerformula$} $\fequ$ \mbox{$\variantveedrinkerformula$}, and both formulas
+  %The formulas \mbox{$\veedrinkerformula$} and \mbox{$\variantveedrinkerformula$}, which are
+  %equivalent modulo $\fequ$,
+  have the same (rectified) fograph
+  $\drinkergraph$, below-left.
   %
@@
   \end{equation*}
-  Above-middle we show the \emph{cotree} of the underlying
+  Above-center we show the \emph{cotree} of the underlying
   cograph (illustrating the idea behind Theorem~\ref{thm:cograph}) and
@@
 Two atoms are \bfit{pre-dual} if they are not $\ttt$ or $\fff$, and their predicate symbols are dual
-(e.g. $p(x, y)$ and $\dual{p}(y, z)$) and two literals are \bfit{pre-dual} if their
+(e.g.\ $p(x, y)$ and $\dual{p}(y, z)$) and two literals are \bfit{pre-dual} if their
 labels (atoms) are pre-dual. A \bfit{linked fograph} $\tuple{\gC,\linkingof\gC}$ is a coloured fograph $\gC$ such
@@
 
-\begin{definition}
+\begin{definition}[{\cite[\S5]{hughes:fopws}}]
 A \bfit{first-order net} or \bfit{fonet} is a linked fograph which
@@
   \begin{center}
-    \vspace{-1ex}
+    \vspace{-3ex}
     \begin{tikzpicture}[graph]
@@
 %
-%\noindent
-Figure~\ref{fig:leap} shows a fonet with a unique dualizer, and its leap graph.
-
+\noindent
+Figure~\ref{fig:leap} shows a fonet with its dualizer and leap graph.%
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
+%
+\begin{figure*}%
   $$
@@
     function symbols), $p$ is a unary predicate symbol, and $q$ is a
-    binary predicate symbol.}
+    binary predicate symbol. For each skew bifibration $\phi$,
+    the variable substitution $\protect\rsubstof\phi$ is an identity,
+    thus we can omit labels from each (coloured) source fograph
+    (since the label of $v$ in the source is that of $\phi(v)$ in the target).}
   \label{fig:cps}
-\end{figure*}
-
-\begin{figure*}
+\end{figure*}%
+%
+\begin{figure*}\vspace{-2ex}%
   $$
@@
   %\vspace{-4ex}
-\end{figure*}
+\end{figure*}%
 
@@
 A graph homomorphism $\phi\colon \tuple{\vG, \eG} \rightarrow
-\tuple{\vH, \eH}$ is a \bfit{fibration} if for all $v \in \vG$ and
+\tuple{\vH, \eH}$ is a \bfit{fibration} \cite{grothendieck:fibration,Gray:fibration} if
+for all $v \in \vG$ and
 $w\phi(v) \in \eH$, there exists a unique $\tilde{w} \in \vG$ such
 that $\tilde{w}v \in \eG$ and $\phi(\tilde{w}) = w$ (indicated below-left),
-and is a
-\bfit{skew fibration} if for all $v \in \vG$ and $w\phi(v) \in \eH$
+and is a \bfit{skew fibration} \cite[\S3]{hughes:pws} if
+for all $v \in \vG$ and $w\phi(v) \in \eH$
 there exists $\tilde{w} \in \vG$ such that $\tilde{w}v \in \eG$ and
@@
 %
-\begin{definition}
+\begin{definition}[{\cite[\S4]{hughes:fopws}}]
   Let $\gG$ and $\gH$ be fographs. A \bfit{skew bifibration}
@@
 %
-%%\subsection{First-order combinatorial proofs}
-%
-\begin{definition}
+%
+\begin{definition}[{\cite[\S6]{hughes:fopws}}]
 A \bfit{first-order combinatorial proof} (\bfit{FOCP}) of a fograph $\gG$ is a skew
@@
 %
-Figure~\ref{fig:cps} shows examples of
+\noindent Figure~\ref{fig:cps} shows examples of
 FOCPs (taken from~\cite{hughes:fopws}), each above the formula it proves.
@@
 graph left implicit.
-%  (No information is lost, since 
-% atom/quantifier-occurrences in a formula
-% are in bijection with vertices of its graph.)
-%
-\begin{thm}[\cite{hughes:fopws}]
+
+\begin{thm}[{\cite[\S6]{hughes:fopws}}]
   \label{thm:FOCP}
@@
   definition of~\cite{hughes:fopws}, as we allow for a variable
-  renaming $\rsubstof\phi$ which was forced to be the identity
+  renaming $\rsubstof\phi$ which was restricted to be the identity
   in~\cite{hughes:fopws}.
-  %The reason for this relaxation in our case is that we want to cover a richer class of proofs, also allowing 
 \end{remark}
@@
 rewriting rules inside any (positive) formula or sequent
-\bfit{context}, which is denoted as $\Sconhole$, and which is a
+\bfit{context}, which is denoted by $\Sconhole$, and which is a
 formula (resp.~sequent) with exactly one occurrence of the \bfit{hole}
@@
 Figure~\ref{fig:KS1} shows the inference rules for the deep inference
-system~$\FOKS$ that we introduce in this paper. It is a slight
+system~$\FOKS$ introduced in this paper. It is a
 variation of the systems presented by Br\"unnler~\cite{brunnler:phd}
@@
 and prove them in later sections. The
-first is routine and expected, but needs to be proved nonetheless:
+first is routine and expected, but must be proved nonetheless:
 
@@
 \begin{proof}
-  This is a straightforward exercise.
-%%  that we leave to the reader. (Note that the
-%%$\ax$-rule can be applied to $\sqn{\fff,\ttt}$ in the cases of $\rr = \faD$.)
+  A routine exercise.
 \end{proof}
@@
 \begin{proof}
-  Straightforward induction on  $\Sconhole$. (see e.g. \cite{gug:str:01})
+  A straightforward induction on $\Sconhole$. (see e.g.~\cite{gug:str:01})
 \end{proof}
@@
   a $\FOMLL$ proof $\Proof$ of $\sqn{\Scons A}$.
-  %% If $\rr$ is
-  %% $\upsmash{\vlinf{\aiD}{}{\Scons{a\vlor\cneg a}}{\Scons\ttt}}$, we replace
-  %% in $\Pi$ all corresponding occurrences of $\ttt$ with
-  %% $a \vlor \cneg a$ and the rule instance
-  %% $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation $ \vlderivation{
-  %%   \vlin{\vlor}{}{\sqn{a \vlor \cneg a}}{ \vlin{\axr}{}{\sqn{a, \cneg
-  %%         a}}{ \vlhy{}}}} $. This gives us a proof of
-  %% $\sqn{\Scons{a \vlor \cneg a}}$. In all other cases, 
-  %%   %\item $\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$
-  %%    % In this case, we replace simultaneously in $\Pi$ the corresponding
-  %%    % occurrences of $\ttt$ with $\forall x.\ttt$ and the rule instance
-  %%    % $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ with the derivation
-  %%    % $
-  %%    % \vlderivation{
-  %%    %   \vlin{\forall}{}{\sqn{\forall x.\ttt}}{
-  %%    %     \vlin{\axr}{}{\sqn{\ttt}}{
-  %%    %       \vlhy{}}}}
-  %%    % $, and we get a proof $\Pi'$ of $\sqn{\Scons{\forall x.\ttt}}$.
       By Lemmas~\ref{lem:shallow} and~\ref{lem:context}, we have a $\FOMLL$ proof of
-      $\sqn{\cneg{\Scons A},\Scons B}$. We can compose them via $\cutr$:
+      $\sqn{\cneg{\Scons A},\Scons B}$. We can compose them via
+%  $\cutr$:
       \begin{equation*}
@@
   $\weakr$. Then the instances of $\weakr$ and $\conr$ are replaced by
-  $\wD$ and $\cD$, which can then be permuted down. Details are in
-  Appendix~\ref{app:LK1-decompose}.
+  $\wD$ and $\cD$, which can then be permuted down.
+  %Details are in
+  %Appendix~\ref{app:LK1-decompose}.
 \end{proof}
@@
   there are formulas $A'$ and $A''$ such that 
-  \begin{equation*}
+  \vspace{-2ex}\begin{equation*}\hspace{-2ex}
     \vlderivation{
@@
   there are formulas $A'$ and $B'$ such that 
-  \begin{equation*}
+  \begin{equation*}\hspace{-3ex}
     \vlderivation{
@@
 \begin{proof}
-  We first permute all instances of $\wD$ and $\wfaD$ to the bottom of
-  the derivation and then permute in a second step the rules $\cD$ and
+  Permute all $\wD$ and $\wfaD$ instances to the bottom of
+  the derivation, then permute all $\cD$ and
   $\cfaD$ below $\set{\me,\mfaD,\mexD}$. This involves a tedious but
-  straightforward case analysis. However, unlike most other rule
+  routine case analysis. However, unlike most other rule
   permutations in this paper, this has not been done before in the deep
-  inference literature. For this reason, we give the full case
-  analysis in Appendix~\ref{app:cw-decomposition}. Note that this
+  inference literature. 
+%  For this reason, we give the full case
+%  analysis in Appendix~\ref{app:cw-decomposition}.
+  This
   Lemma is the reason for the presence of the rules $\wfaD$ and
@@
 \begin{proof}
-  We have to show that none of the operations above can introduce a
+  We must show that none of the operations above introduces a
   bimatching. For cases 1--6, this is immediate. For case 7, observe
@@
 There is a more direct path from a $\FOMLL$ proof $\Pi$ of a rectified
-sequent $\Gamma$ to the linked fograph $\fographof\Pi$: simply take
+sequent $\Gamma$ to the linked fograph $\fographof\Pi$: take
 the fograph $\graphof\Gamma$, and let the equivalence classes of
 $\linkingof\Pi$ be all the atom pairs that meet in an instance of
-$\ax$, and $\dsubstof\Pi$ is simply the collection of all substitutions
-of all the instances of the $\exists$-rule in $\Pi$.
-%
-We have chosen the more cumbersome path above because it gives us a
+$\ax$, and $\dsubstof\Pi$ comprises the substitutions
+at the $\exists$-rules in $\Pi$.
+%
+We chose the more cumbersome path above because it gives us a
 direct proof of Theorem~\ref{thm:MLL1->fonet}.
@@
 
-First observe that in a derivation in $\FOMLS$
+In a derivation in $\FOMLS$
 where the conclusion is rectified, every line is also rectified, as
 the only rules involving bound variables are $\forall$ and $\exists$
-which both remove a binder.
+which (upwards) both remove a binder.
 Therefore, we can call such a derivation \bfit{rectified}, and
-%% if every line in $\Deri$ is
-%% rectified.
-%
-%% \begin{lemma}
-%%   Let  $\Deri$ be a $\FOMLS$ proof of a formula $A$. Then $\Deri$ is rectified iff $A$ is rectified.
-%% \end{lemma}
-%
-%% \begin{proof}
-%%    The only rules involving bound
-%%    variables are $\forall$ and $\exists$ which both remove a binder (and
-%%    all occurrences of the variable it binds).
-%% \end{proof}
-%
-%% Hence,
 for a non-rectified  $\FOMLS$ derivation $\Deri$ we can
@@
 $A$ to the terms substituted for them in the instances of the
-$\exists$-rule in $\Phi$. We denote this substitution with
+$\exists$-rule in $\Phi$. We denote this substitution by
 $\dsubstof\Phi$ and call it the \bfit{dualizer} of
@@
 
-For proving this theorem, we have to show that no inference rule in
+To prove this theorem, we have to show that no inference rule in
 $\FOMLS$ can introduce a bimatching. To simplify the argument, we
@@
   constructed. The construction of $\DDeri_2$, using $\sw$ and $\fequ$, is standard, see,
-  e.g. \cite{ATS:esslli2019,gug:str:01,brunnler:tiu:01,dissvonlutz}. Then, every
+  e.g.~\cite{ATS:esslli2019,gug:str:01,brunnler:tiu:01,dissvonlutz}. Then, every
   occurrence of $\forall y_j.F$ is replaced by
@@
 \begin{proof}
-  Straightforward induction on $A$. 
+  A straightforward induction on $A$. 
 \end{proof}
@@
   derivation in $\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$, in a similar
-  way as in the previous lemma. The technical details are in
-  Appendix~\ref{app:surj->cm}.
+  way as in the previous lemma.
+  %The technical details are in
+  %Appendix~\ref{app:surj->cm}.
 \end{proof}
@@
 
-In this paper we have uncovered a close correspondence between
+We uncovered a close correspondence between
 first-order combinatorial proofs and decomposed deep inference
-derivations of system $\FOKS$, and we have shown that every proof in
+derivations of system $\FOKS$, and showed that every proof in
 $\FOKS$ has such a decomposed form.
@@
 propositional logic~\cite{hughes:invar,str:fscd17}, but both have
-their insufficiencies, and they have not been extended to other
+their insufficiencies, and have not been extended to other
 logics.
 
-Nonetheless, we hope to get new insights in the normalisation of
+We hope to garner new insights on the normalisation of
 classical first-order proofs through our work on combinatorial proofs.
@@
 
-\clearpage
-
+\end{document}
+
+%\clearpage
+\newpage
 \appendix
@@
     \end{equation*}
-  \item In all other cases (e.g. exactly one of the principal formulas
+  \item In all other cases (e.g.\ exactly one of the principal formulas
     is of shape $x\vlor F$ (and none is $x$), we can trivially lift

### 2021-04-26 LICS2021-final.tex
fixed typo
tweak

@@
 \end{equation*}
-Note that $\dual{\dual a} = a$.
-We write $A\implies B$ as abbreviation for $\dual A\vlor B$.
+Note $\dual{\dual a} = a$.
+We write $A\implies B$ as an abbreviation for $\dual A\vlor B$.
 
@@
 If we consider formulas equivalent
-modulo bound variable renaming, the
-rectified form of a formula $A$ is uniquely defined, and we denote it
+modulo bound variable renaming ($\alpha$-conversion), the
+rectified form of a formula $A$ is unique, and we denote it
 by $\rectif A$.

### 2021-04-26 LICS2021-final-with-appendices-for-arxiv.tex
final-with-app

--- 2021-04-26 LICS2021-final.tex
@@
 \IEEEoverridecommandlockouts
-%\IEEEpubid{\makebox[\columnwidth]{\emph{[Long version of the LICS 2021 paper, with proofs in the appendix.]}\hfill}
-%    \hspace{\columnsep}\makebox[\columnwidth]{ }}
-\IEEEpubid{\makebox[\columnwidth]{978-1-6654-4895-6/21/\$31.00~
-\copyright2021 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
+\IEEEpubid{\makebox[\columnwidth]{\emph{[Long version of the LICS 2021 paper, with full proofs in the appendix.]}\hfill}
+    \hspace{\columnsep}\makebox[\columnwidth]{ }}
+%\IEEEpubid{\makebox[\columnwidth]{978-1-6654-4895-6/21/\$31.00~
+%\copyright2021 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
 
@@
 \begin{figure}\vspace{-4ex}\begin{center}\hspace*{-0ex}\begin{math}
-\newcommand\peircescale{.75}
+\newcommand\peircescale{.78}
 \newcommand\drinkerscale{\peircescale}
-\newcommand\cpscale{.9}
+\newcommand\cpscale{.95}
 \begin{array}{@{}c@{\hspace{4ex}}c@{}}
@@
 {}\scalebox{\drinkerscale}{$\lkdrinkerproof$}
-\\[13ex]
+\\[15ex]
 \downarrow
@@
 \downarrow
-\\[1ex]
+\\[3ex]
 \vctr{\scalebox{\cpscale}{\peircecppic}}
@@
 \vctr{\raisebox{-2ex}[16.5ex]{\scalebox{\cpscale}{\drinkerfibcolouredpic}}}
-\\[10ex]
+\\[12ex]
 \uparrow
@@
 \uparrow
-\\[2ex]
+\\[4ex]
 {}\scalebox{\peircescale}{$\dipeirceproof$}
@@
   $\wD$ and $\cD$, which can then be permuted down.
-  %Details are in
-  %Appendix~\ref{app:LK1-decompose}.
+  Details are in
+  Appendix~\ref{app:LK1-decompose}.
 \end{proof}
@@
     \aiD, \tttD}$ can be permuted over the rules in $\set{\sw, \mix,
-    \fequ}$, which is straightforward. For the $\fequ$-instances that
+    \fequ}$, which is straightforward. For $\sw$, $\mix$, and the $\fequ$-instances that
   do not involve the quantifiers, the details can be found
-  in~\cite{dissvonlutz}, and the $\fequ$-instances concerning the
-  quantifiers are admissible in the system without the $\exists$-rule.
+  in~\cite{dissvonlutz}. The $\fequ$-instances concerning the
+  quantifiers are admissible if the \hbox{$\exists$-rule} is not present.
 \end{proof}
@@
   inference literature. 
-%  For this reason, we give the full case
-%  analysis in Appendix~\ref{app:cw-decomposition}.
+  For this reason, we give the full case
+  analysis in Appendix~\ref{app:cw-decomposition}.
   This
@@
   way as in the previous lemma.
-  %The technical details are in
-  %Appendix~\ref{app:surj->cm}.
+  The technical details are in
+  Appendix~\ref{app:surj->cm}.
 \end{proof}
@@
 
-%% We conjecture cut-elimination for first-order combinatorial proofs can be achieved via a method that is similar to the 
-%% \emph{cut-elimination by resolution} method for the sequent calculusthat via the step to first-
-%% \lutz{do we want/can say more here?}
-
-%% \todo{mention CERES}
-
 % conference papers do not normally have an appendix
@@
 
-\end{document}
+%\end{document}
 

### 2021-04-26 LICS2021-final-with-appendices-for-arxiv.tex
put colouring definition back to standard one (no adjacent vertices of same colour), since that's actually shorter than the footnote about not doing it

@@
 A graph $\gG$ is \bfit{labelled} in a set $L$ if each vertex $v\in\vG$
-has a \bfit{label} $\labelof v\in L$ associated with it.
+has an associated \bfit{label} $\labelof v\in L$.
 A graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
-equivalence relation $\linkingof\gG$ on $\vG$; each equivalence class
-is a \bfit{colour}.\footnote{In \cite{hughes:fopws}
-adjacent vertices are required to have distinct colours, since it
-is part of the standard definition of colouring in graph
-theory.
-However, this condition is redundant (ommitted here), since it is implied
-by the preclusion of bimatchings in the next section.}
-%Therefore we do not have this additional condition here.}
+equivalence relation $\linkingof\gG$ on $\vG$
+such that $v\linkingof\gG$ only if $vw\tightnotin\eG$; each equivalence class
+is a \bfit{colour}.
+% \footnote{In \cite{hughes:pws} and \cite{hughes:fopws}
+% adjacent vertices must have distinct colours, as
+% is part of the standard definition of colouring in graph
+% theory.
+% We choose to omit this condition, since it is implied
+% by the preclusion of bimatchings in Def.\,\ref{def:fonet}.}
+% %Therefore we do not have this additional condition here.}
 A \bfit{vertex renaming} of

### 2021-04-27 LICS2021-final-with-appendices-for-arxiv.tex
reverted colouring

@@
 A graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
-equivalence relation $\linkingof\gG$ on $\vG$
-such that $v\linkingof\gG$ only if $vw\tightnotin\eG$; each equivalence class
-is a \bfit{colour}.
-% \footnote{In \cite{hughes:pws} and \cite{hughes:fopws}
-% adjacent vertices must have distinct colours, as
-% is part of the standard definition of colouring in graph
-% theory.
-% We choose to omit this condition, since it is implied
-% by the preclusion of bimatchings in Def.\,\ref{def:fonet}.}
-% %Therefore we do not have this additional condition here.}
+equivalence relation $\linkingof\gG$ on $\vG$;
+%such that $v\linkingof\gG$ only if $vw\tightnotin\eG$;
+each equivalence class is a \bfit{colour}.\footnote{In
+\cite{hughes:pws} and \cite{hughes:fopws}
+adjacent vertices must have distinct colours, following
+the standard definition of colouring in graph
+theory.
+We choose to omit this condition here, as it is implied
+by the preclusion of bimatchings in Def.\,\ref{def:fonet}.}
+%Therefore we do not have this additional condition here.}
 A \bfit{vertex renaming} of
@@
 
-\begin{definition}[{\cite[\S5]{hughes:fopws}}]
+\begin{definition}[{\cite[\S5]{hughes:fopws}}]\label{def:fonet}
 A \bfit{first-order net} or \bfit{fonet} is a linked fograph which

### 2021-04-27 LICS2021-final-with-appendices-for-arxiv.tex
improved description of Fig 1 examples, per referee request

@@
 %depicted below-left,
-a homomorphism from a coloured graph to a graph labelled with
-propositional variables.
+a homomorphism from a 4-vertex graph with two colours (above) to a 4-vertex graph labelled with
+propositional variables (below); dotted vertical lines define the homomorphism, from above to below.
 %
@@
 is shown on the right of Fig.\,\ref{fig:translate}, 
-a homomorphism from a partially coloured graph to a labelled graph.
+a homomorphism from a 5-vertex partially coloured graph to a 4-vertex labelled graph.
 However, even though Hughes proves soundness and completeness, the 

### 2021-04-27 LICS2021-final-with-appendices-for-arxiv.tex
tweak

@@
 is shown on the right of Fig.\,\ref{fig:translate}, 
-a homomorphism from a 5-vertex partially coloured graph to a 4-vertex labelled graph.
+a homomorphism from a 5-vertex partially coloured graph (with one colour) to a 4-vertex labelled graph.
 However, even though Hughes proves soundness and completeness, the 

### 2021-05-07 LICS2021-final-for-proceedings.tex

--- 2021-04-27 LICS2021-final-with-appendices-for-arxiv.tex
@@
 %\usepackage[switch]{lineno}
-\pagestyle{plain}
+%\pagestyle{plain}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \IEEEoverridecommandlockouts
-\IEEEpubid{\makebox[\columnwidth]{\emph{[Long version of the LICS 2021 paper, with full proofs in the appendix.]}\hfill}
-    \hspace{\columnsep}\makebox[\columnwidth]{ }}
-%\IEEEpubid{\makebox[\columnwidth]{978-1-6654-4895-6/21/\$31.00~
-%\copyright2021 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
+\IEEEpubid{\makebox[\columnwidth]{978-1-6654-4895-6/21/\$31.00~
+\copyright2021 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
 
@@
 
-\begin{thm}[\cite{duffin:65}]\label{thm:cograph}
+\begin{thm}[\cite{Ler71,CLS81}]\label{thm:cograph}
   A graph is a cograph iff it can be constructed from the singletons
@@
   Details are in
-  Appendix~\ref{app:LK1-decompose}.
+  Appendix~A of~\cite{HSW21:arxiv}.
 \end{proof}
@@
   For this reason, we give the full case
-  analysis in Appendix~\ref{app:cw-decomposition}.
+  analysis in Appendix~B of~\cite{HSW21:arxiv}.
   This
@@
   The technical details are in
-  Appendix~\ref{app:surj->cm}.
+  Appendix~C of~\cite{HSW21:arxiv}.
 \end{proof}
@@
 
-%\end{document}
-
-%\clearpage
-\newpage
-\appendix
-
-\subsection{Proof of Theorem~\ref{thm:LK1-decompose}}
-\label{app:LK1-decompose}
-
-\begin{proof}[Proof of Theorem~\ref{thm:LK1-decompose}]
-
-Write $\fv(A)$ for the set of variables which occur free in $A$.
-
-Note that the instances of $\wrD,\cD$ in $\Deri_2$ are deep, but inside sequent contexts.
-
-First, if an instance of $\vlinf{\weakr}{}{\sqn{\Gamma,A}}{\sqn{\Gamma}}$
- is followed by a rule in which $A$ is not in the principal
-formula, it can be permuted downwards.
-Otherwise, the proof can be transformed using the following rewriting rules.
-
-\begin{equation*}
-\vlderivation{
-  \vliin{\vlan}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
-      \vlhy{\sqns{\Gamma}}}}{
-    \vlhy{\sqns{B, \Delta}}}}
-\leadsto
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, A \vlan B, \Delta}}{
-    \vlin{\weakr}{}{\vlvdots}{
-      \vlhy{\sqns{\Gamma}}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\vlor}{}{\sqns{\Gamma, A \vlor B}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A, B}}{
-      \vlhy{\sqns{\Gamma, A}}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{\sqns{\Gamma, A \vlor B}}{
-    \vlhy{\sqns{\Gamma, A}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\exists}{}{\sqns{\Gamma, \exists x.A}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A\ssubst{x}{t}}}{
-      \vlhy{\sqns{\Gamma}}}}}
-\leadsto
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, \exists x.A}}{
-    \vlhy{\sqns{\Gamma}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\forall}{}{\sqns{\Gamma, \forall x.A}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A}}{
-      \vlhy{\sqns{\Gamma}}}}}
-\leadsto
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, \forall x.A}}{
-    \vlhy{\sqns{\Gamma}}}}
-\end{equation*}
-\begin{equation*}
-\vlderivation{
-  \vlin{\conr}{}{\sqns{\Gamma, A}}{
-    \vlin{\weakr}{}{\sqns{\Gamma, A, A}}{
-      \vlhy{\sqns{\Gamma, A}}}}}
-\leadsto
-\vlderivation{
-  \vlhy{\sqns{\Gamma, A}}}
-\end{equation*}
-Note that in the case of $\vlor$, we use the deep rule $\wrD$ which can be
-permuted under all the rules. By using these rewriting rules, we can eventually get
-a derivation with all the instances of $\weakr$ and $\wrD$ at the bottom. Now observe
-that the instances of $\conr$ in $\Deri$ can be transformed using the following
-rule:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\conr}{}{\sqns{\Gamma, A}}{
-    \vlhy{\sqns{\Gamma, A, A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cD}{}{\sqns{\Gamma, A}}{
-    \vlin{\vlor}{}{\sqns{\Gamma, A \vlor A}}{
-      \vlhy{\sqns{\Gamma, A, A}}}}}
-\end{equation*}
-
-Knowing that $\cD$ can be permuted under all the rules of $\FOMLL$, we
-eventually obtain a derivation:
-\begin{equation*}
-\vlderivation{
-  \vlde{\set{\weakr, \wrD,\cD,\fequ}}{\Deri'_2}{\sqns{\Gamma}}{
-    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma'}}{
-      \vlhy{\quad}}{
-      \vlhy{}}{
-      \vlhy{}}}}
-\end{equation*}
-Note that $\fequ$ is required here since the permutation of formulas is implicit
-in $\FOMLL$.
-
-By transforming each sequent of $\Deri'_2$ into its corresponding formula, and by
-considering the following rewriting rule:
-\begin{equation*}
-\vlderivation{
-  \vlin{\weakr}{}{\sqns{\Gamma, A}}{
-    \vlhy{\sqns{\Gamma}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{\sqns{\form{\Gamma} \vlor A}}{
-    \vlhy{\sqns{\form{\Gamma}}}}}
-\end{equation*},
-we obtain a derivation
-\begin{equation*}
-\vlderivation{
-  \vlde{\set{\wrD,\cD,\fequ}}{\Deri_2}{\sqns{\form{\Gamma}}}{
-    \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\form{\Gamma'}}}{
-      \vlhy{\quad}}{
-      \vlhy{}}{
-      \vlhy{}}}}
-\end{equation*}
-where $\Deri_1$ can be obtained from $\Deri'_1$
-by applying the $\vlor$ rule.
-\end{proof}
-
-\subsection{Rule permutation for the proof of Lemma~\ref{lem:cw-decomposition}}
-\label{app:cw-decomposition}
-We construct a rewriting system based on rule permutation on derivations in $\set{\wrD, \wfaD, \acD,
-\cfaD, \me, \mfaD, \mexD, \fequ}$ that allows us to reach a derivation of the
-form 
-\begin{equation*}
-    \vlderivation{
-      \vlde{\set{\wrD,\wfaD,\fequ}}{}{B}{
-        \vlde{\set{\acD,\cfaD}}{}{B'}{
-          \vlde{\set{\me,\mfaD,\mexD,\fequ}}{}{A'}{
-            \vlhy{A}}}}}
-\end{equation*}
-from any derivation. Intuitively, we want to move all the instances of $\rr \in
-\set{\wrD, \wfaD}$ downwards and all the instances of $\rr' \in \set{\me,
-\mfaD, \mexD}$ upwards.
-
-We first study the interactions between two rules. Certain cases are unsolved at
-this stage, and they are considered later when we study the interactions between
-two non-$\fequ$ rule instances separated by $\fequ$. Only non-trivial cases are
-presented here:
-\begin{itemize}
-\item $\rr_1/\rr_2$, where $\rr_1 \in \set{\wrD, \wfaD}$ and $\rr_2 \in
-\set{\acD, \cfaD, \me, \mfaD, \mexD}$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\acD}{}{a}{
-    \vlin{\wrD}{}{a \vlor a}{ 
-      \vlhy{a}}}}
-\leadsto
-\vlderivation{
-  \vlhy{a}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\wrD}{}{(A \vlan C) \vlor (B \vlan D)}{
-      \vlhy{A \vlan C}}}}
-\leadsto 
-\vlderivation{
-  \vlin{\wrD}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\wrD}{}{(A \vlor B) \vlan C}{
-      \vlhy{A \vlan C}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\wrD}{}{(\forall x.A) \vlor (\forall x.B)}{
-      \vlhy{\forall x.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-    \vlhy{\forall x.A}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{\forall x.A}{
-    \vlin{\wfaD}{}{\forall x.\forall x.A}{
-      \vlhy{\forall x.A}}}}
-\leadsto
-\vlderivation{
-  \vlhy{\forall x.A}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\wfaD}{}{(\forall x.A) \vlor (\forall x.B)}{
-      \vlhy{A \vlor (\forall x.B)}}}}
-\leadsto
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlhy{A \vlor (\forall x.B)}}} 
-\end{equation*}
-where in the last case, $x$ is not free in $A$.
-
-\item $\rr_1/\rr_2$, where $\rr_1 \in \set{\acD, \cfaD}$ and $\rr_2 \in
-\set{\me, \mfaD, \mexD}$: 
-  \begin{equation*}
-  \scalebox{.9}{$
-  \vlderivation{
-    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
-      \vlin{\cfaD}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
-        \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\mfaD}{}{\Scons{\forall x.(A \vlor B)}}{
-      \vlin{\fequ}{}{\Scons{(\forall x.A) \vlor (\forall x.B)}}{
-        \vlin{\mfaD}{}{\Scons{\forall x.(\forall x.A \vlor B)}}{
-          \vlhy{\Scons{(\forall x.\forall x.A) \vlor (\forall x.B)}}}}}}$}
-  \end{equation*}
-
-\item $\cfaD/\fequ$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall y.\forall x.A}{
-    \vlin{\cfaD}{}{\forall x.\forall y.A}{
-      \vlhy{\forall x.\forall x.\forall y.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cfaD}{}{\forall y.\forall x.A}{
-    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
-      \vlhy{\forall x.\forall x.\forall y.A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
-    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-    \vlin{\fequ}{}{(\forall x.\forall x. A) \vlor B}{
-      \vlhy{\forall x.\forall x.(A \vlor B)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
-\leadsto
-\vlderivation{
-  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
-      \vlhy{(\forall x.\forall x.A) \vlor B}}}}
-\end{equation*}
-where in the last two cases, $x$ is not free in $B$.
-
-\item $\wrD/\fequ$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{B \vlor A}{
-    \vlin{\wrD}{}{A \vlor B}{
-      \vlhy{A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{A \vlor (B \vlor C)}{
-    \vlin{\wrD}{}{(A \vlor B) \vlor C)}{
-      \vlhy{A \vlor C}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
-    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-      \vlhy{\forall x.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{(\forall x. A) \vlor B}{
-    \vlhy{\forall x.A}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
-    \vlin{\wrD}{}{\forall x.(B \vlor A)}{
-      \vlhy{\forall x.B}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlin{\wrD}{}{(\forall x.A) \vlor B}{
-      \vlhy{\forall x.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-    \vlhy{\forall x.A}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlin{\wrD}{}{B \vlor (\forall x.A)}{
-      \vlhy{B}}}}
-\end{equation*}
-where in the last four cases, $x$ is not free in $B$.
-\item $\wfaD/\fequ$:
-
-In the following two cases, we assume $x \neq y$ (otherwise they are trivial).
-
-\begin{equation*}
-\scalebox{.9}{$
-\vlderivation{
-  \vlin{\fequ}{}{\forall y.\forall x.A}{
-    \vlin{\wfaD}{(x \notin \fv(\forall y.A))}{\forall x.\forall y.A}{
-      \vlhy{\forall y.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wfaD}{(x \notin \fv(A))}{\forall y.\forall x.A}{
-    \vlhy{\forall y.A}}}$}
-\end{equation*}
-
-\begin{equation*}
-\scalebox{.9}{$
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.\forall y.A}{
-    \vlin{\wfaD}{(x \notin \fv(A))}{\forall y.\forall x.A}{
-      \vlhy{\forall y.A}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wfaD}{(x \notin \fv(\forall y.A))}{\forall x.\forall y.A}{
-    \vlhy{\forall y.A}}}$}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{(\forall x.A) \vlor B}{
-    \vlin{\wfaD}{}{\forall x.(A \vlor B)}{
-      \vlhy{A \vlor B}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wfaD}{}{(\forall x.A) \vlor B}{
-    \vlhy{A \vlor B}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlin{\wfaD}{}{(\forall x.A) \vlor B}{
-      \vlhy{A \vlor B}}}}
-\leadsto
-\vlderivation{
-  \vlin{\wfaD}{}{\forall x.(A \vlor B)}{
-    \vlhy{A \vlor B}}}
-\end{equation*}
-where in the last two cases, the constraint on $x$ on the left-hand side implies
-that of the right-hand side.
-
-\item $\fequ/\cfaD$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{\forall x.\forall y.A}{
-    \vlin{\fequ}{}{\forall x.\forall x.\forall y. A}{
-      \vlhy{\forall x.\forall y.\forall x.A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{\forall y.\forall x.A}{
-    \vlin{\fequ}{}{\forall y.\forall x.\forall x.A}{
-      \vlhy{\forall x.\forall y.\forall x.A}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-    \vlin{\fequ}{(x \notin \fv(B))}{(\forall x.\forall x.A) \vlor B}{
-      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{(x \notin \fv(B))}{\forall x.\forall x.(A \vlor B)}{
-      \vlhy{\forall x.((\forall x.A) \vlor B)}}}}
-\end{equation*}
-
-\item $\fequ/\me$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
-      \vlhy{(C \vlan A) \vlor (B \vlan D)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
-      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
-\leadsto
-\vlderivation{
-  \vlin{\fequ}{}{(A \vlor B) \vlan (C \vlor D)}{
-    \vlin{\me}{}{(B \vlor A) \vlan (D \vlor C)}{
-      \vlhy{(B \vlan D) \vlor (A \vlan C)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{(A \vlor B) \vlan ((C \vlan E) \vlor D)}{
-    \vlin{\fequ}{}{(A \vlan (C \vlan E)) \vlor (B \vlan D)}{
-      \vlhy{((A \vlan C) \vlan E) \vlor (B \vlan D)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
-    \vlin{\fequ}{(x \notin \fv(B \vlan D))}{\forall x.((A \vlan C) \vlor (B \vlan D))}{
-      \vlhy{(\forall x.(A \vlan C)) \vlor (B \vlan D)}}}}
-\end{equation*}
-
-\item $\fequ/\mfaD$:
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
-      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
-\leadsto
-\vlderivation{
-  \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-    \vlin{\mfaD}{}{\forall x.(B \vlor A)}{
-      \vlhy{(\forall x.B) \vlor (\forall x.A)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.((\forall y.A) \vlor B)}{
-    \vlin{\fequ}{}{(\forall x.\forall y.A) \vlor (\forall x.B)}{
-      \vlhy{(\forall y.\forall x.A) \vlor (\forall x.B)}}}}
-\end{equation*}
-
-\begin{equation*}
-\vlderivation{
-  \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-    \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
-      \vlhy{\forall x.(A \vlor (\forall x.B))}}}}
-\end{equation*}
-
-\item $\fequ/\mexD$: similar to $\fequ/\mfaD$
-
-\end{itemize}
-
-Interactions between two non-$\fequ$ rules with the presence of $\fequ$ in
-between:
-
-\begin{itemize}
-\item $\cfaD/\fequ/\rr$ where $\rr \in \set{\me, \mfaD, \mexD}$: First permute
-$\cfaD$ under $\fequ$ and then permute $\cfaD$ under $\rr$.
-
-\item $\acD/\fequ/\rr$ where $\rr \in \set{\me, \mfaD, \mexD}$: First permute
-$\acD$ under $\fequ$ and then permute $\acD$ under $\rr$.
-
-\item $\wrD/\fequ/\cfaD$:
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-      \vlin{\fequ}{}{(\forall x.\forall x.A) \vlor B}{
-        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
-          \vlhy{\forall x.\forall x.A}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{(\forall x.A) \vlor B}{
-      \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-        \vlhy{\forall x.\forall x.A}}}}
-  \end{equation*}
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\cfaD}{}{(\forall x.A) \vlor B}{
-      \vlin{\fequ}{}{(\forall x.\forall x.A) \vlor B}{
-        \vlin{\wrD}{}{\forall x.(B \vlor (\forall x.A))}{
-          \vlhy{\forall x.B}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\fequ}{}{(\forall x.A) \vlor B}{
-      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
-        \vlhy{\forall x.B}}}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-      \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
-        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
-          \vlhy{\forall x.\forall x.A}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-      \vlin{\cfaD}{}{\forall x.A}{
-        \vlhy{\forall x.\forall x.A}}}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\cfaD}{}{\forall x.(A \vlor B)}{
-      \vlin{\fequ}{}{\forall x.\forall x.(A \vlor B)}{
-        \vlin{\wrD}{}{\forall x.(B \vlor (\forall x.A))}{
-          \vlhy{\forall x.B}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
-        \vlhy{\forall x.B}}}}
-  \end{equation*}
-  where in all four cases, $x$ is not free in $B$.
-\item $\wrD/\fequ/\acD$:
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\acD}{}{a \vlor B}{
-      \vlin{\fequ}{}{(a \vlor a) \vlor B}{
-        \vlin{\wrD}{}{(a \vlor B) \vlor a}{
-          \vlhy{a \vlor B}}}}}
-  \leadsto
-  \vlderivation{
-    \vlhy{a \vlor B}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\acD}{}{a \vlor B}{
-      \vlin{\fequ}{}{(a \vlor a) \vlor B}{
-        \vlin{\wrD}{}{a \vlor (a \vlor B)}{
-          \vlhy{a}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{a \vlor B}{
-      \vlhy{a}}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\acD}{}{\forall x.a}{
-      \vlin{\fequ}{(x \notin \fv(a))}{\forall x.(a \vlor a)}{
-        \vlin{\wrD}{}{(\forall x.a) \vlor a}{
-          \vlhy{\forall x.a}}}}}
-  \leadsto
-  \vlderivation{
-    \vlhy{\forall x.a}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\acD}{}{\forall x.a}{
-      \vlin{\fequ}{(x \notin \fv(a))}{\forall x.(a \vlor a)}{
-        \vlin{\wrD}{}{a \vlor (\forall x.a)}{
-          \vlhy{a}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wfaD}{(x \notin \fv(a))}{\forall x.a}{
-      \vlhy{a}}}
-  \end{equation*}
-
-\item $\wrD/\fequ/\me$:
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\me}{}{(A \vlor B) \vlan (C \vlor D)}{
-      \vlin{\fequ}{}{(A \vlan C) \vlor (B \vlan D)}{
-        \vlin{\wrD}{}{(C \vlan A) \vlor (B \vlan D)}{
-          \vlhy{C \vlan A}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{(A \vlor B) \vlan (C \vlor D)}{
-      \vlin{\wrD}{}{(A \vlor B) \vlan C}{
-        \vlin{\fequ}{}{A \vlan C}{
-          \vlhy{C \vlan A}}}}}
-  \end{equation*}
-
-  \begin{equation*}
-  \scalebox{.9}{$
-  \vlderivation{
-    \vlin{\me}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
-      \vlin{\fequ}{}{\forall x.((A \vlan C) \vlor (B \vlan
-D))}{
-        \vlin{\wrD}{}{(B \vlan D) \vlor (\forall x.(A \vlan C))}{
-          \vlhy{B \vlan D}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\fequ}{}{\forall x.((A \vlor B) \vlan (C \vlor D))}{
-      \vlin{\wrD}{}{\forall x.((B \vlor A) \vlan (D \vlor C))}{
-        \vlin{\wrD}{}{\forall x.((B \vlor A) \vlan D)}{
-          \vlin{\faD}{}{\forall x.(B \vlan D)}{
-            \vlhy{B \vlan D}}}}}}$}
-  \end{equation*}
-  where in the second case, $x$ is free in $B \vlan D$.
-
-\item $\wrD/\fequ/\mfaD$:
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-      \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
-        \vlin{\wrD}{}{(\forall x.B) \vlor (\forall x.A)}{
-          \vlhy{\forall x.B}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\fequ}{}{\forall x.(A \vlor B)}{
-      \vlin{\wrD}{}{\forall x.(B \vlor A)}{
-        \vlhy{\forall x.B}}}}
-  \end{equation*}
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\mfaD}{}{\forall x.(A \vlor B)}{
-      \vlin{\fequ}{}{(\forall x.A) \vlor (\forall x.B)}{
-        \vlin{\wrD}{}{\forall x.((\forall x.A) \vlor B)}{
-          \vlhy{\forall x.\forall x.A}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\wrD}{}{\forall x.(A \vlor B)}{
-      \vlin{\cfaD}{}{\forall x.A}{
-        \vlhy{\forall x.\forall x.A}}}}
-  \end{equation*}
-
-\item $\wrD/\fequ/\mexD$:
-
-  \begin{equation*}
-  \vlderivation{
-    \vlin{\mexD}{}{\exists x.(A \vlor B)}{
-      \vlin{\fequ}{}{(\exists x.A) \vlor (\exists x.B)}{
-        \vlin{\wrD}{}{(\exists x.B) \vlor (\exists x.A)}{
-          \vlhy{\exists x.B}}}}}
-  \leadsto
-  \vlderivation{
-    \vlin{\fequ}{}{\exists x.(A \vlor B)}{
-      \vlin{\wrD}{}{\exists x.(B \vlor A)}{
-        \vlhy{\exists x.B}}}}
-  \end{equation*}
-
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Proof of Lemma~\ref{lem:surj->cm}}
-\label{app:surj->cm}
-
-\begin{proof}[Proof of Lemma~\ref{lem:surj->cm}]
-  By
-  \cite[Proposition~7.5]{str:ral:tableaux19}, there is a derivation
-  $\vlder{\set{\acD,\me,\PE\fequ}}{\DDeri}{\PE H}{\PE{(G\rsubstof\phi)}}$,
-   We plan to show that $\DDeri$ can be lifted to
-  $\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$. However, observe that not
-  every formula occurring in $\DDeri$ is a propositional
-  encoding. There are two reasons for this: (i) we might have
-  $P\PE\fequ Q$ where $P$ is a propositional encoding but $Q$ is not,
-  and (ii) the rule $\acD$ can duplicate an atom
-  $x\in\VAR$. Let us write $\acDx$ for such instances.
-  The problem with (i) is that we could have the following situation
-  \begin{equation}
-    \label{eq:m-illegal}
-    \vlderivation{
-      \vlin{\me}{}{\Scons{((x\vlan E)\vlor(x\vlan F))\vlan(C\vlor D)}}{
-        \vlin{\PE\fequ}{}{\Scons{((x\vlan E)\vlan C)\vlor((x\vlan F)\vlan D)}}{
-          \vlhy{\Scons{(x\vlan (E\vlan C))\vlor(x\vlan (F\vlan D))}}}}}
-  \end{equation}
-  where $x$ occurs in $C\vlor D$. Then premise and conclusion are both
-  propositional encodings, but the whole derivation cannot be
-  lifted. However, since we demand that the mapping is a fibration
-  (and therefore a homomorphism) on the binding graphs, there must be
-  another instance of $\me$ further below in the derivation:
-  \begin{equation}
-    \vlderivation{
-      \vlin{\me}{}{S'\cons{(x\vlor x)\vlan(E\vlor F)}}{
-        \vlhy{S'\cons{(x\vlan E)\vlor(x\vlan F)}}}}
-  \end{equation}
-  We can permute both instances via the following more general scheme
-  (see~\cite{str:07:RTA,lamarche:gap} for a general discussion on
-  permutations of the $\me$-rule):
-  \begin{equation}
-    \label{eq:m-permutation}
-    \scalebox{.66}{$
-    \vlderivation{
-      \vlin{\me}{}{\Scons{(G\vlor H)\vlan(E\vlor F)\vlan(C\vlor D)}}{
-        \vlin{\me}{}{\Scons{((G\vlan E)\vlor(H\vlan F))\vlan(C\vlor D)}}{
-          \vlhy{\Scons{(G\vlan E\vlan C)\vlor(G\vlan F\vlan D)}}}}}
-    \;
-    \leftrightarrow
-    \;
-    \vlderivation{
-      \vlin{\me}{}{\Scons{(G\vlor H)\vlan(E\vlor F)\vlan(C\vlor D)}}{
-        \vlin{\me}{}{\Scons{(G\vlor H)\vlan((E\vlan C)\vlor(F\vlan D))}}{
-          \vlhy{\Scons{(G\vlan E\vlan C)\vlor(G\vlan F\vlan D)}}}}}    
-    $}
-  \end{equation}
-  We omitted some instances of $\PE\fequ$ and some parentheses.  We
-  now call instances of $\me$ as in~\eqref{eq:m-illegal}
-  \bfit{illegal}, and we can transform $\DDeri$ through
-  $\me$-permutations~\eqref{eq:m-permutation} into a derivation that
-  does not contain any illegal $\me$-instances.
-  To
-  address (ii),
-  we also apply a permutation argument, permuting all
-  instances of $\acDx$ up until they either reach the top of the
-  derivation or an instance of $\me$ which separates the two atoms in
-  the premise. More precisely, we consider the following inference rule
-  \begin{equation}
-    \label{eq:acDeq}
-    \vlinf{\acDeq}{}{\Scons{x}}{S_0\cons{S_1\cons{x}\vlor S_2\cons{x}}}
-  \end{equation}
-  where $S_1\conhole\fequ\conhole\vlor E$ and
-  $S_2\conhole\fequ\conhole\vlor F$ and $S\conhole\fequ
-  S_0\cons{\conhole\vlor E\vlor F}$ for some formulas $E$ and $F$, where $E$ or $F$ or both might be empty. The
-  rule $\acDeq$ permutes over $\fequ$, $\acD$, and other instances of $\acDeq$,
-  and over instances of $\me$ if they occur inside $S_0$ or $S_1$ or
-  $S_2$. The only situation in which $\acDeq$ cannot be permuted up is
-  the following:
-  \begin{equation}
-    \label{eq:mac}
-    \vlderivation{
-      \vlin{\acDeq}{}{\Scons{R\cons{x}\vlan(C\vlor D)}}{
-        \vlin{\me}{}{\Scons{(R_1\cons{x}\vlor R_2\cons{x})\vlan(C\vlor D)}}{
-          \vlhy{\Scons{(R_1\cons{x}\vlan C)\vlor (R_2\cons{x}\vlan D)}}}}}
-  \end{equation}
-  We can therefore assume that all instances of $\acDx$, that contract
-  an atom $x\in\VAR$ are either at the top of $\DDeri$ or below a
-  $\me$-instance as in~\eqref{eq:mac}. We now lift $\DDeri$ to
-  $\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}$, proceed by induction on
-  the height of $\DDeri$, beginning at the top, making a case
-  analysis on the topmost rule that is not a~$\fequ$.
-  \begin{itemize}
-  \item $\acDx$: We know that the premise of~\eqref{eq:acDeq} is a
-    propositional encoding. Hence, $S_1\conhole=\conhole\vlor \PE E$ and
-    $S_2\conhole=\conhole\vlor \PE F$ and both $x$ are universals, and
-    $\PE E\vlor \PE F$ contains all occurrences of $x$ bound by that
-    universal. We have the following subcases:
-    \begin{itemize}
-    \item $E$ and $F$ are both non-empty: We have
-      \begin{equation*}
-        \vlinf{\acDeq}{}{\PE S\cons{x\vlor (\PE E\vlor \PE F)}}{\PE S\cons{(x\vlor \PE E)\vlor (x\vlor\PE F)}}
-      \end{equation*}
-      which can be lifted to
-      \begin{equation*}
-        \vlinf{\mfaD}{}{\Scons{\forall x.(E\vlor F)}}{S\cons{(\forall x.E)\vlor (\forall x.F)}}
-      \end{equation*}
-      where $\PE S\conhole, \PE E, \PE F$ are the propositional encodings of $\Sconhole,E,F$, respectively.
-    \item $\PE E$ is empty and $\PE F$ is non-empty: We have
-      \begin{equation*}
-        \vlinf{\acDeq}{}{\PE S\cons{x\vlor \PE F)}}{\PE S\cons{x\vlor (x\vlor \PE F)}}
-      \end{equation*}
-      which can be lifted to
-      \begin{equation*}
-        \vlinf{\cfaD}{}{\Scons{\forall x.F}}{S\cons{\forall x.\forall x.F}}
-      \end{equation*}
-    \item $\PE E$ is non-empty and $\PE F$ is empty: This is similar to the previous case.
-    \item $\PE E$ and $\PE F$ are both empty: This is impossible as the
-      premise would not be a propositional encoding.
-    \end{itemize}
-  \item $\acD$ (contracting an ordinary atom): This can trivially be lifted.
-  \item $\me$: There are several cases to consider.
-    \begin{itemize}
-    \item If none of the four principal formulas in the premise is $x$
-      or $x\vlor F$ for some formula $F$ and $x\in\VAR$, then this
-      instance of $\me$ can trivially be lifted, and we can
-      proceed by induction hypothesis.
-  \item If exactly one of the four principal formulas in the premise
-    is $x$ for some $x\in\VAR$, then this $x$ is the encoding of an existential in the
-    premise and of an universal in the conclusion. This is impossible,
-    as $\phi$ has to preserve existentials.
-  \item If two of the four principal formulas in the premise
-    are $x$ for some $x\in\VAR$, then we are in the following special case of~\eqref{eq:mac}:
-    \begin{equation*}
-      \vlderivation{
-        \vlin{\acDeq}{}{\Scons{x\vlan(C\vlor D)}}{
-          \vlin{\me}{}{\Scons{(x\vlor x)\vlan(C\vlor D)}}{
-            \vlhy{\Scons{(x\vlan C)\vlor (x\vlan D)}}}}}
-    \end{equation*}
-    which can be lifted immediately to
-    \begin{equation*}
-      \vlinf{\mexD}{}{\Scons{\exists x.(C\vlor D)}}{\Scons{(\exists x.C)\vlor(\exists x.D)}}
-    \end{equation*}
-  \item We have a situation~\eqref{eq:mac} where
-    $R_1\cons{x}\fequ x\vlor E$ for some $E$ and $R_2\cons{x}\fequ
-    x\vlor F$ for some $F$ with $R\cons{x}\fequ x\vlor E\vlor
-    F$ (Otherwise, the application of $\acDeq$ would not be correct.)
-    That means, we have: 
-    \begin{equation*}
-      \vlderivation{
-        \vlin{\acDeq}{}{\Scons{(x\vlor E\vlor F)\vlan(C\vlor D)}}{
-          \vlin{\me}{}{\Scons{((x\vlor E)\vlor (x\vlor F))\vlan(C\vlor D)}}{
-            \vlhy{\Scons{((x\vlor E)\vlan C)\vlor ((x\vlor F)\vlan D)}}}}}
-    \end{equation*}
-    which can be lifted to
-    \begin{equation*}
-      \vlderivation{
-        \vlin{\mfaD}{}{\Scons{(\forall x.(E\vlor F))\vlan(C\vlor D)}}{
-          \vlin{\me}{}{\Scons{((\forall x. E)\vlor (\forall x. F))\vlan(C\vlor D)}}{
-            \vlhy{\Scons{((\forall x. E)\vlan C)\vlor ((\forall x. F)\vlan D)}}}}}
-    \end{equation*}
-  \item In all other cases (e.g.\ exactly one of the principal formulas
-    is of shape $x\vlor F$ (and none is $x$), we can trivially lift
-    the $\me$-instance, as the quantifier structure is not affected.
-    \end{itemize}
-  \end{itemize}
-  Thus $\DDeri$ can be lifted to
-  $\vlder{\set{\acD,\cfaD,\me,\mfaD,\mexD,\fequ}}{\Deri}{H}{G\rsubstof\phi}$. 
-\end{proof}
 \end{document}
-
-% that's all folks
-%\end{document}

### 2021-05-07 LICS2021-final-with-appendices-for-arxiv.tex
removed one-line orphan page 18, by culling some space on page 17

@@
   another instance of $\me$ further below in the derivation:
-  \begin{equation}
+  \vspace{-2ex}\begin{equation}
     \vlderivation{
